### 2018-01-11 paper/paper_entailVis.tex
add notes

How to interpret classification task
\begin{itemize}
    \item What feature / dimension / part-of-the-input should change to
    alter the outcome

\end{itemize}

Related works
\begin{itemize}
    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
    Use partial dependency (varying along one feature and observer how prediction changes)
    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)

\end{itemize}

### 2018-01-11 src/exampleVis.py

@@ -36,6 +36,7 @@ data = [{
 
 model = modelInterface(data="../data/snli_1.0-val.hdf5", wordVec="../data/glove.hdf5", model="local_200_parikh")
 gen = sentenceGenerator()
+exit()
 
 modelVis = textEntailVisModule()
 modelVis.setData(data)

### 2018-01-11 src/modelInterface.py

@@ -6,11 +6,92 @@ python eval.py --gpuid -1 --data ../data/snli_1.0-val.hdf5
  --load_file local_200_parikh
 '''
 
+import sys
+sys.path.insert(0, '../')
+from pipeline import *
+import argparse
+import h5py
+import os
+import random
+import time
+import numpy as np
+import torch
+from torch.autograd import Variable
+from torch import nn
+from torch import cuda
+from holder import *
+from optimizer import *
+from embeddings import *
+from data import *
+from forward_hooks import *
+from eval import pick_label, evaluate
+
 class modelInterface:
     #setup model
     def __init__(self, data, wordVec, model, encoder="proj", attention="local",
                 classifier="local", dropout=0.0):
-        pass
+        # import argparse
+    	# build model
+        '''
+            Namespace(att_output='',
+            attention='local',
+            classifier='local',
+            constr='',
+            data='../data/snli_1.0-val.hdf5',
+            dropout=0.0,
+            encoder='proj',
+            fix_word_vecs=1,
+            forward_hooks='',
+
+            gpuid=-1,
+            hidden_size=200,
+            load_file='local_200_parikh',
+            num_att_labels=1,
+            num_labels=3,
+            seed=3435,
+            word_vec_size=300,
+            word_vecs='../data/glove.hdf5')
+        '''
+        opt = argparse.Namespace()
+        opt.att_output=''
+        opt.attention='local'
+        opt.classifier='local'
+        opt.constr=''
+        opt.data = data
+        opt.dropout = dropout
+        opt.encoder = encoder
+        opt.fix_word_vecs=1
+        opt.forward_hooks = ""
+
+        opt.gpuid=-1
+        opt.hidden_size=200
+        opt.load_file=model
+        opt.num_att_labels=1
+        opt.num_labels=3
+        opt.seed=3435
+        opt.word_vec_size=300
+        opt.word_vecs=wordVec
+
+        #evaluate
+
+        shared = Holder()
+    	embeddings = WordVecLookup(opt)
+    	pipeline = Pipeline(opt, shared)
+    	pretrained = torch.load('{0}.pt'.format(opt.load_file))
+
+    	# instead of directly using the pretrained model, copy parameters into a fresh new model
+    	#	this allows post-training customization
+    	print('initializing from pretrained model, might have warnings if code has been changed...')
[…]

### 2018-01-11 paper/meetingNotes.tex

%%%%% Meeting notes %%%%%

Jan 11, 2018

Discussion topics:

- What we are doing: local perturbation
- are we building a saliant map in our mind about the sentence?
  (which part of the sentence is most sensitive to the prediction)
  Should we just build it directly
- What information is important from Tao's point of view
- Comparison to other local explaianation techniques
- Where does the interpretability come from
    - It is interpretable because the application (model is still black box)
    - It is interpretable due to the inherent complexity of
      the model, sparsity linear model, rule list, dicision tree, etc.

### 2018-01-12 paper/meetingNotes.tex
update sentence generator

@@
 - What we are doing: local perturbation
-- are we building a saliant map in our mind about the sentence?
+
+- are we building a "saliant map" in our mind about the sentence?
   (which part of the sentence is most sensitive to the prediction)
   Should we just build it directly
+
 - What information is important from Tao's point of view
-- Comparison to other local explaianation techniques
+
+- Comparison to other local explaination techniques
+    - our method reveal internal states (attention)
+
 - Where does the interpretability come from
-    - It is interpretable because the application (model is still black box)
+    - It is interpretable because the application (model is still a black box)
     - It is interpretable due to the inherent complexity of

### 2018-01-12 src/exampleVis.py

@@ -34,16 +34,18 @@ data = [{
 }]
 
 
-model = modelInterface(data="../data/snli_1.0-val.hdf5", wordVec="../data/glove.hdf5", model="local_200_parikh")
+# model = modelInterface(data="../data/snli_1.0-val.hdf5", wordVec="../data/glove.hdf5", model="local_200_parikh")
 gen = sentenceGenerator()
-exit()
+# ps = gen.perturbSentence("A woman eat an apple.")
+# print ps
+# exit()
 
 modelVis = textEntailVisModule()
 modelVis.setData(data)
-modelVis.setPredictionHook(model.predict)
-modelVis.setSentencePerturbationHook(gen.perturb_noun_in_sentence)
+# modelVis.setPredictionHook(model.predict)
+# modelVis.setSentencePerturbationHook(gen.perturb_noun_in_sentence)
 
 # modelVis.callbackPredictionChange()
 #open browser for visualization
-# modelVis.show()
-modelVis.startServer()
+modelVis.show()
+# modelVis.startServer()

### 2018-01-12 src/sentenceGenerator.py

@@ -5,6 +5,82 @@ from pattern.en import pluralize, singularize
 import copy
 
 class sentenceGenerator:
-    def perturb_noun_in_sentence(self, inputSentence):
-        listOfSentence = {}
-        return listOfSentence
+    def __init__(self, train_dict='../data/snli_1.0.word.dict'):
+        self.train_tokens = {}
+    	with open(train_dict, 'r+') as f:
+    		lines = f.readlines()
+    		for l in lines:
+    			toks = l.split(" ")
+    			self.train_tokens[toks[0]] = 1
+        # print self.train_tokens
+
+    #perturb nouns and verb in the sentence
+    def perturbSentence(self, inputSentence):
+        train_tokens = self.train_tokens
+    	lemma_map = {}
+    	pos_tags = nltk.pos_tag(nltk.word_tokenize(inputSentence))
+    	nouns = [i if i[1].startswith("NN") else None for i in pos_tags]
+    	## a list of pairs (lemma, POS)
+    	noun_lemma = []
+    	for n in nouns:
+    		if n is not None:
+    			word = n[0]
+    			pos = n[1]
+    			## nltk's lemmatizer failed to make plural into singular
+    			## 	so make it manually
+    			if pos == 'NNS':
+    				noun_lemma.append((singularize(word), pos))
+    			else:
+    				noun_lemma.append((word, pos))
+    		else:
+    			noun_lemma.append(None)
+
+    	for l in noun_lemma:
+    		if l is not None:
+    			lemma = l[0]
+    			synsets = wn.synsets(lemma)
+    			if len(synsets) != 0:
+    				lemma_map[lemma] = []
+
+    			for s in synsets:
+    				## add synonyms
+    				## only add synonyms that has a single token (i.e. 	exclude '_')
+    				lemma_map[lemma].extend([ln.lower() for ln in s.lemma_names() if '_' not in ln])
+
+    				## add antonyms
+    				for syn_lemma in s.lemmas():
+    					if syn_lemma.antonyms():
+    						lemma_map[lemma].extend([ln.name().lower() for ln in syn_lemma.antonyms()])
+
+    				## filter out words not in train dict
+    				lemma_map[lemma] = [l for l in lemma_map[lemma] if l in train_tokens]
+
+    				## make synonyms unique
+    				lemma_map[lemma] = list(set(lemma_map[lemma]))
+    				## remove the lemma itself
+    				lemma_map[lemma] = [l for l in lemma_map[lemma] if l != lemma]
+
+
[…]

### 2018-01-12 src/vis/components/triangle.js

@@ -1,10 +1,0 @@
-class triangle {
-
-    constructor() {
-
-    }
-
-    draw() {
-
-    }
-}

### 2018-01-12 src/visPackage/static/components/baseComponent.js

@@ -8,7 +8,7 @@ var namespace = '/app'; //global namespace
 var socket = io.connect('http://' + document.domain + ':' + location.port +
     namespace);
 
-console.log(document.domain, location.port);
+// console.log(document.domain, location.port);
 
 class baseComponent {
     constructor(uuid) {

### 2018-01-12 src/visPackage/static/components/predictionComponent.js

@@ -65,7 +65,7 @@ class predictionComponent extends baseComponent {
 
     updateSelection() {
         if (Object.keys(this.data).length !== 0) {
-            // console.log(this.data);
+            console.log(this.data);
             var data = this.data['predictions'];
             var index = this.data['predictionsHighlight']
 

### 2018-01-19 paper/paper_entailVis.tex
please don't add pyc (which is cache file for python runtime) files to the repo
add paper template

@@
-How to interpret classification task
-\begin{itemize}
-    \item What feature / dimension / part-of-the-input should change to
-    alter the outcome
+\documentclass[journal]{vgtc}                % final (journal style)
+%\documentclass[review,journal]{vgtc}         % review (journal style)
+%\documentclass[widereview]{vgtc}             % wide-spaced review
+%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)
 
-\end{itemize}
+%% Uncomment one of the lines above depending on where your paper is
+%% in the conference process. ``review'' and ``widereview'' are for review
+%% submission, ``preprint'' is for pre-publication, and the final version
+%% doesn't use a specific qualifier.
 
-Related works
-\begin{itemize}
-    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
-    Use partial dependency (varying along one feature and observer how prediction changes)
-    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)
+%% Please use one of the ``review'' options in combination with the
+%% assigned online id (see below) ONLY if your paper uses a double blind
+%% review process. Some conferences, like IEEE Vis and InfoVis, have NOT
+%% in the past.
 
-\end{itemize}
+%% Please note that the use of figures other than the optional teaser is not permitted on the first page
+%% of the journal version.  Figures should begin on the second page and be
+%% in CMYK or Grey scale format, otherwise, colour shifting may occur
+%% during the printing process.  Papers submitted with figures other than the optional teaser on the
+%% first page will be refused. Also, the teaser figure should only have the
+%% width of the abstract as the template enforces it.
+
+%% These few lines make a distinction between latex and pdflatex calls and they
+%% bring in essential packages for graphics and font handling.
+%% Note that due to the \DeclareGraphicsExtensions{} call it is no longer necessary
+%% to provide the the path and extension of a graphics file:
+%% \includegraphics{diamondrule} is completely sufficient.
+%%
+\ifpdf%                                % if we use pdflatex
+  \pdfoutput=1\relax                   % create PDFs from pdfLaTeX
+  \pdfcompresslevel=9                  % PDF Compression
+  \pdfoptionpdfminorversion=7          % create PDF 1.7
+  \ExecuteOptions{pdftex}
+  \usepackage{graphicx}                % allow us to embed graphics files
+  \DeclareGraphicsExtensions{.pdf,.png,.jpg,.jpeg} % for pdflatex we expect .pdf, .png, or .jpg files
+\else%                                 % else we use pure latex
+  \ExecuteOptions{dvips}
+  \usepackage{graphicx}                % allow us to embed graphics files
+  \DeclareGraphicsExtensions{.eps}     % for pure latex we expect eps files
+\fi%
+
+%% it is recomended to use ``\autoref{sec:bla}'' instead of ``Fig.~\ref{sec:bla}''
+\graphicspath{{figures/}{pictures/}{images/}{./}} % where to search for the images
+
+\usepackage{microtype}                 % use micro-typography (slightly more compact, better to read)
+\PassOptionsToPackage{warn}{textcomp}  % to address font issues with \textrightarrow
+\usepackage{textcomp}                  % use better special symbols
+\usepackage{mathptmx}                  % use matching math font
+\usepackage{times}                     % we use Times as the main font
+\renewcommand*\ttdefault{txtt}         % a nicer typewriter font
+\usepackage{cite}                      % needed to automatically sort the references
+\usepackage{tabu}                      % only used for the table example
+\usepackage{booktabs}                  % only used for the table example
+%% We encourage the use of mathptmx for consistent usage of times font
+%% throughout the proceedings. However, if you encounter conflicts
+%% with other math-related packages, you may want to disable it.
+
+%% In preprint mode you may define your own headline.
+%\preprinttext{To appear in IEEE Transactions on Visualization and Computer Graphics.}
+
+%% If you are submitting a paper to a conference for review with a double
+%% blind reviewing process, please replace the value ``0'' below with your
+%% OnlineID. Otherwise, you may safely leave it at ``0''.
+\onlineid{0}
+
+%% declare the category of your paper, only shown in review mode
+\vgtccategory{Research}
+%% please declare the paper type of your paper to help reviewers, only shown in review mode
+%% choices:
+%% * algorithm/technique
+%% * application/design study
+%% * evaluation
+%% * system
+%% * theory/model
+\vgtcpapertype{please specify}
+
+%% Paper title.
+\title{How Attention Impact Language Learning Tasks? \\ A Visual Analytics Tool
+for Interpreting, Debugging, \\ and Tunning Text Entailment Model}
+
+%% This is how authors are specified in the journal style
+
+%% indicate IEEE Member or Student Member in form indicated below
+% \author{Roy G. Biv, Ed Grimley, \textit{Member, IEEE}, and Martha Stewart}
+% \authorfooter{
+% %% insert punctuation at end of each item
+% \item
+%  Roy G. Biv is with Starbucks Research. E-mail: roy.g.biv@aol.com.
+% \item
+%  Ed Grimley is with Grimley Widgets, Inc.. E-mail: ed.grimley@aol.com.
+% \item
+%  Martha Stewart is with Martha Stewart Enterprises at Microsoft
+%  Research. E-mail: martha.stewart@marthastewart.com.
+% }
+
+%other entries to be set up for journal
+\shortauthortitle{Text Entailment Model Visualization}
+%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}
+
+%% Abstract section.
+\abstract{
+
+} % end of abstract
+
+%% Keywords that describe your work. Will show as 'Index Terms' in journal
+%% please capitalize first letter and insert punctuation after last keyword
+\keywords{Natural Language Processing}
+
+%% ACM Computing Classification System (CCS).
+%% See <http://www.acm.org/class/1998/> for details.
+%% The ``\CCScat'' command takes four arguments.
+
+% \CCScatlist{ % not used in journal version
+%  \CCScat{K.6.1}{Management of Computing and Information Systems}%
+% {Project and People Management}{Life Cycle};
+%  \CCScat{K.7.m}{The Computing Profession}{Miscellaneous}{Ethics}
+% }
+
+%% Uncomment below to include a teaser figure.
+% \teaser{
+%   \centering
+%   \includegraphics[width=\linewidth]{CypressView}
+%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
+% 	\label{fig:teaser}
+% }
+
+%% Uncomment below to disable the manuscript note
+%\renewcommand{\manuscriptnotetxt}{}
+
+%% Copyright space is enabled by default as required by guidelines.
+%% It is disabled by the 'review' option or via the following command:
+% \nocopyrightspace
+
+\vgtcinsertpkg
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
+
+%% The ``\maketitle'' command must be the first command after the
+%% ``\begin{document}'' command. It prepares and prints the title block.
+
+%% the only exception to this rule is the \firstsection command
+\input{intro_entailVis.tex}
+\input{relatedWorks_entailVis.tex}
+
+%% if specified like this the section will be committed in review mode
+\acknowledgments{
+The authors wish to thank A, B, and C. This work was supported in part by
+a grant from XYZ (\# 12345-67890).}
+
+%\bibliographystyle{abbrv}
+\bibliographystyle{abbrv-doi}
+%\bibliographystyle{abbrv-doi-narrow}
+%\bibliographystyle{abbrv-doi-hyperref}
+%\bibliographystyle{abbrv-doi-hyperref-narrow}
+
+\bibliography{template}
+\end{document}

### 2018-01-19 paper/paper_entailVis.tex
add layout

@@
 \abstract{
+In Natural Language Processs (NLP) research attention mechanism has gained a
+strong following,
 
@@
 %% please capitalize first letter and insert punctuation after last keyword
-\keywords{Natural Language Processing}
+\keywords{Natural Language Processing, Interpretable Machine Learning,
+Visual Analytics}
 
@@
 %% if specified like this the section will be committed in review mode
-\acknowledgments{
-The authors wish to thank A, B, and C. This work was supported in part by
-a grant from XYZ (\# 12345-67890).}
+% \acknowledgments{
+% The authors wish to thank A, B, and C. This work was supported in part by
+% a grant from XYZ (\# 12345-67890).}
 

### 2018-01-22 paper/paper_entailVis.tex
add comments

@@
 %% Paper title.
-\title{How Attention Impact Language Learning Tasks? \\ A Visual Analytics Tool
+\title{How Alignment Impact Language Learning Tasks? \\ A Visual Analytics Tool
 for Interpreting, Debugging, \\ and Tunning Text Entailment Model}
@@
 %% Abstract section.
+% What are we doing in this paper
 \abstract{
-In Natural Language Processs (NLP) research attention mechanism has gained a
-strong following,
+(What is the highlevel motivation)
+Making sense and explaining the predictions made by deep neural networks
+is not only essential for validating and improving the model, but also
+becoming a necessity with increasing requirement for model accountabilty (e.g., for medical
+application), as well as ethics concerns regarding the potential harm the
+hidden biases learned by a black-box model~\cite{}.
+%
+
+(Limitation of the state-of-the arts)
+Model independent explanations is useful to gain intuition,
+but they lack an examination of the inner mechanism.
+%
+
+(What did we bring)
+Recently attention mechanism~\cite{} has gained a strong following in
+the Natural Language Processs (NLP) research.
 

### 2018-01-25 src/visPackage/static/components/predictionComponent.js
fix single prediction

@@ -85,9 +85,10 @@ class predictionComponent extends baseComponent {
     }
 
     onUpdatePrediction() {
-        var data = [];
-        data.push(this.data['prediction'].concat([0, 0]));
-        this.updatePredictDisplay(data);
+        var prediction = this.data['prediction'][0];
+        prediction.concat([0, 0])
+        console.log(prediction);
+        this.updatePredictDisplay([prediction]);
     }
 
     onUpdateAllPairPrediction() {

### 2018-01-29 paper/intro_entailVis.tex
add paper template
add layout
add comments

--- 2018-01-11 paper/paper_entailVis.tex
@@
+\firstsection{Introduction}
+\maketitle
+
+NLP application using attention
+\begin{itemize}
+    \item Neural translation
+    \item Text summarization
+    \item Text entailment
+    \item Text comprehension (question answering)
+\end{itemize
+
+Attention type:
+\begin{itemize}
+    \item soft vs. hard
+    \item local vs. global
+    \item hierarchical
+    \item attention over attention
+    \item gated
+\end{itemize}
+
 How to interpret classification task
@@
     alter the outcome
+    \item What Examples can you provide that is similar to the current
+    instance
 
 \end{itemize}
-
-Related works
-\begin{itemize}
-    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
-    Use partial dependency (varying along one feature and observer how prediction changes)
-    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)
-
-\end{itemize}

### 2018-01-29 paper/relatedWorks_entailVis.tex

\section{Related Works}

\begin{itemize}
    \item Depth learning vis
    \item Vis
\end{itemize}

Related works
\begin{itemize}
    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
    Use partial dependency (varying along one feature and observer how prediction changes)
    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)

\end{itemize}

### 2018-02-05 src/visPackage/static/components/attentionSentenceComponent.js
add dependency tree to attenSen, but the parse tree compuation is duplicated

@@ -41,6 +41,7 @@ class attentionSentenceComponent extends baseComponent {
     draw() {
         this._updateWidthHeight();
 
+
         if (this.data["attention"] !== undefined) {
             //clear all
             if (!d3.select(this.div).select("svg").empty())
@@ -94,22 +95,26 @@ class attentionSentenceComponent extends baseComponent {
             // console.log(this.srcWords);
             var srcWidth = this.width / (this.srcWords.length + 1);
             var targWidth = this.width / (this.targWords.length + 1);
+            this.rectHeight = this.height / 3.0 * 0.5;
             // console.log(srcWidth, targWidth);
 
+            ///////////////////// draw dependency tree //////////////////
+            this.src_dep = new dependencyTreePlot(this.svg, 'h-top',
+                this.srcPos, this.srcDepTreeData, this.width, this
+                .height);
 
-
-            //////// drawing line ///////////
+            ///////////////////// drawing line //////////////////////
             this.drawConnection();
 
-            //////// drawing rect ///////////
+            ///////////////////// drawing rect //////////////////////
             this.svg.selectAll(".sourceRect")
                 .data(this.srcWords)
                 .enter()
                 .append("rect")
-                .attr("x", (d, i) => this.srcPos[i] - srcWidth / 2.0)
-                .attr("y", this.height / 3 * 0.5)
+                .attr("x", (d, i) => this.srcPos[i].x - srcWidth / 2.0)
+                .attr("y", (d, i) => this.srcPos[i].y)
                 .attr("width", srcWidth)
-                .attr("height", this.height / 3 * 0.5)
+                .attr("height", this.rectHeight)
                 .attr("class", "sourceRect")
                 .style("fill", "#87CEFA")
                 .style("opacity", (d, i) => this.srcAtt[i] * 0.5);
@@ -118,35 +123,35 @@ class attentionSentenceComponent extends baseComponent {
                 .data(this.targWords)
                 .enter()
                 .append("rect")
-                .attr("x", (d, i) => this.targPos[i] - targWidth / 2.0)
-                .attr("y", this.height / 3 * 2.0)
+                .attr("x", (d, i) => this.targPos[i].x - targWidth / 2.0)
+                .attr("y", (d, i) => this.targPos[i].y - this.rectHeight)
                 .attr("width", targWidth)
-                .attr("height", this.height / 3 * 0.5)
+                .attr("height", this.rectHeight)
                 .attr("class", "targRect")
                 .style("fill", "#87CEFA")
[…]

### 2018-02-07 paper/paper_entailVis.tex
fix single prediction
init

@@
 (What is the highlevel motivation)
-Making sense and explaining the predictions made by deep neural networks
-is not only essential for validating and improving the model, but also
-becoming a necessity with increasing requirement for model accountabilty (e.g., for medical
-application), as well as ethics concerns regarding the potential harm the
-hidden biases learned by a black-box model~\cite{}.
+Making sense and explaining the predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing requirement for model accountability (e.g., for medical application where the decision have serious consequences) and model fairness ( e.g., the model may capture and perpetuate the biases exists in the training data~\cite{}).
+
 %
@@
 the Natural Language Processs (NLP) research.
-
 } % end of abstract

### 2018-02-07 src/attention/local_attention.py

@@ -1,0 +1,122 @@
+import sys
+sys.path.insert(0, '../')
+
+import torch
+from torch import nn
+from view import *
+from holder import *
+
+class LocalAttention(torch.nn.Module):
+	def __init__(self, opt, shared):
+		super(LocalAttention, self).__init__()
+		self.f = nn.Sequential(
+			nn.Dropout(opt.dropout),
+			nn.Linear(opt.hidden_size, opt.hidden_size),
+			nn.ReLU(),
+			nn.Dropout(opt.dropout),
+			nn.Linear(opt.hidden_size, opt.hidden_size),
+			nn.ReLU())
+
+		# temp stuff will be changed on the fly
+		batch_l = 1
+		sent_l1 = 2
+		sent_l2 = 3
+
+		self.input_view1 = View(batch_l * sent_l1, opt.hidden_size)
+		self.input_view2 = View(batch_l * sent_l2, opt.hidden_size)
+		self.input_unview1 = View(batch_l, sent_l1, opt.hidden_size)
+		self.input_unview2 = View(batch_l, sent_l2, opt.hidden_size)
+		self.score_view1 = View(batch_l * sent_l1, sent_l2)
+		self.score_view2 = View(batch_l * sent_l2, sent_l1)
+		self.score_unview1 = View(batch_l, sent_l1, sent_l2)
+		self.score_unview2 = View(batch_l, sent_l2, sent_l1)
+		self.softmax = nn.Softmax(1)
+
+		# bookkeeping
+		self.shared = shared
+		self.dropout = opt.dropout
+		self.hidden_size = opt.hidden_size
+
+	def init_weight_from(self, a):
+		for i in [1,4]:
+			self.f[i].weight.data.copy_(a.f[i].weight.data)
+			if self.f[i].bias is not None and a.f[i].bias is not None:
+				self.f[i].bias.data.copy_(a.f[i].bias.data)
+
+
+	def forward(self, sent1, sent2):
+		self.update_context()
+
+		hidden1 = self.input_unview1(self.f(self.input_view1(sent1)))
+		hidden2 = self.input_unview2(self.f(self.input_view2(sent2)))
+		# score tensors of size batch_l x sent_l1 x sent_l2
+		score1 = hidden1.bmm(hidden2.transpose(1,2))
+		score2 = score1.transpose(1,2).contiguous()
+		# attention
[…]

### 2018-02-07 src/classifier/local_classifier.py

@@ -1,0 +1,168 @@
+import sys
+sys.path.insert(0, '../')
+
+import torch
+from torch import nn
+from view import *
+from join_table import *
+from holder import *
+
+class LocalClassifier(torch.nn.Module):
+	def __init__(self, opt, shared):
+		super(LocalClassifier, self).__init__()
+
+		# temp stuff will be changed on the fly
+		batch_l = 1
+		sent_l1 = 2
+		sent_l2 = 3
+
+		cat_size = opt.hidden_size * 2
+		self.input_view1 = View(batch_l * sent_l1, cat_size)
+		self.input_view2 = View(batch_l * sent_l2, cat_size)
+		self.input_unview1 = View(batch_l, sent_l1, opt.hidden_size)
+		self.input_unview2 = View(batch_l, sent_l2, opt.hidden_size)
+		self.input_joiner = JoinTable(2)
+		self.phi_joiner = JoinTable(1)
+
+		# bookkeeping
+		self.shared = shared
+		self.dropout = opt.dropout
+		self.hidden_size = opt.hidden_size
+
+		self.g = nn.Sequential(
+			nn.Dropout(opt.dropout),
+			nn.Linear(cat_size, opt.hidden_size),
+			nn.ReLU(),
+			nn.Dropout(opt.dropout),
+			nn.Linear(opt.hidden_size, opt.hidden_size),
+			nn.ReLU())
+		self.h = nn.Sequential(
+			nn.Dropout(opt.dropout),
+			nn.Linear(cat_size, opt.hidden_size),
+			nn.ReLU(),
+			nn.Dropout(opt.dropout),
+			nn.Linear(opt.hidden_size, opt.hidden_size),
+			nn.ReLU(),
+			nn.Linear(opt.hidden_size, opt.num_labels),
+			nn.LogSoftmax(1))
+
+	def init_weight_from(self, c):
+		for i in [1,4]:
+			self.g[i].weight.data.copy_(c.g[i].weight.data)
+			if self.g[i].bias is not None and c.g[i].bias is not None:
+				self.g[i].bias.data.copy_(c.g[i].bias.data)
+
+		for i in [1,4,6]:
+			self.h[i].weight.data.copy_(c.h[i].weight.data)
+			if self.h[i].bias is not None and c.h[i].bias is not None:
+				self.h[i].bias.data.copy_(c.h[i].bias.data)
+
+
+	def forward(self, sent1, sent2, att1, att2):
+		self.update_context()
+
[…]

### 2018-02-07 src/eval.py

@@ -1,0 +1,134 @@
+import sys
+sys.path.insert(0, '../')
+from pipeline import *
+import argparse
+import h5py
+import os
+import random
+import time
+import numpy as np
+import torch
+from torch.autograd import Variable
+from torch import nn
+from torch import cuda
+from holder import *
+from optimizer import *
+from embeddings import *
+from data import *
+from util import *
+
+parser = argparse.ArgumentParser(description=__doc__, formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+
+parser.add_argument('--data', help="Path to evaluation data hdf5 file.", default="data/entail-val.hdf5")
+parser.add_argument('--res', help="Path to resource files, separated by comma.", default="")
+parser.add_argument('--load_file', help="Path from where model to be loaded.", default="model")
+
+## pipeline specs
+parser.add_argument('--encoder', help="The type of encoder", default="proj")
+parser.add_argument('--attention', help="The type of attention", default="local")
+parser.add_argument('--classifier', help="The type of classifier", default="local")
+parser.add_argument('--hidden_size', help="The hidden size of the pipeline", type=int, default=200)
+parser.add_argument('--word_vec_size', help="The input word embedding dim", type=int, default=300)
+parser.add_argument('--dropout', help="The dropout probability", type=float, default=0.2)
+parser.add_argument('--num_att_labels', help='The number of attention labels', type=int, default=1)
+parser.add_argument('--num_labels', help="The number of prediction labels", type=int, default=3)
+parser.add_argument('--constr', help="The list of constraints to use in hard attention", default='')
+#parser.add_argument('--percent', help="The percent of training data to use", type=float, default=1.0)
+parser.add_argument('--word_vecs', help="The path to word embeddings", default = "")
+parser.add_argument('--fix_word_vecs', help="Whether to make word embeddings NOT learnable", type=int, default=1)
+parser.add_argument('--seed', help="The random seed", type=int, default=3435)
+parser.add_argument('--gpuid', help="The GPU index, if -1 then use CPU", type=int, default=-1)
+
[…]

### 2018-02-07 src/exampleVis.py

@@ -1,0 +1,31 @@
+from visPackage import *
+from modelInterface import *
+from sentenceGenerator import *
+
+model = modelInterface(wordDict="../data/snli_1.0.word.dict", wordVec="../data/glove.hdf5", model="local_200_parikh")
+
+################ test model interface #################
+# model.evaluateTestData("../data/snli_1.0/src-test.txt", "../data/snli_1.0/targ-test.txt", "../data/snli_1.0/label-test.txt")
+# model.predict([exampleData[0]["src"], exampleData[0]["targ"]])
+# model.attention()
+# exit()
+#######################################################
+
+gen = sentenceGenerator()
+###### test sentence perturbation interface ###########
+# ps = gen.perturbSentence("A woman eat an apple.")
+# print ps
+# exit()
+#######################################################
+visComponentList = ["prediction", "sentence", "attention", "evaluation"]
+
+modelVis = textEntailVisModule(visComponentList)
+modelVis.setPredictionHook(model.predict)
+modelVis.setAttentionHook(model.attention)
+modelVis.setSentencePerturbationHook(gen.perturbSentence)
+modelVis.setSentenceParserHook(getDependencyTree)
+# modelVis.predictionChangeHook()
+
+#open browser for visualization
+# modelVis.show()
+modelVis.startServer()

### 2018-02-07 src/pipeline.py

@@ -1,0 +1,175 @@
+import sys
+sys.path.insert(0, './encoder')
+sys.path.insert(0, './attention')
+sys.path.insert(0, './classifier')
+
+import torch
+from torch import nn
+from torch import cuda
+from view import *
+from join_table import *
+from holder import *
+from proj_encoder import *
+from local_attention import *
+from local_classifier import *
+from torch.autograd import Variable
+import numpy as np
+from optimizer import *
+import time
+
+class Pipeline(torch.nn.Module):
+	def __init__(self, opt, shared):
+		super(Pipeline, self).__init__()
+
+		self.shared = shared
+		self.opt = opt
+
+		if opt.encoder == 'proj':
+			self.encoder = ProjEncoder(opt, shared)
+		else:
+			raise Exception('unrecognized enocder: {0}'.format(opt.encoder))
+
+		if opt.attention == 'local':
+			self.attention = LocalAttention(opt, shared)
+		else:
+			raise Exception('unrecognized attention: {0}'.format(opt.attention))
+
+		if opt.classifier == 'local':
+			self.classifier = LocalClassifier(opt, shared)
+		else:
+			raise Exception('unrecognized classifier: {0}'.format(opt.classifier))
+
+	def init_weight(self):
+		if self.opt.param_init_type == 'xavier_uniform':
+			for n, p in self.named_parameters():
+				if 'weight' in n:
+					nn.init.xavier_uniform(p)
+				elif 'bias' in n:
+					nn.init.constant(p, 0)
+		elif self.opt.param_init_type == 'uniform':
+			for n, p in self.named_parameters():
+				if 'weight' in n:
+					p.data.copy_(torch.randn(p.data.shape)).mul_(self.opt.param_init)
+				elif 'bias' in n:
+					p.data.copy_(torch.randn(p.data.shape)).mul_(self.opt.param_init)
+
+	# init weight form a pretrained model
+	#	will recursively pass down network subgraphs accordingly
+	def init_weight_from(self, m):
+		self.encoder.init_weight_from(m.encoder)
+		self.attention.init_weight_from(m.attention)
+		self.classifier.init_weight_from(m.classifier)
+		
+
+	def forward(self, sent1, sent2):
+		shared = self.shared
[…]

### 2018-02-07 src/sentenceGenerator.py

@@ -1,0 +1,91 @@
+import nltk
+from nltk.corpus import wordnet as wn
+from nltk.stem import WordNetLemmatizer
+from pattern.en import pluralize, singularize
+import copy
+
+class sentenceGenerator:
+    def __init__(self, train_dict='../data/snli_1.0.word.dict'):
+        self.train_tokens = {}
+        with open(train_dict, 'r+') as f:
+            lines = f.readlines()
+            for l in lines:
+                toks = l.split(" ")
+                self.train_tokens[toks[0]] = 1
+        # print self.train_tokens
+
+    #perturb nouns and verb in the sentence
+    def perturbSentence(self, inputSentence):
+        train_tokens = self.train_tokens
+        lemma_map = {}
+        pos_tags = nltk.pos_tag(nltk.word_tokenize(inputSentence))
+        nouns = [i if i[1].startswith("NN") else None for i in pos_tags]
+        ## a list of pairs (lemma, POS)
+        noun_lemma = []
+        for n in nouns:
+            if n is not None:
+                word = n[0]
+                pos = n[1]
+                ## nltk's lemmatizer failed to make plural into singular
+                ##     so make it manually
+                if pos == 'NNS':
+                    noun_lemma.append((singularize(word), pos))
+                else:
+                    noun_lemma.append((word, pos))
+            else:
+                noun_lemma.append(None)
+
+        for l in noun_lemma:
+            if l is not None:
+                lemma = l[0]
+                synsets = wn.synsets(lemma)
+                if len(synsets) != 0:
+                    lemma_map[lemma] = []
+
+                for s in synsets:
+                    ## add synonyms
+                    ## only add synonyms that has a single token (i.e.     exclude '_')
+                    lemma_map[lemma].extend([ln.lower() for ln in s.lemma_names() if '_' not in ln])
+
+                    ## add antonyms
+                    for syn_lemma in s.lemmas():
+                        if syn_lemma.antonyms():
+                            lemma_map[lemma].extend([ln.name().lower() for ln in syn_lemma.antonyms()])
+
+                    ## filter out words not in train dict
+                    lemma_map[lemma] = [l for l in lemma_map[lemma] if l in train_tokens.keys()]
+
+                    ## make synonyms unique
+                    lemma_map[lemma] = list(set(lemma_map[lemma]))
+                    ## remove the lemma itself
+                    lemma_map[lemma] = [l for l in lemma_map[lemma] if l != lemma]
[…]

### 2018-02-07 src/sentence_perturbation.py

@@ -1,0 +1,136 @@
+import nltk
+from nltk.corpus import wordnet as wn
+from nltk.stem import WordNetLemmatizer
+from pattern.en import pluralize, singularize
+import copy
+
+lemmatizer = WordNetLemmatizer()
+
+def perturb_noun_in_sentence(s, train_tokens):
+	lemma_map = {}
+	pos_tags = nltk.pos_tag(nltk.word_tokenize(s))
+	nouns = [i if i[1].startswith("NN") else None for i in pos_tags]
+	## a list of pairs (lemma, POS)
+	noun_lemma = []
+	for n in nouns:
+		if n is not None:
+			word = n[0]
+			pos = n[1]
+			## nltk's lemmatizer failed to make plural into singular
+			## 	so make it manually
+			if pos == 'NNS':
+				noun_lemma.append((singularize(word), pos))
+			else:
+				noun_lemma.append((word, pos))
+		else:
+			noun_lemma.append(None)
+
+	for l in noun_lemma:
+		if l is not None:
+			lemma = l[0]
+			synsets = wn.synsets(lemma)
+			if len(synsets) != 0:
+				lemma_map[lemma] = []
+
+			for s in synsets:
+				## add synonyms
+				## only add synonyms that has a single token (i.e. 	exclude '_')
+				lemma_map[lemma].extend([ln.lower() for ln in s.lemma_names() if '_' not in ln])
+
+				## add antonyms
+				for syn_lemma in s.lemmas():
+					if syn_lemma.antonyms():
+						lemma_map[lemma].extend([ln.name().lower() for ln in syn_lemma.antonyms()])
+
+				## filter out words not in train dict
+				lemma_map[lemma] = [l for l in lemma_map[lemma] if l in train_tokens]
+
+				## make synonyms unique
+				lemma_map[lemma] = list(set(lemma_map[lemma]))
+				## remove the lemma itself
+				lemma_map[lemma] = [l for l in lemma_map[lemma] if l != lemma]
+
+
+	orig_list = [i[0] for i in pos_tags]
+	result_list = []
+	for i, l in enumerate(noun_lemma):
+		if l is not None:
+			lemma = l[0]
+			pos = l[1]
+			if lemma in lemma_map:
+				synonyms = lemma_map[lemma]
+				for s in synonyms:
+					target = s
+					## dealing with plural and sigular
+					##	sometimes wordnet gives plural synonym when input is singular, or vice versa
[…]

### 2018-02-07 src/temp/server_backup.py

@@ -1,0 +1,65 @@
+from flask import Flask ,render_template,request,json,jsonify
+import numpy as np
+import h5py
+
+
+app = Flask(__name__)
+######################################################################
+@app.route('/')
+def index():
+    return render_template('attentionVis.html')
+
+@app.route('/_getSentences', methods=['GET', 'POST'])
+def getSentences():
+    source = '../../data/snli_1.0/src-dev.txt'
+    target = '../../data/snli_1.0/targ-dev.txt'
+    
+    #source sentence
+    s_sens = []
+    with open(source) as f:
+        lines = f.readlines()
+    for line in lines:
+        s_sens.append(line.strip())
+    
+    #target sentence
+    t_sens = []
+    with open(target) as f:
+        lines = f.readlines()
+    for line in lines:
+        t_sens.append(line.strip())
+    
+    return json.dumps({'source':s_sens, 'target':t_sens})
+    
+@app.route('/_getData', methods=['GET', 'POST'])
+def getData():
+    
+    rjson = request.get_json()
+    sen1 = rjson['sen1']
+    sen2 = rjson['sen2']
+    index = str(rjson['index'])
+
+    #get prediction label 
+    label = '../../data/snli_1.0/label-dev.txt'
+    with open(label) as f:
+        labels = f.readlines()
+
+    #get attention matrix
+    file = h5py.File('../val_att.hdf5', 'r')    
+    matrix = []
+    for item in file[index]:
+        matrix.extend(item.tolist())
+
+    #get sentence parse tree
+    src_sen_tree = json.load(open('../../data/snli_1.0/src-dev.json'))
+    targ_sen_tree = json.load(open('../../data/snli_1.0/targ-dev.json'))
+
+    result = {'sen1':sen1.strip().split(' ')}
+    result['sen1_tree'] = targ_sen_tree[index] 
+    result['sen2'] = sen2.strip().split(' ') 
+    result['sen2_tree'] = src_sen_tree[index]
+    result['matrix'] = matrix
+    result['label'] = labels[int(index)]
+    return json.dumps(result)
+
+if __name__ == '__main__':
+    app.run(debug=True)

### 2018-02-07 src/temp/static/attention.js

@@ -1,0 +1,1113 @@
+let attention_src_filter_node = [];
+let attention_targ_filter_node = [];
+let aggregation_src = {};
+let aggregation_targ = {};
+
+let attention_para = null;
+
+let filter_index_h = new Set();
+let filter_index_v = new Set();
+
+
+
+let rectw = 50;
+let recth = 30;
+let canvas = d3.select('#canvas').append('svg').attr('width', 3000).attr('height', 3000);
+let div = d3.select("body").append("div").attr("class", "tooltip").style("opacity", 0);
+
+
+bindingEvent();
+load_sentences(INIT);
+/*
+fetch all possible sentence in the server side.
+**/
+function INIT(para){
+	let s_sens = para.source,
+	t_sens = para.target;
+	
+	//source option
+	let source_string_buffer = '';
+	s_sens.forEach(d=>{
+		source_string_buffer += '<option>'+d+'</option>';
+	});
+	$('#source_sentences').html(source_string_buffer);
+	
+	//target option
+	let target_string_buffer = '';
+	t_sens.forEach(d=>{
+		target_string_buffer += '<option>'+d+'</option>';
+	});
+	$('#target_sentences').html(target_string_buffer);
+	
+	load_data({'index':0, 'source':s_sens[0], 'target':t_sens[0]}, resetData);
+}
+
+function draw_attention_matrix(x, y, matrix, row, col){
+	let width = col * rectw,
+	height = row * recth,
+	colorscale = d3.interpolateRdBu;
+	
+	//maxtrix render
+	canvas.append('g').selectAll('.attentionMatrixRect')
+	.data(matrix)
+	.enter()
+	.append('rect')
+	.attr('x', (d, i)=>{
+		return x + i % col * rectw;
+	})
+	.attr('y', (d, i)=>{
+		return y + Math.floor(i / col) * recth;
+	})
+	.attr('width', rectw)
+	.attr('height', recth)
+	.style('stroke', 'black')
+	.style('stroke-width', '1px')
+	.style('fill', d=>{return colorscale(1 - d)});
+	
+	//color scale map
+	linearGradient = canvas.append('defs').append('linearGradient')
+	.attr('id', 'attention_heatmap_gradient')
+	.attr('x1', '0%')
+	.attr('y1', '0%')
+	.attr('x2', '0%')
+	.attr('y2', '100%');
+	
+	//color gradient break point
+	for(let i = 0; i <= 10; i++){
+		linearGradient.append('stop')
[…]

### 2018-02-07 src/temp/tool.py

@@ -1,0 +1,23 @@
+from nltk.parse.stanford import StanfordDependencyParser
+
+def getDependencyTree(sentence):
+    path_to_jar = '/Users/lizhimin/Desktop/NLPModelExplorer/data/snli_1.0/stanford-corenlp-3.8.0.jar'
+    path_to_models_jar = '/Users/lizhimin/Desktop/NLPModelExplorer/data/snli_1.0/stanford-corenlp-3.8.0-models.jar'
+    dependency_parser = StanfordDependencyParser(path_to_jar=path_to_jar, path_to_models_jar=path_to_models_jar)
+    
+    g = dependency_parser.raw_parse(sentence).next()
+    
+    
+    dep_json = []
+    
+    for _, node in sorted(g.nodes.items()):
+        if node['word'] is not None:
+            for key in node['deps']:
+                if len(node['deps'][key]) == 0:
+                    continue
+                else:
+                    for v in node['deps'][key]:
+                        dep_json.append([node['address'], key, v])
+           
+    return dep_json      
+    #return list(g.triples())

### 2018-02-07 src/train.py

@@ -1,0 +1,218 @@
+import sys
+sys.path.insert(0, '../')
+from pipeline import *
+import argparse
+import h5py
+import os
+import random
+import time
+import numpy as np
+import torch
+from torch.autograd import Variable
+from torch import nn
+from torch import cuda
+from holder import *
+from optimizer import *
+from embeddings import *
+from data import *
+
+parser = argparse.ArgumentParser(description=__doc__, formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+
+parser.add_argument('--train_data', help="Path to training data hdf5 file.", default="data/entail-train.hdf5")
+parser.add_argument('--val_data', help="Path to validation data hdf5 file.", default="data/entail-val.hdf5")
+parser.add_argument('--test_data', help="Path to test data hdf5 file.", default="data/entail-test.hdf5")
+
+parser.add_argument('--save_file', help="Path to where model to be saved.", default="model")
+
+## pipeline specs
+parser.add_argument('--encoder', help="The type of encoder", default="proj")
+parser.add_argument('--attention', help="The type of attention", default="local")
+parser.add_argument('--classifier', help="The type of classifier", default="local")
+parser.add_argument('--hidden_size', help="The hidden size of the pipeline", type=int, default=200)
+parser.add_argument('--word_vec_size', help="The input word embedding dim", type=int, default=300)
+parser.add_argument('--dropout', help="The dropout probability", type=float, default=0.2)
+parser.add_argument('--num_att_labels', help='The number of attention labels', type=int, default=1)
+parser.add_argument('--num_labels', help="The number of prediction labels", type=int, default=3)
+parser.add_argument('--constr', help="The list of constraints to use in hard attention", default='')
+#parser.add_argument('--percent', help="The percent of training data to use", type=float, default=1.0)
+parser.add_argument('--epochs', help="The number of epoches for training", type=int, default=100)
+# TODO, param_init of uniform dist or normal dist???
[…]

### 2018-02-07 src/visPackage/socketioManager.py

@@ -1,0 +1,130 @@
+'''
+Send and receive data between server and client using SocketIO
+'''
+from sets import Set
+import socketio
+import json
+import numpy as np
+
+class socketioManager:
+    def __init__(self, sio):
+        self.data2ID = dict()
+        self.data = dict()
+        self.namespace = "/app"
+        self.sio = sio
+
+    def clear(self):
+        self.data2ID = dict()
+        self.data = dict()
+
+    def setObject(self, bindedObject):
+        self.object = bindedObject
+
+    def callFunc(self, funcName, params):
+        func = getattr(self.object,funcName)
+        #params is a dict for storing function parameters
+        return func(**params)
+
+    #receive from client
+    def receiveFromClient(self, msg):
+        # print msg
+        uid = msg["uid"]
+        #parse
+        messageType = msg['type']
+        if messageType == 'setData':
+            self.setData(msg["name"], msg["data"], uid)
+        elif messageType == 'subscribeData':
+            self.subscribeData(msg["name"], uid)
+        elif messageType == "call":
+            returnVal = self.callFunc(msg["func"], msg["params"])
+            self.sendFuncReturn(msg["func"], returnVal, uid)
+
+    def sendToClient(self, uID, json):
+        # print "send to client:", uID, json
+        self.sio.emit(uID, json, namespace = self.namespace, broadcast=True)
+        # emit(uID, json, namespace = self.namespace)
+
+    def sendFuncReturn(self, func, data, uID):
+        mappedData = dataMapper.Py2Js(data)
+        # print "send to client:", data, " => ", mappedData
+        if mappedData:
+            msg = dict()
+            msg['type'] = "funcReturn"
+            msg['func'] = func
+            msg['data'] = mappedData
+            self.sendToClient(uID, msg)
+
+    def sendDataToClient(self, name, data, uID):
+        mappedData = dataMapper.Py2Js(data)
+        # print "send to client:", data, " => ", mappedData
+        if mappedData:
+            msg = dict()
+            msg['type'] = "data"
+            msg['name'] = name
+            msg['data'] = mappedData
+            self.sendToClient(uID, msg)
+
+    def setData(self, name, data, uID = None):
+        self.data[name] = data
+        #propagate data update
+        if name in self.data2ID.keys():
+            for id in self.data2ID[name]:
+                # print "setData:", id
+                if id == uID:
+                    continue
+                mappedData = dataMapper.Py2Js(data)
+                if mappedData:
+                    msg = dict()
[…]

### 2018-02-07 src/visPackage/static/components/attentionComponent.js

@@ -1,0 +1,218 @@
+/*
+
+Matrix representation of attention
+
+
+*/
+
+//beside margin matrix will take 2/3 width and 2/3 height space
+class attentionComponent extends baseComponent {
+    constructor(uuid) {
+        super(uuid);
+        this.subscribeDatabyNames(["attention", "currentPair"]);
+
+        this.margin = {
+            top: 25,
+            right: 25,
+            bottom: 25,
+            left: 25
+        };
+
+    }
+
+    draw() {
+        this._updateWidthHeight();
+
+        if (this.data["attention"] !== undefined && this.data["currentPair"] !==
+            undefined && this.data['targ_depTree'] !== undefined && this.data[
+                'src_depTree'] !== undefined) {
+
+            //clear all
+            if (this.svg)
+                d3.select(this.div).html('');
+
+            //attention matrix
+            let attMatrix = this.data['attention'];
+
+            //init svg
+            this.svg = d3.select(this.div).append("svg")
+                .attr("width", this.pwidth)
+                .attr("height", this.pheight)
+                .append("g")
+                .attr("transform", "translate(" + this.margin.left + "," +
+                    this.margin.top + ")");
+
+            ////////////////////add colormap //////////////////////
+            this.colorbar =
+                new d3UIcolorMap(this.svg, this.uuid, [0, 1], [0, 0], [this
+                    .width * 0.22, 24
+                ], 2);
+            this.colorbar.draw();
+            this.colorbar.callback(this.updateMatrixColormap.bind(this));
+
+            //data
+            this.attList = [];
+            for (let i = 0; i < attMatrix.length; i++)
+                for (let j = 0; j < attMatrix[i].length; j++) {
+                    this.attList.push(attMatrix[i][j])
+                }
+
+            //location of words
+            this.computeWordPosition(this.srcWords, this.targWords);
+
+            //matrix
+            let rectw = (this.width * 3 / 4) / this.targWords.length,
+                recth = (this.height * 3 / 4) / this.srcWords.length;
+
+            this.rectw = rectw;
+            this.recth = recth;
+
+            this.svg.selectAll('.attentionComponent_matrix_rect')
+                .data(this.attList)
+                .enter()
+                .append('rect')
+                .attr('class', 'attentionComponent_matrix_rect')
+                .attr('x', (d, i) => {
+                    return this.width * 1 / 4 + (i % this.targWords.length) *
+                        rectw;
+                })
+                .attr('y', (d, i) => {
[…]

### 2018-02-07 src/visPackage/static/components/baseComponent.js

@@ -1,0 +1,125 @@
+/*
+ - standardize query interface
+ - handle component wise communication
+*/
+
+var namespace = '/app'; //global namespace
+//create a web socket connect to the server domain.
+var socket = io.connect('http://' + document.domain + ':' + location.port +
+    namespace);
+
+// console.log(document.domain, location.port);
+
+class baseComponent {
+    constructor(uuid) {
+        this.uuid = uuid;
+        // console.log(this.uuid);
+        this.div = "#" + this.uuid;
+        this.data = {};
+
+        socket.on(this.uuid, this.parseMessage.bind(this));
+
+        //default margin
+        this.margin = {
+            top: 5,
+            right: 5,
+            bottom: 5,
+            left: 5
+        };
+    }
+
+    subscribeDatabyNames(names) {
+        if (!Array.isArray(names)) {
+            console.log("Error: input need to be a list of names\n");
+            return;
+        }
+
+        for (var i = 0; i < names.length; i++) {
+
+            var msg = {
+                "type": "subscribeData",
+                "name": names[i],
+                "uid": this.uuid
+            };
+            // console.log(msg);
+            socket.emit('message', msg);
+        }
+    }
+
+    callFunc(funcName, params = {}) {
+        var msg = {
+            "type": "call",
+            "func": funcName,
+            "params": params,
+            "uid": this.uuid
+        };
+        socket.emit('message', msg);
+    }
+
+    setData(name, data) {
+        this.data[name] = data;
+        var msg = {
+            "type": "setData",
+            "name": name,
+            "data": data,
+            "uid": this.uuid
+        };
+        // console.log(msg);
+        socket.emit('message', msg);
+    }
+
+    parseMessage(msg) {
+        // console.log("\nparse message in base class\n", msg);
+        switch (msg['type']) {
+            case 'data':
+                this.parseDataUpdate(msg);
+                break;
+                // case 'functionReturn':
+                //     this.parseFunctionReturn(msg);
+                //     return;
+            case 'funcReturn':
+                this.parseFunctionReturn(msg);
+                break;
+        }
+    }
+
+    parseFunctionReturn(msg) {
+
+    }
+
+    parseDataUpdate(msg) {
+        this.updateData(msg);
+    }
+
+    updateData(msg) {
+        var name = msg["name"];
+        var data = msg["data"]["data"];
+        this.data[name] = data;
+
+    }
+
+    ////////// implemented by individual component ////////
+
+    draw() {
+
[…]

### 2018-02-07 src/visPackage/static/components/evaluationComponent.js

@@ -1,0 +1,16 @@
+/*
+Using treemap to visualize the error sentence pairs
+*/
+
+class evaluationComponent extends baseComponent {
+    constructor(uuid) {
+        super(uuid);
+    }
+
+
+    draw() {
+
+    }
+
+
+}

### 2018-02-07 src/visPackage/static/components/predictionComponent.js

@@ -1,0 +1,160 @@
+/*
+
+the triangle vis of the prediction result
+
+*/
+
+class predictionComponent extends baseComponent {
+    constructor(uuid) {
+        super(uuid);
+
+        //subscribe to data
+        this.subscribeDatabyNames(["allSourcePairs", "allTargetPairs",
+            "prediction", "allPairsPrediction"
+        ]);
+
+        this.margin = {
+            top: 25,
+            right: 25,
+            bottom: 25,
+            left: 25
+        };
+
+        this.draw();
+    }
+
+    draw() {
+        // console.log(this.data);
+        this._updateWidthHeight();
+        this.svg = d3.select(this.div + "triangle");
+
+        //entailment
+        //neutral, Contradiction, Entailment
+        //112,0 0,194 224,194
+
+        this.svg.select(this.div + "label").remove();
+        var label = this.svg.append("g").attr("id", this.uuid + "label");
+        label.append('text')
+            // .attr("class", "trilabel")
+            .attr("x", 112 - 20)
+            .attr("y", -2)
+            .text("Neutral")
+            .style("font-size", "14px")
+            .style("fill", "grey");
+
+        //neutral
+        label.append('text')
+            // .attr("class", "trilabel")
+            .attr("x", 0 - 10)
+            .attr("y", 194 + 12)
+            .text("Contradiction")
+            .style("font-size", "14px")
+            .style("fill", "grey");
+
+        //contradiction
+        label.append('text')
+            // .attr("class", "trilabel")
+            .attr("x", 224 - 55)
+            .attr("y", 194 + 12)
+            .text("Entailment")
+            .style("font-size", "14px")
+            .style("fill", "grey");
+        // updateData(sdata, 0);
+
+        this.svg.attr("width", this.pwidth)
+            .attr("height", this.pheight)
+            .attr("x", 0)
+            .attr("y", 0);
+
+        // this.updateSelection();
+    }
+
+    parseDataUpdate(msg) {
+        super.parseDataUpdate(msg);
+        switch (msg["name"]) {
+            case "prediction":
+                this.onUpdatePrediction();
+                break;
+            case "allPairsPrediction":
+                this.onUpdateAllPairPrediction();
+                break;
+        }
+    }
+
+    resize() {
+        // console.log("prediction-resize\n");
+        this.draw();
+    }
+
+    onUpdatePrediction() {
+        var prediction = this.data['prediction'][0];
[…]

### 2018-02-07 src/visPackage/static/components/sentenceComponent.js

@@ -1,0 +1,225 @@
+/*
+Display sentences and apply perturbation to the sentences
+*/
+
+class sentenceComponent extends baseComponent {
+    constructor(uuid) {
+        super(uuid);
+        this.subscribeDatabyNames(["sentenceList", "currentPair"]);
+
+        //setup UI
+        d3.select(this.div + "perturbTarget").on("click", this.perturbTarget
+            .bind(this));
+        d3.select(this.div + "perturbSource").on("click", this.perturbSource
+            .bind(this));
+
+
+        d3.select(this.div + "Predict").on("click", d => {
+            this.callFunc("predict");
+        });
+        d3.select(this.div + "PredictAll").on("click", d => {
+            //produce all combinations
+            this.callFunc("predictAll");
+        });
+
+        //update data when currentPair changes
+        d3.select(this.div + "src").on("change", this.onUpdateCurrentPair.bind(
+            this));
+        d3.select(this.div + "targ").on("change", this.onUpdateCurrentPair.bind(
+            this));
+    }
+
+    draw() {
+        //add to sentence list
+        if (this.data["sentenceList"] !== undefined) {
+            this.onReceiveSentenceList();
+        }
+        //update currentPair display
+        if (this.data["currentPair"] !== undefined) {
+            this.onReceiveCurrentPair();
+        }
+    }
+
+    parseDataUpdate(msg) {
+        super.parseDataUpdate(msg);
+
+        switch (msg['name']) {
+            case "sentenceList":
+                this.onReceiveSentenceList();
+                break;
+            case "currentPair":
+                // console.log(msg, this.data["currentPair"]);
+                this.onReceiveCurrentPair();
+                break;
+        }
+    }
+
+    parseFunctionReturn(msg) {
+        switch (msg['func']) {
+            case 'perturbSentence':
+                this.updatePerturbedSentences(msg["data"]["data"], msg[
+                    "data"]);
+                break;
+                // case 'functionReturn':
+                //     this.parseFunctionReturn(msg);
+                //     return;
+        }
+    }
+
+
+    /////////////////// event handler /////////////////////
+    onReceiveSentenceList() {
+        // console.log("sentenceList:", this.data["sentenceList"]);
+        d3.select(this.div + "selectExample")
+            .on("change", this.onChangeOriginalPair.bind(this));
+        var options = d3.select(this.div + "selectExample")
+            .selectAll('option')
+            .data(this.data["sentenceList"]).enter()
+            .append('option')
[…]

### 2018-02-07 src/visPackage/static/main.js

@@ -1,0 +1,131 @@
+var panelMetaInfo = {
+    'Prediction': ['prediction_view', 'predictionComponent'],
+    'Attention': ['attention_view', 'attentionComponent'],
+    'Sentence': ['sentence_view', 'sentenceComponent'],
+    "AttentionSentence": ['attentionSentence_view',
+        'attentionSentenceComponent'
+    ],
+    'Evaluation': ['evaluation_view', 'evaluationComponent']
+};
+
+//for lookup component class on-the-fly
+var objectMap = {
+    predictionComponent: predictionComponent,
+    attentionComponent: attentionComponent,
+    attentionSentenceComponent: attentionSentenceComponent,
+    sentenceComponent: sentenceComponent,
+    evaluationComponent: evaluationComponent
+};
+
+var config = {
+    settings: {
+        showPopoutIcon: true,
+        // showPopoutIcon: false,
+        showCloseIcon: true
+    },
+    content: [{
+        type: 'column',
+        content: [{
+            type: 'row',
+            content: [{
+                type: 'component',
+                componentName: 'Prediction',
+                componentState: {
+                    route: 'prediction_view',
+                    name: 'predictionComponent'
+                }
+            }, {
+                type: 'component',
+                componentName: 'Attention',
+                componentState: {
+                    route: 'attention_view',
+                    name: 'attentionComponent'
+                }
+            }]
+        }, {
+            type: 'row',
+            content: [{
+                type: 'component',
+                componentName: 'Sentence',
+                componentState: {
+                    route: 'sentence_view',
+                    name: 'sentenceComponent'
+                }
+            }, {
+                type: 'component',
+                componentName: 'AttentionSentence',
+                componentState: {
+                    route: 'attentionSentence_view',
+                    name: 'attentionSentenceComponent'
+                }
+            }]
+        }]
+    }]
+
+};
+
+
+
+function registerComponent(appLayout, name) {
+    //register factory callback
+    appLayout.registerComponent(name, function(container,
+        componentState) {
+        // console.log("loading -- ", componentState);
+        //popout test
+        // console.log("container constructor:", componentState.name);
+        // container.getElement().html( '<h2>' + componentState.name + '</h2>' );
+
+        $.get(componentState.route,
+            function(template) {
+                // var uuid = guid();
+                var uuid = "div_" + uuidv1();
+                var data = {
+                    id: uuid
+                };
[…]

### 2018-02-07 src/visPackage/static/plot/dependencyTreePlot.js

@@ -1,0 +1,311 @@
+/*
+
+add dependencyTreePlot to an existing svg
+*/
+
+class dependencyTreePlot {
+
+    //pos: The index position
+    //width: The width of sentence
+    //heigth: The height of sentence
+    constructor(svg, orientation, sen, pos, dep_triples, width, height) {
+        this.svg = svg.append('g');
+        this.orientation = orientation;
+        this.pos = pos;
+        this.sen = sen;
+        this.dep_triples = dep_triples;
+        this.width = width;
+        this.height = height;
+
+        //text box width and height
+        this.text_box_width = Math.min(this.width * 0.1, 15);
+        this.text_box_height = Math.min(this.height * 0.1, 10);
+
+        this.collapseIndex = new Set();
+
+        this.filter(); //init the display index
+
+        this.draw();
+    }
+
+    setCollapseHandle(func) {
+        this.callback = func;
+    }
+
+    onHandleCollapse() {
+
+        this.sentenceMask = [];
+        for (let i = 0; i < this.sen.length; i++) {
+            if (this.display_index.includes(i)) {
+                this.sentenceMask[i] = 1;
+            } else {
+                this.sentenceMask[i] = 0;
+            }
+        }
+
+        this.callback(this.sentenceMask); //[1,0,0,1]
+        //this.callback(display_index);//the index of word will be presented
+    }
+
+    //i: index of word in sentence
+    collapse(i) {
+        if (this.collapseIndex.has(i)) {
+            this.collapseIndex.delete(i);
+        } else {
+            this.collapseIndex.add(i);
+        }
+
+        this.filter();
+        this.draw();
+
+        //callback called
+        this.onHandleCollapse();
+    }
+
+    //support function for collapse: filter
+    //this.display_index is reset, shows which words are presented
+    filter() {
+        let childs = [];
+        let display_index = [];
+
+        this.collapseIndex.forEach(d => {
+            childs = childs.concat(getChild(d, this.dep_triples))
+        });
+
+        let childs_set = new Set(childs);
+        for (let i = 0; i < this.sen.length; i++) {
+            if (!childs_set.has(i)) {
+                display_index.push(i);
+            }
+        }
+        this.display_index = display_index;
+        console.log(display_index);
+    }
+
+    //support function for collapse: get child index
+    getChild(index, deps) {
+        let childs = [];
+        let filter = new Set();
+
+        //loop throught the dependency until there is not new node
[…]

### 2018-02-07 src/visPackage/visModule.py

@@ -1,0 +1,175 @@
+
+'''
+ - the portal for sending data to the visualization
+ - act as a server for the js based visualization
+ - open web browser
+
+
+ Data Model
+ - data object is linked by object id, json format
+'''
+
+from flask import Flask
+import socketio
+import eventlet
+from socketioManager import *
+import webbrowser, threading
+import time
+
+app = Flask(__name__)
+sio = socketio.Server()
+fApp = socketio.Middleware(sio, app)
+dataManager = socketioManager(sio)
+
+exampleData = [{
+    "index":0,
+    "src": "Two women are embracing while holding to go packages .\n",
+    "targ": "The sisters are hugging goodbye while holding to go packages after just eating lunch .\n"
+},{
+    "index":1,
+    "src": "Two young children in blue jerseys , one with the number 9 and one with the number 2 are standing on wooden steps in a bathroom and washing their hands in a sink .\n",
+    "targ": "Two kids in numbered jerseys wash their hands .\n"
+}
+]
+
+#################### server control ######################
+class visModule:
+    def __init__(self):
+        dataManager.setObject(self)
+
+    @app.route('/')
+    def index():
+        dataManager.clear()
+        dataManager.setData("sentenceList", exampleData)
+        dataManager.setData("currentPair", [exampleData[0]['src'], exampleData[0]['targ']])
+        return app.send_static_file('index.html')
+
+    @app.route('/<name>')
+    def views(name):
+        return {
+            'prediction_view': app.send_static_file('viewTemplates/prediction_view.mst'),
+            'attention_view': app.send_static_file('viewTemplates/template_view.mst'),
+            'attentionSentence_view': app.send_static_file('viewTemplates/attentionSentence_view.mst'),
+            'sentence_view': app.send_static_file('viewTemplates/sentence_view.mst'),
+            'evaluation_view': app.send_static_file('viewTemplates/template_view.mst')
+        }.get(name)
+
+    # envoke callback when the server is running
+    @sio.on('message', namespace='/app')
+    def parsingMessage(sid, msg):
+        # print sid, msg
+        return dataManager.receiveFromClient(msg)
+
+    def show(self):
+        url = 'http://localhost:5050'
+        threading.Timer(1.5, lambda: webbrowser.open(url, new=0) ).start()
+        #
+        eventlet.wsgi.server(eventlet.listen(('localhost', 5050)), fApp)
+
+        # deploy as an eventlet WSGI server
+        # sio.start_background_task(self.startServer)
+
+    # @staticmethod
[…]

### 2018-02-16 paper/application.tex
update paper layout

\section{Put it All Together}
In this section, we utilizes the perturbation based analysis
to illustrate how the proposed system can be used
to diagnose the model behavior, study the model's attention mechanism.

\subsection{Where Are the Mistakes?}

\subsection{What Does Attention Do?}

\subsection{Is Attention All You Need?}

### 2018-02-16 paper/attention.tex
update paper layout

\section{Attention}

\subsection{Visualize Attention}

\subsection{Interpret Attention Via Model Perturbation}

### 2018-02-16 paper/background.tex
update paper layout

\section{Background}

\subsection{Textual Entailment Problem}

\begin{itemize}
    \item what is the textaul entailment problem
    \item the importance of textual entailment problem
    \item how easily can the visualization method extends other NLP problem
\end{itemize}

Textual entailment is one of major natural language tasks, namely translation,
summarization, question

\subsection{Interprebilty Challenges}
Making sense and explaining predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).

### 2018-02-16 paper/discussion.tex
update paper layout

\section{Discussion}

\begin{itemize}
    \item how the visualization approaches generalizes to other NLP task
    \item limitation
\end{itemize}

### 2018-02-16 paper/intro_entailVis.tex
add dependency tree to attenSen, but the parse tree compuation is duplicated
update paper layout

--- 2018-01-11 paper/paper_entailVis.tex
@@
-How to interpret classification task
-\begin{itemize}
-    \item What feature / dimension / part-of-the-input should change to
-    alter the outcome
+\firstsection{Introduction}
+\maketitle
 
-\end{itemize}
-
-Related works
-\begin{itemize}
-    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
-    Use partial dependency (varying along one feature and observer how prediction changes)
-    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)
-
-\end{itemize}
+% NLP application using attention
+% \begin{itemize}
+%     \item Neural translation
+%     \item Text summarization
+%     \item Text entailment
+%     \item Text comprehension (question answering)
+% \end{itemize
+%
+%
+% Attention type:
+% \begin{itemize}
+%     \item soft vs. hard
+%     \item local vs. global
+%     \item hierarchical
+%     \item attention over attention
+%     \item gated
+% \end{itemize}

### 2018-02-16 paper/paper_entailVis.tex
update paper layout

--- 2018-01-19 paper/paper_entailVis.tex
@@
 %% Abstract section.
+% What are we doing in this paper
 \abstract{
-In Natural Language Processs (NLP) research attention mechanism has gained a
-strong following,
-
+With the advances of deep learning, neural network based models have reset
+the state-of-the-art for nearly all linguistic tasks in natural language
+processing. The disruptive advance also brings enormous challenges.
+The opaque nature of neural network model leads to hard to debug system and
+difficult to interpret mechanism~cite{}. In this work, we use textual
+entailment task as an example to illustrate how a flexible visualization
+system can help NLP researchers quickly identify the potential limitation of
+a models and probe the model inner states for interpreting key mechanism
+such as attention.
 } % end of abstract
@@
 \input{relatedWorks_entailVis.tex}
+\input{background.tex}
+% \input{tasks.tex}
+\input{perturbation.tex} % how to do the perturbation
+\input{attention.tex} % how to encode the information
+\input{application.tex}
+%%%%%%%%%%%%% identify errors %%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%% interpret attention %%%%%%%%%%%%%%%%%%%
+
+\input{discussion.tex} % how to encode the information
 

### 2018-02-16 paper/perturbation.tex
update paper layout

\section{Analysis of the Model Via Perturbation}

%%%%%%%% Overview figure for the pipeline %%%%%%%%%%
% \begin{figure}
%     \includegraphics{/path/to/figure}
%     \caption{}
%     \label{}
% \end{figure}

\subsection{Input Perturbation}
Iterate the model design and debug the system hinged on the ability to quickly and identify the errors made by a model.

Perturbation the input is what NLP researchers have subconsciously been doing to study and test a model.

Interpret/probe the relationship between attention and the prediction result

\subsection{Attention Perturbation}

\subsection{Prediction Perturbation}

### 2018-02-19 paper/intro_entailVis.tex
update paper title

@@
 \maketitle
+
+With the advances of deep learning, neural network based models have reset the state-of-the-art for nearly all linguistic tasks in natural language processing.
+The disruptive advance also brings enormous challenges.
+The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanism~cite{}.
+In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a neural models and also probe the inner states of model for interpreting key mechanism such as attention.
+
+(What is the high level motivation)
+
+The importance of attention visualization.
+For natural language processing application, the discrete nature of words and sentences presents additional challenge in interpreting the model.
+Recently, the advances in attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences.
+The new challenges
+
+% ####### Model Interpretability Section ##########
+Making sense and explaining predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
+
+However, investigating the inner mechanism of the model and explaining the model prediction is still an extremely challenging task.
+
+% ######## Why use perturbation ###########
+Iterate the model design and debug the system hinged on the ability to quickly and identify the errors made by a model.
+
+Perturbe the input is what NLP researchers have subconsciously been doing to study and test a model.
+
+Interpret/probe the relationship between attention and the prediction result
 

### 2018-02-19 paper/paper_entailVis.tex
update paper title

@@
 %% Paper title.
-\title{How Alignment Impact Language Learning Tasks? \\ A Visual Analytics Tool
-for Interpreting, Debugging, \\ and Tunning Text Entailment Model}
+\title{Where and Why Does the Model Failed? A Visual Analytics Tool for Debugging, Tunning, and Interpreting Text Entailment Model}
 
@@
 \abstract{
-With the advances of deep learning, neural network based models have reset
+With the recent advances of deep learning, neural network based models have reset
 the state-of-the-art for nearly all linguistic tasks in natural language

### 2018-02-19 paper/relatedWorks_entailVis.tex
add dependency tree to attenSen, but the parse tree compuation is duplicated
update paper title

@@
 
-Related works
+How to interpret classification task
+\begin{itemize}
+    \item What feature / dimension / part-of-the-input should change to
+    alter the outcome
+    \item What Examples can you provide that is similar to the current
+    instance
+
+\end{itemize}
+
+(Limitation of the state-of-the arts)
+Model independent explanations is useful to gain intuition, but they lack the ability to link the external observation with inner states/mechanism of the model.
+
+Papers:
 \begin{itemize}

### 2018-02-22 paper/background.tex
add short intro

@@
 \section{Background}
+
+Recently, with the wide adoption of long-short term memory
+(LSTM) network and the introduction of attention mechanism,
+neural network based model have
+dominated nearly all linguistic tasks and thoroughtly refreshed the
+baseline performances.
+%
+However, the disruptive advance also brings enormous challenges.
+Due to the opaque nature of the neural network model, interpret and making sense
+of many internal model mechanisms can be extremely challenging.
+%
+Many methods has been proprosed
+
+The discrete nature of words and
+sentences presents additional challenge for make sense of the model.
+%
 
@@
 \subsection{Interprebilty Challenges}
+
+The introduction of attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences.
+The new challenges
+
 Making sense and explaining predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).

### 2018-02-22 paper/intro.tex
add short intro

\firstsection{Introduction}
\maketitle

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many obstacles during the training, debugging, tuning process in order to unleash the full potential of these powerful models.
%
Identify where and how does the error occur and understand why does the model fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an important first step in diagnosing procedure.
%the potential limitation of the test dataset
On one hand, the standard evaluation approach provide limited information. Often only performance number is used (i.e., prediction accuracy on the test set) without answering many important questions for the diagnostic process. It would be extremely useful to understand what are the often made mistakes, and how sensitive are the model with respect to perturbation in the input, etc. On the other hand, the understanding why the model fail is even more challenging, which likely require the ability to peak into the model and make sense of the key mechanisms.

Making sense and explaining predictions made by neural networks is also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
%
Due to these demands, many works has been dedicated to providing an more intuitive explanation for a given prediction. Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e. by fitting a similar linear model near the sample of interests).
%
However, these methods despite being invaluable for the prediction interpablity task, do not adequently address the challenge in the model diagnostic process. More importantly, due to the model agnotic nature, they often the lack of the ability to access and explore the inner states of the model, which is vitally important to make sense of why a model fail.

In this work, we introduce a visualization system that through a tight yet flexible integration between visualization and the underlying model, allow user to interrogate the model by perturbing the input, the internal state, as well as prediction output, while observing chances in other part of the pipeline.
We use textual entailment task~\cite{} as an example to illustrate how this system can help natural language processing (NLP) researchers quickly identify the potential limitation of a NLP models and also probe the inner states of model for interpreting key mechanism such as attention.

% ######## Why use perturbation ###########
% Iterate the model design and debug the system hinged on the ability to quickly
% identify the errors made by a model.
%
% Perturbe the input is what NLP researchers have subconsciously been doing to study and test a model.
%
% Interpret/probe the relationship between attention and the prediction result

The key contributions of the proposed works is summarized as the following:
\begin{itemize}
    \item Allow user to quickly identify the mistakes made by the model through input perturbation and visual summerization;

    \item Introduce visual encoding for interpreting the attention that incorporate sentence linguistic structure;

    \item Interactively explore the relationship between attention and prediction via constrained optimization
\end{itemize}

% NLP application using attention
% \begin{itemize}
%     \item Neural translation
%     \item Text summarization
%     \item Text entailment
%     \item Text comprehension (question answering)
% \end{itemize
%
%
% Attention type:
% \begin{itemize}
%     \item soft vs. hard
%     \item local vs. global
%     \item hierarchical
%     \item attention over attention
%     \item gated
% \end{itemize}

### 2018-02-22 paper/paper_entailVis.tex
add short intro

@@
 %% Paper title.
-\title{Where and Why Does the Model Failed? A Visual Analytics Tool for Debugging, Tunning, and Interpreting Text Entailment Model}
+\title{Where and Why Does the Model Failed?  A Visual Analytics Tool for Debugging and Interpreting Text Entailment Model}
 
@@
 system can help NLP researchers quickly identify the potential limitation of
-a models and probe the model inner states for interpreting key mechanism
-such as attention.
+a models and interpret the model inner states for make sense of the attention mechanism.
 } % end of abstract
@@
 %% the only exception to this rule is the \firstsection command
-\input{intro_entailVis.tex}
-\input{relatedWorks_entailVis.tex}
+\input{intro.tex}
+\input{relatedWorks.tex}
 \input{background.tex}

### 2018-02-22 paper/intro.tex
update intro

@@
 With the recent advances in neural network based model, machine learning has
-gained unprecedented popularity and its adaption permeated many fields of studies.
+gained unprecedented popularity, and its adaption permeated many fields of studies.
 %
-However, from researchers to practitioners, one often need to overcome many obstacles during the training, debugging, tuning process in order to unleash the full potential of these powerful models.
+However, from researchers to practitioners, one often need to overcome many
+obstacles during the training, debugging, and tuning processes to unleash
+the full potential of these models.
 %
-Identify where and how does the error occur and understand why does the model fail is critical to the design and application of various models.
+Identify where and how does the error occur and understand why does the model
+fail is critical to the design and application of various models.
 %quickly identify where the errors are
 However, providing meaningful answers to these questions is an extremely challenging task.
-% Naturally the identification of failure scenarios is an important first step in diagnosing procedure.
+% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
 %the potential limitation of the test dataset
-On one hand, the standard evaluation approach provide limited information.
+On the one hand, the standard evaluation approach provides limited information.
 Often only performance number is used (i.e., prediction accuracy on the test set) without answering many important questions for the diagnostic process.
-It would be extremely useful to understand what are the often made mistakes, and how sensitive are the model with respect to perturbation in the input, etc.
-On the other hand, the understanding why the model fail is even more challenging, which likely require the ability to peak into the model and make sense of the key mechanisms.
+It would be instrumental to understand what are the often made mistakes, and how sensitive are the model concerning perturbation in the input, etc.
+On the other hand, the understanding why the model fails is even more challenging, which likely require the ability to peak into the model and make sense of the key mechanisms.
 
@@
 %
-Due to these demands, many works has been dedicated to providing an more intuitive explanation for a given prediction.
-Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e.
-by fitting a similar linear model near the sample of interests).
+Due to these demands, many works have been dedicated to providing a more intuitive explanation for a given prediction.
+Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a similar linear model near the sample of interests).
 %
-However, these methods despite being invaluable for the prediction interpablity task, do not adequently address the challenge in the model diagnostic process.
-More importantly, due to the model agnotic nature, they often the lack of the ability to access and explore the inner states of the model, which is vitally important to make sense of why a model fail.
+However, these methods despite being invaluable for the prediction interpretation task cannot adequately address the challenge in the model diagnostic process.
+More importantly, due to the model agnostic nature, they often the lack of the ability to access and explore the inner states of the model, which is vitally important to make sense of why a model fail.
 
-In this work, we introduce a visualization system that through a tight yet flexible integration between visualization and the underlying model, allow user to interrogate the model by perturbing the input, the internal state, as well as prediction output, while observing chances in other part of the pipeline.
-We use textual entailment task~\cite{} as an example to illustrate how this system can help natural language processing (NLP) researchers quickly identify the potential limitation of a NLP models and also probe the inner states of model for interpreting key mechanism such as attention.
+In this work, we introduce a visualization system that through a tight yet flexible integration between visualization and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
+We use textual entailment task~\cite{} as an example to illustrate how this system can help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model and also probe the inner states of the model for interpreting key mechanism such as attention.
 

### 2018-02-22 paper/relatedWorks.tex
update intro

--- 2018-02-19 paper/relatedWorks_entailVis.tex
@@
 \section{Related Works}
-
-\begin{itemize}
-    \item Depth learning vis
-    \item Vis
-\end{itemize}
 
@@
     instance
-
+\end{itemize}
+\begin{itemize}
+    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
+    Use partial dependency (varying along one feature and observer how prediction changes)
+    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)
 \end{itemize}
@@
 
-Papers:
+Depth learning vis
 \begin{itemize}
-    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
-    Use partial dependency (varying along one feature and observer how prediction changes)
-    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)
+    \item ActiVis: Visual Exploration of Industry-Scale Deep Neural Network Models
+    \item Analyzing the Training Processes of Deep Generative Models
+    \item Visual Diagnosis of Tree Boosting Methods
+    \item TreePOD: Sensitivity-Aware Selection of Pareto-Optimal Decision Trees
+    \item LSTMVis: A Tool for Visual Analysis of Hidden State Dynamics in Recurrent Neural Networks
+    \item Do Convolutional Neural Networks learn Class Hierarchy?
+    \item DeepEyes: Progressive Visual Analytics for Designing Deep Neural Networks
+\end{itemize}
 
-\end{itemize}
+Less emphasis on where does the fail

### 2018-02-22 paper/intro.tex
minor fixes

@@
 \begin{itemize}
-    \item Allow user to quickly identify the mistakes made by the model through input perturbation and visual summerization;
+    \item Identify the mistakes made by the model through perturbation of input sentences and visual summarization of the predictions;
 
-    \item Introduce visual encoding for interpreting the attention that incorporate sentence linguistic structure;
+    \item Enhance the visual representation of attention by overlaying sentence linguistic structure to allow grammar guided simplification;
 
-    \item Interactively explore the relationship between attention and prediction via constrained optimization
+    \item Enable the interrogation of the attention mechanism by interactively exploring how the change in prediction affect the attention and vice versa while fixing other part of the model
+
 \end{itemize}

### 2018-02-22 paper/paper_entailVis.tex
minor fixes

@@
 \abstract{
-With the recent advances of deep learning, neural network based models have reset
-the state-of-the-art for nearly all linguistic tasks in natural language
-processing. The disruptive advance also brings enormous challenges.
-The opaque nature of neural network model leads to hard to debug system and
-difficult to interpret mechanism~cite{}. In this work, we use textual
-entailment task as an example to illustrate how a flexible visualization
-system can help NLP researchers quickly identify the potential limitation of
-a models and interpret the model inner states for make sense of the attention mechanism.
+With the recent advances in deep learning, neural network based models have reset the state-of-the-art performance for nearly all linguistic tasks in natural language processing.
+The disruptive progress also brings enormous challenges.
+The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms.
+In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, attention, and the prediction.
 } % end of abstract

### 2018-02-22 paper/intro.tex
fix bibtex

@@
 On the one hand, the standard evaluation approach provides limited information.
-Often only performance number is used (i.e., prediction accuracy on the test set) without answering many important questions for the diagnostic process.
-It would be instrumental to understand what are the often made mistakes, and how sensitive are the model concerning perturbation in the input, etc.
-On the other hand, the understanding why the model fails is even more challenging, which likely require the ability to peak into the model and make sense of the key mechanisms.
+The performance number (i.e., prediction accuracy on the test set) alone often cannot answer many important questions for the model diagnostic process.
+Understanding what the often made mistakes are, and how sensitive are the model concerning perturbation in the input, etc., are instrumental.
+On the other hand, understanding why the model fails is challenging as well, which undoubtedly will require the ability to peek inside the model and make sense of the critical internal mechanisms.
 
@@
 %
-Due to these demands, many works have been dedicated to providing a more intuitive explanation for a given prediction.
-Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a similar linear model near the sample of interests).
+Due to these demands, many works have been dedicated to providing intuitive explanations for a given prediction.
+Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
 %
-However, these methods despite being invaluable for the prediction interpretation task cannot adequately address the challenge in the model diagnostic process.
-More importantly, due to the model agnostic nature, they often the lack of the ability to access and explore the inner states of the model, which is vitally important to make sense of why a model fail.
+However, despite being invaluable for the prediction interpretation task these methods often cannot adequately address the challenge in the model diagnostic process.
+More importantly, due to the model agnostic nature, they lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail.
 
-In this work, we introduce a visualization system that through a tight yet flexible integration between visualization and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
-We use textual entailment task~\cite{} as an example to illustrate how this system can help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model and also probe the inner states of the model for interpreting key mechanism such as attention.
+In this work, we introduce a visualization system that through a tight yet flexible integration between visual analytic elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
+We use textual entailment task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model and probe the inner states of the model for interpreting key mechanism such as attention.
 

### 2018-02-25 src/modelInterface.py
experiment with different attention

@@ -178,6 +178,8 @@ class modelInterface:
     def attention(self, att_name="att_soft1"):
         #get the current attention, this seems to be reading attention from file
         batch_att = getattr(self.shared, att_name)
+        print self.shared.keys()
+        print "get attention: ", att_name
         # print('printing {0} for {1} examples...'.format(att_name, self.shared.batch_l))
         # for i in xrange(self.shared.batch_l):
         #     ex_id = self.shared.batch_ex_idx[i]

### 2018-02-25 src/visPackage/static/components/predictionComponent.js

@@ -9,7 +9,7 @@ class predictionComponent extends baseComponent {
         super(uuid);
 
         //subscribe to data
-        this.subscribeDatabyNames(["allSourcePairs", "allTargetPairs",
+        this.subscribeDatabyNames(["allSourceSens", "allTargetSens",
             "prediction", "allPairsPrediction"
         ]);
 
@@ -173,9 +173,9 @@ class predictionComponent extends baseComponent {
                 .style("opacity", 0.5)
                 //   .style("opacity", (d,i)=>{if (i==0) return "1.0"; else return "0.5";})
                 .on("click", (d, i) => {
-                    if (this.data["allSourcePairs"] !== undefined) {
-                        var source = this.data["allSourcePairs"][d[3]];
-                        var target = this.data["allTargetPairs"][d[4]];
+                    if (this.data["allSourceSens"] !== undefined) {
+                        var source = this.data["allSourceSens"][d[3]];
+                        var target = this.data["allTargetSens"][d[4]];
                         this.setData("currentPair", [
                             source,
                             target
@@ -213,5 +213,10 @@ class predictionComponent extends baseComponent {
                 .attr("opacity", 0.6)
                 .attr("d", d3.geoPath());
         }
+    }
+
+    //drawing a series of predictions
+    drawPredictPath() {
+
     }
 }

### 2018-02-25 src/visPackage/static/components/sentenceComponent.js

@@ -88,20 +88,20 @@ class sentenceComponent extends baseComponent {
 
         d3.select(this.div + "src").property("value", currentPair[0]);
         d3.select(this.div + "targ").property("value", currentPair[1]);
-        // console.log("----------", this.data["allSourcePairs"]);
-        if (this.data["allSourcePairs"]) {
+        // console.log("----------", this.data["allSourceSens"]);
+        if (this.data["allSourceSens"]) {
 
             $(this.div + "src").highlightWithinTextarea({
                 highlight: this.getSentenceDiff(
-                    this.data["allSourcePairs"][0],
+                    this.data["allSourceSens"][0],
                     currentPair[0]), //
                 className: 'blue'
             });
         }
-        if (this.data["allTargetPairs"]) {
+        if (this.data["allTargetSens"]) {
             $(this.div + "targ").highlightWithinTextarea({
                 highlight: this.getSentenceDiff(
-                    this.data["allTargetPairs"][0],
+                    this.data["allTargetSens"][0],
                     currentPair[1]), //
                 className: 'blue'
             });
@@ -127,8 +127,8 @@ class sentenceComponent extends baseComponent {
         this.clearDropdown(this.div + "srcInput");
         this.clearDropdown(this.div + "targInput");
 
-        this.setData("allSourcePairs", [currentPair[0]]);
-        this.setData("allTargetPairs", [currentPair[1]]);
+        this.setData("allSourceSens", [currentPair[0]]);
+        this.setData("allTargetSens", [currentPair[1]]);
     }
 
     onUpdateCurrentPair() {
@@ -142,11 +142,11 @@ class sentenceComponent extends baseComponent {
     updatePerturbedSentences(sentences) {
 
         if (this.data["currentPair"][0] == sentences[0]) {
-            this.setData("allSourcePairs", sentences);
+            this.setData("allSourceSens", sentences);
             this.addDropdown(this.div + "srcInput", sentences, this.div +
                 "src");
         } else if (this.data["currentPair"][1] == sentences[0]) {
-            this.setData("allTargetPairs", sentences);
+            this.setData("allTargetSens", sentences);
             this.addDropdown(this.div + "targInput", sentences, this.div +
                 "targ");
         }

### 2018-02-25 src/visPackage/visModule.py

@@ -29,6 +29,14 @@ exampleData = [{
     "index":1,
     "src": "Two young children in blue jerseys , one with the number 9 and one with the number 2 are standing on wooden steps in a bathroom and washing their hands in a sink .\n",
     "targ": "Two kids in numbered jerseys wash their hands .\n"
+},{
+    "index":2,
+    "src": "This church choir sings to the masses as they sing joyous songs from the book at a church .",
+    "targ": "The church has cracks in the ceiling ."
+},{
+    "index":3,
+    "src": "A woman with a green headscarf , blue shirt and a very big grin .",
+    "targ": "The woman is young ."
 }
 ]
 
@@ -80,8 +88,8 @@ class visModule:
 data organization structure
     - sentenceList (list of example pairs)
     - currentPair (the current selected pair)
-    - allSourcePairs (all source pairs including the oringal)
-    - allTargetPairs (all target pairs including the oringal)
+    - allSourceSens (all source sentences including the oringal)
+    - allTargetSens (all target sentences including the oringal)
     - allPairsPrediction (a matrix record the predict for all combination of pairs)
     - perturbedSource
     - perturbedTarget
@@ -141,36 +149,38 @@ class textEntailVisModule(visModule):
         sentencePair = dataManager.getData("currentPair")
         predictionResult = self.predictionHook(sentencePair)
         dataManager.setData("prediction", predictionResult)
-        attentionMatrix = self.attentionHook()
+        #use raw attention
+        attentionMatrix = self.attentionHook("att1")
         dataManager.setData("attention", attentionMatrix)
 
     def updateAttention(self):
         sentencePair = dataManager.getData("currentPair")
         predictionResult = self.predictionHook(sentencePair)
         # dataManager.setData("prediction", predictionResult)
-        attentionMatrix = self.attentionHook()
+        #use raw attention
+        attentionMatrix = self.attentionHook("att1")
         dataManager.setData("attention", attentionMatrix)
 
     def predictAll(self):
-        allSourcePairs = None
-        allTargetPairs = None
-        if dataManager.getData("allSourcePairs") is not None:
-            allSourcePairs = dataManager.getData("allSourcePairs")
+        allSourceSens = None
+        allTargetSens = None
+        if dataManager.getData("allSourceSens") is not None:
+            allSourceSens = dataManager.getData("allSourceSens")
         else:
-            allSourcePairs = [dataManager.getData("currentPair")[0]]
[…]

### 2018-03-03 paper/background.tex
fix resizing

@@
 
-Recently, with the wide adoption of long-short term memory
-(LSTM) network and the introduction of attention mechanism,
-neural network based model have
-dominated nearly all linguistic tasks and thoroughtly refreshed the
-baseline performances.
-%
-However, the disruptive advance also brings enormous challenges.
-Due to the opaque nature of the neural network model, interpret and making sense
-of many internal model mechanisms can be extremely challenging.
-%
-Many methods has been proprosed
+\begin{itemize}
+    \item Motivation for TE: reading comprehension, similarity of senten ce
+    \item what is it?
+    \item its connection with other NLP tasks (one of the key)
+    \item
+\end{itemize}
 
-The discrete nature of words and
-sentences presents additional challenge for make sense of the model.
+The grand challenge in natural language processing (NLP) such as
+machine reading require a deeper understanding the
+
+% Recently, with the wide adoption of long-short term memory
+% (LSTM) network and the introduction of attention mechanism,
+% neural network based model have dominated nearly all linguistic tasks
+% and thoroughtly refreshed many baseline performances.
+% %
+% However, the disruptive advance also brings enormous challenges.
+% Netural network work based on has long been critizied for their opaque nature,
+% and often been regarded as back box approach.
+% Due to the opaque nature of the neural network model, interpret and making sense
+% of many internal model mechanisms can be extremely challenging.
+
+The discrete nature of words and sentences presents additional challenge for
+interpreting the model, since many visualization technique often employed
+for images rely on continues nature of the input space (e.g., one can interpolate
+real values much easier than interplolate between words/sentences).
 %
 
-\subsection{Textual Entailment Problem}
+% \subsection{Natural Language Inference}
 
-\begin{itemize}
-    \item what is the textaul entailment problem
-    \item the importance of textual entailment problem
-    \item how easily can the visualization method extends other NLP problem
-\end{itemize}
+% \begin{itemize}
+%     \item what is the textaul entailment problem
+%     \item the importance of textual entailment problem
+%     \item how easily can the visualization method extends other NLP problem
+% \end{itemize}
 
-Textual entailment is one of major natural language tasks, namely translation,
-summarization, question
+Textual entailment is one of major natural language tasks, namely translation, summarization, question
 
-\subsection{Interprebilty Challenges}
+% \subsection{Interprebilty Challenges}
 

### 2018-03-03 paper/intro.tex
fix resizing

@@
 %
-Identify where and how does the error occur and understand why does the model
-fail is critical to the design and application of various models.
+Identify where and how does the error occur and come up with hypothesis for
+why does the model fail is critical to the design and application of various models.
 %quickly identify where the errors are
@@
 On the one hand, the standard evaluation approach provides limited information.
-The performance number (i.e., prediction accuracy on the test set) alone often cannot answer many important questions for the model diagnostic process.
+The performance number (i.e., prediction accuracy on the test set) alone often cannot answer many important questions in the model diagnostic process.
 Understanding what the often made mistakes are, and how sensitive are the model concerning perturbation in the input, etc., are instrumental.
-On the other hand, understanding why the model fails is challenging as well, which undoubtedly will require the ability to peek inside the model and make sense of the critical internal mechanisms.
+On the other hand, infer why the model fails is challenging as well (i.e., models are often referred to as black boxes),
+which require the ability to peek inside the model and understand the relationship between the
+model input, critical internal mechanisms, as well the output predictions.
 
@@
 In this work, we introduce a visualization system that through a tight yet flexible integration between visual analytic elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
-We use textual entailment task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model and probe the inner states of the model for interpreting key mechanism such as attention.
+We use textual entailment task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.
 
@@
 
-    \item Enable the interrogation of the attention mechanism by interactively exploring how the change in prediction affect the attention and vice versa while fixing other part of the model
+    \item Enable the interrogation of the relationship between input sentences, attention, and the prediction by interactively exploring how the change in one of these elements affect other parts of the model.
 

### 2018-03-03 paper/perturbation.tex
fix resizing

@@
 \subsection{Input Perturbation}
+\begin{itemize}
+    \item Just looking at the failure cases is not enough, the prediction maybe correct for the wrong reason
+    \item sensitivity of the model with respect of
+\end{itemize}
+
 Iterate the model design and debug the system hinged on the ability to quickly and identify the errors made by a model.

### 2018-03-03 src/visPackage/static/components/attentionComponent.js

@@ -48,8 +48,6 @@ class attentionComponent extends baseComponent {
         }
     }
 
-
-
     sen2words(sen) {
         var words = sen.match(/\S+/g);
         // words.unshift("\<s\>");

### 2018-03-03 src/visPackage/static/components/evaluationComponent.js

@@ -125,6 +125,8 @@ class evaluationComponent extends baseComponent {
 
     resize() {
         this._updateWidthHeight();
+        this.initSvg(); //update svg size
+
         if (this.treeMap) {
             this.treeMap.update([0, 0], [this.width * 0.5, this.height]);
         }

### 2018-03-03 src/visPackage/static/components/predictionComponent.js

@@ -216,7 +216,11 @@ class predictionComponent extends baseComponent {
     }
 
     //drawing a series of predictions
-    drawPredictPath() {
+    //the old prediction circle with dotted line
+    //the new prediction is solid
+
+    drawPredictPath(path) {
+        //draw arrow
 
     }
 }

### 2018-03-03 src/visPackage/static/plot/histoPlot.js

@@ -4,7 +4,7 @@ Handle multiple histogram
 
 class histoPlot {
     constructor(svg, pos, size) {
-        this.svg = svg;
+        this.svg = svg.append("g");
         this.pos = pos;
         this.size = size;
         this.sample = [10, 9, 7, 6, 7, 3, 2,
@@ -20,6 +20,7 @@ class histoPlot {
     }
 
     draw() {
+        this.svg.selectAll("*").remove();
         var width = this.size[0];
         var height = this.size[1];
         var binNum = 6;
@@ -28,13 +29,11 @@ class histoPlot {
             .domain([0, 11])
             .range([this.pos[0], this.pos[0] + width]);
 
-
         // Generate a histogram using twenty uniformly-spaced bins.
         var histogram = d3.histogram()
             .domain(x.domain())
             .thresholds(x.ticks(binNum))
         var bins = histogram(samples);
-        console.log(bins);
 
         var y = d3.scaleLinear()
             .range([height, 0])

### 2018-03-03 src/visPackage/static/plot/treeMapPlot.js

@@ -1,6 +1,6 @@
 class treeMapPlot {
     constructor(svg, pos, size) {
-        this.svg = svg;
+        this.svg = svg.append("g");
         this.pos = pos;
         this.size = size;
     }
@@ -46,6 +46,7 @@ class treeMapPlot {
     }
 
     drawSimple() {
+        this.svg.selectAll("*").remove();
         var width = this.size[0];
         var height = this.size[1];
 

### 2018-03-06 paper/paper_entailVis.tex
fix bibtex
grammar fix
update title
fix resizing
add perturbation motiation

@@
-\documentclass[journal]{vgtc}                % final (journal style)
-%\documentclass[review,journal]{vgtc}         % review (journal style)
+% \documentclass[journal]{vgtc}                % final (journal style)
+\documentclass[review,journal]{vgtc}         % review (journal style)
 %\documentclass[widereview]{vgtc}             % wide-spaced review
@@
 %% Paper title.
-\title{Where and Why Does the Model Failed?  A Visual Analytics Tool for Debugging and Interpreting Text Entailment Model}
+\title{Where and Why Do Models Fail?  A Visualization Tool for Analyzing and Interpreting Natural Language Inference}
 
@@
 The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms.
-In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, attention, and the prediction.
+In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
 } % end of abstract
@@
 
-\bibliography{template}
+\bibliography{entailVis.bib}
 \end{document}

### 2018-03-06 paper/perturbation.tex
add perturbation motiation

@@
-\section{Analysis of the Model Via Perturbation}
+\section{Error Analysis Via Input Perturbation}
+
+Understand where and how does a model fail is the first step to improve the
+model performance.
+Prediction accuray, i.e., the percentage of the correct prediction according to
+the ground truth label, is the standard technique to verify the performance
+of a model on a given supervised task.
+%
+The accuracy alone does not tell us the whole story, it provides no
+information on the specific example and the condition that lead to a failure.
+%
+Often, the user need to examine individual failure examples to dignostic the
+issue and identify the weakness of the model.
+%
+However, the model may be unstable and generate the right prediction for the wrong
+reason (e.g., by picking up noise in the data that is not the intended features),
+therefore, we are likely to miss some important failure condition by just looking
+at the failure cases.
+%
+An in depth analysis of the error made by the model requires the verification of
+the robustness of the prediction.
+%
+One powerful tool to assess robustness is through the application of small
+perturbation in the input and then check the variation of the prediction.
+%
+For example, we can replace noun and verb in the sentences with words of
+similar/same meaning, such an operation is often carried out by domain experts
+(subconsciously) when they try to figure out the potential issue of a model.
+%
+In another work, the perturbation of the input allow us to do a sensitivity
+analysis on the prediction.
+%
+In this work, we introduce an synonyms perturbation scheme that automatically
+generate the perturbation and generate the prediction and summarized the prediction
+variation.
+%
+
+\begin{itemize}
+    \item perturbation prediction change ratio
+    \item prediction distance (KL divergines) to original prediction
+    \item attention change distance
+\end{itemize}
 
@@
 
-\subsection{Input Perturbation}
-\begin{itemize}
-    \item Just looking at the failure cases is not enough, the prediction maybe correct for the wrong reason
-    \item sensitivity of the model with respect of
-\end{itemize}
+% \subsection{Input Perturbation}
 
@@
 
-\subsection{Attention Perturbation}
+% \subsection{Attention Perturbation}
 
-\subsection{Prediction Perturbation}
+% \subsection{Prediction Perturbation}

### 2018-03-06 src/batchEvaluation.py

@@ -53,36 +53,59 @@ class batchEvaluation:
 
     '''
         generate statistics and write to a JSON file
+        store as hierarchy [origin]->[perturb pairs]
+        - Original Prediction T/F
+        - Perturbation Change Percentage
+        - Prediction Change E/C/N=>E/C/N (all pair)
+
     '''
     def generateStatistic(self):
-        wrongPred = 0
-        allPred = 0
         labels = ["entailment", "neutral", "contradiction"]
+        ## per original pair ##
         self.storage["perturbErrorRatio"] = []
+        ## self.storage["originPredCase"] = []
+        ## per all(perturbed+original) pairs ##
+        self.storage["predCase"] = []
         preOrigIndex = None
         origIndex = None
+
+        count = 0
+        wrongPred = 0
+        allPred = 0
+
+        # json output only have per origina pair information
+        self.jsonOut = {}
+
         for index, srcSen in enumerate(self.storage["srcSens"]):
-            if index > 200:
-                break
+            # if index > 200:
+            #     break
             pred = labels[np.argmax(self.storage["pred"][index])]
             # print  self.storage["mapToOrigIndex"]
             origIndex = self.storage["mapToOrigIndex"][index]
             # print len(self.storage["origLabel"]), origIndex
             # print len(self.storage["origPred"])
-            origLabel = self.storage["origLabel"][origIndex]
-            if pred is not origLabel:
+            origLabel = self.storage["origLabel"][origIndex].rstrip('\n')
+            # print origLabel, pred
+            count = count + 1
+            if pred != origLabel:
                 wrongPred = wrongPred + 1
+                # print wrongPred
 
             allPred = allPred + 1
 
-            if preOrigIndex and preOrigIndex is not origIndex:
+            #store the string for both the ground truth and pred label
+            self.storage["predCase"].append(origLabel+'-'+pred)
+
+            if preOrigIndex and preOrigIndex != origIndex:
+                self.storage["origPerturbCount"] = count
 
                 origPred = self.storage["origPred"][origIndex]
                 ratio = float(wrongPred)/float(allPred)
                 # self.storage["perturbErrorRatio"].append(ratio)
-                print ratio
+                # print ratio
 
                 #### reset variable ####
+                count = 0
                 wrongPred = 0
                 allPred = 0
 
@@ -111,15 +134,25 @@ class batchEvaluation:
                 # generate perturbation
                 # print index, src_orig, targ_orig, label_orig
[…]

### 2018-03-06 src/sentenceGenerator.py

@@ -14,7 +14,7 @@ class sentenceGenerator:
                 self.train_tokens[toks[0].lower()] = 1
 
         # print "angele:", "angele" in self.train_tokens.keys()
-        print "token count:", len(self.train_tokens.keys())
+        # print "token count:", len(self.train_tokens.keys())
 
     def verifySentence(self, sen):
         for word in sen.split():

### 2018-03-19 src/attention/local_attention.py
add swap direction buttom

@@ -61,6 +61,7 @@ class LocalAttention(torch.nn.Module):
 
 		# to use externally specified att values and discard the computed ones
 		if self.opt.customize_att == 1:
+			print "###### using custoimized_att #######"
 			# self.shared.customized_att* will be a torch tensor
 			# thus wrap the tensor in Variable to proceed forward pass
 			customized1 = self.shared.customized_att1 if self.opt.gpuid == -1 else self.shared.customized_att1.cuda()

### 2018-03-19 src/modelInterface.py

@@ -263,10 +263,10 @@ class modelInterface:
 
         ####### set the flag ############
         self.opt.customized = 1
-        self.pipeline = Pipeline(self.opt, self.shared)
+        # self.pipeline = Pipeline(self.opt, self.shared)
         self.shared.customized_att1 = torch.Tensor(attMatrix)
-        print self.shared.customized_att1
-        self.shared.customized_att2 = torch.Tensor(attMatrix).transpose(0,1)
+        # print self.shared.customized_att1
+        self.shared.customized_att2 = torch.Tensor(attMatrix).transpose(1,2).contiguous()
 
         # print source.shape[1], target.shape[1]
         self.pipeline.update_context([0], 1, source.shape[1], target.shape[1])
@@ -280,7 +280,7 @@ class modelInterface:
 
         ####### restore the flag ########
         self.opt.customized = 0
-        self.pipeline = Pipeline(self.opt, self.shared)
+        # self.pipeline = Pipeline(self.opt, self.shared)
         return pred
 
 

### 2018-03-19 src/visPackage/static/components/attentionComponent.js

@@ -122,6 +122,20 @@ class attentionComponent extends baseComponent {
         return normAttention;
     }
 
+    swapAttDirection() {
+        if (this.attentionDirection === 'row') {
+            this.normAttention = this.convertRawAtt(this.rawAttention,
+                'col');
+            this.attentionDirection = 'col';
+            this.draw();
+        } else if (this.attentionDirection === 'col') {
+            this.normAttention = this.convertRawAtt(this.rawAttention,
+                'row');
+            this.attentionDirection = 'row';
+            this.draw();
+        }
+    }
+
     parseDataUpdate(msg) {
         super.parseDataUpdate(msg);
         switch (msg["name"]) {
@@ -135,8 +149,9 @@ class attentionComponent extends baseComponent {
                     this.preRawAtt = JSON.parse(JSON.stringify(this.rawAttention));
                 }
                 this.rawAttention = this.data["attention"];
+                this.attentionDirection = 'row';
                 this.normAttention = this.convertRawAtt(this.rawAttention,
-                    'row');
+                    this.attentionDirection);
 
                 // console.log(this.rawAttention);
                 // console.log(this.normAttention);

### 2018-03-19 paper/paper_entailVis.tex
adjust evaluation panel size

@@
 \documentclass[review,journal]{vgtc}         % review (journal style)
+% \documentclass[review,journal]{vgtc}         % review (journal style)
 %\documentclass[widereview]{vgtc}             % wide-spaced review
@@
 %% it is recomended to use ``\autoref{sec:bla}'' instead of ``Fig.~\ref{sec:bla}''
-\graphicspath{{figures/}{pictures/}{images/}{./}} % where to search for the images
+\graphicspath{{figures/}{pictures/}{figs/}{./}} % where to search for the images
 
@@
 %% * theory/model
-\vgtcpapertype{please specify}
+\vgtcpapertype{application}
 
 %% Paper title.
-\title{Where and Why Do Models Fail?  A Visualization Tool for Analyzing and Interpreting Natural Language Inference}
-
+\title{How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference}
 %% This is how authors are specified in the journal style
@@
 % }
+\teaser{
+% \vspace{-8mm}
+ % \includegraphics[width=0.78\linewidth]{teaser}
+ \includegraphics[width=.96\linewidth]{teaser.pdf}
+ \centering
+ % \vspace{-3mm}
+  \caption{
+ System overview.
+  }
+\label{fig:teaser}
+}
 
@@
 \input{attention.tex} % how to encode the information
+\input{pipeline.tex}
 \input{application.tex}

### 2018-03-19 src/visPackage/static/components/evaluationComponent.js

@@ -41,13 +41,13 @@ class evaluationComponent extends baseComponent {
             // this.svgSave = new svgExporter(this.svgContainer, [this.width -
             //     10, 10
             // ]);
-            this.treeMap = new treeMapPlot(this.svg, [0, 0], [
+            this.treeMap = new treeMapPlot(this.svg, [10, 0], [
                 this.width * 0.5, this.height * 0.5
             ]);
             this.treeMap.bindSelectionCallback(this.updateHisto.bind(
                 this));
 
-            this.histo = new histoPlot(this.svg, [0, this.height * 0.5], [
+            this.histo = new histoPlot(this.svg, [10, this.height * 0.5], [
                 this.width * 0.5, this.height * 0.5
             ], true);
             this.histo.bindSelectionCallback(this.updateScatterplot.bind(
@@ -70,14 +70,14 @@ class evaluationComponent extends baseComponent {
                 .attr("height", this.height);
 
             // this.svg.selectAll("text,rect,path").remove();
-            this.treeMap.update([0, 0], [
-                this.width * 0.5, this.height * 0.5
+            this.treeMap.update([5, 0], [
+                this.width * 0.5 - 5, this.height * 0.5
             ]);
-            this.histo.update([0, this.height * 0.6], [
-                this.width * 0.5, this.height * 0.4
+            this.histo.update([8, this.height * 0.6], [
+                this.width * 0.5 - 8, this.height * 0.4
             ]);
-            this.scatter.update([this.width * 0.5, 0], [
-                this.width * 0.5, this.height
+            this.scatter.update([this.width * 0.5 + 5, 0], [
+                this.width * 0.5 - 5, this.height
             ]);
             // this.svgSave.updatePos([this.width - 10, 10])
             // this.svgSave.draw();

### 2018-03-19 src/visPackage/static/components/attentionComponent.js
fix toggle buttons

@@ -99,7 +99,7 @@ class attentionComponent extends baseComponent {
     }
 
     attUpdate() {
-        console.log(this.normAttention);
+        // console.log(this.normAttention);
         this.callFunc("attentionUpdate", {
             "attMatrix": this.normAttention
         });
@@ -300,12 +300,17 @@ class attentionComponent extends baseComponent {
             this.normAttention = this.convertRawAtt(this.rawAttention);
             this.draw();
         } else if (mode === "P") { //previous
-            this.normAttention = this.convertRawAtt(this.preRawAtt);
-            this.draw();
+            if (this.preRawAtt) {
+                this.normAttention = this.convertRawAtt(this.preRawAtt);
+                this.draw();
+            }
         } else if (mode === "D") { //difference
-            this.normAttention = this.attDiff(this.convertRawAtt(this.rawAttention),
-                this.convertRawAtt(this.preRawAtt));
-            this.draw();
+            if (this.preRawAtt) {
+                this.normAttention = this.attDiff(this.convertRawAtt(this.rawAttention),
+                    this.convertRawAtt(this.preRawAtt));
+
+                this.draw();
+            }
         }
     }
 
@@ -336,6 +341,10 @@ class attentionComponent extends baseComponent {
             .attr("fill", "lightgrey")
             .on("click", d => {
                 this.toggleAttMode(d);
+            }).on("mouseover", function(d) {
+                d3.select(this).attr("fill", "grey");
+            }).on("mouseout", function(d) {
+                d3.select(this).attr("fill", "lightgrey");
             });
 
         toggle.selectAll(".toggleLabel")

### 2018-03-19 paper/background.tex
updates on background, intro (very minor change), and bib

@@
 \begin{itemize}
-    \item Motivation for TE: reading comprehension, similarity of senten ce
+    \item Motivation for : reading comprehension, similarity of sentennce
     \item what is it?
@@
 
-The grand challenge in natural language processing (NLP) such as
-machine reading require a deeper understanding the
+The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
+deep comprehension of textual information. Major tasks include Natural Language Inference,
+Machine Translation, Questions Answering, Summarization, and etc. 
+Recently, neural networks models have performed strongly on these tasks.
+
+Therefore, making sense and explaining predictions made by deep neural networks is not only 
+essential for validating and improving the model, but also becoming a necessity with 
+increasing demands for model accountability (e.g., what is the evidence for making the decision) 
+and model fairness (e.g., is the prediction affected by the bias in the training data).
 
@@
 
-The discrete nature of words and sentences presents additional challenge for
-interpreting the model, since many visualization technique often employed
-for images rely on continues nature of the input space (e.g., one can interpolate
-real values much easier than interplolate between words/sentences).
 %
 
-% \subsection{Natural Language Inference}
+\subsection{Interprebilty Challenges}
+
+Compared with Conputer Vision, the discrete nature of words and sentences 
+presents additional challenge for
+interpreting the model, since many visualization technique often employed
+for images rely on continuous nature of the input space (e.g., one can interpolate
+real values much easier than interplolate between words/sentences).
+
+On the other hand, a majority of recent NLP neural networks share the nature of 
+end-to-end model, where the entire model operates as a black-box that takes 
+vectorized input and yields final prediction for a specific task.
+Therefore, to study the inside of end-to-end neural models, it is important to 
+explore the interaction between intermediate representations and predictions.
+
+The introduction of attention mechanism~\cite{bahdanau2014neural} allows 
+pairwise interaction between hidden states. This interaction can be naturally explained
+as a form of alignment which exposes an interpretable layer in end-to-end neural networks. 
+Recently attention has contributed to many strongly-performed NLP models
+~\cite{parikh2016emnlp},~\cite{rush2015neural},~\cite{yang2016hierarchical},
+~\cite{seo2016bidirectional},~\cite{schwartz2017high}. 
+We will focus on its application in Natural Language Inference task as proposed in~\cite{parikh2016emnlp}.
+However notice that our visualization can be generalized to other attention models as well.
+
+% The introduction of attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences.
+The new challenges
+
+\subsection{Natural Language Inference}
+Natural Language Inference(cite?) is an important machine understanding task in NLP. 
+The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence. 
+The prediction must fall in one of three catergories: $\{Entailment, Contradiction, Neutral\}$. 
+$Entailment$ refers to that the textual information of hypothesis is embedded in premise; 
+$Contradiction$ means the textuals of hypothesis opposes that of premise; 
+and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.
+
+Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine 
+the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.
+
+% showing an example??
 
@@
 % \end{itemize}
-
-Textual entailment is one of major natural language tasks, namely translation, summarization, question
-
-% \subsection{Interprebilty Challenges}
-
-The introduction of attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences.
-The new challenges
-
-Making sense and explaining predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).

### 2018-03-19 paper/intro.tex
minor update to text
adjust evaluation panel size
fix toggle buttons
updates on background, intro (very minor change), and bib

@@
 
+%%%%%%%%% accessing internal states are important %%%%%%%%%%%%
 Making sense and explaining predictions made by neural networks is also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
@@
 
+%%%%%%%%%% interrogate relationship between different componenet, modified different componenets %%%%%%%%%%%
+Beside looking into the internal states, understanding how each of the component interact with each other provide more insight about the mechanism of the model.
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{pipeline}
+ \caption{Language Inference Model Pipeline.}
+\label{fig:projTransition}
+\vspace{-5mm}
+\end{figure}
+
 In this work, we introduce a visualization system that through a tight yet flexible integration between visual analytic elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
-We use textual entailment task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.
+We use natural language inference task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.
 

### 2018-03-19 paper/intro.tex
update intro

@@
 %the potential limitation of the test dataset
-On the one hand, the standard evaluation approach provides limited information.
-The performance number (i.e., prediction accuracy on the test set) alone often cannot answer many important questions in the model diagnostic process.
-Understanding what the often made mistakes are, and how sensitive are the model concerning perturbation in the input, etc., are instrumental.
+On the one hand, recognize where the model fail is non trivial.
+The standard evaluation approach provides limited information.
+i.e., the performance number (e.g., prediction accuracy on the test set) alone cannot answer many important questions in the model diagnostic process, such as what the often made mistakes are, and how sensitive are the model concerning small perturbation in the input, etc.
 On the other hand, infer why the model fails is challenging as well (i.e., models are often referred to as black boxes),
@@
 %%%%%%%%% accessing internal states are important %%%%%%%%%%%%
-Making sense and explaining predictions made by neural networks is also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
+The wide application of machine learning models also call for increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
+% Making sense and explaining predictions made by neural networks is also becoming a necessity.
 %
-Due to these demands, many works have been dedicated to providing intuitive explanations for a given prediction.
-Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
+Many works~\cite{RibeiroSinghGuestrin2016} have been dedicated to providing intuitive explanations for a given prediction, several of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
 %
-However, despite being invaluable for the prediction interpretation task these methods often cannot adequately address the challenge in the model diagnostic process.
-More importantly, due to the model agnostic nature, they lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail.
+Despite being invaluable for the providing human understandable explaination, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
 
 %%%%%%%%%% interrogate relationship between different componenet, modified different componenets %%%%%%%%%%%
-Beside looking into the internal states, understanding how each of the component interact with each other provide more insight about the mechanism of the model.
+Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly exmaine the mechanism of the model.
+%
+Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.
 
@@
 \end{itemize}
-
-% NLP application using attention
-% \begin{itemize}
-%     \item Neural translation
-%     \item Text summarization
-%     \item Text entailment
-%     \item Text comprehension (question answering)
-% \end{itemize
-%
-%
-% Attention type:
-% \begin{itemize}
-%     \item soft vs. hard
-%     \item local vs. global
-%     \item hierarchical
-%     \item attention over attention
-%     \item gated
-% \end{itemize}

### 2018-03-20 src/modelInterface.py
update attention is more or less working

@@ -124,6 +124,20 @@ class modelInterface:
             self.pipeline = self.pipeline.cuda()
             self.optim = self.optim.cuda()
 
+    def mapToToken_without_s(self, sentence):
+        tokenList = []
+        sentence = sentence.rstrip().split(" ")
+        for word in sentence:
+            if word in self.tokenMap.keys():
+                tokenList.append(self.tokenMap[word])
+            else:
+                tokenList.append(self.tokenMap["<unk>"])
+        #1XN array
+        # tokenList.append(self.tokenMap["<s>"])
+        # print tokenList
+        token = torch.LongTensor(tokenList).view(1, len(tokenList))
+        # print token
+        return token
 
     def mapToToken(self, sentence):
         tokenList = [self.tokenMap["<s>"]]
@@ -205,6 +219,7 @@ class modelInterface:
         # for i in xrange(self.shared.batch_l):
         #     ex_id = self.shared.batch_ex_idx[i]
         #remove the attention corresponds to <s>
+        # att = batch_att.data[0, 0:, 0:]
         att = batch_att.data[0, 1:, 1:]
         att = att.numpy()
         print "attention range:", att.min(), att.max()
@@ -244,6 +259,7 @@ class modelInterface:
         # print y
         # m, y = overfit_to_ex(self.opt, self.shared, self.embeddings, self.optim, self.pipeline, ex)
         # print y
+        # print 'att_soft1', self.shared.att_soft1.data[0, 0:, 0:].numpy()
         print 'att_soft1', self.shared.att_soft1.data[0, 1:, 1:].numpy()
         return "att", y.numpy()[0]
 
@@ -251,8 +267,8 @@ class modelInterface:
         #map to token
         sourceSen = sentencePair[0]
         targetSen = sentencePair[1]
-        source = self.mapToToken(sourceSen)
-        target = self.mapToToken(targetSen)
+        source = self.mapToToken_without_s(sourceSen)
+        target = self.mapToToken_without_s(targetSen)
 
         wv_idx1 = Variable(source, requires_grad=False)
         wv_idx2 = Variable(target, requires_grad=False)
@@ -264,9 +280,11 @@ class modelInterface:
         ####### set the flag ############
         self.opt.customize_att = 1
         # self.pipeline = Pipeline(self.opt, self.shared)
+        ##### pad att to correct size to fix <s> ####
+
         self.shared.customized_att1 = torch.Tensor([att_soft1])
[…]

### 2018-03-20 src/visPackage/static/components/attentionMatrixComponent.js

@@ -200,7 +200,7 @@ class attentionMatrixComponent extends attentionComponent {
         let col = i % this.normAttention[0].length;
 
         if (this.dragEventX < d3.event.x) {
-            if (d.value + 0.1 <= 1) {
+            if (d.value <= 1) {
                 d.value += 0.1;
             }
 
@@ -208,11 +208,13 @@ class attentionMatrixComponent extends attentionComponent {
                 this.normAttentionCol[row][col] += 0.1;
             }
         } else if (this.dragEventX > d3.event.x) {
-            if (d.value - 0.1 >= 0) {
+            if (d.value >= 0) {
                 d.value -= 0.1;
             }
-            if (this.normAttentionCol[row][col] >= 1.0) {
+            if (this.normAttentionCol[row][col] >= 0.0) {
                 this.normAttentionCol[row][col] -= 0.1;
+                if (this.normAttentionCol[row][col] < 0.0)
+                    this.normAttentionCol[row][col] = 0.0;
             }
 
         }

### 2018-03-20 src/overfit_to_ex.py
fix sentences refresh

@@ -88,6 +88,7 @@ def overfit_to_ex(opt, shared, wv, optim, m, ex):
 	# e.g. retain_grad(shared, 'att_soft1')
 	#	then after backward pass, shared.att_soft1.grad will has its gradient
 	retain_grad(shared, 'att_soft1')
+	retain_grad(shared, 'att1')
 
 	# zero out previous gradient and do backward pass
 	m.zero_grad()

### 2018-03-20 src/visPackage/static/components/predictionComponent.js

@@ -69,7 +69,6 @@ class predictionComponent extends baseComponent {
                 .style("font-size", 10);
         }
 
-
         //entailment
         //neutral, Contradiction, Entailment
         //112,0 0,194 224,194

### 2018-03-20 src/visPackage/static/components/sentenceComponent.js

@@ -49,7 +49,23 @@ class sentenceComponent extends baseComponent {
                 break;
             case "currentPair":
                 // console.log(msg, this.data["currentPair"]["sentences"]);
+                let pair = msg["data"]["data"]["sentences"];
+                if (this.oldPair) {
+                    if (this.oldPair[0].split(" ").length !== pair[0].split(
+                            " ").length ||
+                        this.oldPair[1].split(" ").length !== pair[1].split(
+                            " ").length
+                    ) {
+                        this.clearDropdown(this.div + "srcInput");
+                        this.clearDropdown(this.div + "targInput");
+
+                        this.setData("allSourceSens", [pair[0]]);
+                        this.setData("allTargetSens", [pair[1]]);
+                    }
+                }
+
                 this.onReceiveCurrentPair();
+                this.oldPair = pair.slice();
                 break;
         }
     }
@@ -77,7 +93,7 @@ class sentenceComponent extends baseComponent {
             .data(this.data["sentenceList"]).enter()
             .append('option')
             .text(function(d) {
-                return d["index"] + "-" + d["src"] + "/" + d["targ"];
+                return d["src"] + " | " + d["targ"];
             })
             .property("value", (d, i) => i);
     }
@@ -140,9 +156,9 @@ class sentenceComponent extends baseComponent {
         var currentPair = [d3.select(this.div + "src").property("value"),
             d3.select(this.div + "targ").property("value")
         ];
-        // console.log(currentPair);
+        console.log(currentPair);
         this.data["currentPair"]["sentences"] = currentPair;
-        this.setData("currentPair", this.data["currentPair"]["sentences"]);
+        this.setData("currentPair", this.data["currentPair"]);
     }
 
     updatePerturbedSentences(sentences) {

### 2018-03-20 src/visPackage/visModule.py

@@ -222,6 +222,9 @@ class textEntailVisModule(visModule):
         # print pred
         dataManager.setData("prediction", pred)
 
+        #update other predictions if available
+        self.predictAll()
+
     def attention(self):
         sentencePair = dataManager.getData("currentPair")['sentences']
         predictionResult = self.predictionHook(sentencePair)

### 2018-03-20 paper/intro.tex
fix sentences refresh
update abstract

@@
 %the potential limitation of the test dataset
-On the one hand, recognize where the model fail is non trivial.
-The standard evaluation approach provides limited information.
-i.e., the performance number (e.g., prediction accuracy on the test set) alone cannot answer many important questions in the model diagnostic process, such as what the often made mistakes are, and how sensitive are the model concerning small perturbation in the input, etc.
-On the other hand, infer why the model fails is challenging as well (i.e., models are often referred to as black boxes),
-which require the ability to peek inside the model and understand the relationship between the
-model input, critical internal mechanisms, as well the output predictions.
+On the one hand, recognize where the model fail is non-trivial.
+The standard evaluation approach (i.e., the prediction accuracy on the test set) provides limited information and cannot answer many important questions that are essential to the model diagnostic process.
+Questions such as, how stable predictions are concerning small perturbation in the input, how these predictions arrive (i.e., the model may come up with the correct prediction by pickup unintended feature/alignment), and what are the often made mistakes, are all essential in systematic examination and evaluation of the model.
+On the other hand, infer why the model fails is even more challenging.
+Since neural network models are often referred to as black boxes, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships between model inputs, critical internal mechanisms, as well the output predictions.
+
+\begin{itemize}
+    \item Study the classifier  vs. single instance evaluation
+    \item Model agnostic vs. reveal intern states
+    \item View model as invariant object vs. interrogate the model via partial/full updates
+\end{itemize}
 
 %%%%%%%%% accessing internal states are important %%%%%%%%%%%%
+To analyzing the
+Many method has been
+
 The wide application of machine learning models also call for increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).

### 2018-03-20 paper/paper_entailVis.tex
update attention is more or less working
update abstract

@@
 %% Paper title.
-\title{How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference}
+\title{Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference}
 %% This is how authors are specified in the journal style
@@
 \abstract{
-With the recent advances in deep learning, neural network based models have reset the state-of-the-art performance for nearly all linguistic tasks in natural language processing.
+With the recent advances in deep learning, neural network based models have obtained the state-of-the-art performance for many linguistic tasks in natural language processing.
 The disruptive progress also brings enormous challenges.
 The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms.
-In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
+In this work, we use natural language inference task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
 } % end of abstract

### 2018-03-21 paper/intro.tex

@@
 On the other hand, infer why the model fails is even more challenging.
-Since neural network models are often referred to as black boxes, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships between model inputs, critical internal mechanisms, as well the output predictions.
+Since neural network models are often referred to as black boxes, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships among model inputs, critical internal mechanisms, as well the output predictions.
 
@@
     \item Study the classifier  vs. single instance evaluation
-    \item Model agnostic vs. reveal intern states
+    \item Model agnostic vs. reveal internal states
     \item View model as invariant object vs. interrogate the model via partial/full updates
@@
 %%%%%%%%% accessing internal states are important %%%%%%%%%%%%
+Several previous works~\cite{BilalJourablooYe2018} have dedicate to analyzing errors made in analyzing 
+There has been a
 To analyzing the
@@
 \label{fig:projTransition}
-\vspace{-5mm}
 \end{figure}

### 2018-03-21 paper/intro.tex
update intro

--- 2018-03-19 paper/intro.tex
@@
 %
-Identify where and how does the error occur and come up with hypothesis for
-why does the model fail is critical to the design and application of various models.
-%quickly identify where the errors are
-However, providing meaningful answers to these questions is an extremely challenging task.
-% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
-%the potential limitation of the test dataset
-On the one hand, recognize where the model fail is non trivial.
-The standard evaluation approach provides limited information.
-i.e., the performance number (e.g., prediction accuracy on the test set) alone cannot answer many important questions in the model diagnostic process, such as what the often made mistakes are, and how sensitive are the model concerning small perturbation in the input, etc.
-On the other hand, infer why the model fails is challenging as well (i.e., models are often referred to as black boxes),
-which require the ability to peek inside the model and understand the relationship between the
-model input, critical internal mechanisms, as well the output predictions.
+Interpreting the internal mechanism and analyzing how predictions are made are critical to both the design and deployment of a given model.
+More importantly, the ability to pinpoint where and how an error is made and come up with hypothesis for the cause of failure is the key to identify the limitation and improve upon existing models.
+However, providing meaningful answers to these questions are extremely challenging and often regarded as impossible by many.
 
+Recently, substantial research has been developed to combat the model interpretability challenge.
+Most notably, the works~\cite{} on interpretation of convolution neural network (CNN) model from both machine learning and visualization community has reveal the enormous potential and instant benefits of model interpretation, yet they also remind us how little we actually know regarding the inner mechanism of these deep neural network models.
+%
+Many of the existing techniques study the model as an invariant object, where the model's behavior are recorded and analyzed in an offline fashion.
+%
+However, the exploration natural of these type of analysis often lead to \emph{what if ...} types of questions.
+What if I perturbed the current input?
+Will the prediction be stable?
+What if when change the internal state of the model, how could the change affect the prediction.
+What if the current prediction is wrong, how and where should we change the model in order to produce the correct result?
+These type of dynamic queries is a natural way for us to gain understanding and come up with hypothesis of the model mechanisms by \emph{interrogating} the relationship between the input, internal states, and output prediction.
+Yet we do not often need to setup extra specialized experiment to answer.
+
+Compare to image classification task, natural language processing systems have a number of innate restriction (e.g., the discrete nature of words) that makes interpreting them even more challenging.
+For example, \emph{feature visualization}~\cite{}, an often deployed technique for illustrating what kind of image feature a given part of the network (e.g., neuron, layer, or channel) captures, can not be easily generalized and applied for natural language due to the requirement of a continuous solution space (i.e., the image pixel values).
+Even though we can encode a word as an vector~\cite{}, the word embedding space is still a discretely defined space, where the interpolation between two vectors (i.e., two words) do not corresponds to explicit meaning.
+
+On the one hand, recognize where the model fail is non-trivial.
+The standard evaluation approach (i.e., the prediction accuracy on the test set) provides limited information and cannot answer many important questions (e.g., how stable the prediction is, which part of the model may contribute to the failure) that are essential to the model diagnostic process.
+On the other hand, infer the cause of model failure is even more challenging.
+Neural network models are often referred to as black boxes due to the hard to recognize  difficult to interpret parameter, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships among model inputs, critical internal mechanisms, as well the output predictions.
+
+%\begin{itemize}
+%    \item Study the classifier  vs. single instance evaluation
+%    \item Model agnostic vs. reveal internal states
+%    \item View model as invariant object vs. interrogate the model via partial/full updates
+%\end{itemize}
+
+Questions such as, how stable predictions are concerning small perturbation in the input, how are these predictions arrived (i.e., the model may come up with the correct prediction by pickup unintended feature/alignment), and what are the often made mistakes, are all essential in systematic examination and evaluation of the model.
 %%%%%%%%% accessing internal states are important %%%%%%%%%%%%
-The wide application of machine learning models also call for increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
+
 % Making sense and explaining predictions made by neural networks is also becoming a necessity.
@@
 
-%%%%%%%%%% interrogate relationship between different componenet, modified different componenets %%%%%%%%%%%
+%%%%%%%%%% interrogate relationship between different components, modified different components %%%%%%%%%%%
 Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly exmaine the mechanism of the model.

### 2018-03-21 paper/relatedWorks.tex
update intro

@@
 \section{Related Works}
+Due to the significant implication of model interpretability, a wealth of researches of be focused on the explanation and interpretation of deep neural network models.
+
+%%%% summarize analyzing prediction, but not sensitivity %%%%
+Several previous works~\cite{BilalJourablooYe2018} have dedicate to analyzing errors made in analyzing
+
+With the increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data), these techniques only provide us a glimpse of what to come.
+
+%%%% summarize analyzing prediction, but not sensitivity %%%%
+LSTMvis~\cite{StrobeltGehrmannHuber2016} making sense of internal states of the model
+
+There has been a
+To analyzing the
+Many method has been
+
+%%%% interactive steering of the model %%%%
+
+\subsection{Model Interpretability}
 
@@
 
+\subsection{Visualization and HCI}
 Depth learning vis

### 2018-03-21 paper/intro.tex
update structure

@@
 % What is the obsatcle for effectively apply machine learning model
-With the recent advances in neural network based model, machine learning has
-gained unprecedented popularity, and its adaption permeated many fields of studies.
+With the recent advances in neural network based model, machine learning has gained unprecedented popularity, and its adaption permeated many fields of studies.
 %
-However, from researchers to practitioners, one often need to overcome many
-obstacles during the training, debugging, and tuning processes to unleash
-the full potential of these models.
+However, from researchers to practitioners, one often need to overcome many obstacles during the training, debugging, and tuning processes to unleash the full potential of these models.
 %
@@
 %
+Compare to image classification task, natural language processing systems have a number of innate restriction (e.g., the discrete nature of words) that makes interpreting them even more challenging.
+For example, \emph{feature visualization}~\cite{}, an often deployed technique for illustrating what kind of image feature a given part of the network (e.g., neuron, layer, or channel) captures, can not be easily generalized and applied for natural language due to the requirement of a continuous solution space (i.e., the image pixel values).
+Even though we can encode a word as an vector~\cite{}, the word embedding space is still a discretely defined space, where the interpolation between two vectors (i.e., two words) do not corresponds to explicit meaning.
+%
+In this work, we introduce a visualization system specific tailor to natural language model, specifical natural language inference, in which we address many domain specific challenges.
+
 Many of the existing techniques study the model as an invariant object, where the model's behavior are recorded and analyzed in an offline fashion.
@@
 Will the prediction be stable?
-What if when change the internal state of the model, how could the change affect the prediction.
+What if we change one of the key internal states of the model, how would the change affect the prediction.
 What if the current prediction is wrong, how and where should we change the model in order to produce the correct result?
 These type of dynamic queries is a natural way for us to gain understanding and come up with hypothesis of the model mechanisms by \emph{interrogating} the relationship between the input, internal states, and output prediction.
-Yet we do not often need to setup extra specialized experiment to answer.
-
-Compare to image classification task, natural language processing systems have a number of innate restriction (e.g., the discrete nature of words) that makes interpreting them even more challenging.
-For example, \emph{feature visualization}~\cite{}, an often deployed technique for illustrating what kind of image feature a given part of the network (e.g., neuron, layer, or channel) captures, can not be easily generalized and applied for natural language due to the requirement of a continuous solution space (i.e., the image pixel values).
-Even though we can encode a word as an vector~\cite{}, the word embedding space is still a discretely defined space, where the interpolation between two vectors (i.e., two words) do not corresponds to explicit meaning.
-
-On the one hand, recognize where the model fail is non-trivial.
-The standard evaluation approach (i.e., the prediction accuracy on the test set) provides limited information and cannot answer many important questions (e.g., how stable the prediction is, which part of the model may contribute to the failure) that are essential to the model diagnostic process.
-On the other hand, infer the cause of model failure is even more challenging.
-Neural network models are often referred to as black boxes due to the hard to recognize  difficult to interpret parameter, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships among model inputs, critical internal mechanisms, as well the output predictions.
+Yet, we often need to tediously setup specialized experiment to obtain the answers.
+%
+In this work, we aim to provide quick and intuitive answers to these \emph{what if ...} questions.
+Instead of viewing the model as an invariant entitle, we employ a perturbation centric mentally to probe the model and examine how changes in one part of the pipeline affect others, which in term provide a new perspective to look at the model interpretation problem.
 
@@
 
-Questions such as, how stable predictions are concerning small perturbation in the input, how are these predictions arrived (i.e., the model may come up with the correct prediction by pickup unintended feature/alignment), and what are the often made mistakes, are all essential in systematic examination and evaluation of the model.
+%Questions such as, how stable predictions are concerning small perturbation in the input, how are these predictions arrived (i.e., the model may come up with the correct prediction by pickup unintended feature/alignment), and what are the often made mistakes, are all essential in systematic examination and evaluation of the model.
 %%%%%%%%% accessing internal states are important %%%%%%%%%%%%
 
-% Making sense and explaining predictions made by neural networks is also becoming a necessity.
-%
-Many works~\cite{RibeiroSinghGuestrin2016} have been dedicated to providing intuitive explanations for a given prediction, several of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
-%
-Despite being invaluable for the providing human understandable explaination, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
-
 %%%%%%%%%% interrogate relationship between different components, modified different components %%%%%%%%%%%
-Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly exmaine the mechanism of the model.
-%
-Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.
-
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipeline}
- \caption{Language Inference Model Pipeline.}
-\label{fig:projTransition}
-\end{figure}
-
-In this work, we introduce a visualization system that through a tight yet flexible integration between visual analytic elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
-We use natural language inference task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.
 
@@
 % Interpret/probe the relationship between attention and the prediction result
+
+% On the one hand, recognize where the model fail is non-trivial.
+The standard evaluation approach (i.e., the prediction accuracy on the test set) provides limited information and cannot answer many important questions (e.g., how stable the prediction is, which part of the model may contribute to the failure) that are essential to the model diagnostic process.
+On the other hand, infer the cause of model failure is even more challenging.
+Neural network models are often referred to as black boxes due to the hard to recognize  difficult to interpret parameter, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships among model inputs, critical internal mechanisms, as well the output predictions.
 

### 2018-03-21 paper/paper_entailVis.tex
update intro
update structure

@@
 %% OnlineID. Otherwise, you may safely leave it at ``0''.
-\onlineid{0}
+\onlineid{1095}
 
@@
 %% * theory/model
-\vgtcpapertype{application}
+\vgtcpapertype{Application}
 
 %% Paper title.
-\title{Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference}
+\title{
+p-NLI: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
+%Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
+}
 %% This is how authors are specified in the journal style
@@
 %other entries to be set up for journal
-\shortauthortitle{Text Entailment Model Visualization}
+\shortauthortitle{Natural Language Inference Model Visualization}
 %\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}
@@
 The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms. 
-In this work, we use natural language inference task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
+%In this work, we use natural language inference task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
+In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
+%
+We use natural language inference task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.
 } % end of abstract
@@
 \input{relatedWorks.tex}
+
 \input{background.tex}
-% \input{tasks.tex}
+%\input{tasks.tex}
+\input{pipeline.tex}
 \input{perturbation.tex} % how to do the perturbation
 \input{attention.tex} % how to encode the information
-\input{pipeline.tex}
+
 \input{application.tex}

### 2018-03-21 paper/pipeline.tex
update structure

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{Language Inference Model Pipeline.}
\label{fig:projTransition}
\end{figure}

\section{Overview}
Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.
%
Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.

### 2018-03-21 paper/relatedWorks.tex
update structure

@@
 \end{itemize}
+% Making sense and explaining predictions made by neural networks is also becoming a necessity.
+%
+Many works~\cite{RibeiroSinghGuestrin2016} have been dedicated to providing intuitive explanations for a given prediction, several of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
+%
+Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
 

### 2018-03-21 paper/intro.tex
update reference

@@
 %
-Interpreting the internal mechanism and analyzing how predictions are made are critical to both the design and deployment of a given model.
+Interpreting the internal mechanism and analyzing how predictions are made are critical to both the design and deployment of a model.
 More importantly, the ability to pinpoint where and how an error is made and come up with hypothesis for the cause of failure is the key to identify the limitation and improve upon existing models.
@@
 Recently, substantial research has been developed to combat the model interpretability challenge.
-Most notably, the works~\cite{} on interpretation of convolution neural network (CNN) model from both machine learning and visualization community has reveal the enormous potential and instant benefits of model interpretation, yet they also remind us how little we actually know regarding the inner mechanism of these deep neural network models.
+Most notably, the works~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018} on interpretation of convolution neural network (CNN) model from both machine learning and visualization community has reveal the enormous potential and instant benefits of model interpretation, yet they also remind us how little we actually know regarding the inner mechanism of these deep neural network models.
 %
-Compare to image classification task, natural language processing systems have a number of innate restriction (e.g., the discrete nature of words) that makes interpreting them even more challenging.
-For example, \emph{feature visualization}~\cite{}, an often deployed technique for illustrating what kind of image feature a given part of the network (e.g., neuron, layer, or channel) captures, can not be easily generalized and applied for natural language due to the requirement of a continuous solution space (i.e., the image pixel values).
-Even though we can encode a word as an vector~\cite{}, the word embedding space is still a discretely defined space, where the interpolation between two vectors (i.e., two words) do not corresponds to explicit meaning.
+Compare to image classification task, natural language processing systems have a number of innate restriction (e.g., the discrete nature of words) that makes the road to interpretion more treacherous.
+For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what kind of image feature a given part of the network (e.g., neuron, layer, or channel) captures, can not be easily generalized and applied for natural language due to the requirement of an interpretable continuous solution space, i.e., the image pixel values, in which human user can easily recongized (or the absent of) patterns or shapes.
+On the other hand, even though we have the ability to encode a word as an vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still a discretely defined space, where the interpolation between two vectors (i.e., two words) do not corresponds to explicit meaning.
+
+These restrictions that prevent the application of the well-established interprability approach to natural language models motivated us to develop the proposed perturbation-driven technique.
 %
-In this work, we introduce a visualization system specific tailor to natural language model, specifical natural language inference, in which we address many domain specific challenges.
-
-Many of the existing techniques study the model as an invariant object, where the model's behavior are recorded and analyzed in an offline fashion.
+In addition, many of the existing techniques study the model as an invariant object, where the model's behaviors are recorded and analyzed in an offline fashion.
 %
-However, the exploration natural of these type of analysis often lead to \emph{what if ...} types of questions.
+However, the exploratory natural of the model interpretation analysis often lead to \emph{what if ...} types of questions.
 What if I perturbed the current input?
 Will the prediction be stable?
-What if we change one of the key internal states of the model, how would the change affect the prediction.
-What if the current prediction is wrong, how and where should we change the model in order to produce the correct result?
-These type of dynamic queries is a natural way for us to gain understanding and come up with hypothesis of the model mechanisms by \emph{interrogating} the relationship between the input, internal states, and output prediction.
-Yet, we often need to tediously setup specialized experiment to obtain the answers.
-%
+What if we change one of the key internal states of the model, how would the modification affect the prediction.
+What if the current prediction is wrong, how and where should we change the model parameters in order to produce the correct result?
+These type of dynamic queries form a natural way for us to gain understanding and come up with hypothesis of the model mechanisms by \emph{interrogating} what a componenet do by perturb it and then observe the effects on other part of the system.
+Therotically, we  Yet, we often need to tediously setup specialized experiment to obtain the answers.
+
+relationship between the input, internal states, and output prediction.
 In this work, we aim to provide quick and intuitive answers to these \emph{what if ...} questions.

### 2018-03-21 paper/intro.tex
update test

@@
 Compare to image classification task, natural language processing systems have a number of innate restriction (e.g., the discrete nature of words) that makes the road to interpretion more treacherous.
-For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what kind of image feature a given part of the network (e.g., neuron, layer, or channel) captures, can not be easily generalized and applied for natural language due to the requirement of an interpretable continuous solution space, i.e., the image pixel values, in which human user can easily recongized (or the absent of) patterns or shapes.
-On the other hand, even though we have the ability to encode a word as an vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still a discretely defined space, where the interpolation between two vectors (i.e., two words) do not corresponds to explicit meaning.
+For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) capture, can not be easily generalized and applied for natural language due to the requirement of an interpretable continuous solution space, i.e., the image pixel values, in which human user can easily recongized (or the absent of) patterns or shapes.
+For natural language, even though we have the ability to encode a word as an vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still a discretely defined space, where the interpolation between two vectors (i.e., two words) do not corresponds to explicit meaning.
+%
+These restrictions call for new avenues to solve the interpretation challenge of natural langugage models, which motivate the proposed work.
 
-These restrictions that prevent the application of the well-established interprability approach to natural language models motivated us to develop the proposed perturbation-driven technique.
+In this work, we focus on model that aim to solve the natural language inference problem.
+In the simplest form, the inference task ask the question about whether \emph{sentence A} can infer the content of \emph{sentence B}  (\emph{entail}), or they contradict with each other (\emph{contradiction}), or they talk about different/unrelated things (\emph{neutral}).
+Language inference addresses the fundimental challenge of sentence semantic similarity in natural language understanding, and is one the core natural language process (NLP) tasks (detials in Section~\ref{sec:languageInference}).
 %
-In addition, many of the existing techniques study the model as an invariant object, where the model's behaviors are recorded and analyzed in an offline fashion.
+One recent advance in NLP is the introduction of attention mechanisms~\cite{VaswaniShazeerParmar2017} (see details in Section~\ref{sec:attention}).
+Intuitively, the \emph{attention} captures where in the input the model should focus on in order to produce the prediction.
+It assigns importance to individual word or a pair of word (i.e., the alignment between two sentences).
+In this work, we enhance the standard visual encoding (e.g., as a bipariate graph or as an matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification.
+% Understanding the relationship between the input and attention and the between attention and prediction is not only essentail to interpret the language inference problem, but also other NLP model utilized the same/similar mechansims.
 %
-However, the exploratory natural of the model interpretation analysis often lead to \emph{what if ...} types of questions.
-What if I perturbed the current input?
+%In the model~\cite{} we focused on, the attention can be described as an matrix where the number of row corresponds to the number of words in sentence A, and the
+%
+Despite our current implementation are geared towards the natural language inference tasks, componenets of our visualization and the overall exploration paradim can be extended to other NLP tasks, such as neural machine translation, and paragram summerization, etc.
+
+Beside explore the internal states of the model, understand how different parts of the model work together and how one may affect one another is as or if not more important.
+% Despite many advanced been made to aid in the interpration of neural network models,
+Many existing techniques study the model as an invariant object, where the model's behaviors are recorded and analyzed in an offline fashion.
+%
+However, the exploratory natural of the model interpretation analysis often lead to many \emph{what if ...} types of questions.
+I.e., what if I perturbed the current input?
 Will the prediction be stable?
@@
 What if the current prediction is wrong, how and where should we change the model parameters in order to produce the correct result?
-These type of dynamic queries form a natural way for us to gain understanding and come up with hypothesis of the model mechanisms by \emph{interrogating} what a componenet do by perturb it and then observe the effects on other part of the system.
-Therotically, we  Yet, we often need to tediously setup specialized experiment to obtain the answers.
+These type of queries form a natural way for us to gain understanding and come up with hypothesis of the model mechanisms by \emph{interrogating} how different componenets of the model will behave when other parts of system are altered.
+Therotically, we can write script for each of these questions, however, manually code up speciallized experiement is not only tedious to setup, but also ignore fact these questions are often not pre-termained.
+We often come up with new questions as we make judgements and analyzing the previous observations.
+%
+In this work, we aim to provide immediate and informative answers to these \emph{what if ...} questions by exploiting the expressive power of visualization and close yet flexible integration with the underlying model.
+Instead of viewing models as an invariant object, we approach the interpretability challenge by studying them in a dynamic setting.
+By employing a perturbation centric approach, we probe the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction.
+See Fig.~\ref{fig:modelPipeline}) affect others, which in turn provide a new perspective to look at the model interpretation problem.
 
-relationship between the input, internal states, and output prediction.
-In this work, we aim to provide quick and intuitive answers to these \emph{what if ...} questions.
-Instead of viewing the model as an invariant entitle, we employ a perturbation centric mentally to probe the model and examine how changes in one part of the pipeline affect others, which in term provide a new perspective to look at the model interpretation problem.
+The key contributions of the proposed works is summarized as the following:
+\begin{itemize}
+    \item Help understand how the model fail by examining stability of the prediction and visual summarization of predictions;
+
+    \item Enhance the visual encoding of the attention by overlaying sentence linguistic structure to allow grammar guided simplification;
+
+    \item Enable the interrogation of the relationship between input sentences, attention, and the prediction by interactively exploring how the change in one place affect other parts of the model.
+
+\end{itemize}
+%
+% In addition,
 
@@
 Neural network models are often referred to as black boxes due to the hard to recognize  difficult to interpret parameter, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships among model inputs, critical internal mechanisms, as well the output predictions.
-
-The key contributions of the proposed works is summarized as the following:
-\begin{itemize}
-    \item Identify the mistakes made by the model through perturbation of input sentences and visual summarization of the predictions;
-
-    \item Enhance the visual representation of attention by overlaying sentence linguistic structure to allow grammar guided simplification;
-
-    \item Enable the interrogation of the relationship between input sentences, attention, and the prediction by interactively exploring how the change in one of these elements affect other parts of the model.
-
-\end{itemize}

### 2018-03-22 paper/intro.tex
introduction is still lacking

--- 2018-03-21 paper/intro.tex
@@
 %
-Interpreting the internal mechanism and analyzing how predictions are made are critical to both the design and deployment of a given model.
-More importantly, the ability to pinpoint where and how an error is made and come up with hypothesis for the cause of failure is the key to identify the limitation and improve upon existing models.
+Interpreting the internal mechanism and analyzing how predictions are made are critical to both the design and deployment of a model.
+More importantly, the ability to pinpoint where and how an error is made and come up with hypotheses for the cause of failure is the key to identify the limitation and improve upon existing models.
 However, providing meaningful answers to these questions are extremely challenging and often regarded as impossible by many.
@@
 Recently, substantial research has been developed to combat the model interpretability challenge.
-Most notably, the works~\cite{} on interpretation of convolution neural network (CNN) model from both machine learning and visualization community has reveal the enormous potential and instant benefits of model interpretation, yet they also remind us how little we actually know regarding the inner mechanism of these deep neural network models.
+Most notably, the works~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018} on interpreting convolution neural network (CNN) model from both machine learning and visualization community have revealed the enormous potential and instant benefits of model interpretation, yet they also remind us how little we actually know about the inner mechanism of these deep neural networks.
 %
-Compare to image classification task, natural language processing systems have a number of innate restriction (e.g., the discrete nature of words) that makes interpreting them even more challenging.
-For example, \emph{feature visualization}~\cite{}, an often deployed technique for illustrating what kind of image feature a given part of the network (e.g., neuron, layer, or channel) captures, can not be easily generalized and applied for natural language due to the requirement of a continuous solution space (i.e., the image pixel values).
-Even though we can encode a word as an vector~\cite{}, the word embedding space is still a discretely defined space, where the interpolation between two vectors (i.e., two words) do not corresponds to explicit meaning.
+Compare to image classification task, natural language processing systems have innate restrictions (e.g., the discrete nature of words) that makes the road to interpretation more treacherous.
+For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) capture, can not be easily generalized to natural language.
+Image (pixel values) represents a continouous space, in which human can easily recognize the existance (or the absence) of patterns or shapes.
+For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, where the interpolation between two vectors (i.e., two words) do not hold clear meaning.
 %
-In this work, we introduce a visualization system specific tailor to natural language model, specifical natural language inference, in which we address many domain specific challenges.
+These restrictions call for new avenues for solving the interpretation challenges of natural language models, which motivate the proposed work.
 
-Many of the existing techniques study the model as an invariant object, where the model's behavior are recorded and analyzed in an offline fashion.
+% Beside explore the internal states of the model, understand how different parts of the model work together and how one may affect one another is as or if not more important.
+Moreover, despite many recent advances, the majority of the existing techniques study the model as an invariant object, where the model's behaviors are recorded and analyzed in an offline fashion.
 %
-However, the exploration natural of these type of analysis often lead to \emph{what if ...} types of questions.
-What if I perturbed the current input?
+However, the exploratory nature of the model interpretation analysis often leads to many \emph{what if ...} types of questions.
+Such as, what if I perturbed the current input?
 Will the prediction be stable?
-What if we change one of the key internal states of the model, how would the change affect the prediction.
-What if the current prediction is wrong, how and where should we change the model in order to produce the correct result?
-These type of dynamic queries is a natural way for us to gain understanding and come up with hypothesis of the model mechanisms by \emph{interrogating} the relationship between the input, internal states, and output prediction.
-Yet, we often need to tediously setup specialized experiment to obtain the answers.
+What if we change one of the critical internal states of the model, how would the modification affect the prediction?
+What if the current prediction is wrong, how and where should we change the model parameters to produce the correct result?
+These type of queries form a natural way to gain understanding and come up with hypotheses of the model mechanisms by \emph{interrogating} how the components of a model interact with each other in a dynamic setting.
+Theoretically, we can code up specialized experiments for each of these scenarios.
+However, such a process is not only tedious but also ignored the iterative nature of the exploratory analysis.
+Often, these questions are not pre-determined.
+Instead, new questions arise as we explore the data and analyze previous observations.
+
+In this work, we aim to provide immediate and informative answers to these \emph{what if} questions by exploiting the expressive power of visualization and flexible integration with the underlying computation model.
+Instead of viewing the model as an invariant object, we approach the interpretability challenge by studying them in a dynamic environment.
+By employing a perturbation-driven paradigm, we probe the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provide a new perspective to attack the model interpretation problem.
 %
-In this work, we aim to provide quick and intuitive answers to these \emph{what if ...} questions.
-Instead of viewing the model as an invariant entitle, we employ a perturbation centric mentally to probe the model and examine how changes in one part of the pipeline affect others, which in term provide a new perspective to look at the model interpretation problem.
+We implement our vision of the perturbation-driven system around the natural language inference problem~\cite{Parikh2016}.
+%
+However, the componenets of the visualization and the overall paradigm can be easily extended to other NLP tasks, such as neural machine translation, and paragram summerization, etc.
+%
+In the simplest form, the inference task ask the question about whether \emph{sentence A} can infer the content of \emph{sentence B} (\emph{entail}), or they contradict with each other (\emph{contradiction}), or they talk about different/unrelated things (\emph{neutral}).
+Language inference addresses the fundimental challenge of sentence semantic similarity, and is one the core natural language process (NLP) tasks (detials in Section~\ref{sec:languageInference}).
+%
+One recent advance in NLP is the introduction of attention mechanisms~\cite{VaswaniShazeerParmar2017} (see details in Section~\ref{sec:attention}).
+Intuitively, the \emph{attention} captures where in the input the model should focus on, which assigns importance to individual word or a pair of word (i.e., the alignment between words in different sentences).
+%
+There has been many speculation on how attention works in various models.
+In this work, by utilizing the the proposed system, we explore how changes in sentence input, attention, or prediction affect each other.
+Such type of exploration is not only essentail to interpret the language inference problem, but also other NLP model utilized the same/similar mechansims.
+%
+Finally, we also enhanced the standard visual encoding (e.g., as a bipariate graph or as an matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification and the ability to examine how attention corresponds to grammarical structure.
+%
+
+The key contributions of the proposed works is summarized as the following:
+\begin{itemize}
+    \item Help understand how the model fail by examining stability of the prediction and visual summarization of predictions;
+
+    \item Enhance the visual encoding of the attention by overlaying sentence linguistic structure to allow grammar guided simplification;
+
+    \item Enable the interrogation of the relationship between input sentences, attention, and the prediction by interactively exploring how the change in one place affect other parts of the model.
+
+\end{itemize}
+%
+% In addition,
 

### 2018-03-22 paper/paper_entailVis.tex
introduction is still lacking

@@
 The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms.
-%In this work, we use natural language inference task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
 In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
-%
-We use natural language inference task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.
+We use natural language inference task as an example to illustrate how this system help natural language processing (NLP) researchers assess the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypotheses on why predictions fail.
 } % end of abstract

### 2018-03-22 paper/application.tex
fix sentences refresh
add new files

@@
 \section{Put it All Together}
+
+\label{sec:caseStudy}
+
 In this section, we utilizes the perturbation based analysis
@@
 
-\subsection{What Does Attention Do?}
+\subsection{How Attention Affect the Prediction?}
 
-\subsection{Is Attention All You Need?}
+% \subsection{Is Attention All You Need?}

### 2018-03-22 paper/intro.tex
add new files

@@
 Most notably, the works~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018} on interpreting convolution neural network (CNN) model from both machine learning and visualization community have revealed the enormous potential and instant benefits of model interpretation, yet they also remind us how little we actually know about the inner mechanism of these deep neural networks.
-%
+
 Compare to image classification task, natural language processing systems have innate restrictions (e.g., the discrete nature of words) that makes the road to interpretation more treacherous.
 For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) capture, can not be easily generalized to natural language.
-Image (pixel values) represents a continouous space, in which human can easily recognize the existance (or the absence) of patterns or shapes.
+Image (pixel values) represents a continuous space, in which human can easily recognize the existence (or the absence) of patterns or shapes.
 For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, where the interpolation between two vectors (i.e., two words) do not hold clear meaning.
@@
 %
-However, the exploratory nature of the model interpretation analysis often leads to many \emph{what if ...} types of questions.
+However, the exploratory nature of the model interpretation analysis often leads to many \emph{``what if ...''} types of questions.
 Such as, what if I perturbed the current input?
@@
 
-In this work, we aim to provide immediate and informative answers to these \emph{what if} questions by exploiting the expressive power of visualization and flexible integration with the underlying computation model.
+In this work, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and direct online query of the neural network model.
 Instead of viewing the model as an invariant object, we approach the interpretability challenge by studying them in a dynamic environment.
-By employing a perturbation-driven paradigm, we probe the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provide a new perspective to attack the model interpretation problem.
+By employing a perturbation-driven paradigm, we probe the internal states of the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provide a new perspective to address the model interpretation problem.
+
+We implement our vision of the perturbation-driven paradigm in an interactive visualization system for natural language inference model~\cite{Parikh2016}.
 %
-We implement our vision of the perturbation-driven system around the natural language inference problem~\cite{Parikh2016}.
+However, the components of the visualization and the overall paradigm can be easily extended to other NLP tasks, such as neural machine translation, and text summarization, etc.
 %
-However, the componenets of the visualization and the overall paradigm can be easily extended to other NLP tasks, such as neural machine translation, and paragram summerization, etc.
-%
-In the simplest form, the inference task ask the question about whether \emph{sentence A} can infer the content of \emph{sentence B} (\emph{entail}), or they contradict with each other (\emph{contradiction}), or they talk about different/unrelated things (\emph{neutral}).
-Language inference addresses the fundimental challenge of sentence semantic similarity, and is one the core natural language process (NLP) tasks (detials in Section~\ref{sec:languageInference}).
-%
-One recent advance in NLP is the introduction of attention mechanisms~\cite{VaswaniShazeerParmar2017} (see details in Section~\ref{sec:attention}).
-Intuitively, the \emph{attention} captures where in the input the model should focus on, which assigns importance to individual word or a pair of word (i.e., the alignment between words in different sentences).
+In the simplest form, the inference task ask the question about whether \textbf{sentence A} can infer the content of \textbf{sentence B} (\emph{entail}), or they contradict with each other (\emph{contradiction}), or they talk about different/unrelated things (\emph{neutral}).
+Language inference addresses the fundamental challenge of measuring sentence semantic similarity, and is one the core natural language process (NLP) tasks (see detail in Section~\ref{sec:languageInference}).
+
+One recent advance in neural natural language process models is the introduction of attention mechanisms~\cite{VaswaniShazeerParmar2017} (see Section~\ref{sec:attention}).
+Intuitively, the \emph{attention} captures where in the input the model determine it should focus on.
+The attention often represents as weights that assigned to individual word or a pair of word (i.e., the alignment between words in different sentences).
 %
 There has been many speculation on how attention works in various models.
-In this work, by utilizing the the proposed system, we explore how changes in sentence input, attention, or prediction affect each other.
-Such type of exploration is not only essentail to interpret the language inference problem, but also other NLP model utilized the same/similar mechansims.
+In this work, by utilizing the the proposed system, we are able to perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention.
+And more importantly, we also allow user to change prediction, where we apply an constrained optimization to find the least amount of parameter update to produce the user assign label.
+Another word, the user can explore how changes in sentence input, attention, or prediction affect each other.
+Such type of exploration is not only essential to interpret the language inference problem, but can also be easily generated to other NLP model utilized the attention mechanisms.
 %
-Finally, we also enhanced the standard visual encoding (e.g., as a bipariate graph or as an matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification and the ability to examine how attention corresponds to grammarical structure.
-%
+In addition, we also enhanced the standard visual encoding (e.g., as a bipartite graph or as an matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification of the visual represent.
+Finally, as discussed in Section~\ref{sec:caseStudy}, the ability to examine how attention corresponds to grammatical structure also help domain expert speculate the potential benefit of including sentence linguistic structure in the design of attention component of the model.
 

### 2018-03-22 paper/prediction.tex
add new files

\subsection{User-Guided Prediction Update}

\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
the mira loss is $|w' - w|^2 + C * J(w')$

### 2018-03-22 paper/task.tex
add new files

\section{Task Analysis}
Effective identify and itemize the visualization tasks and the corresponding goal is the first step in designing a useful visual representation.

In this section,

### 2018-03-22 paper/background.tex
update test
update background

@@
 \section{Background}
+\label{sec:languageInference}
 
-\begin{itemize}
-    \item Motivation for : reading comprehension, similarity of sentennce
-    \item what is it?
-    \item its connection with other NLP tasks (one of the key)
-    \item
-\end{itemize}
+In order to full appreciate the technqiue discussed in this paper, certain background
+in neural network and more specifically neural natural language process models are necessary.
+In the following paragraphs, we aim to cover the most relevent backgound knowledge.
+
+\shusen{high level NLP comments}
 
@@
 
-%
+\subsection{Neural Network Primer}
+\shusen{What is the basic understanding of neural network What is the end-to-end}
 
-\subsection{Interprebilty Challenges}
-
+\subsection{Neural Network Model in NLP}
+% \subsection{Interprebilty Challenges}
 Compared with Conputer Vision, the discrete nature of words and sentences
@@
 real values much easier than interplolate between words/sentences).
-
+%
 On the other hand, a majority of recent NLP neural networks share the nature of
@@
 
-% The introduction of attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences.
-The new challenges
-
 \subsection{Natural Language Inference}
@@
 
+\shusen{What is the most standard example to illustrate NLI problem?}
+
 % \begin{itemize}

### 2018-03-22 paper/pipeline.tex
update test
update background

@@
  \caption{Language Inference Model Pipeline.}
-\label{fig:projTransition}
+\label{fig:modelPipeline}
 \end{figure}
 
-\section{Overview}
-Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.
+\section{The p-NLI System}
+In this section, we describe the p-NLI system.
+
+% Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.
 %

### 2018-03-22 paper/paper_entailVis.tex
add new files
update background
minor changs

@@
 
+\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
+
+\newcommand{\zhimin}[1]{\textcolor{magenta}{[ZHIMIN: #1]}}
+\newcommand{\shusen}[1]{\textcolor{red}{[#1]}}
+
 %% If you are submitting a paper to a conference for review with a double
@@
 \title{
-p-NLI: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
+NLIVis: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
 %Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
@@
 \input{intro.tex}
+\input{background.tex}
 \input{relatedWorks.tex}
 
-\input{background.tex}
-%\input{tasks.tex}
+\input{task.tex}
 \input{pipeline.tex}
@@
 \input{attention.tex} % how to encode the information
+\input{prediction.tex}
 

### 2018-03-22 paper/intro.tex
update paper structure

@@
 %
-In addition, we also enhanced the standard visual encoding (e.g., as a bipartite graph or as an matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification of the visual represent.
+In addition, we also enhanced the standard visual encoding (e.g., as a bipartite graph or as an matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification of the visual representation.
+%
 Finally, as discussed in Section~\ref{sec:caseStudy}, the ability to examine how attention corresponds to grammatical structure also help domain expert speculate the potential benefit of including sentence linguistic structure in the design of attention component of the model.
@@
 \begin{itemize}
+    \item Identify the visualization tasks for making sense of the role of attention in natural langage inference (section~\ref{sec:task});
+
     \item Help understand how the model fail by examining stability of the prediction and visual summarization of predictions;
@@
     \item Enable the interrogation of the relationship between input sentences, attention, and the prediction by interactively exploring how the change in one place affect other parts of the model.
-
 \end{itemize}

### 2018-03-22 paper/relatedWorks.tex
minor changs
update paper structure

--- 2018-02-22 paper/relatedWorks.tex
@@
 \section{Related Works}
+With the increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data),
+the interpretability of the machine learning model held significant implications.
+As a result, a wealth of researches have be focused on the explanation and interpretation of deep neural network models from both machine learning as well as visualization community.
 
+\noindent\textbf{Model Interpretability.}
+What consistitue interpretation for a model learning model
+% The the rising field of explainable AI
+
+~\cite{Doshi-Velez2017}
+Discussion the underspecification of what interprability means~\cite{Lipton2016}
 How to interpret classification task
-\begin{itemize}
-    \item What feature / dimension / part-of-the-input should change to
-    alter the outcome
-    \item What Examples can you provide that is similar to the current
-    instance
-\end{itemize}
-\begin{itemize}
-    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
-    Use partial dependency (varying along one feature and observer how prediction changes)
-    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)
-\end{itemize}
 
-(Limitation of the state-of-the arts)
-Model independent explanations is useful to gain intuition, but they lack the ability to link the external observation with inner states/mechanism of the model.
+Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
+%
+Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
+% (Limitation of the state-of-the arts)
+% Model independent explanations is useful to gain intuition, but they lack the ability to link the external observation with inner states/mechanism of the model.
+
+\noindent\textbf{Visual Interpration.}
+Visual analytics has demonstrate its effectiveness in the exploration of complex relationship. The application~\cite{TzengMa2005} has long been adopted for a
+~\cite{KrausePererNg2016}
+Several previous works~\cite{BilalJourablooYe2018} have dedicate to analyzing errors made in classification
 
 Depth learning vis
-\begin{itemize}
-    \item ActiVis: Visual Exploration of Industry-Scale Deep Neural Network Models
-    \item Analyzing the Training Processes of Deep Generative Models
-    \item Visual Diagnosis of Tree Boosting Methods
-    \item TreePOD: Sensitivity-Aware Selection of Pareto-Optimal Decision Trees
-    \item LSTMVis: A Tool for Visual Analysis of Hidden State Dynamics in Recurrent Neural Networks
-    \item Do Convolutional Neural Networks learn Class Hierarchy?
-    \item DeepEyes: Progressive Visual Analytics for Designing Deep Neural Networks
-\end{itemize}
+% \begin{itemize}
+%     \item ActiVis: Visual Exploration of Industry-Scale Deep Neural Network Models
+%     \item Analyzing the Training Processes of Deep Generative Models
+%     \item Visual Diagnosis of Tree Boosting Methods
+%     \item TreePOD: Sensitivity-Aware Selection of Pareto-Optimal Decision Trees
+%     \item LSTMVis: A Tool for Visual Analysis of Hidden State Dynamics in Recurrent Neural Networks
+%     \item Do Convolutional Neural Networks learn Class Hierarchy?
+%     \item DeepEyes: Progressive Visual Analytics for Designing Deep Neural Networks
+% \end{itemize}
 
-Less emphasis on where does the fail
+\noindent\textbf{Visualization of Neural Linguistic Model.}
+Compare to the multitude of researchs on making sense of convolutional neural networks, relatively less works has been dedicated to the neural linguistic model.
+%
+However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also illuminated many possibility with the application of visual analytics in understanding neural linguistic models.
+% There is many unresolve challenge and the
+The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurent neutural network.
+The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projection in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or glove~\cite{PenningtonSocherManning2014}.

### 2018-03-22 paper/task.tex
update paper structure

@@
 \section{Task Analysis}
+\label{sec:task}
 Effective identify and itemize the visualization tasks and the corresponding goal is the first step in designing a useful visual representation.

### 2018-03-22 paper/relatedWorks.tex
first version of relatedworks

@@
 \noindent\textbf{Model Interpretability.}
-What consistitue interpretation for a model learning model
-% The the rising field of explainable AI
+Before one can solve the model interpertability challenge, we first need to understand what constitute an explaination or interpretation of a machine learning model.
+As discussed in ~\cite{Lipton2016, Doshi-Velez2017}, the concept of interprebale is inherently subjective, since the recipients of the explaination are always human.
+% And the discussion of interpretability quickly become philosophical.
+However, despite the underspecification nature of the problem, we can still refine the concept and provide certain guideline~\cite{Doshi-Velez2017}.
 
-~\cite{Doshi-Velez2017}
-Discussion the underspecification of what interprability means~\cite{Lipton2016}
-How to interpret classification task
-
+One of the most studied aread in model interpretability is the explanation of a given prediction.
 Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
@@
 
-\noindent\textbf{Visual Interpration.}
-Visual analytics has demonstrate its effectiveness in the exploration of complex relationship. The application~\cite{TzengMa2005} has long been adopted for a
-~\cite{KrausePererNg2016}
-Several previous works~\cite{BilalJourablooYe2018} have dedicate to analyzing errors made in classification
+\noindent\textbf{Visual Interpration of Neural Networks.}
+The effectiveness in the exploration of complex relationships, visualization have long been adopted for interpreting neural network models (e.g., the early works such as~\cite{TzengMa2005})
+Recently, many visualization works has dedicated to the neural network model interpretability challenges.
+% The classification~\cite{KrausePererNg2016}
+In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
+Liu et al.~\cite{LiuShiCao2018} explore the possiblility of understanding the training process of deep generative models.
+The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
+The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training procss, so they can provide design guideline to the deep neutral network architect.
 
-Depth learning vis
 % \begin{itemize}
@@
 
-\noindent\textbf{Visualization of Neural Linguistic Model.}
-Compare to the multitude of researchs on making sense of convolutional neural networks, relatively less works has been dedicated to the neural linguistic model.
+\noindent\textbf{Neural Linguistic Model Visualization.}
+Compare to the multitude of researchs for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.
 %
-However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also illuminated many possibility with the application of visual analytics in understanding neural linguistic models.
+However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also revealed enoumous possibility for future applications.
 % There is many unresolve challenge and the
+The early work on charactor level recurrent network~\cite{KarpathyJohnson2015} demonstrates effectness of the hidden state in capturing the unique pattern in training text.
+The compositionality exibited in neural linguistic model (i.e., build sentence from meaing of words and phrases) are examined in the work by Li et al.
+~\cite{LiChenHovy2015}, by utilizing methods inspired by similar work in computer vision.
 The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurent neutural network.
-The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projection in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or glove~\cite{PenningtonSocherManning2014}.
+The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or glove~\cite{PenningtonSocherManning2014}.

### 2018-03-22 paper/evaluation.tex
update layout of the paper

\section{Evaluation}
\shusen{discussed feedback and comment about the proposed system}

### 2018-03-22 paper/pipeline.tex
minor changs
update layout of the paper

@@
 
-\section{The p-NLI System}
-In this section, we describe the p-NLI system.
+\section{NLIVis Design}
+In this section, we describe the design of the NLIVis system, which address the tasks described in the previous section.
+
+\shusen{overview of the system}
 
@@
 %
-Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.
+% Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.

### 2018-03-22 paper/relatedWorks.tex
update layout of the paper

@@
 Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
+
 % (Limitation of the state-of-the arts)
@@
 
-\noindent\textbf{Visual Interpration of Neural Networks.}
+\noindent\textbf{Visual Exploration of Neural Networks.}
 The effectiveness in the exploration of complex relationships, visualization have long been adopted for interpreting neural network models (e.g., the early works such as~\cite{TzengMa2005})

### 2018-03-23 src/visPackage/socketioManager.py
fix persistence value bug, need to deep copy the python object

@@ -5,6 +5,7 @@ from sets import Set
 import socketio
 import json
 import numpy as np
+import copy
 
 class socketioManager:
     def __init__(self, sio):
@@ -66,7 +67,7 @@ class socketioManager:
             self.sendToClient(uID, msg)
 
     def setData(self, name, data, uID = None):
-        self.data[name] = data
+        self.data[name] = copy.deepcopy(data)
         #propagate data update
         if name in self.data2ID.keys():
             for id in self.data2ID[name]:

### 2018-03-23 src/visPackage/static/components/pipelineComponent.js

@@ -38,133 +38,18 @@ class pipelineComponent extends baseComponent {
 
             this.defs.append("marker")
                 .attr("id", "arrow")
-                // .attr("markerUnits", "strokeWidth")
                 .attr("markerWidth", 5)
                 .attr("markerHeight", 5)
                 .attr("viewBox", "0 -5 10 10")
                 .attr("refX", 5)
                 .attr("refY", 0)
                 .attr("orient", "auto")
-                // .attr({
-                //     "id": "arrow",
-                //     "viewBox": "0 -5 10 10",
-                //     "refX": 5,
-                //     "refY": 0,
-                //     "markerWidth": 4,
-                //     "markerHeight": 4,
-                //     "orient": "auto"
-                // })
                 .append("path")
                 .attr("d", "M0,-5L10,0L0,5")
-                // .attr("class", "arrowHead")
                 .style("fill", "grey");
-
-            // this.defs.append("marker")
-            //     .attr("id", "arrow")
-            //     .attr("markerUnits", "strokeWidth")
-            //     .attr("markerWidth", "10")
-            //     .attr("markerHeight", "10")
-            //     .attr("viewBox", "0 0 10 10")
-            //     .attr("refX", "6")
-            //     .attr("refY", "6")
-            //     .attr("orient", "auto")
-            //     .append("path")
-            //     .attr("d", "M2,2 L10,6 L2,10 L6,6 L2,2")
-            //     .style("fill", "grey");
 
             //draw legend
             this.legend = this.svgContainer.append("g").attr("id", "legend");
-
-            //reset
-            this.reset = this.svgContainer.append("g");
-            this.reset.append("rect")
-                .attr("rx", 3)
-                .attr("ry", 3)
-                .attr("x", 20)
-                .attr("y", 20)
-                .attr("width", 50)
-                .attr("height", 30)
-                .attr("fill", "lightgrey")
-                .on("click", this.resetPipeline.bind(this))
-                .on("mouseover", function(d) {
-                    d3.select(this).attr("fill", "grey");
-                })
-                .on("mouseout", function(d) {
-                    d3.select(this).attr("fill", "lightgrey");
-
-                });
-            this.reset.append("text")
-                .text("reset")
-                .attr("x", 20 + 25)
-                .attr("y", 20 + 15)
-                .style("text-anchor", "middle")
-                .style("alignment-baseline", "middle")
-                .style("pointer-events", "none");
-
-            this.mode = this.svgContainer.append("g");
-            this.updateMode = [{
-                "name": "single",
[…]

### 2018-03-23 src/visPackage/static/plot/histoPlot.js

@@ -127,14 +127,18 @@ class histoPlot {
 
         // add the x Axis
         if (this.axisXflag) {
+            this.svg.select("#xAxis").remove();
             this.svg.append("g")
+                .attr("id", "xAxis")
                 .attr("transform", "translate(0," + (pos[1] + height) +
                     ")")
                 .call(d3.axisBottom(x).ticks(4));
         }
         // add the y Axis
         if (this.axisYflag) {
+            this.svg.select("#yAxis").remove();
             this.svg.append("g")
+                .attr("id", "yAxis")
                 .attr("transform", "translate(" + this.pos[0] + ",0)")
                 .call(d3.axisLeft(y).ticks(4));
         }

### 2018-03-23 src/visPackage/static/plot/pipelineItemPlot.js

@@ -120,13 +120,15 @@ class pipelineItemPlot {
                 this.hist.setHisto(this.histoList);
             }
 
-        } else {
-            this.svg.select("rect")
-                .attr("x", this.pos[0] - this.size[0] * 0.5)
-                .attr("y", this.pos[1] - this.size[1] * 0.5)
-                .attr("width", this.size[0])
-                .attr("height", this.size[1]);
         }
+        // else {
+        //     this.svg.select("rect")
+        //         .attr("x", this.pos[0] - this.size[0] * 0.5)
+        //         .attr("y", this.pos[1] - this.size[1] * 0.5)
+        //         .attr("width", this.size[0])
+        //         .attr("height", this.size[1]);
+        //     this.hist.update()
+        // }
     }
 
     getOutputPortPos() {

### 2018-03-23 src/visPackage/visModule.py

@@ -54,21 +54,18 @@ pipelineState = [{
     "index":0,
     "name": "encoder",
     "histName": "Gradient Histo",
-    # "hist": [1, 5, 6, 4, 7],
     "state": True,
     "arrow": [1]
     }, {
     "index":1,
     "name": "attention",
     "histName": "Gradient Histo",
-    # "hist": [1, 5, 6, 4, 7],
     "state": True,
     "arrow": [2]
     }, {
     "index":2,
     "name": "classifier",
     "histName": "Gradient Histo",
-    # "hist": [1, 5, 6, 4, 7],
     "state": True,
     "arrow": []
     }
@@ -129,6 +126,7 @@ class textEntailVisModule(visModule):
         dataManager.clear()
         dataManager.setData("componentLayout", layoutConfig)
         dataManager.setData("sentenceList", exampleData)
+        # print pipelineState
         dataManager.setData("pipeline", pipelineState)
         dataManager.setData("currentPair", {"sentences":[exampleData[0]['src'], exampleData[0]['targ']],"label":exampleData[0]['pred']})
         return app.send_static_file('index.html')
@@ -203,13 +201,13 @@ class textEntailVisModule(visModule):
             depTree = self.parserHook(sentence)
             return {"depTree": depTree, "sentence":sentence}
 
-    def predictUpdate(self, newLabel, iteration, encoderFlag, attFlag, classFlag ):
+    def predictUpdate(self, newLabel, iteration, learningRate, encoderFlag, attFlag, classFlag ):
         print "predictUpdate", newLabel, iteration, encoderFlag, attFlag, classFlag
         mode = dataManager.getData("updateMode")
         print " ===== predict update mode: ", mode
         if mode == "single":
             sentencePair = dataManager.getData("currentPair")['sentences']
-            att, pred = self.predictionUpdateHook(sentencePair, newLabel, iteration, encoderFlag, attFlag, classFlag)
+            att, pred = self.predictionUpdateHook(sentencePair, newLabel, iteration, learningRate, encoderFlag, attFlag, classFlag)
             # print att, pred
 
             dataManager.setData("attention", att)

### 2018-03-23 paper/task.tex
update tasks

@@
 \label{sec:task}
-Effective identify and itemize the visualization tasks and the corresponding goal is the first step in designing a useful visual representation.
+Identify the analysis goals and distill the corresponding visualization tasks is the first yet significant step in designing a useful tool.
+In this section, we examine how domain experts approach the challenge of analyzing a new model and assess its strength and weakness.
+Then, we reify the observations into a common paradigm and identify where and how a visualization tool could help experts intrepret the model and development intuitve, more importantly, how such augmentation fit into the domain experts' though process and workflow.
+
+During our long-term colloration with two domain experts in NLP, we have conducted extensive interview and discussion on the common approach researchers employ to interpret the behavior and obtain intuition for a new model.
+%
+Often, the most important metric for evaluating a model is the prediction accuracy.
+However, most researchers would agree, the accuracy alone does not provide the full picture.
+The model could perform much worse on a different test set.
+The model may prodcue many correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that does not exist in real word senarios).
+%
+As a result, NLP researchers often employ a set of tests, which are driven by their domain knowledge and hypotheses based on the archtecture, to assess the model.
+%
+A stereotypical senario can be summarized as the follow.
+%
+To assess a model for a specific NLP task, the research start the analysis from looking at the failure cases.
+
+\shusen{What is the paradigm?}
+Look at example, perturb the example, see how the perturb the one fails,
+
+learn the limtation and strength from the where and how the errors occurs. iterate
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{errorAnalysis}
+ \caption{How domain experts carry out error analysis on the model.}
+\label{fig:modelPipeline}
+\end{figure}
 

### 2018-03-23 src/visPackage/static/plot/sliderPlot.js

@@ -1,0 +1,20 @@
+class sliderPlot {
+    constructor(svg, pos, size) {
+        this.svg = svg.append("g");
+        this.pos = pos;
+        this.size = size;
+    }
+
+    draw() {
+
+        //draw background quad
+        this.svg.append("rect");
+
+        //draw for ground quad
+        this.svg.append("rect");
+
+        this.svg.append('text');
+
+    }
+
+}

### 2018-03-23 paper/background.tex
update background
update paper structure
add figure for end2end
update intro

@@
 \section{Background}
-\label{sec:languageInference}
 
@@
 
-\subsection{Neural Network Primer}
+% \subsection{Neural Network Primer}
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{end2end}
+ \caption{End-to-end attention based model.}
+\label{fig:modelPipeline}
+\end{figure}
+
+\subsection{Neural Network Model in NLP}
+
+\shusen{neural linguistic models?}
+
 \shusen{What is the basic understanding of neural network What is the end-to-end}
 
-\subsection{Neural Network Model in NLP}
 % \subsection{Interprebilty Challenges}
@@
 
+\subsection{Attention Mechansim}
+\label{sec:attention}
 The introduction of attention mechanism~\cite{bahdanau2014neural} allows
@@
 \subsection{Natural Language Inference}
+\label{sec:languageInference}
 Natural Language Inference(cite?) is an important machine understanding task in NLP.

### 2018-03-23 paper/task.tex
update intro

--- 2018-03-22 paper/task.tex
@@
 \label{sec:task}
-Effective identify and itemize the visualization tasks and the corresponding goal is the first step in designing a useful visual representation.
+Identify the analysis goals and distill the corresponding visualization tasks is the first yet significant step in designing a useful tool.
+In this section, we examine how domain experts approach the challenge of analyzing a new model and assess its strength and weakness.
+Then, we reify the observations into a common paradigm and identify where and how a visualization tool could help experts interpret the model and development intuitive, more importantly, how the proposed fit into the domain experts' though process and workflow.
+
+During our long-term collaboration with two domain experts in NLP, we have conducted extensive interview and discussion on the common approach researchers employ to interpret the behavior and obtain intuition for a new model.
+%
+Often, the most important metric for evaluating a model is the prediction accuracy.
+However, most researchers would agree, the accuracy alone does not provide the full picture.
+The model could perform much worse on a different test set.
+The model may produce many correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that does not exist in real word scenarios).
+%
+As a result, NLP researchers often employ a set of tests, which are driven by their domain knowledge and hypotheses based on the architecture, to assess the model.
+%
+A stereotypical scenario can be summarized as the follow.
+%
+To assess a model for a specific NLP task, the research start the analysis by looking at the failure cases.
+
+\shusen{What is the paradigm?}
+Look at example, perturb the example, see how the perturb the one fails,
+
+learn the limitation and strength from the where and how the errors occurs. iterate
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{errorAnalysis}
+ \caption{How domain experts carry out error analysis on the model.}
+\label{fig:modelPipeline}
+\end{figure}
 

### 2018-03-23 paper/intro.tex

--- 2018-03-22 paper/intro.tex
@@
 More importantly, the ability to pinpoint where and how an error is made and come up with hypotheses for the cause of failure is the key to identify the limitation and improve upon existing models.
-However, providing meaningful answers to these questions are extremely challenging and often regarded as impossible by many.
+However, providing meaningful answers to these questions are incredibly challenging and often regarded as impossible by many.
 
-Recently, substantial research has been developed to combat the model interpretability challenge.
-Most notably, the works~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018} on interpreting convolution neural network (CNN) model from both machine learning and visualization community have revealed the enormous potential and instant benefits of model interpretation, yet they also remind us how little we actually know about the inner mechanism of these deep neural networks.
-%
-Compare to image classification task, natural language processing systems have innate restrictions (e.g., the discrete nature of words) that makes the road to interpretation more treacherous.
-For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) capture, can not be easily generalized to natural language.
-Image (pixel values) represents a continouous space, in which human can easily recognize the existance (or the absence) of patterns or shapes.
-For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, where the interpolation between two vectors (i.e., two words) do not hold clear meaning.
+Recently, sizable research has been developed to combat the model interpretability challenges.
+Most notably, the works~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018} on interpreting convolution neural network (CNN) model from both machine learning and visualization community have revealed the enormous potential and immediate benefits of model interpretation.
+At the same time, these works also remind us how little we truly understand about the inner mechanism of these deep neural networks.
+
+Compare to image classification task, natural language processing (NLP) systems have innate restrictions (e.g., the discrete nature of words) that makes the road to interpretation more treacherous.
+For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) capture, can not be readily generalized to natural language.
+Image (pixel values) represents a continuous solution space, in which human can quickly recognize the existence (or the absence) of patterns or shapes.
+For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) do not hold clear meaning.
 %
@@
 %
-However, the exploratory nature of the model interpretation analysis often leads to many \emph{what if ...} types of questions.
-Such as, what if I perturbed the current input?
+However, the exploratory nature of the model interpretation analysis often leads to many \emph{``what if ...''} type of questions.
+Such as, what if we perturbed the current input?
 Will the prediction be stable?
 What if we change one of the critical internal states of the model, how would the modification affect the prediction?
-What if the current prediction is wrong, how and where should we change the model parameters to produce the correct result?
+What if the current prediction is wrong, how and where could we apply minimal change to the model to produce the correct result?
+And how would it affect the internal state we care about?
 These type of queries form a natural way to gain understanding and come up with hypotheses of the model mechanisms by \emph{interrogating} how the components of a model interact with each other in a dynamic setting.
-Theoretically, we can code up specialized experiments for each of these scenarios.
-However, such a process is not only tedious but also ignored the iterative nature of the exploratory analysis.
+Hypothetically, we can code up specialized experiments for each of these scenarios.
+However, such a process is not only tedious but also ignores the iterative nature of the exploratory analysis.
 Often, these questions are not pre-determined.
-Instead, new questions arise as we explore the data and analyze previous observations.
+Instead, new exploration paths arise as we investigate and analyze previous observations.
 
-In this work, we aim to provide immediate and informative answers to these \emph{what if} questions by exploiting the expressive power of visualization and flexible integration with the underlying computation model.
+In this work, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and direct online query/optimization of the neural network model.
 Instead of viewing the model as an invariant object, we approach the interpretability challenge by studying them in a dynamic environment.
-By employing a perturbation-driven paradigm, we probe the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provide a new perspective to attack the model interpretation problem.
+By employing a perturbation-driven paradigm, we probe the internal states of the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provides a new perspective to address the model interpretation problem.
+
+We implement our vision of the perturbation-driven exploration in an interactive visualization system for natural language inference models~\cite{Parikh2016}.
+However, the components of the visualization and the overall paradigm can be readily extended to other NLP tasks, such as neural machine translation, and text summarization, etc.
 %
-We implement our vision of the perturbation-driven system around the natural language inference problem~\cite{Parikh2016}.
+In the simplest form, the inference task ask the question about whether if we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), or are they contradict with each other (\emph{contradiction}), or are they talk about different/unrelated things (\emph{neutral}).
+Language inference addresses the fundamental challenge of measuring sentences' semantic similarity, and is one the core natural language processing tasks (see detail in Section~\ref{sec:languageInference}).
+
+One recent advance in neural natural language process models is the introduction of attention mechanisms~\cite{VaswaniShazeerParmar2017} (Section~\ref{sec:attention}).
+Intuitively, the \emph{attention} help capture which part of the input the model deemed more important for making the right prediction.
+The attention is often represented as weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
 %
-However, the componenets of the visualization and the overall paradigm can be easily extended to other NLP tasks, such as neural machine translation, and paragram summerization, etc.
+%\shusen{seems repeated some of the previous points}
+There have been many speculations on how attention works in various models.
+By utilizing the proposed tool, the domain experts study how changes in sentence input, attention, or prediction affect each other, which help them develop deeper intuitive and alternative hypotheses.
+%we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention.
+And more importantly, we also allow the user to change prediction, where we apply a constrained optimization to find the least amount of parameter update to produce the user assign label.
+%Another word, 
+%Such type of exploration is not only essential to interpret the language inference problem, but can also be generalized to other NLP model utilized the attention mechanisms.
+Moreover, we enhanced the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification of the visual representation.
 %
-In the simplest form, the inference task ask the question about whether \emph{sentence A} can infer the content of \emph{sentence B} (\emph{entail}), or they contradict with each other (\emph{contradiction}), or they talk about different/unrelated things (\emph{neutral}).
-Language inference addresses the fundimental challenge of sentence semantic similarity, and is one the core natural language process (NLP) tasks (detials in Section~\ref{sec:languageInference}).
-%
-One recent advance in NLP is the introduction of attention mechanisms~\cite{VaswaniShazeerParmar2017} (see details in Section~\ref{sec:attention}).
-Intuitively, the \emph{attention} captures where in the input the model should focus on, which assigns importance to individual word or a pair of word (i.e., the alignment between words in different sentences).
-%
-There has been many speculation on how attention works in various models.
-In this work, by utilizing the the proposed system, we explore how changes in sentence input, attention, or prediction affect each other.
-Such type of exploration is not only essentail to interpret the language inference problem, but also other NLP model utilized the same/similar mechansims.
-%
-Finally, we also enhanced the standard visual encoding (e.g., as a bipariate graph or as an matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification and the ability to examine how attention corresponds to grammarical structure.
-%
+Finally, as discussed in Section~\ref{sec:caseStudy}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate the potential benefit of including the linguistic structure in the design of attention component of the model.
 
-The key contributions of the proposed works is summarized as the following:
+In summary, the key contributions of the proposed works is the following:
 \begin{itemize}
-    \item Help understand how the model fail by examining stability of the prediction and visual summarization of predictions;
+  % \item Distill the visualization tasks for making sense of the role of attention in natural language inference (section~\ref{sec:task});
+    \item Introduce the perturbation-driven exploration paradigm for exploring natural language processing models;
+
+    \item Perform error analysis by examining stability of the predictions under perturbation;
 
@@
 
-    \item Enable the interrogation of the relationship between input sentences, attention, and the prediction by interactively exploring how the change in one place affect other parts of the model.
-
+    \item Enable the interrogation of the relationship between input sentences, model internals, and the prediction by interactively exploring how the change in one place affect other parts of the model.
 \end{itemize}

### 2018-03-23 paper/paper_entailVis.tex
update paper structure
update layout of the paper
fix persistence value bug, need to deep copy the python object

@@
 \title{
-NLIVis: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
+NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
 %Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
@@
 \abstract{
-With the recent advances in deep learning, neural network based models have obtained the state-of-the-art performance for many linguistic tasks in natural language processing.
+With the recent advances in deep learning, neural network based models have obtained state-of-the-art performances for many linguistic tasks in natural language processing.
 The disruptive progress also brings enormous challenges.
 The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms.
-In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
-We use natural language inference task as an example to illustrate how this system help natural language processing (NLP) researchers assess the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypotheses on why predictions fail.
+In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
+We use natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states and interpreting and hypothesizing the fundamental model mechanism such as attention.
 } % end of abstract
@@
 %% please capitalize first letter and insert punctuation after last keyword
-\keywords{Natural Language Processing, Interpretable Machine Learning,
-Visual Analytics}
+\keywords{Natural Language Processing, Interpretable Machine Learning, Natural Language Inference, Attention Visualization}
 
@@
 \input{perturbation.tex} % how to do the perturbation
+\input{sentence.tex}
 \input{attention.tex} % how to encode the information
@@
 \input{application.tex}
-%%%%%%%%%%%%% identify errors %%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%% interpret attention %%%%%%%%%%%%%%%%%%%
 
+\input{evaluation.tex}
 \input{discussion.tex} % how to encode the information

### 2018-03-23 paper/intro.tex
minor correction to intro

@@
 We implement our vision of the perturbation-driven exploration in an interactive visualization system for natural language inference models~\cite{Parikh2016}.
-However, the components of the visualization and the overall paradigm can be readily extended to other NLP tasks, such as neural machine translation, and text summarization, etc.
+However, the components of the visualization and the overall paradigm can be readily extended to other NLP tasks, such as question and answer, and text summarization, etc.
 %
-In the simplest form, the inference task ask the question about whether if we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), or are they contradict with each other (\emph{contradiction}), or are they talk about different/unrelated things (\emph{neutral}).
-Language inference addresses the fundamental challenge of measuring sentences' semantic similarity, and is one the core natural language processing tasks (see detail in Section~\ref{sec:languageInference}).
+In the simplest form, the inference task asks the question about whether if we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), or are they contradict with each other (\emph{contradiction}), or are they talk about different/unrelated things (\emph{neutral}).
+Language inference addresses the fundamental challenge of measuring sentences' semantic similarity, and is one the core NLP tasks (see detail in Section~\ref{sec:languageInference}).
 
-One recent advance in neural natural language process models is the introduction of attention mechanisms~\cite{VaswaniShazeerParmar2017} (Section~\ref{sec:attention}).
-Intuitively, the \emph{attention} help capture which part of the input the model deemed more important for making the right prediction.
+One recent advance in neural natural language process models is the introduction of \emph{attention mechanisms}~\cite{VaswaniShazeerParmar2017} (Section~\ref{sec:attention}).
+Intuitively, the attention helps capture which part of the input the model deemed more important for making a prediction.
 The attention is often represented as weights for individual words or pairs of words (i.e., the alignment between words in different sentences).

### 2018-03-24 paper/background.tex
update background

@@
 \section{Background}
+The target audiences of the proposed tool is domain experts who develop learning model for natural language processing tasks.
+Therefore, certain domain specific background knowledge is required to fully understand and appreciate the technique discussed in this paper.
+In this section, we first explain the natural language inference (NLI) task and how it fit into the grand challenges in NLP.
+Then, we examine the common architecture characteristics shared by many state-of-the-art neural linguistic models.
+Finally, we discuss the role the attention plays in the model and why attention is closely tided to model interpretability.
 
-In order to full appreciate the technqiue discussed in this paper, certain background
-in neural network and more specifically neural natural language process models are necessary.
-In the following paragraphs, we aim to cover the most relevent backgound knowledge.
+\subsection{Natural Language Inference}
+\label{sec:languageInference}
+Natural Language Inference~\cite{MacCartney2009} is an important machine understanding task in NLP.
+The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence.
 
+\begin{center}
+ \begin{tabular}{c | c c c c} 
+ \hline
+  & sentences & entail & contradict  & neutral \\ [0.5ex] 
+ \hline
+ premise & Jim ate an apple. &  -  &  -  & - \\ 
+ hypothesis & Jim ate fruits. & \checkmark &   &  \\
+ hypothesis & Jim ate an banana. &  & \checkmark & \\
+ hypothesis & Tom ate an apple &  &  & \checkmark \\
+ hypothesis & Jim ate a Fuji apple. &   &  & \checkmark? \\
+ \hline
+\end{tabular}
+\end{center}
+\shusen{What is the most standard example to illustrate NLI problem?}
 \shusen{high level NLP comments}
+
+The prediction must fall in one of three categories: $\{Entailment, Contradiction, Neutral\}$.
+$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
+$Contradiction$ means the textual of hypothesis opposes that of premise;
+and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.
+%
+Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
+the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.
 
@@
 \subsection{Neural Network Model in NLP}
-
 \shusen{neural linguistic models?}
@@
 
-\subsection{Natural Language Inference}
-\label{sec:languageInference}
-Natural Language Inference(cite?) is an important machine understanding task in NLP.
-The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence.
-The prediction must fall in one of three catergories: $\{Entailment, Contradiction, Neutral\}$.
-$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
-$Contradiction$ means the textuals of hypothesis opposes that of premise;
-and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.
-
-Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
-the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.
-
-% showing an example??
-
-\shusen{What is the most standard example to illustrate NLI problem?}
-
 % \begin{itemize}

### 2018-03-24 paper/relatedWorks.tex
update background

@@
 One of the most studied aread in model interpretability is the explanation of a given prediction.
-Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
+Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simpler linear model near the prediction of interests).
 %

### 2018-03-24 paper/background.tex
add figure
add simple example

@@
 \label{sec:languageInference}
-Natural Language Inference~\cite{MacCartney2009} is an important machine understanding task in NLP.
-The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence.
+Natural Language Inference~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
+The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence. A simple example is illustrated in Table.~\ref{table:NLI}.
 
-\begin{center}
+\begin{table}[htbp]
+\label{table:NLI}
+\centering
+\caption{An illustration of natural language inference.}
  \begin{tabular}{c | c c c c} 
@@
  premise & Jim ate an apple. &  -  &  -  & - \\ 
+ hypothesis & Jim ate a Fuji apple. &   &  & \checkmark \\
  hypothesis & Jim ate fruits. & \checkmark &   &  \\
@@
  hypothesis & Tom ate an apple &  &  & \checkmark \\
- hypothesis & Jim ate a Fuji apple. &   &  & \checkmark? \\
+ %\hline
+ %premise & Facebook's IPO electrified the general public. &  -  &  -  & - \\ 
+ %hypothesis & Facebook went public. & \checkmark   &  &  \\
+ %hypothesis & General Electric went public. &  &   & \checkmark \\
+ %hypothesis & People ignored Facebook's IPO. &  & \checkmark & \\
+
  \hline
 \end{tabular}
-\end{center}
-\shusen{What is the most standard example to illustrate NLI problem?}
-\shusen{high level NLP comments}
+\end{table}
+
+However, in the real word the task can be quick challenge especially for learning algorithm.
+Take the following sentences are an example:  (P) Facebook's IPO electrified the general public.
+(H1) Facebook went public.
+(H2) General Electric went public.
+(H3) People ignored Facebook's IPO.
 

### 2018-03-24 paper/background.tex
add attention figure

@@
 In this section, we first explain the natural language inference (NLI) task and how it fit into the grand challenges in NLP.
-Then, we examine the common architecture characteristics shared by many state-of-the-art neural linguistic models.
+Then, we examine the common architecture characteristics shared by many state-of-the-art neural network models.
 Finally, we discuss the role the attention plays in the model and why attention is closely tided to model interpretability.
@@
 Natural Language Inference~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
-The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence. A simple example is illustrated in Table.~\ref{table:NLI}.
+The problem definition is to classify the relationship between a premise (\textbf{P}) sentence and a hypothesis (\textbf{H}) sentence. 
+The prediction must fall in one of three categories: $\{Entailment, Contradiction, Neutral\}$.
+$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
+$Contradiction$ means the textual of hypothesis opposes that of premise;
+and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.
+A simple example is illustrated in Table.~\ref{table:NLI}.
 
@@
  \hline
-  & sentences & entail & contradict  & neutral \\ [0.5ex] 
+  P / H & sentences & entail & contradict  & neutral \\ [0.5ex] 
  \hline
@@
 
-However, in the real word the task can be quick challenge especially for learning algorithm.
-Take the following sentences are an example:  (P) Facebook's IPO electrified the general public.
-(H1) Facebook went public.
-(H2) General Electric went public.
-(H3) People ignored Facebook's IPO.
+However, in real word, the task can be quite challenging, especially for learning algorithms.
+Take the following sentences as an example (here \textbf{P} refer to premise, \textbf{H} refer to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public.
+(\textbf{H1}) Facebook went public.
+(\textbf{H2}) General Electric went public.
+(\textbf{H3}) People ignored Facebook's IPO.
+The literal semantic similarity between ``Electric'' and ``electrified'' will like trick the model to predict \textbf{H2} as \emph{entailment}.
+The model likely will also not be able to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
 
-The prediction must fall in one of three categories: $\{Entailment, Contradiction, Neutral\}$.
-$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
-$Contradiction$ means the textual of hypothesis opposes that of premise;
-and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.
-%
-Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
-the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.
-
+\shusen{How does the NLI related to the other challenges in NLP}
 The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
@@
 Recently, neural networks models have performed strongly on these tasks.
-
+%
 Therefore, making sense and explaining predictions made by deep neural networks is not only
@@
 and model fairness (e.g., is the prediction affected by the bias in the training data).
+%
+Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
+the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.
 
@@
 
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=0.9\linewidth]{attentionIllustration}
+ \caption{Attention illustrate. The soft alignment between two sentences.}
+\label{fig:attention}
+\end{figure}
+
 % \begin{itemize}

### 2018-03-24 paper/background.tex
clarify NLI

--- 2018-03-24 paper/background.tex
@@
 \section{Background}
-The target audiences of the proposed tool is domain experts who develop learning model for natural language processing tasks.
+The target audiences of the proposed tool is domain experts who develop NLP models.
 Therefore, certain domain specific background knowledge is required to fully understand and appreciate the technique discussed in this paper.
 In this section, we first explain the natural language inference (NLI) task and how it fit into the grand challenges in NLP.
-Then, we examine the common architecture characteristics shared by many state-of-the-art neural linguistic models.
+Then, we examine the common architecture characteristics shared by many state-of-the-art neural network models.
 Finally, we discuss the role the attention plays in the model and why attention is closely tided to model interpretability.
@@
 Natural Language Inference~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
-The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence. A simple example is illustrated in Table.~\ref{table:NLI}.
+The goal of natural language inference is to classify the relationship between a premise (\textbf{P}) sentence and a hypothesis (\textbf{H}) sentence. 
+The prediction fall in one of three categories: \emph{entailment}, \emph{contradiction}, \emph{neutral}.
+A simple example is shown in Table.~\ref{table:NLI}.
+In this case, the premise is ``Jim ate an apple''. 
+The hypothesis statement ``Jim ate fruits.'' can be concluded from the premise.
+Therefore, the relationship between premise and hypothesis is \emph{entailment}.
+However, we should note such a relationship is not necessarily reversible.
+Since the concept ``fruits'' is less restrictive than ``apple'', we can not conclude ``Jim ate an apple'' from the statement ``Jim ate fruits''.
+The same logic applies to ``Jim ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
+%\emph{Contradiction} means the textual of hypothesis opposes that of premise;
+%and \emph{Neutral} implies no conclusion can be made on either \emph{Entailment} or \emph{Contradiction}.
 
@@
  \hline
-  & sentences & entail & contradict  & neutral \\ [0.5ex] 
+  P / H & sentences & entail & contradict & neutral \\ [0.5ex] 
  \hline
  premise & Jim ate an apple. &  -  &  -  & - \\ 
- hypothesis & Jim ate a Fuji apple. &   &  & \checkmark \\
  hypothesis & Jim ate fruits. & \checkmark &   &  \\
@@
  hypothesis & Tom ate an apple &  &  & \checkmark \\
+ hypothesis & Jim ate a Fuji apple. &   &  & \checkmark \\
  %\hline
@@
 
-However, in the real word the task can be quick challenge especially for learning algorithm.
-Take the following sentences are an example:  (P) Facebook's IPO electrified the general public.
-(H1) Facebook went public.
-(H2) General Electric went public.
-(H3) People ignored Facebook's IPO.
+The inference task can be quite challenging, considering the ambiguousness of natural language (especially from learning algorithm's point of view).
+Take the following sentences as an example (here \textbf{P} refer to premise, \textbf{H} refer to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
+The literal semantic similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}.
+The model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
 
-The prediction must fall in one of three categories: $\{Entailment, Contradiction, Neutral\}$.
-$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
-$Contradiction$ means the textual of hypothesis opposes that of premise;
-and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.
-%
-Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
-the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.
-
+%\shusen{How does the NLI related to the other challenges in NLP}
 The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
@@
 Recently, neural networks models have performed strongly on these tasks.
-
-Therefore, making sense and explaining predictions made by deep neural networks is not only
-essential for validating and improving the model, but also becoming a necessity with
-increasing demands for model accountability (e.g., what is the evidence for making the decision)
-and model fairness (e.g., is the prediction affected by the bias in the training data).
+%
+Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
+the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.
 

### 2018-03-24 paper/background.tex
update background

@@
 
-The inference task can be quite challenging, considering the ambiguousness of natural language (especially from learning algorithm's point of view).
+Considering the ambiguousness  of natural language and polysemy words, the inference task can be quite challenging (especially from learning algorithm's point of view).
 Take the following sentences as an example (here \textbf{P} refer to premise, \textbf{H} refer to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
@@
 The model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
-
-%\shusen{How does the NLI related to the other challenges in NLP}
-The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
-deep comprehension of textual information. Major tasks include Natural Language Inference,
-Machine Translation, Questions Answering, Summarization, and etc.
-Recently, neural networks models have performed strongly on these tasks.
 %
-Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
-the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.
+At a first glance, the task of natural language inference may seem less practical compared to other common NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
+%The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
+%deep comprehension of textual information. Major tasks include Natural Language Inference,
+%Machine Translation, Questions Answering, Summarization, and etc.
+%Recently, neural networks models have performed strongly on these tasks.
+%
+Recently, Bowman et al.
+introduce a large corpus~\cite{BowmanAngeliPotts2015} for the NLI task, which helps spawn a new wave of effective neural network based models.
+In this work, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.
 
@@
 \subsection{Neural Network Model in NLP}
-\shusen{neural linguistic models?}
-
-\shusen{What is the basic understanding of neural network What is the end-to-end}
-
-% \subsection{Interprebilty Challenges}
-Compared with Conputer Vision, the discrete nature of words and sentences
-presents additional challenge for
-interpreting the model, since many visualization technique often employed
-for images rely on continuous nature of the input space (e.g., one can interpolate
-real values much easier than interplolate between words/sentences).
+%\shusen{neural linguistic models?}
+%\shusen{What is the basic understanding of neural network What is the end-to-end}
+There are many connection and distinction between neural network model employed for vision tasks and NLP tasks.
+On the one hand, as discussed in the introduction, the discrete nature of words and sentences presents additional challenge for
+interpreting the NLP model.
 %
@@
 vectorized input and yields final prediction for a specific task.
-Therefore, to study the inside of end-to-end neural models, it is important to
+Therefore, to make sense of how predictions are made inside of end-to-end neural models, it is important to
 explore the interaction between intermediate representations and predictions.
 
-\subsection{Attention Mechansim}
+Many of the recent NLP end-to-end neural network models, despite having potentially drastic different network architecture, share a similar high-level design that consist of three distinct stages (encode, attent/align, classify, see Fig.~\ref{fig:modelPipeline}).
+These models usually take pre-trained word vectors (a numerical vector representation of individual words, where the semantic similarities are encode by distances in the high-dimensional space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, the
+
+\subsection{Attention Mechanism}
 \label{sec:attention}

### 2018-03-24 paper/background.tex
update attent discussion

@@
 %
-At a first glance, the task of natural language inference may seem less practical compared to other common NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
+At the first glance, the task of natural language inference may seem less practical compared to other common NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
 %The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
@@
 Recently, Bowman et al.
-introduce a large corpus~\cite{BowmanAngeliPotts2015} for the NLI task, which helps spawn a new wave of effective neural network based models.
+introduce a large corpus~\cite{BowmanAngeliPotts2015} for the NLI task, which helps spawn a new wave of effective neural network based NLI models.
 In this work, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.
@@
 
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{end2end}
- \caption{End-to-end attention based model.}
-\label{fig:modelPipeline}
-\end{figure}
-
 \subsection{Neural Network Model in NLP}
-%\shusen{neural linguistic models?}
 %\shusen{What is the basic understanding of neural network What is the end-to-end}
@@
 vectorized input and yields final prediction for a specific task.
-Therefore, to make sense of how predictions are made inside of end-to-end neural models, it is important to
-explore the interaction between intermediate representations and predictions.
 
-Many of the recent NLP end-to-end neural network models, despite having potentially drastic different network architecture, share a similar high-level design that consist of three distinct stages (encode, attent/align, classify, see Fig.~\ref{fig:modelPipeline}).
-These models usually take pre-trained word vectors (a numerical vector representation of individual words, where the semantic similarities are encode by distances in the high-dimensional space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, the
+\begin{figure}[htbp]
+\centering
+ \includegraphics[width=1.0\linewidth]{end2end}
+ \vspace{-2mm}
+ \caption{End-to-end NLP neural network model.}
+  \vspace{-2mm}
+\label{fig:modelPipeline}
+\end{figure}
+
+Many of the recent NLP end-to-end neural network models, despite having potentially drastic different network architectures, share a similar high-level design that consist of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
+%
+The existence of the similar structures mean the proposed tool, which designed for NLI task, can be generalized for a much broader set of applications.
+
+These end-to-end models usually take pre-trained word vectors (numerical vector representation of individual words, in which the semantic similarities are encode by distances in the high-dimensional vector space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, and then in the encode stage pre-trained vectors are adjusted to the specialized task at hand.
+Subsequently, the next stage aim at finding alignment between words in the input sequence.
+For task like NLI, this means finding the corresponds between words from premise sentence to hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
+Finally, in the last stage the alignment information and the encoded vector representations are aggregated and then used as features for a classification network (last part of the end-to-end neural network).
+%
+Since, all these three stages of the model are train jointly in an end-to-end fashion, therefore, to make sense of how predictions are made inside such a models, it is important to explore the interaction between intermediate representations and predictions.
 
@@
 \label{sec:attention}
+Among the three stages, the second stage often constitutes the most crucial part of the model as it determines where the classifier will focus on for generating a prediction.
+The operation to compute the alignment between words in the input is refer to as the attention mechanism.
 The introduction of attention mechanism~\cite{bahdanau2014neural} allows
-pairwise interaction between hidden states. This interaction can be naturally explained
-as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
-Recently attention has contributed to many strongly-performed NLP models
+pairwise interaction between internal representation of words (\shusen{the original text is hidden states, isn't the pairwise interaction between the representation of words, are the hidden states refer to that?}).
+This interaction can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
+%
+%As the only interpretable part of the internal state of the network, understanding how attention information 
+Recently, attention has contributed to many strongly-performed NLP models
 ~\cite{parikh2016emnlp},~\cite{rush2015neural},~\cite{yang2016hierarchical},
 ~\cite{seo2016bidirectional},~\cite{schwartz2017high}.
-We will focus on its application in Natural Language Inference task as proposed in~\cite{parikh2016emnlp}.
-However notice that our visualization can be generalized to other attention models as well.
 

### 2018-03-24 paper/background.tex
add ground truth

@@
 Among the three stages, the second stage often constitutes the most crucial part of the model as it determines where the classifier will focus on for generating a prediction.
-The operation to compute the alignment between words in the input is refer to as the attention mechanism.
+The operation to compute the alignment between words in the input is referred to as the attention mechanism.
 The introduction of attention mechanism~\cite{bahdanau2014neural} allows
@@
  \includegraphics[width=0.9\linewidth]{attentionIllustration}
- \caption{Attention illustrate. The soft alignment between two sentences.}
+ \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
+On the left, the matrix shows the soft alignment between between premise and hypothesis pair.}
 \label{fig:attention}
 \end{figure}
+
+For natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft aligned between words in premise and the words in the hypothesis.
+As we can see in this example, the higher values indicate better alignment between words.
+The subject, verb, and object between these two sentence are aligned correctly.
+More importantly, the difference between the subject words does not affect their alignment.
+The classification stage can then utilize the attention information to determine the subject of the sentence are different, therefore, despite the other part of the sentences are the same, the relationship between premise and hypothesis should be neutral.
 

### 2018-03-24 paper/background.tex
update background

--- 2018-03-24 paper/background.tex
@@
 \section{Background}
-The target audiences of the proposed tool is domain experts who develop NLP models.
-Therefore, certain domain specific background knowledge is required to fully understand and appreciate the technique discussed in this paper.
-In this section, we first explain the natural language inference (NLI) task and how it fit into the grand challenges in NLP.
+The target audiences of the proposed tool are domain experts who analyze and develop NLP models.
+Therefore, certain background knowledge in NLP is required to fully understand and appreciate the technique discussed in this paper.
+In this section, we first explain the definition of natural language inference (NLI) task and how it fits into the grand challenges in NLP.
 Then, we examine the common architecture characteristics shared by many state-of-the-art neural network models.
-Finally, we discuss the role the attention plays in the model and why attention is closely tided to model interpretability.
+Finally, we discuss the role the attention plays in the model and why attention is closely tied to model interpretability.
 
@@
 \label{sec:languageInference}
-Natural Language Inference~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
-The goal of natural language inference is to classify the relationship between a premise (\textbf{P}) sentence and a hypothesis (\textbf{H}) sentence. 
-The prediction fall in one of three categories: \emph{entailment}, \emph{contradiction}, \emph{neutral}.
+Natural Language Inference (NLI)~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
+The goal of NLI is to predict the relationship between a premise (\textbf{P}) sentence and a hypothesis (\textbf{H}) sentence. 
+The prediction fall in one of three categories: \emph{entailment} (\textbf{E}), \emph{contradiction} (\textbf{C}), \emph{neutral} (\textbf{N}).
 A simple example is shown in Table.~\ref{table:NLI}.
@@
 Therefore, the relationship between premise and hypothesis is \emph{entailment}.
-However, we should note such a relationship is not necessarily reversible.
-Since the concept ``fruits'' is less restrictive than ``apple'', we can not conclude ``Jim ate an apple'' from the statement ``Jim ate fruits''.
-The same logic applies to ``Jim ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
+However, we should note that such a relationship is not necessarily reversible.
+Since the concept ``fruits'' is less restrictive than that of ``apple'', we can not conclude ``Jim ate an apple'' from the statement ``Jim ate fruits''.
+The same logic applies to the hypothesis of ``Jim ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
 %\emph{Contradiction} means the textual of hypothesis opposes that of premise;
@@
  %hypothesis & People ignored Facebook's IPO. &  & \checkmark & \\
-
  \hline
@@
 
-Considering the ambiguousness  of natural language and polysemy words, the inference task can be quite challenging (especially from learning algorithm's point of view).
+At the first glance, the task of natural language inference may seem less practical compared to other common NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
+%
+Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from learning algorithm's point of view).
 Take the following sentences as an example (here \textbf{P} refer to premise, \textbf{H} refer to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
-The literal semantic similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}.
+The literal similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}.
 The model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
 %
-At the first glance, the task of natural language inference may seem less practical compared to other common NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
 %The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
@@
 %\shusen{What is the basic understanding of neural network What is the end-to-end}
-There are many connection and distinction between neural network model employed for vision tasks and NLP tasks.
-On the one hand, as discussed in the introduction, the discrete nature of words and sentences presents additional challenge for
+There are many connection and distinction between neural network model employed for vision and NLP tasks.
+On the one hand, as discussed in the introduction, the discrete nature of words and sentences presents additional challenges for
 interpreting the NLP model.
@@
 vectorized input and yields final prediction for a specific task.
+%
+Many of the recent NLP end-to-end neural network models, despite having potentially drastic different network architectures, share a similar high-level design that consist of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
+%
+The existence of shared conceptual structures mean the proposed tool, though designed for NLI task, can be generalized for a much broader set of applications.
 
@@
 
-Many of the recent NLP end-to-end neural network models, despite having potentially drastic different network architectures, share a similar high-level design that consist of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
+These end-to-end models usually take pre-trained word vectors (numerical vector representation of individual words, in which the semantic similarities are expressed by distances in the high-dimensional vector space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, and then in the encoding stage, the pre-trained vectors are adjusted to the specialized task at hand.
+Subsequently, the next stage aim at finding alignment between words in the input sequences.
+For NLI task, this means finding the corresponds between words from premise sentence to hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
+Finally, in the last stage, the alignment information and the encoded vector representations are aggregated and then used as features for a classification network (last part of the end-to-end neural network).
 %
-The existence of the similar structures mean the proposed tool, which designed for NLI task, can be generalized for a much broader set of applications.
-
-These end-to-end models usually take pre-trained word vectors (numerical vector representation of individual words, in which the semantic similarities are encode by distances in the high-dimensional vector space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, and then in the encode stage pre-trained vectors are adjusted to the specialized task at hand.
-Subsequently, the next stage aim at finding alignment between words in the input sequence.
-For task like NLI, this means finding the corresponds between words from premise sentence to hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
-Finally, in the last stage the alignment information and the encoded vector representations are aggregated and then used as features for a classification network (last part of the end-to-end neural network).
-%
-Since, all these three stages of the model are train jointly in an end-to-end fashion, therefore, to make sense of how predictions are made inside such a models, it is important to explore the interaction between intermediate representations and predictions.
+Since, all these three stages of the model are trained jointly in an end-to-end fashion, therefore, to make sense of how predictions are made inside such a model, it is important to explore the interaction between intermediate representations and predictions.
 
@@
  \includegraphics[width=0.9\linewidth]{attentionIllustration}
- \caption{Attention illustrate. The soft alignment between two sentences.}
+ \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
+On the left, the matrix shows the soft alignment between between premise and hypothesis pair.}
 \label{fig:attention}
 \end{figure}
+
+For natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft alignment between words in premise and the words in the hypothesis.
+As we can see in this example, the higher values indicate better alignments between words.
+The \emph{subject}, \emph{verb}, and \emph{object} between these two sentences are aligned correctly (words, such as ``an'', that hold less importance in determine sentence relationship was assigned a lower score).
+Interestingly, the difference between the subject words does not affect their alignment.
+The classification stage can then utilize this information to determine the subject of the sentence are different, therefore, despite the other part of the sentences are identical, the relationship between premise and hypothesis is neutral.
 

### 2018-03-24 src/visPackage/static/components/attentionMatrixComponent.js

@@ -304,26 +304,6 @@ class attentionMatrixComponent extends attentionComponent {
         let row = Math.floor(i / this.normAttention[0].length);
         let col = i % this.normAttention[0].length;
 
-        /*if (this.dragEventX < d3.event.x) {
-            if (d.value <= 1) {
-                d.value += 0.1;
-            }
-
-            if (this.normAttentionCol[row][col] <= 1.0) {
-                this.normAttentionCol[row][col] += 0.1;
-            }
-        } else if (this.dragEventX > d3.event.x) {
-            if (d.value >= 0) {
-                d.value -= 0.1;
-            }
-            if (this.normAttentionCol[row][col] >= 0.0) {
-                this.normAttentionCol[row][col] -= 0.1;
-                if (this.normAttentionCol[row][col] < 0.0)
-                    this.normAttentionCol[row][col] = 0.0;
-            }
-
-        }*/
-
         //renormalize current row.
 
         this.normAttention[row][col] = d;

### 2018-03-24 paper/appendix_modelDescription.tex
update appendix

--- 2018-03-23 paper/paper_entailVis.tex
@@
 \usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
+\usepackage{listings}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\footnotesize,
+    breakatwhitespace=false,         
+    %breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+
+\lstset{style=mystyle}
 
@@
 \newcommand{\shusen}[1]{\textcolor{red}{[#1]}}
+
+\usepackage{tikz}
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
 
@@
 \title{
-NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
+Supplementary Materials
 %Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
 }
-%% This is how authors are specified in the journal style
+\vgtcinsertpkg
 
-%% indicate IEEE Member or Student Member in form indicated below
-% \author{Roy G. Biv, Ed Grimley, \textit{Member, IEEE}, and Martha Stewart}
-% \authorfooter{
-% %% insert punctuation at end of each item
-% \item
-%  Roy G. Biv is with Starbucks Research. E-mail: roy.g.biv@aol.com.
-% \item
-%  Ed Grimley is with Grimley Widgets, Inc.. E-mail: ed.grimley@aol.com.
-% \item
-%  Martha Stewart is with Martha Stewart Enterprises at Microsoft
-%  Research. E-mail: martha.stewart@marthastewart.com.
-% }
+\begin{document}
+\firstsection{Appendix 1, Detailed description of the Model}
+\maketitle
 
-%other entries to be set up for journal
-\shortauthortitle{Natural Language Inference Model Visualization}
-%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}
+\section{Appendix 2, Code Example: Link Visualization with Model}
+\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
+from visPackage import *
+from modelInterface import *
+from sentenceGenerator import *
 
-%% Abstract section.
-% What are we doing in this paper
-\abstract{
-With the recent advances in deep learning, neural network based models have obtained state-of-the-art performances for many linguistic tasks in natural language processing.
-The disruptive progress also brings enormous challenges.
-The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms.
-In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
-We use natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states and interpreting and hypothesizing the fundamental model mechanism such as attention.
-} % end of abstract
+#initialize NLP model
+model = modelInterface(
+    wordDict="../data/snli_1.0/snli_1.0.word.dict",
+    wordVec="../data/glove.hdf5", 
+    model="../data/local_300_parikh")
 
-%% Keywords that describe your work. Will show as 'Index Terms' in journal
-%% please capitalize first letter and insert punctuation after last keyword
-\keywords{Natural Language Processing, Interpretable Machine Learning, Natural Language Inference, Attention Visualization}
+#sentence perturbation
+gen = sentenceGenerator()
+#dependency parsing
+dep = dependencyTree()
 
-%% ACM Computing Classification System (CCS).
-%% See <http://www.acm.org/class/1998/> for details.
-%% The ``\CCScat'' command takes four arguments.
-
-% \CCScatlist{ % not used in journal version
-%  \CCScat{K.6.1}{Management of Computing and Information Systems}%
-% {Project and People Management}{Life Cycle};
-%  \CCScat{K.7.m}{The Computing Profession}{Miscellaneous}{Ethics}
-% }
-
-%% Uncomment below to include a teaser figure.
-% \teaser{
-%   \centering
-%   \includegraphics[width=\linewidth]{CypressView}
-%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
-% 	\label{fig:teaser}
-% }
-\teaser{
-% \vspace{-8mm}
- % \includegraphics[width=0.78\linewidth]{teaser}
- \includegraphics[width=.96\linewidth]{teaser.pdf}
- \centering
- % \vspace{-3mm}
-  \caption{
- System overview.
-  }
-\label{fig:teaser}
+#define visualization components
+visLayout = {
+    "column":[{"row":["Selector", 
+                                "Sentence", 
+                                "Pipeline"]},
+            {"row":["AttentionGraph", 
+                       "AttentionMatrix", 
+                       "Prediction"]}]
     }
 
-%% Uncomment below to disable the manuscript note
-%\renewcommand{\manuscriptnotetxt}{}
+#create vis interface
+vis = textEntailVisModule(visLayout)
 
-%% Copyright space is enabled by default as required by guidelines.
-%% It is disabled by the 'review' option or via the following command:
-% \nocopyrightspace
+#setup model callbacks
+vis.setPredictionHook(model.predict)
+vis.setAttentionHook(model.attention)
+vis.setPredictionUpdateHook(model.updatePrediction)
+vis.setAttentionUpdateHook(model.updateAttention)
+vis.setReloadModelCallback(model.reloadModel)
+vis.setPipelineStatisticHook(model.pipelineStatistic)
 
-\vgtcinsertpkg
+#setup perturbation and grammar parsing callbacks
+vis.setSentencePerturbationHook(gen.perturbSentence)
+vis.setSentenceParserHook(dep.getDependencyTree)
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+#open browser to show visualization
+modelVis.show()
 
-\begin{document}
+\end{lstlisting}
 
-%% The ``\maketitle'' command must be the first command after the
-%% ``\begin{document}'' command. It prepares and prints the title block.
-
-%% the only exception to this rule is the \firstsection command
-\input{intro.tex}
-\input{background.tex}
-\input{relatedWorks.tex}
-
-\input{task.tex}
-\input{pipeline.tex}
-\input{perturbation.tex} % how to do the perturbation
-\input{sentence.tex}
-\input{attention.tex} % how to encode the information
-\input{prediction.tex}
-
-\input{application.tex}
-
-\input{evaluation.tex}
-\input{discussion.tex} % how to encode the information
-
-%% if specified like this the section will be committed in review mode
-% \acknowledgments{
-% The authors wish to thank A, B, and C. This work was supported in part by
-% a grant from XYZ (\# 12345-67890).}
-
-%\bibliographystyle{abbrv}
-\bibliographystyle{abbrv-doi}
-%\bibliographystyle{abbrv-doi-narrow}
-%\bibliographystyle{abbrv-doi-hyperref}
-%\bibliographystyle{abbrv-doi-hyperref-narrow}
-
-\bibliography{entailVis.bib}
 \end{document}

### 2018-03-24 paper/relatedWorks.tex
update appendix

@@
 
-\noindent\textbf{Visual Exploration of Neural Networks.}
-The effectiveness in the exploration of complex relationships, visualization have long been adopted for interpreting neural network models (e.g., the early works such as~\cite{TzengMa2005})
-Recently, many visualization works has dedicated to the neural network model interpretability challenges.
+\noindent\textbf{Visual Exploration of Neural Network Models.}
+Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network models~\cite{TzengMa2005}.
+Recently, the increasingly apparent interpretability challenge for deep neural network model motivate the introduction of many visualization works has dedicated to the neural network models.
 % The classification~\cite{KrausePererNg2016}
 In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
-Liu et al.~\cite{LiuShiCao2018} explore the possiblility of understanding the training process of deep generative models.
+Liu et al.~\cite{LiuShiCao2018} explore the possibility of understanding the training process of deep generative models.
 The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
-The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training procss, so they can provide design guideline to the deep neutral network architect.
+The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training process, so they can provide design guideline to the deep neutral network architect.
 
@@
 
-\noindent\textbf{Neural Linguistic Model Visualization.}
-Compare to the multitude of researchs for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.
+\noindent\textbf{NLP Models Visualization.}
+Compare to the multitude of research for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.
 %

### 2018-03-24 paper/sentence.tex
add sections structure

\subsection{All Pair Summary View}
\begin{itemize}
\item How go from 10k pair to one pair
\item How constitute interesting example
\item How to get a sense of overall prediction result
\end{itemize}

\subsection{Sentence View}
\begin{itemize}
\item Examine perturbed pair
\item See which word is perturbed in a sentence
\item Add to existing example collection
\end{itemize}

### 2018-03-25 paper/task.tex
update task

--- 2018-03-22 paper/task.tex
@@
 \label{sec:task}
-Effective identify and itemize the visualization tasks and the corresponding goal is the first step in designing a useful visual representation.
+Identify the analysis goals and the corresponding visualization tasks is the first yet significant step in designing a useful tool.
+In this section, we first examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
+% and how they fit into the domain experts experts' though process and workflow.
+Then, we reify the observations into concrete goals, from which we identify the visualization tasks that guide the design and implementation of the proposed tool.
 
-In this section,
+During our long-term collaboration with NLP experts, we have conducted extensive interview and discussion on the common approach employed by research for assessing the behavior of a model.%
+The prediction accuracy has it place as an objective evaluation metric to measure the overall effectiveness of the model, however, the accuracy number alone does not provide the full story.
+For example, the model can perform much worse on a different test set, or the model may produce correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that does not exist in real word scenarios).
+%
+Therefore, beside standard metrics, the domain experts often rely on exploration centric approach to 
+conduct error analysis and obtain intuition.
+%
+Such a process is iterative in nature, in which the domain experts go through many cycles of examine examples (e.g, what are the mistakes made by the model), and conduct experiments (e.g., perturb the input and observe the changes), formulate hypothesis (e.g, what are the potential causes for the failure).
+%ultimate forms intuition about the strength or the weakness of a given model. 
+% , then additional examples or variation of existing examples are bring in to rejected or confirm the hypotheses. And new questions or hypothesis may arise.
+%Such an analysis is iterative in nature and guided by domain knowledge and hypotheses based on the architecture. As they ask more questions and experiment 
+%experiment with model iterate their understanding of the model behavior, ultimate forms intuition about the strength or the weakness of a given model. 
+%and come up hypothesis about the potential cause for the failure.
+
+%%% iterative process call for interactive visualization
+
+%
+%A stereotypical scenario can be summarized as the follow.
+%
+To assess a model for a specific NLP task, the research start the analysis by looking at the failure cases.
+
+Look at example, perturb the example, see how the perturb the one fails,
+
+learn the limitation and strength from the where and how the errors occurs. iterate
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{errorAnalysis}
+ \caption{How domain experts conduct error analysis on the model.}
+\label{fig:modelPipeline}
+\end{figure}
+
+\begin{itemize}
+\item \textbf{G1} Understand how attention affect the prediction 
+\item \textbf{G2} Why sentences are misclassified 
+\item \textbf{G3} 
+\item \textbf{G4} 
+\end{itemize}
+
+\begin{itemize}
+\item \textbf{T1} Encode the internal state \emph{attention} of the model
+\end{itemize}

### 2018-03-25 paper/task.tex
update task

@@
 %
-%A stereotypical scenario can be summarized as the follow.
-%
+A stereotypical scenario can be summarized as the follow.
 To assess a model for a specific NLP task, the research start the analysis by looking at the failure cases.
-
 Look at example, perturb the example, see how the perturb the one fails,
-
 learn the limitation and strength from the where and how the errors occurs. iterate
 
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{errorAnalysis}
- \caption{How domain experts conduct error analysis on the model.}
-\label{fig:modelPipeline}
-\end{figure}
+%\begin{figure}[htbp]
+%\centering
+%\vspace{-2mm}
+% \includegraphics[width=1.0\linewidth]{errorAnalysis}
+% \caption{How domain experts conduct error analysis on the model.}
+%\label{fig:modelPipeline}
+%\end{figure}
 
+Analysis Goal
 \begin{itemize}
@@
 
+Visualization Tasks
 \begin{itemize}

### 2018-03-25 paper/perturbation.tex
add json print out
update structure
update paper structure
update layout of the paper
add figure for end2end
update tasks
minor fix

@@
-\section{Error Analysis Via Input Perturbation}
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{pipeline}
+ \caption{
+ Perturbation-Driven Exploration of the Language Inference Model.
+ }
+\label{fig:modelPipeline}
+\end{figure}
+
+\subsection{Perturbation-Driven Exploration}
+
+Fig.~\ref{fig:modelPipeline}
 
@@
 model performance.
-Prediction accuray, i.e., the percentage of the correct prediction according to
+Prediction accuracy, i.e., the percentage of the correct prediction according to
 the ground truth label, is the standard technique to verify the performance
@@
 %
-Often, the user need to examine individual failure examples to dignostic the
+Often, the user need to examine individual failure examples to diagnostic the
 issue and identify the weakness of the model.
@@
 
-\begin{itemize}
-    \item perturbation prediction change ratio
-    \item prediction distance (KL divergines) to original prediction
-    \item attention change distance
-\end{itemize}
+% \begin{itemize}
+%     \item perturbation prediction change ratio
+%     \item distribution distance (KL divergence) to original prediction
+%     \item attention change distance
+% \end{itemize}
 

### 2018-03-25 paper/pipeline.tex
minor fix

@@
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipeline}
- \caption{Language Inference Model Pipeline.}
-\label{fig:modelPipeline}
-\end{figure}
-
 \section{NLIVis Design}
-In this section, we describe the design of the NLIVis system, which address the tasks described in the previous section.
-
-\shusen{overview of the system}
+We describe the design of the NLIVis system, which address the visualization tasks described in the previous section. 
+%
+First, we discuss the perturbation-driven paradigm that is central to the achieving the visualization tasks.
+%
+Then, we describe in detail the five major components of the proposed system, namely, all pair summary view, sentence view, attention view, prediction view, pipeline view.
 

### 2018-03-25 paper/relatedWorks.tex
minor fix

@@
 Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network models~\cite{TzengMa2005}.
-Recently, the increasingly apparent interpretability challenge for deep neural network model motivate the introduction of many visualization works has dedicated to the neural network models.
+Recently, the increasingly apparent interpretability challenge for deep neural network model motivate the introduction of many visualization works that dedicated to the neural network models.
 % The classification~\cite{KrausePererNg2016}

### 2018-03-25 paper/sentence.tex
minor fix

@@
-\subsection{All Pair Summary View}
+\subsection{All Pairs Summary View}
+\label{sec:allPairs}
+Since we can only focus on one individual example at a time for detail analysis, 
+how to pick an single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
+%
+In addition, we also want to obtain certain high-level understand of how the whole set behave, beyond the information the prediction accuracy provide.
+
+%The all pair
 \begin{itemize}
-\item How go from 10k pair to one pair
-\item How constitute interesting example
+\item How to go from 10k pair to one pair
+\item What constitute interesting example
 \item How to get a sense of overall prediction result
@@
 \subsection{Sentence View}
+The sentence view shows the premise and hypothesis sentences, and in case of the existence of perturbation, highlight the where in the sentence the perturbation happens.
+%
+Add user customized sentences.
+
 \begin{itemize}

### 2018-03-25 paper/task.tex
update task

@@
 Identify the analysis goals and the corresponding visualization tasks is the first yet significant step in designing a useful tool.
-In this section, we first examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
-% and how they fit into the domain experts experts' though process and workflow.
-Then, we reify the observations into concrete goals, from which we identify the visualization tasks that guide the design and implementation of the proposed tool.
+In this section, we examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
+Then, we reify the multitude discussion with domain experts into concrete goals, from which we identify the visualization tasks that guide the design and implementation of the proposed tool.
 
 During our long-term collaboration with NLP experts, we have conducted extensive interview and discussion on the common approach employed by research for assessing the behavior of a model.%
-The prediction accuracy has it place as an objective evaluation metric to measure the overall effectiveness of the model, however, the accuracy number alone does not provide the full story.
-For example, the model can perform much worse on a different test set, or the model may produce correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that does not exist in real word scenarios).
+The prediction accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model, however, the accuracy number alone does not provide the full story. 
+For example, the model may produce correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that can not be generalized in real word scenarios).
 %
-Therefore, beside standard metrics, the domain experts often rely on exploration centric approach to 
+As a result, beside using standard metrics, the domain experts often rely on exploration centric approach to 
 conduct error analysis and obtain intuition.
+
+There is little one can learn when everything is working as expect, therefore, observing how model make mistakes under various scenarios is at the center of such a process. 
+The experts often start with simple failure examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction.
+This exercise help isolate where in the input is likely contributed to the failures.
+For many NLP models, the attention information (see Section~\ref{sec:attention}) is essential to infer the mechanism of the model.
+The expert can print out the attention values or generate plots to visualize the alignment between sentences or compare attentions.
+As the experts explore more variation of similar examples, combined with their domain knowledge, he / she may develop hypotheses about the cause of failures, or ask additional questions, which lead to further experimentation.
 %
-Such a process is iterative in nature, in which the domain experts go through many cycles of examine examples (e.g, what are the mistakes made by the model), and conduct experiments (e.g., perturb the input and observe the changes), formulate hypothesis (e.g, what are the potential causes for the failure).
+Since such a process is highly exploratory, get responsive answers to the domain experts' query is essential to maintain the flow of reasoning.
+
+The requirement for such analysis meshed nicely with the benefit of interactive visual exploration. 
+Therefore, adopting an visualization system that could provide visual representation of various model information should yield immediate benefits.
+%
+Moreover, by introducing new visual encoding and summarization, we can drastically expand the ways how domain experts interact with the model, enable exploration options that is not possible before either due to tedious manual operation or lack of communication channels.
+
+Through many discussions and iterations with NLP experts, we solidify the analysis goals as the the following.
+%Study the effect of perturbation of input to the prediction.
+Firstly, understanding how perturbation (e.g., replacing words) of the input affect the prediction is the curial part of error analysis.
+It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input (\textbf{G1}).
+%Understand how attention affect the prediction.
+Secondly, study the role and mechanism of attention by examine how variation in the input affect the attention, and how changes in attention affect prediction (\textbf{G1}).
+%Study the relationship between model stages (encoder, attention, classifier) and the prediction
+So far, we focus on how changes in earlier stage of the model affect later stages or final prediction.
+%
+However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction and how would that affect attention.
+Thirdly, examine the change of prediction lead to what type of change in each stages and it effects on attention (\textbf{G3}).
+%
+Based on the NLP analysis goals, we identify the visualization tasks to achieve these goals.
+
+\begin{itemize}
+\item \textbf{T1} Visualize the \emph{input}, \emph{attention}, \emph{prediction} of the model.
+\item \textbf{T2} Automate the perturbation of the input, explore the perturbation result.
+\item \textbf{T3} Customize the \emph{attention} for studying the relationship between attention and prediction
+\item \textbf{T4} Visualize the changes in the model stages with respect to prediction change driven model update \shusen{does not make sense}
+\end{itemize}
+
+%interrupted when they can not easily receive the answers to their immediate queries.
+
+% examining examples (e.g, what are the mistakes made by the model), and conduct experiments (e.g., perturb the input and observe the changes), formulate hypothesis (e.g, what are the potential causes for the failure).
 %ultimate forms intuition about the strength or the weakness of a given model. 
@@
 %and come up hypothesis about the potential cause for the failure.
-
-%%% iterative process call for interactive visualization
-
-%
-A stereotypical scenario can be summarized as the follow.
-To assess a model for a specific NLP task, the research start the analysis by looking at the failure cases.
-Look at example, perturb the example, see how the perturb the one fails,
-learn the limitation and strength from the where and how the errors occurs. iterate
 
@@
 %\end{figure}
-
-Analysis Goal
-\begin{itemize}
-\item \textbf{G1} Understand how attention affect the prediction 
-\item \textbf{G2} Why sentences are misclassified 
-\item \textbf{G3} 
-\item \textbf{G4} 
-\end{itemize}
-
-Visualization Tasks
-\begin{itemize}
-\item \textbf{T1} Encode the internal state \emph{attention} of the model
-\end{itemize}

### 2018-03-25 paper/relatedWorks.tex
update tasks

@@
 \section{Related Works}
-With the increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data),
+With the increasing demands for model accountability (e.g., what is the evidence for making the prediction) and model fairness (e.g., is the prediction affected by the bias in the training data),
 the interpretability of the machine learning model held significant implications.
-As a result, a wealth of researches have be focused on the explanation and interpretation of deep neural network models from both machine learning as well as visualization community.
+As a result, a wealth of research have be focused on the explanation and interpretation of deep neural network models from both machine learning as well as visualization community.
 
-\noindent\textbf{Model Interpretability.}
-Before one can solve the model interpertability challenge, we first need to understand what constitute an explaination or interpretation of a machine learning model.
-As discussed in ~\cite{Lipton2016, Doshi-Velez2017}, the concept of interprebale is inherently subjective, since the recipients of the explaination are always human.
+\textbf{Model Interpretability.}
+Before one can solve the model interpretability challenge, it worth to define what constitute an explanation or interpretation of a machine learning model.
+As discussed in ~\cite{Lipton2016, Doshi-Velez2017}, the concept of interpretable is inherently subjective, since the recipients of the explanation are always human.
 % And the discussion of interpretability quickly become philosophical.
 However, despite the underspecification nature of the problem, we can still refine the concept and provide certain guideline~\cite{Doshi-Velez2017}.
-
-One of the most studied aread in model interpretability is the explanation of a given prediction.
-Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simpler linear model near the prediction of interests).
+%
+%And as suggested in~\cite{Doshi-Velez2017}
+One of the most studied areas in model interpretability is the explanation of a given prediction.
+Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic perspective that made them applicable to different applications (i.e., by fitting a simpler linear model near the prediction of interests).
 %
@@
 
-% (Limitation of the state-of-the arts)
-% Model independent explanations is useful to gain intuition, but they lack the ability to link the external observation with inner states/mechanism of the model.
-
-\noindent\textbf{Visual Exploration of Neural Network Models.}
+\textbf{Visual Exploration of Neural Network Models.}
 Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network models~\cite{TzengMa2005}.
@@
 
-\noindent\textbf{NLP Models Visualization.}
+\textbf{NLP Models Visualization.}
 Compare to the multitude of research for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.

### 2018-03-25 paper/perturbation.tex
add figures

@@
+\subsection{Perturbation-Driven Exploration}
+To answer the questions arise during the exploration and address the analysis tasks, we adopted a .
+
+As illustrated in Fig.~\ref{fig:modelPipeline},
+
 \begin{figure}[htbp]
@@
 
-\subsection{Perturbation-Driven Exploration}
-
-Fig.~\ref{fig:modelPipeline}
-
-Understand where and how does a model fail is the first step to improve the
-model performance.
-Prediction accuracy, i.e., the percentage of the correct prediction according to
-the ground truth label, is the standard technique to verify the performance
-of a model on a given supervised task.
-%
-The accuracy alone does not tell us the whole story, it provides no
-information on the specific example and the condition that lead to a failure.
-%
 Often, the user need to examine individual failure examples to diagnostic the
@@
 
+% Understand where and how does a model fail is the first step to improve the
+% model performance.
+% Prediction accuracy, i.e., the percentage of the correct prediction according to
+% the ground truth label, is the standard technique to verify the performance
+% of a model on a given supervised task.
+% %
+% The accuracy alone does not tell us the whole story, it provides no
+% information on the specific example and the condition that lead to a failure.
+
 % \begin{itemize}

### 2018-03-25 paper/predSummary.tex
add figures

--- 2018-03-25 paper/sentence.tex
@@
 
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{summaryView}
+ \caption{Explore the full development set and examine their prediction result and sensitivity.}
+\label{fig:modelPipeline}
+\end{figure}
+
 %The all pair
@@
 \end{itemize}
-
-\subsection{Sentence View}
-The sentence view shows the premise and hypothesis sentences, and in case of the existence of perturbation, highlight the where in the sentence the perturbation happens.
-%
-Add user customized sentences.
-
-\begin{itemize}
-\item Examine perturbed pair
-\item See which word is perturbed in a sentence
-\item Add to existing example collection
-\end{itemize}

### 2018-03-25 paper/relatedWorks.tex
add figures

@@
 ~\cite{LiChenHovy2015}, by utilizing methods inspired by similar work in computer vision.
-The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurent neutural network.
-The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or glove~\cite{PenningtonSocherManning2014}.
+The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurrent neutral network.
+The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}.

### 2018-03-25 paper/sentence.tex
add figures

--- 2018-03-24 paper/sentence.tex
@@
-\subsection{All Pair Summary View}
-\begin{itemize}
-\item How go from 10k pair to one pair
-\item How constitute interesting example
-\item How to get a sense of overall prediction result
-\end{itemize}
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=0.85\linewidth]{sentenceView}
+ \caption{Sentence view shows the premise and the hypothesis sentence pair.}
+\label{fig:modelPipeline}
+\end{figure}
 
 \subsection{Sentence View}
+The sentence view shows the premise and hypothesis sentences, and in case of the existence of perturbation, highlight the where in the sentence the perturbation happens.
+%
+Add user customized sentences.
+
 \begin{itemize}

### 2018-03-25 paper/sentence.tex
update sentence view

@@
+\subsection{Sentence View}
+To start an exploration cycle, the experts need to examine the premise and hypothesis sentence the current example. 
+As illustrated in Fig.~\ref{fig:modelPipeline}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
+%
+To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces nous and verb by their synonymous in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
+%
+When perturbation is applied to either of the sentences, the replaced words are highlight in blue (see Fig~\ref{fig:modelPipeline}(e) ) to indicate the modification to the original sentence.
+%
+%%% sentence perturbation %%%%
+In addition, the user can type any sentences or modified existing text in the (c) and (d) to accommodate customized input when expert want to conduct quick experiment or when the automatic perturbation does not meet expectations.
+
 \begin{figure}[htbp]
@@
 
-\subsection{Sentence View}
-The sentence view shows the premise and hypothesis sentences, and in case of the existence of perturbation, highlight the where in the sentence the perturbation happens.
-%
-Add user customized sentences.
-
 \begin{itemize}

### 2018-03-25 paper/overview.tex

\begin{figure}[htbp]
\centering
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{
Perturbation-driven exploration of the natural language inference model.
In the proposed tool, we enables the automated or user-guided perturbation of the input sentence (e.g., replace words), the attention in the model (e.g., alter the alignment between sentences), and the prediction (e.g., adjust the prediction by making updates to the model).
}
\label{fig:modelPipeline}
\end{figure}

\section{NLIZE System}
In this section, we describe the design and implementation of the NLIZE (pronounced as ``analyze'') system, which address the analysis tasks (T1-3).
%
As discussed in the task analysis, the experts obtain intuition about the model via guided exploration by studying how various parts of the pipeline behave when certain components are altered.
%
This can be generalized as the perturbation-driven paradigm, which formulated the basic guiding principal for designing the proposed tool.
As illustrated in Fig.~\ref{fig:modelPipeline}, we enables the automated or user-guided perturbation of the input sentence (e.g., replace words), the attention in the model (e.g., alter the alignment between sentences), and the prediction (e.g., adjust the prediction by making updates to the model).
%
In the following sections, we describe in detail the five major components of the proposed system, namely, all pair summary view, sentence view, attention view, prediction view, pipeline view.

% Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.
%
% Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.

### 2018-03-25 paper/task.tex

@@
 In this section, we examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
-Then, we reify the multitude discussion with domain experts into concrete goals, from which we identify the visualization tasks that guide the design and implementation of the proposed tool.
+Then, we reify the multitude discussion with domain experts into concrete tasks, which guide the design and implementation of the proposed tool.
 
-During our long-term collaboration with NLP experts, we have conducted extensive interview and discussion on the common approach employed by research for assessing the behavior of a model.%
+During our long-term collaboration with NLP experts, we have conducted extensive discussion to understand the common approach employed by researcher for assessing the behavior of a model.%
 The prediction accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model, however, the accuracy number alone does not provide the full story.
@@
 %
-As a result, beside using standard metrics, the domain experts often rely on exploration centric approach to 
+As a result, the domain experts often rely on exploration centric approach to
 conduct error analysis and obtain intuition.
 
-There is little one can learn when everything is working as expect, therefore, observing how model make mistakes under various scenarios is at the center of such a process. 
+There is little one can learn when everything is behaving as expect, therefore,
+observing how model make mistakes under various scenarios is at the center of such a process.
 The experts often start with simple failure examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction.
@@
 %
-Since such a process is highly exploratory, get responsive answers to the domain experts' query is essential to maintain the flow of reasoning.
+The requirement for such exploratory analysis meshed nicely with the benefit of interactive visual exploration, in which the user can make adjustment on-the-fly and obtain instantaneous visual feedbacks that encode various model information.
+%
+Moreover, by introducing new visual encoding and summarization, we can drastically expand the ways domain experts interact with the model, enable exploration options that is not possible before either due to tedious manual operation or lack of communication channels.
 
-The requirement for such analysis meshed nicely with the benefit of interactive visual exploration. 
-Therefore, adopting an visualization system that could provide visual representation of various model information should yield immediate benefits.
+%Through many rounds of discussions with NLP experts,
+In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
 %
-Moreover, by introducing new visual encoding and summarization, we can drastically expand the ways how domain experts interact with the model, enable exploration options that is not possible before either due to tedious manual operation or lack of communication channels.
+Here, we solidify the analysis goals around the support for these type workflow and thought process of the experts.
+%
+\begin{itemize}
+\item Firstly, understanding how perturbation (e.g., replacing words) of the input affect the prediction is the curial part of error analysis.
+It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input (\textbf{T1}).
 
-Through many discussions and iterations with NLP experts, we solidify the analysis goals as the the following.
-%Study the effect of perturbation of input to the prediction.
-Firstly, understanding how perturbation (e.g., replacing words) of the input affect the prediction is the curial part of error analysis.
-It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input (\textbf{G1}).
 %Understand how attention affect the prediction.
-Secondly, study the role and mechanism of attention by examine how variation in the input affect the attention, and how changes in attention affect prediction (\textbf{G1}).
+\item Secondly, study the role and mechanism of attention by examine how variation in the input affect the attention, and how changes in attention affect prediction (\textbf{T2}).
 %Study the relationship between model stages (encoder, attention, classifier) and the prediction
 So far, we focus on how changes in earlier stage of the model affect later stages or final prediction.
+
+\item However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction and how would such a modification affect attention.
+Therefore, thirdly, we want to explore how model should be updated to produce the desirable change of prediction, and how the attention respond to such a change (\textbf{T3}).
+\end{itemize}
 %
-However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction and how would that affect attention.
-Thirdly, examine the change of prediction lead to what type of change in each stages and it effects on attention (\textbf{G3}).
-%
-Based on the NLP analysis goals, we identify the visualization tasks to achieve these goals.
+% Based on the NLP analysis goals, we identify the visualization tasks to achieve these goals.
 
-\begin{itemize}
-\item \textbf{T1} Visualize the \emph{input}, \emph{attention}, \emph{prediction} of the model.
-\item \textbf{T2} Automate the perturbation of the input, explore the perturbation result.
-\item \textbf{T3} Customize the \emph{attention} for studying the relationship between attention and prediction
-\item \textbf{T4} Visualize the changes in the model stages with respect to prediction change driven model update \shusen{does not make sense}
-\end{itemize}
+% \begin{itemize}
+% \item \textbf{T1} Visualize the \emph{input}, \emph{attention}, \emph{prediction} of the model.
+% \item \textbf{T2} Automate the perturbation of the input, explore the perturbation result.
+% \item \textbf{T3} Customize the \emph{attention} for studying the relationship between attention and prediction
+% \item \textbf{T4} Visualize the changes in the model stages with respect to prediction change driven model update %\shusen{does not make sense}
+% \end{itemize}
 

### 2018-03-26 paper/pipeline.tex
update captions

--- 2018-03-22 paper/pipeline.tex
@@
+\subsection{Pipeline View}
+
 \begin{figure}[htbp]
@@
 \vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipeline}
- \caption{Language Inference Model Pipeline.}
+ \includegraphics[width=1.0\linewidth]{pipelineView}
+ \caption{
+Visual representation of the three stages (encoder, attention, classifier) model.
+In the proposed tool, we allow the model parameter to be updated to fix a prediction error.
+The pipeline view, by showing the aggregated gradient distribution, inform the user about the how different part of the model response to the optimization.
+%
+The optimization parameters is shown in (a), each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ).
+In (c), we select whether if we want to use current update setting as display or try all the configuration combination (i.e., update for each stage can be enabled or disabled).
+ }
 \label{fig:modelPipeline}
@@
 
-\section{The p-NLI System}
-In this section, we describe the p-NLI system.
-
-% Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.
-%
-Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.
+\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
+the mira loss is $|w' - w|^2 + C * J(w')$

### 2018-03-26 paper/predSummary.tex
update sentence view
update captions

--- 2018-03-24 paper/sentence.tex
@@
-\subsection{All Pair Summary View}
-\begin{itemize}
-\item How go from 10k pair to one pair
-\item How constitute interesting example
-\item How to get a sense of overall prediction result
-\end{itemize}
+\subsection{All Predictions Summary View}
+\label{sec:allPairs}
+Since we can only focus on one individual example at a time for detail analysis,
+how to pick a single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
+%
+Beside the selection task, generate visual summarization there we also want to obtain certain high-level understand of how the whole set behave, beyond the information the prediction accuracy provide.
 
-\subsection{Sentence View}
-\begin{itemize}
-\item Examine perturbed pair
-\item See which word is perturbed in a sentence
-\item Add to existing example collection
-\end{itemize}
+%treemap for prediction
+We utilized a treemap (a) to encode the ground truth label and the model prediction generated by the
+By click on the treemap cell, we can narrow down the selection by focus on specific senarios.
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{summaryView}
+ \caption{
+Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select example of interests.
+We summarize all the prediction results in (a), where the green block indicates correct predictions, and orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
+%
+The user can select the treemap to focus on the specific type of senarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
+The selection can be further narrowed down by select the bin in the histogram.
+In (c) and (d), each point corresponds to one prediction.
+ }
+\label{fig:modelPipeline}
+\end{figure}
+
+%The all pair
+% \begin{itemize}
+% \item How to go from 10k pair to one pair
+% \item What constitute interesting example
+% \item How to get a sense of overall prediction result
+% \end{itemize}

### 2018-03-26 paper/prediction.tex
update paper structure
add sections structure
update task
update captions

@@
-\subsection{User-Guided Prediction Update}
+\subsection{Prediction View}
 
-\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
-the mira loss is $|w' - w|^2 + C * J(w')$
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=0.85\linewidth]{predictionView}
+ \caption{
+ In the prediction view, the prediciton probability (the probability of being neutral, contradict, and entailment) is encoded as barycentric coordinate system in an triangle.
+ The prediction result for the original sentence pair is represented by larger yellow dot) and their perturbations are illustrated by smaller grey dots.
+ A density contour of the prediction is computed to emphasis the highly cluttered areas and distinguish the outliers.
+ %How domain experts conduct error analysis on the model.
+ }
+\label{fig:modelPipeline}
+\end{figure}

### 2018-03-26 paper/sentence.tex
update captions

@@
 %
+In (a), \emph{Predict} and \emph{Predict All}, each corresponds to predict the current displayed sentence pairs, or predict all combinations of perturbed premise and hypothesis, provided there is only one perturbation per sentence pair (i.e., we use original premise if hypothesis is perturbed, or use original hypothesis if premise is perturbed).
 %%% sentence perturbation %%%%
+In (b), previous explored original sentence are stored in the dropdown list that allow the user to revisit previous examined sentence.
 In addition, the user can type any sentences or modified existing text in the (c) and (d) to accommodate customized input when expert want to conduct quick experiment or when the automatic perturbation does not meet expectations.
@@
 \vspace{-2mm}
- \includegraphics[width=0.85\linewidth]{sentenceView}
- \caption{Sentence view shows the premise and the hypothesis sentence pair.}
+ \includegraphics[width=0.95\linewidth]{sentenceView}
+ \caption{
+Sentence view shows the premise (c) and the hypothesis (d) sentence pair. The word that replaces the original text is highlight in blue, as illustrated in (e)
+In (a), \emph{Predict} and \emph{Predict All}, each corresponds to predict the current displayed sentence pairs, or predict all combinations of perturbed premise and hypothesis.
+In (b), previous explored original sentence are stored in the dropdown list that allow the user to revisit previous examined sentence.
+ }
 \label{fig:modelPipeline}
@@
 
-\begin{itemize}
-\item Examine perturbed pair
-\item See which word is perturbed in a sentence
-\item Add to existing example collection
-\end{itemize}
+%\begin{itemize}
+%\item Examine perturbed pair
+%\item See which word is perturbed in a sentence
+%\item Add to existing example collection
+%\end{itemize}

### 2018-03-26 paper/attention.tex
experiment with different attention
update paper structure

@@
-\section{Attention}
+\subsection{Attention View}
+Attention layer is an intermediate layer which gives some sense making information for domain expert to understand what information is generated from previous neural layer and how those information will affect the final prediction.
 
-\subsection{Visualize Attention}
+\begin{figure}[htbp]
+	\centering
+	\vspace{-2mm}
+	\includegraphics[width=1.0\linewidth]{MatrixAttention}
+	\caption{matrix visualize attention}
+	\label{fig:MatrixAttention}
+\end{figure}
 
-\subsection{Interpret Attention Via Model Perturbation}
+\begin{figure}[htbp]
+	\centering
+	\vspace{-2mm}
+	\includegraphics[width=1.0\linewidth]{attentionGraph}
+	\caption{bipartite graph visualize attention}
+	\label{fig:attentionGraph}
+\end{figure}
+
+%\subsubsection{Attention visualization challenges}
+\begin{itemize}
+	\item Why we need two different visual encoding to visualize attention? bipartite visualization more easier to highlight the 
+	\item long sentence, collapse
+	\item quickly compare the alignment information with the sentence's linguistic structure.
+\end{itemize}
+
+% \subsection{Interpret Attention Via Model Perturbation}

### 2018-03-26 paper/implementation.tex
update teaser

\subsection{Implementation}
\label{sec:implementation}

### 2018-03-26 paper/paper_entailVis.tex
update background
update teaser
update captions

@@
  % \includegraphics[width=0.78\linewidth]{teaser}
- \includegraphics[width=.96\linewidth]{teaser.pdf}
+ \includegraphics[width=1.0\linewidth]{teaser.pdf}
  \centering
@@
   \caption{
- System overview.
+The interface of the NLIZE system.
+During exploration, we can filter through large number of sentence examples summarized in (A) and select the example of interests displayed in (B).
+The model internal information (attention) is displayed (D) and (E).
+The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (F).
+Finally, the high-level model structure and the updates to the model are summarized in (C).
 }
@@
 \input{task.tex}
-\input{pipeline.tex}
-\input{perturbation.tex} % how to do the perturbation
+\input{overview.tex}
+
 \input{sentence.tex}
@@
 \input{prediction.tex}
+\input{pipeline.tex}
+\input{predSummary.tex}
 

### 2018-03-26 paper/predSummary.tex
update teaser

@@
 \label{sec:allPairs}
-Since we can only focus on one individual example at a time for detail analysis,
-how to pick a single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
+Since we can only focus on one individual example at a time for detail analysis, how to pick a single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
 %
@@
 %treemap for prediction
-We utilized a treemap (a) to encode the ground truth label and the model prediction generated by the
+As illustrate in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the ground truth label and the model prediction generated by the
 By click on the treemap cell, we can narrow down the selection by focus on specific senarios.
@@
  }
-\label{fig:modelPipeline}
+\label{fig:summaryView}
 \end{figure}

### 2018-03-26 paper/implementation.tex
add implementation

@@
 \label{sec:implementation}
+We design the tool with flexibility and extensibility in mind.
+One of the key objectives is to allow easy integration with existing NLP workflow.
+Therefore, instead of implementing the tool as a standalone application, we encapsulate the visualization functionality as a python library, in which the behavior of the visualization (e.g., what predict to show) can be specified in python using existing model in the expert's workflow.
+Also, due to the separation between the visualization and the underlying model computation, we can readily adapt to different models or the same model with different configuration or training.
+
+To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as for generating a prediction or access attention, to link the visualization with their models.
+The code use to create the visualization in this paper is included in appendix B (consists only a few lines of code).
+%
+The NLP model is implemented in pytorch~\cite{PaszkeGrossChintala2017}.
+The visual elements are implemented in D3.js using javascript, the python server act as glue between the javascript visualization and the pytorch model.

### 2018-03-26 paper/attention.tex
add attention vis
update teaser
add attention view

--- 2018-02-16 paper/attention.tex
@@
-\section{Attention}
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+\includegraphics[width=1.0\linewidth]{attentionView}
+\caption{
+Attention visualization.
+}
+\label{fig:attentionVis}
+\end{figure*}
 
-\subsection{Visualize Attention}
+\subsection{Attention View}
+\label{sec:attention}
+\shusen{How to fit dependency into the task, what is the motivation}
+As discussed in Section~\ref{sec:attention}, the attention is the only intermediate layer in the network that provide interpretable information for domain expert to infer the inner mechanisms of the model.
+%
+Intuitively, the attention captures the alignment of words between input sentences.
+In the NLI model examined in this work, the attention is represented as a matrix, in which the $i^{th}$ row corresponds to the probability of words in hypotheses align to the $i^{th}$ word in the premise.
+% The
 
-\subsection{Interpret Attention Via Model Perturbation}
+As illustrated in Fig.~\ref{fig:attentionVis}, we employ too visual encoding for attention.
+In the grpah attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+Such a view is good for highlight the most dominate alignments.
+However, if many attention values are high, the edges may become cluttered lead to less effective visualization.
+In addition, if the sentence structure different between premise and hypothesis is drastically different, we are likely to see the prominent edges cross each other, which can also lead to confusing visual patterns.
+The matrix attention view (b), despite being more verbose and less efficient in highlighting the dominate alignment, do not have similar shortcomings.
+Together them complement each other and provide the same information from different perspective.
+As illustrated by the pink arrow line, we can see how the same attention value is visualization in both the grpah and the matrix view.
+To help the user recongnize the correspondence during the exploration, we enable the linkage between highlight actions in both view.
+
+To full address the \emph{T2}, we also include the attention editing functionality.
+The attention matrix view is the most suitable place conduct the edit, since it provide a direction mapping of attention value.
+As we can see in Fig.~\ref{fig:attentionVis}(c), when the cell of the matrix is clicked, a sider will pop up to allow user customize the attention value (as the user edit the value, each row will be automatically normalized).
+%allow the user to view all the values clearly.
+
+%\subsubsection{Attention visualization challenges}
+% \begin{itemize}
+% 	\item Why we need two different visual encoding to visualize attention? bipartite visualization more easier to highlight the
+% 	\item long sentence, collapse
+% 	\item quickly compare the alignment information with the sentence's linguistic structure.
+% \end{itemize}
+
+% \subsection{Interpret Attention Via Model Perturbation}

### 2018-03-26 paper/pipeline.tex
add placeholder test
update teaser
add description for mira

@@
 \subsection{Pipeline View}
+\label{sec:pipeline}
+Visual representation of the three stages (encoder, attention, classifier) model.
+In the proposed tool, we allow the model parameter to be updated to fix a prediction error (\textbf{T3}).
+The pipeline view, by showing the aggregated gradient distribution, we inform the user on the how different part of the model response to the optimization.
+
+The optimization parameters is shown in (a), each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ).
+In (c), we select whether if we want to use current update setting as displayed or try all the configuration combination (i.e., each stage can be enabled or disabled).
 
@@
  }
-\label{fig:modelPipeline}
+\label{fig:pipelineView}
 \end{figure}
 
-\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
-the mira loss is $|w' - w|^2 + C * J(w')$
+% \textbf{Margin-Infused Relaxed Algorithm (MIRA)}
+There are many way to update the model to correct a prediction.
+The simplest way to achieve it is applying standard back propagation that overfit to the example.
+However, without any constrain, the update step may alter the model in unexpected ways.
+\shusen{what is the benefit of using mira?}
+Insetad, we adopted the \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003} update, where we regulate the optimization with the amount of change to the parameter.
+In the proposed tool, we define the mira loss as the following:
+\begin{equation}
+\mathrm{argmin}(  C J(w') + ||w' - w|| ),
+\end{equation}
+$J$ is the lost function for the model.

### 2018-03-26 paper/attention.tex

@@
 \includegraphics[width=1.0\linewidth]{attentionView}
+\vspace{-6mm}
 \caption{
 Attention visualization.
+In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+In the matrix attention view (b), the $i^{th}$ row corresponds to the probability of words in hypotheses align to the $i^{th}$ word in the premise.
+The user can alter the attention values via the pop up interface illustrated in (c).
 }
@@
 As illustrated in Fig.~\ref{fig:attentionVis}, we employ too visual encoding for attention.
-In the grpah attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
 Such a view is good for highlight the most dominate alignments.

### 2018-03-26 paper/overview.tex

@@
+\section{NLIZE System}
+In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze'', see interface overview in Fig.~\ref{fig:teaser}) system, which address the analysis tasks (\textbf{T1-3}).
+%
+As discussed in the task analysis, the experts often analyze and obtain intuition about the model by studying how altering one part of the model affect other stages of the pipeline.
+%
+Such a process can be generalized as the perturbation-driven paradigm, which is used as guiding principal for designing the proposed tool.
+%
+As illustrated in Fig.~\ref{fig:modelPipeline}, we enables the automated or user-guided perturbation of the input sentence (e.g., replace words), the attention in the model (e.g., alter the alignment between sentences), and the prediction (e.g., adjust the prediction by making updates to the model).
+%
+In the following sections, we describe in detail the five major components of the proposed system, namely, sentence view  (Section~\ref{sec:sentence}), attention view (Section~\ref{sec:attention}), prediction view (Section~\ref{sec:prediction}), pipeline view (Section~\ref{sec:pipeline}), all pair summary view (Section~\ref{sec:allPairs}).
+
 \begin{figure}[htbp]
@@
 
-\section{NLIZE System}
-In this section, we describe the design and implementation of the NLIZE (pronounced as ``analyze'') system, which address the analysis tasks (T1-3).
-%
-As discussed in the task analysis, the experts obtain intuition about the model via guided exploration by studying how various parts of the pipeline behave when certain components are altered.
-%
-This can be generalized as the perturbation-driven paradigm, which formulated the basic guiding principal for designing the proposed tool.
-As illustrated in Fig.~\ref{fig:modelPipeline}, we enables the automated or user-guided perturbation of the input sentence (e.g., replace words), the attention in the model (e.g., alter the alignment between sentences), and the prediction (e.g., adjust the prediction by making updates to the model).
-%
-In the following sections, we describe in detail the five major components of the proposed system, namely, all pair summary view, sentence view, attention view, prediction view, pipeline view.
-
 % Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.

### 2018-03-26 paper/prediction.tex
add placeholder test
update teaser

--- 2018-03-22 paper/prediction.tex
@@
-\subsection{User-Guided Prediction Update}
+\subsection{Prediction View}
+\label{sec:prediction}
+For a given sentence pair, the model predicts a discrete probability distribution of the three labels (neutral, contradict, and entailment).
+%
+In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}, a prediction probability is encoded as a point in the barycentric coordinate system of the triangle.
+In the triangle, the distinct color indicates the region corresponds to different labels.
+The prediction result for the original sentence pair is represented by the larger yellow circle, whereas smaller grey circles illustrate the perturbed sentence pairs.
+A density contour of the prediction is computed to emphasis the highly cluttered areas and distinguish the outliers.
 
-\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
-the mira loss is $|w' - w|^2 + C * J(w')$
+To address \textbf{T3}, we need a way to communicate the reassignment of the prediction.
+As illustrated in (b), we integrate such operation in the prediction panel.
+When press and drag the circle (prediction), the user is presented with the three option (E, N, C) corresponds to the labels.
+When the user hovers on one of the options, a dotted line is shown to indicate the newly assigned label.
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{predictionView}
+ \vspace{-2mm}
+ \caption{
+In the prediction view, the prediction is encoded as a point in the barycentric coordinate system of the triangle shown in (a).
+%
+The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
+A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+As illustrated in (b), the predicted label does not match the ground truth, therefore, we apply a label reassignment operation, which triggers the model update.
+% when press and drag the circle (prediction), the user is presented with the three option corresponds to the labels. The dotted line and arrow indicate the newly assigned label.
+ }
+\label{fig:predictionView}
+\end{figure}

### 2018-03-26 paper/sentence.tex

@@
 \subsection{Sentence View}
+\label{sec:sentence}
 To start an exploration cycle, the experts need to examine the premise and hypothesis sentence the current example.
-As illustrated in Fig.~\ref{fig:modelPipeline}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
+As illustrated in Fig.~\ref{fig:sentenceView}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
 %
@@
  }
-\label{fig:modelPipeline}
+\label{fig:sentenceView}
 \end{figure}

### 2018-03-26 paper/predSummary.tex
update prediction section
update pred summary

@@
-\subsection{All Predictions Summary View}
+\subsection{Summary View}
 \label{sec:allPairs}
-Since we can only focus on one individual example at a time for detail analysis, how to pick a single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
+% outline:
+%  - how to identify the sensitivity of pairs
+We can only focus on one individual example at a time for detailed analysis using the combination of all previously discussed views.
+As a result, how to select a pair of sentences of interests from the development or test dataset, which consists of close to $10k$ examples, is an obvious challenge.
+% - what is the interesting pairs
+In addition, the experts also interested in obtain high-level understanding that beyond the information the prediction accuracy provide of the behavior of the $10k$ sentence pairs.
 %
-Beside the selection task, generate visual summarization there we also want to obtain certain high-level understand of how the whole set behave, beyond the information the prediction accuracy provide.
+These two goals are the two sides of the same coin, the selection task will become much easier if we can generate a good visual summary of the $10k$ examples that help experts obtain deeper understanding of the whole $10k$ examples.
 
+To address these challenges, we introduce the summary view (see Fig.~\ref{fig:teaser}(A) ) that consist of a treemap, a histogram, and a scatterplot, to summary the prediction results of the $10k$ examples, and provide the ability to drill down to individual example for detailed analysis.
 %treemap for prediction
-As illustrate in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the ground truth label and the model prediction generated by the
-By click on the treemap cell, we can narrow down the selection by focus on specific senarios.
+As illustrated in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the different combination of ground truth label and the model prediction.
+In the treemap, the green blocks indicate examples where the predicted label agree with the ground truth label, where as the orange blocks indicate disagreement between the labels.
+The size of the block encodes the number of examples belongs to each category.
+%
+By click on the treemap cell, we can narrow down the selection by focus on specific scenarios.
+%
+As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are revealed to focus on the selected subset.
+The histogram shows the distribution of the prediction sensitivity in this category.
+For each original pair, the sensitivity is defined by the ratio between the number of unchanged predictions among the perturbed pairs and the all perturbed pairs.
+In other words, if we generated 100 sentence pairs via the automated sentence perturbation (i.e., replace nouns, and verbs, with synonymous), and after we predict the labels on all 100 pairs, if 80 out of the 100 maintain the original prediction label, we will have a sensitivity of 0.8.
+The \emph{sensitivity} measures how likely a sentence pair will change its prediction after applying minor perturbations to the original, which help the expert infer the model stability on the given example.
+%
+We can further narrow down the focused set by selecting the bins in the histogram (see Fig.~\ref{fig:summaryView}(b),(d)). 
+%
+In the scatterplot, beside showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to aid user better assess the sensitivity.
+For example, if the \emph{perturbCount} is rather small ($<10$), the sensitivity number is likely to be noisy and less trust compare to the ratio computed from much larger number of perturbed pairs.
 
@@
 %
-The user can select the treemap to focus on the specific type of senarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
+The user can select the treemap to focus on the specific type of scenarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
 The selection can be further narrowed down by select the bin in the histogram.

### 2018-03-26 paper/prediction.tex
update pred summary

@@
 To address \textbf{T3}, we need a way to communicate the reassignment of the prediction.
-As illustrated in (b), we integrate such operation in the prediction panel.
-When press and drag the circle (prediction), the user is presented with the three option (E, N, C) corresponds to the labels.
+As illustrated in (b), we integrate such operation in the prediction review.
+When press and drag the prediction (represented as circle), the user is presented with the three option (E, N, C) corresponds to the labels.
 When the user hovers on one of the options, a dotted line is shown to indicate the newly assigned label.
+The new label is assigned when the user release the mouse, when hovering on the desired label choice.
 

### 2018-03-26 paper/background.tex
update prediction section

@@
 
-At the first glance, the task of natural language inference may seem less practical compared to other common NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
+At the first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
 %
 Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from learning algorithm's point of view).
-Take the following sentences as an example (here \textbf{P} refer to premise, \textbf{H} refer to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
+Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
 The literal similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}.

### 2018-03-26 paper/predSummary.tex

@@
 %
-In the scatterplot, beside showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to aid user better assess the sensitivity.
-For example, if the \emph{perturbCount} is rather small ($<10$), the sensitivity number is likely to be noisy and less trust compare to the ratio computed from much larger number of perturbed pairs.
+In the scatterplot, beside showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help user better assess the \emph{sensitivity}.
+For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compare to the sensitivity ratio computed from much larger number of perturbed pairs.
 

### 2018-03-26 paper/relatedWorks.tex
update related works

@@
 the interpretability of the machine learning model held significant implications.
-As a result, a wealth of research have be focused on the explanation and interpretation of deep neural network models from both machine learning as well as visualization community.
+As a result, a wealth of research has been developed that focused on the explanation and interpretation of neural network models from both machine learning and visualization community.
 
@@
 % And the discussion of interpretability quickly become philosophical.
-However, despite the underspecification nature of the problem, we can still refine the concept and provide certain guideline~\cite{Doshi-Velez2017}.
+However, despite the underspecification nature of the problem, we can still refine the concept and provide certain guidelines~\cite{Doshi-Velez2017}.
+%And as suggested in~\cite{Doshi-Velez2017}
+In machine learning domain, one of the most studied areas in model interpretability is the explanation of predictions made by a convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015,OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
 %
-%And as suggested in~\cite{Doshi-Velez2017}
-One of the most studied areas in model interpretability is the explanation of a given prediction.
-Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic perspective that made them applicable to different applications (i.e., by fitting a simpler linear model near the prediction of interests).
+These methods either identify the pattern that maximally activate a part of the network (referred to as feature visualization, i.e., what feature does the given neuron, channel, or layer captures), or reveal what area in the input contribute most to the prediction label (often referred to as attribution, i.e., attribute the prediction label in the input domain).
 %
-Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
+Beside the techqniues design for specific type of model, a few works~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} approach the interpretability challenge from a model agnostic perspective, which make them applicable to different applications.
+Intuitively, many of them aim to fit a simpler linear model near the prediction of interests to provide a simpler but easier to understanding snapshot of the model near the a specific input.
+%
+Despite being invaluable for providing human understandable explanation, however, the lack of the ability to access and explore the internal states of the model, which is vitally important for making sense of the inner works of a model, limits their ability for more in depth exploration and evaluation of the model.
 
 \textbf{Visual Exploration of Neural Network Models.}
-Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network models~\cite{TzengMa2005}.
-Recently, the increasingly apparent interpretability challenge for deep neural network model motivate the introduction of many visualization works that dedicated to the neural network models.
+Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network model~\cite{TzengMa2005}.
+Recently, the increasingly demand for interpretability for deep neural network model motivate the introduction of many visualization works that dedicated to the neural network models.
 % The classification~\cite{KrausePererNg2016}
@@
 %
-However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also revealed enoumous possibility for future applications.
+However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also revealed enormous possibility for future applications.
 % There is many unresolve challenge and the
-The early work on charactor level recurrent network~\cite{KarpathyJohnson2015} demonstrates effectness of the hidden state in capturing the unique pattern in training text.
-The compositionality exibited in neural linguistic model (i.e., build sentence from meaing of words and phrases) are examined in the work by Li et al.
+The early work on character level recurrent network~\cite{KarpathyJohnson2015} demonstrates effectiveness of the hidden state in capturing the unique pattern in training text.
+The compositionality exibited in neural linguistic model (i.e., build sentence from meaning of words and phrases) are examined in the work by Li et al.
 ~\cite{LiChenHovy2015}, by utilizing methods inspired by similar work in computer vision.
-The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurrent neutral network.
+In the RNNVis~\cite{MingCaoZhang2017} work, the Ming et al. explore the  hidden state units in recurrent neural network based on their expected response to input texts.
+The RNNbow~\cite{CashmanPattersonMosca2017} work visualizes the backpropagation gradient information during the training of a recurrent neutral network to help the domain experts understand the how the model is trained.
+The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilizes a line plot style visual encoding to visualize the time varying hidden states of recurrent neutral network.
 The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}.

### 2018-03-27 paper/relatedWorks.tex
update related works

--- 2018-03-25 paper/relatedWorks.tex
@@
 the interpretability of the machine learning model held significant implications.
-As a result, a wealth of research have be focused on the explanation and interpretation of deep neural network models from both machine learning as well as visualization community.
+As a result, a wealth of research has been developed that focused on the explanation and interpretation of neural network models from both machine learning and visualization community.
 
 \textbf{Model Interpretability.}
-Before one can solve the model interpretability challenge, it worth to define what constitute an explanation or interpretation of a machine learning model.
-As discussed in ~\cite{Lipton2016, Doshi-Velez2017}, the concept of interpretable is inherently subjective, since the recipients of the explanation are always human.
-% And the discussion of interpretability quickly become philosophical.
-However, despite the underspecification nature of the problem, we can still refine the concept and provide certain guideline~\cite{Doshi-Velez2017}.
+Before one can solve the model interpretability challenge, it worth to define what constitutes an explanation or interpretation of a machine learning model.
+As discussed in ~\cite{Lipton2016, Doshi-Velez2017}, despite the concept of interpretable is inherently subjective, it is still necessary to refine the concept and devise guidelines for approaching model interpretability problems.
+%And as suggested in~\cite{Doshi-Velez2017}
+In machine learning community, one of the most studied areas in model interpretability is the interpretation of convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
 %
-%And as suggested in~\cite{Doshi-Velez2017}
-One of the most studied areas in model interpretability is the explanation of a given prediction.
-Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic perspective that made them applicable to different applications (i.e., by fitting a simpler linear model near the prediction of interests).
+These methods either identify the pattern that maximally activate a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures), or reveal what areas in the input contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
 %
-Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
+Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which make them applicable to different applications.
+In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understanding snapshot of the classifier near a specific input.
+%
+Despite being invaluable for generating a human understandable explanation, however, the lack of the ability to access and explore the internal states of the system limits their application. 
+%which is vitally important for making sense of the inner works of a model, 
+To avoid similar limitation, the proposed system enabled direct access and manipulation of the internal of the model.
 
 \textbf{Visual Exploration of Neural Network Models.}
-Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network models~\cite{TzengMa2005}.
-Recently, the increasingly apparent interpretability challenge for deep neural network model motivate the introduction of many visualization works that dedicated to the neural network models.
+Due to the effectiveness of exploring complex relationships, visualization has long been adopted for interpreting neural network model~\cite{TzengMa2005}.
+Recently, the increasing demand for interpretability for deep neural network model motivate the introduction of many visualization works that dedicated to the neural network models.
 % The classification~\cite{KrausePererNg2016}
-In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
-Liu et al.~\cite{LiuShiCao2018} explore the possibility of understanding the training process of deep generative models.
-The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
-The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training process, so they can provide design guideline to the deep neutral network architect.
+The Prospector~\cite{KrausePererNg2016} provided a model agnostic approach for analyzing and interpreting predictions via an interactive visual interface.
+%
+In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzed classification errors in convolutional neural networks (CNN) and answered the question on whether class hierarchy is learned in the network.
+%
+The DeepEyes~\cite{Pezzotti2018} focused on the analyzing the training process of CNN so that they can provide design guideline to the deep neutral network architect.
+%
+The ActiVis~\cite{KahngAndrewsKalro2018} introduced an interactive system tailored for tuning industry-scale neural network in Facebook.
+Finally, Liu et al.~\cite{LiuShiCao2018} presented a visualization tool for understanding the often challenging training process of deep generative models.
 
@@
 \textbf{NLP Models Visualization.}
-Compare to the multitude of research for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.
+Compare to the multitude of research for making sense of convolutional neural networks, relatively fewer works have been dedicated to neural language processing models.
 %
-However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also revealed enoumous possibility for future applications.
-% There is many unresolve challenge and the
-The early work on charactor level recurrent network~\cite{KarpathyJohnson2015} demonstrates effectness of the hidden state in capturing the unique pattern in training text.
-The compositionality exibited in neural linguistic model (i.e., build sentence from meaing of words and phrases) are examined in the work by Li et al.
-~\cite{LiChenHovy2015}, by utilizing methods inspired by similar work in computer vision.
-The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurrent neutral network.
-The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}.
+The previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models but also revealed enormous possibility for future applications.
+% There is many unresolved challenges and the
+The early work on character level recurrent network~\cite{KarpathyJohnson2015} demonstrates the effectiveness of the hidden state in capturing the unique pattern in the training text.
+The compositionality (i.e., build the meaning of a sentence from the meaning of words and phrases) exhibited in neural network linguistic models are examined by utilizing techniques inspired by model interpretability techniques in computer vision by Li et al.
+~\cite{LiChenHovy2015},
+In the RNNVis~\cite{MingCaoZhang2017} work, the Ming et al. visualize the hidden state units in a recurrent neural network based on their expected responses to model input.
+The RNNbow~\cite{CashmanPattersonMosca2017} system help domain experts understand how the model is trained by visualizing the backpropagation gradient information.
+The LSTMvis~\cite{StrobeltGehrmannPfister2018} work employs a line plot style visual encoding to represent the time varying hidden states of the recurrent neural network.
+The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrates how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space (e.g., word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}).
+%As discussed in the introduction, the experts guided exploration calls for the ability to interact with internal of the model in a dynamic setting.
+
+All of the previously discussed works either focus on the training process or examine the trained model as a fixed object.
+In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that is not possible before.
+%In addition, instead of exploring a language model or low-level, the proposed method focus on a specific NLP task, which provide insight on

### 2018-03-27 paper/background.tex
update related works
updates on background

@@
 The goal of NLI is to predict the relationship between a premise (\textbf{P}) sentence and a hypothesis (\textbf{H}) sentence. 
-The prediction fall in one of three categories: \emph{entailment} (\textbf{E}), \emph{contradiction} (\textbf{C}), \emph{neutral} (\textbf{N}).
-A simple example is shown in Table.~\ref{table:NLI}.
+The prediction falls in one of three categories: \emph{entailment} (\textbf{E}), \emph{contradiction} (\textbf{C}), \emph{neutral} (\textbf{N}).
+A simple example is shown in Table~\ref{tab:NLI}.
 In this case, the premise is ``Jim ate an apple''. 
-The hypothesis statement ``Jim ate fruits.'' can be concluded from the premise.
+The hypothesis statement ``Jim ate fruit.'' can be concluded from the premise.
 Therefore, the relationship between premise and hypothesis is \emph{entailment}.
 However, we should note that such a relationship is not necessarily reversible.
-Since the concept ``fruits'' is less restrictive than that of ``apple'', we can not conclude ``Jim ate an apple'' from the statement ``Jim ate fruits''.
+Since the concept ``fruit'' is less restrictive than that of ``apple'', we can not conclude ``Boy ate an apple'' from the statement ``Kid ate fruit''.
 The same logic applies to the hypothesis of ``Jim ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
@@
 \begin{table}[htbp]
-\label{table:NLI}
+\label{tab:NLI}
 \centering
@@
  \hline
- premise & Jim ate an apple. &  -  &  -  & - \\ 
- hypothesis & Jim ate fruits. & \checkmark &   &  \\
- hypothesis & Jim ate an banana. &  & \checkmark & \\
+ premise & Boy ate an apple. &  -  &  -  & - \\ 
+ hypothesis & Kid ate fruits. & \checkmark &   &  \\
+ hypothesis & Boy ate an banana. &  & \checkmark & \\
  hypothesis & Tom ate an apple &  &  & \checkmark \\
- hypothesis & Jim ate a Fuji apple. &   &  & \checkmark \\
+ hypothesis & Boy ate a Fuji apple. &   &  & \checkmark \\
  %\hline
@@
 Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
-The literal similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}.
-The model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
+The literal similarity between ``Electric'' and ``electrified'' may trick a model to predict \textbf{H2} as \emph{entailment}.
+A model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
 %
@@
 %
-Many of the recent NLP end-to-end neural network models, despite having potentially drastic different network architectures, share a similar high-level design that consist of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
+Many of the recent NLP end-to-end neural network models, despite having potentially drastic different network architectures, share a similar high-level design that consists of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
 %
@@
 These end-to-end models usually take pre-trained word vectors (numerical vector representation of individual words, in which the semantic similarities are expressed by distances in the high-dimensional vector space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, and then in the encoding stage, the pre-trained vectors are adjusted to the specialized task at hand.
-Subsequently, the next stage aim at finding alignment between words in the input sequences.
+Subsequently, the next stage aims at finding alignment between words in the input sequences.
 For NLI task, this means finding the corresponds between words from premise sentence to hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
@@
 \label{sec:attention}
-Among the three stages, the second stage often constitutes the most crucial part of the model as it determines where the classifier will focus on for generating a prediction.
+Among the three stages, the second stage often constitutes a crucial part of the model as it determines where the classifier will focus on for generating a prediction.
 The operation to compute the alignment between words in the input is referred to as the attention mechanism.
 The introduction of attention mechanism~\cite{bahdanau2014neural} allows
-pairwise interaction between internal representation of words (\shusen{the original text is hidden states, isn't the pairwise interaction between the representation of words, are the hidden states refer to that?}).
+pairwise interaction between internal representation of words. 
 This interaction can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
@@
 
+\taoli{The example needs to be changed accordingly.}
+
 \begin{figure}[htbp]
@@
  \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
-On the left, the matrix shows the soft alignment between between premise and hypothesis pair.}
+On the left, the matrix shows the attention between between premise and hypothesis pair.
+On the right, attention can also be interpreted as alignment.}
 \label{fig:attention}
@@
 For natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft alignment between words in premise and the words in the hypothesis.
-As we can see in this example, the higher values indicate better alignments between words.
+As we can see in this example, the higher values indicate significant alignments between words.
 The \emph{subject}, \emph{verb}, and \emph{object} between these two sentences are aligned correctly (words, such as ``an'', that hold less importance in determine sentence relationship was assigned a lower score).

### 2018-03-27 paper/background.tex
updates on background
update attention illustration
update task

@@
 A simple example is shown in Table~\ref{tab:NLI}.
-In this case, the premise is ``Jim ate an apple''. 
-The hypothesis statement ``Jim ate fruit.'' can be concluded from the premise.
+In this case, the premise is ``Boy ate an apple''.
+The hypothesis statement ``Kid ate fruits.'' can be concluded from the premise.
 Therefore, the relationship between premise and hypothesis is \emph{entailment}.
@@
 Since the concept ``fruit'' is less restrictive than that of ``apple'', we can not conclude ``Boy ate an apple'' from the statement ``Kid ate fruit''.
-The same logic applies to the hypothesis of ``Jim ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
+The same logic applies to the hypothesis of ``Boy ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
 %\emph{Contradiction} means the textual of hypothesis opposes that of premise;
@@
  hypothesis & Boy ate an banana. &  & \checkmark & \\
- hypothesis & Tom ate an apple &  &  & \checkmark \\
+ hypothesis & Tom ate an apple. &  &  & \checkmark \\
  hypothesis & Boy ate a Fuji apple. &   &  & \checkmark \\
@@
 
-\taoli{The example needs to be changed accordingly.}
-
 \begin{figure}[htbp]

### 2018-03-27 paper/task.tex
add attention view
update task

@@
 %
-As a result, the domain experts often rely on exploration centric approach to
-conduct error analysis and obtain intuition.
+As a result, the domain experts often rely on exploration centric approach to conduct error analysis and obtain intuition.
 
@@
 %
-Here, we solidify the analysis goals around the support for these type workflow and thought process of the experts.
+Here, we solidify the visualization tasks to facilitate the exploratory workflow and thought process of the domain experts.
 %
 \begin{itemize}
-\item Firstly, understanding how perturbation (e.g., replacing words) of the input affect the prediction is the curial part of error analysis.
+    \item Firstly, understanding how perturbation (e.g., replacing words with synonymous) of the input affect the prediction is the curial part of error analysis.
 It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input (\textbf{T1}).
@@
     %Understand how attention affect the prediction.
-\item Secondly, study the role and mechanism of attention by examine how variation in the input affect the attention, and how changes in attention affect prediction (\textbf{T2}).
+    \item Secondly, study the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
     %Study the relationship between model stages (encoder, attention, classifier) and the prediction
-So far, we focus on how changes in earlier stage of the model affect later stages or final prediction.
 
-\item However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction and how would such a modification affect attention.
+    \item So far, we focus on how changes in earlier stage of the model affect later stages or final prediction.
+However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction and how would such a modification affect attention.
     Therefore, thirdly, we want to explore how model should be updated to produce the desirable change of prediction, and how the attention respond to such a change (\textbf{T3}).

### 2018-03-27 paper/application.tex
update layout of the paper
update tasks
update section 5

@@
-\section{Put it All Together}
+\section{Application Story}
+\label{sec:caseStudy}
+% \shusen{A full case study that driven by the visualization task and the question associated with them}
+In this section, we utilizes the perturbation based analysis to illustrate how the proposed system can help the domain experts making sense of attention mechanism and assess the behavior of the model.
 
-\label{sec:caseStudy}
-
-In this section, we utilizes the perturbation based analysis
-to illustrate how the proposed system can be used
-to diagnose the model behavior, study the model's attention mechanism.
+\subsection{Is the Prediction Stable?}
+\shusen{difference in sensitivity among entail netural and contradict relationships}
 
@@
 
-% \subsection{Is Attention All You Need?}
+\subsection{What Does It Take to Change the Prediction?}
+
+\subsection{Is Attention All You Need?}

### 2018-03-27 paper/sentence.tex
update section 5

@@
 \label{sec:sentence}
-To start an exploration cycle, the experts need to examine the premise and hypothesis sentence the current example.
+% Once an exploration cycle started, the experts need to examine the premise and hypothesis sentence the current example.
 As illustrated in Fig.~\ref{fig:sentenceView}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
 %
-To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces nous and verb by their synonymous in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
+To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces \emph{nouns} and \emph{verbs} by their synonymous in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
 %
-When perturbation is applied to either of the sentences, the replaced words are highlight in blue (see Fig~\ref{fig:modelPipeline}(e) ) to indicate the modification to the original sentence.
-%
-In (a), \emph{Predict} and \emph{Predict All}, each corresponds to predict the current displayed sentence pairs, or predict all combinations of perturbed premise and hypothesis, provided there is only one perturbation per sentence pair (i.e., we use original premise if hypothesis is perturbed, or use original hypothesis if premise is perturbed).
-%%% sentence perturbation %%%%
-In (b), previous explored original sentence are stored in the dropdown list that allow the user to revisit previous examined sentence.
-In addition, the user can type any sentences or modified existing text in the (c) and (d) to accommodate customized input when expert want to conduct quick experiment or when the automatic perturbation does not meet expectations.
+When the perturbation is applied to either of the sentences, the replaced words are highlighted in blue (see Fig~\ref{fig:modelPipeline}(e) ) to signal the modification made to the original sentence.
 
@@
  \includegraphics[width=0.95\linewidth]{sentenceView}
+ \vspace{-2mm}
  \caption{
-Sentence view shows the premise (c) and the hypothesis (d) sentence pair. The word that replaces the original text is highlight in blue, as illustrated in (e)
-In (a), \emph{Predict} and \emph{Predict All}, each corresponds to predict the current displayed sentence pairs, or predict all combinations of perturbed premise and hypothesis.
-In (b), previous explored original sentence are stored in the dropdown list that allow the user to revisit previous examined sentence.
+ Sentence view shows the premise (c) and the hypothesis (d) sentence pair. The word that replaces the word in the original text is highlighted in blue (e).
+ The \emph{Predict} and \emph{Predict All} controls (a) correspond to predicting the currently displayed sentence pairs and predicting all combinations of perturbed premise and hypothesis, respectively.
+ Previous explored original sentence are stored in the dropdown list (d) that allow the user to revisit previous examined sentence.
 }
@@
 \end{figure}
+
+At the top left of the view, the two controls \emph{Predict} and \emph{Predict All} (a) correspond to predicting the currently displayed sentence pairs and predict all combinations of perturbed premise and hypothesis, respectively.
+%
+To avoid the situation where both sentences are perturbed, we ensure that only one perturbation per sentence pair (i.e., we use original premise if the hypothesis is perturbed, or use original hypothesis if the premise is perturbed).
+%%% sentence perturbation %%%%
+The previous explored original sentences are stored in the dropdown list (see Fig.~\ref{fig:sentenceView}(b)) that allow the user to revisit previous examined sentence.
+Also, the user can type any sentences or modified existing text in text areas (Fig.~\ref{fig:sentenceView}(c)(d)) to accommodate customized input when expert want to conduct a quick experiment or when the automatic perturbation is not sufficient.
 

### 2018-03-27 paper/appendix_modelDescription.tex
added model description in appendix

@@
 \usepackage{booktabs}                  % only used for the table example
+\usepackage{amsmath,bm}
 %% We encourage the use of mathptmx for consistent usage of times font
@@
 \usepackage{listings}
+
+\newcommand{\taoli}[1]{\textcolor{orange}{[#1]}}
 
@@
 \begin{document}
-\firstsection{Appendix 1, Detailed description of the Model}
+\firstsection{Appendix A: Detailed description of the Model}
 \maketitle
 
-\section{Appendix 2, Code Example: Link Visualization with Model}
+The Decomposable Attention model is an end-to-end model that takes vectorized premise sentence and hypothesis sentence, and output a probability distribution over three labels.
+The pipeline can be separated into three phases: encoder, attention and classifier.
+Here we briefly formalize these three layers.
+
+\subsection{Encoder}
+Denote the premise sentence as $\overline{\boldsymbol{P}} = (\overline{\boldsymbol{p}}_1, \overline{\boldsymbol{p}}_2, ..., \overline{\boldsymbol{p}}_m)$ and hypothesis sentence as $\overline{\boldsymbol{H}} = (\overline{\boldsymbol{h}}_1, \overline{\boldsymbol{h}}_2, ..., \overline{\boldsymbol{h}}_n)$ where $\overline{\boldsymbol{p}}_i$ and $\overline{\boldsymbol{h}}_j$ are the input embedding vectors respectively.
+The purpose of encoder is to generate specialized encodings that will participate in the following steps of the model.
+Define the encoder function as
+\begin{align}
+  \boldsymbol{P} &= F(\overline{\boldsymbol{P}})\\
+  \boldsymbol{H} &= F(\overline{\boldsymbol{H}})
+\end{align}
+
+where $F$ function is the encoder layer (e.g.
+a context-free two-layer ReLU).
+Let $\boldsymbol{P}$ denote the output premise encoding of size $m \times d$, and $\boldsymbol{H}$ the hypothesis encoding of size $n \times d$ where $d$ is the encoding size.
+
+\subsection{Attention} \label{sec:att}
+The job of attention layer is to capture pairwise interaction between encodings of premise and hypothesis. First we compute a similarity score matrix $\boldsymbol{S}$ ($m \times n$) by the following
+\begin{align}
+  S_{ij} &= \boldsymbol{p}_i ^T \boldsymbol{h}_j
+\end{align}
+
+Then attention weights are obtained by normalizing $\boldsymbol{S}$ bidirectionally.
+We will use $\leftarrow$ and $\rightarrow$ to differentiate the notation.
+That is, for premise token $\boldsymbol{p}_i$, a probability distribution over all $\boldsymbol{h}_j$`s are done as
+\begin{align}
+  \overleftarrow{\boldsymbol{a}}_i &= \frac{exp(S_{ij})}{\sum_{j \in h} exp(S_{ij})}
+\end{align}
+
+where $\overleftarrow{\boldsymbol{a}}_i$ is of dimension $1 \times n$ naturally. Similarly, for every $\boldsymbol{h}_j$, there is a probability distribution over all premise tokens.
+\begin{align}
+  \overrightarrow{\boldsymbol{a}}_j &= \frac{exp(S_{ij})}{\sum_{i \in p} exp(S_{ij})} \label{eq:aright}
+\end{align}
+
+where $\overrightarrow{\boldsymbol{a}}_j$ is a $1 \times m$ dimension.
+In case a token is not correlated with any other tokens, the model added an extra artificial token to both premise and hypothesis to allow a word aligning with null.
+
+\subsection{Classifier} \label{sec:cls}
+Classifier takes features from previous steps and predict a probability distribution over three labels. First, it aggregates features following the bidirectional attentions as
+\begin{align}
+  \boldsymbol{u}_i &= G([\overleftarrow{\boldsymbol{a}}_i \cdot \boldsymbol{H} \hspace{1ex} | \hspace{1ex}  \overline{\boldsymbol{p}}_i]) \\
+  \boldsymbol{v}_j &= G([\overrightarrow{\boldsymbol{a}}_j \cdot \boldsymbol{P} \hspace{1ex}  | \hspace{1ex}  \overline{\boldsymbol{h}}_j])
+\end{align}
+
+where G is the aggregation layer (e.g.
+two-layer ReLU) and $[\cdot|\cdot]$ denotes concatenation.
+Notice this aggregation layer jointly considers embeddings, encodings and attentions.
+With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict weight on each entailment score:
+\begin{align}
+  \boldsymbol{y} &= Z([\sum_i \boldsymbol{u}_i | \sum_j \boldsymbol{v}_j]) \label{eq:yscore}
+\end{align}
+
+where $Z$ is another neural layer (e.g.
+two-layer ReLU followed by a linear layer).
+For training, the scores $\boldsymbol{y}$ are connected to multi-class cross entropy loss function.
+For inference, the predicted label is $\arg\max_i y_i$.
+
+\taoli{Do we need citation in Appendix?}
+
+\textbf{Comment} We used the same network setting in the Decomposable Attention paper (cite).
+That are, network hidden size is $200$; input word embeddings are $200$ embeddings (downsampled from $300$ dimensional GloVe embeddings (cite) by a learnable linear layer); dropout (cite) is $0.2$ for learning; and learning rate is $0.05$.
+
+\section{Appendix B: Code Example: Link Visualization with Model}
 \begin{lstlisting}[language=Python, caption=Code for generating the visualization.]

### 2018-03-27 paper/attention.tex
update section 5
update attention section

--- 2018-03-26 paper/attention.tex
@@
-\subsection{Attention View}
-Attention layer is an intermediate layer which gives some sense making information for domain expert to understand what information is generated from previous neural layer and how those information will affect the final prediction.
-
-\begin{figure}[htbp]
+\begin{figure*}[htbp]
 \centering
 \vspace{-2mm}
-	\includegraphics[width=1.0\linewidth]{MatrixAttention}
-	\caption{matrix visualize attention}
-	\label{fig:MatrixAttention}
-\end{figure}
+\includegraphics[width=1.0\linewidth]{attentionView}
+\vspace{-6mm}
+\caption{
+Attention visualization.
+In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
+The user can alter the attention values via the pop-up interface illustrated in (c).
+We overlay the dependency tree ($a_1$) grammar structure to highlight important words and simplify complex sentence to reduce clutter (d-e).
+In (f), we show the difference between two attention matrix (the comparison feature is controlled by the buttons in the top left of all attention plots ($a_2$) ).
+}
+\label{fig:attentionVis}
+\end{figure*}
 
-\begin{figure}[htbp]
-	\centering
-	\vspace{-2mm}
-	\includegraphics[width=1.0\linewidth]{attentionGraph}
-	\caption{bipartite graph visualize attention}
-	\label{fig:attentionGraph}
-\end{figure}
+\subsection{Attention View}
+\label{sec:attention}
+As discussed in Section~\ref{sec:attention}, the attention is the only intermediate layer in the network that provides interpretable information for domain experts to infer the inner mechanisms of the model.
+%
+Intuitively, the attention captures the alignment of words between input sentences.
+For the NLI model examined in this work, the attention is represented as a matrix, in which the entries in the $i^{th}$ row corresponds to the probabilities of words in the hypotheses align to the $i^{th}$ word in the premise.
+
+As illustrated in Fig.~\ref{fig:attentionVis}, we employ two visual encodings for visualizing attention.
+In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+The color of rectangle text block encodes the sum of all edge values connect to it (darker shade of blues correspond to higher values).
+%
+The graph view is good for highlighting the most dominate alignments.
+However, if many attention values are high, the edges may become cluttered lead to less effective visualization.
+Also, if the sentence structures between premise and hypothesis are drastically different, we are likely to see the prominent edges cross each other, which can also lead to confusing and misleading visual patterns.
+
+The matrix attention view (Fig.~\ref{fig:attentionVis}(b)), despite being more verbose and less efficient in highlighting the dominant alignment, do not have similar shortcomings.
+Together, they complement each other and provide the same information from different perspectives.
+As illustrated by the pink arrow line, we can see how the same attention value is visualization in both the graph and the matrix view.
+To help the user recognize the correspondence during the exploration, we enable the linkage between highlight actions in both views.
+
+To support the ability to perturb the attention values (\textbf{T2}), we include the attention editing functionality.
+The attention matrix view is the most suitable place to conduct the edit operation since it provides a direct mapping of attention value.
+As we can see in Fig.~\ref{fig:attentionVis}(c), when a user clicks the cell of the matrix, a sider will pop up for customizing the attention value (as the user edit the value, each row is automatically normalized).
+%
+As illustrated in Fig.~\ref{fig:attentionVis}($a_{2}$)(f), we allow the user to compare currently and previously displayed attentions by computing and visualizing their difference.
+
+Even though the attention does not explicitly encode any grammar, they often highlight essential words in the sentence structure.
+%
+To help the researcher better understand the relationship between attention and sentence structure, as illustrated in Fig.~\ref{fig:attentionVis}($a_{1}$), we overlay the grammar dependency tree~\cite{Nivre2005} structure next to the sentence.
+%
+Since the dependency tree encodes the word importance information in a hierarchical matter, it is very suitable for sentence simplification task.
+Therefore, we utilize the grammar dependency tree to simplify the attention representations to combat the visual clutter when examining long sentences (see Fig.~\ref{fig:attentionVis}(d)).
+A simplfication example is show in  Fig.~\ref{fig:attentionVis}(d)(e)(f).
 
 %\subsubsection{Attention visualization challenges}
-\begin{itemize}
-	\item Why we need two different visual encoding to visualize attention? bipartite visualization more easier to highlight the 
-	\item long sentence, collapse
-	\item quickly compare the alignment information with the sentence's linguistic structure.
-\end{itemize}
+% \begin{itemize}
+% 	\item Why we need two different visual encoding to visualize attention? bipartite visualization more easier to highlight the
+% 	\item long sentence, collapse
+% 	\item quickly compare the alignment information with the sentence's linguistic structure.
+% \end{itemize}
 

### 2018-03-27 paper/sentence.tex
update attention section

@@
 %%% sentence perturbation %%%%
-The previous explored original sentences are stored in the dropdown list (see Fig.~\ref{fig:sentenceView}(b)) that allow the user to revisit previous examined sentence.
-Also, the user can type any sentences or modified existing text in text areas (Fig.~\ref{fig:sentenceView}(c)(d)) to accommodate customized input when expert want to conduct a quick experiment or when the automatic perturbation is not sufficient.
+The previous explored original sentences are stored in the dropdown list (see Fig.~\ref{fig:sentenceView}(b)) that allow the user to revisit examined examples.
+Also, the user can type any sentences or modified existing text in the text areas (Fig.~\ref{fig:sentenceView}(c)(d)) to accommodate user defined input.
 

### 2018-03-27 paper/pipeline.tex
update eaquation
update pipeline

--- 2018-03-26 paper/pipeline.tex
@@
 \subsection{Pipeline View}
+\label{sec:pipeline}
+Pipeline view provides a direct visual representation of the three stages (encoder, attention, classifier) of the model.
+In the proposed tool, we allow the model parameter to be updated (via an optimization) to correct a prediction error (\textbf{T3}).
+The pipeline view, by visualizing the aggregated gradient distribution, informs the user on the how each stage of the model responses to the optimization.
+
+There are many ways to update the model to correct a prediction.
+The simplest way to achieve it is applying standard backpropagation that overfits to the example.
+However, without any constraint, the update step may alter the model in unexpected ways.
+% \shusen{what is the benefit of using mira?}
+Instead, we adopted the \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003} update, where we regulate the optimization with the amount of change to the parameter.
+In the proposed tool, we define the MIRA loss as the following:
+\begin{equation}
+\underset{w'}{\mathrm{argmin}}( C_{mira} \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||),
+\end{equation}
+where $\mathbb{J}(\mathbf{W})$ is the lost function for the model, and $\mathbf{W}$ is the original model's parameters, and $\mathbf{W}'$ is the updated parameters.
+$C_{mira}$ is the weighting term, which determines whether we intended to emphasis more on obtaining better fitting or deviating less from the original model.
+%
+Under this formation, we try to find the best approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
+
+As illustrated in Fig.~\ref{fig:pipelineView},
+the optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a).
+Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by click on the parameter bar (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d) ).
+In Fig.~\ref{fig:pipelineView}(c), we select whether if we want to use current update setting as displayed or try all the configuration combination (i.e., each stage can either be enabled or disabled for the three stage, therefore, there are $8$ combinations in total, $7$ if discard the case where all stages are not updated).
 
@@
  \caption{
-Visual representation of the three stages (encoder, attention, classifier) model.
-In the proposed tool, we allow the model parameter to be updated to fix a prediction error.
-The pipeline view, by showing the aggregated gradient distribution, inform the user about the how different part of the model response to the optimization.
+ The pipeline view provides the visual representation of three stages (encoder, attention, classifier) model.
+In the proposed tool, we allow the model parameter to be updated to correct a prediction error.
+The pipeline view, by showing the aggregated gradient distribution, informs the user about the how different part of the model response to the optimization.
  %
-The optimization parameters is shown in (a), each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ).
-In (c), we select whether if we want to use current update setting as display or try all the configuration combination (i.e., update for each stage can be enabled or disabled).
+ The optimization hyperparameters are shown in (a), each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ).
+In (c), we select whether if we want to use current update setting as displayed or try all the possible configuration combination (i.e., each stage's parameter update can be enabled or disabled).
  }
-\label{fig:modelPipeline}
+\label{fig:pipelineView}
 \end{figure}
 
-\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
-the mira loss is $|w' - w|^2 + C * J(w')$
+% \textbf{Margin-Infused Relaxed Algorithm (MIRA)}

### 2018-03-27 paper/appendix_modelDescription.tex
add citation for description
add missing citation

@@
 
-\taoli{Do we need citation in Appendix?}
+%\taoli{Do we need citation in Appendix?}
 
-\textbf{Comment} We used the same network setting in the Decomposable Attention paper (cite).
-That are, network hidden size is $200$; input word embeddings are $200$ embeddings (downsampled from $300$ dimensional GloVe embeddings (cite) by a learnable linear layer); dropout (cite) is $0.2$ for learning; and learning rate is $0.05$.
+\textbf{Comment} We used the same network setting in the Decomposable Attention paper~\cite{parikh2016emnlp}.
+That are, network hidden size is $200$; input word embeddings are $200$ embeddings (downsampled from $300$ dimensional GloVe embeddings~\cite{PenningtonSocherManning2014} by a learnable linear layer); dropout~\cite{SrivastavaHinton2014} is $0.2$ for learning; and learning rate is $0.05$.
 
@@
 \end{lstlisting}
+\bibliographystyle{abbrv-doi}
+%\bibliographystyle{abbrv-doi-narrow}
+%\bibliographystyle{abbrv-doi-hyperref}
+%\bibliographystyle{abbrv-doi-hyperref-narrow}
 
+\bibliography{entailVis.bib}
 \end{document}

### 2018-03-27 paper/background.tex
update the text based on feedback from christine

--- 2018-03-26 paper/background.tex
@@
 In this section, we first explain the definition of natural language inference (NLI) task and how it fits into the grand challenges in NLP.
-Then, we examine the common architecture characteristics shared by many state-of-the-art neural network models.
-Finally, we discuss the role the attention plays in the model and why attention is closely tied to model interpretability.
+Then, we examine the common architectural characteristics shared by many state-of-the-art neural network models.
+Finally, we discuss the role attention plays in the model and why attention is closely tied to model interpretability.
 
@@
 \label{sec:languageInference}
-Natural Language Inference (NLI)~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
+Natural language inference (NLI)~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
 The goal of NLI is to predict the relationship between a premise (\textbf{P}) sentence and a hypothesis (\textbf{H}) sentence. 
-The prediction fall in one of three categories: \emph{entailment} (\textbf{E}), \emph{contradiction} (\textbf{C}), \emph{neutral} (\textbf{N}).
+The prediction falls into one of three categories: \emph{entailment} (\textbf{E}), \emph{contradiction} (\textbf{C}), and \emph{neutral} (\textbf{N}).
 A simple example is shown in Table.~\ref{table:NLI}.
 In this case, the premise is ``Jim ate an apple''. 
-The hypothesis statement ``Jim ate fruits.'' can be concluded from the premise.
-Therefore, the relationship between premise and hypothesis is \emph{entailment}.
+The hypothesis statement ``Jim ate fruits'' can be concluded from the premise.
+Therefore, the relationship between the premise and hypothesis is \emph{entailment}.
 However, we should note that such a relationship is not necessarily reversible.
-Since the concept ``fruits'' is less restrictive than that of ``apple'', we can not conclude ``Jim ate an apple'' from the statement ``Jim ate fruits''.
-The same logic applies to the hypothesis of ``Jim ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
+Since the concept ``fruits'' is less restrictive than that of ``apple'', we cannot conclude ``Jim ate an apple'' from the statement ``Jim ate fruits''.
+The same logic applies to the hypothesis ``Jim ate a Fuji apple'', in which the premise neither implies nor opposes the hypothesis, and therefore, their relationship is \emph{neutral}.
 %\emph{Contradiction} means the textual of hypothesis opposes that of premise;
@@
  hypothesis & Jim ate fruits. & \checkmark &   &  \\
- hypothesis & Jim ate an banana. &  & \checkmark & \\
- hypothesis & Tom ate an apple &  &  & \checkmark \\
+ hypothesis & Jim ate a banana. &  & \checkmark & \\
+ hypothesis & Tom ate an apple. &  &  & \checkmark \\
  hypothesis & Jim ate a Fuji apple. &   &  & \checkmark \\
@@
 
-At the first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
+At first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
 %
-Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from learning algorithm's point of view).
+Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from the learning algorithm's point of view).
 Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
 The literal similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}.
-The model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
+The model likely will also fail to understand the link between ``went public'' and ``IPO'', and therefore, mistake \textbf{H1} as \emph{neutral}.
 %
@@
 Recently, Bowman et al.
-introduce a large corpus~\cite{BowmanAngeliPotts2015} for the NLI task, which helps spawn a new wave of effective neural network based NLI models.
+introduced a large corpus~\cite{BowmanAngeliPotts2015} for the NLI tasks, which has helped spawn a new wave of effective neural network models for those tasks.
 In this work, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.
@@
 %\shusen{What is the basic understanding of neural network What is the end-to-end}
-There are many connection and distinction between neural network model employed for vision and NLP tasks.
+There are many connections and distinctions between neural network models employed for vision and NLP tasks.
 On the one hand, as discussed in the introduction, the discrete nature of words and sentences presents additional challenges for
@@
 end-to-end model, where the entire model operates as a black-box that takes
-vectorized input and yields final prediction for a specific task.
+vectorized input and yields a final prediction for a specific task.
 %
-Many of the recent NLP end-to-end neural network models, despite having potentially drastic different network architectures, share a similar high-level design that consist of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
+Many of the recent NLP end-to-end neural network models, despite having potentially drastically different network architectures, share a similar high-level design that consists of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
 %
-The existence of shared conceptual structures mean the proposed tool, though designed for NLI task, can be generalized for a much broader set of applications.
+The existence of shared conceptual structures means the proposed tool, although designed for NLI task, can be generalized for a much broader set of applications.
 
@@
 These end-to-end models usually take pre-trained word vectors (numerical vector representation of individual words, in which the semantic similarities are expressed by distances in the high-dimensional vector space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, and then in the encoding stage, the pre-trained vectors are adjusted to the specialized task at hand.
-Subsequently, the next stage aim at finding alignment between words in the input sequences.
-For NLI task, this means finding the corresponds between words from premise sentence to hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
+Subsequently, the next stage aims at finding alignment between words in the input sequences.
+For the NLI task, this means finding the corresponds between words from the premise sentence to the hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
 Finally, in the last stage, the alignment information and the encoded vector representations are aggregated and then used as features for a classification network (last part of the end-to-end neural network).
 %
-Since, all these three stages of the model are trained jointly in an end-to-end fashion, therefore, to make sense of how predictions are made inside such a model, it is important to explore the interaction between intermediate representations and predictions.
+Since all these three stages of the model are trained jointly in an end-to-end fashion, it is important to explore the interaction between intermediate representations and predictions to make sense of how predictions are made inside such a model.
 
@@
 \label{sec:attention}
-Among the three stages, the second stage often constitutes the most crucial part of the model as it determines where the classifier will focus on for generating a prediction.
+Among the three stages, the second stage often constitutes the most crucial part of the model as it determines where the classifier will focus for generating a prediction.
 The operation to compute the alignment between words in the input is referred to as the attention mechanism.
-The introduction of attention mechanism~\cite{bahdanau2014neural} allows
-pairwise interaction between internal representation of words (\shusen{the original text is hidden states, isn't the pairwise interaction between the representation of words, are the hidden states refer to that?}).
-This interaction can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
+The introduction of the attention mechanism~\cite{bahdanau2014neural} allows
+pairwise interaction between internal representations of words (\shusen{the original text is hidden states, isn't the pairwise interaction between the representation of words, are the hidden states refer to that?}).
+This interaction can be naturally explained as a form of alignment that exposes an interpretable layer in end-to-end neural networks.
 %
 %As the only interpretable part of the internal state of the network, understanding how attention information 
-Recently, attention has contributed to many strongly-performed NLP models
+Recently, attention has contributed to many strongly performed NLP models
 ~\cite{parikh2016emnlp},~\cite{rush2015neural},~\cite{yang2016hierarchical},
@@
  \includegraphics[width=0.9\linewidth]{attentionIllustration}
- \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
-On the left, the matrix shows the soft alignment between between premise and hypothesis pair.}
+ \caption{Attention can be naturally explained as a form of alignment that exposes an interpretable layer in end-to-end neural networks.
+On the left, the matrix shows the soft alignment between between the premise and hypothesis pair.}
 \label{fig:attention}
@@
 
-For natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft alignment between words in premise and the words in the hypothesis.
+For the natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft alignment between words in the premise and the words in the hypothesis.
 As we can see in this example, the higher values indicate better alignments between words.
-The \emph{subject}, \emph{verb}, and \emph{object} between these two sentences are aligned correctly (words, such as ``an'', that hold less importance in determine sentence relationship was assigned a lower score).
+The \emph{subject}, \emph{verb}, and \emph{object} between these two sentences are aligned correctly (words such as ``an'', which has less importance in determining the sentence relationship were assigned a lower score).
 Interestingly, the difference between the subject words does not affect their alignment.
-The classification stage can then utilize this information to determine the subject of the sentence are different, therefore, despite the other part of the sentences are identical, the relationship between premise and hypothesis is neutral.
+The classification stage can then utilize this information to determine if the subject of the sentence is different, and therefore, despite the other part of the sentences being identical, the relationship between the premise and hypothesis is neutral.
 

### 2018-03-27 paper/paper_entailVis.tex
add implementation
updates on background
update pipeline
update the text based on feedback from christine

@@
 %\preprinttext{To appear in IEEE Transactions on Visualization and Computer Graphics.}
-
+\usepackage{amsmath}
 \usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
@@
 \title{
-NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
+NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
 %Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
@@
 \abstract{
-With the recent advances in deep learning, neural network based models have obtained state-of-the-art performances for many linguistic tasks in natural language processing.
+With the recent advances in deep learning, neural network models have obtained state-of-the-art performances for many linguistic tasks in natural language processing.
 The disruptive progress also brings enormous challenges.
-The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms.
-In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
-We use natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states and interpreting and hypothesizing the fundamental model mechanism such as attention.
+The opaque nature of neural network model leads to hard-to-debug-systems and difficulty interpreting mechanisms.
+In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, and prediction while observing changes in other parts of the pipeline.
+We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states and interpreting and hypothesizing fundamental model mechanisms such as attention.
 } % end of abstract
@@
 The interface of the NLIZE system.
-During exploration, we can filter through large number of sentence examples summarized in (A) and select the example of interests displayed in (B).
+During exploration, we can filter through a large number of sentence examples summarized in (A) and select examples of interest displayed in (B).
 The model internal information (attention) is displayed (D) and (E).
@@
 \input{predSummary.tex}
+\input{implementation.tex}
 

### 2018-03-27 paper/overview.tex

@@
 \section{NLIZE System}
-In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze'', see interface overview in Fig.~\ref{fig:teaser}) system, which address the analysis tasks (\textbf{T1-3}).
+In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze'', see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-3}).
 %
@@
 %
-As illustrated in Fig.~\ref{fig:modelPipeline}, we enables the automated or user-guided perturbation of the input sentence (e.g., replace words), the attention in the model (e.g., alter the alignment between sentences), and the prediction (e.g., adjust the prediction by making updates to the model).
+As illustrated in Fig.~\ref{fig:modelPipeline}, we enables the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences)inside the model, as well as the \emph{perturbation} the prediction (e.g., adjust the prediction by making updates to the model).
 %
@@
  Perturbation-driven exploration of the natural language inference model.
-In the proposed tool, we enables the automated or user-guided perturbation of the input sentence (e.g., replace words), the attention in the model (e.g., alter the alignment between sentences), and the prediction (e.g., adjust the prediction by making updates to the model).
+ In the proposed tool, we enables the interrogation of the relationship between different components of the model via the perturbation-based analysis.
+ %
+ The user can perturb the of the input sentence (i.e., replace words with synonymous), perturb the attention (i.e., alter the soft alignment between sentences), and perturb the prediction (i.e., adjust the prediction by making updates to the model).
 }

### 2018-03-27 paper/prediction.tex

--- 2018-03-26 paper/prediction.tex
@@
 %
-In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}, a prediction probability is encoded as a point in the barycentric coordinate system of the triangle.
-In the triangle, the distinct color indicates the region corresponds to different labels.
+In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle.
+In the triangle, the distinctly colored background indicates the regions corresponds to different labels.
 The prediction result for the original sentence pair is represented by the larger yellow circle, whereas smaller grey circles illustrate the perturbed sentence pairs.
-A density contour of the prediction is computed to emphasis the highly cluttered areas and distinguish the outliers.
+A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
 
-To address \textbf{T3}, we need a way to communicate the reassignment of the prediction.
-As illustrated in (b), we integrate such operation in the prediction panel.
-When press and drag the circle (prediction), the user is presented with the three option (E, N, C) corresponds to the labels.
+To perturb the prediction (\textbf{T3}), we need a way to communicate the reassignment of the predicted label.
+As illustrated in Fig.~\ref{fig:predictionView}(b), we integrate such operation in the prediction view.
+When press and drag the prediction (represented as a circle), the user is presented with the three options (E, N, C) correspond to the labels.
 When the user hovers on one of the options, a dotted line is shown to indicate the newly assigned label.
+The assignment is applied when the user releases the mouse while hovering on the label of choice.
 
@@
  %
-The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
+% The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
 A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
-As illustrated in (b), the predicted label does not match the ground truth, therefore, we apply a label reassignment operation, which triggers the model update.
+As illustrated in (b), the predicted label does not match the ground truth. Therefore, we apply a label reassignment operation, which triggers a model update.
 % when press and drag the circle (prediction), the user is presented with the three option corresponds to the labels. The dotted line and arrow indicate the newly assigned label.

### 2018-03-27 paper/pipeline.tex
updates on pipeline

@@
 There are many ways to update the model to correct a prediction.
-The simplest way to achieve it is applying standard backpropagation that overfits to the example.
+A simple way to achieve it is applying standard backpropagation that overfits to the example.
 However, without any constraint, the update step may alter the model in unexpected ways.
 % \shusen{what is the benefit of using mira?}
-Instead, we adopted the \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003} update, where we regulate the optimization with the amount of change to the parameter.
-In the proposed tool, we define the MIRA loss as the following:
+Instead, we adopted the same idea in \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the amount of change to the parameter.
+Therefore, in the proposed tool, we minimize the combined loss function by the following:
 \begin{equation}
-\underset{w'}{\mathrm{argmin}}( C_{mira} \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||),
+\underset{w'}{\mathrm{argmin}}( C \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||^2)
 \end{equation}
-where $\mathbb{J}(\mathbf{W})$ is the lost function for the model, and $\mathbf{W}$ is the original model's parameters, and $\mathbf{W}'$ is the updated parameters.
-$C_{mira}$ is the weighting term, which determines whether we intended to emphasis more on obtaining better fitting or deviating less from the original model.
+where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural model, $\mathbf{W}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the parameters to update, and $C$ is the weighting term, which determines whether we intended to emphasis more on obtaining better fitting or deviating less from the original model.
+Due to the nonconvex nature of the neural networks, we use SGD to optimize the above combined loss function.
 %
-Under this formation, we try to find the best approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
+Under this formation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
 

### 2018-03-27 paper/pipeline.tex
updates on pipeline

@@
 % \shusen{what is the benefit of using mira?}
-Instead, we adopted the same idea in \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the amount of change to the parameter.
+Instead, we adopt the same idea in \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the amount of change to the parameter.
 Therefore, in the proposed tool, we minimize the combined loss function by the following:

### 2018-03-27 paper/background.tex

@@
 \label{sec:languageInference}
-Natural language inference (NLI)~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
+Natural Language Inference (NLI)~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
 The goal of NLI is to predict the relationship between a premise (\textbf{P}) sentence and a hypothesis (\textbf{H}) sentence.
-The prediction falls into one of three categories: \emph{entailment} (\textbf{E}), \emph{contradiction} (\textbf{C}), and \emph{neutral} (\textbf{N}).
-A simple example is shown in Table.~\ref{table:NLI}.
-In this case, the premise is ``Jim ate an apple''. 
-The hypothesis statement ``Jim ate fruits'' can be concluded from the premise.
+The prediction falls in one of three categories: \emph{entailment} (\textbf{E}), \emph{contradiction} (\textbf{C}), and \emph{neutral} (\textbf{N}).
+A simple example is shown in Table~\ref{tab:NLI}.
+In this case, the premise is ``Boy ate an apple''.
+The hypothesis statement ``Kid ate fruits'' can be concluded from the premise.
 Therefore, the relationship between the premise and hypothesis is \emph{entailment}.
 However, we should note that such a relationship is not necessarily reversible.
-Since the concept ``fruits'' is less restrictive than that of ``apple'', we cannot conclude ``Jim ate an apple'' from the statement ``Jim ate fruits''.
-The same logic applies to the hypothesis ``Jim ate a Fuji apple'', in which the premise neither implies nor opposes the hypothesis, and therefore, their relationship is \emph{neutral}.
+Since the concept ``fruit'' is less restrictive than that of ``apple'', we can not conclude ``Boy ate an apple'' from the statement ``Kid ate fruit''.
+The same logic applies to the hypothesis of ``Boy ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
 %\emph{Contradiction} means the textual of hypothesis opposes that of premise;
@@
  \hline
- premise & Jim ate an apple. &  -  &  -  & - \\ 
- hypothesis & Jim ate fruits. & \checkmark &   &  \\
- hypothesis & Jim ate a banana. &  & \checkmark & \\
+ premise & Boy ate an apple. &  -  &  -  & - \\
+ hypothesis & Kid ate fruits. & \checkmark &   &  \\
+ hypothesis & Boy ate a banana. &  & \checkmark & \\
  hypothesis & Tom ate an apple. &  &  & \checkmark \\
- hypothesis & Jim ate a Fuji apple. &   &  & \checkmark \\
+ hypothesis & Boy ate a Fuji apple. &   &  & \checkmark \\
  %\hline
@@
 
-At first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
+At the first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
 %
-Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from the learning algorithm's point of view).
+Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from learning algorithm's point of view).
 Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
-The literal similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}.
-The model likely will also fail to understand the link between ``went public'' and ``IPO'', and therefore, mistake \textbf{H1} as \emph{neutral}.
+The literal similarity between ``Electric'' and ``electrified'' may trick a model to predict \textbf{H2} as \emph{entailment}.
+A model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
 %
@@
 %
+
 Many of the recent NLP end-to-end neural network models, despite having potentially drastically different network architectures, share a similar high-level design that consists of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
@@
 \label{sec:attention}
-Among the three stages, the second stage often constitutes the most crucial part of the model as it determines where the classifier will focus for generating a prediction.
+Among the three stages, the second stage often constitutes a crucial part of the model as it determines where the classifier will focus for generating a prediction.
 The operation to compute the alignment between words in the input is referred to as the attention mechanism.
 The introduction of the attention mechanism~\cite{bahdanau2014neural} allows
-pairwise interaction between internal representations of words (\shusen{the original text is hidden states, isn't the pairwise interaction between the representation of words, are the hidden states refer to that?}).
+pairwise interaction between internal representations of words. 
 This interaction can be naturally explained as a form of alignment that exposes an interpretable layer in end-to-end neural networks.
@@
 Recently, attention has contributed to many strongly performed NLP models
+
 ~\cite{parikh2016emnlp},~\cite{rush2015neural},~\cite{yang2016hierarchical},
@@
  \includegraphics[width=0.9\linewidth]{attentionIllustration}
- \caption{Attention can be naturally explained as a form of alignment that exposes an interpretable layer in end-to-end neural networks.
-On the left, the matrix shows the soft alignment between between the premise and hypothesis pair.}
+
+ \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
+On the left, the matrix shows the attention between between premise and hypothesis pair.
+On the right, attention can also be interpreted as alignment.}
 \label{fig:attention}
@@
 
-For the natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft alignment between words in the premise and the words in the hypothesis.
-As we can see in this example, the higher values indicate better alignments between words.
-The \emph{subject}, \emph{verb}, and \emph{object} between these two sentences are aligned correctly (words such as ``an'', which has less importance in determining the sentence relationship were assigned a lower score).
+For natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft alignment between words in the premise and the words in the hypothesis.
+As we can see in this example, the higher values indicate significant alignments between words.
+The \emph{subject}, \emph{verb}, and \emph{object} between these two sentences are aligned correctly (words, such as ``an'', which has less importance in determine sentence relationship was assigned a lower score).
 Interestingly, the difference between the subject words does not affect their alignment.
-The classification stage can then utilize this information to determine if the subject of the sentence is different, and therefore, despite the other part of the sentences being identical, the relationship between the premise and hypothesis is neutral.
+The classification stage can then utilize this information to determine the subject of the sentence are different, therefore, despite the other part of the sentences are identical, the relationship between the premise and the hypothesis is neutral.
 

### 2018-03-27 paper/intro.tex
add figures

@@
 % (What is the high level motivation)
-% What is the obsatcle for effectively apply machine learning model
-With the recent advances in neural network based model, machine learning has gained unprecedented popularity, and its adaption permeated many fields of studies.
+% What is the obstacle for effectively apply machine learning model
+With the recent advances in neural network model, machine learning has gained unprecedented popularity, and its adaption has permeated many fields of studies.
 %
@@
 Interpreting the internal mechanism and analyzing how predictions are made are critical to both the design and deployment of a model.
-More importantly, the ability to pinpoint where and how an error is made and come up with hypotheses for the cause of failure is the key to identify the limitation and improve upon existing models.
-However, providing meaningful answers to these questions are incredibly challenging and often regarded as impossible by many.
+More importantly, the ability to pinpoint where and how an error is made and come up with hypotheses for the cause of the error is the key to identifying the limitation and improving upon existing models.
+However, providing meaningful answers to these questions is incredibly challenging and often regarded as impossible by many.
 
 Recently, sizable research has been developed to combat the model interpretability challenges.
-Most notably, the works~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018} on interpreting convolution neural network (CNN) model from both machine learning and visualization community have revealed the enormous potential and immediate benefits of model interpretation.
+Most notably, the works~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018} on interpreting the convolution neural network (CNN) model from both the machine learning and visualization communities have revealed the enormous potential and immediate benefits of model interpretation.
 At the same time, these works also remind us how little we truly understand about the inner mechanism of these deep neural networks.
 
-Compare to image classification task, natural language processing (NLP) systems have innate restrictions (e.g., the discrete nature of words) that makes the road to interpretation more treacherous.
-For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) capture, can not be readily generalized to natural language.
-Image (pixel values) represents a continuous solution space, in which human can quickly recognize the existence (or the absence) of patterns or shapes.
-For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) do not hold clear meaning.
+Compared to image classification task, natural language processing (NLP) systems have innate restrictions (e.g., the discrete nature of words) that make the road to interpretation more treacherous.
+For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) captures, cannot be readily generalized to natural language.
+An image (pixel values) represents a continuous solution space, in which human can quickly recognize the existence (or the absence) of patterns or shapes.
+For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.
 %
-These restrictions call for new avenues for solving the interpretation challenges of natural language models, which motivate the proposed work.
+These restrictions call for new avenues for solving the interpretation challenges of natural language models, which motivates the proposed work.
 
@@
 Will the prediction be stable?
-What if we change one of the critical internal states of the model, how would the modification affect the prediction?
-What if the current prediction is wrong, how and where could we apply minimal change to the model to produce the correct result?
+What if we change one of the critical internal states of the model?
+How would the modification affect the prediction?
+What if the current prediction is wrong?
+How and where could we apply minimal change to the model to produce the correct result?
 And how would it affect the internal state we care about?
-These type of queries form a natural way to gain understanding and come up with hypotheses of the model mechanisms by \emph{interrogating} how the components of a model interact with each other in a dynamic setting.
-Hypothetically, we can code up specialized experiments for each of these scenarios.
+These types of queries form a natural way to gain understanding and come up with hypotheses of the model mechanisms by \emph{interrogating} how the components of a model interact with each other in a dynamic setting.
+Hypothetically, we can code specialized experiments for each of these scenarios.
 However, such a process is not only tedious but also ignores the iterative nature of the exploratory analysis.
@@
 In this work, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and direct online query/optimization of the neural network model.
-Instead of viewing the model as an invariant object, we approach the interpretability challenge by studying them in a dynamic environment.
+Instead of viewing the models as invariant objects, we approach the interpretability challenge by studying them in a dynamic environment.
 By employing a perturbation-driven paradigm, we probe the internal states of the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provides a new perspective to address the model interpretation problem.
@@
 %
-In the simplest form, the inference task asks the question about whether if we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), or are they contradict with each other (\emph{contradiction}), or are they talk about different/unrelated things (\emph{neutral}).
-Language inference addresses the fundamental challenge of measuring sentences' semantic similarity, and is one the core NLP tasks (see detail in Section~\ref{sec:languageInference}).
+In the simplest form, the inference task asks the question about whether we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), or if they are contradict with each other (\emph{contradiction}), or whether two sentences talk about different/unrelated things (\emph{neutral}).
+Language inference addresses the fundamental challenge of measuring the semantic similarity of sentences, and is one the core NLP tasks (see detail in Section~\ref{sec:languageInference}).
 
 One recent advance in neural natural language process models is the introduction of \emph{attention mechanisms}~\cite{VaswaniShazeerParmar2017} (Section~\ref{sec:attention}).
-Intuitively, the attention helps capture which part of the input the model deemed more important for making a prediction.
+Intuitively, the attention helps capture which part of the input the model is deemed more important for making a prediction.
 The attention is often represented as weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
@@
 There have been many speculations on how attention works in various models.
-By utilizing the proposed tool, the domain experts study how changes in sentence input, attention, or prediction affect each other, which help them develop deeper intuitive and alternative hypotheses.
+By utilizing the proposed tool, the domain experts study how changes in sentence input, attention, or prediction affect each other, which helps them develop deeper intuitive and alternative hypotheses.
 %we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention.
@@
 %Such type of exploration is not only essential to interpret the language inference problem, but can also be generalized to other NLP model utilized the attention mechanisms.
-Moreover, we enhanced the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification of the visual representation.
+Moreover, we enhanced the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar-guided simplification of the visual representation.
 %
-Finally, as discussed in Section~\ref{sec:caseStudy}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate the potential benefit of including the linguistic structure in the design of attention component of the model.
+Finally, as discussed in Section~\ref{sec:caseStudy}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate about the potential benefits of including the linguistic structure in the design of the attention component of the model.
 
-In summary, the key contributions of the proposed works is the following:
+In summary, the key contributions of the proposed works are the following:
 \begin{itemize}
@@
 
-    \item Perform error analysis by examining stability of the predictions under perturbation;
+    \item Perform error analysis by examining the stability of the predictions under perturbation;
 
-    \item Enhance the visual encoding of the attention by overlaying sentence linguistic structure to allow grammar guided simplification;
+    \item Enhance the visual encoding of the attention by overlaying sentence linguistic structure to allow grammar-guided simplification;
 
-    \item Enable the interrogation of the relationship between input sentences, model internals, and the prediction by interactively exploring how the change in one place affect other parts of the model.
+    \item Enable the interrogation of the relationships among input sentences, model internals, and the prediction by interactively exploring how the change in one place affects other parts of the model.
 \end{itemize}

### 2018-03-27 paper/pipeline.tex

@@
 % \shusen{what is the benefit of using mira?}
-Instead, we adopt the same idea in \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the amount of change to the parameter.
-Therefore, in the proposed tool, we minimize the combined loss function by the following:
+Instead, we adopt the same idea in \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the L2-norm of the parameter change.
+Therefore, in the proposed tool, we obtain the target parameters by the following:
 \begin{equation}

### 2018-03-27 paper/application.tex
minor fixeds

--- 2018-03-22 paper/application.tex
@@
-\section{Put it All Together}
+\section{Application Scenarios}
+\label{sec:caseStudy}
+% \shusen{A full case study that driven by the visualization task and the question associated with them}
+In this section, we discuss application scenarios, in which the domain experts utilize the perturbation driven analysis to explore and assess the model and interpret the attention mechanism.
+%
+These scenarios are summarized by the domain experts who integrated the tool into their model exploration workflow.
 
-\label{sec:caseStudy}
+\subsection{Scenario 1: Interpretting Model Decision Making Process}
+The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
+% \shusen{difference in sensitivity among entail natural and contradict relationships}
+% the generate the correct prediction for the wrong reason
 
-In this section, we utilizes the perturbation based analysis
-to illustrate how the proposed system can be used
-to diagnose the model behavior, study the model's attention mechanism.
+\subsection{Scenario 2: Which Part of the Model is the Problem?}
 
-\subsection{Where Are the Mistakes?}
+\subsection{Scenario 3: Handcraft Example Exploration}
+Well-know tough examples, such as the Facebook IPO example discussed in Section~\ref{sec:background}.
 
-\subsection{How Attention Affect the Prediction?}
+\subsection{Scenario 4: Handcraft Example Exploration?}
 
-% \subsection{Is Attention All You Need?}
+%\subsection{Is the Prediction Stable?}
+%\subsection{Where Are the Mistakes?}
+%\subsection{How Attention Affect the Prediction?}
+%\subsection{What Does It Take to Change the Prediction?}
+%\subsection{Is Attention All You Need?}

### 2018-03-27 src/modelInterface.py

@@ -256,6 +256,7 @@ class modelInterface:
         #map to token
         sourceSen = sentences[0]
         targetSen = sentences[1]
+        # if source and target:
         source = self.mapToToken(sourceSen)
         target = self.mapToToken(targetSen)
 

### 2018-03-27 src/visPackage/static/components/evaluationComponent.js

@@ -99,13 +99,13 @@ class evaluationComponent extends baseComponent {
         // var stabilities = data.map(d => d.stability);
         // console.log(stabilities);
         this.histo.setSample(data, d => d.stability);
-        this.histo.setTitle("Sensitivity");
-        this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
+        this.histo.setTitle("CorrectRatio");
+        this.scatter.setData(data, ["CorrectRatio", "PerturbCount"],
             d => [d.stability, d.perturbCount]);
     }
 
     updateScatterplot(data) {
-        this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
+        this.scatter.setData(data, ["CorrectRatio", "PerturbCount"],
             d => [d.stability, d.perturbCount]);
     }
 

### 2018-03-27 src/visPackage/visModule.py

@@ -205,40 +205,41 @@ class textEntailVisModule(visModule):
     def predictUpdate(self, newLabel, iteration, learningRate, encoderFlag, attFlag, classFlag, mira_c ):
         print "predictUpdate", newLabel, iteration, learningRate, encoderFlag, attFlag, classFlag
         mode = dataManager.getData("updateMode")
-        print " ===== predict update mode: ", mode
-        if mode == "single":
-            sentencePair = dataManager.getData("currentPair")['sentences']
-            att, pred = self.predictionUpdateHook(sentencePair, newLabel, iteration, learningRate, encoderFlag, attFlag, classFlag)
-            # print att, pred
+        sentencePair = dataManager.getData("currentPair")['sentences']
+        if sentencePair[0] and sentencePair[1]:
+            print " ===== predict update mode: ", mode
+            if mode == "single":
 
-            dataManager.setData("attention", att)
-            dataManager.setData("predictionUpdate", pred)
+                att, pred = self.predictionUpdateHook(sentencePair, newLabel, iteration, learningRate, encoderFlag, attFlag, classFlag)
+                # print att, pred
 
-            #update other predictions
-            self.predictAll()
-            self.pipelineStatistic()
-            return True
+                dataManager.setData("attention", att)
+                dataManager.setData("predictionUpdate", pred)
 
-        elif mode == "batch":
-            self.batchRecords = []
-            self.batchPreds = []
-            for encoderFlag in [True, False]:
-                for attFlag in [True, False]:
-                    for classFlag in [True, False]:
-                        if encoderFlag | attFlag | classFlag:
-                            print "batch run:", encoderFlag, attFlag, classFlag
-                            # restore the pipeline
-                            self.reloadModelCallback()
+                #update other predictions
+                self.predictAll()
+                self.pipelineStatistic()
+                return True
 
-                            sentencePair = dataManager.getData("currentPair")['sentences']
-                            att, pred = self.predictionUpdateHook(sentencePair, newLabel, iteration, learningRate, encoderFlag, attFlag, classFlag, mira_c)
+            elif mode == "batch":
+                self.batchRecords = []
+                self.batchPreds = []
+                for encoderFlag in [True, False]:
+                    for attFlag in [True, False]:
+                        for classFlag in [True, False]:
+                            if encoderFlag | attFlag | classFlag:
+                                print "batch run:", encoderFlag, attFlag, classFlag
+                                # restore the pipeline
[…]

### 2018-03-27 paper/appendix_modelDescription.tex

@@
 
-The Decomposable Attention model is an end-to-end model that takes vectorized premise sentence and hypothesis sentence, and output a probability distribution over three labels.
+The Decomposable Attention~\cite{parikh2016emnlp} model is an end-to-end model that takes vectorized premise sentence and hypothesis sentence, and output a probability distribution over three labels.
 The pipeline can be separated into three phases: encoder, attention and classifier.
@@
 Denote the premise sentence as $\overline{\boldsymbol{P}} = (\overline{\boldsymbol{p}}_1, \overline{\boldsymbol{p}}_2, ..., \overline{\boldsymbol{p}}_m)$ and hypothesis sentence as $\overline{\boldsymbol{H}} = (\overline{\boldsymbol{h}}_1, \overline{\boldsymbol{h}}_2, ..., \overline{\boldsymbol{h}}_n)$ where $\overline{\boldsymbol{p}}_i$ and $\overline{\boldsymbol{h}}_j$ are the input embedding vectors respectively.
-The purpose of encoder is to generate specialized encodings that will participate in the following steps of the model.
+The purpose of encoder is to generate specialized encodings for attention.
 Define the encoder function as
@@
 two-layer ReLU) and $[\cdot|\cdot]$ denotes concatenation.
-Notice this aggregation layer jointly considers embeddings, encodings and attentions.
 With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict weight on each entailment score:
@@
 
-\textbf{Comment} We used the same network setting in the Decomposable Attention paper~\cite{parikh2016emnlp}.
-That are, network hidden size is $200$; input word embeddings are $200$ embeddings (downsampled from $300$ dimensional GloVe embeddings~\cite{PenningtonSocherManning2014} by a learnable linear layer); dropout~\cite{SrivastavaHinton2014} is $0.2$ for learning; and learning rate is $0.05$.
+\textbf{Comment} We adopted the same network setting in the Decomposable Attention paper~\cite{parikh2016emnlp}.
+That are, network hidden size is $200$; input word embeddings are $200$d embeddings (downsampled from $300$d GloVe embeddings~\cite{PenningtonSocherManning2014} by a learnable linear layer).
+For learning, dropout~\cite{SrivastavaHinton2014} is $0.2$ and learning rate is $0.05$.
+Optimization algorithm is AdaGrad~\cite{duchi2011adaptive} with mini-batch size 64 and number of epochs 300.
 

### 2018-03-27 paper/appendix_modelDescription.tex
add legend for optimized

@@
 \section{Appendix B: Code Example: Link Visualization with Model}
+From the user point of view, the following python script is all the code the domain expert needs to link the NLP model with the visual interface.
+The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to supplied by the NLP model.
+
 \begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
@@
 vis.setAttentionUpdateHook(model.updateAttention)
-vis.setReloadModelCallback(model.reloadModel)
+vis.setReloadModelHook(model.reloadModel)
 vis.setPipelineStatisticHook(model.pipelineStatistic)

### 2018-03-27 paper/application.tex
add legend for optimized

@@
 In this section, we discuss application scenarios, in which the domain experts utilize the perturbation driven analysis to explore and assess the model and interpret the attention mechanism.
+These scenarios are summarized by the domain experts who try to integrate the tool into their workflow.
+
+\subsection{Scenario 1: Interpreting Decision Making Process}
+The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
 %
-These scenarios are summarized by the domain experts who integrated the tool into their model exploration workflow.
-
-\subsection{Scenario 1: Interpretting Model Decision Making Process}
-The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
+Mistake can be made in either of these stages.
 % \shusen{difference in sensitivity among entail natural and contradict relationships}
@@
 
-\subsection{Scenario 2: Which Part of the Model is the Problem?}
+\subsection{Scenario 2: Assess the Model Prediction Stability}
+Utilize input sentence perturbation to assess the overall stability of the prediction
 
-\subsection{Scenario 3: Handcraft Example Exploration}
-Well-know tough examples, such as the Facebook IPO example discussed in Section~\ref{sec:background}.
+\subsection{Scenario 3: What Does It Take to Correct the Prediction?}
+In the previous section, we discussed how we can use forward prediction
 
-\subsection{Scenario 4: Handcraft Example Exploration?}
+\subsection{Scenario 4: Handcraft Example Analysis}
+Well-known tough examples, such as the Facebook IPO example discussed in Section~\ref{sec:background}.
 
+\subsection{Scenario 5: Grammar Structure and Attention}
+Can attention capture grammar structure? Is 
 %\subsection{Is the Prediction Stable?}

### 2018-03-27 src/visPackage/static/components/predictionComponent.js

@@ -71,24 +71,41 @@ class predictionComponent extends baseComponent {
                 .style("alignment-baseline", "middle")
                 .style("pointer-events", "none")
                 .style("font-size", 10);
+            this.legend.append("rect")
+                .attr("class", "legend")
+                .attr("x", -3)
+                .attr("y", 30 - 3)
+                .attr("width", 6)
+                .attr("height", 6)
+                .attr("fill", "lightblue")
+                .style("stroke", "white");
+            this.legend.append("text")
+                .attr("x", 10)
+                .attr("y", 30)
+                .text("Optimized")
+                .style("alignment-baseline", "middle")
+                .style("pointer-events", "none")
+                .style("font-size", 10);
 
             //ground truth
             this.legend.append("rect")
                 .attr("rx", 3)
                 .attr("ry", 3)
                 .attr("x", -10)
-                .attr("y", 25)
+                .attr("y", 40)
                 .attr("width", 20)
                 .attr("height", 15)
                 .attr("stroke", "none")
                 .attr("fill", "lightgreen");
             this.legend.append("text")
                 .attr("x", 12)
-                .attr("y", 32.5)
+                .attr("y", 47)
                 .text("Ground Truth")
                 .style("alignment-baseline", "middle")
                 .style("pointer-events", "none")
                 .style("font-size", 10);
+
+            //prediction update
         }
 
         //entailment
@@ -265,7 +282,7 @@ class predictionComponent extends baseComponent {
             })
             .attr("width", 6)
             .attr("height", 6)
-            .style("fill", "#3F3F3F")
+            .style("fill", "lightblue")
             .style("stroke", "white")
             .style("opacity", 1.0)
             .on("click", (d, i) => {

### 2018-03-27 paper/application.tex
update task

@@
 % \shusen{A full case study that driven by the visualization task and the question associated with them}
-In this section, we discuss application scenarios, in which the domain experts utilize the perturbation driven analysis to explore and assess the model and interpret the attention mechanism.
-These scenarios are summarized by the domain experts who try to integrate the tool into their workflow.
+%In this section, we discuss application scenarios, in which the domain experts utilize the 
+To illustrate how the proposed perturbation-driven exploration tool help the domain experts interpret the neural network model,
+summarized  and interpret the attention mechanism.
+These scenarios are summarized by the domain experts who integrating the proposed tool into their model analysis workflow.
 
 \subsection{Scenario 1: Interpreting Decision Making Process}
+Understanding the decision making process, i.e., why the model make a prediction, is most crucial aspect in model analysis.
 The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
 %
-Mistake can be made in either of these stages.
+%One of the essential task for can be made in either of these stages.
 % \shusen{difference in sensitivity among entail natural and contradict relationships}
@@
 
-\subsection{Scenario 2: Assess the Model Prediction Stability}
+\subsection{Scenario 2: What Does It Take to Correct a Wrong Prediction?}
+In the previous section, we discussed how we can use forward prediction
+
+\subsection{Scenario 3: Assess the Model Prediction Stability}
 Utilize input sentence perturbation to assess the overall stability of the prediction
-
-\subsection{Scenario 3: What Does It Take to Correct the Prediction?}
-In the previous section, we discussed how we can use forward prediction
 
@@
 
-\subsection{Scenario 5: Grammar Structure and Attention}
+\subsection{Scenario 5: Explore Relationship Between Grammar and Attention}
 Can attention capture grammar structure? Is 

### 2018-03-27 paper/task.tex
update task

@@
 
-    \item So far, we focus on how changes in earlier stage of the model affect later stages or final prediction.
-However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction and how would such a modification affect attention.
-    Therefore, thirdly, we want to explore how model should be updated to produce the desirable change of prediction, and how the attention respond to such a change (\textbf{T3}).
+    \item So far, we have focused on how changes in earlier stage of the model affect later stages or the final prediction.
+However, what if the current prediction is wrong, where and how can we apply update to the model to produce correct prediction and how the attention respond to such a change (\textbf{T3}).
+    %Therefore, thirdly, we want to explore how model should be updated to produce the desirable change of prediction, and how the attention respond to such a change (\textbf{T3}).
 \end{itemize}

### 2018-03-28 paper/intro.tex
update intro

@@
   % \item Distill the visualization tasks for making sense of the role of attention in natural language inference (section~\ref{sec:task});
-    \item Introduce the perturbation-driven exploration paradigm for exploring natural language processing models;
+    \item Distill the perturbation-driven exploration paradigm from close examination of how domain experts conduct exploratory analysis on end-to-end NLP neural network models;
 
-    \item Perform error analysis by examining the stability of the predictions under perturbation;
+    \item Present the NLIZE system that enriches such a paradigm by providing an intuitive environment where the domain experts can readily express experiment ideas and obtain instantaneous feedbacks;
+    %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
+    %\item Perform error analysis by examining the stability of the predictions under perturbation;
 
-    \item Enhance the visual encoding of the attention by overlaying sentence linguistic structure to allow grammar-guided simplification;
+    \item Introduce an optimization scheme for correcting a failed prediction based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network.
+    % to minimally update the model to fix a failed prediction, which help reason about the  better understand the re the question about how t
 
-    \item Enable the interrogation of the relationships among input sentences, model internals, and the prediction by interactively exploring how the change in one place affects other parts of the model.
+    \item Enhance the visual encoding of the attention by imposing sentence linguistic structure to allow grammar-guided sentence simplification.
 \end{itemize}

### 2018-03-28 paper/task.tex
update intro

@@
 %
-As a result, the domain experts often rely on exploration centric approach to conduct error analysis and obtain intuition.
+As a result, the domain experts also rely on exploration centric approach to conduct error analysis and obtain intuition.
 
@@
 For many NLP models, the attention information (see Section~\ref{sec:attention}) is essential to infer the mechanism of the model.
-The expert can print out the attention values or generate plots to visualize the alignment between sentences or compare attentions.
+The expert often print out the attention values or generate plots to visualize sentence alignment or compare attention values.
 As the experts explore more variation of similar examples, combined with their domain knowledge, he / she may develop hypotheses about the cause of failures, or ask additional questions, which lead to further experimentation.
+
+In such an exploration workflow, NLP researchers often need to utilize multiple scripts and manually run all the experiments.
+The batch process based approach, is not only time consuming, but also hinders the flow of reasoning which rely on obtaining instantaneous feedbacks, and making many on-the-fly adjustments.
 %
-The requirement for such exploratory analysis meshed nicely with the benefit of interactive visual exploration, in which the user can make adjustment on-the-fly and obtain instantaneous visual feedbacks that encode various model information.
+Therefore, the expert driven exploration process can greatly benefit from the introduction of an interactive visual exploration environment, where the researchers can easily express their experiment ideas and obtain quick visual feedback of the results.
 %
@@
 %Through many rounds of discussions with NLP experts,
-In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
+%In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
 %
-Here, we solidify the visualization tasks to facilitate the exploratory workflow and thought process of the domain experts.
+To support the visual exploratory workflow, we have summarized the following visualization tasks.
 %
 \begin{itemize}
-    \item Firstly, understanding how perturbation (e.g., replacing words with synonymous) of the input affect the prediction is the curial part of error analysis.
-It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input (\textbf{T1}).
+    \item Firstly, we need to design visual representation for the key information the domain experts are interested in, e.g., input sentences, the attention information, prediction results, the overall model pipeline (T1).
+    \item Secondly understanding how perturbation (e.g., replacing words with synonymous) of the input affect the prediction is the curial part of error analysis.
+It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input
+     (\textbf{T1}).
 
     %Understand how attention affect the prediction.
-    \item Secondly, study the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
+    \item Secondly, the user should be able to easily express the perturbation of input sentences, the   the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
     %Study the relationship between model stages (encoder, attention, classifier) and the prediction

### 2018-03-28 paper/task.tex
update task

@@
 Moreover, by introducing new visual encoding and summarization, we can drastically expand the ways domain experts interact with the model, enable exploration options that is not possible before either due to tedious manual operation or lack of communication channels.
+%
+To support the visual exploratory workflow, we need to address the following visualization tasks.
 
+\begin{itemize}
+
+\item To begin with, understanding how perturbation (e.g., replacing words with synonymous) of the input affect the prediction is the curial part of error analysis.
+It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input (\textbf{T1}).
+
+%Understand how attention affect the prediction.
+\item In addition, study the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
+%Study the relationship between model stages (encoder, attention, classifier) and the prediction
+
+\item So far, we focus on how changes in earlier stage of the model affect later stages or final prediction.
+However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction.
+and how would such a modification affect attention (\textbf{T3}).
+% Therefore, thirdly, we want to explore how model should be updated to produce the desirable change of prediction, and how the attention respond to such a change (\textbf{T3}).
+
+\end{itemize}
 %Through many rounds of discussions with NLP experts,
 %In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
+
+%To support the analysis goal and visual exploratory workflow, we have summarized the following visualization tasks.
+
+% \begin{itemize}
+% \item To start with, we need to construct the visual language for communicating the model information to the user, which mean designing visual encoding for key model information, such as attention, the prediction results, as well as input sentences (T1).
+%but also the user interface to convey various perturbation operation (T2);
 %
-To support the visual exploratory workflow, we have summarized the following visualization tasks.
+% \item  In addition, convey the user intend to the underlying computation is the other part of the puzzle.
+% The user should be able to easily express operations such as perturb input sentences, update attention values, as well as re-assign prediction.
+% % the   the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
 %
-\begin{itemize}
-    \item Firstly, we need to design visual representation for the key information the domain experts are interested in, e.g., input sentences, the attention information, prediction results, the overall model pipeline (T1).
-    \item Secondly understanding how perturbation (e.g., replacing words with synonymous) of the input affect the prediction is the curial part of error analysis.
-It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input
-     (\textbf{T1}).
-
-    %Understand how attention affect the prediction.
-    \item Secondly, the user should be able to easily express the perturbation of input sentences, the   the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
-    %Study the relationship between model stages (encoder, attention, classifier) and the prediction
-
-    \item So far, we have focused on how changes in earlier stage of the model affect later stages or the final prediction.
+% \item Finally, to identify the where and how the model change to  update  res we have focused on how changes in earlier stage of the model affect later stages or the final prediction.
 However, what if the current prediction is wrong, where and how can we apply update to the model to produce correct prediction and how the attention respond to such a change (\textbf{T3}).
-    %Therefore, thirdly, we want to explore how model should be updated to produce the desirable change of prediction, and how the attention respond to such a change (\textbf{T3}).
-\end{itemize}
+%
+% \end{itemize}
 %

### 2018-03-28 src/visPackage/NLPtool.py

@@ -4,6 +4,8 @@ import hashlib
 class dependencyTree:
     def __init__(self):
         self.cache = {}
+        ## init the modules
+        # self.getDependencyTree("Who am I .")
 
     def hashSentence(self, sentence):
         # print "sentence:", sentence
@@ -13,7 +15,6 @@ class dependencyTree:
 
     def getDependencyTree(self, sentence):
         # return {}
-        
         hashKey = self.hashSentence(sentence)
         if hashKey in self.cache.keys():
             # print "found:", sentence
@@ -24,7 +25,6 @@ class dependencyTree:
             dependency_parser = StanfordDependencyParser(path_to_jar=path_to_jar, path_to_models_jar=path_to_models_jar)
 
             g = dependency_parser.raw_parse(sentence).next()
-
 
             dep_json = []
 
@@ -39,10 +39,10 @@ class dependencyTree:
                                 dep_json.append([node['address']-1, key, v-1])
 
             self.cache[hashKey] = dep_json
-            
+
             #print '#####################', dep_json
-            
+
             #print self.cache
-            
+
             return dep_json
         #return list(g.triples())

### 2018-03-28 src/visPackage/static/components/predictionComponent.js

@@ -258,7 +258,6 @@ class predictionComponent extends baseComponent {
 
     onUpdateOptimizedBatchPrediction(preds) {
         // console.log(preds);
-
         //draw batch prediction
         this.updatePredictDisplay();
         this.svg.selectAll(".predSquare").remove();

### 2018-03-28 paper/background.tex
Pass through first two sections

@@
 %
-Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from learning algorithm's point of view).
+Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from the learning algorithm's point of view).
 Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
@@
 Recently, Bowman et al.
-introduced a large corpus~\cite{BowmanAngeliPotts2015} for the NLI tasks, which has helped spawn a new wave of effective neural network models for those tasks.
-In this work, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.
+introduced a large corpus~\cite{BowmanAngeliPotts2015} for NLI tasks, which has helped spawn a new wave of effective neural network models for those tasks.
+Here, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.
 
@@
 On the other hand, a majority of recent NLP neural networks share the nature of
-end-to-end model, where the entire model operates as a black-box that takes
+end-to-end models, where the entire model operates as a black-box that takes
 vectorized input and yields a final prediction for a specific task.
@@
 %
-The existence of shared conceptual structures means the proposed tool, although designed for NLI task, can be generalized for a much broader set of applications.
+The existence of shared conceptual structures means the proposed tool, although designed for NLI tasks, can be readily generalized for a much broader set of applications.
 
@@
 Subsequently, the next stage aims at finding alignment between words in the input sequences.
-For the NLI task, this means finding the corresponds between words from the premise sentence to the hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
+For the NLI task, this means finding the correspondance between words from the premise sentence to the hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
 Finally, in the last stage, the alignment information and the encoded vector representations are aggregated and then used as features for a classification network (last part of the end-to-end neural network).
@@
 %As the only interpretable part of the internal state of the network, understanding how attention information 
-Recently, attention has contributed to many strongly performed NLP models
-
-~\cite{parikh2016emnlp},~\cite{rush2015neural},~\cite{yang2016hierarchical},
-~\cite{seo2016bidirectional},~\cite{schwartz2017high}.
+Recently, attention has contributed to many strongly performed NLP models~\cite{parikh2016emnlp,rush2015neural,yang2016hierarchical,seo2016bidirectional,schwartz2017high}.
 
@@
 % \end{itemize}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "paper_entailVis"
+%%% End:

### 2018-03-28 paper/intro.tex
update task
Pass through first two sections

@@
 % What is the obstacle for effectively apply machine learning model
-With the recent advances in neural network model, machine learning has gained unprecedented popularity, and its adaption has permeated many fields of studies.
+Based on some stunning recent advances, machine learning and neural networks base deep learning approaches in particular have gained unprecedented popularity, and have been adopted in a wide variety of scientific applications.
 %
-However, from researchers to practitioners, one often need to overcome many obstacles during the training, debugging, and tuning processes to unleash the full potential of these models.
+However, researchers as well as practitioners often need to overcome many obstacles during the training, debugging, and tuning processes to realize the full potential of these models.
 %
-Interpreting the internal mechanism and analyzing how predictions are made are critical to both the design and deployment of a model.
-More importantly, the ability to pinpoint where and how an error is made and come up with hypotheses for the cause of the error is the key to identifying the limitation and improving upon existing models.
-However, providing meaningful answers to these questions is incredibly challenging and often regarded as impossible by many.
+Interpreting the internal mechanism and analyzing how predictions are made is critical to both the design and deployment of a model.
+More importantly, the ability to pinpoint where and how an error is made and propose hypotheses for the cause of the error is key to identifying the limitations of and improving upon existing models.
+However, providing meaningful answers to these questions is challenging and has been described as impossible by many.
 
-Recently, sizable research has been developed to combat the model interpretability challenges.
-Most notably, the works~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018} on interpreting the convolution neural network (CNN) model from both the machine learning and visualization communities have revealed the enormous potential and immediate benefits of model interpretation.
-At the same time, these works also remind us how little we truly understand about the inner mechanism of these deep neural networks.
+Recently, significant research has been developed to combat the model interpretability challenges.
+Both the machine learning as well as the visualization community have proposed a number of promising techniques aimed at interpreting convolution neural networks (CNN)~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018}.
+At the same time, these approaches also remind us how little we truly understand about the inner mechanism of such deep neural networks.
 
-Compared to image classification task, natural language processing (NLP) systems have innate restrictions (e.g., the discrete nature of words) that make the road to interpretation more treacherous.
+Compared to image classification tasks, natural language processing (NLP) systems have innate restrictions (e.g., the discrete nature of words) that make the road to interpretation even more challenging.
 For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) captures, cannot be readily generalized to natural language.
@@
 % Beside explore the internal states of the model, understand how different parts of the model work together and how one may affect one another is as or if not more important.
-Moreover, despite many recent advances, the majority of the existing techniques study the model as an invariant object, where the model's behaviors are recorded and analyzed in an offline fashion.
+Despite a number of recent advances, the majority of existing techniques study the model as an invariant object, where the model's behaviors are recorded and analyzed in an offline fashion.
 %
-However, the exploratory nature of the model interpretation analysis often leads to many \emph{``what if ...''} type of questions.
+However, the exploratory nature of the model interpretation often leads to many \emph{``what if ...''} type of questions. 
 Such as, what if we perturbed the current input?
@@
 And how would it affect the internal state we care about?
-These types of queries form a natural way to gain understanding and come up with hypotheses of the model mechanisms by \emph{interrogating} how the components of a model interact with each other in a dynamic setting.
+These types of queries form a natural way to gain understanding and develop hypotheses of the model mechanisms by \emph{interrogating} how the components of a model interact with each other in a dynamic setting.
 Hypothetically, we can code specialized experiments for each of these scenarios.
-However, such a process is not only tedious but also ignores the iterative nature of the exploratory analysis.
-Often, these questions are not pre-determined.
+However, such a process is not only tedious but also ignores the iterative nature of the exploratory analysis. Often, these questions are not pre-determined.
 Instead, new exploration paths arise as we investigate and analyze previous observations.
 
-In this work, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and direct online query/optimization of the neural network model.
+Here, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and direct online query/optimization of the neural network model.
 Instead of viewing the models as invariant objects, we approach the interpretability challenge by studying them in a dynamic environment.
@@
 We implement our vision of the perturbation-driven exploration in an interactive visualization system for natural language inference models~\cite{Parikh2016}.
-However, the components of the visualization and the overall paradigm can be readily extended to other NLP tasks, such as question and answer, and text summarization, etc.
+However, the components of the visualization and the overall paradigm can be readily extended to other NLP tasks, such as question and answer, text summarization, etc.
 %
-In the simplest form, the inference task asks the question about whether we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), or if they are contradict with each other (\emph{contradiction}), or whether two sentences talk about different/unrelated things (\emph{neutral}).
-Language inference addresses the fundamental challenge of measuring the semantic similarity of sentences, and is one the core NLP tasks (see detail in Section~\ref{sec:languageInference}).
+In the simplest form, the inference task asks the question about whether \textbf{sentence A} and \textbf{sentence B}: (1) are \emph{entailed} (one can infer \textbf{B} from \textbf{A}; (2) \emph{contradict} (\textbf{B} disagrees with \textbf{A}) or (3) are \emph{neutral} (\textbf{A} and \textbf{B} talk about different/unrelated thins
+% we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), if they contradict with each other (\emph{contradiction}), or whether two sentences talk about different/unrelated things (\emph{neutral}).
+Language inference addresses the fundamental challenge of measuring the semantic similarity of sentences, and is one the core NLP tasks (see Section~\ref{sec:languageInference} for details).
 
@@
 %Such type of exploration is not only essential to interpret the language inference problem, but can also be generalized to other NLP model utilized the attention mechanisms.
-Moreover, we enhanced the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar-guided simplification of the visual representation.
+Moreover, we propose to enhance the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar-guided simplification of the visual representation.
 %
@@
   % \item Distill the visualization tasks for making sense of the role of attention in natural language inference (section~\ref{sec:task});
-    \item Distill the perturbation-driven exploration paradigm from close examination of how domain experts conduct exploratory analysis on end-to-end NLP neural network models;
+    \item A perturbation-driven exploration paradigm derived from close examination of how domain experts conduct exploratory analysis on end-to-end NLP neural network models;
 
-    \item Present the NLIZE system that enriches such a paradigm by providing an intuitive environment where the domain experts can readily express experiment ideas and obtain instantaneous feedbacks;
+    \item The NLIZE system that enriches such a paradigm by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedbacks; 
     %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
@@
 
-    \item Introduce an optimization scheme for correcting a failed prediction based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network.
+    \item An optimization scheme for correcting a failed prediction based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network; and
     % to minimally update the model to fix a failed prediction, which help reason about the  better understand the re the question about how t
 
-    \item Enhance the visual encoding of the attention by imposing sentence linguistic structure to allow grammar-guided sentence simplification.
+    \item A visual encoding of the attention by imposing sentence linguistic structure to allow grammar-guided sentence simplification.
 \end{itemize}
@@
 Neural network models are often referred to as black boxes due to the hard to recognize  difficult to interpret parameter, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships among model inputs, critical internal mechanisms, as well the output predictions.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "paper_entailVis"
+%%% End:

### 2018-03-28 paper/paper_entailVis.tex
Pass through first two sections

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
@@
 \newcommand{\shusen}[1]{\textcolor{red}{[#1]}}
+\newcommand{\taoli}[1]{\textcolor{orange}{[#1]}}
 
@@
 With the recent advances in deep learning, neural network models have obtained state-of-the-art performances for many linguistic tasks in natural language processing.
-The disruptive progress also brings enormous challenges.
-The opaque nature of neural network model leads to hard-to-debug-systems and difficulty interpreting mechanisms.
-In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, and prediction while observing changes in other parts of the pipeline.
-We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states and interpreting and hypothesizing fundamental model mechanisms such as attention.
+However, this rapid progress also brings enormous challenges.
+The opaque nature of neural network model leads to hard-to-debug-systems and difficult to interpret mechanisms.
+Here, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, and prediction while observing changes in other parts of the pipeline.
+We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states and interpret and hypothesize about fundamental model mechanisms such as attention.
 } % end of abstract

### 2018-03-28 paper/relatedWorks.tex
Pass through first two sections

@@
-\section{Related Works}
+\section{Related Work}
 With the increasing demands for model accountability (e.g., what is the evidence for making the prediction) and model fairness (e.g., is the prediction affected by the bias in the training data),
@@
 %In addition, instead of exploring a language model or low-level, the proposed method focus on a specific NLP task, which provide insight on
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "paper_entailVis"
+%%% End:

### 2018-03-28 paper/overview.tex
More small changes

@@
 %
-As illustrated in Fig.~\ref{fig:modelPipeline}, we enables the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences)inside the model, as well as the \emph{perturbation} the prediction (e.g., adjust the prediction by making updates to the model).
+As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences)inside the model, as well as the \emph{perturbation} the prediction (e.g., adjust the prediction by making updates to the model).
 %
-In the following sections, we describe in detail the five major components of the proposed system, namely, sentence view  (Section~\ref{sec:sentence}), attention view (Section~\ref{sec:attention}), prediction view (Section~\ref{sec:prediction}), pipeline view (Section~\ref{sec:pipeline}), all pair summary view (Section~\ref{sec:allPairs}).
+In the following sections, we describe in detail the five major components of the proposed system, namely, the sentence view  (Section~\ref{sec:sentence}), the attention view (Section~\ref{sec:attention}), the prediction view (Section~\ref{sec:prediction}), the pipeline view (Section~\ref{sec:pipeline}), and the all pair summary view (Section~\ref{sec:allPairs}).
 
@@
 % Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "paper_entailVis"
+%%% End:

### 2018-03-28 paper/task.tex
More small changes

@@
 In this section, we examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
-Then, we reify the multitude discussion with domain experts into concrete tasks, which guide the design and implementation of the proposed tool.
+Then, we distill the numerous discussions with domain experts into concrete tasks, which guide the design and implementation of the proposed tool.
 
@@
 %
-As a result, the domain experts also rely on exploration centric approach to conduct error analysis and obtain intuition.
+As a result, the domain experts rely on an exploration centric approach to conduct error analysis and obtain intuition.
 
 There is little one can learn when everything is behaving as expect, therefore,
-observing how model make mistakes under various scenarios is at the center of such a process.
+observing how models make mistakes under various scenarios is at the center of such a process.
 The experts often start with simple failure examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction.
-This exercise help isolate where in the input is likely contributed to the failures.
+This exercise helps isolate where in the input is likely contributing to the failures.
 For many NLP models, the attention information (see Section~\ref{sec:attention}) is essential to infer the mechanism of the model.
-The expert often print out the attention values or generate plots to visualize sentence alignment or compare attention values.
+Experts often print out the attention values or generate plots to visualize sentence alignment or compare attention values.
 As the experts explore more variation of similar examples, combined with their domain knowledge, he / she may develop hypotheses about the cause of failures, or ask additional questions, which lead to further experimentation.
@@
 %
-Therefore, the expert driven exploration process can greatly benefit from the introduction of an interactive visual exploration environment, where the researchers can easily express their experiment ideas and obtain quick visual feedback of the results.
+Therefore, the expert driven exploration process can greatly benefit from the introduction of an interactive visual exploration environment, where the researchers can easily express their hypotheses and obtain quick visual feedback of the results.
 %
-Moreover, by introducing new visual encoding and summarization, we can drastically expand the ways domain experts interact with the model, enable exploration options that is not possible before either due to tedious manual operation or lack of communication channels.
+Moreover, by introducing new visual encodings and summarizations, we can drastically expand the ways domain experts interact with the model, enable exploration options that previously were not possible either due to tedious manual operation or the lack of communication channels.
+
+%Through many rounds of discussions with NLP experts,
+%In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
+%
+To support the visual exploratory workflow, we have summarized the following visualization tasks.
+>>>>>>> More small changes
 %

### 2018-03-28 paper/application.tex
update relate works

@@
 %In this section, we discuss application scenarios, in which the domain experts utilize the 
-To illustrate how the proposed perturbation-driven exploration tool help the domain experts interpret the neural network model,
-summarized  and interpret the attention mechanism.
-These scenarios are summarized by the domain experts who integrating the proposed tool into their model analysis workflow.
+To better illustrate how the proposed perturbation-driven exploration tool helps the domain experts interpret the neural network model, we present five application scenarios, which summarized by the domain experts who integrated the proposed tool into their model analysis workflow.
 
 \subsection{Scenario 1: Interpreting Decision Making Process}
-Understanding the decision making process, i.e., why the model make a prediction, is most crucial aspect in model analysis.
+Understanding why the model make a given prediction is of great interests to the domain expert, 
+since interpreting decision making processing is not only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
+%
 The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.

### 2018-03-28 paper/relatedWorks.tex
update relate works

@@
 \textbf{Model Interpretability.}
-Before one can solve the model interpretability challenge, it worth to define what constitutes an explanation or interpretation of a machine learning model.
-As discussed in ~\cite{Lipton2016, Doshi-Velez2017}, despite the concept of interpretable is inherently subjective, it is still necessary to refine the concept and devise guidelines for approaching model interpretability problems.
-%And as suggested in~\cite{Doshi-Velez2017}
+Before one can solve the model interpretability challenge, it worth to understand what constitutes an explanation for a machine learning model.
+As discussion in~\cite{Lipton2016, Doshi-Velez2017}, there is little consensus on what interpretability is in the context of machine learning.
+A taxonomy is suggested~\cite{Doshi-Velez2017} to promote a more rigorous study on such a subject.
+In the work by Lipton~\cite{Lipton2016}, many philosophical questions related to model interpretability are examined and the study also challenged the commonly held belief that linear models are more interpretable than deep neural networks.
+%
 In machine learning community, one of the most studied areas in model interpretability is the interpretation of convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
 %
-These methods either identify the pattern that maximally activate a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures), or reveal what areas in the input contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
+These methods either identify the pattern that maximally activate a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures), or reveal what areas in the input that contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
 %

### 2018-03-28 paper/application.tex
update mira update

--- 2018-03-27 paper/application.tex
@@
 %In this section, we discuss application scenarios, in which the domain experts utilize the 
-To illustrate how the proposed perturbation-driven exploration tool help the domain experts interpret the neural network model,
-summarized  and interpret the attention mechanism.
-These scenarios are summarized by the domain experts who integrating the proposed tool into their model analysis workflow.
+To better illustrate how the proposed perturbation-driven exploration tool helps the domain experts interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their model analysis workflow.
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{predictStability}
+ \caption{
+Prediction stability assessment. Isolate unstable one
+ }
+\label{fig:pipelineView}
+\end{figure}
+
+\subsection{Scenario 1: Assess the Model Prediction Stability}
+Utilize input sentence perturbation to assess the overall stability of the prediction
 
 \subsection{Scenario 1: Interpreting Decision Making Process}
-Understanding the decision making process, i.e., why the model make a prediction, is most crucial aspect in model analysis.
+Understand how the model arrive at the prediction is the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
+%
 The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
@@
 In the previous section, we discussed how we can use forward prediction
-
-\subsection{Scenario 3: Assess the Model Prediction Stability}
-Utilize input sentence perturbation to assess the overall stability of the prediction
 

### 2018-03-28 src/modelInterface.py

@@ -279,7 +279,8 @@ class modelInterface:
             # 	here, it's gonna be updated w using sgd
             print self.opt
             # just one pass sgd
-            self.pipeline, y = overfit_to_ex(self.opt, self.shared, self.embeddings, self.optim, self.pipeline, ex)
+            self.pipeline = perturb_params(self.opt, self.shared, self.pipeline)
+            # self.pipeline, y = overfit_to_ex(self.opt, self.shared, self.embeddings, self.optim, self.pipeline, ex)
             for i in xrange(interation):
                 # print('epoch {0}'.format(i))
                 m, y = mirafit_to_ex(self.opt, self.shared, self.embeddings, self.optim, self.pipeline, ex, w_start)

### 2018-03-28 src/sentenceGenerator.py

@@ -13,6 +13,8 @@ class sentenceGenerator:
                 toks = l.split()
                 self.train_tokens[toks[0]] = 1
 
+        ### perturb one sentence to preload the nltk ####
+        self.perturbSentence("Who am I.")
         # print "angele:", "angele" in self.train_tokens.keys()
         # print "token count:", len(self.train_tokens.keys())
 

### 2018-03-28 src/visPackage/static/components/evaluationComponent.js

@@ -99,13 +99,13 @@ class evaluationComponent extends baseComponent {
         // var stabilities = data.map(d => d.stability);
         // console.log(stabilities);
         this.histo.setSample(data, d => d.stability);
-        this.histo.setTitle("CorrectRatio");
-        this.scatter.setData(data, ["CorrectRatio", "PerturbCount"],
+        this.histo.setTitle("Stability");
+        this.scatter.setData(data, ["Stability", "PerturbCount"],
             d => [d.stability, d.perturbCount]);
     }
 
     updateScatterplot(data) {
-        this.scatter.setData(data, ["CorrectRatio", "PerturbCount"],
+        this.scatter.setData(data, ["Stability", "PerturbCount"],
             d => [d.stability, d.perturbCount]);
     }
 

### 2018-03-28 src/visPackage/static/components/pipelineComponent.js

@@ -82,13 +82,13 @@ class pipelineComponent extends baseComponent {
 
         //
         this.Cslider = new sliderPlot(this.mode, [50, 50], [70, 15],
-            "C", [1.0, 10.0], 5.0, ".0f");
+            "C", [1.0, 10.0], 2.0, ".0f");
         this.Cslider.bindUpdateCallback(d => {
             this.setData("C_mira", Number(this.Cslider.value));
         });
 
         this.learnRate = new sliderPlot(this.mode, [50, 70], [70, 15],
-            "l_rate", [0.00001, 0.001], 0.0001, ".4f");
+            "l_rate", [0.000001, 0.0001], 0.00001, ".4f");
         this.learnRate.bindUpdateCallback(d => {
             this.setData("learningRate", Number(this.learnRate.value));
         });

### 2018-03-28 paper/application.tex
add figure

@@
  }
-\label{fig:pipelineView}
+\label{fig:predictStability}
 \end{figure}
@@
 
-\subsection{Scenario 1: Interpreting Decision Making Process}
+\subsection{Scenario 1: Examine the Decision Making Process}
+\begin{itemize}
+\item if the prediction look for attention alignment
+\item 
+\end{itemize}
+
 Understand how the model arrive at the prediction is the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
@@
 The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
-%
+
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=0.9\linewidth]{failledEncoding}
+ \caption{
+The prediction is failed due to incorrect alignment. For all the failed case, 
+ }
+\label{fig:failedEncoding}
+\end{figure*}
+
 %One of the essential task for can be made in either of these stages.
@@
 % the generate the correct prediction for the wrong reason
+
+Another
+Does the model arrived at the correct prediction for the wrong reason?
 

### 2018-03-28 src/visPackage/visModule.py

@@ -271,7 +271,7 @@ class textEntailVisModule(visModule):
         dataManager.setData("prediction", pred)
 
         #update other predictions if available
-        self.predictAll()
+        # self.predictAll()
         return True
 
     def attention(self):

### 2018-03-28 paper/application.tex
update 6.1

@@
 %In this section, we discuss application scenarios, in which the domain experts utilize the 
-To better illustrate how the proposed perturbation-driven exploration tool helps the domain experts interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their model analysis workflow.
+To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their model analysis workflow.
+%Here
 
@@
  \caption{
-Prediction stability assessment. Isolate unstable one
+Prediction stability assessment.
+In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (100k examples).
+The user can drill down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a case by case exploration, as illustrated in (d)(e).
+For highly unstable outliers, we often observe the prediction of the original sentences near the decision boundary (e.g., the yellow circle in (f) corresponds to a entailment prediction that is very close to neural), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence).
+%
 }
@@
 \subsection{Scenario 1: Assess the Model Prediction Stability}
-Utilize input sentence perturbation to assess the overall stability of the prediction
+The robustness of the prediction is often the information the researchers wish they know, yet hard measure easily.
+Utilize the automated system input sentence perturbation to assess the overall stability of the prediction.
+As illustrated in Fig.~\ref{fig:predictStability}, we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (100k examples).
+The user can drill down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a case by case exploration, as illustrated in (d)(e).
+For highly unstable outliers, we often observe the prediction of the original sentences near the decision boundary (e.g., the yellow circle in (f) corresponds to a entailment prediction that is very close to neural), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence
 
-\subsection{Scenario 1: Examine the Decision Making Process}
+\subsection{Scenario 2: Examine the Decision Making Process}
 \begin{itemize}
-\item if the prediction look for attention alignment
+\item What alignment the prediction looks for attention alignment
 \item 
@@
 
-Understand how the model arrive at the prediction is the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
+%Hypothesizing
+Interpreting how the model arrive at a prediction is one of the most important goal for the expert driven exploratory analysis.
+%
+
+ first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
 %

### 2018-03-28 src/visPackage/static/components/pipelineComponent.js

@@ -229,11 +229,6 @@ class pipelineComponent extends baseComponent {
         pipeline[index]["state"] = state;
         // console.log("updatePipeline: ", index, state, pipeline);
         this.setData("pipeline", pipeline);
-        // if (this.items) {
-        //     for (var i = 0; this.items.length; i++) {
-        //         this.items[i].setState(states[i] === 0 ? false : true);
-        //     }
-        // }
     }
 
     draw() {

### 2018-03-28 paper/application.tex
update 6.1

@@
 %In this section, we discuss application scenarios, in which the domain experts utilize the 
-To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their model analysis workflow.
-%Here
+To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their analysis workflow.
 
@@
 \centering
-\vspace{-2mm}
+%\vspace{-2mm}
  \includegraphics[width=1.0\linewidth]{predictStability}
@@
 Prediction stability assessment.
-In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (100k examples).
+In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
 The user can drill down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a case by case exploration, as illustrated in (d)(e).
@@
 \subsection{Scenario 1: Assess the Model Prediction Stability}
-The robustness of the prediction is often the information the researchers wish they know, yet hard measure easily.
-Utilize the automated system input sentence perturbation to assess the overall stability of the prediction.
-As illustrated in Fig.~\ref{fig:predictStability}, we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (100k examples).
-The user can drill down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a case by case exploration, as illustrated in (d)(e).
-For highly unstable outliers, we often observe the prediction of the original sentences near the decision boundary (e.g., the yellow circle in (f) corresponds to a entailment prediction that is very close to neural), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence
+The robustness of the prediction is often hard to evaluate, however, they provide valuable information for the researchers to evaluate the model.
+%
+In the proposed work, we approach the prediction robustness from sensitivity analysis point of view.
+The stability of the prediction is measured by how often the predicted labels are altered after small perturbations are applied to the input.
+%
+Compare to other types of input (e.g., image), perturbation of the natural language can be particular tricky, as small alteration of words can drastically change the meaning of the sentence.
+As discussed in Section~\ref{sec:sentence}, we try to maintain semantic of the sentence by only replace words with their synonymous and only replace one word for each pair.
+%
+As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the automated input perturbation and visual interface in the proposed tool, the domain expert can not only examine visual summary of the stability, but also quickly dive into individual examples for case by case analysis.%which system input sentence perturbation to assess the overall stability of the prediction.
+
+By viewing the distribution of the stability in the histogram (Fig.~\ref{fig:predictStability}(a)(b)(c)), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
+%
+We can observe a drastic difference between the stability for entailment predictions compare to the contradiction and neutral ones.
+%
+Such a distinction can be partially explained by how entailment relationship is defined.
+As discussed in the Section~\ref{sec:background}, the relationship is only valid if the concept in premise is more specific than the concept in hypothesis (therefore, you can infer the hypothesis from the premise, but not other way around).
+This means, we may change the entailment relationships simply by replacing nouns and verb by synonymous, whereas, the same does not apply for neutral and contradiction.
+%
+By exploring the inherent sensitivity difference among the three types of relationship, the researcher may consider designing dedicate model mechanism to address the such a disparity.
+
+Beside making overall assess, the proposed tool also allow user to narrow down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a detailed exploration, as illustrated in Fig.~ref{fig:predictStability}(d)(e).
+%
+Through exploring multiple samples (in the entailment category, E/E in Fig.~\ref{fig:summaryView}(a)), the domain experts noticed many highly unstable outliers are from sentence pairs where the prediction is near the decision boundary (e.g., the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence.
+We will try to understand the what is happened inside the model in the following section (see Fig.~\ref{fig:att2pred}).
 
 \subsection{Scenario 2: Examine the Decision Making Process}
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{att2pred}
+ \caption{
+How attention affect prediction.).
+%
+}
+\label{fig:att2pred}
+\end{figure}
+
 \begin{itemize}
-\item What alignment the prediction looks for attention alignment
-\item 
+\item A very young child in a red plaid coat and pink winter hat makes a snowball in a large pile of snow .
+\item A child in a red plaid coat and pink winter hat makes a snowball in a large heap of snow .
 \end{itemize}

### 2018-03-28 paper/application.tex
update 6.3

@@
 % the generate the correct prediction for the wrong reason
-
-Another
 Does the model arrived at the correct prediction for the wrong reason?
 
-\subsection{Scenario 2: What Does It Take to Correct a Wrong Prediction?}
+\subsection{Scenario 3: What Does It Take to Correct a Wrong Prediction?}
 In the previous section, we discussed how we can use forward prediction
 
-\subsection{Scenario 4: Handcraft Example Analysis}
-Well-known tough examples, such as the Facebook IPO example discussed in Section~\ref{sec:background}.
+\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
+Can attention capture grammar structure? Is
 
-\subsection{Scenario 5: Explore Relationship Between Grammar and Attention}
-Can attention capture grammar structure? Is 
+\subsection{Scenario 5: Handcraft Example Analysis}
+To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:background}) that they know most model will have a difficult time making correct inference.
+%
+%The exploration is just started once the prediction result is examined, 
+Often the researchers have a set of "what if..." experiments they would like to run.
+And dependent on the experiment out come, they like will have new questions to ask and try out the different variations or combinations.
+%
+In some way, we can think of such a process as a nature blend of all previously discussed scenario, where the domain experts do not necessarily have specific goal in mind, instead focus on probing around and see if they can find anything interesting and out-of-ordinary behaviors in the model.
+%
+Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures an streamlined exploration experience that free the users from interruption and grunt work, allow them to focus on more productive activity.
+
 %\subsection{Is the Prediction Stable?}

### 2018-03-28 paper/application.tex
update evaluation

@@
 The user can drill down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a case by case exploration, as illustrated in (d)(e).
-For highly unstable outliers, we often observe the prediction of the original sentences near the decision boundary (e.g., the yellow circle in (f) corresponds to a entailment prediction that is very close to neural), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence).
+For highly unstable outliers, we often observe the prediction of the original sentences near the decision boundary (e.g., the yellow circle in (f) corresponds to a entailment prediction that is very close to neural), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``pile'' is replace by ``heap'' in the hypothesis sentence).
 %
@@
 Such a distinction can be partially explained by how entailment relationship is defined.
-As discussed in the Section~\ref{sec:background}, the relationship is only valid if the concept in premise is more specific than the concept in hypothesis (therefore, you can infer the hypothesis from the premise, but not other way around).
+As discussed in the Section~\ref{sec:languageInference}, the relationship is only valid if the concept in premise is more specific than the concept in hypothesis (therefore, you can infer the hypothesis from the premise, but not other way around).
 This means, we may change the entailment relationships simply by replacing nouns and verb by synonymous, whereas, the same does not apply for neutral and contradiction.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% perturb input, attention
 \subsection{Scenario 2: Examine the Decision Making Process}
@@
 
-\begin{itemize}
-\item A very young child in a red plaid coat and pink winter hat makes a snowball in a large pile of snow .
-\item A child in a red plaid coat and pink winter hat makes a snowball in a large heap of snow .
-\end{itemize}
+%Hypothesizing
+Examining how the model arrive at a prediction is not only instrumental for evaluating the model performance but also essential for hypothesizing improvement strategies.
+%
+A model may produce the correct prediction for the wrong reason (or the randomness of ), the prediction may be correct due to luc label provide one way to evaluation model.
+To ensure a model does what it intended to do, we need to answer the questions whether the model arrived at the correct prediction for the wrong reason?
+prediction can mean a number of things
+It is not only the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
 
-%Hypothesizing
-Interpreting how the model arrive at a prediction is one of the most important goal for the expert driven exploratory analysis.
+The three stages (encoder, attention, classifier) work in synergy to produce the prediction.
+%
+Therefore, making sense of the prediction involving understand how different part of the model affect the final prediction.
 %
 
- first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
-%
-The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
+The example discussed in the previous section, 
+\textbf{P}: ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \emph{pile} of snow.''
+\textbf{H}: ``A child in a red plaid coat and pink winter hat makes a snowball in a large \emph{heap} of snow.''
 
@@
 % the generate the correct prediction for the wrong reason
-Does the model arrived at the correct prediction for the wrong reason?
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Scenario 3: What Does It Take to Correct a Wrong Prediction?}
-In the previous section, we discussed how we can use forward prediction
+Once, we get a sense of how prediction are being made, where it went wrong. The next obvious questions are what does it take to correct the wrong prediction. 
+In addition, when we interpreting how decision are made, we always fix the model and make forward pass in the neural network.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
+There is no simple answer to what exactly is the information attention captures.
 Can attention capture grammar structure? Is
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Scenario 5: Handcraft Example Analysis}
-To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:background}) that they know most model will have a difficult time making correct inference.
+To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most model will have a difficult time making correct inference.
 %

### 2018-03-29 paper/application.tex
update 6.2

@@
 
+%Hypothesizing
+Examining how the model arrive at a given conclusion is not only instrumental for evaluating the model performance but also essential for hypothesizing improvement strategies for developing future models.
+
+%%%% are we obtain correct prediction from wrong alignment %%%%%
+As discussed the introduction, the predicted label alone provide limited information to evaluate a model.
+By looking into the model decision making process, we can assess whether the model is behaving as intended.
+For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
+However, since there is only three output labels, it is also likely in some cases the model produce correct predictions due to pure luck with attention that does not make sense (i.e., the important words are mis-align).
+It is also possible that even the alignment is perfect, the model still generate a wrong prediction.
+
+The three stages (encoder, attention, classifier) work in synergy to produce the prediction.
+Therefore, making sense of the prediction involving understand how different part of the model affect the final prediction.
+
+We have noticed some very unusual behavior in the example discussed in the previous section,  where a minor perturbation of the text from \emph{pile} to \emph{heap} lead to drastically change in the prediction (Fig.~\ref{fig:predictStability}(d)).
+Here, we want to make sense of what lead to the failed prediction.
+In this example, the premise \textbf{P} is ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.'', and the original hypothesis \textbf{H1} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{heap} of snow.''.
+The perturbed hypothesis \textbf{H2} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.''
+
+As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see the for the (\textbf{P}, \textbf{H2}) pair, the word \textbf{pile} and \textbf{heap} is not well-aligned (see Fig.~\ref{fig:att2pred}(a)).
+%
+To verify whether the alignment is what contribute to the mis-classification, we can utilize the attention editing functionality in the matrix view (Fig.~\ref{fig:attentionView}) to make the word \textbf{pile} align correctly with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
+%
+In the update prediction view (see Fig.~\ref{fig:att2pred} (d)), we can see the new attention moved the original prediction from neutral toward the entailment (which is the true label) and straddle on the class boundary.
+This is very interesting, as showed in Fig~\ref{fig:predictStability}(d), the original pair (\textbf{P}, \textbf{H1}) has almost identify alignment (not shown in the figure).
+This mean is the model do not strongly believe ``\textbf{pile} of snow'' and ``\textbf{heap} snow'' has the same meaning.
+
 \begin{figure}[htbp]
@@
  \caption{
-How attention affect prediction.).
+How attention affect prediction.
 %
@@
 \end{figure}
-
-%Hypothesizing
-Examining how the model arrive at a prediction is not only instrumental for evaluating the model performance but also essential for hypothesizing improvement strategies.
-%
-A model may produce the correct prediction for the wrong reason (or the randomness of ), the prediction may be correct due to luc label provide one way to evaluation model.
-To ensure a model does what it intended to do, we need to answer the questions whether the model arrived at the correct prediction for the wrong reason?
-prediction can mean a number of things
-It is not only the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
-
-The three stages (encoder, attention, classifier) work in synergy to produce the prediction.
-%
-Therefore, making sense of the prediction involving understand how different part of the model affect the final prediction.
-%
-
-The example discussed in the previous section, 
-\textbf{P}: ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \emph{pile} of snow.''
-\textbf{H}: ``A child in a red plaid coat and pink winter hat makes a snowball in a large \emph{heap} of snow.''
+%%%% hypothesis on which part of model is wrong? %%%%%
 

### 2018-03-29 paper/paper_entailVis.tex
update paper_entailVis Based on chris. feedback

@@
 Here, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, and prediction while observing changes in other parts of the pipeline.
-We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states and interpret and hypothesize about fundamental model mechanisms such as attention.
+We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states, and interpret and form hypothesize about fundamental model mechanisms such as attention.
 } % end of abstract
@@
 During exploration, we can filter through a large number of sentence examples summarized in (A) and select examples of interest displayed in (B).
-The model internal information (attention) is displayed (D) and (E).
+The model internal information (attention) is displayed in (D) and (E).
 The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (F).

### 2018-03-29 paper/intro.tex
update intro based on chris feedback

@@
 %
-However, researchers as well as practitioners often need to overcome many obstacles during the training, debugging, and tuning processes to realize the full potential of these models.
+However, researchers as well as practitioners often needs to overcome many obstacles during the training, debugging, and tuning processes to realize the full potential of these models.
 %
@@
 Both the machine learning as well as the visualization community have proposed a number of promising techniques aimed at interpreting convolution neural networks (CNN)~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, LiuShiLi2017, OlahSatyanarayanJohnson2018, BilalJourablooYe2018}.
-At the same time, these approaches also remind us how little we truly understand about the inner mechanism of such deep neural networks.
+At the same time, these approaches also remind us how little we truly understand about the inner mechanisms of such deep neural networks.
 
@@
 %
-However, the exploratory nature of the model interpretation often leads to many \emph{``what if ...''} type of questions. 
-Such as, what if we perturbed the current input?
+However, the exploratory nature of the model interpretation often leads to many \emph{``what if ...''} types of questions, 
+such as, what if we perturbed the current input?
 Will the prediction be stable?
@@
 % we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), if they contradict with each other (\emph{contradiction}), or whether two sentences talk about different/unrelated things (\emph{neutral}).
-Language inference addresses the fundamental challenge of measuring the semantic similarity of sentences, and is one the core NLP tasks (see Section~\ref{sec:languageInference} for details).
+Language inference addresses the fundamental challenge of measuring the semantic similarity of sentences, and is one of the core NLP tasks (see Section~\ref{sec:languageInference} for details).
 

### 2018-03-29 paper/background.tex
update background

@@
 However, we should note that such a relationship is not necessarily reversible.
-Since the concept ``fruit'' is less restrictive than that of ``apple'', we can not conclude ``Boy ate an apple'' from the statement ``Kid ate fruit''.
-The same logic applies to the hypothesis of ``Boy ate a Fuji apple.'', in which the premise neither imply nor oppose the hypothesis, therefore, their relationship is \emph{neutral}.
+Since the concept ``fruit'' is less restrictive than that of ``apple'', we cannot conclude ``Boy ate an apple'' from the statement ``Kid ate fruit''.
+The same logic applies to the hypothesis of ``Boy ate a Fuji apple.'', in which the premise neither implies nor opposes the hypothesis, and therefore, their relationship is \emph{neutral}.
 %\emph{Contradiction} means the textual of hypothesis opposes that of premise;
@@
 
-At the first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
+At first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
 %
@@
 The literal similarity between ``Electric'' and ``electrified'' may trick a model to predict \textbf{H2} as \emph{entailment}.
-A model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
+A model likely will also fail to understand the link between ``went public'' and ``IPO'', and therefore, mistake \textbf{H1} as \emph{neutral}.
 %
@@
 As we can see in this example, the higher values indicate significant alignments between words.
-The \emph{subject}, \emph{verb}, and \emph{object} between these two sentences are aligned correctly (words, such as ``an'', which has less importance in determine sentence relationship was assigned a lower score).
+The \emph{subject}, \emph{verb}, and \emph{object} between these two sentences are aligned correctly (words, such as ``an'', which has less importance in determining sentence relationship, was assigned a lower score).
 Interestingly, the difference between the subject words does not affect their alignment.
-The classification stage can then utilize this information to determine the subject of the sentence are different, therefore, despite the other part of the sentences are identical, the relationship between the premise and the hypothesis is neutral.
+The classification stage can then utilize this information to determine the subject of the sentence is different, and therefore, despite the other part of the sentences are identical, the relationship between the premise and the hypothesis is neutral.
 

### 2018-03-29 paper/application.tex
fix prediction crash

@@
 \subsection{Scenario 1: Assess the Model Prediction Stability}
-The robustness of the prediction is often hard to evaluate, however, they provide valuable information for the researchers to evaluate the model.
+The robustness of the prediction is often hard to evaluate, however, they provide valuable information for the researchers to better understand the model.
 %
@@
 As discussed in Section~\ref{sec:sentence}, we try to maintain semantic of the sentence by only replace words with their synonymous and only replace one word for each pair.
+As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert can not only examine visual summary of the stability, but also quickly dive into individual examples for case by case analysis.
+
+In Fig.~\ref{fig:predictStability}(a)(b)(c),  %by viewing the distribution of the stability in the histogram
+we compare the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
 %
-As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the automated input perturbation and visual interface in the proposed tool, the domain expert can not only examine visual summary of the stability, but also quickly dive into individual examples for case by case analysis.%which system input sentence perturbation to assess the overall stability of the prediction.
-
-By viewing the distribution of the stability in the histogram (Fig.~\ref{fig:predictStability}(a)(b)(c)), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
-%
-We can observe a drastic difference between the stability for entailment predictions compare to the contradiction and neutral ones.
+We observe a drastic difference between the stability for entailment predictions compare to the contradiction and neutral ones.
 %
@@
 %
-By exploring the inherent sensitivity difference among the three types of relationship, the researcher may consider designing dedicate model mechanism to address the such a disparity.
+The inherent sensitivity difference may motivate domain experts designing dedicate model mechanism to address the such a disparity.
 
-Beside making overall assess, the proposed tool also allow user to narrow down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a detailed exploration, as illustrated in Fig.~ref{fig:predictStability}(d)(e).
+Beside presenting the summary view, the tool also allow user to quickly narrow down the select to single example  by filtering through the histogram and scatterplot (see Fig.~\ref{fig:summaryView}). 
 %
-Through exploring multiple samples (in the entailment category, E/E in Fig.~\ref{fig:summaryView}(a)), the domain experts noticed many highly unstable outliers are from sentence pairs where the prediction is near the decision boundary (e.g., the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence.
+Through exploring multiple samples (in the entailment category, E/E in Fig.~\ref{fig:summaryView}(a)), the domain experts noticed many highly unstable outliers are from sentence pairs where the prediction is near the decision boundary (see Fig.~\ref{fig:predictStability}(e), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
+However, some predictions, such as the one illustrated in Fig.~ref{fig:predictStability}(d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence.
 We will try to understand the what is happened inside the model in the following section (see Fig.~\ref{fig:att2pred}).
@@
 \subsection{Scenario 2: Examine the Decision Making Process}
-
-%Hypothesizing
-Examining how the model arrive at a given conclusion is not only instrumental for evaluating the model performance but also essential for hypothesizing improvement strategies for developing future models.
-
-%%%% are we obtain correct prediction from wrong alignment %%%%%
-As discussed the introduction, the predicted label alone provide limited information to evaluate a model.
-By looking into the model decision making process, we can assess whether the model is behaving as intended.
-For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
-However, since there is only three output labels, it is also likely in some cases the model produce correct predictions due to pure luck with attention that does not make sense (i.e., the important words are mis-align).
-It is also possible that even the alignment is perfect, the model still generate a wrong prediction.
-
-The three stages (encoder, attention, classifier) work in synergy to produce the prediction.
+The predicted label alone provide limited information, often the domain experts want to know how does the model arrive at the conclusion. And if the prediction is incorrect where does the error occur.
+%
+Examining the decision making process is not only instrumental for evaluating the model performance but also essential for hypothesizing improvement strategies for developing future models.
+%
+In the NLI model, the three stages (encoder, attention, classifier) work in synergy to produce the prediction.
 Therefore, making sense of the prediction involving understand how different part of the model affect the final prediction.
 
-We have noticed some very unusual behavior in the example discussed in the previous section,  where a minor perturbation of the text from \emph{pile} to \emph{heap} lead to drastically change in the prediction (Fig.~\ref{fig:predictStability}(d)).
+In the previous section, we have noticed some very unusual behavior, where a minor perturbation of the text from \emph{pile} to \emph{heap} lead to drastically change in the prediction (Fig.~\ref{fig:predictStability}(d)).
 Here, we want to make sense of what lead to the failed prediction.
@@
  \caption{
-How attention affect prediction.
+Editing the original attention (a) to correctly align the word "heap" with "pile" as shown in (b) (these two words are highlight in orange).  
+The change of attention lead to change of prediction from neutral to the class boundary between neutral and entialment.
 %
@@
 \end{figure}
+
+%%%% are we obtain correct prediction from wrong alignment %%%%%
+%By looking into the model decision making process, we can assess whether the model is behaving as intended.
+For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
+However, since there is only three output labels, it is also likely in some cases the model produce correct predictions due to pure luck with attention that does not make sense (i.e., the important words are mis-align).
+It is also possible that even the alignment is perfect, the model still generate a wrong prediction.
+
 %%%% hypothesis on which part of model is wrong? %%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scenario 5: Handcraft Example Analysis}
+\subsection{Scenario 5: Handcraft Example Exploration}
 To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most model will have a difficult time making correct inference.
@@
 %The exploration is just started once the prediction result is examined, 
-Often the researchers have a set of "what if..." experiments they would like to run.
-And dependent on the experiment out come, they like will have new questions to ask and try out the different variations or combinations.
+Often the researchers have a set of experiments they plan test, from which they likely develop new hypothesis for further experiments.
 %
-In some way, we can think of such a process as a nature blend of all previously discussed scenario, where the domain experts do not necessarily have specific goal in mind, instead focus on probing around and see if they can find anything interesting and out-of-ordinary behaviors in the model.
+In some way, we can think of such a process as a nature blend of all previously discussed scenarios.
+However,  instead with specific analysis goal in mind, the domain experts focus on probing around and see if they can find anything interesting or out-of-ordinary behaviors in the model.
 %
-Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures an streamlined exploration experience that free the users from interruption and grunt work, allow them to focus on more productive activity.
+Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures an streamlined exploration experience that free the users from interruption and tedious grunt work, allow them to focus on more productive activity.
 

### 2018-03-29 paper/implementation.tex
fix prediction crash

--- 2018-03-26 paper/implementation.tex
@@
 \label{sec:implementation}
+We design the tool with flexibility and extensibility in mind.
+One of the key objectives is to allow easy integration with existing NLP workflow.
+Therefore, instead of implementing the tool as a standalone application, we encapsulate the visualization functionality as a python library, in which the behavior of the visual interaction (e.g., once prediction button is pressed what should be the prediction result) is defined in python using existing model in the expert's workflow.
+Also, due to the separation between the visualization and the underlying model computation, we can readily adapt different models or the same model with different configurations or training.
+
+To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their models.
+The code (consists only a few lines of code) use to create the visualization in this paper is included in appendix B.
+%
+The NLP model is implemented in python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
+The visual elements are implemented in javascript using \emph{D3.js} library , the python server act as glue between the javascript visualization and the \emph{pytorch} model.

### 2018-03-29 paper/prediction.tex
fix prediction crash

@@
 \label{sec:prediction}
-For a given sentence pair, the model predicts a discrete probability distribution of the three labels (neutral, contradict, and entailment).
+For a given sentence pair, the model predicts a discrete probability distribution of the three labels (neutral, contradiction, and entailment).
 %
 In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle. 
+Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defines a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction and entailment, respectively.
+The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.
 In the triangle, the distinctly colored background indicates the regions corresponds to different labels.

### 2018-03-29 src/visPackage/static/components/attentionComponent.js

@@ -209,7 +209,10 @@ class attentionComponent extends baseComponent {
                 break;
 
             case "currentPair":
-                let pair = msg["data"]["data"]["sentences"];
+                let pair = msg["data"]["data"][
+                    "sentences"
+                ];
+                // console.log("pair", pair);
 
                 if (this.oldPair) {
                     //clear the current dependency
@@ -233,7 +236,7 @@ class attentionComponent extends baseComponent {
 
                 this.srcWords = pair[0].match(/\S+/g);
                 this.targWords = pair[1].match(/\S+/g);
-                this.oldPair = pair.slice();
+                this.oldPair = JSON.parse(JSON.stringify(pair));
                 break;
 
             case "attentionDirection":

### 2018-03-29 src/visPackage/static/components/pipelineComponent.js

@@ -240,7 +240,7 @@ class pipelineComponent extends baseComponent {
 
             this.items = [];
             var pipelineData = this.data["pipeline"];
-            console.log(pipelineData);
+            // console.log(pipelineData);
 
             // if (this.items === undefined) {
             var len = pipelineData.length;

### 2018-03-29 src/visPackage/static/components/predictionComponent.js

@@ -414,23 +414,25 @@ class predictionComponent extends baseComponent {
                 })
                 //   .style("opacity", (d,i)=>{if (i==0) return "1.0"; else return "0.5";})
                 .on("click", (d, i) => {
+                    // console.log(d);
                     if (this.data["allSourceSens"] !== undefined) {
                         var source, target;
                         if (this.data["allSourceSens"])
                             source = this.data["allSourceSens"][d[3]];
                         else
-                            source = this.data["originalPair"][0];
+                            source = this.data["currentPair"][0];
 
                         if (this.data["allTargetSens"])
                             target = this.data["allTargetSens"][d[4]];
                         else
-                            target = this.data["originalPair"][1];
+                            target = this.data["currentPair"][1];
                         this.data["currentPair"]["sentences"] = [
                             source,
                             target
                         ];
                         //update the pair
-                        console.log("update pair/att");
+                        // console.log("update pair/att", this.data[
+                        // "allSourceSens"]);
                         this.setData("currentPair", this.data[
                             "currentPair"]);
 
@@ -490,7 +492,8 @@ class predictionComponent extends baseComponent {
             var w = 20;
             var h = 15;
 
-            var g = this.svg.append("g").attr("id", "reassignPredict");
+            var g = this.svg.append("g").attr("id",
+                "reassignPredict");
 
             var entailRect = g.append("g");
 
@@ -514,7 +517,8 @@ class predictionComponent extends baseComponent {
                     that.drawCurrentAssignedPred();
                 })
                 .on("mouseout", function(d) {
-                    d3.select(this).attr("fill", "lightgrey");
+                    d3.select(this).attr("fill",
+                        "lightgrey");
                     that.reassignedPred = undefined;
                     that.drawCurrentAssignedPred();
                 })
@@ -541,7 +545,8 @@ class predictionComponent extends baseComponent {
                     that.drawCurrentAssignedPred();
                 })
                 .on("mouseout", function(d) {
-                    d3.select(this).attr("fill", "lightgrey");
+                    d3.select(this).attr("fill",
+                        "lightgrey");
                     that.reassignedPred = undefined;
                     that.drawCurrentAssignedPred();
                 })
@@ -569,7 +574,8 @@ class predictionComponent extends baseComponent {
                     that.drawCurrentAssignedPred();
                 })
[…]

### 2018-03-29 src/visPackage/visModule.py

@@ -40,14 +40,19 @@ exampleData = [
     "pred": "entailment"
 },{
     "index":3,
-    "src": "<s> This church choir sings to the masses as they sing joyous songs from the book at a church .",
-    "targ": "<s> The church has cracks in the ceiling .",
+    "src": "<s> This church choir sings to the masses as they sing joyous songs from the book at a church .\n",
+    "targ": "<s> The church has cracks in the ceiling .\n",
     "pred": "neutral"
 },{
     "index":4,
-    "src": "<s> A woman with a green headscarf , blue shirt and a very big grin .",
-    "targ": "<s> The woman is young .",
+    "src": "<s> A woman with a green headscarf , blue shirt and a very big grin .\n",
+    "targ": "<s> The woman is young .\n",
     "pred": "neutral"
+},{
+    "index":5,
+    "src": "<s> A very young child in a red plaid coat and pink winter hat makes a snowball in a large pile of snow .\n",
+    "targ": "<s> A child in a red plaid coat and pink winter hat makes a snowball in a large pile of snow .\n",
+    "pred": "entailment"
 }
 ]
 pipelineState = [{

### 2018-03-29 paper/relatedWorks.tex

@@
 \section{Related Work}
-With the increasing demands for model accountability (e.g., what is the evidence for making the prediction) and model fairness (e.g., is the prediction affected by the bias in the training data),
-the interpretability of the machine learning model held significant implications.
-As a result, a wealth of research has been developed that focused on the explanation and interpretation of neural network models from both machine learning and visualization community.
+With the increasing demands for model accountability (e.g., what is the evidence for making the prediction?) and model fairness (e.g., is the prediction affected by the bias in the training data),
+the interpretability of the machine learning model has significant implications.
+As a result, a wealth of research has been developed that focuses on the explanation and interpretation of neural network models by both the machine learning and visualization communities.
 
@@
 %
-In machine learning community, one of the most studied areas in model interpretability is the interpretation of convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
+In the machine learning community, one of the most studied areas in model interpretability is the interpretation of the convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
 %
-These methods either identify the pattern that maximally activate a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures), or reveal what areas in the input that contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
+These methods either identify the pattern that maximally activates a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures?), or reveals what areas in the input that contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
 %
-Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which make them applicable to different applications.
-In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understanding snapshot of the classifier near a specific input.
+Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications.
+In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understand snapshot of the classifier near a specific input.
 %
@@
 %which is vitally important for making sense of the inner works of a model, 
-To avoid similar limitation, the proposed system enabled direct access and manipulation of the internal of the model.
+To avoid similar limitations, the proposed system enables direct access and manipulation of the internals of the model.
 
 \textbf{Visual Exploration of Neural Network Models.}
-Due to the effectiveness of exploring complex relationships, visualization has long been adopted for interpreting neural network model~\cite{TzengMa2005}.
-Recently, the increasing demand for interpretability for deep neural network model motivate the introduction of many visualization works that dedicated to the neural network models.
+Due to the effectiveness of exploring complex relationships, visualization has long been adopted for interpreting neural network models~\cite{TzengMa2005}.
+Recently, the increasing demand for interpretability for deep neural network models has motivated the introduction of many visualization works that are dedicated to neural network models.
 % The classification~\cite{KrausePererNg2016}
-The Prospector~\cite{KrausePererNg2016} provided a model agnostic approach for analyzing and interpreting predictions via an interactive visual interface.
+The Prospector~\cite{KrausePererNg2016} provides a model agnostic approach for analyzing and interpreting predictions via an interactive visual interface.
 %
-In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzed classification errors in convolutional neural networks (CNN) and answered the question on whether class hierarchy is learned in the network.
+In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzed classification errors in convolutional neural networks (CNN) and answered the question of whether class hierarchy is learned in the network.
 %
-The DeepEyes~\cite{Pezzotti2018} focused on the analyzing the training process of CNN so that they can provide design guideline to the deep neutral network architect.
+The DeepEyes~\cite{Pezzotti2018} focused on analyzing the training process of CNN, which provides domain experts design guideline of the deep neutral network architecture.
 %
-The ActiVis~\cite{KahngAndrewsKalro2018} introduced an interactive system tailored for tuning industry-scale neural network in Facebook.
+The ActiVis~\cite{KahngAndrewsKalro2018} introduced an interactive system tailored for tuning industry-scale neural networks in Facebook.
 Finally, Liu et al.~\cite{LiuShiCao2018} presented a visualization tool for understanding the often challenging training process of deep generative models.
@@
 
-\textbf{NLP Models Visualization.}
-Compare to the multitude of research for making sense of convolutional neural networks, relatively fewer works have been dedicated to neural language processing models.
+\textbf{Visualization Of NLP Models.}
+Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studys have been dedicated to neural language processing models.
 %
@@
 % There is many unresolved challenges and the
-The early work on character level recurrent network~\cite{KarpathyJohnson2015} demonstrates the effectiveness of the hidden state in capturing the unique pattern in the training text.
-The compositionality (i.e., build the meaning of a sentence from the meaning of words and phrases) exhibited in neural network linguistic models are examined by utilizing techniques inspired by model interpretability techniques in computer vision by Li et al.
-~\cite{LiChenHovy2015},
-In the RNNVis~\cite{MingCaoZhang2017} work, the Ming et al. visualize the hidden state units in a recurrent neural network based on their expected responses to model input.
-The RNNbow~\cite{CashmanPattersonMosca2017} system help domain experts understand how the model is trained by visualizing the backpropagation gradient information.
+The early work on character-level recurrent networks~\cite{KarpathyJohnson2015} demonstrates the effectiveness of the hidden state in capturing the unique pattern in the training text.
+The compositionality (i.e., build the meaning of a sentence from the meaning of words and phrases) exhibited in neural network linguistic models is examined by utilizing techniques inspired by model interpretability techniques in computer vision by Li et al.
+~\cite{LiChenHovy2015}.
+In the RNNVis~\cite{MingCaoZhang2017} work, Ming et al. visualize the hidden state units in a recurrent neural network based on their expected responses to model input.
+The RNNbow~\cite{CashmanPattersonMosca2017} system helps domain experts understand how the model is trained by visualizing the backpropagation gradient information.
 The LSTMvis~\cite{StrobeltGehrmannPfister2018} work employs a line plot style visual encoding to represent the time varying hidden states of the recurrent neural network.
@@
 
-All of the previously discussed works either focus on the training process or examine the trained model as a fixed object.
+All the previously discussed works either focus on the training process or examine the trained model as a fixed object.
 In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that is not possible before.

### 2018-03-29 paper/overview.tex
update overview

@@
 \section{NLIZE System}
-In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze'', see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-3}).
+In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-3}).
 %
-As discussed in the task analysis, the experts often analyze and obtain intuition about the model by studying how altering one part of the model affect other stages of the pipeline.
+As discussed in the task analysis, the experts often analyze and obtain intuition about the model by studying how altering one part of the model affects other stages of the pipeline.
 %
-Such a process can be generalized as the perturbation-driven paradigm, which is used as guiding principal for designing the proposed tool.
+Such a process can be generalized as the perturbation-driven paradigm, which is used as a guiding principal for designing the proposed tool.
 %
-As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences)inside the model, as well as the \emph{perturbation} the prediction (e.g., adjust the prediction by making updates to the model).
+As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (e.g., adjust the prediction by making updates to the model).
 %
@@
  Perturbation-driven exploration of the natural language inference model.
- In the proposed tool, we enables the interrogation of the relationship between different components of the model via the perturbation-based analysis.
+ In the proposed tool, we enable the interrogation of the relationship between different components of the model via the perturbation-based analysis.
  %
- The user can perturb the of the input sentence (i.e., replace words with synonymous), perturb the attention (i.e., alter the soft alignment between sentences), and perturb the prediction (i.e., adjust the prediction by making updates to the model).
+ The user can perturb the input sentences (i.e., replace words with synonymous), perturb the attention (i.e., alter the soft alignment between sentences), and perturb the prediction (i.e., adjust the prediction by making updates to the model).
 }

### 2018-03-29 paper/task.tex
update 6.1

@@
 \label{sec:task}
-Identify the analysis goals and the corresponding visualization tasks is the first yet significant step in designing a useful tool.
+Identifying the analysis goals and the corresponding visualization tasks is the first significant step in designing a useful tool.
 In this section, we examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
@@
 
-During our long-term collaboration with NLP experts, we have conducted extensive discussion to understand the common approach employed by researcher for assessing the behavior of a model.%
-The prediction accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model, however, the accuracy number alone does not provide the full story.
-For example, the model may produce correct predictions for the ``wrong'' reasons (e.g., pickup unintended pattern in the training data that can not be generalized in real word scenarios).
+During our long-term collaboration with NLP experts, we have conducted extensive discussions to understand the common approach employed by researcher for assessing the behavior of a model.%
+The predictive accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model; however, the accuracy number alone does not provide the full story.
+For example, the model may produce correct predictions for the ``wrong'' reasons (e.g., pick up an unintended pattern in the training data that cannot be generalized in real-word scenarios).
 %
-As a result, the domain experts rely on an exploration centric approach to conduct error analysis and obtain intuition.
+As a result, the domain experts rely on an exploration-centric approach to conduct error analysis and obtain intuition.
 
-There is little one can learn when everything is behaving as expect, therefore,
+There is little one can learn when everything is behaving as expected, and therefore,
 observing how models make mistakes under various scenarios is at the center of such a process.
 The experts often start with simple failure examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction.
-This exercise helps isolate where in the input is likely contributing to the failures.
+This exercise helps isolate where in the input likely contribute to the failures.
 For many NLP models, the attention information (see Section~\ref{sec:attention}) is essential to infer the mechanism of the model.
 Experts often print out the attention values or generate plots to visualize sentence alignment or compare attention values.
-As the experts explore more variation of similar examples, combined with their domain knowledge, he / she may develop hypotheses about the cause of failures, or ask additional questions, which lead to further experimentation.
+As the experts explore more variation of similar examples, combined with their domain knowledge, they may develop hypotheses about the cause of failures, or ask additional questions that lead to further experimentation.
 
@@
 %
-To support the visual exploratory workflow, we have summarized the following visualization tasks.
->>>>>>> More small changes
-%
 To support the visual exploratory workflow, we need to address the following visualization tasks.
@@
 
-\item To begin with, understanding how perturbation (e.g., replacing words with synonymous) of the input affect the prediction is the curial part of error analysis.
-It not only measures the prediction sensitivity, but also help reveal the potential source of the errors in the input (\textbf{T1}).
+\item To begin with, understanding how perturbation (e.g., replacing words with synonymous) of the input affects the prediction is the crucial part of error analysis.
+It not only measures the prediction sensitivity, but also helps reveal the potential source of the errors in the input (\textbf{T1}).
 
 %Understand how attention affect the prediction.
-\item In addition, study the role and mechanism of attention by examine how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
+\item In addition, we study the role and mechanism of attention by examining how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
 %Study the relationship between model stages (encoder, attention, classifier) and the prediction
 
-\item So far, we focus on how changes in earlier stage of the model affect later stages or final prediction.
+\item So far, we focus on how changes in earlier stage of the model affect later stages or the final prediction.
 However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction.

### 2018-03-29 paper/sentence.tex
update sentence.tex

@@
 %
-To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces \emph{nouns} and \emph{verbs} by their synonymous in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
+To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces \emph{nouns} and \emph{verbs} by their synonyms in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
 %
-When the perturbation is applied to either of the sentences, the replaced words are highlighted in blue (see Fig~\ref{fig:modelPipeline}(e) ) to signal the modification made to the original sentence.
+When the perturbation is applied to either of the sentences, the replaced words are highlighted in blue (see Fig.~\ref{fig:modelPipeline}(e) ) to signal the modification made to the original sentence.
 
@@
 
-At the top left of the view, the two controls \emph{Predict} and \emph{Predict All} (a) correspond to predicting the currently displayed sentence pairs and predict all combinations of perturbed premise and hypothesis, respectively.
+At the top left of the view, the two controls \emph{Predict} and \emph{Predict All} (a) correspond to predicting the currently displayed sentence pairs and predict all combinations of perturbed premises and hypotheses, respectively.
 %
-To avoid the situation where both sentences are perturbed, we ensure that only one perturbation per sentence pair (i.e., we use original premise if the hypothesis is perturbed, or use original hypothesis if the premise is perturbed).
+To avoid the situation where both sentences are perturbed, we ensure only one perturbation per sentence pair (i.e., we use the original premise if the hypothesis is perturbed, or use the original hypothesis if the premise is perturbed).
 %%% sentence perturbation %%%%
-The previous explored original sentences are stored in the dropdown list (see Fig.~\ref{fig:sentenceView}(b)) that allow the user to revisit examined examples.
-Also, the user can type any sentences or modified existing text in the text areas (Fig.~\ref{fig:sentenceView}(c)(d)) to accommodate user defined input.
+The previously explored original sentences are stored in the dropdown list (see Fig.~\ref{fig:sentenceView}(b)) that allow the user to revisit examined examples.
+Also, the user can type any sentences or modified existing text in the text areas (Fig.~\ref{fig:sentenceView}(c)(d)) to accommodate user-defined input.
 

### 2018-03-29 paper/application.tex

@@
 \subsection{Scenario 2: Examine the Decision Making Process}
-The predicted label alone provide limited information, often the domain experts want to know how does the model arrive at the conclusion. And if the prediction is incorrect where does the error occur.
+The predicted label alone provide limited information.
+Often, domain experts want to know how does the model arrive at such a conclusion.
+And if the prediction is incorrect, where does the error occur in the model?
 %
@@
 In the NLI model, the three stages (encoder, attention, classifier) work in synergy to produce the prediction.
-Therefore, making sense of the prediction involving understand how different part of the model affect the final prediction.
+Therefore, making sense of the prediction involves understanding how different parts of the model affect the final prediction.
 
-In the previous section, we have noticed some very unusual behavior, where a minor perturbation of the text from \emph{pile} to \emph{heap} lead to drastically change in the prediction (Fig.~\ref{fig:predictStability}(d)).
+In the previous section, we have noticed some unexpected behavior, where a minor perturbation of the text from \emph{pile} to \emph{heap} lead to change in the final prediction label (Fig.~\ref{fig:predictStability}(d)).
 Here, we want to make sense of what lead to the failed prediction.
-In this example, the premise \textbf{P} is ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.'', and the original hypothesis \textbf{H1} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{heap} of snow.''.
-The perturbed hypothesis \textbf{H2} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.''
+In this particular example, the premise \textbf{P} is ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.'', and the original hypothesis \textbf{H1} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.''.
+The perturbed hypothesis \textbf{H2} replaced the word \textbf{pile} with \textbf{heap}.
 
-As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see the for the (\textbf{P}, \textbf{H2}) pair, the word \textbf{pile} and \textbf{heap} is not well-aligned (see Fig.~\ref{fig:att2pred}(a)).
+As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair, the word \textbf{pile} and \textbf{heap} is not well-aligned (see Fig.~\ref{fig:att2pred}(a)).
 %
-To verify whether the alignment is what contribute to the mis-classification, we can utilize the attention editing functionality in the matrix view (Fig.~\ref{fig:attentionView}) to make the word \textbf{pile} align correctly with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
+To verify whether the alignment is what contribute to the misclassification, the domain expert utilize the attention editing functionality in the matrix view (Fig.~\ref{fig:attView}) to make the word \textbf{pile} align with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
 %
-In the update prediction view (see Fig.~\ref{fig:att2pred} (d)), we can see the new attention moved the original prediction from neutral toward the entailment (which is the true label) and straddle on the class boundary.
-This is very interesting, as showed in Fig~\ref{fig:predictStability}(d), the original pair (\textbf{P}, \textbf{H1}) has almost identify alignment (not shown in the figure).
-This mean is the model do not strongly believe ``\textbf{pile} of snow'' and ``\textbf{heap} snow'' has the same meaning.
+In the update prediction view (see Fig.~\ref{fig:att2pred} (d)), we can see the editing of attention lead to changes in prediction.
+The original prediction moved from neutral toward the entailment (which is the true label) and straddle on the class boundary.
+However, the correct alignment does not full fix the prediction problem as the original pair (\textbf{P}, \textbf{H1}) is clearly predicted as \emph{entailment} (as showed in Fig~\ref{fig:predictStability}(d)).
+%
+Interestingly, the original pair's attention is almost identical to the edited attention (the comparison is not shown in the figure).
+Such an observation means that the model do not strongly believe ``\textbf{heap} of snow'' and ``\textbf{pile} snow'' has the same meaning, which indicate the potential issue with encoder or word embedding.
 
@@
 
+\shusen{Example where the prediction is correct but the alignment is wrong}
 %%%% are we obtain correct prediction from wrong alignment %%%%%

### 2018-03-29 paper/attention.tex
update attention

@@
 Intuitively, the attention captures the alignment of words between input sentences.
-For the NLI model examined in this work, the attention is represented as a matrix, in which the entries in the $i^{th}$ row corresponds to the probabilities of words in the hypotheses align to the $i^{th}$ word in the premise.
+For the NLI model examined in this work, the attention is represented as a matrix, in which the entries in the $i^{th}$ row correspond to the probabilities of words in the hypotheses aligned to the $i^{th}$ word in the premise.
 
@@
 In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-The color of rectangle text block encodes the sum of all edge values connect to it (darker shade of blues correspond to higher values).
+The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
 %
-The graph view is good for highlighting the most dominate alignments.
-However, if many attention values are high, the edges may become cluttered lead to less effective visualization.
+The graph view is good for highlighting the most dominant alignments.
+However, if many attention values are high, the edges may become cluttered, leading to less effective visualization.
 Also, if the sentence structures between premise and hypothesis are drastically different, we are likely to see the prominent edges cross each other, which can also lead to confusing and misleading visual patterns.
 
-The matrix attention view (Fig.~\ref{fig:attentionVis}(b)), despite being more verbose and less efficient in highlighting the dominant alignment, do not have similar shortcomings.
-Together, they complement each other and provide the same information from different perspectives.
-As illustrated by the pink arrow line, we can see how the same attention value is visualization in both the graph and the matrix view.
-To help the user recognize the correspondence during the exploration, we enable the linkage between highlight actions in both views.
+The matrix attention view (Fig.~\ref{fig:attentionVis}(b)), despite being more verbose and less efficient in highlighting the dominant alignment, does not have similar shortcomings.
+Together, the graph and matrix views complement each other and provide the same information from different perspectives.
+As illustrated by the pink arrow line, we can see how the same attention value is visualized in both the graph and the matrix view.
+To help the user recognize the correspondence during the exploration, we enable the linkage between highlighted actions in both views.
 
@@
 The attention matrix view is the most suitable place to conduct the edit operation since it provides a direct mapping of attention value.
-As we can see in Fig.~\ref{fig:attentionVis}(c), when a user clicks the cell of the matrix, a sider will pop up for customizing the attention value (as the user edit the value, each row is automatically normalized).
+As we can see in Fig.~\ref{fig:attentionVis}(c), when a user clicks the cell of the matrix, a sider will pop up for customizing the attention value (as the user edits the value, each row is automatically normalized).
 %
@@
 
-Even though the attention does not explicitly encode any grammar, they often highlight essential words in the sentence structure.
+Even though the attention does not explicitly encode any grammar, it often highlights essential words in the sentence structure.
 %
@@
 %
-Since the dependency tree encodes the word importance information in a hierarchical matter, it is very suitable for sentence simplification task.
+Since the dependency tree encodes the word importance information in a hierarchical matter, it is very suitable for sentence simplification tasks.
 Therefore, we utilize the grammar dependency tree to simplify the attention representations to combat the visual clutter when examining long sentences (see Fig.~\ref{fig:attentionVis}(d)).
-A simplfication example is show in  Fig.~\ref{fig:attentionVis}(d)(e)(f).
+A simplification example is shown in  Fig.~\ref{fig:attentionVis}(d)(e)(f).
 

### 2018-03-29 paper/prediction.tex
update prediction

@@
 The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.
-In the triangle, the distinctly colored background indicates the regions corresponds to different labels.
-The prediction result for the original sentence pair is represented by the larger yellow circle, whereas smaller grey circles illustrate the perturbed sentence pairs.
+In the triangle, the distinctly colored background indicates the regions that correspond to different labels.
+The prediction result for the original sentence pair is represented by the larger yellow circle, whereas the smaller gray circles illustrate the perturbed sentence pairs.
 A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
@@
 To perturb the prediction (\textbf{T3}), we need a way to communicate the reassignment of the predicted label.
-As illustrated in Fig.~\ref{fig:predictionView}(b), we integrate such operation in the prediction view.
-When press and drag the prediction (represented as a circle), the user is presented with the three options (E, N, C) correspond to the labels.
+As illustrated in Fig.~\ref{fig:predictionView}(b), we integrate such an operation in the prediction view.
+When pressing and dragging the prediction (represented as a circle), the user is presented with the three options (E, N, C) corresponding to the labels.
 When the user hovers on one of the options, a dotted line is shown to indicate the newly assigned label.

### 2018-03-29 paper/pipeline.tex
update pipeline

@@
 \label{sec:pipeline}
-Pipeline view provides a direct visual representation of the three stages (encoder, attention, classifier) of the model.
+The Pipeline view provides a direct visual representation of the three stages (encoder, attention, classifier) of the model.
 In the proposed tool, we allow the model parameter to be updated (via an optimization) to correct a prediction error (\textbf{T3}).
-The pipeline view, by visualizing the aggregated gradient distribution, informs the user on the how each stage of the model responses to the optimization.
+The pipeline view, by visualizing the aggregated gradient distribution, informs the user about how each stage of the model responds to the optimization.
 
 There are many ways to update the model to correct a prediction.
-A simple way to achieve it is applying standard backpropagation that overfits to the example.
+A simple way to is by applying standard backpropagation that overfits to the example.
 However, without any constraint, the update step may alter the model in unexpected ways.
 % \shusen{what is the benefit of using mira?}
-Instead, we adopt the same idea in \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the L2-norm of the parameter change.
+Instead, we adopt the same idea in \emph{margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the L2-norm of the parameter change.
 Therefore, in the proposed tool, we obtain the target parameters by the following:
@@
 \end{equation}
-where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural model, $\mathbf{W}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the parameters to update, and $C$ is the weighting term, which determines whether we intended to emphasis more on obtaining better fitting or deviating less from the original model.
+where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural model, $\mathbf{W}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the parameters to update, and $C$ is the weighting term, which determines whether we intended to emphasize more on obtaining better fitting or deviating less from the original model.
 Due to the nonconvex nature of the neural networks, we use SGD to optimize the above combined loss function.
 %
-Under this formation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
+With this formation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
 
-As illustrated in Fig.~\ref{fig:pipelineView},
-the optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a).
-Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by click on the parameter bar (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d) ).
-In Fig.~\ref{fig:pipelineView}(c), we select whether if we want to use current update setting as displayed or try all the configuration combination (i.e., each stage can either be enabled or disabled for the three stage, therefore, there are $8$ combinations in total, $7$ if discard the case where all stages are not updated).
+The optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a).
+Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the parameter bar (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d) ).
+In Fig.~\ref{fig:pipelineView}(c), we select whether we want to use the current update setting as displayed or try all the configuration combinations (i.e., each stage can either be enabled or disabled for the three stages; therefore, there are $8$ combinations in total, or $7$ we discard the case where all stages are not updated).
 
@@
  \caption{
- The pipeline view provides the visual representation of three stages (encoder, attention, classifier) model.
+ The pipeline view provides the visual representation of three-stage (encoder, attention, classifier) model.
 In the proposed tool, we allow the model parameter to be updated to correct a prediction error.
-The pipeline view, by showing the aggregated gradient distribution, informs the user about the how different part of the model response to the optimization.
+The pipeline view, by showing the aggregated gradient distribution, informs the user about how different parts of the model respond to the optimization.
  %
- The optimization hyperparameters are shown in (a), each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ).
-In (c), we select whether if we want to use current update setting as displayed or try all the possible configuration combination (i.e., each stage's parameter update can be enabled or disabled).
+ The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ).
+In (c), we select whether we want to use the current update setting as displayed or try all the possible configuration combinations (i.e., each stage's parameter update can be enabled or disabled).
  }

### 2018-03-29 paper/predSummary.tex
add summary

--- 2018-03-26 paper/predSummary.tex
@@
-\subsection{All Predictions Summary View}
+\subsection{Summary View}
 \label{sec:allPairs}
-Since we can only focus on one individual example at a time for detail analysis, how to pick a single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
+% outline:
+%  - how to identify the sensitivity of pairs
+We can focus on only one individual example at a time for a detailed analysis using the combination of all previously discussed views.
+As a result, how to select a pair of sentences of interest from the development or test dataset, which consists of close to $10k$ examples, is an obvious challenge.
+% - what is the interesting pairs
+In addition, the experts are also interested in obtaining a high-level understanding beyond the information the prediction accuracy provides of the behavior of the $10k$ sentence pairs.
 %
-Beside the selection task, generate visual summarization there we also want to obtain certain high-level understand of how the whole set behave, beyond the information the prediction accuracy provide.
+These two goals are the two sides of the same coin, the selection task will become much easier if we can generate a good visual summary of the $10k$ examples that help experts obtain a deeper understanding of the whole $10k$ examples.
 
+To address these challenges, we introduce the summary view (see Fig.~\ref{fig:teaser}(A) ), which consists of a treemap, a histogram, and a scatterplot, to summarize the prediction results of the $10k$ examples, and provide the ability to drill down to an individual example for detailed analysis.
 %treemap for prediction
-As illustrate in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the ground truth label and the model prediction generated by the
-By click on the treemap cell, we can narrow down the selection by focus on specific senarios.
+As illustrated in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the different combinations of the ground truth label and the model prediction.
+In the treemap, the green blocks indicate examples where the predicted label agrees with the ground truth label, whereas the orange blocks indicate disagreement between the labels.
+The size of the block encodes the number of examples belonging to each category.
+%
+By clicking on the treemap cell, we can narrow down the selection by focusing on specific scenarios.
+%
+As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are revealed to focus on the selected subset.
+The histogram shows the distribution of the prediction sensitivity in this category.
+For each original pair, the sensitivity is defined by the ratio between the number of unchanged predictions among the perturbed pairs and the all the perturbed pairs.
+In other words, if we generated 100 sentence pairs via the automated sentence perturbation (i.e., replace nouns and verbs with synonymous), and after we predict the labels on all 100 pairs, if 80 out of the 100 maintain the original prediction label, we will have a sensitivity of 0.8.
+The \emph{sensitivity} measures how likely it is a sentence pair will change its prediction after applying minor perturbations to the original, which helps the expert infer the model stability on the given example.
+%
+We can further narrow down the focused set by selecting the bins in the histogram (see Fig.~\ref{fig:summaryView}(b),(d)). 
+%
+In the scatterplot, besides showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{sensitivity}.
+For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.
 
@@
  \caption{
-Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select example of interests.
-We summarize all the prediction results in (a), where the green block indicates correct predictions, and orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
+Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
+We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
 %
-The user can select the treemap to focus on the specific type of senarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
-The selection can be further narrowed down by select the bin in the histogram.
+The user can select the treemap to focus on the specific type of scenarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
+The selection can be further narrowed down by selecting the bin in the histogram.
 In (c) and (d), each point corresponds to one prediction.

### 2018-03-29 paper/implementation.tex
add implementation

--- 2018-03-26 paper/implementation.tex
@@
 \label{sec:implementation}
+We design the tool with flexibility and extensibility in mind.
+One of the key objectives is to allow easy integration with the existing NLP workflow.
+Therefore, instead of implementing the tool as a standalone application, we encapsulate the visualization functionality as a Python library, in which the behavior of the visual interaction (e.g., once prediction button is pressed what should be the prediction result) is defined in Python using the existing model in the expert's workflow.
+Also, due to the separation between the visualization and the underlying model computation, we can readily adapt different models or the same model with a different configuration or training.
+
+To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their models.
+The code (consists only a few lines of code) used to create the visualization in this paper is included in appendix B.
+%
+The NLP model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
+The visual elements are implemented in Javascript using \emph{D3.js} library , and the Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.

### 2018-03-29 paper/application.tex
update 6

@@
 In this particular example, the premise \textbf{P} is ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.'', and the original hypothesis \textbf{H1} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.''.
-The perturbed hypothesis \textbf{H2} replaced the word \textbf{pile} with \textbf{heap}.
+The perturbed hypothesis \textbf{H2} replaces the word \textbf{pile} with \textbf{heap}.
 
@@
 
-\begin{figure*}[t]
-\centering
-\vspace{-2mm}
- \includegraphics[width=0.9\linewidth]{failledEncoding}
- \caption{
-The prediction is failed due to incorrect alignment. For all the failed case, 
- }
-\label{fig:failedEncoding}
-\end{figure*}
-
 %One of the essential task for can be made in either of these stages.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scenario 3: What Does It Take to Correct a Wrong Prediction?}
-Once, we get a sense of how prediction are being made, where it went wrong. The next obvious questions are what does it take to correct the wrong prediction. 
-In addition, when we interpreting how decision are made, we always fix the model and make forward pass in the neural network.
+\subsection{Scenario 3: What Does It Take to Correct a Failed Prediction?}
+Up till now, we have employed perturbation for input to understand prediction robustness, utilized the perturbation of attention to infer the model decision making process.
+Both these perturbation operations rely on forward propagation in the pipeline and assume the model parameter stay unchanged.
+%
+However, once we get a sense of how predictions are being made and hypothesized about the cause of failure in case of a prediction error, it nature to ask the follow up question, what does it take to fix an incorrect prediction?
+And more importantly, what role does each of the three stages play in such a process, are they affect the prediction differently?
+
+Domain experts obtain answers to these questions by utilizing the prediction and pipeline view in the proposed.
+As discussed in details in Section~\ref{sec:pipelineView}, we employed an margin-infused relaxed algorithm (MIRA) based optimization with two complementary objectives (1.
+apply least amount of change to the parameter, 2.
+making the new prediction as close to the reassigned prediction as possible) to update the network parameters.
+%
+We can then visualize how much each stage of the model is changed through the distribution of parameters change.
+
+To infer the role each stage of the pipeline plays, the proposed tool allow the parameter update to be enabled or disabled for each pipeline stage.
+The tool also includes an automatic option to try all the possible combination configurations.
+As illustrated in Fig.~\ref{fig:pipelineUpdate}, the ground truth for this sentence pair is neutral.
+However, the model produces an incorrect label entailment.
+We reassign the prediction to neural, which triggers model update optimization for $7$ different pipeline configurations.
+Four configurations are shown in Fig.~\ref{fig:pipelineUpdate}(a)(b)(c)(d), the arrow line highlights the corresponding prediction for each of the update model.
+
+Interestingly, all configurations except one are concentrated around the full neural prediction.
+Referring back to the pipeline visualization, we can see the one configuration that failed to produce the correct label is when only attention stage update is allowed.
+%
+In other words, update of attention stage seems to have significant less impact on the prediction result compared to the classifier or encoder of the model. 
+%The attention layer is less sensitive compared to encoding layer and classification layer. 
+We also examined many other sentences pairs, such an observation remains.  
+%This gives domain expert some hint about the significance of the role of each pipeline stage play in this model.
+% which based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network generalize the concept of maligin combined effort of the  proposed technique
+
+%
+%However, to understand how the model should
+
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{pipelineUpdate}
+ \caption{
+How changes in different stage impact the prediction.
+ }
+\label{fig:pipelineUpdate}
+\end{figure*}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
-There is no simple answer to what exactly is the information attention captures.
-Can attention capture grammar structure? Is
+%\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
+%There is no simple answer to what exactly is the information attention captures.
+%Can attention capture grammar structure? Is
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scenario 5: Handcraft Example Exploration}
+\subsection{Scenario 4: Handcraft Example Exploration}
 To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most model will have a difficult time making correct inference.

### 2018-03-29 paper/evaluation.tex
update evaluation
update 6

@@
-\section{Evaluation}
-\shusen{discussed feedback and comment about the proposed system}
+\section{Evaluation and Feedback}
+%\shusen{discussed feedback and comment about the proposed system}
+
+once we change the final prediction label of the sentence pair, user observe that the update attention has the less significant impact compared to other layers of the model.
+The attention layer is less sensitive compared to encoding layer and classification layer.
+This gives domain expert some hint about the significance of the role of each pipeline stage play in this model.
+
+\begin{itemize}
+\item Emphasis on long term collabration 
+\item Two set of feedback from both vis background and NLP background
+\item what are the list of things we learn from the user feedback
+\end{itemize}

### 2018-03-29 paper/evaluation.tex
re-arrange figure

--- 2018-03-22 paper/evaluation.tex
@@
-\section{Evaluation}
-\shusen{discussed feedback and comment about the proposed system}
+\section{Evaluation and Feedback}
+%\shusen{discussed feedback and comment about the proposed system}
+
+The initial motivation for designing the proposed tool is driven by the error analysis challenges faces by NLP researchers working on natural language inference problem.
+We work closely with two NLP experts, and their constant evaluation and feedback have guided our entire design and development process.
+%
+However, since two NLP experts are heavy involved in the design process, they may be blinded for the potential limitation of the tool due to familiarity.
+In order to undercover the limitation and identify the areas for improvements we gathered a wider audience from both visualization (4 researchers include 3 PhD student and one Postdoc Researcher) and NLP background (5 PhD students who are familiar with the concept of natural language inference and attention) for the evaluation of the tool.
+%
+
+We first conduct a informal feedback session with the visualization group, with the goal to identify the potential interface design issues.
+During the feedback session, we first explain the NLP concept in an easily to approach manner, and then demonstrate the feature of tool in detail, while answering questions and address comments.
+%
+From this session, we have gather a number of common complaints, including difficult to distinguish predictions, hard to recognize ground truth label, as well as the lack of legends to understand the key elements in several plot.
+We address these interface issues in the version of tool presented to the NLP group.
+
+We conduct a more thorough evaluation session with the NLP group, in which each of the participants is first given 30 min to experiment with the tool after a overall feature demonstration.
+As the participants explore the tool,
+We will continue to answer more detailed question regarding the individual component, as well as how we implement the model update feature.
+%
+One participant hypothesis about the role attention is playing.
+After playing with the tool, he show us two sentence pair that he think is interesting.
+One sentence give a correct final prediction but he tell us that when he see the attention layer, the alignment is incorrect.
+At the other example, he show us a sentence pair which give a wrong prediction, he force two sentence?s attention to align but the final prediction is still incorrect.
+He tell us that through those two example  he can tell that a alignment may not give the correct prediction and correct prediction does not mean correct alignment.
+%
+The other interesting observation that he get is that once he force the incorrect final prediction to the ground truth label.
+In the update pipeline,  he observed that only update the attention stage won?t make the current sentence pair to the correct prediction.
+%
+After explaining the tool, the one participant try to use two same sentences and check how each component of the platform show.
+He also negate the meaning of a sentence ``A couple is taking a break from bicycling .''  by using ``A couple is not taking a break from bicycling .'' and see whether the relationship between two sentence is contradiction.
+He also comment that the ability to enable and disable update in the pipeline view is really helpful.
+%
+Overall, all the user think this tool is very convenient for them to verify their hypothesis and help them build a better intuition to improve the current model.

### 2018-03-29 paper/sentence.tex
re-arrange figure

@@
 %
-When the perturbation is applied to either of the sentences, the replaced words are highlighted in blue (see Fig.~\ref{fig:modelPipeline}(e) ) to signal the modification made to the original sentence.
+When the perturbation is applied to either of the sentences, the replaced words are highlighted in blue (see Fig.~\ref{fig:modelPipeline}(e)) to signal the modification made to the original sentence.
 
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=0.95\linewidth]{sentenceView}
- \vspace{-2mm}
- \caption{
- Sentence view shows the premise (c) and the hypothesis (d) sentence pair. The word that replaces the word in the original text is highlighted in blue (e).
- The \emph{Predict} and \emph{Predict All} controls (a) correspond to predicting the currently displayed sentence pairs and predicting all combinations of perturbed premise and hypothesis, respectively.
- Previous explored original sentence are stored in the dropdown list (d) that allow the user to revisit previous examined sentence.
-}
-\label{fig:sentenceView}
-\end{figure}
+% \begin{figure}[htbp]
+% \centering
+% \vspace{-2mm}
+%  \includegraphics[width=0.9\linewidth]{sentenceView}
+%  \vspace{-2mm}
+%  \caption{
+%  Sentence view shows the premise (c) and the hypothesis (d) sentence pair. The word that replaces the word in the original text is highlighted in blue (e).
+%  The \emph{Predict} and \emph{Predict All} controls (a) correspond to predicting the currently displayed sentence pairs and predicting all combinations of perturbed premise and hypothesis, respectively.
+%  Previous explored original sentence are stored in the dropdown list (d) that allow the user to revisit previous examined sentence.
+% }
+% \label{fig:sentenceView}
+% \end{figure}
 

### 2018-03-29 paper/discussion.tex
update layout of the paper
re-arrange figure
update discussion

@@
 
-\begin{itemize}
-    \item how the visualization approaches generalizes to other NLP task
-    \item limitation
-\end{itemize}
+Even though the current setup for the proposed tool is only suitable for natural language inference task.
+However, due to the modular design and the many shared attribution among end-two-end NLP models we can readily extends the system to handle other tasks.
+We plan add support for neural machine translation, question and answer, and more in the future.
+%
+Initial setup cost and learning curve of the tool are often the major barriers for visualization adoption.
+In the proposed system, we approach these challenges by designing the system as an python library rather than as an monolithic tool. 
+Just like a python plotting library, the different pieces of the visualization can be access individual or combined in any ways by the user via a simple python API.
+As a result, the proposed tool can not only be configured to suit the different needs of the individual domain experts to better fit into their workflow, but also enable NLP researchers to experiment to simpler features reduce the learning curved.
+Finally, the researchers are really appreciated the ability to easily swap functionality of the visualization in python.
+%defined and combined  The long term goal for the
+
+How to generate meaningful perturbation
+Limitation: sometime wordNet produce not very meaningful  perturbations
+
+%\begin{itemize}
+%    \item how the visualization approaches generalizes to other NLP task
+%    \item limitation
+%    \item future direction
+%\end{itemize}

### 2018-03-29 paper/application.tex
re-arrange figure
add figure

@@
 To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their analysis workflow.
+
+\subsection{Scenario 1: Assess the Model Prediction Stability}
+The robustness of the prediction is often hard to evaluate, however, they provide valuable information for the researchers to better understand the model.
+%
+In the proposed work, we approach the prediction robustness from sensitivity analysis point of view.
+The stability of the prediction is measured by how often the predicted labels are altered after small perturbations are applied to the input.
+%
+Compare to other types of input (e.g., image), perturbation of the natural language can be particular tricky, as small alteration of words can drastically change the meaning of the sentence.
+As discussed in Section~\ref{sec:sentence}, we try to maintain semantic of the sentence by only replace words with their synonymous and only replace one word for each pair.
+As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert can not only examine visual summary of the stability, but also quickly dive into individual examples for case by case analysis.
 
@@
 \end{figure}
-
-\subsection{Scenario 1: Assess the Model Prediction Stability}
-The robustness of the prediction is often hard to evaluate, however, they provide valuable information for the researchers to better understand the model.
-%
-In the proposed work, we approach the prediction robustness from sensitivity analysis point of view.
-The stability of the prediction is measured by how often the predicted labels are altered after small perturbations are applied to the input.
-%
-Compare to other types of input (e.g., image), perturbation of the natural language can be particular tricky, as small alteration of words can drastically change the meaning of the sentence.
-As discussed in Section~\ref{sec:sentence}, we try to maintain semantic of the sentence by only replace words with their synonymous and only replace one word for each pair.
-As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert can not only examine visual summary of the stability, but also quickly dive into individual examples for case by case analysis.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
-%There is no simple answer to what exactly is the information attention captures.
-%Can attention capture grammar structure? Is
+\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
+There is no simple answer to what exactly is the information attention captures.
+Can attention capture grammar structure? Is
+
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{depTreeExample}
+ \caption{
+Dependency tree.
+ }
+\label{fig:depTreeExample}
+\end{figure*}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scenario 4: Handcraft Example Exploration}
+\subsection{Scenario 5: Handcraft Example Exploration}
 To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most model will have a difficult time making correct inference.

### 2018-03-29 paper/application.tex
remove test set from drop down menu

@@
 
-\shusen{Example where the prediction is correct but the alignment is wrong}
+%\shusen{Example where the prediction is correct but the alignment is wrong}
 %%%% are we obtain correct prediction from wrong alignment %%%%%
@@
 For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
-However, since there is only three output labels, it is also likely in some cases the model produce correct predictions due to pure luck with attention that does not make sense (i.e., the important words are mis-align).
-It is also possible that even the alignment is perfect, the model still generate a wrong prediction.
+In the previous example, we show that even the alignment is perfect, the model still does not generate a correct prediction.
+However, as illustrated in Fig.~\ref{fig:wrongAlignRightPred}, it is also likely that model produce correct predictions from the wrong attention (i.e., the important words are mis-align).
+The word \textbf{break} and \textbf{sit} should not align with each other (Fig.~\ref{fig:wrongAlignRightPred}(a)), however, it still produce the correct \emph{neutral} label (Fig.~\ref{fig:wrongAlignRightPred}(b)).
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{wrongAlignRightPred}
+ \caption{
+The example of model producing right prediction with wrong attention.
+The word \textbf{break} and \textbf{sit} should not align with each other (a), yet, it still yield the correct prediction (b).
+}
+\label{fig:wrongAlignRightPred}
+\end{figure}
 
@@
 \subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
+
 There is no simple answer to what exactly is the information attention captures.
-Can attention capture grammar structure? Is
+Can attention capture grammar structure?
+
+The prediction is Entailment which is wrong.
+The "green" will be aligned to "green".
+However they are actually attached to different words in the dependency tree.
+That is "green" in P is attached to jacket, while "green" in H is attached to tea.
+They should not be aligned.
+And more interestingly is, by forcing the two "green"'s alignment to be zero, the prediction label is corrected to Neutral. This stresses the importance of dependency tree in our tool.
 

### 2018-03-29 src/visPackage/static/components/evaluationComponent.js

@@ -124,8 +124,8 @@ class evaluationComponent extends baseComponent {
 
     setupUI() {
         let fileList = [
-            "../data/dev-set-statistic.json",
-            "../data/test-set-statistic.json"
+            "../data/dev-set-statistic.json"
+            // , "../data/test-set-statistic.json"
         ]
         d3.select(this.div + "selectData")
             .selectAll('option')

### 2018-03-29 src/visPackage/visModule.py

@@ -53,6 +53,16 @@ exampleData = [
     "src": "<s> A very young child in a red plaid coat and pink winter hat makes a snowball in a large pile of snow .\n",
     "targ": "<s> A child in a red plaid coat and pink winter hat makes a snowball in a large heap of snow .\n",
     "pred": "entailment"
+},{
+    "index":6,
+    "src": "<s> A couple is taking a break from bicycling .\n",
+    "targ": "<s> sisters sit next to their bikes .\n",
+    "pred": "neutral"
+},{
+    "index":7,
+    "src": "<s> A woman in a green jacket is drinking tea .\n",
+    "targ": "<s> A woman is drinking green tea .\n",
+    "pred": "neutral"
 }
 ]
 pipelineState = [{

### 2018-03-29 paper/application.tex
update section 6.4

@@
 \centering
-%\vspace{-2mm}
+\vspace{-2mm}
  \includegraphics[width=1.0\linewidth]{predictStability}
+ \vspace{-4mm}
  \caption{
@@
 In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
-The user can drill down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a case by case exploration, as illustrated in (d)(e).
-For highly unstable outliers, we often observe the prediction of the original sentences near the decision boundary (e.g., the yellow circle in (f) corresponds to a entailment prediction that is very close to neural), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``pile'' is replace by ``heap'' in the hypothesis sentence).
-%
+The user can drill down to individual examples by filtering via the histogram or scatterplot (see Fig.~\ref{fig:summaryView}).
+For highly unstable prediction, we often observe the original prediction is near a decision boundary (e.g., the yellow circle in (e) corresponds to a prediction that is at the boundary between \emph{entailment} and \emph{neutral}), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``pile'' is replace by ``heap'' in the hypothesis sentence).
 }
 \label{fig:predictStability}
+\vspace{-2mm}
 \end{figure}
@@
 \subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
+The attention computation in the NLI model does not take the grammar structure of the sentences into consideration,
+% There is no simple answer to what exactly is the information attention captures.
+% Can attention capture grammar structure? 
+yet, the attention often can highlight the key structural elements of the sentence. 
+Therefore, domain experts want to understand whether attention alone is sufficient to distinguish, 
+and more important what kind of benefit can the additional information from grammar parsing help address NLI challenge.
 
-There is no simple answer to what exactly is the information attention captures.
-Can attention capture grammar structure?
-
-The prediction is Entailment which is wrong.
-The "green" will be aligned to "green".
-However they are actually attached to different words in the dependency tree.
-That is "green" in P is attached to jacket, while "green" in H is attached to tea.
-They should not be aligned.
-And more interestingly is, by forcing the two "green"'s alignment to be zero, the prediction label is corrected to Neutral. This stresses the importance of dependency tree in our tool.
+In our tool, we overly the sentence dependency tree with the attention that enables researchers to conduct easy comparable between attention and grammar structure.
+As illustrated in Fig.~\ref{fig:depTreeExample}(a), the prediction of the sentence pair (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is \emph{entailment}, which is wrong.
+We can understand the reasoning by examine the attention, in which we observes that the word \textbf{green} in "\textbf{green} jacket" is aligned to the \textbf{green} in "\textbf{green} tea".
+Due to such an alignment, the model mistakenly believe the \textbf{green}s are used to describe the same thing (therefore, producing the \emph{entailment} label).
+However, as we examine the dependency tree, the two \textbf{green}s are actually attached to different words, i.e., "green" in \textbf{P} is attached to jacket, while "green" in \textbf{H} is attached to tea.
+Therefore, they should not be aligned in the attention in order to allow the classifier make the right prediction.
+%
+This experiment demonstrate the potential benefit to include grammar structure in the alignment computation. %This stresses the importance of dependency tree in our tool.
+%
+And more interestingly is, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected to \emph{neutral}.
 

### 2018-03-29 paper/overview.tex
re-arrange figure
update section 6.4

@@
-\section{NLIZE System}
-In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-3}).
-%
-As discussed in the task analysis, the experts often analyze and obtain intuition about the model by studying how altering one part of the model affects other stages of the pipeline.
-%
-Such a process can be generalized as the perturbation-driven paradigm, which is used as a guiding principal for designing the proposed tool.
-%
-As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (e.g., adjust the prediction by making updates to the model).
-%
-In the following sections, we describe in detail the five major components of the proposed system, namely, the sentence view  (Section~\ref{sec:sentence}), the attention view (Section~\ref{sec:attention}), the prediction view (Section~\ref{sec:prediction}), the pipeline view (Section~\ref{sec:pipeline}), and the all pair summary view (Section~\ref{sec:allPairs}).
-
 \begin{figure}[htbp]
@@
 
+\section{NLIZE System}
+In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-3}).
+%
+As discussed in the previous section, the experts often analyze and obtain intuition about the model by studying how altering one part of the model affects other stages of the pipeline.
+%
+Such a process can be generalized as the perturbation-driven paradigm, which is used as a guiding principal for designing the proposed tool.
+%
+As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (e.g., adjust the prediction by making updates to the model).
+%
+In the following sections, we describe in detail the five major components of the proposed system, namely, the sentence view  (Section~\ref{sec:sentence}), the attention view (Section~\ref{sec:attention}), the prediction view (Section~\ref{sec:prediction}), the pipeline view (Section~\ref{sec:pipeline}), and the all pair summary view (Section~\ref{sec:allPairs}).
+
 % Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.

### 2018-03-29 paper/sentence.tex
update section 6.4

@@
 % Once an exploration cycle started, the experts need to examine the premise and hypothesis sentence the current example.
-As illustrated in Fig.~\ref{fig:sentenceView}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
+As illustrated in Fig.~\ref{fig:teaser}(B), the sentence view shows the premise and hypothesis sentence.
 %
@@
 %
-When the perturbation is applied to either of the sentences, the replaced words are highlighted in blue (see Fig.~\ref{fig:modelPipeline}(e)) to signal the modification made to the original sentence.
+When the perturbation is applied to either of the sentences, the replaced words are highlighted in blue to signal the modification made to the original sentence.
 
@@
 
-At the top left of the view, the two controls \emph{Predict} and \emph{Predict All} (a) correspond to predicting the currently displayed sentence pairs and predict all combinations of perturbed premises and hypotheses, respectively.
+At the top left of the view, the two controls \emph{Predict} and \emph{Predict All} correspond to predicting the currently displayed sentence pairs and predict all combinations of perturbed premises and hypotheses, respectively.
 %
@@
 %%% sentence perturbation %%%%
-The previously explored original sentences are stored in the dropdown list (see Fig.~\ref{fig:sentenceView}(b)) that allow the user to revisit examined examples.
-Also, the user can type any sentences or modified existing text in the text areas (Fig.~\ref{fig:sentenceView}(c)(d)) to accommodate user-defined input.
+The previously explored original sentences are stored in the dropdown list (left of the buttons) that allow the user to revisit examined examples.
+Also, the user can type any sentences or modified existing text in the sentence display areas to accommodate user-defined input.
 

### 2018-03-29 src/visPackage/static/components/evaluationComponent.js

@@ -99,13 +99,13 @@ class evaluationComponent extends baseComponent {
         // var stabilities = data.map(d => d.stability);
         // console.log(stabilities);
         this.histo.setSample(data, d => d.stability);
-        this.histo.setTitle("Stability");
-        this.scatter.setData(data, ["Stability", "PerturbCount"],
+        this.histo.setTitle("Sensitivity");
+        this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
             d => [d.stability, d.perturbCount]);
     }
 
     updateScatterplot(data) {
-        this.scatter.setData(data, ["Stability", "PerturbCount"],
+        this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
             d => [d.stability, d.perturbCount]);
     }
 

### 2018-03-30 paper/application.tex
finish section 6.1

@@
 %In this section, we discuss application scenarios, in which the domain experts utilize the
-To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their analysis workflow.
+To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool in their analysis workflow.
 
 \subsection{Scenario 1: Assess the Model Prediction Stability}
-The robustness of the prediction is often hard to evaluate, however, they provide valuable information for the researchers to better understand the model.
+The robustness of the prediction is often hard to evaluate. However, the prediction stability provides valuable information for the researchers to better understand the model.
 %
@@
 %
-Compare to other types of input (e.g., image), perturbation of the natural language can be particular tricky, as small alteration of words can drastically change the meaning of the sentence.
+Compare to other types of input (e.g., image), perturbation of the natural language can be particularly tricky, as small alteration of words can drastically change the meaning of the sentence.
 As discussed in Section~\ref{sec:sentence}, we try to maintain semantic of the sentence by only replace words with their synonymous and only replace one word for each pair.
-As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert can not only examine visual summary of the stability, but also quickly dive into individual examples for case by case analysis.
+As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert can not only examine a visual summary of the stability but also quickly dive into individual examples for case by case analysis.
 
@@
 The user can drill down to individual examples by filtering via the histogram or scatterplot (see Fig.~\ref{fig:summaryView}).
-For highly unstable prediction, we often observe the original prediction is near a decision boundary (e.g., the yellow circle in (e) corresponds to a prediction that is at the boundary between \emph{entailment} and \emph{neutral}), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``pile'' is replace by ``heap'' in the hypothesis sentence).
+For highly unstable prediction, we often observe the original prediction is near a decision boundary (e.g., the yellow circle in (e) corresponds to a prediction that is at the boundary between \emph{entailment} and \emph{neutral}), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word \textbf{pile} is replaced by \textbf{heap} in the hypothesis sentence).
 }
@@
 
-In Fig.~\ref{fig:predictStability}(a)(b)(c),  %by viewing the distribution of the stability in the histogram
-we compare the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
+In Fig.~\ref{fig:predictStability}(a)(b)(c), we compare the overall prediction stability (regarding synonymous perturbation) for all correct predictions in the development set (10k examples in total).
 %
-We observe a drastic difference between the stability for entailment predictions compare to the contradiction and neutral ones.
+We observe a drastic difference between the stability for \emph{entailment} predictions compare to the \emph{contradiction} and \emph{neutral} ones.
 %
-Such a distinction can be partially explained by how entailment relationship is defined.
-As discussed in the Section~\ref{sec:languageInference}, the relationship is only valid if the concept in premise is more specific than the concept in hypothesis (therefore, you can infer the hypothesis from the premise, but not other way around).
-This means, we may change the entailment relationships simply by replacing nouns and verb by synonymous, whereas, the same does not apply for neutral and contradiction.
+Such a distinction can be partially explained by how \emph{entailment} relationship is defined.
+The relationship is only valid if the concept in the premise is more specific than the concept in the hypothesis.
+Therefore, the synonymous perturbation may change the \emph{entailment} relationship, as the replaced noun and verb can be more or less restrictive compared to the original.
+This inherent disparity of sensitivity may worth be taken into consideration when designing future NLI models.
+
+Besides presenting the summary view, the tool also allows the user to quickly narrow down the selection to single example by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}).
 %
-The inherent sensitivity difference may motivate domain experts designing dedicate model mechanism to address the such a disparity.
-
-Beside presenting the summary view, the tool also allow user to quickly narrow down the select to single example  by filtering through the histogram and scatterplot (see Fig.~\ref{fig:summaryView}).
-%
-Through exploring multiple samples (in the entailment category, E/E in Fig.~\ref{fig:summaryView}(a)), the domain experts noticed many highly unstable outliers are from sentence pairs where the prediction is near the decision boundary (see Fig.~\ref{fig:predictStability}(e), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
-However, some predictions, such as the one illustrated in Fig.~ref{fig:predictStability}(d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence.
-We will try to understand the what is happened inside the model in the following section (see Fig.~\ref{fig:att2pred}).
+Through exploration of many samples with low stabilities (i.e., high sensitivities values in the plots), the domain experts noticed that many highly unstable outliers are from sentence pairs where the prediction is near the decision boundary (see Fig.~\ref{fig:predictStability}(e), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
+However, some predictions, such as the one illustrated in Fig.~\ref{fig:predictStability}(d) can alter the prediction quite drastically with minor perturbation (shown in $d_1$, where the word \textbf{heap} is replaced by \textbf{pile} in the hypothesis sentence.
+In the following section, we will examine what happened inside the model and hypothesis on the cause of failure (see Fig.~\ref{fig:att2pred}).
 
@@
  \caption{
-The example of model producing right prediction with wrong attention.
-The word \textbf{break} and \textbf{sit} should not align with each other (a), yet, it still yield the correct prediction (b).
+The model may produces the right prediction for the ``wrong'' reason, i.e., attention.
+The word \textbf{break} and \textbf{sit} should not align with each other (a). Yet, based on the attention, model still produces the correct prediction (b).
 }

### 2018-03-30 paper/application.tex
finish application

@@
 \subsection{Scenario 2: Examine the Decision Making Process}
-The predicted label alone provide limited information.
-Often, domain experts want to know how does the model arrive at such a conclusion.
-And if the prediction is incorrect, where does the error occur in the model?
-%
-Examining the decision making process is not only instrumental for evaluating the model performance but also essential for hypothesizing improvement strategies for developing future models.
+The predicted label alone provides limited information.
+Often, domain experts want to know how does the model arrive at a conclusion.
+And if the prediction is incorrect, wherein the model does the error occur?
+Examining the decision making process is not only instrumental in evaluating the model performance but also essential for hypothesizing improvement strategies for future models.
 %
@@
 
-In the previous section, we have noticed some unexpected behavior, where a minor perturbation of the text from \emph{pile} to \emph{heap} lead to change in the final prediction label (Fig.~\ref{fig:predictStability}(d)).
+In the previous section, we have noticed a minor change of the sentence (replace \emph{pile} with \emph{heap}) lead to difference in the final prediction label (Fig.~\ref{fig:predictStability}(d)).
 Here, we want to make sense of what lead to the failed prediction.
-In this particular example, the premise \textbf{P} is ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.'', and the original hypothesis \textbf{H1} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.''.
-The perturbed hypothesis \textbf{H2} replaces the word \textbf{pile} with \textbf{heap}.
-
-As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair, the word \textbf{pile} and \textbf{heap} is not well-aligned (see Fig.~\ref{fig:att2pred}(a)).
-%
-To verify whether the alignment is what contribute to the misclassification, the domain expert utilize the attention editing functionality in the matrix view (Fig.~\ref{fig:attView}) to make the word \textbf{pile} align with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
-%
-In the update prediction view (see Fig.~\ref{fig:att2pred} (d)), we can see the editing of attention lead to changes in prediction.
-The original prediction moved from neutral toward the entailment (which is the true label) and straddle on the class boundary.
-However, the correct alignment does not full fix the prediction problem as the original pair (\textbf{P}, \textbf{H1}) is clearly predicted as \emph{entailment} (as showed in Fig~\ref{fig:predictStability}(d)).
-%
-Interestingly, the original pair's attention is almost identical to the edited attention (the comparison is not shown in the figure).
-Such an observation means that the model do not strongly believe ``\textbf{heap} of snow'' and ``\textbf{pile} snow'' has the same meaning, which indicate the potential issue with encoder or word embedding.
+In this example, the premise \textbf{P} is ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.'', and the original hypothesis \textbf{H1} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.''.
+The perturbed hypothesis \textbf{H2} replaces the word \textbf{pile} with \textbf{heap} in \textbf{H1}.
+This example should be rather straightforward for the model since there are only minor differences between the \textbf{P} and \textbf{H1}/\textbf{H2}.
 
@@
  \caption{
-Editing the original attention (a) to correctly align the word "heap" with "pile" as shown in (b) (these two words are highlight in orange).
-The change of attention lead to change of prediction from neutral to the class boundary between neutral and entialment.
+Editing the original attention (a) to correctly align the word "heap" with "pile" as shown in (b) (these two words are highlighted in orange).
+The change of attention leads to the change of prediction from neutral to the class boundary between \emph{neutral} and \emph{entitlement}.
 %
@@
 
-%\shusen{Example where the prediction is correct but the alignment is wrong}
-%%%% are we obtain correct prediction from wrong alignment %%%%%
-%By looking into the model decision making process, we can assess whether the model is behaving as intended.
-For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
-In the previous example, we show that even the alignment is perfect, the model still does not generate a correct prediction.
-However, as illustrated in Fig.~\ref{fig:wrongAlignRightPred}, it is also likely that model produce correct predictions from the wrong attention (i.e., the important words are mis-align).
-The word \textbf{break} and \textbf{sit} should not align with each other (Fig.~\ref{fig:wrongAlignRightPred}(a)), however, it still produce the correct \emph{neutral} label (Fig.~\ref{fig:wrongAlignRightPred}(b)).
+As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair, the word \textbf{pile} and \textbf{heap} is not well-aligned (see Fig.~\ref{fig:att2pred}(a)).
+%
+To test whether the alignment is what contribute to the misclassification, the domain expert utilizes the attention editing functionality in the matrix attention view (Fig.~\ref{fig:attentionVis}(c)) to make the word \textbf{pile} align with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
+%
+As illustrated in Fig.~\ref{fig:att2pred} (d), after the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary, but the corrected attention fails to produce a conclusive \emph{entailment} prediction.
+%
+%Interestingly, the original pair's attention is almost identical to the edited attention (the comparison is not shown in the figure). 
+Such an observation implies that the model does not firmly believe ``\textbf{heap} of snow'' and ``\textbf{pile} of snow'' have the same meaning, which may indicate the potential issue with the encoder or word embedding.
 
@@
 
+%\shusen{Example where the prediction is correct but the alignment is wrong}
+%%%% are we obtain correct prediction from wrong alignment %%%%%
+%By looking into the model decision making process, we can assess whether the model is behaving as intended.
+For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
+In the previous example, we show that the perfect alignment does not necessarily guarantee a correct prediction.
+%
+On the flip side, we may produce the right predictions for the ``wrong'' reason (i.e., incorrect attention). 
+As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, the word \textbf{break} and \textbf{sit} should not align with each other (Fig.~\ref{fig:wrongAlignRightPred}(a)), however, it still produce the correct \emph{neutral} label (Fig.~\ref{fig:wrongAlignRightPred}(b)).
+%
+%By looking into the model decision making process, we can assess whether the model is behaving as intended. 
+%These situations demonstrate the important of understanding the model decision making process, we can assess whether the model is behaving as intended.
+
 %%%% hypothesis on which part of model is wrong? %%%%%
@@
 \subsection{Scenario 3: What Does It Take to Correct a Failed Prediction?}
-Up till now, we have employed perturbation for input to understand prediction robustness, utilized the perturbation of attention to infer the model decision making process.
+Up till now, we have employed perturbation for input to understand prediction robustness, utilized the perturbation of attention (and input sentences) to infer the model decision making process.
 Both these perturbation operations rely on forward propagation in the pipeline and assume the model parameter stay unchanged.
 %
-However, once we get a sense of how predictions are being made and hypothesized about the cause of failure in case of a prediction error, it nature to ask the follow up question, what does it take to fix an incorrect prediction?
-And more importantly, what role does each of the three stages play in such a process, are they affect the prediction differently?
+However, once we get a sense of how predictions are being made and hypothesized about the cause of failure in case of a prediction error, it is natural to ask the follow-up questions.
+What does it take to fix an incorrect prediction?
+And more importantly, what role does each of the three stages play in such a process?
+Are they affecting the prediction differently?
 
-Domain experts obtain answers to these questions by utilizing the prediction and pipeline view in the proposed.
-As discussed in details in Section~\ref{sec:pipelineView}, we employed an margin-infused relaxed algorithm (MIRA) based optimization with two complementary objectives (1.
+Domain experts can obtain answers to these questions by utilizing the prediction and pipeline view in the proposed.
+As discussed in details in Section~\ref{sec:pipeline}, we employed an margin-infused relaxed algorithm (MIRA) based optimization with two objectives (1.
 apply least amount of change to the parameter, 2.
-making the new prediction as close to the reassigned prediction as possible) to update the network parameters.
+make the new prediction as close to the reassigned prediction as possible) to update the network parameters.
 %
-We can then visualize how much each stage of the model is changed through the distribution of parameters change.
-
-To infer the role each stage of the pipeline plays, the proposed tool allow the parameter update to be enabled or disabled for each pipeline stage.
-The tool also includes an automatic option to try all the possible combination configurations.
-As illustrated in Fig.~\ref{fig:pipelineUpdate}, the ground truth for this sentence pair is neutral.
-However, the model produces an incorrect label entailment.
-We reassign the prediction to neural, which triggers model update optimization for $7$ different pipeline configurations.
-Four configurations are shown in Fig.~\ref{fig:pipelineUpdate}(a)(b)(c)(d), the arrow line highlights the corresponding prediction for each of the update model.
-
-Interestingly, all configurations except one are concentrated around the full neural prediction.
-Referring back to the pipeline visualization, we can see the one configuration that failed to produce the correct label is when only attention stage update is allowed.
-%
-In other words, update of attention stage seems to have significant less impact on the prediction result compared to the classifier or encoder of the model.
-%The attention layer is less sensitive compared to encoding layer and classification layer.
-We also examined many other sentences pairs, such an observation remains.
-%This gives domain expert some hint about the significance of the role of each pipeline stage play in this model.
-% which based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network generalize the concept of maligin combined effort of the  proposed technique
-
-%
-%However, to understand how the model should
+We then visualize how much each stage of the model is changed through the distribution of parameters change.
 
@@
  \caption{
-How changes in different stage impact the prediction.
+Experiment with all configurations for the label reassignment optimization.
+As shown in (d), the update of attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
  }
 \label{fig:pipelineUpdate}
+\end{figure*}
+
+To infer the role each stage of the pipeline plays, the proposed tool allow the parameter update to be enabled or disabled for each pipeline stage.
+The tool also includes an automatic option for testing all the possible combination configurations.
+As illustrated in Fig.~\ref{fig:pipelineUpdate}, the ground truth for this sentence pair is neutral.
+However, the model produces an incorrect label \emph{entailment}.
+The domain expert reassigns the prediction to \emph{neural}, which triggers model update optimization for $7$ different pipeline configurations.
+Four configurations are shown in Fig.~\ref{fig:pipelineUpdate}(a)(b)(c)(d).
+The updated predictions are illustrated as blue squares, and the pointers highlighted the corresponding pipeline configuration.
+
+Interestingly, all configurations except one are concentrated around the full \emph{neural} prediction.
+Referring back to the pipeline configuration visualization, we observe that the only configuration that failed to produce the correct label is the one, in which we only allow attention stage update.
+%
+In other words, the update of attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
+%The attention layer is less sensitive compared to encoding layer and classification layer.
+%When examined other sentences pairs, such an observation remains.
+%This gives domain expert some hint about the significance of the role of each pipeline stage play in this model.
+% which based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network generalize the concept of maligin combined effort of the  proposed technique
+
+%
+%However, to understand how the model should
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{depTreeExample}
+ \caption{
+Dependency tree provides valuable information which can help fix the prediction error.
+In (a), the model mistakenly aligns the word green, which lead to wrong prediction.  
+After examining the dependency tree, we can see the two \textbf{green} are attached to different words.
+In (b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected to \emph{neutral}. 
+ }
+\label{fig:depTreeExample}
 \end{figure*}
@@
 The attention computation in the NLI model does not take the grammar structure of the sentences into consideration,
-% There is no simple answer to what exactly is the information attention captures.
-% Can attention capture grammar structure? 
-yet, the attention often can highlight the key structural elements of the sentence. 
-Therefore, domain experts want to understand whether attention alone is sufficient to distinguish, 
-and more important what kind of benefit can the additional information from grammar parsing help address NLI challenge.
+yet, the attention often can highlight the key elements of the sentence. 
+Therefore, domain experts wish to understand whether attention alone is sufficient to capture sentence structure. 
+And more important what kind of benefit can the additional information from grammar parsing help address the NLI challenge.
 
-In our tool, we overly the sentence dependency tree with the attention that enables researchers to conduct easy comparable between attention and grammar structure.
+In the proposed system, we overlay the sentence dependency tree with the attention, which enables researchers to conduct comparisons between attention and grammar structure.
 As illustrated in Fig.~\ref{fig:depTreeExample}(a), the prediction of the sentence pair (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is \emph{entailment}, which is wrong.
-We can understand the reasoning by examine the attention, in which we observes that the word \textbf{green} in "\textbf{green} jacket" is aligned to the \textbf{green} in "\textbf{green} tea".
-Due to such an alignment, the model mistakenly believe the \textbf{green}s are used to describe the same thing (therefore, producing the \emph{entailment} label).
-However, as we examine the dependency tree, the two \textbf{green}s are actually attached to different words, i.e., "green" in \textbf{P} is attached to jacket, while "green" in \textbf{H} is attached to tea.
-Therefore, they should not be aligned in the attention in order to allow the classifier make the right prediction.
+We can understand the reasoning by examining the attention, in which the word \textbf{green} in ``\textbf{green} jacket" is aligned to the \textbf{green} in ``\textbf{green} tea".
+Due to such an alignment, the model mistakenly believe the two \textbf{green} are used to describe the same thing (therefore, producing the \emph{entailment} label).
+However, as we examine the dependency tree, the two \textbf{green} are attached to different words, i.e., ``green" in \textbf{P} is attached to jacket, while ``green" in \textbf{H} is attached to tea.
+Therefore, they should not be aligned with the attention to allow the classifier make the right decision.
 %
-This experiment demonstrate the potential benefit to include grammar structure in the alignment computation. %This stresses the importance of dependency tree in our tool.
+This experiment demonstrates the potential benefit to include grammar structure in the alignment computation. %This stresses the importance of dependency tree in our tool.
 %
-And more interestingly is, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected to \emph{neutral}.
-
-\begin{figure*}[t]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{depTreeExample}
- \caption{
-Dependency tree.
- }
-\label{fig:depTreeExample}
-\end{figure*}
+And more interestingly, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected to \emph{neutral}.
 
@@
 \subsection{Scenario 5: Handcraft Example Exploration}
-To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most model will have a difficult time making correct inference.
+To test the limits of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most models will have a difficult time making correct inference.
 %
-%The exploration is just started once the prediction result is examined,
-Often the researchers have a set of experiments they plan test, from which they likely develop new hypothesis for further experiments.
+Often the researchers have a set of experiments they plan to run, from which, they will likely develop new hypotheses for further analysis.
 %
-In some way, we can think of such a process as a nature blend of all previously discussed scenarios.
-However,  instead with specific analysis goal in mind, the domain experts focus on probing around and see if they can find anything interesting or out-of-ordinary behaviors in the model.
+In some way, we can think of such a process as a natural blend of all previously discussed scenarios.
+However,  instead of with specific goal in mind, the domain experts focus on probing around and see if they can find anything interesting or out-of-ordinary behaviors in the model.
 %
-Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures an streamlined exploration experience that free the users from interruption and tedious grunt work, allow them to focus on more productive activity.
+Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures a streamlined exploration experience that free the users from interruption and tedious operations, allow them to focus on the more productive activity.
 

### 2018-03-30 src/exampleVis.py
fix all pair update bug

@@ -14,7 +14,7 @@ dep = dependencyTree()
 
 #visualization components
 visLayout = {
-    "column":[{"row":["Selector", "Sentence", "Pipeline"]},
+    "column":[{"row":["Summary", "Sentence", "Pipeline"]},
             {"row":["AttentionGraph", "AttentionMatrix", "Prediction"]}]
     }
 

### 2018-03-30 src/visPackage/static/components/attentionComponent.js

@@ -229,6 +229,8 @@ class attentionComponent extends baseComponent {
                         this.targDepTreeData = undefined;
                         this.targ_dep = undefined;
                         this.normAttention = undefined;
+                        this.setData("allSourceSens", [pair[0]]);
+                        this.setData("allTargetSens", [pair[1]]);
                     }
                 } else {
 

### 2018-03-30 src/visPackage/static/components/sentenceComponent.js

@@ -59,13 +59,12 @@ class sentenceComponent extends baseComponent {
                         this.clearDropdown(this.div + "srcInput");
                         this.clearDropdown(this.div + "targInput");
 
-                        // this.setData("allSourceSens", [pair[0]]);
-                        // this.setData("allTargetSens", [pair[1]]);
+                        console.log("refresh the allSourceSens");
                     }
                 }
 
                 this.onReceiveCurrentPair();
-                this.oldPair = pair.slice();
+                this.oldPair = JSON.parse(JSON.stringify(pair));
                 break;
         }
     }

### 2018-03-30 paper/application.tex
grammar fix

@@
 %
-We observe a drastic difference between the stability for \emph{entailment} predictions compare to the \emph{contradiction} and \emph{neutral} ones.
+We observe a drastic difference for the stability for \emph{entailment} predictions compare to the \emph{contradiction} and \emph{neutral} ones.
 %
@@
 The relationship is only valid if the concept in the premise is more specific than the concept in the hypothesis.
-Therefore, the synonymous perturbation may change the \emph{entailment} relationship, as the replaced noun and verb can be more or less restrictive compared to the original.
-This inherent disparity of sensitivity may worth be taken into consideration when designing future NLI models.
+Therefore, the synonymous perturbation may change the \emph{entailment} relationship, as the replaced \emph{noun} or \emph{verb} can be more or less restrictive compared to the original.
+This inherent disparity of sensitivity may worth extra consideration when designing future NLI models.
 
-Besides presenting the summary view, the tool also allows the user to quickly narrow down the selection to single example by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}).
+Besides presenting the summary view, the tool also allows the user to quickly narrow down the selection to a single example by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}).
 %
-Through exploration of many samples with low stabilities (i.e., high sensitivities values in the plots), the domain experts noticed that many highly unstable outliers are from sentence pairs where the prediction is near the decision boundary (see Fig.~\ref{fig:predictStability}(e), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
+Through the exploration of many samples with low stabilities (i.e., high sensitivities values in the plots), domain experts notice that many highly unstable outliers are from sentence pairs where the predictions are near the decision boundary (see Fig.~\ref{fig:predictStability}(e), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
 However, some predictions, such as the one illustrated in Fig.~\ref{fig:predictStability}(d) can alter the prediction quite drastically with minor perturbation (shown in $d_1$, where the word \textbf{heap} is replaced by \textbf{pile} in the hypothesis sentence.
@@
 Often, domain experts want to know how does the model arrive at a conclusion.
-And if the prediction is incorrect, wherein the model does the error occur?
+And if the prediction is incorrect, where in the model does the error occur?
 Examining the decision making process is not only instrumental in evaluating the model performance but also essential for hypothesizing improvement strategies for future models.
@@
 
-In the previous section, we have noticed a minor change of the sentence (replace \emph{pile} with \emph{heap}) lead to difference in the final prediction label (Fig.~\ref{fig:predictStability}(d)).
+In the previous section, we have noticed that a minor perturbation of the sentence (replace \emph{pile} with \emph{heap}) may result in change to the final prediction (Fig.~\ref{fig:predictStability}(d)).
 Here, we want to make sense of what lead to the failed prediction.

### 2018-03-30 paper/application.tex
grammar fix

@@
 Through the exploration of many samples with low stabilities (i.e., high sensitivities values in the plots), domain experts notice that many highly unstable outliers are from sentence pairs where the predictions are near the decision boundary (see Fig.~\ref{fig:predictStability}(e), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
-However, some predictions, such as the one illustrated in Fig.~\ref{fig:predictStability}(d) can alter the prediction quite drastically with minor perturbation (shown in $d_1$, where the word \textbf{heap} is replaced by \textbf{pile} in the hypothesis sentence.
-In the following section, we will examine what happened inside the model and hypothesis on the cause of failure (see Fig.~\ref{fig:att2pred}).
+However, some predictions, such as the one illustrated in Fig.~\ref{fig:predictStability}(d) can alter the prediction quite drastically with minor perturbation (shown in Fig.~\ref{fig:predictStability}$d_1$, where the word \textbf{heap} is replaced by \textbf{pile} in the hypothesis sentence).
+In the following section, we will examine what happened inside the model and hypothesize the cause of failure (see Fig.~\ref{fig:att2pred}).
 
@@
 
-In the previous section, we have noticed that a minor perturbation of the sentence (replace \emph{pile} with \emph{heap}) may result in change to the final prediction (Fig.~\ref{fig:predictStability}(d)).
+In the previous section, we have noticed that a minor perturbation of the sentence may result in change of the final prediction (Fig.~\ref{fig:predictStability}(d)).
 Here, we want to make sense of what lead to the failed prediction.
@@
 %
-As illustrated in Fig.~\ref{fig:att2pred} (d), after the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary, but the corrected attention fails to produce a conclusive \emph{entailment} prediction.
+As illustrated in Fig.~\ref{fig:att2pred} (d), after the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary (Fig.~\ref{fig:att2pred}(d)), but the corrected attention fails to produce a conclusive \emph{entailment} prediction.
 %
@@
 \subsection{Scenario 3: What Does It Take to Correct a Failed Prediction?}
-Up till now, we have employed perturbation for input to understand prediction robustness, utilized the perturbation of attention (and input sentences) to infer the model decision making process.
+Up till now, we have employed perturbation for input to understand prediction robustness, utilized the perturbation of attention (and input) to infer the model decision making process.
 Both these perturbation operations rely on forward propagation in the pipeline and assume the model parameter stay unchanged.
 %
-However, once we get a sense of how predictions are being made and hypothesized about the cause of failure in case of a prediction error, it is natural to ask the follow-up questions.
+However, once we get a sense of how predictions are made and hypothesized about the cause of failure in case of a prediction error, it is natural to ask the follow-up questions.
 What does it take to fix an incorrect prediction?
@@
 %
-We then visualize how much each stage of the model is changed through the distribution of parameters change.
+We then visualize how much each stage of the model is changed through the distribution of parameters difference (see Fig.~\ref{fig:pipelineView}).
 
@@
  \includegraphics[width=1.0\linewidth]{pipelineUpdate}
+ \vspace{-2mm}
  \caption{
@@
 
-To infer the role each stage of the pipeline plays, the proposed tool allow the parameter update to be enabled or disabled for each pipeline stage.
-The tool also includes an automatic option for testing all the possible combination configurations.
+To infer the role each stage of the pipeline plays, the proposed tool allows the parameter update to be enabled or disabled for each pipeline stage.
+The tool also includes an automatic option to test all the possible configuration combinations.
 As illustrated in Fig.~\ref{fig:pipelineUpdate}, the ground truth for this sentence pair is neutral.
 However, the model produces an incorrect label \emph{entailment}.
-The domain expert reassigns the prediction to \emph{neural}, which triggers model update optimization for $7$ different pipeline configurations.
+The domain expert reassigns the prediction to \emph{neutral}, which triggers the prediction update optimization for $7$ different pipeline configurations.
 Four configurations are shown in Fig.~\ref{fig:pipelineUpdate}(a)(b)(c)(d).
-The updated predictions are illustrated as blue squares, and the pointers highlighted the corresponding pipeline configuration.
+The updated predictions are illustrated as blue squares, and the pointers highlighted the corresponding pipeline configurations.
 
-Interestingly, all configurations except one are concentrated around the full \emph{neural} prediction.
-Referring back to the pipeline configuration visualization, we observe that the only configuration that failed to produce the correct label is the one, in which we only allow attention stage update.
+Interestingly, all configurations except one are concentrated around the full \emph{neutral} prediction.
+Referring back to the pipeline visualization, we observe that the only configuration that failed to produce the correct label is the one, in which we only allow to update attention stage of the model.
 %
 In other words, the update of attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
+Similar observation can be obtained for most examples we experimented.
 %The attention layer is less sensitive compared to encoding layer and classification layer.
@@
  \caption{
-Dependency tree provides valuable information which can help fix the prediction error.
+Dependency tree provides valuable information that can help fix the prediction error.
 In (a), the model mistakenly aligns the word green, which lead to wrong prediction.  
-After examining the dependency tree, we can see the two \textbf{green} are attached to different words.
+After examining the dependency tree (highlighted by pink squares), we can see the two \textbf{green} are attached to different words.
 In (b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected to \emph{neutral}. 
@@
 The attention computation in the NLI model does not take the grammar structure of the sentences into consideration,
-yet, the attention often can highlight the key elements of the sentence. 
+yet, the attention often highlight key elements of the sentence. 
 Therefore, domain experts wish to understand whether attention alone is sufficient to capture sentence structure. 
@@
 In the proposed system, we overlay the sentence dependency tree with the attention, which enables researchers to conduct comparisons between attention and grammar structure.
-As illustrated in Fig.~\ref{fig:depTreeExample}(a), the prediction of the sentence pair (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is \emph{entailment}, which is wrong.
-We can understand the reasoning by examining the attention, in which the word \textbf{green} in ``\textbf{green} jacket" is aligned to the \textbf{green} in ``\textbf{green} tea".
-Due to such an alignment, the model mistakenly believe the two \textbf{green} are used to describe the same thing (therefore, producing the \emph{entailment} label).
-However, as we examine the dependency tree, the two \textbf{green} are attached to different words, i.e., ``green" in \textbf{P} is attached to jacket, while ``green" in \textbf{H} is attached to tea.
-Therefore, they should not be aligned with the attention to allow the classifier make the right decision.
+As illustrated in Fig.~\ref{fig:depTreeExample}(a), the prediction of the sentence pair (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is wrong.
+We can infer the cause by examining the attention, in which the word \textbf{green} in ``\textbf{green} jacket" is aligned to the \textbf{green} in ``\textbf{green} tea".
+Due to such an alignment, the model mistakenly believe the two \textbf{green} are used to describe the same thing (therefore, predict \emph{entailment}).
+However, as we examine the dependency tree, the two \textbf{green} are attached to different words, i.e., ``green" in \textbf{P} is attached to jacket, while ``green" in \textbf{H} to tea.
+Therefore, they should not be aligned to allow the classifier make the right decision.
 %
@@
 %
-And more interestingly, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected to \emph{neutral}.
+And interestingly, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected (\emph{neutral}).
 
@@
 %
-Often the researchers have a set of experiments they plan to run, from which, they will likely develop new hypotheses for further analysis.
+The researchers start with a set of experiments they plan to run, from which, they will develop new hypotheses for further analysis.
 %
 In some way, we can think of such a process as a natural blend of all previously discussed scenarios.
-However,  instead of with specific goal in mind, the domain experts focus on probing around and see if they can find anything interesting or out-of-ordinary behaviors in the model.
+However, instead of with specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-ordinary behaviors in the model.
 %
-Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures a streamlined exploration experience that free the users from interruption and tedious operations, allow them to focus on the more productive activity.
+Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes, ensures a streamlined exploration experience that free the users from interruptions and tedious operations, allow them to focus on the more productive activities.
 

### 2018-03-30 paper/attention.tex
space squeeze

@@
-\begin{figure*}[htbp]
-\centering
-\vspace{-2mm}
-\includegraphics[width=1.0\linewidth]{attentionView}
-\vspace{-6mm}
-\caption{
-Attention visualization.
-In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
-The user can alter the attention values via the pop-up interface illustrated in (c).
-We overlay the dependency tree ($a_1$) grammar structure to highlight important words and simplify complex sentence to reduce clutter (d-e).
-In (f), we show the difference between two attention matrix (the comparison feature is controlled by the buttons in the top left of all attention plots ($a_2$) ).
-}
-\label{fig:attentionVis}
-\end{figure*}
-
 \subsection{Attention View}

### 2018-03-30 paper/evaluation.tex
space squeeze

@@
 
-The initial motivation for designing the proposed tool is driven by the error analysis challenges faces by NLP researchers working on natural language inference problem.
-We work closely with two NLP experts, and their constant evaluation and feedback have guided our entire design and development process.
+The initial motivation for designing the proposed tool is driven by the error analysis challenges faces by NLP researchers working on the natural language inference task.
+We work closely with two NLP experts, and their constant evaluation and feedback have guided the design and development process.
 %
-However, since two NLP experts are heavy involved in the design process, they may be blinded for the potential limitation of the tool due to familiarity.
-In order to undercover the limitation and identify the areas for improvements we gathered a wider audience from both visualization (4 researchers include 3 PhD student and one Postdoc Researcher) and NLP background (5 PhD students who are familiar with the concept of natural language inference and attention) for the evaluation of the tool.
+However, since the two NLP experts are heavy involved in the design process, they may be blinded for the potential problems of the tool due to familiarity.
+In order to undercover the limitation and identify areas for improvements we gathered a wider audience from both visualization (4 researchers include 3 PhD student and one Postdoc Researcher) and NLP background (5 PhD students who are familiar with the concept of natural language inference and attention) for the evaluation of the tool.
 %
 
-We first conduct a informal feedback session with the visualization group, with the goal to identify the potential interface design issues.
+We first conduct an informal feedback session with the visualization group, with the goal to identify the potential interface design issues.
 During the feedback session, we first explain the NLP concept in an easily to approach manner, and then demonstrate the feature of tool in detail, while answering questions and address comments.
 %
-From this session, we have gather a number of common complaints, including difficult to distinguish predictions, hard to recognize ground truth label, as well as the lack of legends to understand the key elements in several plot.
+From this session, we have gather a number of complaints and suggestion on improve the user interface.
+These  including difficult to distinguish predictions, hard to recognize ground truth label, as well as the lack of legends to understand the key elements in several plot.
 We address these interface issues in the version of tool presented to the NLP group.
 
-We conduct a more thorough evaluation session with the NLP group, in which each of the participants is first given 30 min to experiment with the tool after a overall feature demonstration.
-As the participants explore the tool,
-We will continue to answer more detailed question regarding the individual component, as well as how we implement the model update feature.
+We then conduct a revaluation session with the NLP group, in which each of the participants is given 30 minutes to experiment with the tool after an overall feature demonstration.
+As the participants explore the tool, we continue answering more detailed questions regarding the individual component, as well as on how we implement the model update feature.
 %

### 2018-03-30 paper/sentence.tex
space squeeze

@@
+\begin{figure*}[htbp]
+\centering
+\vspace{-2mm}
+\includegraphics[width=1.0\linewidth]{attentionView}
+\vspace{-6mm}
+\caption{
+Attention visualization.
+In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
+The user can alter the attention values via the pop-up interface illustrated in (c).
+We overlay the dependency tree ($a_1$) grammar structure to highlight important words and simplify complex sentence to reduce clutter (d-e).
+In (f), we show the difference between two attention matrix (the comparison feature is controlled by the buttons in the top left of all attention plots ($a_2$) ).
+}
+\label{fig:attentionVis}
+\vspace{-4mm}
+\end{figure*}
+
 \subsection{Sentence View}

### 2018-03-30 paper/discussion.tex
fix all pair update bug
update discussion

--- 2018-02-16 paper/discussion.tex
@@
 \section{Discussion}
+The initial learning curve and workflow setup cost of the tool are often the most significant barriers to adaptation.
+In the proposed system, we approach these challenges by designing the system as a python library rather than as a monolithic tool. 
+Just like a python plotting library, the different pieces of the visualization can be accessed individually, which help ease the initial learning curve. 
+The individual components can also be combined in any configuration desired by the user via a simple Python API to better fit into one's workflow.
+More importantly, the library based design allows easily integrate with existing model implemented in python (a code example is illustrated in \textbf{Appendix B}).
+%defined and combined  The long term goal for the 
+Even though the current setup for the proposed tool is only suitable for natural language inference task.
+However, due to the modular design and the many shared attribution among end-two-end NLP models we can readily extends the system to handle other tasks.
+We plan to add support for more NLP task, such as neural machine translation, question and answer, in the future.
 
-\begin{itemize}
-    \item how the visualization approaches generalizes to other NLP task
-    \item limitation
-\end{itemize}
+One hard to address limitation of the tool is the quality of the perturbed sentences. 
+Since we rely on WordNet to generate the perturbation, which has a quite inclusive definition for synonymous.
+Often, we can identify perturbed sentences that are not particularly meaningful (e.g., sentences with very obscured words or usages).
+Even if all the words are meaning, currently, there is no way we can verify whether the perturbed sentence is valid natural language composition or not.
+%
+However, the perturbation of sentence is an open research area on its own. 
+%As better method appears, we can easily swap out the sentence perturbation functionality
+
+To sum up, this work introduces the NLIVZ, a perturbation-driven visual interrogation system that provides the expert with a streamlined exploration environment.
+The proposed system frees the researchers from interruptions and tedious chores and allows them to focus on the more productive activities.
+
+%\begin{itemize}
+%    \item how the visualization approaches generalizes to other NLP task
+%    \item limitation
+%    \item future direction
+%\end{itemize}

### 2018-03-30 paper/evaluation.tex
remove test

@@
 \section{Evaluation and Feedback}
-%\shusen{discussed feedback and comment about the proposed system}
 
@@
 However, since the two NLP experts are heavy involved in the design process, they may be blinded for the potential problems of the tool due to familiarity.
-In order to undercover the limitation and identify areas for improvements we gathered a wider audience from both visualization (4 researchers include 3 PhD student and one Postdoc Researcher) and NLP background (5 PhD students who are familiar with the concept of natural language inference and attention) for the evaluation of the tool.
-%
+In order to undercover the limitation and identify areas for improvements we gathered a wider audience from both visualization (4 researchers include 3 Ph.D.
+level student and one postdoc researcher) and NLP background (5 Ph.D.
+level students who are familiar with the concept of natural language inference and attention) for the evaluation of the tool.
 

### 2018-03-30 paper/predSummary.tex
re-arrange figure
space squeeze
remove test

@@
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{summaryView}
+ \vspace{-6mm}
+ \caption{
+Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
+We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
+%
+The user can select the treemap to focus on the specific type of scenarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
+The selection can be further narrowed down by selecting the bin in the histogram.
+In (c) and (d), each point corresponds to one prediction.
+ }
+ \vspace{-2mm}
+\label{fig:summaryView}
+\end{figure}
+
 \subsection{Summary View}
@@
 We can focus on only one individual example at a time for a detailed analysis using the combination of all previously discussed views.
-As a result, how to select a pair of sentences of interest from the development or test dataset, which consists of close to $10k$ examples, is an obvious challenge.
+As a result, how to select a pair of sentences of interest from the development dataset, which consists of close to $10k$ examples, is an obvious challenge.
 % - what is the interesting pairs
@@
 
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{summaryView}
- \caption{
-Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
-We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
-%
-The user can select the treemap to focus on the specific type of scenarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
-The selection can be further narrowed down by selecting the bin in the histogram.
-In (c) and (d), each point corresponds to one prediction.
- }
-\label{fig:summaryView}
-\end{figure}
-
 %The all pair

### 2018-03-30 paper/appendix_modelDescription.tex
minor change in appendix

@@
 
+\textbf{Comment} $\overleftarrow{\boldsymbol{a}}$ and $\overrightarrow{\boldsymbol{a}}$ are referred as \emph{att1} and \emph{att2} in the visualization.
+
 \subsection{Classifier} \label{sec:cls}
@@
 From the user point of view, the following python script is all the code the domain expert needs to link the NLP model with the visual interface.
-The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to supplied by the NLP model.
+The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to be supplied by the NLP model.
 

### 2018-03-30 paper/appendix_modelDescription.tex
minor change in appendix

@@
 two-layer ReLU) and $[\cdot|\cdot]$ denotes concatenation.
-With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict weight on each entailment score:
+With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict score on each entailment label:
 \begin{align}

### 2018-03-30 paper/application.tex
update discussion
change example in 6.2

@@
 On the flip side, we may produce the right predictions for the ``wrong'' reason (i.e., incorrect attention). 
-As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, the word \textbf{break} and \textbf{sit} should not align with each other (Fig.~\ref{fig:wrongAlignRightPred}(a)), however, it still produce the correct \emph{neutral} label (Fig.~\ref{fig:wrongAlignRightPred}(b)).
+As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, the word \textbf{take} and \textbf{next} should not align with each other (Fig.~\ref{fig:wrongAlignRightPred}(a)), however, it still produce the correct \emph{neutral} label (Fig.~\ref{fig:wrongAlignRightPred}(b)).
 %
@@
 %
-Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes, ensures a streamlined exploration experience that free the users from interruptions and tedious operations, allow them to focus on the more productive activities.
 

### 2018-03-30 paper/application.tex
remove figure, finish discussion

@@
 
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{wrongAlignRightPred}
- \caption{
-The model may produces the right prediction for the ``wrong'' reason, i.e., attention.
-The word \textbf{break} and \textbf{sit} should not align with each other (a). Yet, based on the attention, model still produces the correct prediction (b).
-}
-\label{fig:wrongAlignRightPred}
-\end{figure}
+%\begin{figure}[htbp]
+%\centering
+%\vspace{-2mm}
+% \includegraphics[width=1.0\linewidth]{wrongAlignRightPred}
+% \caption{
+%The model may produces the right prediction for the ``wrong'' reason, i.e., attention.
+%The word \textbf{break} and \textbf{sit} should not align with each other (a). Yet, based on the attention, model still produces the correct prediction (b).
+%}
+%\label{fig:wrongAlignRightPred}
+%\end{figure}
 
@@
 For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
-In the previous example, we show that the perfect alignment does not necessarily guarantee a correct prediction.
+We have shown that the perfect alignment does not necessarily guarantee a correct prediction.
 %
 On the flip side, we may produce the right predictions for the ``wrong'' reason (i.e., incorrect attention). 
-As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, the word \textbf{take} and \textbf{next} should not align with each other (Fig.~\ref{fig:wrongAlignRightPred}(a)), however, it still produce the correct \emph{neutral} label (Fig.~\ref{fig:wrongAlignRightPred}(b)).
+%As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, 
+For example the sentence pair (\emph{H}: ``A couple is taking a break from bicycling.'', \textbf{H}: ``sisters sit next to their bikes.'').
+The word \textbf{take} and \textbf{next} should not align with each other,
+%(Fig.~\ref{fig:wrongAlignRightPred}(a)), 
+yet, it still produce the correct \emph{neutral} label.% (Fig.~\ref{fig:wrongAlignRightPred}(b)).
 %

### 2018-03-30 paper/discussion.tex
remove figure, finish discussion

--- 2018-02-16 paper/discussion.tex
@@
 \section{Discussion}
+The current setup for the proposed tool is only suitable for natural language inference task.
+However, due to the modular design and the many shared attribution among end-two-end NLP models, we can readily extend the system to handle other tasks.
+We plan to add support for more NLP task, such as neural machine translation, question and answer, in the future.
+%
+From our evaluation process, we found that the quality of automatic perturbed sentences can be a potential limitation of the tool.
+Since we rely on WordNet to generate the perturbation, which has a rather inclusive definition for synonymous.
+Often, we can identify perturbed sentences that are not particularly meaningful (e.g., sentences with very obscured words or usages).
+Even if all the words are meaning, currently, there is no way we can verify whether the perturbed sentence is valid natural language composition or not.
+%
+However, from natural language process point of view the perturbation of sentence while maintaining semantic and sentence correctness is an open research area on its own. 
+%As better method appears, we can easily swap out the sentence perturbation functionality
 
-\begin{itemize}
-    \item how the visualization approaches generalizes to other NLP task
-    \item limitation
-\end{itemize}
+The initial learning curve and workflow setup cost of the tool are often the most significant barriers to adaptation.
+In the proposed system, we approach these challenges by designing the system as a python library rather than as a monolithic standalone application. 
+Just like a python plotting library, the different pieces of the visualization can be accessed individually, which help ease the initial learning curve. 
+The individual components can also be combined in any configuration desired by the user via a simple Python API to better fit into one's workflow.
+More importantly, the library based design allows easily integrate with existing model implemented in python (see the code example in \textbf{Appendix B}).
+%defined and combined  The long term goal for the
+
+To conclude, this work introduces the \textbf{NLIVZ}, a perturbation-driven visual interrogation system that provides the expert with a streamlined exploration environment for testing their hypothesis and obtain intuition about the model.
+The proposed system frees the researchers from interruptions and tedious operations and allows them to focus on the more productive activities.
+
+%\begin{itemize}
+%    \item how the visualization approaches generalizes to other NLP task
+%    \item limitation
+%    \item future direction
+%\end{itemize}

### 2018-03-30 paper/application.tex
minor fix

@@
 %
-As illustrated in Fig.~\ref{fig:att2pred} (d), after the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary (Fig.~\ref{fig:att2pred}(d)), but the corrected attention fails to produce a conclusive \emph{entailment} prediction.
+As illustrated in Fig.~\ref{fig:att2pred} (d), after the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary (Fig.~\ref{fig:att2pred}(d)), but the corrected attention fails to produce a conclusive \emph{entailment} prediction (a case where the attention edit corrects the final prediction is shown in Fig.~ref{fig:depTreeExample}).
 %
@@
 %As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, 
-For example the sentence pair (\emph{H}: ``A couple is taking a break from bicycling.'', \textbf{H}: ``sisters sit next to their bikes.'').
-The word \textbf{take} and \textbf{next} should not align with each other,
+For example, in the sentence pair (\textbf{P}: ``A couple is taking a break from bicycling.'', \textbf{H}: ``sisters sit next to their bikes.''), the word \textbf{take} and \textbf{next} should not align with each other,
 %(Fig.~\ref{fig:wrongAlignRightPred}(a)), 
 yet, it still produce the correct \emph{neutral} label.% (Fig.~\ref{fig:wrongAlignRightPred}(b)).
-%
+
 %By looking into the model decision making process, we can assess whether the model is behaving as intended. 

### 2018-03-30 paper/evaluation.tex
finsihed the full draft

@@
 \section{Evaluation and Feedback}
+The motivation for designing the proposed tool is driven by the error analysis challenges faced by our long-term collaborators working on natural language inference research.
+During the entire design and development process, we work closely with two NLP experts, and their constant evaluation and feedback have helped shape the tool we see today.
+%
+Since these two NLP experts are heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.
+To uncover the limitation and identify areas for improvements, we gathered a wider audiences from either visualization (4 researchers include 3 Ph.D.
+level student and one postdoc researcher) or NLP background (5 Ph.D.
+level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.
 
-The initial motivation for designing the proposed tool is driven by the error analysis challenges faces by NLP researchers working on the natural language inference task.
-We work closely with two NLP experts, and their constant evaluation and feedback have guided the design and development process.
+With the goal to identify the potential interface design issues, we first conduct an informal demonstration-and-feedback session with the visualization group.
+We start by explaining the basic natural language inference concept.
+We then demonstrate the features of the tool in detail while answering questions and address comments.
 %
-However, since the two NLP experts are heavy involved in the design process, they may be blinded for the potential problems of the tool due to familiarity.
-In order to undercover the limitation and identify areas for improvements we gathered a wider audience from both visualization (4 researchers include 3 Ph.D.
-level student and one postdoc researcher) and NLP background (5 Ph.D.
-level students who are familiar with the concept of natural language inference and attention) for the evaluation of the tool.
+From this session, we have gathered complaints and suggestions on various aspect of the visual interface.
+Some of the identified issues include: (1) difficult to distinguish different type of predictions (distinct colors are added for the final version); (2) hard to recognize ground truth label (now, we use a green rectangle to indicate the ground truth); (3) lack of legends to understand the key elements in plots (legends are added).
+We address these interface issues before presenting the final version to the NLP group.
 
-We first conduct an informal feedback session with the visualization group, with the goal to identify the potential interface design issues.
-During the feedback session, we first explain the NLP concept in an easily to approach manner, and then demonstrate the feature of tool in detail, while answering questions and address comments.
+We conduct individual revaluation session with each participant from the NLP group, in which the participant is given 30 minutes to experiment with the tool after an overall feature demonstration. 
 %
-From this session, we have gather a number of complaints and suggestion on improve the user interface.
-These  including difficult to distinguish predictions, hard to recognize ground truth label, as well as the lack of legends to understand the key elements in several plot.
-We address these interface issues in the version of tool presented to the NLP group.
+Since both the matrix and graph-based visual encoding is the most common attention representations used in NLP literature, most the participant can utilize them immediately and find the linked highlighting feature of the two views quiet useful.
+% 
+Once the participants familiarize with the tool, the first thing they try is often typing two similar sentences and examine the attention and prediction.
+After that, they will modified some words, or negate the hypothesis sentence, then check the attention and prediction again.
+%
+Such a ``perturb and observe'' operation demonstrates the most fundamental exploration strategy and matches well with the perturbation-driven paradigm the proposed tool aim to support.
 
-We then conduct a revaluation session with the NLP group, in which each of the participants is given 30 minutes to experiment with the tool after an overall feature demonstration.
-As the participants explore the tool, we continue answering more detailed questions regarding the individual component, as well as on how we implement the model update feature.
+One participant shows us two examples after a quick exploration session. 
+In the first example, he identifies a case where the wrong attention alignment produces a correct final prediction.
 %
-One participant hypothesis about the role attention is playing.
-After playing with the tool, he show us two sentence pair that he think is interesting.
-One sentence give a correct final prediction but he tell us that when he see the attention layer, the alignment is incorrect.
-At the other example, he show us a sentence pair which give a wrong prediction, he force two sentence?s attention to align but the final prediction is still incorrect.
-He tell us that through those two example  he can tell that a alignment may not give the correct prediction and correct prediction does not mean correct alignment.
+In the other example, he finds a sentence pair with the incorrect attention that produces a wrong prediction. 
+However, even after he forces the correct alignment, the prediction result remain incorrect. He believes observation such as these will provide valuable insights for him to interpret the model. 
 %
-The other interesting observation that he get is that once he force the incorrect final prediction to the ground truth label.
-In the update pipeline,  he observed that only update the attention stage won?t make the current sentence pair to the correct prediction.
+Another participant comment that the ability to enable and disable update in the pipeline view is beneficial.
+
+The participants also identify potential issues and places for improvement. 
+One participant wishes the pipeline view could provide more detailed information compared to the current aggregated histogram visualization. 
+Another participant suggests the possibility to examine multiple similar examples at a time (instead of one by one). 
 %
-After explaining the tool, the one participant try to use two same sentences and check how each component of the platform show.
-He also negate the meaning of a sentence ``A couple is taking a break from bicycling .''  by using ``A couple is not taking a break from bicycling .'' and see whether the relationship between two sentence is contradiction.
-He also comment that the ability to enable and disable update in the pipeline view is really helpful.
+Also, for the participants do not focus on NLI research, understand all the views at first can be a bit challenging.
+However, this issue can be addressed by the modular design, as the user can simply enable, only the sentence, attention, and prediction views, at first.
 %
-Overall, all the user think this tool is very convenient for them to verify their hypothesis and help them build a better intuition to improve the current model.
+Overall, all the participants believe the proposed tool is very convenient for conduction experiment and exploring various hypothesis, which is essential to build intuitions about the model.

### 2018-03-30 paper/paper_entailVis.tex
update section 6.4
update figures
update teaser

@@
 \def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
+
+%make paper compact
+\setlength{\parskip}{0.04cm}
+\setlength{\parindent}{0.7em}
 
@@
 \teaser{
-% \vspace{-8mm}
+\vspace{-4mm}
  % \includegraphics[width=0.78\linewidth]{teaser}
@@
  \centering
- % \vspace{-3mm}
+ \vspace{-4mm}
   \caption{
 The interface of the NLIZE system.
-During exploration, we can filter through a large number of sentence examples summarized in (A) and select examples of interest displayed in (B).
-The model internal information (attention) is displayed in (D) and (E).
-The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (F).
-Finally, the high-level model structure and the updates to the model are summarized in (C).
+During exploration, we can filter through a large number of sentence pairs summarized in (a) and the current selected pair is displayed in (b).
+The model internal information (attention) is displayed in (d) and (e).
+The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (f).
+Finally, the high-level model structure and the updates to the model are summarized in (c).
 }
+% \vspace{-2mm}
 \label{fig:teaser}

### 2018-03-30 paper/relatedWorks.tex
space squeeze
update teaser

@@
 
-\textbf{Visualization Of NLP Models.}
+\textbf{Visualization of NLP Models.}
 Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studys have been dedicated to neural language processing models.
@@
 %As discussed in the introduction, the experts guided exploration calls for the ability to interact with internal of the model in a dynamic setting. 
-
-All the previously discussed works either focus on the training process or examine the trained model as a fixed object.
+%
+All the previously discussed NLP model visualization works either focus on the training process or examine the trained model as a fixed object.
 In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that is not possible before.

### 2018-03-30 paper/pipeline.tex
re-arrange figure
update section 6.4
space squeeze
space saving

@@
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{pipelineView}
+ \vspace{-6mm}
+ \caption{
+The pipeline view provides the visual representation of three-stage (encoder, attention, classifier) model. 
+%The pipeline view, by showing the aggregated gradient distribution, informs the user about how different parts of the model respond to the optimization.
+ %
+In the proposed tool, we allow the model parameter to be updated to correct a prediction error. 
+The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the blue ``parameter'' area to enable or disable its update (the legend is shown in (d)).
+In (c), we select whether we want to use the current update setting as displayed or try all the configuration combinations as the parameter update can be enabled or disabled for each stage.
+ }
+\label{fig:pipelineView}
+\vspace{-2mm}
+\end{figure}
+
 \subsection{Pipeline View}
@@
 \begin{equation}
-\underset{w'}{\mathrm{argmin}}( C \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||^2)
+\underset{\mathbf{W}'}{\mathrm{argmin}}( C \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||^2)
 \end{equation}
@@
 
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipelineView}
- \caption{
- The pipeline view provides the visual representation of three-stage (encoder, attention, classifier) model.
-In the proposed tool, we allow the model parameter to be updated to correct a prediction error.
-The pipeline view, by showing the aggregated gradient distribution, informs the user about how different parts of the model respond to the optimization.
- %
- The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ).
-In (c), we select whether we want to use the current update setting as displayed or try all the possible configuration combinations (i.e., each stage's parameter update can be enabled or disabled).
- }
-\label{fig:pipelineView}
-\end{figure}
-
 % \textbf{Margin-Infused Relaxed Algorithm (MIRA)}

### 2018-03-30 paper/predSummary.tex
space saving

@@
  \caption{
-Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
-We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
+%Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
+We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) shows the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
 %
-The user can select the treemap to focus on the specific type of scenarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
+The user can select the treemap to focus on the specific type of scenarios (e.g., E/E) and reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
 The selection can be further narrowed down by selecting the bin in the histogram.
-In (c) and (d), each point corresponds to one prediction.
+In (c) and (d), each point corresponds to one sentence pair.
  }
@@
 %  - how to identify the sensitivity of pairs
-We can focus on only one individual example at a time for a detailed analysis using the combination of all previously discussed views.
-As a result, how to select a pair of sentences of interest from the development dataset, which consists of close to $10k$ examples, is an obvious challenge.
+We can focus on only one example at a time for a detailed analysis using the combination of all previously discussed views.
+Therefore, how to select a pair of sentences of interest from the development dataset, which consists of close to $10k$ examples, is an obvious challenge.
 % - what is the interesting pairs
-In addition, the experts are also interested in obtaining a high-level understanding beyond the information the prediction accuracy provides of the behavior of the $10k$ sentence pairs.
+In addition, the experts are also interested in obtaining a high-level understanding beyond the information prediction accuracy provides.% of the behavior of the $10k$ sentence pairs.
 %
-These two goals are the two sides of the same coin, the selection task will become much easier if we can generate a good visual summary of the $10k$ examples that help experts obtain a deeper understanding of the whole $10k$ examples.
+These two goals are the two sides of the same coin. 
+The selection task will become easier if we can generate a good visual summary of the $10k$ examples.% that could also help experts obtain a deeper understanding of the whole $10k$ examples.
 
-To address these challenges, we introduce the summary view (see Fig.~\ref{fig:teaser}(A) ), which consists of a treemap, a histogram, and a scatterplot, to summarize the prediction results of the $10k$ examples, and provide the ability to drill down to an individual example for detailed analysis.
+To address these challenges, we introduce the summary view (see Fig.~\ref{fig:teaser}(a)), which consists of a treemap, a histogram, and a scatterplot, to summarize the prediction results of the $10k$ examples and provide the ability to drill down to individual examples for detailed analysis.
 %treemap for prediction
-As illustrated in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the different combinations of the ground truth label and the model prediction.
-In the treemap, the green blocks indicate examples where the predicted label agrees with the ground truth label, whereas the orange blocks indicate disagreement between the labels.
+As illustrated in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the different combinations of the ground truth label and the predicted label.
+The green treemap blocks correspond to examples with correct predictions, whereas the orange blocks indicate failures.
 The size of the block encodes the number of examples belonging to each category.
 %
-By clicking on the treemap cell, we can narrow down the selection by focusing on specific scenarios.
+By clicking on the treemap blocks, we can narrow down the selection by focusing on specific scenarios.
 %
-As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are revealed to focus on the selected subset.
-The histogram shows the distribution of the prediction sensitivity in this category.
-For each original pair, the sensitivity is defined by the ratio between the number of unchanged predictions among the perturbed pairs and the all the perturbed pairs.
-In other words, if we generated 100 sentence pairs via the automated sentence perturbation (i.e., replace nouns and verbs with synonymous), and after we predict the labels on all 100 pairs, if 80 out of the 100 maintain the original prediction label, we will have a sensitivity of 0.8.
-The \emph{sensitivity} measures how likely it is a sentence pair will change its prediction after applying minor perturbations to the original, which helps the expert infer the model stability on the given example.
+As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are shown.
+The histogram shows the distribution of the prediction sensitivity in the selected category.
+For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and the all the perturbed pairs.
+Considering we generated 100 pairs via the automated sentence perturbation (i.e., replace nouns and verbs with synonymous), the stability is 0.8 if 80 out of the 100 maintain the original prediction label.
+%The \emph{stability} measures how likely a sentence pair will change its prediction after applying minor perturbations.% which helps the expert infer the model stability on the given example.
 %
@@
 %
-In the scatterplot, besides showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{sensitivity}.
-For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.
+In the scatterplot, besides showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{stability} number (i.e., if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy).
+%For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.
 

### 2018-03-30 src/visPackage/static/components/evaluationComponent.js

@@ -100,12 +100,14 @@ class evaluationComponent extends baseComponent {
         // console.log(stabilities);
         this.histo.setSample(data, d => d.stability);
         this.histo.setTitle("Sensitivity");
-        this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
+        // this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
+        this.scatter.setData(data, ["Stability", "PerturbCount"],
             d => [d.stability, d.perturbCount]);
     }
 
     updateScatterplot(data) {
-        this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
+        // this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
+        this.scatter.setData(data, ["Stability", "PerturbCount"],
             d => [d.stability, d.perturbCount]);
     }
 
@@ -159,12 +161,4 @@ class evaluationComponent extends baseComponent {
         }
     }
 
-    // parseFunctionReturn(msg) {
-    //     switch (msg["func"]) {
-    //         case "loadSummaryStatistic":
-    //             //load data
-    //             console.log(msg);
-    //             break;
-    //     }
-    // }
 }

### 2018-03-30 paper/implementation.tex
update figure

@@
 \label{sec:implementation}
-We design the tool with flexibility and extensibility in mind.
+The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
+In the proposed system, we approach these challenges by designing the system as a python library rather than as a monolithic standalone application. 
+Just like a python plotting library, the different pieces of the visualization can be accessed individually, which help ease the initial learning curve. 
+The individual components can also be combined in any configuration desired by the user via a simple Python API to better fit into one's workflow.
+More importantly, the library based design allows easily integrate with existing model implemented in python.
+%
+To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models (see the code example in \textbf{Appendix B}).
+
+%We design the tool with flexibility and extensibility in mind.
 One of the key objectives is to allow easy integration with the existing NLP workflow.
@@
 
-To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their models.
-The code (consists only a few lines of code) used to create the visualization in this paper is included in appendix B.
 %

### 2018-03-30 src/visPackage/static/components/evaluationComponent.js

@@ -99,7 +99,7 @@ class evaluationComponent extends baseComponent {
         // var stabilities = data.map(d => d.stability);
         // console.log(stabilities);
         this.histo.setSample(data, d => d.stability);
-        this.histo.setTitle("Sensitivity");
+        this.histo.setTitle("Stability");
         // this.scatter.setData(data, ["Sensitivity", "PerturbCount"],
         this.scatter.setData(data, ["Stability", "PerturbCount"],
             d => [d.stability, d.perturbCount]);

### 2018-03-30 paper/discussion.tex
length fit

@@
 
-The initial learning curve and workflow setup cost of the tool are often the most significant barriers to adaptation.
-In the proposed system, we approach these challenges by designing the system as a python library rather than as a monolithic standalone application. 
-Just like a python plotting library, the different pieces of the visualization can be accessed individually, which help ease the initial learning curve. 
-The individual components can also be combined in any configuration desired by the user via a simple Python API to better fit into one's workflow.
-More importantly, the library based design allows easily integrate with existing model implemented in python (see the code example in \textbf{Appendix B}).
-%defined and combined  The long term goal for the
-
 To conclude, this work introduces the \textbf{NLIVZ}, a perturbation-driven visual interrogation system that provides the expert with a streamlined exploration environment for testing their hypothesis and obtain intuition about the model.

### 2018-03-30 paper/pipeline.tex
update figure
length fit

@@
 \vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipelineView}
- \vspace{-6mm}
+ \includegraphics[width=0.95\linewidth]{pipelineView}
+ \vspace{-3mm}
  \caption{
@@
 In the proposed tool, we allow the model parameter to be updated (via an optimization) to correct a prediction error (\textbf{T3}).
-The pipeline view, by visualizing the aggregated gradient distribution, informs the user about how each stage of the model responds to the optimization.
+The pipeline view, by visualizing the aggregated gradient distribution, informs the user about how each stage responds to the optimization.
 
 There are many ways to update the model to correct a prediction.
-A simple way to is by applying standard backpropagation that overfits to the example.
+The simplest approach is applying standard backpropagation and overfits to the example.
 However, without any constraint, the update step may alter the model in unexpected ways.
 % \shusen{what is the benefit of using mira?}
-Instead, we adopt the same idea in \emph{margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the L2-norm of the parameter change.
+Instead, we adopt the idea in \emph{margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the L2-norm of the parameter change.
 Therefore, in the proposed tool, we obtain the target parameters by the following:
 \begin{equation}
-\underset{\mathbf{W}'}{\mathrm{argmin}}( C \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||^2)
+\underset{\mathbf{W}'}{\mathrm{argmin}}( C \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W_o}||^2)
 \end{equation}
-where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural model, $\mathbf{W}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the parameters to update, and $C$ is the weighting term, which determines whether we intended to emphasize more on obtaining better fitting or deviating less from the original model.
+where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural model, $\mathbf{W_o}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the parameters to update, and $C$ is the weighting term, which determines whether we intended to emphasize more on obtaining better fitting or deviating less from the original model.
 Due to the nonconvex nature of the neural networks, we use SGD to optimize the above combined loss function.
 %
-With this formation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
+With this formulation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
 

### 2018-03-30 paper/predSummary.tex
length fit

@@
 %
-In the scatterplot, besides showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{stability} number (i.e., if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy).
+In the scatterplot, besides showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{stability} number (i.e., if the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} number is likely to be quite noisy).
 %For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.

### 2018-03-30 paper/application.tex
finsihed the full draft
space saving
length fit
update application 6.1

@@
 To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool in their analysis workflow.
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{predictStability}
+ \vspace{-6mm}
+ \caption{
+Prediction stability assessment.
+In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type of predictions over the entire development set (10k examples).
+The user can drill down to individual examples by using the interface described in Fig.~\ref{fig:summaryView}.
+In (d), we illustrate a highly unstable prediction, where the original pair's prediction is near a decision boundary (i.e., the yellow circle is between \emph{entailment} and \emph{neutral}).
+In (e), we show another example of unstable predictions, in which the prediction changes drastically with a minor perturbation (see ($\mathbf{e_1}$)).
+%( For the perturbed pair , the word \textbf{pile} is replaced by \textbf{heap} in the hypothesis sentence).
+}
+\label{fig:predictStability}
+\vspace{-3mm}
+\end{figure}
 
@@
 
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{predictStability}
- \vspace{-4mm}
- \caption{
-Prediction stability assessment.
-In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
-The user can drill down to individual examples by filtering via the histogram or scatterplot (see Fig.~\ref{fig:summaryView}).
-For highly unstable prediction, we often observe the original prediction is near a decision boundary (e.g., the yellow circle in (e) corresponds to a prediction that is at the boundary between \emph{entailment} and \emph{neutral}), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word \textbf{pile} is replaced by \textbf{heap} in the hypothesis sentence).
-}
-\label{fig:predictStability}
-\vspace{-2mm}
-\end{figure}
-
 In Fig.~\ref{fig:predictStability}(a)(b)(c), we compare the overall prediction stability (regarding synonymous perturbation) for all correct predictions in the development set (10k examples in total).
@@
 
-Besides presenting the summary view, the tool also allows the user to quickly narrow down the selection to a single example by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}).
+Besides presenting the summary view, the tool also allows the user to quickly narrow down the selection to a single example by filtering via the histogram and scatterplot (see details in Fig.~\ref{fig:summaryView}).
 %
-Through the exploration of many samples with low stabilities (i.e., high sensitivities values in the plots), domain experts notice that many highly unstable outliers are from sentence pairs where the predictions are near the decision boundary (see Fig.~\ref{fig:predictStability}(e), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
-However, some predictions, such as the one illustrated in Fig.~\ref{fig:predictStability}(d) can alter the prediction quite drastically with minor perturbation (shown in Fig.~\ref{fig:predictStability}$d_1$, where the word \textbf{heap} is replaced by \textbf{pile} in the hypothesis sentence).
-In the following section, we will examine what happened inside the model and hypothesize the cause of failure (see Fig.~\ref{fig:att2pred}).
+Through the exploration of many samples with low stabilities (i.e., high sensitivities values in the plots), domain experts notice that many highly unstable outliers are from sentence pairs where the predictions are near the decision boundary (see Fig.~\ref{fig:predictStability}(d), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
+%
+However, we can also find sentence pairs, such as the one illustrated in Fig.~\ref{fig:predictStability}(e), in which the prediction is altered drastically with minor perturbations (e.g., replace the word \textbf{pile} with \textbf{heap} in ``pile of snow'').
+In the following section, we examine what happened inside the model and hypothesize the cause of failure (see Fig.~\ref{fig:att2pred}).
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{att2pred}
+ \vspace{-6mm}
+ \caption{
+Editing the original attention (a) to correctly align the word "heap" with "pile" as shown in (b) (these two words are highlighted in orange).
+The change of attention leads to the change of prediction from neutral to the class boundary between \emph{neutral} and \emph{entitlement}.
+%
+}
+\label{fig:att2pred}
+\end{figure}
+
 % perturb input, attention
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{pipelineUpdate}
+  \vspace{-6mm}
+ \caption{
+Experiment with all configurations for the label reassignment optimization.
+As shown in (d), the update of attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
+ }
+  \vspace{-4mm}
+\label{fig:pipelineUpdate}
+\end{figure*}
+
 \subsection{Scenario 2: Examine the Decision Making Process}
@@
 This example should be rather straightforward for the model since there are only minor differences between the \textbf{P} and \textbf{H1}/\textbf{H2}.
-
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{att2pred}
- \caption{
-Editing the original attention (a) to correctly align the word "heap" with "pile" as shown in (b) (these two words are highlighted in orange).
-The change of attention leads to the change of prediction from neutral to the class boundary between \emph{neutral} and \emph{entitlement}.
-%
-}
-\label{fig:att2pred}
-\end{figure}
 
@@
 
-\begin{figure*}[t]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipelineUpdate}
- \vspace{-2mm}
- \caption{
-Experiment with all configurations for the label reassignment optimization.
-As shown in (d), the update of attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
- }
-\label{fig:pipelineUpdate}
-\end{figure*}
-
 To infer the role each stage of the pipeline plays, the proposed tool allows the parameter update to be enabled or disabled for each pipeline stage.
@@
  \includegraphics[width=1.0\linewidth]{depTreeExample}
+  \vspace{-6mm}
  \caption{
@@
 \label{fig:depTreeExample}
+ \vspace{-4mm}
 \end{figure*}

### 2018-03-30 paper/discussion.tex
update application 6.1

@@
 
-To conclude, this work introduces the \textbf{NLIVZ}, a perturbation-driven visual interrogation system that provides the expert with a streamlined exploration environment for testing their hypothesis and obtain intuition about the model.
-The proposed system frees the researchers from interruptions and tedious operations and allows them to focus on the more productive activities.
-
-%\begin{itemize}
-%    \item how the visualization approaches generalizes to other NLP task
-%    \item limitation
-%    \item future direction
-%\end{itemize}
+To conclude, this work introduces a perturbation-driven visual interrogation system that provides the expert with a streamlined exploration environment for testing hypothesis and obtain intuition about the model.
+The proposed system frees the researchers from interruptions and tedious operations, therefore, allows them to focus on the more productive activities.

### 2018-03-30 paper/evaluation.tex
update application 6.1

@@
 Since these two NLP experts are heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.
-To uncover the limitation and identify areas for improvements, we gathered a wider audiences from either visualization (4 researchers include 3 Ph.D.
-level student and one postdoc researcher) or NLP background (5 Ph.D.
+To uncover the limitation and identify areas for improvements, we gathered a wider audience from either visualization (4 researchers include 3 Ph.D.
+level students and one postdoc researcher) or NLP background (5 Ph.D.
 level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.
@@
 From this session, we have gathered complaints and suggestions on various aspect of the visual interface.
-Some of the identified issues include: (1) difficult to distinguish different type of predictions (distinct colors are added for the final version); (2) hard to recognize ground truth label (now, we use a green rectangle to indicate the ground truth); (3) lack of legends to understand the key elements in plots (legends are added).
+Some of the identified issues include: (1) difficult to distinguish different type of predictions (distinct colors are added to the final version); (2) hard to recognize ground truth label (now, we use a green rectangle to indicate the ground truth); (3) lack of legends to understand the key elements in plots (legends are added).
 We address these interface issues before presenting the final version to the NLP group.
@@
 Once the participants familiarize with the tool, the first thing they try is often typing two similar sentences and examine the attention and prediction.
-After that, they will modified some words, or negate the hypothesis sentence, then check the attention and prediction again.
+After that, they will modify some words, or negate the hypothesis sentence, then check the attention and prediction again.
 %
@@
 %
-Overall, all the participants believe the proposed tool is very convenient for conduction experiment and exploring various hypothesis, which is essential to build intuitions about the model.
+Overall, all the participants believe the proposed tool is very convenient for conduction experiment and exploring various hypothesis, which is essential for building intuitions about the model.

### 2018-03-30 paper/task.tex
update task

@@
 
-\item To begin with, understanding how perturbation (e.g., replacing words with synonymous) of the input affects the prediction is the crucial part of error analysis.
+\item \textbf{T1}: Understand the stability of a prediction, i.e., how perturbation of input affects the behavior of the model?
+
+\item \textbf{T2}: Examine the attention mechanism, i.e., what is the relationship between input and attention and how does the attention affect the prediction?
+
+\item \textbf{T3}: When the predicted label is incorrect, what does it take to fix the model? What is the effect of updating different stages of the model?
+
+%\item To begin with, understanding how perturbation (e.g., replacing words with synonymous) of the input affects the prediction is the crucial part of error analysis.
 It not only measures the prediction sensitivity, but also helps reveal the potential source of the errors in the input (\textbf{T1}).
@@
 %Understand how attention affect the prediction.
-\item In addition, we study the role and mechanism of attention by examining how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
+%\item In addition, we study the role and mechanism of attention by examining how perturbation in the input sentence affect the attention, and how changes in attention affect prediction (\textbf{T2}).
 %Study the relationship between model stages (encoder, attention, classifier) and the prediction
 
-\item So far, we focus on how changes in earlier stage of the model affect later stages or the final prediction.
+%\item So far, we focus on how changes in earlier stage of the model affect later stages or the final prediction.
 However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction.

### 2018-03-31 paper/background.tex
space squeeze
update figures
update teaser
add open source comment add title to the appendix

@@
 \begin{table}[htbp]
+\vspace{-2mm}
 \label{tab:NLI}
@@
 \end{tabular}
+\vspace{-2mm}
 \end{table}
@@
 introduced a large corpus~\cite{BowmanAngeliPotts2015} for NLI tasks, which has helped spawn a new wave of effective neural network models for those tasks.
-Here, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.
+Here, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset (see \textbf{Appendix A} for a detailed description of the model).
 
@@
 \begin{figure}[htbp]
+\vspace{-2mm}
 \centering
  \includegraphics[width=1.0\linewidth]{end2end}
- \vspace{-2mm}
- \caption{End-to-end NLP neural network model.}
+ \vspace{-5mm}
+ \caption{The shared structure of end-to-end NLP neural network models.}
   \vspace{-2mm}
@@
 \vspace{-2mm}
- \includegraphics[width=0.9\linewidth]{attentionIllustration}
-
+ \includegraphics[width=0.85\linewidth]{attentionIllustration}
+  \vspace{-2mm}
  \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
@@
 \label{fig:attention}
+  \vspace{-2mm}
 \end{figure}

### 2018-03-31 paper/appendix_modelDescription.tex
add open source comment add title to the appendix
update supplementray material

@@
 \title{
-Supplementary Materials
+NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials
 %Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
@@
 \begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
-from visPackage import *
+from nlize import *
 from modelInterface import *
@@
 visLayout = {
-    "column":[{"row":["Selector", 
+    "column":[{"row":["Summary", 
                       "Sentence", 
@@
 #create vis interface
-vis = textEntailVisModule(visLayout)
+vis = nlizeModule(visLayout)
 

### 2018-03-31 paper/task.tex
update supplementray material

@@
 
-\item \textbf{T3}: When the predicted label is incorrect, what does it take to fix the model? What is the effect of updating different stages of the model?
+\item \textbf{T3}: When the predicted label is wrong, how can we update the model to correct the prediction? What is the effect of updating different parts of the model?
 

### 2018-03-31 paper/discussion.tex
add open source comment add title to the appendix
integration grammar fix

@@
 \section{Discussion}
-The current setup for the proposed tool is only suitable for natural language inference task.
-However, due to the modular design and the many shared attribution among end-two-end NLP models, we can readily extend the system to handle other tasks.
-We plan to add support for more NLP task, such as neural machine translation, question and answer, in the future.
+The current setup for the proposed tool is suitable only for natural language inference task.
+However, due to the modular design and the many shared attributions among the end-two-end NLP models, we can readily extend the system to handle other tasks.
+In the future, we plan to open source our projection and add support for more NLP tasks, such as neural machine translation and question-and-answer.
 %
-From our evaluation process, we found that the quality of automatic perturbed sentences can be a potential limitation of the tool.
-Since we rely on WordNet to generate the perturbation, which has a rather inclusive definition for synonymous.
-Often, we can identify perturbed sentences that are not particularly meaningful (e.g., sentences with very obscured words or usages).
-Even if all the words are meaning, currently, there is no way we can verify whether the perturbed sentence is valid natural language composition or not.
+From our evaluation process, we found that the quality of automatic perturbed sentences can be a potential limitation of the tool, since we rely on WordNet to generate the perturbation, which has a rather inclusive definition for synonymous.
+Often, we can identify perturbed sentences that are not particularly meaningful (e.g., sentences with very obscure words or usages).
+Even if all the words are meaningful, currently, there is no way we can verify whether the perturbed sentence is valid natural language composition or not.
 %
-However, from natural language process point of view the perturbation of sentence while maintaining semantic and sentence correctness is an open research area on its own. 
+However, from the natural language process point of view, the perturbation of a sentence while maintaining semantic and grammar correctness is an open research area on its own. 
 %As better method appears, we can easily swap out the sentence perturbation functionality
 
-To conclude, this work introduces a perturbation-driven visual interrogation system that provides the expert with a streamlined exploration environment for testing hypothesis and obtain intuition about the model.
-The proposed system frees the researchers from interruptions and tedious operations, therefore, allows them to focus on the more productive activities.
+To conclude, this work introduces a perturbation-driven visual interrogation system that provides experts with a streamlined exploration environment for testing hypothesis and obtaining intuition about the model.
+The proposed system frees the researchers from interruptions and tedious operations, therefore, allows them to focus on more productive activities.

### 2018-03-31 paper/evaluation.tex
integration grammar fix

--- 2018-03-30 paper/evaluation.tex
@@
 \section{Evaluation and Feedback}
-The motivation for designing the proposed tool is driven by the error analysis challenges faced by our long-term collaborators working on natural language inference research.
-During the entire design and development process, we work closely with two NLP experts, and their constant evaluation and feedback have helped shape the tool we see today.
+The motivation for designing the proposed tool is the error analysis challenges faced by our long-term collaborators working on natural language inference research.
+During the entire design and development process, we worked closely with two NLP experts, and their constant evaluation and feedback have helped shape the tool we see today.
 %
-Since these two NLP experts are heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.
-To uncover the limitation and identify areas for improvements, we gathered a wider audiences from either visualization (4 researchers include 3 Ph.D.
-level student and one postdoc researcher) or NLP background (5 Ph.D.
-level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.
+Since these two NLP experts have been heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.
+To uncover the limitation and identify areas for improvement, we gathered a wider audience from either visualization (4 researchers, including 3 Ph.D.-level students and one postdoc researcher) or NLP backgrounds (5 Ph.D.-level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.
 
-With the goal to identify the potential interface design issues, we first conduct an informal demonstration-and-feedback session with the visualization group.
-We start by explaining the basic natural language inference concept.
-We then demonstrate the features of the tool in detail while answering questions and address comments.
+With the goal to identify the potential interface design issues, we first conducted an informal demonstration-and-feedback session with the visualization group.
+We started by explaining the basic natural language inference concept.
+We then demonstrated the features of the tool in detail.
+After that, we answered questions and seek feedback.
 %
-From this session, we have gathered complaints and suggestions on various aspect of the visual interface.
-Some of the identified issues include: (1) difficult to distinguish different type of predictions (distinct colors are added for the final version); (2) hard to recognize ground truth label (now, we use a green rectangle to indicate the ground truth); (3) lack of legends to understand the key elements in plots (legends are added).
+From this session, we have gathered complaints and suggestions on various aspects of the visual interface.
+Some of the identified issues include: (1) difficult to distinguish different types of predictions (distinct colors are added to the final version); (2) hard to recognize the ground truth label (we now use a green rectangle to indicate the ground truth); (3) lack of legends to understand the key elements in plots (legends are added).
 We address these interface issues before presenting the final version to the NLP group.
 
-We conduct individual revaluation session with each participant from the NLP group, in which the participant is given 30 minutes to experiment with the tool after an overall feature demonstration. 
+We conduct an individual revaluation session with each participant from the NLP group, in which the participant is given 30 minutes to experiment with the tool after an overall feature demonstration. 
 %
-Since both the matrix and graph-based visual encoding is the most common attention representations used in NLP literature, most the participant can utilize them immediately and find the linked highlighting feature of the two views quiet useful.
+Since both the matrix and graph-based visual encodings are the most common attention representations used in the NLP literature, most participants can utilize them immediately and find the linked highlighting feature of the two views quite useful.
 % 
-Once the participants familiarize with the tool, the first thing they try is often typing two similar sentences and examine the attention and prediction.
-After that, they will modified some words, or negate the hypothesis sentence, then check the attention and prediction again.
+Once the participants familiarize with the tool, they often try to type two similar sentences and examine the attention and prediction.
+After that, they will modify some words, or negate the hypothesis sentence, and then check the attention and prediction again.
 %
-Such a ``perturb and observe'' operation demonstrates the most fundamental exploration strategy and matches well with the perturbation-driven paradigm the proposed tool aim to support.
+Such a ``perturb and observe'' operation demonstrates the most fundamental exploration strategy and matches well to the perturbation-driven paradigm the proposed tool aims to support.
 
@@
 In the other example, he finds a sentence pair with the incorrect attention that produces a wrong prediction. 
-However, even after he forces the correct alignment, the prediction result remain incorrect. He believes observation such as these will provide valuable insights for him to interpret the model. 
+However, even after he forces the correct alignment, the prediction result remains incorrect. He believes observations such as these will provide valuable insights for him to interpret the model. 
 %
-Another participant comment that the ability to enable and disable update in the pipeline view is beneficial.
+Another participant comments that the ability to enable or disable model parameter update in the pipeline view is beneficial.
 
@@
 %
-Also, for the participants do not focus on NLI research, understand all the views at first can be a bit challenging.
-However, this issue can be addressed by the modular design, as the user can simply enable, only the sentence, attention, and prediction views, at first.
+Also, for the participants who do not focus on NLI research, understanding all the views at first can be a bit challenging.
+However, this issue can be addressed by the modular design, as the user can simply enable, only the sentence, attention, and prediction views.
 %
-Overall, all the participants believe the proposed tool is very convenient for conduction experiment and exploring various hypothesis, which is essential to build intuitions about the model.
+Overall, all the participants believe the proposed tool is very convenient for conducting experiment and exploring various hypotheses, which is essential for building intuitions about the model.

### 2018-03-31 paper/application.tex
integration grammar fix
grammar fix

@@
 %In this section, we discuss application scenarios, in which the domain experts utilize the
-To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool in their analysis workflow.
+To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their analysis workflow.
 
@@
 Experiment with all configurations for the label reassignment optimization.
-As shown in (d), the update of attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
+As shown in (d), the update of the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
  }
@@
  \caption{
-Dependency tree provides valuable information that can help fix the prediction error.
-In (a), the model mistakenly aligns the word green, which lead to wrong prediction.  
-After examining the dependency tree (highlighted by pink squares), we can see the two \textbf{green} are attached to different words.
-In (b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected to \emph{neutral}. 
+The dependency tree provides valuable information that can help fix the prediction error.
+In (a), the model mistakenly aligns the word green, which leads to an incorrect prediction.  
+After examining the dependency tree (highlighted by pink squares), we can see the two \textbf{greens} are attached to different words.
+In (b), by editing the attention and forcing the alignment of the two \textbf{greens} to be zero, the prediction label is corrected to \emph{neutral}. 
  }
@@
 \subsection{Scenario 5: Handcraft Example Exploration}
-To test the limits of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most models will have a difficult time making correct inference.
+To test the limits of the model, domain experts often handcraft ``extreme'' examples (such as the Facebook IPO example discussed in Section~\ref{sec:languageInference}) for which they know most models will have difficulty making a correct inference.
 %
-The researchers start with a set of experiments they plan to run, from which, they will develop new hypotheses for further analysis.
+The researchers start with a set of experiments they plan to run, from which they will develop new hypotheses for further analysis.
 %
 In some way, we can think of such a process as a natural blend of all previously discussed scenarios.
-However, instead of with specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-ordinary behaviors in the model.
+However, instead of having a specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-the-ordinary behaviors in the model.
 %

### 2018-03-31 paper/implementation.tex
grammar fix

@@
 The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
-In the proposed system, we approach these challenges by designing the system as a python library rather than as a monolithic standalone application. 
-Just like a python plotting library, the different pieces of the visualization can be accessed individually, which help ease the initial learning curve. 
-The individual components can also be combined in any configuration desired by the user via a simple Python API to better fit into one's workflow.
-More importantly, the library based design allows easily integrate with existing model implemented in python.
+In the proposed system, we approach these challenges by designing the system as a Python library rather than as a monolithic standalone application. 
+Just like a Python plotting library, the different pieces of the visualization can be accessed individually, which helps ease the initial learning curve. 
+The individual components can also be combined in any configuration desired by users via a simple Python API to better fit into one's workflow.
+More importantly, the library-based design allows easy integration with the existing model implemented in Python.
 %

### 2018-03-31 paper/application.tex
fix grammar in seciton 6

@@
 In (e), we show another example of unstable predictions, in which the prediction changes drastically with a minor perturbation (see ($\mathbf{e_1}$)).
-%( For the perturbed pair , the word \textbf{pile} is replaced by \textbf{heap} in the hypothesis sentence).
 }
@@
 %
-In the proposed work, we approach the prediction robustness from sensitivity analysis point of view.
+In the proposed work, we approach the prediction robustness from a sensitivity analysis point of view.
 The stability of the prediction is measured by how often the predicted labels are altered after small perturbations are applied to the input.
 %
-Compare to other types of input (e.g., image), perturbation of the natural language can be particularly tricky, as small alteration of words can drastically change the meaning of the sentence.
-As discussed in Section~\ref{sec:sentence}, we try to maintain semantic of the sentence by only replace words with their synonymous and only replace one word for each pair.
-As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert can not only examine a visual summary of the stability but also quickly dive into individual examples for case by case analysis.
+Compared to other types of input (e.g., image), the perturbation of the natural language can be particularly tricky, as small alterations of words can drastically change the meaning of the sentence.
+As discussed in Section~\ref{sec:sentence}, we try to maintain the sentence semantic by replacing only words with their synonymous and only one word for each pair.
+As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert not only can examine a visual summary of the stability but also quickly dive into individual examples for a case-by-case analysis.
 
@@
 %
-We observe a drastic difference for the stability for \emph{entailment} predictions compare to the \emph{contradiction} and \emph{neutral} ones.
+We observe a drastic difference for the stability for \emph{entailment} predictions compared to the \emph{contradiction} and \emph{neutral} ones.
 %
-Such a distinction can be partially explained by how \emph{entailment} relationship is defined.
-The relationship is only valid if the concept in the premise is more specific than the concept in the hypothesis.
+Such a distinction can be partially explained by how the \emph{entailment} relationship is defined.
+The relationship is valid only if the concept in the premise is more specific than the concept in the hypothesis.
 Therefore, the synonymous perturbation may change the \emph{entailment} relationship, as the replaced \emph{noun} or \emph{verb} can be more or less restrictive compared to the original.
-This inherent disparity of sensitivity may worth extra consideration when designing future NLI models.
+This inherent disparity of sensitivity may warrant extra consideration when designing future NLI models.
 
@@
 %
-Through the exploration of many samples with low stabilities (i.e., high sensitivities values in the plots), domain experts notice that many highly unstable outliers are from sentence pairs where the predictions are near the decision boundary (see Fig.~\ref{fig:predictStability}(d), the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
+Through the exploration of many samples with low stabilities, domain experts notice that many highly unstable outliers are from sentence pairs where the predictions are near the decision boundary (see Fig.~\ref{fig:predictStability}(d): the yellow circle corresponds to a \emph{entailment} prediction that is very close to \emph{neutral}).
 %
 However, we can also find sentence pairs, such as the one illustrated in Fig.~\ref{fig:predictStability}(e), in which the prediction is altered drastically with minor perturbations (e.g., replace the word \textbf{pile} with \textbf{heap} in ``pile of snow'').
-In the following section, we examine what happened inside the model and hypothesize the cause of failure (see Fig.~\ref{fig:att2pred}).
+In the following section, we examine what happened inside the model and hypothesize the cause of the failure (see Fig.~\ref{fig:att2pred}).
 
@@
 Experiment with all configurations for the label reassignment optimization.
-As shown in (d), the update of the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
+As shown in (d), the update to the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder stage of the model.
  }
@@
 
-\subsection{Scenario 2: Examine the Decision Making Process}
+\subsection{Scenario 2: Examine the Decision-Making Process}
 The predicted label alone provides limited information.
-Often, domain experts want to know how does the model arrive at a conclusion.
-And if the prediction is incorrect, where in the model does the error occur?
-Examining the decision making process is not only instrumental in evaluating the model performance but also essential for hypothesizing improvement strategies for future models.
+Often, domain experts want to know how the model arrives at a conclusion, and if the prediction is incorrect, where in the model the error occurs?
+Examining the decision-making process is not only instrumental in evaluating the model performance but also essential for hypothesizing improvement strategies for future models.
 %
@@
 In the previous section, we have noticed that a minor perturbation of the sentence may result in change of the final prediction (Fig.~\ref{fig:predictStability}(d)).
-Here, we want to make sense of what lead to the failed prediction.
-In this example, the premise \textbf{P} is ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.'', and the original hypothesis \textbf{H1} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow.''.
+Here, we want to make sense of what leads to the failed prediction.
+In this example, the premise \textbf{P} is ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow'', and the original hypothesis \textbf{H1} is ``A child in a red plaid coat and pink winter hat makes a snowball in a large \textbf{pile} of snow''.
 The perturbed hypothesis \textbf{H2} replaces the word \textbf{pile} with \textbf{heap} in \textbf{H1}.
@@
 
-As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair, the word \textbf{pile} and \textbf{heap} is not well-aligned (see Fig.~\ref{fig:att2pred}(a)).
+As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair that the words \textbf{pile} and \textbf{heap} are not well aligned (see Fig.~\ref{fig:att2pred}(a)).
 %
-To test whether the alignment is what contribute to the misclassification, the domain expert utilizes the attention editing functionality in the matrix attention view (Fig.~\ref{fig:attentionVis}(c)) to make the word \textbf{pile} align with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
+To test whether the alignment is what contributes to the misclassification, the domain expert utilizes the attention editing functionality in the matrix attention view (Fig.~\ref{fig:attentionVis}(c)) to make the word \textbf{pile} align with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
 %
@@
 %Interestingly, the original pair's attention is almost identical to the edited attention (the comparison is not shown in the figure). 
-Such an observation implies that the model does not firmly believe ``\textbf{heap} of snow'' and ``\textbf{pile} of snow'' have the same meaning, which may indicate the potential issue with the encoder or word embedding.
+Such an observation implies that the model does not firmly believe ``\textbf{heap} of snow'' and ``\textbf{pile} of snow'' have the same meaning, which may indicate a potential issue with the encoder or word embedding.
 
@@
 %As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, 
-For example, in the sentence pair (\textbf{P}: ``A couple is taking a break from bicycling.'', \textbf{H}: ``sisters sit next to their bikes.''), the word \textbf{take} and \textbf{next} should not align with each other,
-%(Fig.~\ref{fig:wrongAlignRightPred}(a)), 
-yet, it still produce the correct \emph{neutral} label.% (Fig.~\ref{fig:wrongAlignRightPred}(b)).
+For example, in the sentence pair (\textbf{P}: ``A couple is taking a break from bicycling'', \textbf{H}: ``sisters sit next to their bikes''), the words \textbf{take} and \textbf{next} should not align with each other,
+yet it still produces the correct label (\emph{neutral}).% (Fig.~\ref{fig:wrongAlignRightPred}(b)).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scenario 3: What Does It Take to Correct a Failed Prediction?}
-Up till now, we have employed perturbation for input to understand prediction robustness, utilized the perturbation of attention (and input) to infer the model decision making process.
-Both these perturbation operations rely on forward propagation in the pipeline and assume the model parameter stay unchanged.
+\subsection{Scenario 3: Update the Model to Correct a Prediction}
+%\subsection{Scenario 3: What Does It Take to Correct a Failed Prediction?}
+Up to here, we have employed perturbation for input to understand prediction robustness, and utilized the perturbation of attention (and input) to infer the model decision-making process.
+Both these perturbation operations rely on forward propagation in the pipeline and assume the model parameter remains unchanged.
 %
-However, once we get a sense of how predictions are made and hypothesized about the cause of failure in case of a prediction error, it is natural to ask the follow-up questions.
-What does it take to fix an incorrect prediction?
+However, once we get a sense of how predictions are made and hypothesize about the cause of the failure in the case of a prediction error, it is natural to ask follow-up questions: What does it take to fix an incorrect prediction?
 And more importantly, what role does each of the three stages play in such a process?
@@
 
-Domain experts can obtain answers to these questions by utilizing the prediction and pipeline view in the proposed.
-As discussed in details in Section~\ref{sec:pipeline}, we employed an margin-infused relaxed algorithm (MIRA) based optimization with two objectives (1.
-apply least amount of change to the parameter, 2.
-make the new prediction as close to the reassigned prediction as possible) to update the network parameters.
+Domain experts can obtain answers to these questions by utilizing the prediction and pipeline view in the proposed tool.
+As discussed in detail in Section~\ref{sec:pipeline}, we employed a margin-infused relaxed algorithm (MIRA) based optimization with two objectives (apply the least amount of change to the parameter, and make the new prediction as close to the reassigned prediction as possible) to update the network parameters.
 %
-We then visualize how much each stage of the model is changed through the distribution of parameters difference (see Fig.~\ref{fig:pipelineView}).
+We then visualize how much each stage of the model is changed through the distribution of parameters' difference (see Fig.~\ref{fig:pipelineView}).
 
@@
 Four configurations are shown in Fig.~\ref{fig:pipelineUpdate}(a)(b)(c)(d).
-The updated predictions are illustrated as blue squares, and the pointers highlighted the corresponding pipeline configurations.
+The updated predictions are illustrated as blue squares, and the pointers highlight the corresponding pipeline configurations.
 
 Interestingly, all configurations except one are concentrated around the full \emph{neutral} prediction.
-Referring back to the pipeline visualization, we observe that the only configuration that failed to produce the correct label is the one, in which we only allow to update attention stage of the model.
+Referring back to the pipeline visualization, we observe that the only configuration that failed to produce the correct label is the one for which we allow only updating of the attention stage of the model.
 %
-In other words, the update of attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
-Similar observation can be obtained for most examples we experimented.
+In other words, the updating of the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder stage of the model.
+Similar observations can be obtained for most examples we have experimented with.
 %The attention layer is less sensitive compared to encoding layer and classification layer.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
+\subsection{Scenario 4: Explore the Relationship Between Grammar and Attention}
 The attention computation in the NLI model does not take the grammar structure of the sentences into consideration,
-yet, the attention often highlight key elements of the sentence. 
-Therefore, domain experts wish to understand whether attention alone is sufficient to capture sentence structure. 
-And more important what kind of benefit can the additional information from grammar parsing help address the NLI challenge.
+yet the attention often highlights key elements of the sentence. 
+Therefore, domain experts wish to understand whether attention alone is sufficient to capture sentence structure; 
+and, more importantly, what kind of benefit the additional information from grammar parsing can help address the NLI challenge.
 
@@
 We can infer the cause by examining the attention, in which the word \textbf{green} in ``\textbf{green} jacket" is aligned to the \textbf{green} in ``\textbf{green} tea".
-Due to such an alignment, the model mistakenly believe the two \textbf{green} are used to describe the same thing (therefore, predict \emph{entailment}).
-However, as we examine the dependency tree, the two \textbf{green} are attached to different words, i.e., ``green" in \textbf{P} is attached to jacket, while ``green" in \textbf{H} to tea.
-Therefore, they should not be aligned to allow the classifier make the right decision.
+Due to such an alignment, the model mistakenly believes the two \textbf{greens} are used to describe the same thing (therefore, predict \emph{entailment}).
+However, as we examine the dependency tree, the two \textbf{greens} are attached to different words, i.e., ``green" in \textbf{P} is attached to ``jacket'', whereas ``green" in \textbf{H} is attached to ``tea''.
+Therefore, they should not be aligned to allow the classifier to make the right decision.
 %
-This experiment demonstrates the potential benefit to include grammar structure in the alignment computation. %This stresses the importance of dependency tree in our tool.
+This experiment demonstrates the potential benefit of including grammar structure in the alignment computation. %This stresses the importance of dependency tree in our tool.
 %
-And interestingly, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected (\emph{neutral}).
+And interestingly, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the alignment of the two \textbf{greens} to be zero, the prediction label is corrected (\emph{neutral}).
 

### 2018-03-31 paper/application.tex
grammar fix

@@
 %In this section, we discuss application scenarios, in which the domain experts utilize the
-To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their analysis workflow.
+To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios (first three roughly correspond to \textbf{T1-3}) gathered by the domain experts who integrated the proposed tool into their analysis workflow.
 

### 2018-03-31 paper/intro.tex
grammar fix

@@
 % What is the obstacle for effectively apply machine learning model
-Based on some stunning recent advances, machine learning and neural networks base deep learning approaches in particular have gained unprecedented popularity, and have been adopted in a wide variety of scientific applications.
+Based on some stunning recent advances, neural networks based machine learning approaches have gained unprecedented popularity, and have been adopted in a wide variety of applications.
 %

### 2018-03-31 paper/application.tex
intro pass

@@
 \subsection{Scenario 4: Explore the Relationship Between Grammar and Attention}
+\label{sec:grammarAttention}
 The attention computation in the NLI model does not take the grammar structure of the sentences into consideration,

### 2018-03-31 paper/intro.tex
intro pass

@@
 %
-In the simplest form, the inference task asks the question about whether \textbf{sentence A} and \textbf{sentence B}: (1) are \emph{entailed} (one can infer \textbf{B} from \textbf{A}; (2) \emph{contradict} (\textbf{B} disagrees with \textbf{A}) or (3) are \emph{neutral} (\textbf{A} and \textbf{B} talk about different/unrelated thins
+In the simplest form, the inference task asks the question about whether \textbf{sentence A} and \textbf{sentence B}: (1) are \emph{entailed} (one can infer \textbf{B} from \textbf{A}; (2) \emph{contradict} (\textbf{B} disagrees with \textbf{A}) or (3) are \emph{neutral} (\textbf{A} and \textbf{B} talk about different/unrelated things
 % we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), if they contradict with each other (\emph{contradiction}), or whether two sentences talk about different/unrelated things (\emph{neutral}).
@@
 %
-Finally, as discussed in Section~\ref{sec:caseStudy}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate about the potential benefits of including the linguistic structure in the design of the attention component of the model.
+Finally, as discussed in Section~\ref{sec:grammarAttention}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate about the potential benefits of including the linguistic structure in the design of the attention component of the model.
 

### 2018-03-31 paper/background.tex
section 2, 3 global pass

@@
 
-Many of the recent NLP end-to-end neural network models, despite having potentially drastically different network architectures, share a similar high-level design that consists of three distinct stages (encode, align, classify, see Fig.~\ref{fig:modelPipeline}).
+Many of the recent NLP end-to-end neural network models, despite having potentially drastically different network architectures, share a similar high-level design that consists of three distinct stages (encode, align, classify, see Fig.~\ref{fig:end2end}).
 %
@@
 \begin{figure}[htbp]
-\vspace{-2mm}
 \centering
  \includegraphics[width=1.0\linewidth]{end2end}
+ \vspace{-6mm}
+ \caption{The shared structure of end-to-end NLP neural network models.}
   \vspace{-5mm}
- \caption{The shared structure of end-to-end NLP neural network models.}
-  \vspace{-2mm}
-\label{fig:modelPipeline}
+\label{fig:end2end}
 \end{figure}
@@
  \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
-On the left, the matrix shows the attention between between premise and hypothesis pair.
-On the right, attention can also be interpreted as alignment.}
+On the left, the matrix shows the attention between the premise and hypothesis pair.
+On the right, we illustrate that the attention can also be interpreted as alignment.}
 \label{fig:attention}

### 2018-03-31 paper/relatedWorks.tex
section 2, 3 global pass

@@
 %
-Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications.
+Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications.
 In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understand snapshot of the classifier near a specific input.
@@
 Due to the effectiveness of exploring complex relationships, visualization has long been adopted for interpreting neural network models~\cite{TzengMa2005}.
-Recently, the increasing demand for interpretability for deep neural network models has motivated the introduction of many visualization works that are dedicated to neural network models.
+Recently, the increasing demand for interpretability for machine learning models has motivated the introduction of many visualization works that are dedicated to neural network models.
 % The classification~\cite{KrausePererNg2016}
-The Prospector~\cite{KrausePererNg2016} provides a model agnostic approach for analyzing and interpreting predictions via an interactive visual interface.
+%The Prospector~\cite{KrausePererNg2016} provides a model agnostic approach for analyzing and interpreting predictions via an interactive visual interface.
 %
@@
 %
-The DeepEyes~\cite{Pezzotti2018} focused on analyzing the training process of CNN, which provides domain experts design guideline of the deep neutral network architecture.
+The DeepEyes~\cite{Pezzotti2018} focused on analyzing the training process of CNN, which provided domain experts design guideline of the deep neutral network architecture.
 %
 The ActiVis~\cite{KahngAndrewsKalro2018} introduced an interactive system tailored for tuning industry-scale neural networks in Facebook.
+The TensorFlow Graph Visualizer~\cite{Wongsuphasawat2018} work designed a hierarchical visual representation to encode complex computation graphs of deep neural networks for the TensorFlow framework~\cite{Abadi2016}.
 Finally, Liu et al.~\cite{LiuShiCao2018} presented a visualization tool for understanding the often challenging training process of deep generative models.

### 2018-03-31 paper/attention.tex
update 4 5

@@
 \subsection{Attention View}
-\label{sec:attention}
+\label{sec:attentionView}
 As discussed in Section~\ref{sec:attention}, the attention is the only intermediate layer in the network that provides interpretable information for domain experts to infer the inner mechanisms of the model.

### 2018-03-31 paper/overview.tex
space squeeze
update 4 5

@@
-\begin{figure}[htbp]
-\centering
- \includegraphics[width=1.0\linewidth]{pipeline}
- \caption{
- Perturbation-driven exploration of the natural language inference model.
- In the proposed tool, we enable the interrogation of the relationship between different components of the model via the perturbation-based analysis.
- %
- The user can perturb the input sentences (i.e., replace words with synonymous), perturb the attention (i.e., alter the soft alignment between sentences), and perturb the prediction (i.e., adjust the prediction by making updates to the model).
-}
-\label{fig:modelPipeline}
-\end{figure}
-
 \section{NLIZE System}
@@
 %
-As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (e.g., adjust the prediction by making updates to the model).
+As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (i.e., adjust the prediction by making updates to the model).
 %
-In the following sections, we describe in detail the five major components of the proposed system, namely, the sentence view  (Section~\ref{sec:sentence}), the attention view (Section~\ref{sec:attention}), the prediction view (Section~\ref{sec:prediction}), the pipeline view (Section~\ref{sec:pipeline}), and the all pair summary view (Section~\ref{sec:allPairs}).
+In the following sections, we describe in detail the five major components of the proposed system, namely, the sentence view  (Section~\ref{sec:sentence}), the attention view (Section~\ref{sec:attention}), the prediction view (Section~\ref{sec:prediction}), the pipeline view (Section~\ref{sec:pipeline}), and the pair summary view (Section~\ref{sec:allPairs}).
+
+\begin{figure}[htbp]
+\vspace{-2mm}
+\centering
+ \includegraphics[width=1.0\linewidth]{pipeline}
+ \vspace{-5mm}
+ \caption{
+ Perturbation-driven exploration of the natural language inference model.
+ In the proposed tool, we enable the interrogation of the relationship between different components of the model via the perturbation-based analysis.
+ %
+ The user can perturb the input sentences (i.e., replace words with synonymous), perturb the attention (i.e., alter the soft alignment between sentences), and perturb the prediction (i.e., adjust the prediction by making updates to the model).
+}
+\vspace{-2mm}
+\label{fig:modelPipeline}
+\end{figure}
 

### 2018-03-31 paper/task.tex
update 4 5

@@
 %
-To support the visual exploratory workflow, we need to address the following visualization tasks.
+To support the exploratory workflow for analyzing NLI models, we need to address the following tasks.
 
@@
 
-\item \textbf{T1}: Understand the stability of a prediction, i.e., how perturbation of input affects the behavior of the model?
+\item \textbf{T1}: Understand the stability of a prediction, i.e., how perturbations of the input affect the behavior of the model?
 
-\item \textbf{T2}: Examine the attention mechanism, i.e., what is the relationship between input and attention and how does the attention affect the prediction?
+\item \textbf{T2}: Examine the attention mechanism, i.e., what is the relationship between the input and the attention, and how does the attention affect the prediction?
 
-\item \textbf{T3}: When the predicted label is wrong, how can we update the model to correct the prediction? What is the effect of updating different parts of the model?
+\item \textbf{T3}: When the predicted label is wrong, how can we update the model to correct the prediction? What are the effects of updating different parts of the model?
 

### 2018-03-31 paper/appendix_modelDescription.tex
minor fixes

@@
 \section{Appendix B: Code Example: Link Visualization with Model}
-From the user point of view, the following python script is all the code the domain expert needs to link the NLP model with the visual interface.
-The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to be supplied by the NLP model.
+From the user's point of view, the following Python script is all the code the domain expert needs to link the NLP model with the visual interface and generate the tool used in the paper.
+The visualization library's API defines several callbacks (called Hook in the code) that describe the model functionality (e.g., prediction) need to be supplied by the NLP model.
 

### 2018-03-31 paper/attention.tex
minor fixes

@@
 Together, the graph and matrix views complement each other and provide the same information from different perspectives.
-As illustrated by the pink arrow line, we can see how the same attention value is visualized in both the graph and the matrix view.
-To help the user recognize the correspondence during the exploration, we enable the linkage between highlighted actions in both views.
+As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.
+To help the user recognize the correspondence during the exploration, we enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), the attention of the two ``couple'' is highlighted).
 
@@
 The attention matrix view is the most suitable place to conduct the edit operation since it provides a direct mapping of attention value.
-As we can see in Fig.~\ref{fig:attentionVis}(c), when a user clicks the cell of the matrix, a sider will pop up for customizing the attention value (as the user edits the value, each row is automatically normalized).
+As we can see in Fig.~\ref{fig:attentionVis}(c), when a user clicks the cell of the matrix, a sider will pop up for customizing the attention value (as the user edits the value, each row is automatically renormalized).
 %

### 2018-03-31 paper/pipeline.tex
adjust figures
minor fixes

@@
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=0.95\linewidth]{pipelineView}
- \vspace{-3mm}
- \caption{
-The pipeline view provides the visual representation of three-stage (encoder, attention, classifier) model. 
-%The pipeline view, by showing the aggregated gradient distribution, informs the user about how different parts of the model respond to the optimization.
- %
-In the proposed tool, we allow the model parameter to be updated to correct a prediction error. 
-The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the blue ``parameter'' area to enable or disable its update (the legend is shown in (d)).
-In (c), we select whether we want to use the current update setting as displayed or try all the configuration combinations as the parameter update can be enabled or disabled for each stage.
- }
-\label{fig:pipelineView}
-\vspace{-2mm}
-\end{figure}
-
 \subsection{Pipeline View}
@@
 The Pipeline view provides a direct visual representation of the three stages (encoder, attention, classifier) of the model.
-In the proposed tool, we allow the model parameter to be updated (via an optimization) to correct a prediction error (\textbf{T3}).
-The pipeline view, by visualizing the aggregated gradient distribution, informs the user about how each stage responds to the optimization.
+In the proposed tool, we allow model parameters to be updated (via an optimization) to correct a prediction error (\textbf{T3}).
+The pipeline view, by visualizing the distribution of the parameter changes, informs the user about how each stage responds to the optimization.
 
@@
 Instead, we adopt the idea in \emph{margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the L2-norm of the parameter change.
-Therefore, in the proposed tool, we obtain the target parameters by the following:
+In the proposed tool, we obtain the target parameters by the following optimization:
 \begin{equation}
@@
 \end{equation}
-where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural model, $\mathbf{W_o}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the parameters to update, and $C$ is the weighting term, which determines whether we intended to emphasize more on obtaining better fitting or deviating less from the original model.
+where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural network model, $\mathbf{W_o}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the updated parameters, and $C$ is the weighting term, which determines whether we intended to emphasize more on obtaining better fitting or deviating less from the original model.
 Due to the nonconvex nature of the neural networks, we use SGD to optimize the above combined loss function.
@@
 
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=0.95\linewidth]{pipelineView}
+ \vspace{-2mm}
+ \caption{
+The pipeline view provides the visual representation of the three-stage (encoder, attention, classifier) model. 
+%
+In the proposed tool, we allow model parameters to be updated to correct a prediction error. 
+The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the blue rectangle marked with ``parameter'' to enable or disable its update (the legend is shown in (d)).
+In (c), we select whether we want to use the current pipeline setting as displayed or try all the pipeline configuration combinations as the parameter update operation can be enabled or disabled for each stage.
+ }
+\label{fig:pipelineView}
+\vspace{-2mm}
+\end{figure}
+
 The optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a).
-Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the parameter bar (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d) ).
+Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the blue rectangle marked with ``parameter'' (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d) ).
 In Fig.~\ref{fig:pipelineView}(c), we select whether we want to use the current update setting as displayed or try all the configuration combinations (i.e., each stage can either be enabled or disabled for the three stages; therefore, there are $8$ combinations in total, or $7$ we discard the case where all stages are not updated).

### 2018-03-31 paper/prediction.tex
space squeeze
update task
adjust figures
minor fixes

@@
 In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle. 
-Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defines a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction and entailment, respectively.
+Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defines a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction or entailment.
 The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.
-In the triangle, the distinctly colored background indicates the regions that correspond to different labels.
+In the triangle, the distinctly colored background (grey, light grey, and light green) indicates the regions that correspond to different labels.
 The prediction result for the original sentence pair is represented by the larger yellow circle, whereas the smaller gray circles illustrate the perturbed sentence pairs.
 A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
-
-To perturb the prediction (\textbf{T3}), we need a way to communicate the reassignment of the predicted label.
-As illustrated in Fig.~\ref{fig:predictionView}(b), we integrate such an operation in the prediction view.
-When pressing and dragging the prediction (represented as a circle), the user is presented with the three options (E, N, C) corresponding to the labels.
-When the user hovers on one of the options, a dotted line is shown to indicate the newly assigned label.
-The assignment is applied when the user releases the mouse while hovering on the label of choice.
 
@@
  \includegraphics[width=1.0\linewidth]{predictionView}
- \vspace{-2mm}
+ \vspace{-5mm}
  \caption{
@@
  }
+  \vspace{-2mm}
 \label{fig:predictionView}
 \end{figure}
+
+To perturb the prediction (\textbf{T3}), we need a way to communicate the reassignment of the predicted label.
+As illustrated in Fig.~\ref{fig:predictionView}(b), we integrate such an operation in the prediction view.
+When pressing and dragging the prediction (represented as a circle), the user is presented with the three options (E, N, C) corresponding to the labels.
+When the user hovers on one of the options, a dotted line is shown to indicate the newly assigned label.
+The reassignment is applied when the user releases the mouse while hovering on the label of choice.

### 2018-03-31 paper/sentence.tex
add open source comment add title to the appendix
minor fixes

@@
 % Once an exploration cycle started, the experts need to examine the premise and hypothesis sentence the current example.
-As illustrated in Fig.~\ref{fig:teaser}(B), the sentence view shows the premise and hypothesis sentence.
+As illustrated in Fig.~\ref{fig:teaser}(b), the sentence view shows the premise and hypothesis sentence.
 %
@@
 %%% sentence perturbation %%%%
-The previously explored original sentences are stored in the dropdown list (left of the buttons) that allow the user to revisit examined examples.
-Also, the user can type any sentences or modified existing text in the sentence display areas to accommodate user-defined input.
+The previously explored original sentences are stored in the dropdown list (on the right side of the buttons) that allow the user to revisit examined examples.
+Also, the user can type any sentences or modify existing text in the sentence display areas to accommodate user-defined inputs.
 

### 2018-03-31 paper/implementation.tex
finsih section 5 pass

@@
 %
-The NLP model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
-The visual elements are implemented in Javascript using \emph{D3.js} library , and the Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.
+In the proposed work, the NLI model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
+The visual interface is implemented in Javascript using \emph{D3.js} library , and the Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.

### 2018-03-31 paper/pipeline.tex
finsih section 5 pass

@@
 In the proposed tool, we allow model parameters to be updated to correct a prediction error. 
-The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the blue rectangle marked with ``parameter'' to enable or disable its update (the legend is shown in (d)).
+The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the blue rectangle marked with the word ``parameter'' to enable or disable its update (the legend is shown in (d)).
 In (c), we select whether we want to use the current pipeline setting as displayed or try all the pipeline configuration combinations as the parameter update operation can be enabled or disabled for each stage.
@@
 The optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a).
-Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the blue rectangle marked with ``parameter'' (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d) ).
-In Fig.~\ref{fig:pipelineView}(c), we select whether we want to use the current update setting as displayed or try all the configuration combinations (i.e., each stage can either be enabled or disabled for the three stages; therefore, there are $8$ combinations in total, or $7$ we discard the case where all stages are not updated).
+Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the blue rectangle marked with the word``parameter'' (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d)).
+In Fig.~\ref{fig:pipelineView}(c), we select whether we want to use the current pipeline update setting as displayed or try all the pipeline configuration combinations (i.e., each stage can either be enabled or disabled; therefore, there are $8$ combinations in total, or $7$ if we discard the case where all stages are not enabled).
 

### 2018-03-31 paper/predSummary.tex
finsih section 5 pass

@@
 %
-The user can select the treemap to focus on the specific type of scenarios (e.g., E/E) and reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
+The user can select the treemap node to focus on the specific type of scenarios (e.g., E/E) and reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
 The selection can be further narrowed down by selecting the bin in the histogram.
@@
 %
-By clicking on the treemap blocks, we can narrow down the selection by focusing on specific scenarios.
-%
+By clicking on the treemap node, we can narrow down the selection by focusing on a specific scenario.
+
 As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are shown.
-The histogram shows the distribution of the prediction sensitivity in the selected category.
+The histogram shows the distribution of the prediction stability in the selected category.
 For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and the all the perturbed pairs.
-Considering we generated 100 pairs via the automated sentence perturbation (i.e., replace nouns and verbs with synonymous), the stability is 0.8 if 80 out of the 100 maintain the original prediction label.
+Considering we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonymous), the stability is 0.8 if 80 out of the 100 maintain the original prediction label.
 %The \emph{stability} measures how likely a sentence pair will change its prediction after applying minor perturbations.% which helps the expert infer the model stability on the given example.
 %
-We can further narrow down the focused set by selecting the bins in the histogram (see Fig.~\ref{fig:summaryView}(b),(d)).
+We can further narrow down the focused set by selecting the bins in the histogram (see Fig.~\ref{fig:summaryView}(b)).
 %
-In the scatterplot, besides showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{stability} number (i.e., if the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} number is likely to be quite noisy).
+In the scatterplot (Fig.~\ref{fig:summaryView}(c)(d)), besides showing the stability values, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{stability} number (i.e., if the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} value is likely very noisy).
 %For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.

### 2018-03-31 paper/application.tex
finish full pass

@@
 
-In the previous section, we have noticed that a minor perturbation of the sentence may result in change of the final prediction (Fig.~\ref{fig:predictStability}(d)).
+In the previous section, we have noticed that a minor perturbation of the sentence may result in change of the final prediction (Fig.~\ref{fig:predictStability}(e)).
 Here, we want to make sense of what leads to the failed prediction.
@@
 
-As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair that the words \textbf{pile} and \textbf{heap} are not well aligned (see Fig.~\ref{fig:att2pred}(a)).
+As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair that the words \textbf{pile} and \textbf{heap} are not well aligned.
 %
@@
 %
-As illustrated in Fig.~\ref{fig:att2pred} (d), after the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary (Fig.~\ref{fig:att2pred}(d)), but the corrected attention fails to produce a conclusive \emph{entailment} prediction (a case where the attention edit corrects the final prediction is shown in Fig.~ref{fig:depTreeExample}).
+After the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary (Fig.~\ref{fig:att2pred}(d)), but the corrected attention fails to produce a conclusive \emph{entailment} prediction (another example, in which the attention edit corrects the final prediction, is shown in Fig.~\ref{fig:depTreeExample}).
 %
@@
 And more importantly, what role does each of the three stages play in such a process?
-Are they affecting the prediction differently?
+And, are they affecting the prediction differently?
 
@@
 %
-We then visualize how much each stage of the model is changed through the distribution of parameters' difference (see Fig.~\ref{fig:pipelineView}).
+We then visualize how much each stage of the model is changed through the distribution of differences between the two sets of parameters (see Fig.~\ref{fig:pipelineView}).
 
 To infer the role each stage of the pipeline plays, the proposed tool allows the parameter update to be enabled or disabled for each pipeline stage.
-The tool also includes an automatic option to test all the possible configuration combinations.
-As illustrated in Fig.~\ref{fig:pipelineUpdate}, the ground truth for this sentence pair is neutral.
+The system also includes an automatic option to test all the possible configuration combinations.
+As illustrated in Fig.~\ref{fig:pipelineUpdate}, the ground truth for this sentence pair is \emph{neutral}.
 However, the model produces an incorrect label \emph{entailment}.
@@
 Four configurations are shown in Fig.~\ref{fig:pipelineUpdate}(a)(b)(c)(d).
-The updated predictions are illustrated as blue squares, and the pointers highlight the corresponding pipeline configurations.
+The updated predictions are illustrated as blue squares, and the arrowed lines highlight the corresponding pipeline configurations.
 
@@
 Due to such an alignment, the model mistakenly believes the two \textbf{greens} are used to describe the same thing (therefore, predict \emph{entailment}).
-However, as we examine the dependency tree, the two \textbf{greens} are attached to different words, i.e., ``green" in \textbf{P} is attached to ``jacket'', whereas ``green" in \textbf{H} is attached to ``tea''.
+However, as we examine the dependency tree, the two \textbf{greens} are attached to different words, i.e., \textbf{green} in \textbf{P} is attached to ``jacket'', whereas \textbf{green} in \textbf{H} is attached to ``tea''.
 Therefore, they should not be aligned to allow the classifier to make the right decision.

### 2018-03-31 paper/discussion.tex
grammar fix
finish full pass

@@
 The current setup for the proposed tool is suitable only for natural language inference task.
-However, due to the modular design and the many shared attributions among the end-two-end NLP models, we can readily extend the system to handle other tasks.
+However, due to the modular design and the many shared attributions among the end-to-end NLP models, we can readily extend the system to handle other tasks.
 In the future, we plan to open source our projection and add support for more NLP tasks, such as neural machine translation and question-and-answer.
@@
 %
-However, from the natural language process point of view, the perturbation of a sentence while maintaining semantic and grammar correctness is an open research area on its own. 
+However, from the natural language process point of view, the perturbation of a sentence while maintaining semantic and correct grammar is an open research area on its own. 
 %As better method appears, we can easily swap out the sentence perturbation functionality
@@
 To conclude, this work introduces a perturbation-driven visual interrogation system that provides experts with a streamlined exploration environment for testing hypothesis and obtaining intuition about the model.
-The proposed system frees the researchers from interruptions and tedious operations, therefore, allows them to focus on more productive activities.
+The proposed system frees the researchers from interruptions and tedious operations, thereby allowing them to focus on more productive activities.

### 2018-03-31 paper/implementation.tex
finish full pass

@@
 In the proposed work, the NLI model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
-The visual interface is implemented in Javascript using \emph{D3.js} library , and the Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.
+The visual interface is implemented in Javascript using \emph{D3.js} library , and a Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.

### 2018-03-31 paper/appendix_modelDescription.tex
update supplemental material

@@
 From the user's point of view, the following Python script is all the code the domain expert needs to link the NLP model with the visual interface and generate the tool used in the paper.
-The visualization library's API defines several callbacks (called Hook in the code) that describe the model functionality (e.g., prediction) need to be supplied by the NLP model.
+The visualization library's API defines several callbacks (called Hook in the code) that correspond to functions (e.g., prediction) need to be supplied by the NLP model.
 

### 2018-03-31 paper/background.tex
Minor changes (mainly in language)

@@
 A simple example is shown in Table~\ref{tab:NLI}.
-In this case, the premise is ``Boy ate an apple''.
-The hypothesis statement ``Kid ate fruits'' can be concluded from the premise.
+In this case, the premise is ``A boy ate an apple''.
+The hypothesis statement ``A kid ate fruit'' can be concluded from the premise.
 Therefore, the relationship between the premise and hypothesis is \emph{entailment}.
 However, we should note that such a relationship is not necessarily reversible.
-Since the concept ``fruit'' is less restrictive than that of ``apple'', we cannot conclude ``Boy ate an apple'' from the statement ``Kid ate fruit''.
-The same logic applies to the hypothesis of ``Boy ate a Fuji apple.'', in which the premise neither implies nor opposes the hypothesis, and therefore, their relationship is \emph{neutral}.
+Since the concept ``fruit'' is less restrictive than that of ``apple'', we cannot conclude ``A boy ate an apple'' from the statement ``A kid ate fruit''.
+The same logic applies to the hypothesis of ``A boy ate a Fuji apple.'', in which the premise neither implies nor opposes the hypothesis, and therefore, their relationship is \emph{neutral}.
 %\emph{Contradiction} means the textual of hypothesis opposes that of premise;
@@
  \hline
- premise & Boy ate an apple. &  -  &  -  & - \\
- hypothesis & Kid ate fruits. & \checkmark &   &  \\
- hypothesis & Boy ate a banana. &  & \checkmark & \\
+ premise & A boy ate an apple. &  -  &  -  & - \\
+ hypothesis & A kid ate fruit. & \checkmark &   &  \\
+ hypothesis & A boy ate a banana. &  & \checkmark & \\
  hypothesis & Tom ate an apple. &  &  & \checkmark \\
- hypothesis & Boy ate a Fuji apple. &   &  & \checkmark \\
+ hypothesis & A boy ate a Fuji apple. &   &  & \checkmark \\
  %\hline
@@
 %
-Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from the learning algorithm's point of view).
+Considering the ambiguousness of natural language and polysemy of words, the inference task can become quite challenging (especially from the learning algorithm's point of view).
 Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
@@
 
-\subsection{Neural Network Model in NLP}
+\subsection{Neural Network Models in NLP}
 %\shusen{What is the basic understanding of neural network What is the end-to-end}
-There are many connections and distinctions between neural network models employed for vision and NLP tasks.
-On the one hand, as discussed in the introduction, the discrete nature of words and sentences presents additional challenges for
-interpreting the NLP model.
-%
-On the other hand, a majority of recent NLP neural networks share the nature of
-end-to-end models, where the entire model operates as a black-box that takes
-vectorized input and yields a final prediction for a specific task.
+Neural network models employed for computer vision and NLP tasks share a key common characteristic: a majority of recent approaches use end-to-end models.
+That is, the entire model operates as a black-box that takes vectorized inputs and yields a final prediction for a task of interest.
+However, as discussed in the introduction, the discrete nature of words and sentences presents additional challenges for
+interpreting NLP models.
 %
 
-Many of the recent NLP end-to-end neural network models, despite having potentially drastically different network architectures, share a similar high-level design that consists of three distinct stages (encode, align, classify, see Fig.~\ref{fig:end2end}).
+Many recent end-to-end neural network models in NLP, despite having  diverse network architectures, share a similar high-level design that consists of three distinct stages (encode, align, classify, see Fig.~\ref{fig:end2end}).
 %
@@
 Among the three stages, the second stage often constitutes a crucial part of the model as it determines where the classifier will focus for generating a prediction.
-The operation to compute the alignment between words in the input is referred to as the attention mechanism.
-The introduction of the attention mechanism~\cite{bahdanau2014neural} allows
+The operation to compute the alignment between words in the input is referred to as the attention mechanism~\cite{bahdanau2014neural}.
+The introduction of the attention mechanism allows
 pairwise interaction between internal representations of words. 
@@
 %As the only interpretable part of the internal state of the network, understanding how attention information 
-Recently, attention has contributed to many strongly performed NLP models~\cite{parikh2016emnlp,rush2015neural,yang2016hierarchical,seo2016bidirectional,schwartz2017high}.
+Recently, attention has contributed to the strong performance of many NLP models~\cite{parikh2016emnlp,rush2015neural,yang2016hierarchical,seo2016bidirectional,schwartz2017high}.
 

### 2018-03-31 paper/intro.tex
Minor changes (mainly in language)

@@
 %
-In the simplest form, the inference task asks the question about whether \textbf{sentence A} and \textbf{sentence B}: (1) are \emph{entailed} (one can infer \textbf{B} from \textbf{A}; (2) \emph{contradict} (\textbf{B} disagrees with \textbf{A}) or (3) are \emph{neutral} (\textbf{A} and \textbf{B} talk about different/unrelated things
+In the simplest form, the inference task asks whether the
+relationship between \textbf{sentence A} and \textbf{sentence B}: (1) is \emph{entailment} (one can infer \textbf{B} from \textbf{A}), (2) \emph{contradiction} (\textbf{B} disagrees with \textbf{A}) or (3) is \emph{neutral} (\textbf{A} and \textbf{B} talk about different/unrelated things).
 % we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), if they contradict with each other (\emph{contradiction}), or whether two sentences talk about different/unrelated things (\emph{neutral}).
-Language inference addresses the fundamental challenge of measuring the semantic similarity of sentences, and is one of the core NLP tasks (see Section~\ref{sec:languageInference} for details).
+Natural language inference addresses the fundamental challenge of identifying semantic relationships between sentences, and is a core NLP task (see Section~\ref{sec:languageInference} for details).
 
-One recent advance in neural natural language process models is the introduction of \emph{attention mechanisms}~\cite{VaswaniShazeerParmar2017} (Section~\ref{sec:attention}).
-Intuitively, the attention helps capture which part of the input the model is deemed more important for making a prediction.
-The attention is often represented as weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
+One recent advance in neural natural language process models is the
+introduction of \emph{attention
+  mechanisms}~\cite[for example]{bahdanau2014neural,VaswaniShazeerParmar2017}
+(Section~\ref{sec:attention}). Intuitively, attention asks which parts of the
+input are deemed more important for making a prediction.
+The attention is often represented via weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
 %
@@
 There have been many speculations on how attention works in various models.
-By utilizing the proposed tool, the domain experts study how changes in sentence input, attention, or prediction affect each other, which helps them develop deeper intuitive and alternative hypotheses.
+Using the proposed tool, the domain experts can study how changes in sentence input, attention, or prediction affect each other, which helps them develop deeper intuitive and alternative hypotheses. 
 %we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention.
@@
 
-In summary, the key contributions of the proposed works are the following:
+In summary, the key contributions of this paper are:
 \begin{itemize}
@@
 
-    \item The NLIZE system that enriches such a paradigm by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedbacks; 
+    \item The NLIZE system that enriches such a paradigm by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback; 
     %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
@@
 
-    \item An optimization scheme for correcting a failed prediction based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network; and
+    \item An optimization scheme for correcting a failed prediction based on a natural extension of the margin-infused relaxed algorithm (MIRA) to neural networks; and
     % to minimally update the model to fix a failed prediction, which help reason about the  better understand the re the question about how t

### 2018-03-31 paper/task.tex
Minor changes (mainly in language)

@@
 
-During our long-term collaboration with NLP experts, we have conducted extensive discussions to understand the common approach employed by researcher for assessing the behavior of a model.%
+During our long-term collaboration with NLP experts, we have conducted extensive discussions to understand the common approach employed by researchers for assessing the behavior of a model.%
 The predictive accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model; however, the accuracy number alone does not provide the full story.

### 2018-03-31 paper/intro.tex
update intro

--- 2018-03-31 paper/intro.tex
@@
 %
-However, researchers as well as practitioners often needs to overcome many obstacles during the training, debugging, and tuning processes to realize the full potential of these models.
+However, researchers as well as practitioners often need to overcome many obstacles during the training, debugging, and tuning processes to realize the full potential of these models.
 %
 Interpreting the internal mechanism and analyzing how predictions are made is critical to both the design and deployment of a model.
-More importantly, the ability to pinpoint where and how an error is made and propose hypotheses for the cause of the error is key to identifying the limitations of and improving upon existing models.
+More importantly, the ability to pinpoint where and how an error is made and propose hypotheses for the cause of the failure is key to identifying the limitations of and improving upon existing models.
 However, providing meaningful answers to these questions is challenging and has been described as impossible by many.

### 2018-03-31 paper/application.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scenario 5: Handcraft Example Exploration}
+\subsection{Scenario 5: Handcrafted Example Exploration}
 To test the limits of the model, domain experts often handcraft ``extreme'' examples (such as the Facebook IPO example discussed in Section~\ref{sec:languageInference}) for which they know most models will have difficulty making a correct inference.

### 2018-03-31 paper/intro.tex
minor change

@@
 introduction of \emph{attention
-  mechanisms}~\cite[for example]{bahdanau2014neural,VaswaniShazeerParmar2017}
+  mechanisms}~\cite{bahdanau2014neural,VaswaniShazeerParmar2017}
 (Section~\ref{sec:attention}). Intuitively, attention asks which parts of the

### 2018-03-31 paper/appendix_modelDescription.tex
update module name

--- 2018-03-31 paper/appendix_modelDescription.tex
@@
 The pipeline can be separated into three phases: encoder, attention and classifier.
-Here we briefly formalize these three layers.
+Here we briefly formalize these three layers (referred to as stages in the main text of the paper).
 
@@
 \section{Appendix B: Code Example: Link Visualization with Model}
-From the user point of view, the following python script is all the code the domain expert needs to link the NLP model with the visual interface.
-The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to be supplied by the NLP model.
+From the user's point of view, the following Python script is all the code the domain expert needs to link the NLP model with the visual interface and set up the visualization system shown in the paper.
+The visualization library's API defines several callbacks (called ``Hook'' in the API) that correspond to functions (e.g., prediction) need to be supplied by the NLP model.
 
-\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
+\begin{lstlisting}[language=Python, caption=Code for setting up the visualization system shown in the paper.]
 from nlize import *

### 2018-03-31 src/exampleVis.py

@@ -19,7 +19,7 @@ visLayout = {
     }
 
 #setup interface
-modelVis = textEntailVisModule(visLayout)
+modelVis = nlizeModule(visLayout)
 
 modelVis.setPredictionHook(model.predict)
 modelVis.setAttentionHook(model.attention)

### 2018-03-31 src/visPackage/visModule.py

@@ -128,7 +128,7 @@ data organization structure
 
 layoutConfig = None
 
-class textEntailVisModule(visModule):
+class nlizeModule(visModule):
     def __init__(self, componentLayout):
         # super(visModule, self).__init__()
         self.index = 0

### 2018-05-17 EMNLP-demo-paper/NLPVis-demo-paper.tex
update hover

%
% File emnlp2018.tex
%
%% Based on the style files for EMNLP 2018, which were
%% Based on the style files for ACL 2018, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp2018}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP 2018}
\newcommand\conforg{SIGDAT}

\title{Visual Integration Tool for the Natural Language Inference and Machine Comprehension Tasks}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of \confname{}. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions for earlier ACL
and NAACL proceedings. It represents a recent build from
\url{https://github.com/acl-org/acl-pub}, with modifications by Micha
Elsner and Preethi Raghavan, based on the NAACL 2018 instructions by
Margaret Michell and Stephanie Lukin, 2017/2018 (NA)ACL bibtex
suggestions from Jason Eisner, ACL 2017 by Dan Gildea and Min-Yen Kan,
NAACL 2017 by Margaret Mitchell, ACL 2012 by Maggie Li and Michael
White, those from ACL 2010 by Jing-Shing Chang and Philipp Koehn,
those for ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan,
and Sadaoki Furui, those for ACL 2005 by Hwee Tou Ng and Kemal
Oflazer, those for ACL 2002 by Eugene Charniak and Dekang Lin, and
earlier ACL and EACL formats.  Those versions were written by several
people, including John Chen, Henry S. Thompson and Donald
Walker. Additional elements were taken from the formatting
instructions of the {\em International Joint Conference on Artificial
  Intelligence} and the \emph{Conference on Computer Vision and
  Pattern Recognition}.

\section{Introduction}

exploration task

Comparsion with AllenNLP

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, authors' names and complete
addresses, which must be centered at the top of the first page, and
any full-width figures or tables (see the guidelines in
Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
pages directly under the top margin. See the guidelines later
regarding formatting the first page.  The manuscript should be
printed single-sided and its length
should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages are numbered for  initial submission. However, {\bf do not number the pages in the camera-ready version}.

By uncommenting {\small\verb|\aclfinalcopy|} at the top of this
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.  When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.
However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.  The \confname{} \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.

The author list for submissions should include all (and only) individuals who made substantial contributions to the work presented. Each author listed on a submission to \confname{} will be notified of submissions, revisions and the final decision. No authors may be added to or removed from submissions to \confname{} after the submission deadline.

\subsection{The Ruler}
The \confname{} style defines a printed ruler which should be presented in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document without the provided
style files, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\small\verb|\aclfinalcopy|} command in the document preamble.)

Reviewers: note that the ruler measurements do not align well with
lines in the paper -- this turns out to be very difficult to do well
when the paper contains many figures and equations, and, when done,
looks ugly. In most cases one would expect that the approximate
location will be adequate, although you can also use fractional
references ({\em e.g.}, the first paragraph on this page ends at mark $108.5$).

\subsection{Electronically-available resources}

\conforg{} provides this description in \LaTeX2e{} ({\small\tt
  emnlp2018.tex}) and PDF format ({\small\tt emnlp2018.pdf}), along
with the \LaTeX2e{} style file used to format it ({\small\tt
  emnlp2018.sty}) and an ACL bibliography style ({\small\tt
  acl\_natbib\_nourl.bst}) and example bibliography ({\small\tt
  emnlp2018.bib}).  These files are all available at
\url{http://emnlp2018.org/downloads/emnlp18-latex.zip}; a Microsoft
Word template file ({\small\tt emnlp18-word.docx}) and example
submission pdf ({\small\tt emnlp18-word.pdf}) is available at
\url{http://emnlp2018.org/downloads/emnlp18-word.zip}.  We strongly
recommend the use of these style files, which have been appropriately
tailored for the \confname{} proceedings.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). PDF files are usually produced from
\LaTeX\ using the \textit{pdflatex} command. If your version of
\LaTeX\ produces Postscript files, you can convert these into PDF
using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
Adobe Distiller to generate PDF.

Please make sure that your PDF file includes all the necessary fonts
(especially tree diagrams, symbols, and fonts with Asian
characters). When you print or create the PDF file, there is usually
an option in your printer setup to include none, all or just
non-standard fonts.  Please make sure that you select the option of
including ALL the fonts. \textbf{Before sending it, test your PDF by
  printing it from a computer different from the one where it was
  created.} Moreover, some word processors may generate very large PDF
files, where each page is rendered as an image. Such images may
reproduce poorly. In this case, try alternative ways to obtain the
PDF. One way on some systems is to install a driver for a postscript
printer, send your document to the printer specifying ``Output to a
file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm
x 29.7 cm) when formatting the paper. When working with
{\tt dvips}, for instance, one should specify {\tt -t a4}.
Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
preamble (directly below the \verb|\usepackage| commands). Then using
{\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version. If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on A4
paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
 If you cannot meet the above requirements about the production of
 your electronic submission, please contact the publication chairs
 above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use {\bf Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[t!]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations. Do not include the
paper ID number assigned during the submission process. Use the
two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15-point bold font. (For a complete guide to font sizes and styles,
see Table~\ref{font-table}) Long titles should be typed on two lines
without a blank line intervening. Approximately, put the title at 2.5
cm from the top of the page, followed by a blank line, then the
author's names(s), and the affiliation on the following line. Do not
use only initials for given names (middle initials are allowed). Do
not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
``MITCHELL'').  Do not format title and section headings in all
capitals as well except for proper names (such as ``BLEU'') that are
conventionally in all capitals.  The affiliation should contain the
author's complete address, and if possible, an electronic mail
address. Start the body of the first page 7.5 cm from the top of the
page.

The title, author names and addresses should be completely identical
to those entered to the electronical paper submission website in order
to maintain the consistency of author information among all
publications of the conference. If they are different, the publication
chairs may resolve the difference without consulting with you; so it
is in your own interest to double-check that the information is
consistent.

{\bf Abstract}: Type the abstract at the beginning of the first
column. The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
font above the body of the abstract. The abstract should be a concise
summary of the general thesis and conclusions of the paper. It should
be no longer than 200 words. The abstract text should be in 10 point font.

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in

the present document. Do not include page numbers.

{\bf Indent}: Indent when starting a new paragraph, about 0.4 cm. Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.

\begin{table}
\centering
\small
\begin{tabular}{cc}
\begin{tabular}{|l|l|}
\hline
{\bf Command} & {\bf Output}\\\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\
\verb|{\.I}| & {\.I} \\
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular} &
\begin{tabular}{|l|l|}
\hline
{\bf Command} & {\bf  Output}\\\hline
\verb|{\c c}| & {\c c} \\
\verb|{\u g}| & {\u g} \\
\verb|{\l}| & {\l} \\
\verb|{\~n}| & {\~n} \\
\verb|{\H o}| & {\H o} \\
\verb|{\v r}| & {\v r} \\
\verb|{\ss}| & {\ss} \\\hline
\end{tabular}
\end{tabular}
\caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals.
Do not number subsubsections.

\begin{table*}[t!]
\centering
\begin{tabular}{lll}
  output & natbib & previous \conforg{} style files\\
  \hline
  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
\end{tabular}
\caption{Citation commands supported by the style file.
  The citation style is based on the natbib package and
  supports all natbib citation commands.
  It also supports commands defined in previous \conforg{} style files
  for compatibility.
  }
\end{table*}

{\bf Citations}: Citations within the text appear in parentheses
as~\cite{Gusfield:97} or, if the author's name appears in the text
itself, as Gusfield~\shortcite{Gusfield:97}.
Using the provided \LaTeX\ style, the former is accomplished using
{\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}. Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\small\verb|\cite|} command, {\em e.g.}, {\small\verb|\cite{Gusfield:97,Aho:72}|}. Append lowercase letters to the year in cases of ambiguities.
 Treat double authors as
in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
authors are involved. Collapse multiple citations as
in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
as sentence constituents.

We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\citet| (cite in text)
to get ``author (year)'' citations.

If the Bib\TeX{} file contains DOI fields, the paper
title in the references section will appear as a hyperlink
to the DOI, using the hyperref \LaTeX{} package.
To disable the hyperref package, load the style file
with the \verb|nohyperref| option: \\{\small
\verb|\usepackage[nohyperref]{acl2018}|}

\textbf{Digital Object Identifiers}: As part of our work to make ACL
materials more widely used and cited outside of our discipline, ACL
has registered as a CrossRef member, as a registrant of Digital Object
Identifiers (DOIs), the standard for registering permanent URNs for
referencing scholarly materials. \conforg{} has \textbf{not} adopted the
ACL policy of requiring camera-ready references to contain the appropriate
  DOIs (or as a second resort, the hyperlinked ACL Anthology
  Identifier). But we certainly encourage you to use
  Bib\TeX\ records that contain DOI or URLs for any of the ACL
  materials that you reference. Appropriate records should be found
for most materials in the current ACL Anthology at
\url{http://aclanthology.info/}.

As examples, we cite \cite{P16-1001} to show you how papers with a DOI
will appear in the bibliography.  We cite \cite{C14-1001} to show how
papers without a DOI but with an ACL Anthology Identifier will appear
in the bibliography.

\textbf{Anonymity:} As reviewing will be double-blind, the submitted
version of the papers should not include the authors' names and
affiliations. Furthermore, self-references that reveal the author's
identity, {\em e.g.},
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''
\end{quote}
should be avoided. Instead, use citations such as
\begin{quote}
``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

Preprint servers such as arXiv.org and workshops that do not
have published proceedings are not considered archival for purposes of
submission. However, to preserve the spirit of blind review, authors
are encouraged to refrain from posting until the completion of the
review process. Otherwise, authors must state in the online submission
form the name of the workshop or preprint server and title of the
non-archival version. The submitted version should be suitably
anonymized and not contain references to the prior non-archival
version. Reviewers will be told: ``The author(s) have notified us that
there exists a non-archival previous version of this paper with
significantly overlapping text. We have approved submission under
these circumstances, but to preserve the spirit of blind review, the
current submission does not reference the non-archival version.''

\textbf{Please do not use anonymous citations} and do not include
 when submitting your papers. Papers that do not
conform to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading {\bf References}; place the section before any Appendices,
unless they contain references. Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
By using a .bib file, as in this template, this will be automatically
handled for you. See the \verb|\bibliography| commands near the end for more.

Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the
{\em Publication Manual of the American
Psychological Association\/}~\cite{APA:83}. Use of full names for
authors rather than initials is preferred. A list of abbreviations
for common computer science journals can be found in the ACM
{\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations,
short citations and multiple citations as described above.

\begin{itemize}
\item Example citing an arxiv paper: \cite{rasooli-tetrault-2015}.
\item Example article in journal citation: \cite{Ando2005}.
\item Example article in proceedings, with location: \cite{borsch2011}.
\item Example article in proceedings, without location: \cite{andrew2007scalable}.
\end{itemize}
See corresponding .bib file for further details.

Submissions should accurately reference prior and related work, including code and data. If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced. If multiple versions of a piece of prior work exist, the one used by the authors should be referenced. Authors should not rely on automated citation indices to provide accurate references for prior and related work.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\subsection{URLs}

URLs can be typeset using the \verb|\url| command. However, very long
URLs cause a known issue in which the URL highlighting may incorrectly
cross pages or columns in the document. Please check carefully for
URLs too long to appear in the column, which we recommend you break,
shorten or place in footnotes. Be aware that actual URL should appear
in the text in human-readable format; neither internal nor external
hyperlinks will appear in the proceedings.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
point font. They may be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the line
separating the footnotes from the text.}

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns.  Color
illustrations are discouraged, unless you have verified that
they will be understandable when printed in black ink.

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and
tables below the body, using 11 point text.

\subsection{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate people who are color-blind (as well as those printing
to paper), grayscale readability for all accepted papers will be
encouraged.  Color is not forbidden, but authors should ensure that
tables and figures do not rely solely on color to convey critical
distinctions. A simple criterion: All curves and points in your figures should be clearly distinguishable without color.

% Min: no longer used as of ACL 2018, following ACL exec's decision to
% remove this extra workflow that was not executed much.
% BEGIN: remove
%% \section{XML conversion and supported \LaTeX\ packages}

%% Following ACL 2014 we will also we will attempt to automatically convert
%% your \LaTeX\ source files to publish papers in machine-readable
%% XML with semantic markup in the ACL Anthology, in addition to the
%% traditional PDF format.  This will allow us to create, over the next
%% few years, a growing corpus of scientific text for our own future research,
%% and picks up on recent initiatives on converting ACL papers from earlier
%% years to XML.

%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
%% with the camera-ready version of your paper. We will then convert them
%% to XML automatically, using the LaTeXML tool
%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
%% a number of \LaTeX\ packages, including the ACL 2018 stylefile. These
%% bindings allow LaTeXML to render the commands from these packages
%% correctly in XML. For best results, we encourage you to use the
%% packages that are officially supported by LaTeXML, listed at
%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
% END: remove

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

The \confname{} main conference accepts submissions of long papers and
short papers.
 Long papers may consist of up to eight (8) pages of
content plus unlimited pages for references. Upon acceptance, final
versions of long papers will be given one additional page -- up to nine (9)
pages of content plus unlimited pages for references -- so that reviewers' comments
can be taken into account. Short papers may consist of up to four (4)
pages of content, plus unlimited pages for references. Upon
acceptance, short papers will be given five (5) pages in the
proceedings and unlimited pages for references.

For both long and short papers, all illustrations and tables that are part
of the main text must be accommodated within these page limits, observing
the formatting instructions given in the present document. Supplementary
material in the form of appendices does not count towards the page limit; see appendix A for further information.

However, note that supplementary material should be supplementary
(rather than central) to the paper, and that reviewers may ignore
supplementary material when reviewing the paper (see Appendix
\ref{sec:supplemental}). Papers that do not conform to the specified
length and formatting requirements are subject to be rejected without
review.

Workshop chairs may have different rules for allowed length and
whether supplemental material is welcome. As always, the respective
call for papers is the authoritative source.

\section*{Acknowledgments}

The acknowledgments should go immediately before the references.  Do
not number the acknowledgments section. Do not include this section
when submitting your paper for review. \\

\noindent {\bf Preparing References:} \\

Include your own bib file like this:
{\small\verb|\bibliographystyle{acl_natbib_nourl}|
\verb|\bibliography{emnlp2018}|}

Where \verb|emnlp2018| corresponds to the {\tt emnlp2018.bib} file.
\bibliography{emnlp2018}
\bibliographystyle{acl_natbib_nourl}

\appendix

\section{Supplemental Material}
\label{sec:supplemental}
Each \confname{} submission can be accompanied by a single PDF
appendix, one {\small\tt.tgz} or {\small\tt.zip} appendix containing
software, and one {\small\tt.tgz} or {\small\tt.zip} appendix
containing data.

Submissions may include resources (software and/or data) used in in
the work and described in the paper. Papers that are submitted with
accompanying software and/or data may receive additional credit toward
the overall evaluation score, and the potential impact of the software
and data will be taken into account when making the
acceptance/rejection decisions. Any accompanying software and/or data
should include licenses and documentation of research review as
appropriate.

\confname{} also encourages the submission of supplementary material
to report preprocessing decisions, model parameters, and other details
necessary for the replication of the experiments reported in the
paper. Seemingly small preprocessing decisions can sometimes make a
large difference in performance, so it is crucial to record such
decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather
than central) to the paper. {\bf Submissions that misuse the supplementary
material may be rejected without review.}
Essentially, supplementary material may include explanations or details
of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system,
pseudo-code or source code, and data. (Source code and data should
be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper
may refer to and cite the supplementary material and the supplementary material will be available to the
reviewers, they will not be asked to review the
supplementary material.

Appendices ({\em i.e.} supplementary material in the form of proofs, tables,
or pseudo-code) should be {\bf uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here. Use
\verb|\appendix| before any appendix section to switch the section
numbering over to letters.

\end{document}

### 2018-05-17 EMNLP-demo-paper/emnlp2018.tex
update hover

--- 2018-05-17 EMNLP-demo-paper/NLPVis-demo-paper.tex
@@
 
-\title{Visual Integration Tool for the Natural Language Inference and Machine Comprehension Tasks}
+\title{Instructions for \confname{} Proceedings}
 
@@
 \section{Introduction}
-
-exploration task
-
-Comparsion with AllenNLP
+The following instructions are directed to authors of papers submitted
+to \confname{} or accepted for publication in its proceedings. All
+authors are required to adhere to these specifications. Authors are
+required to provide a Portable Document Format (PDF) version of their
+papers. \textbf{The proceedings are designed for printing on A4
+paper.}
 

### 2018-05-21 src/translationPerturbation.py
linked subMatrix vis is working

@@ -44,26 +44,3 @@ class translationPerturbation:
             sentenceList.add(outputSentence["translatedText"])
 
         return list(sentenceList)
-
-    def translate_text_with_model(target, text, model):
-        """Translates text into the target language.
-
-        Make sure your project is whitelisted.
-
-        Target must be an ISO 639-1 language code.
-        See https://g.co/cloud/translate/v2/translate-reference#supported_languages
-        """
-        translate_client = translate.Client()
-
-        if isinstance(text, six.binary_type):
-            text = text.decode('utf-8')
-
-        # Text can also be a sequence of strings, in which case this method
-        # will return a sequence of results for each text.
-        result = translate_client.translate(
-            text, target_language=target, model=model)
-
-        print(u'Text: {}'.format(result['input']))
-        print(u'Translation: {}'.format(result['translatedText']))
-        print(u'Detected source language: {}'.format(
-            result['detectedSourceLanguage']))

### 2018-05-21 src/visPackage/static/components/attentionMatrixComponent.js

@@ -14,6 +14,8 @@ class attentionMatrixComponent extends attentionComponent {
             'index': -1,
             'flag': false
         };
+
+        this.backgourndText = ['Premise', 'Hypothesis'];
     }
 
     draw() {
@@ -27,8 +29,6 @@ class attentionMatrixComponent extends attentionComponent {
             this.initSvg();
 
             //attention matrix
-            let attMatrix = this.normAttention;
-            // console.log(attMatrix);
             let attMax = 1.0;
             let attMin = 0.0;
             if (this.comparisonFlag) {
@@ -55,13 +55,23 @@ class attentionMatrixComponent extends attentionComponent {
 
             //location of words
             var pair = this.data["currentPair"]["sentences"];
+            this.srcWords = this.sen2words(pair[0]);
+            this.targWords = this.sen2words(pair[1]);
 
             this.aggregatedMatrix = Object.assign(this.normAttention);
 
-            this.attList = this.generateMatrixGeometry();
+            //for subMatrix
+            if (this.data["selectionRange"]) {
+                console.log(this.data["selectionRange"]);
+                this.srcWords = this.srcWords.slice(this.data[
+                        "selectionRange"][0],
+                    this.data["selectionRange"][1]);
+                this.aggregatedMatrix = this.aggregatedMatrix.slice(
+                    this.data["selectionRange"][0],
+                    this.data["selectionRange"][1]);
+            }
 
-            this.srcWords = this.sen2words(pair[0]);
-            this.targWords = this.sen2words(pair[1]);
+            this.attList = this.generateMatrixGeometry();
 
             this.computeWordPosition(this.srcWords, this.targWords);
 
@@ -195,12 +205,11 @@ class attentionMatrixComponent extends attentionComponent {
 
             ////////////// rect mouse over event ///////////////
             //this.rectMouseEvent(rects, targtext, srctext);
-
             //draw text background only when depTree do not exist
             if (this.srcDepTreeData === undefined) {
                 this.svg.selectAll(
                         '.attentionMatrixComponent_background_text')
-                    .data(['Premise', 'Hypothesis'])
+                    .data([this.backgourndText[0], this.backgourndText[1]])
                     .enter()
                     .append('text')
                     .text(d => d)
[…]

### 2018-05-21 src/visPackage/static/components/attentionSubMatrixComponent.js

@@ -1,0 +1,40 @@
+class attentionSubMatrixComponent extends attentionMatrixComponent {
+    constructor(uuid) {
+        super(uuid);
+        //sub matrix
+        this.subscribeDatabyNames(["selectionRange"]);
+        this.backgourndText = ['Paragraph', 'Question'];
+    }
+
+    parseDataUpdate(msg) {
+        // super.parseDataUpdate(msg);
+        //skip the base class's parse operation
+        this.updateData(msg);
+        switch (msg["name"]) {
+            case "selectionRange":
+                this.draw();
+                break;
+            case "attention":
+                if (this.rawAttention) {
+                    //clone the raw attention
+                    this.preRawAtt = JSON.parse(JSON.stringify(this.rawAttention));
+                }
+                this.rawAttention = this.data["attention"];
+                this.attentionDirection = 'row';
+                this.normAttentionRow = this.convertRawAtt(this.rawAttention,
+                    'row');
+
+                this.normAttentionCol = this.convertRawAtt(this.rawAttention,
+                    'col');
+
+                this.normAttention = this.normAttentionRow;
+                break;
+        }
+
+    }
+
+    // resize() {
+    //
+    // }
+
+}

### 2018-05-22 EMNLP-demo-paper/intro.tex

\section{Introduction}

exploration task

Comparsion with AllenNLP

### 2018-05-24 EMNLP-demo-paper/intro.tex
updates in intro

@@
 \section{Introduction}
+
+Neural networks have been successful in various natural language processing tasks,
+where end-to-end training become a primary option (cite).
+As the design of neural networks evolve, there is a clear trend that more and more
+parameters participate in training and prediction. While the strong expressivity
+enhance model performance, the lack of interpretability presents challenging for analysis.
+Without understanding the background meaning that features carry, visualization relies
+on proper quantification analysis (cite). Such analysis is not easy to come up with,
+and is tied to specific task (cite).
+
+Recently attention networks become a widely-adopted setup (cite), partly because it yields
+intermediate representations (e.g. alignment) that are not just beneficially expressive for performance,
+but also intuitive to model. Indeed, the interpretability of attention networks introduce
+a natural interface for analyzing the inside of neural networks. The wide popularity of attention networks
+in recent NLP works necessitate a convenience framework for visualization and analyzing.
+
+To facilitate exploration in attention models, we introduce an interactive visualization toolset.
 

### 2018-05-25 EMNLP-demo-paper/relatedWorks.tex
relate work in ACL demo

\section{Related Works}

Visualizing and understanding neural models in nlp
Understanding Neural Networks through Representation Erasure
Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights

\subseciton{other}
DeepLife: an Entity-aware Search, Analytics and Exploration Platform for Health and Life Sciences
Visualizing and Curating Knowledge Graphs over Time and Space
GoWvis: a Web Application for Graph-of-Words-based Text Visualization and summarization
new/s/leak - Information Extraction and Visualization for an Investigative Data Journalists
Multi-modal Visualization and Search for Text and Prosody Annotations
Visual Error Analysis for Entity Linking
JoBimViz: A Web-based Visualization for Graph-based Distributional Semantic Models
WA-Continuum: Visualising Word Alignments across Multiple Parallel Sentences Simultaneously
Scattertext: a Browser-Based Tool for Visualizing how Corpora Differ
Interactive Visual Analysis of Transcribed Multi-Party Discourse
Visualization, Search, and Error Analysis for Coreference Annotations

### 2018-05-26 bidaf_src/bidafModelInterface.py
update normalization of attention

@@ -55,7 +55,7 @@ class bidafModelInterface:
 
         # build model
         self.m = Pipeline(opt, self.shared)
-        self.m.train(False)
+        # self.m.train(False)
 
         # initialization
         self.opt = opt

### 2018-05-26 visPackage/static/components/attentionAsymmetricComponent.js

@@ -4,7 +4,7 @@ class attentionAsymmetricComponent extends attentionComponent {
         // this.subscribeDatabyNames(["attention", "currentPair"]);
 
         //create default colormap
-        this.colormap = generateColormap([1.0, 0.0], ["#253494", "#2c7fb8",
+        this.colormap = generateColormap([0.0, 1.0], ["#253494", "#2c7fb8",
             "#41b6c4", "#a1dab4",
             "#ffffcc"
         ]);
@@ -122,9 +122,11 @@ class attentionAsymmetricComponent extends attentionComponent {
 
             ///FIXME duplicated code from attentionGraphComponent
             ////////// getting attention normalized //////
-            let attMatrix = this.normAttention;
-            var srcAtt = attMatrix.map(d => d.reduce((a, b) => a +
-                b));
+            let attMatrix = this.rawAttention;
+            // var srcAtt = attMatrix.map(d => d.reduce((a, b) => a +
+            // b));
+            var srcAtt = attMatrix.map(d => Math.max(...d));
+            this.srcAtt = this.softmax(srcAtt);
             let srcAttMax = Math.max(...srcAtt);
             let srcAttMin = Math.min(...srcAtt);
             this.srcAtt = srcAtt.map(d =>
@@ -138,7 +140,9 @@ class attentionAsymmetricComponent extends attentionComponent {
                 return sum;
             });
             let targAttMax = Math.max(...targAtt);
-            targAtt = targAtt.map(d => d / targAttMax);
+            let targAttMin = Math.min(...targAtt);
+            targAtt = targAtt.map(d =>
+                (d - targAttMin) / (targAttMax - targAttMin));
 
             let unit = this.width * 0.85 / paragraphLen;
             this.paraPos = [];
@@ -192,11 +196,11 @@ class attentionAsymmetricComponent extends attentionComponent {
 
             // console.log(this.questionPos);
             if (this.aggregateSen) {
-                this.aggregateMatrix = this.aggregateMatrixBySen(attMatrix,
+                this.aggregateMatrix = this.aggregateMatrixBySen(this.normAttention,
                     this.segmentList);
                 this.drawLink(this.paraPos, this.questionPos, this.aggregateMatrix);
             } else {
-                this.drawLink(this.paraPos, this.questionPos, attMatrix);
+                this.drawLink(this.paraPos, this.questionPos, this.normAttention);
             }
 
         }

### 2018-05-26 EMNLP-demo-paper/NLPVis-demo-paper.tex
linked subMatrix vis is working
updates in intro
update normalization of attention
cleanup paper layout

@@
 %% Based on the style files for EACL 2006 by
-%%e.agirre@ehu.es or Sergi.Balari@uab.es
+%% e.agirre@ehu.es or Sergi.Balari@uab.es
 %% and that of ACL 08 by Joakim Nivre and Noah Smith
@@
 \usepackage{latexsym}
-
 \usepackage{url}
@@
 
-\title{Visual Integration Tool for the Natural Language Inference and Machine Comprehension Tasks}
+\title{Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension}
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
+\author{Shusen Liu \\
+  Lawrence Livermore National Laboratory  / 7000 East Ave, Livermore, CA 94550 \\
   {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
+  Tao Li \\
+  University of Utah / Address line 1 \\
   Affiliation / Address line 2 \\
@@
 \begin{abstract}
-  This document contains the instructions for preparing a camera-ready
-  manuscript for the proceedings of \confname{}. The document itself
-  conforms to its own specifications, and is therefore an example of
-  what your manuscript should look like. These instructions should be
-  used for both papers submitted for review and for final versions of
-  accepted papers.  Authors are asked to conform to all the directions
-  reported in this document.
+Neural-network-based end-to-end models have gained unprecedented popularity in natural language processing, despite their impressive performance, the lack of interpretability hinder the development and refinement of the model.
+%
+In this work, we present a flexible visualization library for creating customized visual analytic environment that allow the user to explore the model internals (i.e., attention) and interrogate the model decision making process.
+
 \end{abstract}
 
-\section{Credits}
+\input{intro.tex}
+\input{relatedWorks.tex}
+\input{system.tex}
+\input{result.tex}
 
-This document has been adapted from the instructions for earlier ACL
-and NAACL proceedings. It represents a recent build from
-\url{https://github.com/acl-org/acl-pub}, with modifications by Micha
-Elsner and Preethi Raghavan, based on the NAACL 2018 instructions by
-Margaret Michell and Stephanie Lukin, 2017/2018 (NA)ACL bibtex
-suggestions from Jason Eisner, ACL 2017 by Dan Gildea and Min-Yen Kan,
-NAACL 2017 by Margaret Mitchell, ACL 2012 by Maggie Li and Michael
-White, those from ACL 2010 by Jing-Shing Chang and Philipp Koehn,
-those for ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan,
-and Sadaoki Furui, those for ACL 2005 by Hwee Tou Ng and Kemal
-Oflazer, those for ACL 2002 by Eugene Charniak and Dekang Lin, and
-earlier ACL and EACL formats.  Those versions were written by several
-people, including John Chen, Henry S. Thompson and Donald
-Walker. Additional elements were taken from the formatting
-instructions of the {\em International Joint Conference on Artificial
-  Intelligence} and the \emph{Conference on Computer Vision and
-  Pattern Recognition}.
+\bibliographystyle{abbrv-doi}
+%\bibliographystyle{abbrv-doi-narrow}
+%\bibliographystyle{abbrv-doi-hyperref}
+%\bibliographystyle{abbrv-doi-hyperref-narrow}
 
-\section{Introduction}
-
-exploration task
-
-Comparsion with AllenNLP
-
-\section{General Instructions}
-
-Manuscripts must be in two-column format.  Exceptions to the
-two-column format include the title, authors' names and complete
-addresses, which must be centered at the top of the first page, and
-any full-width figures or tables (see the guidelines in
-Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
-pages directly under the top margin. See the guidelines later
-regarding formatting the first page.  The manuscript should be
-printed single-sided and its length
-should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Pages are numbered for  initial submission. However, {\bf do not number the pages in the camera-ready version}.
-
-By uncommenting {\small\verb|\aclfinalcopy|} at the top of this
- document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.
-When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top.
-
-The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.
-However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.
-The \confname{} \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.
-
-The author list for submissions should include all (and only) individuals who made substantial contributions to the work presented.
-Each author listed on a submission to \confname{} will be notified of submissions, revisions and the final decision.
-No authors may be added to or removed from submissions to \confname{} after the submission deadline.
-
-\subsection{The Ruler}
-The \confname{} style defines a printed ruler which should be presented in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document without the provided
-style files, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\small\verb|\aclfinalcopy|} command in the document preamble.)
-
-Reviewers: note that the ruler measurements do not align well with
-lines in the paper -- this turns out to be very difficult to do well
-when the paper contains many figures and equations, and, when done,
-looks ugly. In most cases one would expect that the approximate
-location will be adequate, although you can also use fractional
-references ({\em e.g.}, the first paragraph on this page ends at mark $108.5$).
-
-\subsection{Electronically-available resources}
-
-\conforg{} provides this description in \LaTeX2e{} ({\small\tt
-  emnlp2018.tex}) and PDF format ({\small\tt emnlp2018.pdf}), along
-with the \LaTeX2e{} style file used to format it ({\small\tt
-  emnlp2018.sty}) and an ACL bibliography style ({\small\tt
-  acl\_natbib\_nourl.bst}) and example bibliography ({\small\tt
-  emnlp2018.bib}).  These files are all available at
-\url{http://emnlp2018.org/downloads/emnlp18-latex.zip}; a Microsoft
-Word template file ({\small\tt emnlp18-word.docx}) and example
-submission pdf ({\small\tt emnlp18-word.pdf}) is available at
-\url{http://emnlp2018.org/downloads/emnlp18-word.zip}.  We strongly
-recommend the use of these style files, which have been appropriately
-tailored for the \confname{} proceedings.
-
-\subsection{Format of Electronic Manuscript}
-\label{sect:pdf}
-
-For the production of the electronic manuscript you must use Adobe's
-Portable Document Format (PDF). PDF files are usually produced from
-\LaTeX\ using the \textit{pdflatex} command. If your version of
-\LaTeX\ produces Postscript files, you can convert these into PDF
-using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
-Adobe Distiller to generate PDF.
-
-Please make sure that your PDF file includes all the necessary fonts
-(especially tree diagrams, symbols, and fonts with Asian
-characters). When you print or create the PDF file, there is usually
-an option in your printer setup to include none, all or just
-non-standard fonts.  Please make sure that you select the option of
-including ALL the fonts. \textbf{Before sending it, test your PDF by
-  printing it from a computer different from the one where it was
-  created.} Moreover, some word processors may generate very large PDF
-files, where each page is rendered as an image. Such images may
-reproduce poorly. In this case, try alternative ways to obtain the
-PDF. One way on some systems is to install a driver for a postscript
-printer, send your document to the printer specifying ``Output to a
-file'', then convert the file to PDF.
-
-It is of utmost importance to specify the \textbf{A4 format} (21 cm
-x 29.7 cm) when formatting the paper. When working with
-{\tt dvips}, for instance, one should specify {\tt -t a4}.
-Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
-preamble (directly below the \verb|\usepackage| commands). Then using
-{\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.
-
-Print-outs of the PDF file on A4 paper should be identical to the
-hardcopy version. If you cannot meet the above requirements about the
-production of your electronic submission, please contact the
-publication chairs as soon as possible.
-
-\subsection{Layout}
-\label{ssec:layout}
-
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted. The exact dimensions for a page on A4
-paper are:
-
-\begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
-\end{itemize}
-
-\noindent Papers should not be submitted on any other paper size.
- If you cannot meet the above requirements about the production of
- your electronic submission, please contact the publication chairs
- above as soon as possible.
-
-\subsection{Fonts}
-
-For reasons of uniformity, Adobe's {\bf Times Roman} font should be
-used. In \LaTeX2e{} this is accomplished by putting
-
-\begin{quote}
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
-in the preamble. If Times Roman is unavailable, use {\bf Computer
-  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
-  10\% less dense than Adobe's Times Roman font.
-
-\begin{table}[t!]
-\begin{center}
-\begin{tabular}{|l|rl|}
-\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-document text & 11 pt  &\\
-captions & 10 pt & \\
-abstract text & 10 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
-\hline
-\end{tabular}
-\end{center}
-\caption{\label{font-table} Font guide. }
-\end{table}
-
-\subsection{The First Page}
-\label{ssec:first}
-
-Center the title, author's name(s) and affiliation(s) across both
-columns. Do not use footnotes for affiliations. Do not include the
-paper ID number assigned during the submission process. Use the
-two-column format only when you begin the abstract.
-
-{\bf Title}: Place the title centered at the top of the first page, in
-a 15-point bold font. (For a complete guide to font sizes and styles,
-see Table~\ref{font-table}) Long titles should be typed on two lines
-without a blank line intervening. Approximately, put the title at 2.5
-cm from the top of the page, followed by a blank line, then the
-author's names(s), and the affiliation on the following line. Do not
-use only initials for given names (middle initials are allowed). Do
-not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
-``MITCHELL'').  Do not format title and section headings in all
-capitals as well except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.  The affiliation should contain the
-author's complete address, and if possible, an electronic mail
-address. Start the body of the first page 7.5 cm from the top of the
-page.
-
-The title, author names and addresses should be completely identical
-to those entered to the electronical paper submission website in order
-to maintain the consistency of author information among all
-publications of the conference. If they are different, the publication
-chairs may resolve the difference without consulting with you; so it
-is in your own interest to double-check that the information is
-consistent.
-
-{\bf Abstract}: Type the abstract at the beginning of the first
-column. The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by about
-0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
-font above the body of the abstract. The abstract should be a concise
-summary of the general thesis and conclusions of the paper. It should
-be no longer than 200 words. The abstract text should be in 10 point font.
-
-{\bf Text}: Begin typing the main body of the text immediately after
-the abstract, observing the two-column format as shown in
-
-the present document. Do not include page numbers.
-
-{\bf Indent}: Indent when starting a new paragraph, about 0.4 cm. Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.
-
-\begin{table}
-\centering
-\small
-\begin{tabular}{cc}
-\begin{tabular}{|l|l|}
-\hline
-{\bf Command} & {\bf Output}\\\hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\
-\verb|{\.I}| & {\.I} \\
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular} &
-\begin{tabular}{|l|l|}
-\hline
-{\bf Command} & {\bf  Output}\\\hline
-\verb|{\c c}| & {\c c} \\
-\verb|{\u g}| & {\u g} \\
-\verb|{\l}| & {\l} \\
-\verb|{\~n}| & {\~n} \\
-\verb|{\H o}| & {\H o} \\
-\verb|{\v r}| & {\v r} \\
-\verb|{\ss}| & {\ss} \\\hline
-\end{tabular}
-\end{tabular}
-\caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
-\end{table}
-
-\subsection{Sections}
-
-{\bf Headings}: Type and label section and subsection headings in the
-style shown on the present document.  Use numbered sections (Arabic
-numerals) in order to facilitate cross references. Number subsections
-with the section number and the subsection number separated by a dot,
-in Arabic numerals.
-Do not number subsubsections.
-
-\begin{table*}[t!]
-\centering
-\begin{tabular}{lll}
-  output & natbib & previous \conforg{} style files\\
-  \hline
-  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
-  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
-  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
-\end{tabular}
-\caption{Citation commands supported by the style file.
-  The citation style is based on the natbib package and
-  supports all natbib citation commands.
-  It also supports commands defined in previous \conforg{} style files
-  for compatibility.
-  }
-\end{table*}
-
-{\bf Citations}: Citations within the text appear in parentheses
-as~\cite{Gusfield:97} or, if the author's name appears in the text
-itself, as Gusfield~\shortcite{Gusfield:97}.
-Using the provided \LaTeX\ style, the former is accomplished using
-{\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}.
-Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\small\verb|\cite|} command, {\em e.g.}, {\small\verb|\cite{Gusfield:97,Aho:72}|}.
-Append lowercase letters to the year in cases of ambiguities.
- Treat double authors as
-in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
-authors are involved. Collapse multiple citations as
-in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
-as sentence constituents.
-
-We suggest that instead of
-\begin{quote}
-  ``\cite{Gusfield:97} showed that ...''
-\end{quote}
-you use
-\begin{quote}
-``Gusfield \shortcite{Gusfield:97}   showed that ...''
-\end{quote}
-
-If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
-can use the command \verb|\citet| (cite in text)
-to get ``author (year)'' citations.
-
-If the Bib\TeX{} file contains DOI fields, the paper
-title in the references section will appear as a hyperlink
-to the DOI, using the hyperref \LaTeX{} package.
-To disable the hyperref package, load the style file
-with the \verb|nohyperref| option: \\{\small
-\verb|\usepackage[nohyperref]{acl2018}|}
-
-\textbf{Digital Object Identifiers}: As part of our work to make ACL
-materials more widely used and cited outside of our discipline, ACL
-has registered as a CrossRef member, as a registrant of Digital Object
-Identifiers (DOIs), the standard for registering permanent URNs for
-referencing scholarly materials. \conforg{} has \textbf{not} adopted the
-ACL policy of requiring camera-ready references to contain the appropriate
-  DOIs (or as a second resort, the hyperlinked ACL Anthology
-  Identifier). But we certainly encourage you to use
-  Bib\TeX\ records that contain DOI or URLs for any of the ACL
-  materials that you reference. Appropriate records should be found
-for most materials in the current ACL Anthology at
-\url{http://aclanthology.info/}.
-
-As examples, we cite \cite{P16-1001} to show you how papers with a DOI
-will appear in the bibliography.  We cite \cite{C14-1001} to show how
-papers without a DOI but with an ACL Anthology Identifier will appear
-in the bibliography.
-
-\textbf{Anonymity:} As reviewing will be double-blind, the submitted
-version of the papers should not include the authors' names and
-affiliations. Furthermore, self-references that reveal the author's
-identity, {\em e.g.},
-\begin{quote}
-``We previously showed \cite{Gusfield:97} ...''
-\end{quote}
-should be avoided. Instead, use citations such as
-\begin{quote}
-``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
-previously showed ... ''
-\end{quote}
-
-Preprint servers such as arXiv.org and workshops that do not
-have published proceedings are not considered archival for purposes of
-submission. However, to preserve the spirit of blind review, authors
-are encouraged to refrain from posting until the completion of the
-review process. Otherwise, authors must state in the online submission
-form the name of the workshop or preprint server and title of the
-non-archival version. The submitted version should be suitably
-anonymized and not contain references to the prior non-archival
-version. Reviewers will be told: ``The author(s) have notified us that
-there exists a non-archival previous version of this paper with
-significantly overlapping text. We have approved submission under
-these circumstances, but to preserve the spirit of blind review, the
-current submission does not reference the non-archival version.''
-
-\textbf{Please do not use anonymous citations} and do not include
- when submitting your papers. Papers that do not
-conform to these requirements may be rejected without review.
-
-\textbf{References}: Gather the full set of references together under
-the heading {\bf References}; place the section before any Appendices,
-unless they contain references. Arrange the references alphabetically
-by first author, rather than by order of occurrence in the text.
-By using a .bib file, as in this template, this will be automatically
-handled for you. See the \verb|\bibliography| commands near the end for more.
-
-Provide as complete a citation as possible, using a consistent format,
-such as the one for {\em Computational Linguistics\/} or the one in the
-{\em Publication Manual of the American
-Psychological Association\/}~\cite{APA:83}. Use of full names for
-authors rather than initials is preferred. A list of abbreviations
-for common computer science journals can be found in the ACM
-{\em Computing Reviews\/}~\cite{ACM:83}.
-
-The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
-American Psychological Association format, allowing regular citations,
-short citations and multiple citations as described above.
-
-\begin{itemize}
-\item Example citing an arxiv paper: \cite{rasooli-tetrault-2015}.
-\item Example article in journal citation: \cite{Ando2005}.
-\item Example article in proceedings, with location: \cite{borsch2011}.
-\item Example article in proceedings, without location: \cite{andrew2007scalable}.
-\end{itemize}
-See corresponding .bib file for further details.
-
-Submissions should accurately reference prior and related work, including code and data.
-If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
-If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
-Authors should not rely on automated citation indices to provide accurate references for prior and related work.
-
-{\bf Appendices}: Appendices, if any, directly follow the text and the
-references (but see above).  Letter them in sequence and provide an
-informative title: {\bf Appendix A. Title of Appendix}.
-
-\subsection{URLs}
-
-URLs can be typeset using the \verb|\url| command. However, very long
-URLs cause a known issue in which the URL highlighting may incorrectly
-cross pages or columns in the document. Please check carefully for
-URLs too long to appear in the column, which we recommend you break,
-shorten or place in footnotes. Be aware that actual URL should appear
-in the text in human-readable format; neither internal nor external
-hyperlinks will appear in the proceedings.
-
-\subsection{Footnotes}
-
-{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
-point font. They may be numbered or referred to by asterisks or other
-symbols.\footnote{This is how a footnote should appear.} Footnotes
-should be separated from the text by a line.\footnote{Note the line
-separating the footnotes from the text.}
-
-\subsection{Graphics}
-
-{\bf Illustrations}: Place figures, tables, and photographs in the
-paper near where they are first discussed, rather than at the end, if
-possible.  Wide illustrations may run across both columns.  Color
-illustrations are discouraged, unless you have verified that
-they will be understandable when printed in black ink.
-
-{\bf Captions}: Provide a caption for every illustration; number each one
-sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
-Caption of the Table.''  Type the captions of the figures and
-tables below the body, using 11 point text.
-
-\subsection{Accessibility}
-\label{ssec:accessibility}
-
-In an effort to accommodate people who are color-blind (as well as those printing
-to paper), grayscale readability for all accepted papers will be
-encouraged.  Color is not forbidden, but authors should ensure that
-tables and figures do not rely solely on color to convey critical
-distinctions. A simple criterion: All curves and points in your figures should be clearly distinguishable without color.
-
-% Min: no longer used as of ACL 2018, following ACL exec's decision to
-% remove this extra workflow that was not executed much.
-% BEGIN: remove
-%% \section{XML conversion and supported \LaTeX\ packages}
-
-%% Following ACL 2014 we will also we will attempt to automatically convert
-%% your \LaTeX\ source files to publish papers in machine-readable
-%% XML with semantic markup in the ACL Anthology, in addition to the
-%% traditional PDF format.  This will allow us to create, over the next
-%% few years, a growing corpus of scientific text for our own future research,
-%% and picks up on recent initiatives on converting ACL papers from earlier
-%% years to XML.
-
-%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
-%% with the camera-ready version of your paper. We will then convert them
-%% to XML automatically, using the LaTeXML tool
-%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
-%% a number of \LaTeX\ packages, including the ACL 2018 stylefile. These
-%% bindings allow LaTeXML to render the commands from these packages
-%% correctly in XML. For best results, we encourage you to use the
-%% packages that are officially supported by LaTeXML, listed at
-%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
-% END: remove
-
-\section{Translation of non-English Terms}
-
-It is also advised to supplement non-English characters and terms
-with appropriate transliterations and/or translations
-since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in
-the order of: original-form transliteration ``translation''.
-
-\section{Length of Submission}
-\label{sec:length}
-
-The \confname{} main conference accepts submissions of long papers and
-short papers.
- Long papers may consist of up to eight (8) pages of
-content plus unlimited pages for references. Upon acceptance, final
-versions of long papers will be given one additional page -- up to nine (9)
-pages of content plus unlimited pages for references -- so that reviewers' comments
-can be taken into account. Short papers may consist of up to four (4)
-pages of content, plus unlimited pages for references. Upon
-acceptance, short papers will be given five (5) pages in the
-proceedings and unlimited pages for references.
-
-For both long and short papers, all illustrations and tables that are part
-of the main text must be accommodated within these page limits, observing
-the formatting instructions given in the present document. Supplementary
-material in the form of appendices does not count towards the page limit; see appendix A for further information.
-
-However, note that supplementary material should be supplementary
-(rather than central) to the paper, and that reviewers may ignore
-supplementary material when reviewing the paper (see Appendix
-\ref{sec:supplemental}). Papers that do not conform to the specified
-length and formatting requirements are subject to be rejected without
-review.
-
-Workshop chairs may have different rules for allowed length and
-whether supplemental material is welcome. As always, the respective
-call for papers is the authoritative source.
-
-\section*{Acknowledgments}
-
-The acknowledgments should go immediately before the references.  Do
-not number the acknowledgments section. Do not include this section
-when submitting your paper for review. \\
-
-\noindent {\bf Preparing References:} \\
-
-Include your own bib file like this:
-{\small\verb|\bibliographystyle{acl_natbib_nourl}|
-\verb|\bibliography{emnlp2018}|}
-
-Where \verb|emnlp2018| corresponds to the {\tt emnlp2018.bib} file.
-\bibliography{emnlp2018}
-\bibliographystyle{acl_natbib_nourl}
-
-\appendix
-
-\section{Supplemental Material}
-\label{sec:supplemental}
-Each \confname{} submission can be accompanied by a single PDF
-appendix, one {\small\tt.tgz} or {\small\tt.zip} appendix containing
-software, and one {\small\tt.tgz} or {\small\tt.zip} appendix
-containing data.
-
-Submissions may include resources (software and/or data) used in in
-the work and described in the paper. Papers that are submitted with
-accompanying software and/or data may receive additional credit toward
-the overall evaluation score, and the potential impact of the software
-and data will be taken into account when making the
-acceptance/rejection decisions. Any accompanying software and/or data
-should include licenses and documentation of research review as
-appropriate.
-
-\confname{} also encourages the submission of supplementary material
-to report preprocessing decisions, model parameters, and other details
-necessary for the replication of the experiments reported in the
-paper. Seemingly small preprocessing decisions can sometimes make a
-large difference in performance, so it is crucial to record such
-decisions to precisely characterize state-of-the-art methods.
-
-Nonetheless, supplementary material should be supplementary (rather
-than central) to the paper. {\bf Submissions that misuse the supplementary
-material may be rejected without review.}
-Essentially, supplementary material may include explanations or details
-of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system,
-pseudo-code or source code, and data. (Source code and data should
-be separate uploads, rather than part of the paper).
-
-The paper should not rely on the supplementary material: while the paper
-may refer to and cite the supplementary material and the supplementary material will be available to the
-reviewers, they will not be asked to review the
-supplementary material.
-
-Appendices ({\em i.e.} supplementary material in the form of proofs, tables,
-or pseudo-code) should be {\bf uploaded as supplementary material} when submitting the paper for review.
-Upon acceptance, the appendices come after the references, as shown here. Use
-\verb|\appendix| before any appendix section to switch the section
-numbering over to letters.
+\bibliography{NLPvis.bib}
 

### 2018-05-26 EMNLP-demo-paper/relatedWorks.tex
cleanup paper layout

@@
 
-\subseciton{other}
+%\subseciton{other}
 DeepLife: an Entity-aware Search, Analytics and Exploration Platform for Health and Life Sciences

### 2018-05-27 EMNLP-demo-paper/intro.tex
cleanup paper layout
updates in intro

@@
 Neural networks have been successful in various natural language processing tasks,
-where end-to-end training become a primary option (cite).
+where end-to-end training become a primary option (\cite{}).
 As the design of neural networks evolve, there is a clear trend that more and more
 parameters participate in training and prediction. While the strong expressivity
-enhance model performance, the lack of interpretability presents challenging for analysis.
+enhance model performance, the lack of interpretability presents challenge for analysis.
 Without understanding the background meaning that features carry, visualization relies
@@
 
-To facilitate exploration in attention models, we introduce an interactive visualization toolset.
+To facilitate exploration in attention models, we introduce an interactive visualization toolset
+for word-attention models. We demonstrate our system on two primary NLP tasks: natural language
+inference (NLI) and machine comprehension (MC). For the NLI task, we visualize
+decomposable attention networks which represents a series of strongly performing models \cite{}.
+For the MC task, we present your visualization methods on bidirectional attention flow model,
+which also represents a line of strong models \cite{}.
+
+In summary, our contribution in this papers are:
+\begin{itemize}
+	\item 1. We present an interactive visualization system for word-attention neural
+	networks in NLP. Our system allows to...
+	\item 2. We demonstrate our system on two major NLP tasks with strong-performing
+	models. We observe functional limitations of these models which can be helpful
+	for future improvement on modeling.
+\end{itemize}
 

### 2018-05-27 EMNLP-demo-paper/NLPVis-demo-paper.tex
add abstract
update intro

@@
 
-\title{Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension}
+\title{Visual Interpretation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension}
 
@@
 \maketitle
+
 \begin{abstract}
-Neural-network-based end-to-end models have gained unprecedented popularity in natural language processing, despite their impressive performance, the lack of interpretability hinder the development and refinement of the model.
+Neural networks models have gained unprecedented popularity in natural language processing due to their state-of-the-art performance and the straightforward end-to-end training scheme.
+Despite their advantages, the lack of interpretability hinders the further development and refinement of the model.
 %
-In this work, we present a flexible visualization library for creating customized visual analytic environment that allow the user to explore the model internals (i.e., attention) and interrogate the model decision making process.
+These models often relying on the attention mechanism, which not only helps improve predicting performance but also provide interpretable representations for users to peak into the opaque models that are usually considered as black boxes.
+%
+In this work, we present a flexible visualization library for creating customized visual analytic environments, which enables the user to investigate and interrogate the relationship among the input, the model internals, and the output predictions that in turn shed light on the model decision making processing.
 
@@
 
-\bibliographystyle{abbrv-doi}
-%\bibliographystyle{abbrv-doi-narrow}
-%\bibliographystyle{abbrv-doi-hyperref}
-%\bibliographystyle{abbrv-doi-hyperref-narrow}
-
+\bibliographystyle{acl_natbib_nourl}
 \bibliography{NLPvis.bib}

### 2018-05-27 EMNLP-demo-paper/NLPVis-demo-paper.tex
update abstract

--- 2018-05-26 EMNLP-demo-paper/NLPVis-demo-paper.tex
@@
 \maketitle
+
 \begin{abstract}
-Neural-network-based end-to-end models have gained unprecedented popularity in natural language processing, despite their impressive performance, the lack of interpretability hinder the development and refinement of the model.
+Neural networks models have gained unprecedented popularity in natural language processing due to their state-of-the-art performance and the flexible end-to-end training scheme.
+Despite their advantages, the lack of interpretability hinders the further development and refinement of the model.
+%These models often relying on the attention mechanism, which not only helps improve predicting performance but also provide interpretable representations for users to peak into the opaque models that are usually considered as black boxes.
 %
-In this work, we present a flexible visualization library for creating customized visual analytic environment that allow the user to explore the model internals (i.e., attention) and interrogate the model decision making process.
+In this work, we present a flexible visualization library for creating customized visual analytic environments, which enables the user to investigate and interrogate the relationship among the input, the model internals (i.e., attention), and the output predictions that in turn shed light on the model decision making processing.
 

### 2018-05-27 EMNLP-demo-paper/intro.tex
add abstract
update intro
add figure

@@
 Neural networks have been successful in various natural language processing tasks,
-where end-to-end training become a primary option (\cite{}).
+where end-to-end training become a primary option \cite{Seo2016}.
 As the design of neural networks evolve, there is a clear trend that more and more
@@
 
-In summary, our contribution in this papers are:
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{pipeline}
+ \caption{
+ Perturbation-Driven Exploration of the NLP Model.
+ }
+\label{fig:modelPipeline}
+\end{figure}
+
+In summary, our key contributions are:
 \begin{itemize}
-	\item 1. We present an interactive visualization system for word-attention neural
-	networks in NLP. Our system allows to...
-	\item 2. We demonstrate our system on two major NLP tasks with strong-performing
+	\item Introduce an flexible visualization system for creating customized interactive visual analytic environment for attention centric neural networks model in NLP. 
+	\item Illustrate the importance of streamlining the query to the model
+	\item Demonstrate our system on two major NLP tasks with strong-performing
 	models. We observe functional limitations of these models which can be helpful
@@
 exploration task
-
+\cite{Seo2016}
 Comparsion with AllenNLP

### 2018-05-27 EMNLP-demo-paper/result.tex
add figure

\section{Application Results}
\subsection{Natural Language Inference}

\subsection{Machine Comprehension}

### 2018-05-27 EMNLP-demo-paper/system.tex
add figure

\section{System}
We design the proposed system with modularity in mind
\subsection{Input Perturbation}

### 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
delete unrelated work

@@
 Understanding Neural Networks through Representation Erasure
+
 Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
+\textcolor{blue}{Lee visualizes the beam search and attention component in the NMT model.
+The work allows user involve into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.}
+
 End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights
-
-%\subseciton{other}
-DeepLife: an Entity-aware Search, Analytics and Exploration Platform for Health and Life Sciences
-Visualizing and Curating Knowledge Graphs over Time and Space
-GoWvis: a Web Application for Graph-of-Words-based Text Visualization and summarization
-new/s/leak - Information Extraction and Visualization for an Investigative Data Journalists
-Multi-modal Visualization and Search for Text and Prosody Annotations
-Visual Error Analysis for Entity Linking
-JoBimViz: A Web-based Visualization for Graph-based Distributional Semantic Models
-WA-Continuum: Visualising Word Alignments across Multiple Parallel Sentences Simultaneously
-Scattertext: a Browser-Based Tool for Visualizing how Corpora Differ
-Interactive Visual Analysis of Transcribed Multi-Party Discourse
-Visualization, Search, and Error Analysis for Coreference Annotations
+\textcolor{blue}{Instead of visualizing the attention matrix directly, the system shows the text context and highlights the critical phrase, which used to answers the questions, using color map.
+In this platform, user able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.}

### 2018-05-28 EMNLP-demo-paper/NLPVis-demo-paper.tex
add figure
update intro

@@
 %\aclfinalcopy % Uncomment this line for the final submission
+
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 
+\usepackage{graphicx}
+\graphicspath{{figures/}{pictures/}{figs/}{./}} % where to search for the images
+
 \newcommand\BibTeX{B{\sc ib}\TeX}
 \newcommand\confname{EMNLP 2018}
-\newcommand\conforg{SIGDAT}
+%\newcommand\conforg{SIGDAT}
 
@@
 \author{Shusen Liu \\
-  Lawrence Livermore National Laboratory  / 7000 East Ave, Livermore, CA 94550 \\
-  {\tt email@domain} \\\And
-  Tao Li \\
-  University of Utah / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+  Lawrence Livermore National Laboratory\\
+  {\tt liu42@llnl.gov} \\\And
+  Tao Li,  Zhimin Li,  Vivek Srikumar, Valerio Pascucci \\
+  School of Computing, University of Utah\\
+    {\tt {tao.li, zhimin.li, vivek, pacucci}@utah.edu}
+}
 

### 2018-05-28 EMNLP-demo-paper/intro.tex
update intro

@@
 
-Neural networks have been successful in various natural language processing tasks,
+Deep neural networks have been successfully applied to various natural language processing tasks,
 where end-to-end training become a primary option \cite{Seo2016}.
-As the design of neural networks evolve, there is a clear trend that more and more
-parameters participate in training and prediction. While the strong expressivity
-enhance model performance, the lack of interpretability presents challenge for analysis.
-Without understanding the background meaning that features carry, visualization relies
-on proper quantification analysis (cite). Such analysis is not easy to come up with,
-and is tied to specific task (cite).
+As the design of neural networks evolve, there is a clear trend of increasing complexity of the model in term of architecture and parameters count. 
+While the strong expressivity enhance model performance, the lack of interpretability presents challenge for analyzing and improving upon the existing models.
+%Without understanding the background meaning that features carry, visualization relies
+%on proper quantification analysis (cite). Such analysis is not easy to come up with,
+%and is tied to specific task (cite).
 
-Recently attention networks become a widely-adopted setup (cite), partly because it yields
+Recently, attention networks have become a widely-adopted mechanism  \cite{VaswaniShazeerParmar2017, Parikh2016}, partly because it yields
 intermediate representations (e.g. alignment) that are not just beneficially expressive for performance,

### 2018-05-28 EMNLP-demo-paper/intro.tex
update intro

@@
 Deep neural networks have been successfully applied to various natural language processing tasks,
-where end-to-end training become a primary option \cite{Seo2016}.
-As the design of neural networks evolve, there is a clear trend of increasing complexity of the model in term of architecture and parameters count. 
-While the strong expressivity enhance model performance, the lack of interpretability presents challenge for analyzing and improving upon the existing models.
+%where end-to-end training become a primary option.
+and as the design of neural networks evolve, there is a clear trend of increasing model complexity both in term of architecture and parameters count. 
+%
+While the expressiveness of these models help improve the prediction performance, there is a fundamental lack of interpretability that lead many to consider neural network based models black boxes. 
+%
+Despite the difficulties, it is imperative to devise techniques to interpret the model internals and reason about a given prediction, which are essential to understand limitation of the model and improve upon the existing designs.
+
 %Without understanding the background meaning that features carry, visualization relies
@@
 
-Recently, attention networks have become a widely-adopted mechanism  \cite{VaswaniShazeerParmar2017, Parikh2016}, partly because it yields
-intermediate representations (e.g. alignment) that are not just beneficially expressive for performance,
-but also intuitive to model. Indeed, the interpretability of attention networks introduce
-a natural interface for analyzing the inside of neural networks. The wide popularity of attention networks
-in recent NLP works necessitate a convenience framework for visualization and analyzing.
+Recently, attention networks have become a widely-adopted mechanism \cite{VaswaniShazeerParmar2017, Parikh2016}, the attention not only improves the model performance, but also yields interpretable intermediate representations (e.g.
+alignment among words).
+As a result, attention has been used as a natural interface for analyzing the internals of neural networks.
+Conduct analysis directly on the raw attention values can be challenging for human user, therefore, visual representations that highlight word alignments between sentences have been adopted, such as bipartite graph and heat map of the attention matrix~\cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
+However, many challenges remains.
+To begin with, for some NLP tasks, the word sequence pair among which the attentions are computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), where the standard visual encoding can not adequately handle.
+In addition, many previous works present the attention in a statics setting.
+Yet, the ability to provide an interactive environment, where the user can instantaneously look at how changes in the input will affect the attention, and how small changes in attention will affect the prediction is crucial for interpreting the model.
+Finally, many previous visualization efforts, despite reveal many interesting results, focus more on illustrating potentially useful visualization technique than provide a flexible software tool that can be easily integrated into existing code base.
+As a result, applying these proposed techniques to real word examples may involving substantial engineering effort than many user may not willing to undertake.
 
-To facilitate exploration in attention models, we introduce an interactive visualization toolset
-for word-attention models. We demonstrate our system on two primary NLP tasks: natural language
+To address these challenges and facilitate interpretation of attention-based models, 
+we introduce a flexible python library that allow user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
+%
+To facilitate exploratory analysis (see Figure~\ref{fig:modelPipeline}), we adopted a fully interactive pipeline, where the user can perturb the input text (via two perturbation schemes discussed in Section~\ref{sec:perturb}) and observe the effects on attention and prediction, or modify the attention to understand how it affect the predictions.
+%
+We demonstrate our system on two primary NLP tasks: natural language
 inference (NLI) and machine comprehension (MC). For the NLI task, we visualize
-decomposable attention networks which represents a series of strongly performing models \cite{}.
+decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
 For the MC task, we present your visualization methods on bidirectional attention flow model,
-which also represents a line of strong models \cite{}.
+which also represents a line of strong models \cite{Seo2016}.
 
@@
  \caption{
- Perturbation-Driven Exploration of the NLP Model.
+ Perturbation-driven exploration of the end-to-end models that follows the encoder, attention, and classifier structure. The user can generate small perturbation of the input (i.e., paraphrasing)
  }
@@
 
-In summary, our key contributions are:
-\begin{itemize}
-	\item Introduce an flexible visualization system for creating customized interactive visual analytic environment for attention centric neural networks model in NLP. 
-	\item Illustrate the importance of streamlining the query to the model
-	\item Demonstrate our system on two major NLP tasks with strong-performing
-	models. We observe functional limitations of these models which can be helpful
-	for future improvement on modeling.
-\end{itemize}
-
-exploration task
-\cite{Seo2016}
-Comparsion with AllenNLP
+%In summary, our key contributions are:
+%\begin{itemize}
+%	\item Introduce an flexible visualization system for creating customized interactive visual analytic environment for attention centric neural networks models;
+%	\item Illustrate the importance of envire
+%	\item Demonstrate our system on two major NLP tasks with strong-performing
+%	models. We observe functional limitations of these models which can be helpful
+%	for future improvement on modeling.
+%\end{itemize}

### 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
update intro
add figure

@@
 
-Visualizing and understanding neural models in nlp
-Understanding Neural Networks through Representation Erasure
+Visualizing and understanding neural models in nlp \cite{LiChenHovy2015}
+Understanding Neural Networks through Representation Erasure \cite{li2016understanding}
 
-Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
-\textcolor{blue}{Lee visualizes the beam search and attention component in the NMT model.
-The work allows user involve into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.}
+AllenNLP demo
 
-End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights
-\textcolor{blue}{Instead of visualizing the attention matrix directly, the system shows the text context and highlights the critical phrase, which used to answers the questions, using color map.
-In this platform, user able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.}
+%Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
+Lee et al.
+visualizes the beam search and attention component in the NMT model~\cite{lee2017interactive}.
+The work allows user involve into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.
+%}
+
+%End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights
+%\textcolor{blue}{
+In the recent attention visualization work focus on question and answering model~\cite{ruckle2017end}, 
+instead of visualizing the attention matrix directly, the system shows the text context and highlights the critical phrase, which used to answers the questions, using color map.
+In this system, the user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.
+%}

### 2018-05-28 EMNLP-demo-paper/system.tex
update intro
add figure

@@
 We design the proposed system with modularity in mind
-\subsection{Input Perturbation}
+
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{attentionPanels}
+  \vspace{-6mm}
+ \caption{
+Attention visualization.
+In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
+The user can alter the attention values via the pop-up interface illustrated in (c).
+We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
+%
+For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
+}
+\label{fig:pipelineUpdate}
+\end{figure*}
+
+\subsection{Attention Views}
+Bipartie graph
+Attention matrix
+
+\subsection{Perturbation based exploration}
+\label{sec:perturb}
+
+\subsection{Prediction Summarization}

### 2018-05-28 NLIexampleVis.py

@@ -17,11 +17,15 @@ gen = translationPerturbation()
 dep = dependencyTree()
 
 #visualization components
-visLayout = {
-    "column":[{"row":["Summary", "Sentence", "Pipeline"]},
-            {"row":["AttentionGraph", "AttentionMatrix", "Prediction"]}]
-    }
+# visLayout = {
+#     "column":[{"row":["Summary", "Sentence", "Pipeline"]},
+#             {"row":["AttentionGraph", "AttentionMatrix", "Prediction"]}]
+#     }
 
+visLayout = {
+    "column":[{"row":["Sentence", "Prediction"]},
+            {"row":["AttentionGraph", "AttentionMatrix"]}]
+    }
 #setup interface
 modelVis = nlizeModule(visLayout)
 

### 2018-05-28 visPackage/static/components/attentionAsymmetricComponent.js

@@ -329,7 +329,7 @@ class attentionAsymmetricComponent extends attentionComponent {
             let width = this.width - 20;
             let height = 60;
             let posX = 10;
-            let posY = this.height * 0.3;
+            let posY = this.height * 0.35;
 
             let srcWidth = endPos[0] - startPos[0];
 

### 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
update related works

@@
 \section{Related Works}
+Due to increasing demand for interpretability to make sense of individual predictions and the model as a whole, many works has been proposed for understanding NLP models.
 
-Visualizing and understanding neural models in nlp \cite{LiChenHovy2015}
-Understanding Neural Networks through Representation Erasure \cite{li2016understanding}
-
-AllenNLP demo
-
+In the work by Li et al., the composability of the vector-based representation of text is investigate by utilizing techniques from vision community \cite{LiChenHovy2015}. 
+%
+In the representation erasure work~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of various parts of model by altering or removing the corresponding representations (i.e., dimension of hidden units, or input words).
 %Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
@@
 %}
-
 %End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights
 %\textcolor{blue}{
-In the recent attention visualization work focus on question and answering model~\cite{ruckle2017end}, 
-instead of visualizing the attention matrix directly, the system shows the text context and highlights the critical phrase, which used to answers the questions, using color map.
-In this system, the user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.
+In the recent attention visualization work on question and answering model~\cite{ruckle2017end}, 
+instead of visualizing the attention matrix directly, the system using color map to show the text context and highlights the critical phrase that used to answers the questions.
+The user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.
 %}
+Interactive demo system, such as AllenNLP web demo (\url{http://demo.allennlp.org/}), also attract attention as it provide an flexible environment that the user can experiment and explore the various input combination and carry out error analysis.

### 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
update related works

@@
 \section{Related Works}
-Due to increasing demand for interpretability to make sense of individual predictions and the model as a whole, many works has been proposed for understanding NLP models.
+Due to the increasing demand for model interpretability, many works has been proposed for understanding NLP models in term of making sense of individual predictions as well as the understanding model mechanism as a whole.
 
-In the work by Li et al., the composability of the vector-based representation of text is investigate by utilizing techniques from vision community \cite{LiChenHovy2015}. 
+In the work~\cite{LiChenHovy2015} by Li et al., the composability of the vector-based representation of text is investigate by utilizing instance based attribution techniques originated from the vision community (i.e., \cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017}).
 %
 In the representation erasure work~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of various parts of model by altering or removing the corresponding representations (i.e., dimension of hidden units, or input words).
+
+Beside interpret the model via carefully designed experiments, interactive systems, such as AllenNLP web demo (\url{http://demo.allennlp.org/}), also attract attention as it provide a flexible environment where the user can experiment and explore the various input combination and carry out error analysis.
+%
+As a result, interactive visual analytics system that incorporate novel visual encoding has been adopted in these interactive environment.
+%
+The training process of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and the properties of the LSTM are investigated in the LSTMvis visualization tool~\cite{StrobeltGehrmannPfister2018}.
 %Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
@@
 %}
-Interactive demo system, such as AllenNLP web demo (\url{http://demo.allennlp.org/}), also attract attention as it provide an flexible environment that the user can experiment and explore the various input combination and carry out error analysis.

### 2018-05-28 EMNLP-demo-paper/NLPVis-demo-paper.tex
add figure
full intro/related work pass

@@
 \usepackage{url}
+\usepackage{mathptmx}
 
@@
 Neural networks models have gained unprecedented popularity in natural language processing due to their state-of-the-art performance and the flexible end-to-end training scheme.
-Despite their advantages, the lack of interpretability hinders the further development and refinement of the model.
+Despite their advantages, the lack of interpretability hinders the deployment and refinement of the model.
 %These models often relying on the attention mechanism, which not only helps improve predicting performance but also provide interpretable representations for users to peak into the opaque models that are usually considered as black boxes.
 %
-In this work, we present a flexible visualization library for creating customized visual analytic environments, which enables the user to investigate and interrogate the relationship among the input, the model internals (i.e., attention), and the output predictions that in turn shed light on the model decision making processing.
+In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationship among the input, the model internals (i.e., attention), and the output predictions that in turn shed light on the model decision making processing.
 

### 2018-05-28 EMNLP-demo-paper/intro.tex
full intro/related work pass

@@
 %where end-to-end training become a primary option.
-and as the design of neural networks evolve, there is a clear trend of increasing model complexity both in term of architecture and parameters count. 
+and as the design of neural networks evolve, there is a clear trend of increasing model complexity both in term of the architecture and the parameters count. 
 %
-While the expressiveness of these models help improve the prediction performance, there is a fundamental lack of interpretability that lead many to consider neural network based models black boxes. 
+While the expressiveness of these models help improve the prediction performance, there is a fundamental lack of interpretability that lead many to consider neural network models black boxes. 
 %
-Despite the difficulties, it is imperative to devise techniques to interpret the model internals and reason about a given prediction, which are essential to understand limitation of the model and improve upon the existing designs.
+Despite the difficulties, interpreting the model internals and reason about predictions are essential for understanding limitation of the model and improve upon the existing designs.
 
@@
 However, many challenges remains.
-To begin with, for some NLP tasks, the word sequence pair among which the attentions are computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), where the standard visual encoding can not adequately handle.
+Firstly, for some NLP tasks, the word sequence pair among which the attentions are computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), where the standard visual encoding can not adequately handle.
 In addition, many previous works present the attention in a statics setting.
-Yet, the ability to provide an interactive environment, where the user can instantaneously look at how changes in the input will affect the attention, and how small changes in attention will affect the prediction is crucial for interpreting the model.
+Yet, the ability to provide an interactive environment, where the user can instantaneously look at how changes in the input will affect the attention, and how small changes in attention will affect the prediction are crucial for interpreting the model.
 Finally, many previous visualization efforts, despite reveal many interesting results, focus more on illustrating potentially useful visualization technique than provide a flexible software tool that can be easily integrated into existing code base.
-As a result, applying these proposed techniques to real word examples may involving substantial engineering effort than many user may not willing to undertake.
+As a result, applying these proposed techniques to real word examples may involving substantial engineering effort than many user may not affort to undertake.
 
-To address these challenges and facilitate interpretation of attention-based models, 
+To address these challenges in interpretating attention-based models, 
 we introduce a flexible python library that allow user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
@@
 For the MC task, we present your visualization methods on bidirectional attention flow model,
-which also represents a line of strong models \cite{Seo2016}.
+which also represents a line of state-of-the-art models \cite{Seo2016}.
 

### 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
full intro/related work pass

--- 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
@@
 \section{Related Works}
+Due to the increasing demand for model interpretability, many previous works has been proposed for understanding NLP models in term of making sense of individual predictions as well as model mechanism as a whole.
 
-Visualizing and understanding neural models in nlp \cite{LiChenHovy2015}
-Understanding Neural Networks through Representation Erasure \cite{li2016understanding}
+In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based representation of text is investigate by utilizing instance based attribution techniques originated from the vision community (i.e., \cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017}).
+%
+In the representation erasure work~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of various parts of the model by altering or removing the corresponding representations (i.e., the dimension count of hidden units, or input words).
 
-AllenNLP demo
-
+Beside interpreting the model via carefully designed experiments, interactive demo / visualization systems, such as AllenNLP demo (\url{http://demo.allennlp.org/}), also attract attention as it provide a flexible environment where the user can experiment and explore the various input combination and carry out error analysis.
+%
+Some of these interactive systems incorporate various visual encodings to summary the key information of the model.
+%
+The training dynamic of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and the hidden state properties of the LSTM are investigated in the LSTMvis visualization tool~\cite{StrobeltGehrmannPfister2018}.
 %Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
 Lee et al.
-visualizes the beam search and attention component in the NMT model~\cite{lee2017interactive}.
-The work allows user involve into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.
+visualizes the beam search and attention component in the NMT model.
+The work~\cite{lee2017interactive} directly involve the user into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.
 %}
-
-%End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights
-%\textcolor{blue}{
-In the recent attention visualization work focus on question and answering model~\cite{ruckle2017end}, 
-instead of visualizing the attention matrix directly, the system shows the text context and highlights the critical phrase, which used to answers the questions, using color map.
-In this system, the user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.
-%}
+In the recent attention visualization work on question and answering model~\cite{ruckle2017end}, 
+instead of visualizing the attention matrix directly, the system using color map to show the text context and highlights the critical phrase that used to answers the questions.
+%The user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.
+%

### 2018-05-28 EMNLP-demo-paper/system.tex
add figures
add code

@@
 \section{System}
-We design the proposed system with modularity in mind
+We design the visualization system with modularity and easy of use in mind.
+%The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
+As a result, we designing the system as a Python library rather than as a monolithic standalone application. 
+Just like a plotting library (i.e., matplotlib), the different pieces of the visualization (i.e., matrix based attention encoding) can be accessed individually, which helps ease the initial learning curve.
+The individual components can also be combined in any configuration desired by users via a simple API to better fit into one's workflow.
+More importantly, the library-based design allows easy integration with the existing model implemented in Python.
+%
+To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models.
+
+\begin{lstlisting}[language=Python, caption=Code for setting up the visualization system shown in the paper.]
+from visPackage import MCModule
+from bidaf_src import bidafModelInterface
+from NLPutility import translationPerturbation
+
+#initialize machine comprehension model
+model = bidafModelInterface(
+    wordDict="data/bidaf/squad.word.dict",
+    wordVec="data/bidaf/glove.hdf5",
+    model="data/bidaf/bidaf.ema")
+
+gen = translationPerturbation()
+
+# visualization components
+visLayout = {
+  "column":[{"row": ["Paragraph", "AttentionSubMatrix"]},
+            {"row": ["AttentionAsymmetric"]}]
+  }
+
+#setup interface
+modelVis = MCModule(visLayout)
+
+modelVis.setPredictionHook(model.predict)
+modelVis.setAttentionHook(model.attention)
+modelVis.setReloadModelCallback(model.reloadModel)
+modelVis.setSentenceHook(gen.perturbSentence)
+
+#open browser for visualization
+modelVis.startServer()
+\end{lstlisting}
 
@@
 }
-\label{fig:pipelineUpdate}
+\label{fig:attention}
 \end{figure*}
@@
 \subsection{Attention Views}
-Bipartie graph
+As illustrated in Figure~\ref{fig:attention}(a)(b), the most widely adopted technique to bipartie graph
+
 Attention matrix

### 2018-05-28 MCexampleVis.py

@@ -1,32 +1,21 @@
 from visPackage import MCModule
-# from nli_src import modelInterface
 from bidaf_src import bidafModelInterface
 from NLPutility import translationPerturbation
 
-#initialize NLP model
+#initialize machine comprehension model
 model = bidafModelInterface(
     wordDict="data/bidaf/squad.word.dict",
-    wordVec="data/bidaf/glove.hdf5", model="data/bidaf/bidaf_clip5_20.ema")
-# print model
+    wordVec="data/bidaf/glove.hdf5",
+    model="data/bidaf/bidaf_clip5_20.ema")
 
-# exit()
-# model = modelInterface(
-#     wordDict="data/snli_1.0/snli_1.0.word.dict",
-#     wordVec="data/glove.hdf5", model="data/local_300_parikh")
-
-#sentence perturbation
-# gen = sentenceGenerator()
 gen = translationPerturbation()
 
 # visualization components
 # attention is linked to paragraph
 visLayout = {
-    "column":[{"row":
-                [
-                "Paragraph",
-                "AttentionSubMatrix"
-                ]},
-            {"row":["AttentionAsymmetric"]}]
+    "column":[{"row": ["Paragraph",
+                        "AttentionSubMatrix"]},
+            {"row": ["AttentionAsymmetric"]}]
     }
 
 #setup interface
@@ -38,5 +27,4 @@ modelVis.setReloadModelCallback(model.reloadModel)
 modelVis.setSentencePerturbationHook(gen.perturbSentence)
 
 #open browser for visualization
-# modelVis.show()
 modelVis.startServer()

### 2018-05-28 EMNLP-demo-paper/system.tex
add back old perturbation

@@
 \section{System}
-We design the visualization system with modularity and easy of use in mind.
-%The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
-As a result, we designing the system as a Python library rather than as a monolithic standalone application. 
-Just like a plotting library (i.e., matplotlib), the different pieces of the visualization (i.e., matrix based attention encoding) can be accessed individually, which helps ease the initial learning curve.
-The individual components can also be combined in any configuration desired by users via a simple API to better fit into one's workflow.
+
+\subsection{Perturbation-Driven Exploration}
+\label{sec:perturb}
+
+\subsection{Attention Visualization}
+As illustrated in Figure~\ref{fig:attention}(a)(b), the most widely adopted technique to bipartie graph
+
+Attention matrix
+
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{attentionPanels}
+  \vspace{-6mm}
+ \caption{
+Attention visualization.
+In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
+The user can alter the attention values via the pop-up interface illustrated in (c).
+We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
+%
+For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
+}
+\label{fig:attention}
+\end{figure*}
+
+\subsection{Prediction Summarization}
+
+\subsection{Implementation}
+The initial setup cost and learning curve of the tool are often the barriers for user adaptation.
+To address these challenge, we design the visualization system as a Python library with modularity and easy accessibility in mind.
+Instead of using the visualization system as a monolithic standalone application, just like a plotting library (i.e., matplotlib), the different pieces of the visualization (i.e., matrix based attention encoding) can be accessed individually.
+% 
+Yet, the components can also be combined in any configuration desired by users via a simple API to better fit into one's workflow.
 More importantly, the library-based design allows easy integration with the existing model implemented in Python.
@@
 To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models.
+The the code required to create an interactive exploration environment for machine comprehension model is illustrated bellow.
 
@@
 
-#open browser for visualization
-modelVis.startServer()
+#open browser for the web-based interactive visualization
+modelVis.show()
 \end{lstlisting}
-
-\begin{figure*}[t]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{attentionPanels}
-  \vspace{-6mm}
- \caption{
-Attention visualization.
-In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
-The user can alter the attention values via the pop-up interface illustrated in (c).
-We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
-%
-For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
-}
-\label{fig:attention}
-\end{figure*}
-
-\subsection{Attention Views}
-As illustrated in Figure~\ref{fig:attention}(a)(b), the most widely adopted technique to bipartie graph
-
-Attention matrix
-
-\subsection{Perturbation based exploration}
-\label{sec:perturb}
-
-\subsection{Prediction Summarization}

### 2018-05-28 NLIexampleVis.py

@@ -1,7 +1,8 @@
 ## FIXME fix the import ###
 from visPackage.nlizeModule import nlizeModule
 from nli_src import modelInterface
-from NLPutility import translationPerturbation
+# from NLPutility import translationPerturbation
+from NLPutility import sentenceGenerator
 from NLPutility import dependencyTree
 
 #initialize NLP model
@@ -10,7 +11,9 @@ model = modelInterface(
     wordVec="data/glove.hdf5", model="data/local_300_parikh")
 
 #sentence perturbation
-gen = translationPerturbation()
+# gen = translationPerturbation()
+gen = sentenceGenerator()
+
 #dependency parsing
 dep = dependencyTree()
 

### 2018-05-28 NLPutility/sentenceGenerator.py

@@ -5,7 +5,7 @@ from pattern.en import pluralize, singularize
 import copy
 
 class sentenceGenerator:
-    def __init__(self, train_dict='../data/snli_1.0/snli_1.0.word.dict'):
+    def __init__(self, train_dict='data/snli_1.0/snli_1.0.word.dict'):
         self.train_tokens = {}
         with open(train_dict, 'r+') as f:
             lines = f.readlines()

### 2018-05-28 EMNLP-demo-paper/result.tex
add figure
added model description, very brief

@@
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{NLI_MC_interface}
+  \vspace{-6mm}
+ \caption{
+Illustration of different configurations for the natural language inference and machine comprehension tasks.
+}
+\label{fig:pipelineUpdate}
+\end{figure*}
+
 \section{Application Results}
+
 \subsection{Natural Language Inference}
+We demonstrate our visualization system on the decomposable attention networks
+for NLI task. The goal is that, given a premise sentence and a hypothesis sentence,
+predict their relation as one of \emph{Entailment, Contradiction, Neutral}.
+The model can be formalized as the following:
+\begin{align}
+	P^\prime, H^\prime &= f(P), f(H)\\
+	\overleftarrow{A} &= P^\prime \cdot H^\prime\\
+	\overrightarrow{A} &= H^\prime \cdot P^\prime\\
+	y &= g(P, H, P^\prime, H^\prime, \overleftarrow{A}, \overrightarrow{A})
+\end{align}
+where $P$ and $H$ are input embedding matrices for the premise and the hypothesis, $\overleftarrow{A}$
+and $\overrightarrow{A}$ are attentions, and $y$ is the predicted probabilities for candidate classes.
+Our system visualized the bidirectional attentions and their interaction with output distribution over labels.
 
 \subsection{Machine Comprehension}
+In machine comprehension task, two sequences of texts are given: context and question.
+The target is to select a span of text from the context that answers the question. We provide a simple model
+formulation and refer the reader to the paper for details.
+\begin{align}
+	C^\prime, Q^\prime &= BiLSTM(C), BiLSTM(Q)\\
+	\overleftarrow{A} &= u(C^\prime, Q^\prime)\\
+	\overrightarrow{A} & v(C^\prime, Q^\prime)\\
+	s &= m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})\\
+	e &= n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})
+\end{align}
+where $C$ and $Q$ are embedding matrices for the context and the question,
+$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
+$s$ and $e$ are probabilities for starting and ending indices of the answer span.
+Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
+$s$ and $e$.

### 2018-05-29 EMNLP-demo-paper/intro.tex
add perturbation discussion

@@
 Finally, many previous visualization efforts, despite reveal many interesting results, focus more on illustrating potentially useful visualization technique than provide a flexible software tool that can be easily integrated into existing code base.
-As a result, applying these proposed techniques to real word examples may involving substantial engineering effort than many user may not affort to undertake.
+As a result, applying these proposed techniques to real word examples may involving substantial engineering effort than many user may not afford to undertake.
 
-To address these challenges in interpretating attention-based models, 
+To address these challenges in interpreting attention-based models, 
 we introduce a flexible python library that allow user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
@@
 
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipeline}
- \caption{
- Perturbation-driven exploration of the end-to-end models that follows the encoder, attention, and classifier structure. The user can generate small perturbation of the input (i.e., paraphrasing)
- }
-\label{fig:modelPipeline}
-\end{figure}
-
 %In summary, our key contributions are:

### 2018-05-29 EMNLP-demo-paper/relatedWorks.tex
add perturbation discussion

@@
 
-In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based representation of text is investigate by utilizing instance based attribution techniques originated from the vision community (i.e., \cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017}).
+In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based representation of text is investigated by utilizing instance-based attribution techniques originated from the vision community (i.e., \cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017}).
 %

### 2018-05-29 EMNLP-demo-paper/system.tex
add perturbation discussion

@@
-\section{System}
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{pipeline}
+ \caption{
+ Perturbation-driven exploration of the end-to-end models that follows the encoder, attention, and classifier structure.
+The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing)
+ }
+\label{fig:modelPipeline}
+\end{figure}
 
-\subsection{Perturbation-Driven Exploration}
+\section{Visualization System}
+As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encode, attent, and classify structure, in which the attention stage provide a window for peeking into the model decision making process.
+However, the static attention alone likely does not tell the whole story, instead we can learn more about the model by examining the dynamic between the input, the attention, and the output.
+To explore the relationship between different components of the pipeline, the proposed system utilizes a perturbation-driven exploration strategy, where the  user can manually or automatically generate small changes in the input sentence and then view the aggregated prediction information.
+Beside the perturbation of the input, the system also allows interactive modification of the attention values, where the prediction will instantaneously updated to reflect the changes.
+%
+
+\subsection{Input Sentences Perturbation}
 \label{sec:perturb}
+Due to the discrete nature of the natural language, applying perturbation to sentence for sensitivity analysis can be particularly challenging compared to other problem domain, as small changes in words can leading to drastic different in the semantics of the sentences.
+To reduce the potential semantic deviation, we first devise a simple perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the wordNet~\cite{Miller1995}.
+However, the limitation is apparent, as synonyms replacement does not guarantee the meaning of the sentence remain the same.
+And the wordNet also has a rather inclusive definition for synonyms, where many infrequent/obscure usages exists, which leads to less meaningful perturbed sentence.
+However, this method requires minimal computation and easy to code and understand.
 
-\subsection{Attention Visualization}
-As illustrated in Figure~\ref{fig:attention}(a)(b), the most widely adopted technique to bipartie graph
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{sentence}
+ \caption{
+The interface for showing input sentences.
+The user can manually alter the words or apply automatic perturbation/paraphrasing of the inputs.
+In the \emph{perturbed} dropdown menu, the blue words are the only not exist in the original sentence.
+ }
+\label{fig:sentence}
+\end{figure}
 
-Attention matrix
+To improve the perturbation quality, we also adopted a translation based paraphrasing technique that is similar to the method discussed in \cite{mallinson2017paraphrasing}.
+Here, we translate the original English sentence into several other languages are then translate back into the English.
+Provided the translation produce correct result, we essential obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows the paraphrased/perturbed sentence).
 
@@
 }
-\label{fig:attention}
+\label{fig:attentionVis}
 \end{figure*}
+
+\subsection{Attention Visualization}
+The system consistence several visualization components that can be combine to generate an functional interactive system. Here we will focus on the attention visualization components. 
+As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted technique to bipartie graph (a), as well as the heatmap attention matrix representation (b). 
+%
+In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
+%%%%%%%%
+The graph view is suitable for highlighting the most dominant alignments.
+However, the edges may become cluttered if multiple attention values are high.
+The matrix attention view (Fig.~\ref{fig:attentionVis}(b)) resolve these issues, despite being more verbose and less efficient in highlighting the dominant alignments.
+%Together, the graph and matrix views complement each other and provide the same information from different perspectives.
+As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.
+To help the user recognize the correspondence during the exploration, we enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), the attention of the two ``couple'' is highlighted).
+%
+To address the challenge of visualizing long sentence, we incorporated the grammar structure.
+One augmentation
+
+However, when the one of the text sequence become signification
 
@@
 visLayout = {
-  "column":[{"row": ["Paragraph", "AttentionSubMatrix"]},
+  "column":[{"row": ["Paragraph", 
+                     "AttentionSubMatrix"]},
             {"row": ["AttentionAsymmetric"]}]
@@
 modelVis.setAttentionHook(model.attention)
-modelVis.setReloadModelCallback(model.reloadModel)
 modelVis.setSentenceHook(gen.perturbSentence)
 
-#open browser for the web-based interactive visualization
+#open browser for the web-based visualization
 modelVis.show()

### 2018-05-29 EMNLP-demo-paper/system.tex
add prediction section

@@
 \vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{sentence}
+ \includegraphics[width=0.9\linewidth]{sentence}
  \caption{
@@
 Provided the translation produce correct result, we essential obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows the paraphrased/perturbed sentence).
-
-\begin{figure*}[t]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{attentionPanels}
-  \vspace{-6mm}
- \caption{
-Attention visualization.
-In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
-The user can alter the attention values via the pop-up interface illustrated in (c).
-We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
-%
-For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
-}
-\label{fig:attentionVis}
-\end{figure*}
 
@@
 
-\subsection{Prediction Summarization}
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=0.8\linewidth]{prediction}
+ \caption{
+Summarize the prediction results of the perturbed input for the natural language inference model.
+the prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label, namely, \emph{entail}, \emph{contradict}, and \emph{neutral}.
+ %
+ }
+\label{fig:prediction}
+\end{figure}
+
+\subsection{Prediction Visualization}
+
+The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
+
+A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=0.9\linewidth]{attentionPanels}
+  \vspace{-3mm}
+ \caption{
+Attention visualization.
+In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
+The user can alter the attention values via the pop-up interface illustrated in (c).
+We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
+%
+For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
+}
+\label{fig:attentionVis}
+\end{figure*}
 

### 2018-05-29 EMNLP-demo-paper/result.tex
added model description, very brief
add prediction section
update structure

@@
 
-\section{Application Results}
+\section{Application}
+We demonstrate our visualization system on the decomposable attention networks
+for natural language inference task, and the bi-directional attention flow for the machine comprehension task.
 
 \subsection{Natural Language Inference}
-We demonstrate our visualization system on the decomposable attention networks
-for NLI task. The goal is that, given a premise sentence and a hypothesis sentence,
+Given a premise sentence and a hypothesis sentence,
 predict their relation as one of \emph{Entailment, Contradiction, Neutral}.
@@
 	\overleftarrow{A} &= u(C^\prime, Q^\prime)\\
-	\overrightarrow{A} & v(C^\prime, Q^\prime)\\
+	\overrightarrow{A} &= v(C^\prime, Q^\prime)\\
 	s &= m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})\\

### 2018-05-29 EMNLP-demo-paper/system.tex
update structure

@@
 
-\subsection{Attention Visualization}
-The system consistence several visualization components that can be combine to generate an functional interactive system. Here we will focus on the attention visualization components. 
-As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted technique to bipartie graph (a), as well as the heatmap attention matrix representation (b). 
-%
-In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
-%%%%%%%%
-The graph view is suitable for highlighting the most dominant alignments.
-However, the edges may become cluttered if multiple attention values are high.
-The matrix attention view (Fig.~\ref{fig:attentionVis}(b)) resolve these issues, despite being more verbose and less efficient in highlighting the dominant alignments.
-%Together, the graph and matrix views complement each other and provide the same information from different perspectives.
-As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.
-To help the user recognize the correspondence during the exploration, we enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), the attention of the two ``couple'' is highlighted).
-%
-To address the challenge of visualizing long sentence, we incorporated the grammar structure.
-One augmentation
-
-However, when the one of the text sequence become signification
-
 \begin{figure}[htbp]
@@
 
+\subsection{Attention Visualization}
+The system consistence several visualization components that can be combine to generate an functional interactive system. Here we will focus on the attention visualization components. 
+As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted technique to bipartie graph (a), as well as the heatmap attention matrix representation (b). 
+%
+In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
+%%%%%%%%
+The graph view is suitable for highlighting the most dominant alignments.
+However, the edges may become cluttered if multiple attention values are high.
+The matrix attention view (Fig.~\ref{fig:attentionVis}(b)) resolve these issues, despite being more verbose and less efficient in highlighting the dominant alignments.
+%Together, the graph and matrix views complement each other and provide the same information from different perspectives.
+As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.
+To help the user recognize the correspondence during the exploration, we enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), the attention of the two ``couple'' is highlighted).
+%
+To address the challenge of visualizing long sentence, we incorporated the grammar structure.
+One augmentation
+
+However, when the one of the text sequence become signification
+
 \subsection{Implementation}
@@
     model="data/bidaf/bidaf.ema")
-
 gen = translationPerturbation()
-
-# visualization components
+#visualization components
 visLayout = {
@@
   }
-
 #setup interface
 modelVis = MCModule(visLayout)
-
 modelVis.setPredictionHook(model.predict)
@@
 modelVis.setSentenceHook(gen.perturbSentence)
-
 #open browser for the web-based visualization

### 2018-05-29 EMNLP-demo-paper/system.tex
add result figure

@@
  \caption{
- Perturbation-driven exploration of the end-to-end models that follows the encoder, attention, and classifier structure.
+ Perturbation-driven interrogation of the end-to-end models that follows the encoder, attention, and classifier structure.
 The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing)
@@
 \section{Visualization System}
-As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encode, attent, and classify structure, in which the attention stage provide a window for peeking into the model decision making process.
+As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provide a window for peeking into the model decision making process.
 However, the static attention alone likely does not tell the whole story, instead we can learn more about the model by examining the dynamic between the input, the attention, and the output.
-To explore the relationship between different components of the pipeline, the proposed system utilizes a perturbation-driven exploration strategy, where the  user can manually or automatically generate small changes in the input sentence and then view the aggregated prediction information.
+To allow the user to interrogate the relationship between different components of the pipeline, the proposed system utilizes a perturbation-driven exploration strategy, where the user can manually or automatically perturb the input sentence and then view the aggregated prediction information.
 Beside the perturbation of the input, the system also allows interactive modification of the attention values, where the prediction will instantaneously updated to reflect the changes.
@@
 \label{sec:perturb}
-Due to the discrete nature of the natural language, applying perturbation to sentence for sensitivity analysis can be particularly challenging compared to other problem domain, as small changes in words can leading to drastic different in the semantics of the sentences.
-To reduce the potential semantic deviation, we first devise a simple perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the wordNet~\cite{Miller1995}.
+Due to the discrete nature of the natural language, automatically applying perturbation to sentence for sensitivity analysis can be particularly challenging (compared to other domain, i.e., image), as small changes in words can leading to drastic differences in the semantics of the sentences.
+To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the wordNet~\cite{Miller1995}.
 However, the limitation is apparent, as synonyms replacement does not guarantee the meaning of the sentence remain the same.
-And the wordNet also has a rather inclusive definition for synonyms, where many infrequent/obscure usages exists, which leads to less meaningful perturbed sentence.
-However, this method requires minimal computation and easy to code and understand.
+And the wordNet often produces infrequent/obscure usages that may leads to less meaningful perturbed sentences.
+However, this method requires minimal computation and is easy to implement.
 
@@
 The user can manually alter the words or apply automatic perturbation/paraphrasing of the inputs.
-In the \emph{perturbed} dropdown menu, the blue words are the only not exist in the original sentence.
+In the ``perturbed'' dropdown menu, the blue words are the only not exist in the original sentence.
  }
@@
 
-To improve the perturbation quality, we also adopted a translation based paraphrasing technique that is similar to the method discussed in \cite{mallinson2017paraphrasing}.
-Here, we translate the original English sentence into several other languages are then translate back into the English.
-Provided the translation produce correct result, we essential obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows the paraphrased/perturbed sentence).
+To improve the perturbation quality, we also adopted a translation based paraphrasing technique that is similar to the one discussed in \cite{mallinson2017paraphrasing}.
+Here, we translate the original English sentence into several other languages and then translate back into English.
+Provided the translation produce correct result (in our case, we utilized the google cloud translation platform), we essential obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows the paraphrased/perturbed sentence).
 
@@
 the prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label, namely, \emph{entail}, \emph{contradict}, and \emph{neutral}.
- %
 }

### 2018-05-29 EMNLP-demo-paper/result.tex
add result figure
add figure for result

@@
+%\begin{figure*}[t]
+%\centering
+%\vspace{-2mm}
+% \includegraphics[width=1.0\linewidth]{NLI_MC_interface}
+%  \vspace{-6mm}
+% \caption{
+%Illustration of different configurations for the natural language inference and machine comprehension tasks.
+%}
+%\label{fig:pipelineUpdate}
+%\end{figure*}
+
 \begin{figure*}[t]
@@
 \vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{NLI_MC_interface}
+ \includegraphics[width=1.0\linewidth]{NLIexample}
   \vspace{-6mm}
  \caption{
-Illustration of different configurations for the natural language inference and machine comprehension tasks.
+An illustrate of the attention editing process. 
+The model originally predict, as shown by dependency tree help the user better understanding the attention. 
 }
-\label{fig:pipelineUpdate}
+\label{fig:NLIexample}
 \end{figure*}
@@
 
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{MC_interface}
+  \vspace{-6mm}
+ \caption{
+An illustrate of an attention exploration session with the machine comprehension model.
+}
+\label{fig:MCexample}
+\end{figure*}
+
 \subsection{Machine Comprehension}
@@
 $s$ and $e$.
+
+As illustrated in Figure~\ref{fig:MCexample},

### 2018-05-29 EMNLP-demo-paper/system.tex
add figure for result

@@
 %
+The system consistence several visualization components that can be combined to generate an functional interactive system. In the following section, we will cover some of the key components.
 
@@
 Summarize the prediction results of the perturbed input for the natural language inference model.
-the prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label, namely, \emph{entail}, \emph{contradict}, and \emph{neutral}.
+the prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label.
 }
@@
 \subsection{Prediction Visualization}
+Efficient visual encoding for prediction is crucial for communicating the model behavior.
+And to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
 
-The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
-
+For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities is encoded in the triangle, where the three vertices represents the three possible prediction (namely, \emph{entail}, \emph{contradict}, and \emph{neutral}).
+The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs are represented by smaller grey circles.
 A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
@@
 \subsection{Attention Visualization}
-The system consistence several visualization components that can be combine to generate an functional interactive system. Here we will focus on the attention visualization components. 
 As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted technique to bipartie graph (a), as well as the heatmap attention matrix representation (b). 

### 2018-05-29 EMNLP-demo-paper/result.tex
done with system

@@
 \subsection{Natural Language Inference}
+\label{sec:NLIexample}
 Given a premise sentence and a hypothesis sentence,
@@
 \subsection{Machine Comprehension}
+\label{sec:MCexample}
 In machine comprehension task, two sequences of texts are given: context and question.

### 2018-05-29 EMNLP-demo-paper/system.tex
done with system

@@
 And to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
-
+%
 For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities is encoded in the triangle, where the three vertices represents the three possible prediction (namely, \emph{entail}, \emph{contradict}, and \emph{neutral}).
@@
 The matrix attention view (Fig.~\ref{fig:attentionVis}(b)) resolve these issues, despite being more verbose and less efficient in highlighting the dominant alignments.
-%Together, the graph and matrix views complement each other and provide the same information from different perspectives.
-As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.
-To help the user recognize the correspondence during the exploration, we enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), the attention of the two ``couple'' is highlighted).
+We also enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), one the most dominant attention is highlighted in orange).
 %
-To address the challenge of visualizing long sentence, we incorporated the grammar structure.
-One augmentation
+To facilitate the perturbation of attention (see Figure~\ref{fig:pipeline}), as illustrated in Figure~\ref{fig:attentionVis}(c), we implement an interface in the matrix view for user to directly manipulate the attention value.
 
-However, when the one of the text sequence become signification
+To address the challenge of visualizing long sentence, we augmented the standard visual encoding with grammar structure, and allow dynamic simplification of the sentence based on the dependency tree (see Figure~\ref{fig:attentionVis}(a1)).
+We also show how the dependency information can potentially improve the prediction result in Section~\ref{sec:NLIexample}
+
+However, when the one of the text sequence become signification longer, i.e., a full paragraph as in the machine comprehension task, the even the simplified sentence can not be meaningfully represented in the graph or matrix visual encoding.
+To address this visualization challenge, as illustrated in Figure~\ref{fig:attentionVis}(d), we introduce the hierarchical representation.
+Here, a pure graphical encoding (the color bars marked by \emph{att2}) is used to capture the aggregated alignment information of the whole paragraph, and the user can focus on localized attention information by selecting the a pixel bar that presents a single sentence.
+We can also link this attention representation with matrix, such that whenever a sentence is selected the local attention relationship is allow shown in the matrix view (see Figure~\ref{MCexample}(a)).
 
@@
 
-\begin{lstlisting}[language=Python, caption=Code for setting up the visualization system shown in the paper.]
+\begin{lstlisting}[language=Python, caption=Code for setting up the visualization system shown in Figure~\ref{fig:MCexample}(a).]
 from visPackage import MCModule

### 2018-05-29 EMNLP-demo-paper/NLPVis-demo-paper.tex
add code
added model description, very brief
add perturbation discussion
done with system
add author list

@@
 \usepackage{mathptmx} 
+\usepackage{amsmath}
 
-%\aclfinalcopy % Uncomment this line for the final submission
+\aclfinalcopy % Uncomment this line for the final submission
 
@@
 \graphicspath{{figures/}{pictures/}{figs/}{./}} % where to search for the images
+\usepackage{xcolor}  % Coloured text etc.
+\usepackage{listings}
+%\usepackage{authblk}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+\lstdefinestyle{mystyle}{
+    %backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\scriptsize\ttfamily\bfseries,
+    %basicstyle=\footnotesize\ttfamily,
+    breakatwhitespace=false,         
+    %breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    %numbers=left,                    
+    %numbersep=1pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=1
+}
+
+\lstset{style=mystyle}
 
@@
 \newcommand\confname{EMNLP 2018}
-%\newcommand\conforg{SIGDAT}
 
@@
 
-\author{Shusen Liu \\
-  Lawrence Livermore National Laboratory\\
-  {\tt liu42@llnl.gov} \\\And
-  Tao Li,  Zhimin Li,  Vivek Srikumar, Valerio Pascucci \\
-  School of Computing, University of Utah\\
-    {\tt {tao.li, zhimin.li, vivek, pacucci}@utah.edu}
+\author{Shusen Liu$^{1}$, Tao Li$^{2}$,  Zhimin Li$^{3}$,  Vivek Srikumar$^{2}$, Valerio Pascucci$^{3}$, Peer-Timo Bremer$^{1}$ \\
+ % {\tt liu42@llnl.gov} \\\And
+  Lawrence Livermore National Laboratory$^{1}$\\
+  School of Computing, University of Utah$^{2}$\\  
+  SCI Institute, University of Utah$^{3}$\\
+   % {\tt {tao.li, zhimin.li, vivek, pacucci}@utah.edu}
 }
 
-\date{}
-
+%\date{}
 \begin{document}
 \maketitle
+
+%\vspace{-4mm}
 

### 2018-05-29 EMNLP-demo-paper/system.tex
add author list

@@
  }
+ \vspace{-3mm}
 \label{fig:sentence}
@@
 }
+\vspace{-3mm}
 \label{fig:prediction}
@@
 }
+\vspace{-3mm}
 \label{fig:attentionVis}
@@
 %
-To facilitate the perturbation of attention (see Figure~\ref{fig:pipeline}), as illustrated in Figure~\ref{fig:attentionVis}(c), we implement an interface in the matrix view for user to directly manipulate the attention value.
+To facilitate the perturbation of attention (see Figure~\ref{fig:modelPipeline}), as illustrated in Figure~\ref{fig:attentionVis}(c), we implement an interface in the matrix view for user to directly manipulate the attention value.
 
@@
 Here, a pure graphical encoding (the color bars marked by \emph{att2}) is used to capture the aggregated alignment information of the whole paragraph, and the user can focus on localized attention information by selecting the a pixel bar that presents a single sentence.
-We can also link this attention representation with matrix, such that whenever a sentence is selected the local attention relationship is allow shown in the matrix view (see Figure~\ref{MCexample}(a)).
+We can also link this attention representation with matrix, such that whenever a sentence is selected the local attention relationship is allow shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).
 

### 2018-05-29 EMNLP-demo-paper/conclusion.tex
full paper draft

\section{Discussion}
In this work, we introduce a visualization library for creating customized environments that allow the user to interrogate the relationship between different parts of the model pipeline via interactive queries.
%
We demonstrate the usability and flexibility of tool by configuring the visual components to investigate models for solving different NLP tasks (e.g., NLI, MC).
%
Due to the limited space, we didn't demonstrate all the available components, such as a visual summary of predict results of the entire development set, as well as a scheme to update the model based on user assigned prediction. 
%
We also conducted a small-scale user study, in which we ask several Ph.D. level student with NLP background to spend 30 minutes with the tool and provide feedback. The positive feedbacks mentioned the environment allow them to iteratively refine their queries and identify potential issues with the model, but some student also suggests the tool may not provide enough guidance for user do not have an in-depth understanding of the model.

We design the individual components with versatility in mind. Due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available models.
%
In the future, we plan to expand the visualization component further to handle tasks such neural machine translation and more.

### 2018-05-29 EMNLP-demo-paper/result.tex
full paper draft

@@
 %\end{figure*}
+\section{Applications}
+We demonstrate the proposed visualization system on the decomposable attention network~\cite{parikh2016emnlp}
+for the NLI task and the bi-directional attention flow network~\cite{Seo2016} for the MC task.
 
@@
 An illustrate of the attention editing process. 
-The model originally predict, as shown by dependency tree help the user better understanding the attention. 
+By removing the alignment mistake between the two "green", the originally wrong prediction \emph{entailment} is corrected to \emph{netural}.
 }
@@
 
-\section{Application}
-We demonstrate our visualization system on the decomposable attention networks
-for natural language inference task, and the bi-directional attention flow for the machine comprehension task.
-
 \subsection{Natural Language Inference}
 \label{sec:NLIexample}
-Given a premise sentence and a hypothesis sentence,
-predict their relation as one of \emph{Entailment, Contradiction, Neutral}.
-The model can be formalized as the following:
-\begin{align}
-	P^\prime, H^\prime &= f(P), f(H)\\
-	\overleftarrow{A} &= P^\prime \cdot H^\prime\\
-	\overrightarrow{A} &= H^\prime \cdot P^\prime\\
-	y &= g(P, H, P^\prime, H^\prime, \overleftarrow{A}, \overrightarrow{A})
-\end{align}
-where $P$ and $H$ are input embedding matrices for the premise and the hypothesis, $\overleftarrow{A}$
-and $\overrightarrow{A}$ are attentions, and $y$ is the predicted probabilities for candidate classes.
-Our system visualized the bidirectional attentions and their interaction with output distribution over labels.
+The NLI task predict the relationship between a premise sentence (\textbf{P}) and a hypothesis sentence (\textbf{H}).
+%as either \emph{entailment}, \emph{contradiction}, or \emph{neutral}.
+%The model can be formalized as the following:
+%%\begin{align}
+%	$P^\prime, H^\prime = f(P), f(H)$,
+%	$\overleftarrow{A} = P^\prime \cdot H^\prime$,
+%	$\overrightarrow{A} = H^\prime \cdot P^\prime$,
+%	$y = g(P, H, P^\prime, H^\prime, \overleftarrow{A}, \overrightarrow{A})$,
+%%\end{align}
+%where $P$ and $H$ are input embedding matrices for the premise and the hypothesis, $\overleftarrow{A}$
+%and $\overrightarrow{A}$ are attentions, and $y$ is the predicted probabilities for candidate classes.
+%Our system visualized the bidirectional attentions and their interaction with output distribution over labels.
+The model produces two attention matrices, representing alignment from premise to hypothesis, and from hypothesis to premise.
+
+Here we show an example, in which the wrong prediction can be fixed by correcting the attention value.  
+%In the proposed system, we overlay the sentence dependency tree with the attention, which enables researchers to conduct comparisons between attention and grammar structure.
+%
+As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be entailment, which is incorrect.
+By examining the attention, we can see the word \textbf{green} in ``\textbf{green} jacket" is aligned to the \textbf{green} in ``\textbf{green} tea", yet these two ``green'' decorate different nouns.
+Such a relationship can be confirmed by examining the dependency tree, where  \textbf{green} in \textbf{P} is attached to ``jacket'', whereas \textbf{green} in \textbf{H} is attached to ``tea''.
+However, the model does not aware of these the grammar information.
+As a result, the model mistakenly believes the two \textbf{greens} are used to describe the same thing (thus predict \emph{entailment}).
+%
+To correct the mistake, we edit the attention value and remove the align between these two "green" (see Figure~\ref{fig:NLIexample}(b)).
+As expected, the prediction label is corrected (\emph{neutral}) (see in Figure~\ref{fig:NLIexample}(c)).
 
@@
  \caption{
-An illustrate of an attention exploration session with the machine comprehension model.
+The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
+The $p1$, $p2$ color bar illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
+The answer to the question is found in (a1), where the ``Two'' is aligned with the ``many'' in the question. However, the number 9 is also aligned with many, which may potentially lead to confusions.
+The second best answer is illustrated in b2.
 }
@@
 \label{sec:MCexample}
-In machine comprehension task, two sequences of texts are given: context and question.
-The target is to select a span of text from the context that answers the question. We provide a simple model
-formulation and refer the reader to the paper for details.
-\begin{align}
-	C^\prime, Q^\prime &= BiLSTM(C), BiLSTM(Q)\\
-	\overleftarrow{A} &= u(C^\prime, Q^\prime)\\
-	\overrightarrow{A} &= v(C^\prime, Q^\prime)\\
-	s &= m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})\\
-	e &= n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})
-\end{align}
-where $C$ and $Q$ are embedding matrices for the context and the question,
-$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
-$s$ and $e$ are probabilities for starting and ending indices of the answer span.
-Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
-$s$ and $e$.
+In machine comprehension task, two sequences of texts are given: context/paragraph and question.
+The goal is to select a span of text from the context that answers the question. 
+%We provide a simple model formulation and refer the reader to the paper for details.
+%%\begin{align}
+%	$C^\prime, Q^\prime = BiLSTM(C), BiLSTM(Q)$,
+%	$\overleftarrow{A} = u(C^\prime, Q^\prime)$,
+%	$\overrightarrow{A} = v(C^\prime, Q^\prime)$,
+%	$s = m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
+%	$e = n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
+%%\end{align}
+%where $C$ and $Q$ are embedding matrices for the context and the question,
+%$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
+%$s$ and $e$ are probabilities for starting and ending indices of the answer span.
+%Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
+%$s$ and $e$.
+Similarly, the attention information is also encoded as a bi-directional alignment (i.e., from context to question and vice versa). 
+The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
+Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2}.
 
-As illustrated in Figure~\ref{fig:MCexample},
+As illustrated in Figure~\ref{fig:MCexample}, we show \emph{att2} in the overview attention colored bars (yellow-green-blue colormap), in which each rectangular corresponds to one sentence.
+We can then focus on individual sentences by click on the rectangular (see Figure~\ref{fig:MCexample}).
+%The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
+The $p1$, $p2$ colored bars (white-red colormap) illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
+The span of text defined by the start and end index with the highest probability is the answer.
+%
+As we can see, there are two spans of text that correspond to higher probabilities.
+We can examine the corresponding sentence in (a3) and (b2).
+Both sentences exhibit excellent alignment with the question.
+The spans with high probability are ``Two'' and ``No'' (highlight in orange), which both align well with many.
+Another interesting observation is that the number ``9'' (in ``Falcon 9') is also aligned with ``many'', yet in the prediction both ``Two'' and ``No'' have significantly higher probability.
+One possible explanation is the word ``Two'' has much higher \emph{att2} attention value compare to ``9'', which may contribute to the current outcome.

### 2018-05-29 EMNLP-demo-paper/relatedWorks.tex
update related works

--- 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
@@
 \section{Related Works}
-Due to the increasing demand for model interpretability, many previous works has been proposed for understanding NLP models in term of making sense of individual predictions as well as model mechanism as a whole.
+Due to the increasing demand for model interpretability, many previous works have been proposed for making sense NLP models by examining individual predictions as well as the model mechanism as a whole.
+%
+In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based text representation is investigated by utilizing instance-level attribution techniques originated from the vision community, i.e., \cite{ZeilerFergus2014}.
+%
+In the representation erasure work~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
 
-In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based representation of text is investigate by utilizing instance based attribution techniques originated from the vision community (i.e., \cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017}).
-%
-In the representation erasure work~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of various parts of the model by altering or removing the corresponding representations (i.e., the dimension count of hidden units, or input words).
-
-Beside interpreting the model via carefully designed experiments, interactive demo / visualization systems, such as AllenNLP demo (\url{http://demo.allennlp.org/}), also attract attention as it provide a flexible environment where the user can experiment and explore the various input combination and carry out error analysis.
-%
-Some of these interactive systems incorporate various visual encodings to summary the key information of the model.
-%
-The training dynamic of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and the hidden state properties of the LSTM are investigated in the LSTMvis visualization tool~\cite{StrobeltGehrmannPfister2018}.
-%Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
+Besides interpreting the model via carefully designed experiments, interactive demo/visualization systems, such as AllenNLP demo (\url{http://demo.allennlp.org/}), also attract attention.
+These systems often rely on visual encodings to summary the critical information of the model and provide a flexible environment, in which the user can experiment and explore the various input combinations and carry out error analysis.
+%The training dynamic of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and 
+The hidden state properties of the LSTM are visualized and investigated in the LSTMvis visualization system \cite{StrobeltGehrmannPfister2018}.
 Lee et al.
-visualizes the beam search and attention component in the NMT model.
-The work~\cite{lee2017interactive} directly involve the user into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.
-%}
-In the recent attention visualization work on question and answering model~\cite{ruckle2017end}, 
-instead of visualizing the attention matrix directly, the system using color map to show the text context and highlights the critical phrase that used to answers the questions.
+visualize the beam search and attention component in the NMT model~\cite{lee2017interactive},  in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
+In the visualization work on the question and answering model~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that used to answers the questions. 
 %The user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.
-%

### 2018-05-29 EMNLP-demo-paper/intro.tex
update related works
finialize intro

@@
 %where end-to-end training become a primary option.
-and as the design of neural networks evolve, there is a clear trend of increasing model complexity both in term of the architecture and the parameters count. 
+and as the design of neural networks evolves, there is a clear trend of increasing model complexity both in term of the architecture and the parameters count. 
 %
-While the expressiveness of these models help improve the prediction performance, there is a fundamental lack of interpretability that lead many to consider neural network models black boxes. 
+While the expressiveness of these models helps improve the prediction performance, there is a fundamental lack of interpretability that leads many to consider neural network models black boxes. 
 %
-Despite the difficulties, interpreting the model internals and reason about predictions are essential for understanding limitation of the model and improve upon the existing designs.
+Despite the difficulties, interpreting the model internals and reason about predictions are essential for understanding the limitation of the model and improve upon the existing designs.
 
@@
 
-Recently, attention networks have become a widely-adopted mechanism \cite{VaswaniShazeerParmar2017, Parikh2016}, the attention not only improves the model performance, but also yields interpretable intermediate representations (e.g.
-alignment among words).
-As a result, attention has been used as a natural interface for analyzing the internals of neural networks.
-Conduct analysis directly on the raw attention values can be challenging for human user, therefore, visual representations that highlight word alignments between sentences have been adopted, such as bipartite graph and heat map of the attention matrix~\cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
-However, many challenges remains.
-Firstly, for some NLP tasks, the word sequence pair among which the attentions are computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), where the standard visual encoding can not adequately handle.
-In addition, many previous works present the attention in a statics setting.
-Yet, the ability to provide an interactive environment, where the user can instantaneously look at how changes in the input will affect the attention, and how small changes in attention will affect the prediction are crucial for interpreting the model.
-Finally, many previous visualization efforts, despite reveal many interesting results, focus more on illustrating potentially useful visualization technique than provide a flexible software tool that can be easily integrated into existing code base.
-As a result, applying these proposed techniques to real word examples may involving substantial engineering effort than many user may not afford to undertake.
+Recently, attention networks have become a widely-adopted mechanism \cite{VaswaniShazeerParmar2017, Parikh2016}.
+The attention not only improves the model performance but also yields interpretable intermediate representations (i.e., alignment among words).
+As a result, attention is often considered as a natural interface for analyzing the internals of neural networks.
+Conduct analysis directly on the raw attention values can be challenging for human users, therefore, visual representations that highlight word alignments between sentences have been proposed, such as bipartite graph and heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
+However, many challenges remain.
+Firstly, for some NLP tasks, the word sequences pair among which the attention is computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), where the standard visual encoding cannot adequately handle.
+Also, many previous works present the attention in a static setting.
+However, the ability to provide an interactive environment, in which the user can instantaneously look at how changes in the input affect the attention, and how small variations in the attention alter the prediction are crucial for interpreting the model.
+Finally, many previous visualization efforts, despite reveal many exciting results, focus more on illustrating potentially useful visualization technique than provide a flexible software tool that can be easily integrated into existing code base.
+As a result, applying these proposed techniques to real-world examples may involving substantial engineering effort that could prevent wide adoption.
 
 To address these challenges in interpreting attention-based models, 
-we introduce a flexible python library that allow user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
+we introduce a flexible python library that allows the user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
 %
-To facilitate exploratory analysis (see Figure~\ref{fig:modelPipeline}), we adopted a fully interactive pipeline, where the user can perturb the input text (via two perturbation schemes discussed in Section~\ref{sec:perturb}) and observe the effects on attention and prediction, or modify the attention to understand how it affect the predictions.
+To facilitate exploratory analysis (see Figure~\ref{fig:modelPipeline}), we employ a fully interactive pipeline, in which the user can perturb the input text (via two perturbation schemes discussed in Section~\ref{sec:perturb}) and observe the effects on attention and prediction, or modify the attention to understand how it affects the predictions.
 %
-We demonstrate our system on two primary NLP tasks: natural language
-inference (NLI) and machine comprehension (MC). For the NLI task, we visualize
-decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
-For the MC task, we present your visualization methods on bidirectional attention flow model,
-which also represents a line of state-of-the-art models \cite{Seo2016}.
+Finally, we demonstrate our system on two primary NLP tasks: natural language
+inference (NLI) and machine comprehension (MC). 
+%For the NLI task, we visualize
+%decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
+%For the MC task, we present your visualization methods on bidirectional attention flow model,
+%which also represents a line of state-of-the-art models \cite{Seo2016}.
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{pipeline}
+ \vspace{-3mm}
+ \caption{
+ Perturbation-driven interrogation of the end-to-end models that follows the encoder, attention, and classifier structure.
+The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing)
+ }
+ \vspace{-3mm}
+\label{fig:modelPipeline}
+\end{figure}
 

### 2018-05-29 EMNLP-demo-paper/intro.tex
update intro

@@
  \caption{
- Perturbation-driven interrogation of the end-to-end models that follows the encoder, attention, and classifier structure.
-The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing)
+ Perturbation-driven interrogation of the end-to-end models that follow the encoder, attention, and classifier structure.
+The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing), edit the attention, and observe the changes.
  }

### 2018-05-29 EMNLP-demo-paper/conclusion.tex
minor fix
update pixel bar layout scheme

@@
 We design the individual components with versatility in mind.
-Due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available models.
+However, due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available configurations.
 %
-In the future, we plan to expand the visualization component further to handle tasks such neural machine translation and more.
+In the future, we plan to improve the flexibility of the attention interface and expand the visualization component further to handle tasks such neural machine translation and more.

### 2018-05-29 EMNLP-demo-paper/relatedWorks.tex
update pixel bar layout scheme

@@
 \section{Related Works}
-Due to the increasing demand for model interpretability, many previous works have been proposed for making sense NLP models by examining individual predictions as well as the model mechanism as a whole.
+Due to the increasing demand for model interpretability, many previous works have been proposed for making sense of NLP models by examining individual predictions as well as the model mechanism as a whole.
 %

### 2018-05-29 visPackage/static/components/attentionAsymmetricComponent.js

@@ -121,8 +121,9 @@ class attentionAsymmetricComponent extends attentionComponent {
 
     drawPixelBar(values, yPos) {
         let paragraphLen = this.paragraphLen;
-        let unit = this.width * 0.85 / paragraphLen;
         let pos = this.pixelBarXoffset;
+        let unit = (this.width - (20 * this.segmentList.length - 1) - pos) /
+            paragraphLen;
         let minIndex = 0;
 
         for (var i = 0; i < this.segmentList.length; i++) {
@@ -214,7 +215,9 @@ class attentionAsymmetricComponent extends attentionComponent {
             targAtt = targAtt.map(d =>
                 (d - targAttMin) / (targAttMax - targAttMin));
 
-            let unit = this.width * 0.85 / paragraphLen;
+            let unit = (this.width - (20 * this.segmentList.length - 1) -
+                    pos) /
+                paragraphLen;
             this.paraPos = [];
             for (var i = 0; i < this.segmentList.length; i++) {
                 let senLen = this.segmentList[i].length;
@@ -446,7 +449,7 @@ class attentionAsymmetricComponent extends attentionComponent {
                     .node().getBBox();
                 // console.log(cbbox);
                 if (cbbox.height > cbbox.width)
-                    return "vertical-rl";
+                    return "vertical-lr";
                 else
                     return "hortizontal-rl";
             })

### 2018-05-30 EMNLP-demo-paper/result.tex
update related works
shorten implementation

@@
 %\end{figure*}
-\section{Applications}
-We demonstrate the proposed visualization system on the decomposable attention network~\cite{parikh2016emnlp}
-for the NLI task and the bi-directional attention flow network~\cite{Seo2016} for the MC task.
-
 \begin{figure*}[t]
@@
  \caption{
-An illustrate of the attention editing process. 
-By removing the alignment mistake between the two "green", the originally wrong prediction \emph{entailment} is corrected to \emph{netural}.
+An illustration of the attention editing process. 
+By removing the ``wrong'' alignment between the two ``green", the originally prediction \emph{entailment} is corrected to \emph{netural}.
 }
+  \vspace{-3mm}
 \label{fig:NLIexample}
@@
 
+\section{Applications}
+We demonstrate the proposed visualization system on the decomposable attention network~\cite{parikh2016emnlp}
+for the NLI task and the bi-directional attention flow network~\cite{Seo2016} for the MC task.
+
 \subsection{Natural Language Inference}
 \label{sec:NLIexample}
-The NLI task predict the relationship between a premise sentence (\textbf{P}) and a hypothesis sentence (\textbf{H}).
+The NLI task predicts the relationship between a premise sentence (\textbf{P}) and a hypothesis sentence (\textbf{H}).
+The attention matrix captures the alignment of words between these two sentences.
+Here we give an example of how a wrong prediction can be correct by editing the attention value.
+
+%The model produces two attention matrices, representing alignment from premise to hypothesis, and from hypothesis to premise.
 %as either \emph{entailment}, \emph{contradiction}, or \emph{neutral}.
@@
 %Our system visualized the bidirectional attentions and their interaction with output distribution over labels.
-The model produces two attention matrices, representing alignment from premise to hypothesis, and from hypothesis to premise.
 
-Here we show an example, in which the wrong prediction can be fixed by correcting the attention value.  
-%In the proposed system, we overlay the sentence dependency tree with the attention, which enables researchers to conduct comparisons between attention and grammar structure.
+As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be entailment, which is incorrect.
+By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea".
+However, these two ``green'' decorate different nouns, which lead to the wrong prediction.
+The grammar structure is captured by the dependency tree, i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
+However, the model does not has access to the grammar information and mistakenly assume the two \emph{greens} are describing the same thing (thus predict \emph{entailment}).
 %
-As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be entailment, which is incorrect.
-By examining the attention, we can see the word \textbf{green} in ``\textbf{green} jacket" is aligned to the \textbf{green} in ``\textbf{green} tea", yet these two ``green'' decorate different nouns.
-Such a relationship can be confirmed by examining the dependency tree, where  \textbf{green} in \textbf{P} is attached to ``jacket'', whereas \textbf{green} in \textbf{H} is attached to ``tea''.
-However, the model does not aware of these the grammar information.
-As a result, the model mistakenly believes the two \textbf{greens} are used to describe the same thing (thus predict \emph{entailment}).
-%
-To correct the mistake, we edit the attention value and remove the align between these two "green" (see Figure~\ref{fig:NLIexample}(b)).
+To correct the mistake, we can edit the attention value and remove the align between these two "green" (see Figure~\ref{fig:NLIexample}(b)).
 As expected, the prediction label is corrected (\emph{neutral}) (see in Figure~\ref{fig:NLIexample}(c)).

### 2018-05-30 EMNLP-demo-paper/system.tex
update related works
update figures
shorten implementation

@@
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipeline}
- \caption{
- Perturbation-driven interrogation of the end-to-end models that follows the encoder, attention, and classifier structure.
-The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing)
- }
-\label{fig:modelPipeline}
-\end{figure}
-
 \section{Visualization System}
 As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provide a window for peeking into the model decision making process.
-However, the static attention alone likely does not tell the whole story, instead we can learn more about the model by examining the dynamic between the input, the attention, and the output.
+%However, the static attention alone likely does not tell the whole story, instead we can learn more about the model by examining the dynamic between the input, the attention, and the output. 
 To allow the user to interrogate the relationship between different components of the pipeline, the proposed system utilizes a perturbation-driven exploration strategy, where the user can manually or automatically perturb the input sentence and then view the aggregated prediction information.
@@
 %
-The system consistence several visualization components that can be combined to generate an functional interactive system. In the following section, we will cover some of the key components.
+The system consistence several visualization components that can be combined to generate an functional interactive system.
+In the following section, we will cover some of the essential components (the usage of other components
+%such as a prediction summary statistics the entire development set, as well as a scheme to update the model based 
+can be found in the accompany video).
 
@@
  \includegraphics[width=0.9\linewidth]{sentence}
+ \vspace{-2mm}
  \caption{
@@
  }
- \vspace{-3mm}
+ \vspace{-1mm}
 \label{fig:sentence}
@@
 \vspace{-2mm}
- \includegraphics[width=0.9\linewidth]{attentionPanels}
+ \includegraphics[width=0.95\linewidth]{attentionPanels}
   \vspace{-3mm}
@@
 In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
-The user can alter the attention values via the pop-up interface illustrated in (c).
+The same values can also be directly visualized in the matrix form (b).
+The user can edit the attention values via the pop-up interface illustrated in (c).
 We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
 %
-For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
+For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d). User can focus on individual sentence by clicking the rectangular bars.
 }
@@
 The initial setup cost and learning curve of the tool are often the barriers for user adaptation. 
-To address these challenge, we design the visualization system as a Python library with modularity and easy accessibility in mind.
-Instead of using the visualization system as a monolithic standalone application, just like a plotting library (i.e., matplotlib), the different pieces of the visualization (i.e., matrix based attention encoding) can be accessed individually.
-% 
-Yet, the components can also be combined in any configuration desired by users via a simple API to better fit into one's workflow.
-More importantly, the library-based design allows easy integration with the existing model implemented in Python.
-%
-To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models.
+Therefore, instead of design visualization system as a monolithic standalone application, 
+we implement the proposed system as a python library with modularity and ease of accessibility in mind.
+To fit one's workflow, the different pieces of the visualization (i.e., matrix based attention encoding) can be accessed individually, 
+or combined in any configuration desired by users via a simple API.
+More importantly, the library-based design allows easy integration with the existing model implemented in python.
+%To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models.
 The the code required to create an interactive exploration environment for machine comprehension model is illustrated bellow.

### 2018-05-30 EMNLP-demo-paper/system.tex
update prediction discussion

@@
 \section{Visualization System}
-As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provide a window for peeking into the model decision making process.
-%However, the static attention alone likely does not tell the whole story, instead we can learn more about the model by examining the dynamic between the input, the attention, and the output. 
-To allow the user to interrogate the relationship between different components of the pipeline, the proposed system utilizes a perturbation-driven exploration strategy, where the user can manually or automatically perturb the input sentence and then view the aggregated prediction information.
-Beside the perturbation of the input, the system also allows interactive modification of the attention values, where the prediction will instantaneously updated to reflect the changes.
+As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provide a window to peek into the model decision making process.
+However, the static attention alone likely does not tell the whole story, 
+the proposed system utilizes a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes in others.
 %
-The system consistence several visualization components that can be combined to generate an functional interactive system.
-In the following section, we will cover some of the essential components (the usage of other components
+The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task.
+In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video).
 %such as a prediction summary statistics the entire development set, as well as a scheme to update the model based
-can be found in the accompany video).
-
-\subsection{Input Sentences Perturbation}
-\label{sec:perturb}
-Due to the discrete nature of the natural language, automatically applying perturbation to sentence for sensitivity analysis can be particularly challenging (compared to other domain, i.e., image), as small changes in words can leading to drastic differences in the semantics of the sentences.
-To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the wordNet~\cite{Miller1995}.
-However, the limitation is apparent, as synonyms replacement does not guarantee the meaning of the sentence remain the same.
-And the wordNet often produces infrequent/obscure usages that may leads to less meaningful perturbed sentences.
-However, this method requires minimal computation and is easy to implement.
 
@@
 The interface for showing input sentences.
-The user can manually alter the words or apply automatic perturbation/paraphrasing of the inputs.
-In the ``perturbed'' dropdown menu, the blue words are the only not exist in the original sentence.
+The user can manually edit the words or apply automatic perturbation/paraphrasing of the inputs.
+In the ``perturbed'' drop-down menu, the blue words are the ones not exist in the original sentence.
  }
@@
 
+\subsection{Input Sentences Perturbation}
+\label{sec:perturb}
+Due to the discrete nature of the natural language, automatically applying perturbation to sentence for sensitivity analysis can be particularly challenging (compared to other domain, i.e., image), as small changes in words can leading to drastic differences in the semantics of the sentences.
+To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the wordNet~\cite{Miller1995}.
+However, the limitation is apparent, as synonyms replacement does not guarantee the meaning of the sentence remains the same.
+And the WordNet often produces rare/obscure usages that may lead to less meaningful sentences.
+However, this method requires minimal computation and is easy to implement.
+
 To improve the perturbation quality, we also adopted a translation based paraphrasing technique that is similar to the one discussed in \cite{mallinson2017paraphrasing}.
 Here, we translate the original English sentence into several other languages and then translate back into English.
-Provided the translation produce correct result (in our case, we utilized the google cloud translation platform), we essential obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows the paraphrased/perturbed sentence).
+Provided the translation produce correct result (in our case, we utilized the Google cloud translation platform), we obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows the some of the paraphrased/perturbed sentences).
 
@@
 %
-For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities is encoded in the triangle, where the three vertices represents the three possible prediction (namely, \emph{entail}, \emph{contradict}, and \emph{neutral}).
-The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs are represented by smaller grey circles.
-A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the three vertices represent the three possible predictions (namely, \emph{entail}, \emph{contradict}, and \emph{neutral}).
+The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.
+A density contour of the prediction is computed to emphasize the highly cluttered areas and detect outliers.
 
@@
 The user can edit the attention values via the pop-up interface illustrated in (c).
-We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
+We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the grammar structure.
 %
-For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d). User can focus on individual sentence by clicking the rectangular bars.
+For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by clicking the rectangular bars.
 }
@@
 \subsection{Attention Visualization}
-As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted technique to bipartie graph (a), as well as the heatmap attention matrix representation (b). 
+As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted technique to visualize attention matrix are bipartie graph (a) and heatmap (b). 
 %
 In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
-%%%%%%%%
+%The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
+%
 The graph view is suitable for highlighting the most dominant alignments.
@@
 \subsection{Implementation}
-The initial setup cost and learning curve of the tool are often the barriers for user adaptation. 
+The initial setup cost and unnecessary learning curve are often the barriers to the broad adaptation of a tool. 
 Therefore, instead of design visualization system as a monolithic standalone application, 
-we implement the proposed system as a python library with modularity and ease of accessibility in mind.
-To fit one's workflow, the different pieces of the visualization (i.e., matrix based attention encoding) can be accessed individually, 
-or combined in any configuration desired by users via a simple API.
+we implement the proposed system as a python library with modularity and ease of use in mind.
+The different pieces of the visualization (i.e., matrix-based attention encoding) can be accessed individually, 
+or combined in other componenets to fit one's workflow via a simple API.
 More importantly, the library-based design allows easy integration with the existing model implemented in python.
 %To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models.
-The the code required to create an interactive exploration environment for machine comprehension model is illustrated bellow.
+The code for creating an interactive exploration environment for a machine comprehension model is illustrated below.
 

### 2018-05-30 EMNLP-demo-paper/NLPVis-demo-paper.tex
full paper draft
update abstract
feedback from chris.

@@
 Neural networks models have gained unprecedented popularity in natural language processing due to their state-of-the-art performance and the flexible end-to-end training scheme.
-Despite their advantages, the lack of interpretability hinders the deployment and refinement of the model.
+Despite their advantages, the lack of interpretability hinders the deployment and refinement of the models.
 %These models often relying on the attention mechanism, which not only helps improve predicting performance but also provide interpretable representations for users to peak into the opaque models that are usually considered as black boxes.
 %
-In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationship among the input, the model internals (i.e., attention), and the output predictions that in turn shed light on the model decision making processing.
+In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationships among the input, the model internals (i.e., attention), and the output predictions which in turn shed light on the model decision-making processing.
 
@@
 \input{result.tex}
+\input{conclusion.tex}
 

### 2018-05-30 EMNLP-demo-paper/relatedWorks.tex
update relate
feedback from chris

@@
 %
-In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based text representation is investigated by utilizing instance-level attribution techniques originated from the vision community, i.e., \cite{ZeilerFergus2014}.
+In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based text representation is investigated utilizing instance-level attribution techniques originated from the vision community, i.e., \cite{ZeilerFergus2014}.
 %
-In the representation erasure work~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
+In a study of the representation of erasure~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
 
 Besides interpreting the model via carefully designed experiments, interactive demo/visualization systems, such as AllenNLP demo (\url{http://demo.allennlp.org/}), also attract attention.
-These systems often rely on visual encodings to summary the critical information of the model and provide a flexible environment, in which the user can experiment and explore the various input combinations and carry out error analysis.
+These systems often rely on visual encodings to summarize the critical information of the model and provide a flexible environment in which the user can experiment and explore the various input combinations and carry out error analysis.
 %The training dynamic of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and 
@@
 visualize the beam search and attention component in the NMT model~\cite{lee2017interactive},  in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
-In the visualization work on the question and answering model~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that used to answers the questions. 
+In the visualization work on the question and answering model~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that is used to answers the question. 
 %The user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.

### 2018-05-30 EMNLP-demo-paper/intro.tex
added citations
update intro
feedback from chris

@@
 %where end-to-end training become a primary option.
-and as the design of neural networks evolves, there is a clear trend of increasing model complexity both in term of the architecture and the parameters count. 
+and as the design of neural networks evolves, there is a clear trend of increasing model complexity in terms of both the architecture and the parameters count. 
 %
-While the expressiveness of these models helps improve the prediction performance, there is a fundamental lack of interpretability that leads many to consider neural network models black boxes. 
+The expressiveness of these models helps improve the prediction performance, there is a fundamental lack of interpretability leads many researchers to consider neural network models black boxes. 
 %
-Despite the difficulties, interpreting the model internals and reason about predictions are essential for understanding the limitation of the model and improve upon the existing designs.
+Despite the difficulties, interpreting the model internals and reason about predictions are essential for understanding the limitation of the models and improving upon the existing designs.
 
@@
 
-Recently, attention networks have become a widely-adopted mechanism \cite{VaswaniShazeerParmar2017, Parikh2016}.
+Recently, the attention networks have become a widely-adopted mechanism \cite{bahdanau2014neural,seo2016bidirectional,Parikh2016, VaswaniShazeerParmar2017}.
 The attention not only improves the model performance but also yields interpretable intermediate representations (i.e., alignment among words).
 As a result, attention is often considered as a natural interface for analyzing the internals of neural networks.
-Conduct analysis directly on the raw attention values can be challenging for human users, therefore, visual representations that highlight word alignments between sentences have been proposed, such as bipartite graph and heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
+Conduct analysis directly on the raw attention values can be challenging for human users, and therefore, visual representations that highlight word alignments between sentences have been proposed, such as bipartite graph and heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
 However, many challenges remain.
-Firstly, for some NLP tasks, the word sequences pair among which the attention is computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), where the standard visual encoding cannot adequately handle.
+Firstly, for some NLP tasks, the word sequences pair for which the attention is computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), which the standard visual encoding cannot adequately handle.
 Also, many previous works present the attention in a static setting.
-However, the ability to provide an interactive environment, in which the user can instantaneously look at how changes in the input affect the attention, and how small variations in the attention alter the prediction are crucial for interpreting the model.
-Finally, many previous visualization efforts, despite reveal many exciting results, focus more on illustrating potentially useful visualization technique than provide a flexible software tool that can be easily integrated into existing code base.
-As a result, applying these proposed techniques to real-world examples may involving substantial engineering effort that could prevent wide adoption.
+However, the ability to provide an interactive environment, in which the user can instantaneously look at how changes in the input affect the attention, and how small variations in the attention alter the prediction, is crucial for interpreting the model.
+Finally, many previous visualization efforts, despite revealing many exciting results, focus more on illustrating potentially useful visualization technique than on providing a flexible software tool that can be easily integrated into an existing code base.
+As a result, applying these proposed techniques to real-world examples may involve substantial engineering effort that could prevent wide adoption.
 
 To address these challenges in interpreting attention-based models, 
-we introduce a flexible python library that allows the user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
+we introduce a flexible Python library that allows the user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
 %
-To facilitate exploratory analysis (see Figure~\ref{fig:modelPipeline}), we employ a fully interactive pipeline, in which the user can perturb the input text (via two perturbation schemes discussed in Section~\ref{sec:perturb}) and observe the effects on attention and prediction, or modify the attention to understand how it affects the predictions.
+To facilitate exploratory analysis (see Figure~\ref{fig:modelPipeline}), we employ a fully interactive pipeline, in which the user can perturb the input text (via two perturbation schemes discussed in Section~\ref{sec:perturb}) and observe the effects on the attention and prediction, or modify the attention to understand how it affects predictions.
 %
@@
  Perturbation-driven interrogation of the end-to-end models that follow the encoder, attention, and classifier structure.
-The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing), edit the attention, and observe the changes.
+The user can generate a small perturbation of the input (i.e., replacing synonyms, paraphrasing), edit the attention, and observe the changes.
  }

### 2018-05-30 EMNLP-demo-paper/system.tex
finalize section 3

@@
 \section{Visualization System}
-As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provide a window to peek into the model decision making process.
-However, the static attention alone likely does not tell the whole story, 
-the proposed system utilizes a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes in others.
+As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provides a window to peek into the model decision making process.
+However, the static attention alone likely does not tell the whole story. 
+The proposed system utilizes a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes in others.
 %
@@
 The user can manually edit the words or apply automatic perturbation/paraphrasing of the inputs.
-In the ``perturbed'' drop-down menu, the blue words are the ones not exist in the original sentence.
+In the ``perturbed'' drop-down menu, the blue background highlight words not in the original sentence.
  }
@@
 However, the limitation is apparent, as synonyms replacement does not guarantee the meaning of the sentence remains the same.
-And the WordNet often produces rare/obscure usages that may lead to less meaningful sentences.
+And the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
 However, this method requires minimal computation and is easy to implement.
@@
 Here, we translate the original English sentence into several other languages and then translate back into English.
-Provided the translation produce correct result (in our case, we utilized the Google cloud translation platform), we obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows the some of the paraphrased/perturbed sentences).
+Provided the translation produce correct result (in our case, we utilize the Google cloud translation platform), we obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the paraphrased/perturbed sentences).
 
@@
 %
-For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the three vertices represent the three possible predictions (namely, \emph{entail}, \emph{contradict}, and \emph{neutral}).
+For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entail}, \emph{contradict}, and \emph{neutral}).
 The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.
@@
 Attention visualization.
-In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-The same values can also be directly visualized in the matrix form (b).
+A bipartite graph encoding is adopted in the graph attention view (a), in which the edge thickness corresponds to the attention value.
+The same attention values can also be directly visualized in the matrix form (b).
 The user can edit the attention values via the pop-up interface illustrated in (c).
-We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the grammar structure.
+We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentences (shown in the video).
 %
-For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by clicking the rectangular bars.
+For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting in the summary visualization.
 }
@@
 \subsection{Attention Visualization}
-As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted technique to visualize attention matrix are bipartie graph (a) and heatmap (b). 
+As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted visual encodings for attention matrix are bipartite graph (a) and heatmap (b). 
 %
-In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
+In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), the edge thickness corresponds to the attention value of word pairs.
 %The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
+The graph view is suitable for highlighting the most dominant alignments. However, the edges may become cluttered if multiple attention values are high. 
+The matrix attention view (Fig.~\ref{fig:attentionVis}(b)) resolves these issues, despite being more verbose and less efficient in highlighting the most dominant alignments. 
+We also enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), where one alignment relationship is highlighted).
+
+We augment these standard visual encoding with grammar structure to address the challenge of long sentences.
+The text can be dynamically simplified based on the dependency tree (see Figure~\ref{fig:attentionVis}(a1)).
+We also show how the dependency information can potentially improve the prediction result in Section~\ref{sec:NLIexample}.
 %
-The graph view is suitable for highlighting the most dominant alignments.
-However, the edges may become cluttered if multiple attention values are high.
-The matrix attention view (Fig.~\ref{fig:attentionVis}(b)) resolve these issues, despite being more verbose and less efficient in highlighting the dominant alignments.
-We also enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), one the most dominant attention is highlighted in orange).
-%
-To facilitate the perturbation of attention (see Figure~\ref{fig:modelPipeline}), as illustrated in Figure~\ref{fig:attentionVis}(c), we implement an interface in the matrix view for user to directly manipulate the attention value.
+To facilitate the perturbation of attention (see Figure~\ref{fig:modelPipeline}), as illustrated in Figure~\ref{fig:attentionVis}(c), we implement an interface for directly manipulating the attention value.
 
-To address the challenge of visualizing long sentence, we augmented the standard visual encoding with grammar structure, and allow dynamic simplification of the sentence based on the dependency tree (see Figure~\ref{fig:attentionVis}(a1)).
-We also show how the dependency information can potentially improve the prediction result in Section~\ref{sec:NLIexample}
-
-However, when the one of the text sequence become signification longer, i.e., a full paragraph as in the machine comprehension task, the even the simplified sentence can not be meaningfully represented in the graph or matrix visual encoding.
-To address this visualization challenge, as illustrated in Figure~\ref{fig:attentionVis}(d), we introduce the hierarchical representation.
-Here, a pure graphical encoding (the color bars marked by \emph{att2}) is used to capture the aggregated alignment information of the whole paragraph, and the user can focus on localized attention information by selecting the a pixel bar that presents a single sentence.
-We can also link this attention representation with matrix, such that whenever a sentence is selected the local attention relationship is allow shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).
+However, when the text sequence becomes signification longer, i.e., a full paragraph in the machine comprehension task,  even the simplified sentence cannot be meaningfully represented in the graph or matrix visual encoding.
+To address this visualization challenge, as illustrated in Figure~\ref{fig:attentionVis}(d), we introduce a hierarchical representation.
+Here, a pure graphical encoding (the color bars marked by \emph{att2}) is used to capture the aggregated attention information for the whole paragraph.
+The user can focus on localized attention information by selecting a pixel bar that presents a single sentence (the colored blocks in the bar correspond to individual works).
+We can also link this attention representation with matrix form, such that whenever a sentence is selected the local attention relationship is shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).
 
@@
 The different pieces of the visualization (i.e., matrix-based attention encoding) can be accessed individually, 
-or combined in other componenets to fit one's workflow via a simple API.
+or combined with other components to fit one's workflow via a simple API.
 More importantly, the library-based design allows easy integration with the existing model implemented in python.

### 2018-05-30 visPackage/static/components/paragraphComponent.js

@@ -83,6 +83,10 @@ class paragraphComponenet extends sentenceComponent {
         d3.select(this.div + "src").html(coloredSrc);
     }
 
+    showAggregatedPrediction() {
+        let allPrediction = this.data["allPairsPrediction"];
+    }
+
     colorSentenceByValue(sentence, prob, color) {
         let wordList = sentence.split(" ");
         var outputStr = "";

### 2018-05-30 EMNLP-demo-paper/conclusion.tex
shorten implementation
update result

--- 2018-05-29 EMNLP-demo-paper/conclusion.tex
@@
 %
-Due to the limited space, we didn't demonstrate all the available components, such as a visual summary of predict results of the entire development set, as well as a scheme to update the model based on user assigned prediction.
+We also conducted a small-scale user evaluation, where we ask five Ph.D.
+level students with NLP background to spend 30 minutes with the tool and then provide feedback.
+Most suggest the environment allow them to refine queries iteratively and identify potential issues with the model, but some student also mentioned the tool might not provide enough guidance for user do not already have an in-depth understanding of the model at hand.
+
+Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available configurations.
 %
-We also conducted a small-scale user study, in which we ask several Ph.D.
-level student with NLP background to spend 30 minutes with the tool and provide feedback.
-The positive feedbacks mentioned the environment allow them to iteratively refine their queries and identify potential issues with the model, but some student also suggests the tool may not provide enough guidance for user do not have an in-depth understanding of the model.
-
-We design the individual components with versatility in mind.
-Due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available models.
-%
-In the future, we plan to expand the visualization component further to handle tasks such neural machine translation and more.
+In the future, we plan to improve upon the current attention interface and expand the visualization component further to handle tasks such neural machine translation and more.

### 2018-05-30 EMNLP-demo-paper/result.tex
update result

@@
  \caption{
-The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
-The $p1$, $p2$ color bar illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
+In the machine comprehension visualization interface (a), the $p1$, $p2$ color bar illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
 The answer to the question is found in (a1), where the ``Two'' is aligned with the ``many'' in the question. However, the number 9 is also aligned with many, which may potentially lead to confusions.
-The second best answer is illustrated in b2.
+%
+We can evaluate the robustness of the prediction by perturbing the question sentence (b1, b3).
+As illustrated in (b1, b2) by removing the word ``partial'' the model still find the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
 }
@@
 %$s$ and $e$.
-Similarly, the attention information is also encoded as a bi-directional alignment (i.e., from context to question and vice versa). 
-The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
-Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2}.
+The attention information is encoded as a bi-directional alignment (i.e., from context to question and vice versa). 
+%The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
+Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2} (the \emph{att2} is a vector instead of a matrix, see \cite{Seo2016} for more details).
 

### 2018-05-30 EMNLP-demo-paper/relatedWorks.tex
update figure

@@
 %
-In a study of the representation of erasure~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
+In a study of the representation of erasure, \citet{li2016understanding} explain the neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
 
@@
 The hidden state properties of the LSTM are visualized and investigated in the LSTMvis visualization system \cite{StrobeltGehrmannPfister2018}.
-Lee et al.
-visualize the beam search and attention component in the NMT model~\cite{lee2017interactive},  in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
+\citet{lee2017interactive} visualize the beam search and attention component in the NMT model,  in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
 In the visualization work on the question and answering model~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that is used to answers the question. 

### 2018-05-30 EMNLP-demo-paper/result.tex
update figure

@@
 An illustration of the attention editing process.
-By removing the ``wrong'' alignment between the two ``green", the originally prediction \emph{entailment} is corrected to \emph{netural}.
+The dependency structure is shown in (a), where the two ``green'' are decorating different nouns.
+By removing the ``wrong'' alignment in (b), the originally prediction \emph{entailment} is corrected to \emph{netural} in (c).
 }
@@
 %The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
-Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2} (the \emph{att2} is a vector instead of a matrix, see \cite{Seo2016} for more details).
+Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2} (the \emph{att2} is a vector instead of a matrix, see \cite{Seo2016} for more details.
+In this demo, we applied a min max normalization for \emph{att2} after the softmax computation to better distinguish attention values).
 

### 2018-05-30 visPackage/static/components/attentionAsymmetricComponent.js

@@ -192,6 +192,7 @@ class attentionAsymmetricComponent extends attentionComponent {
             // b));
             var srcAtt = attMatrix.map(d => Math.max(...d));
             this.srcAtt = this.softmax(srcAtt);
+            // console.log(srcAtt);
             let srcAttMax = Math.max(...srcAtt);
             let srcAttMin = Math.min(...srcAtt);
             this.srcAtt = srcAtt.map(d =>

### 2018-05-30 visPackage/static/components/paragraphComponent.js

@@ -71,6 +71,11 @@ class paragraphComponenet extends sentenceComponent {
     showPrediction() {
         let indexS = this.predP1.indexOf(Math.max(...this.predP1));
         let indexE = this.predP2.indexOf(Math.max(...this.predP2));
+        let answer = this.source.split(" ").slice(indexS, indexE +
+            1).join(" ");
+        // console.log(answer);
+        d3.select(this.div + "pred").property("value", answer);
+
         let prob = new Array(this.predP1.length).fill(0);
 
         for (let i = indexS; i < indexE + 1; i++) {

### 2018-05-30 EMNLP-demo-paper/conclusion.tex
update intro

@@
 %
-In the future, we plan to improve upon the current attention interface and expand the visualization component further to handle tasks such neural machine translation and more.
+In the future, we plan to improve upon the current attention interface, release the library as an open source package, and expand the visualization component further to handle tasks such neural machine translation and more.

### 2018-05-30 EMNLP-demo-paper/intro.tex
update intro

@@
 
-To address these challenges in interpreting attention-based models, 
-we introduce a flexible Python library that allows the user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
-%
-To facilitate exploratory analysis (see Figure~\ref{fig:modelPipeline}), we employ a fully interactive pipeline, in which the user can perturb the input text (via two perturbation schemes discussed in Section~\ref{sec:perturb}) and observe the effects on the attention and prediction, or modify the attention to understand how it affects predictions.
-%
-Finally, we demonstrate our system on two primary NLP tasks: natural language
-inference (NLI) and machine comprehension (MC). 
-%For the NLI task, we visualize
-%decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
-%For the MC task, we present your visualization methods on bidirectional attention flow model,
-%which also represents a line of state-of-the-art models \cite{Seo2016}.
-
 \begin{figure}[htbp]
@@
 
+To address these challenges in interpreting attention-based models, 
+we introduce a python library that allows users to create web-based interactive visual analytics environments,
+in which they can interrogate the model by perturbing the input text and observing the effects on the attention and prediction, or modifying the attention and studying how it affects predictions (see Figure~\ref{fig:modelPipeline}).
+%
+We demonstrate our system on two primary NLP tasks: natural language
+inference (NLI) and machine comprehension (MC). 
+%For the NLI task, we visualize
+%decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
+%For the MC task, we present your visualization methods on bidirectional attention flow model,
+%which also represents a line of state-of-the-art models \cite{Seo2016}.
+
 %In summary, our key contributions are:

### 2018-05-31 EMNLP-demo-paper/conclusion.tex
update result

--- 2018-05-30 EMNLP-demo-paper/conclusion.tex
@@
 %
-In the future, we plan to improve upon the current attention interface and expand the visualization component further to handle tasks such neural machine translation and more.
+In the future, we plan to improve upon the current attention interface, release the library as an open source package, and expand the visualization components to handle tasks such neural machine translation and more.

### 2018-05-31 EMNLP-demo-paper/result.tex
update result

@@
 }
-  \vspace{-3mm}
+\vspace{-2mm}
 \label{fig:NLIexample}
@@
 %
-To correct the mistake, we can edit the attention value and remove the align between these two "green" (see Figure~\ref{fig:NLIexample}(b)).
-As expected, the prediction label is corrected (\emph{neutral}) (see in Figure~\ref{fig:NLIexample}(c)).
-
-\begin{figure*}[t]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{MC_interface}
-  \vspace{-6mm}
- \caption{
-In the machine comprehension visualization interface (a), the $p1$, $p2$ color bar illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
-The answer to the question is found in (a1), where the ``Two'' is aligned with the ``many'' in the question. However, the number 9 is also aligned with many, which may potentially lead to confusions.
-%
-We can evaluate the robustness of the prediction by perturbing the question sentence (b1, b3).
-As illustrated in (b1, b2) by removing the word ``partial'' the model still find the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
-}
-\label{fig:MCexample}
-\end{figure*}
+To correct the mistake, we can edit the attention value and remove the align between these two "green" (see (c)(b)).
+As expected, the prediction label is corrected (\emph{neutral}).
 
@@
 
-As illustrated in Figure~\ref{fig:MCexample}, we show \emph{att2} in the overview attention colored bars (yellow-green-blue colormap), in which each rectangular corresponds to one sentence.
-We can then focus on individual sentences by click on the rectangular (see Figure~\ref{fig:MCexample}).
+\begin{figure*}[t]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{MC_interface}
+  \vspace{-6mm}
+ \caption{
+In the machine comprehension visualization interface (a), the $p1$, $p2$ colored bar (in $a3$) illustrate the predicted start and end index of the answer in the context (the deeper the red the higher the probability).
+The most likely answer is shown in ($a1$).
+The global and local attention are visualized by ($a2$, $a3$).
+%
+We can evaluate the robustness of the prediction by perturbing the question sentence ($b1$, $b3$).
+As illustrated in ($b1$, $b2$) by removing the word ``partial'' the model still find the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
+}
+\label{fig:MCexample}
+\end{figure*}
+
+As illustrated in Figure~\ref{fig:MCexample}, we show \emph{att2} as the colored bars with \emph{yellow-green-blue} colormap.
+Each rectangular bar corresponds to one sentence.
+The user can focus on individual sentences by click on the bar (see Figure~\ref{fig:MCexample}).
 %The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
-The $p1$, $p2$ colored bars (white-red colormap) illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
+The $p1$, $p2$ colored bars (\emph{white-red} colormap) illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
 The span of text defined by the start and end index with the highest probability is the answer.
 %
-As we can see, there are two spans of text that correspond to higher probabilities.
+As we can see in Figure~\ref{fig:MCexample} ($a3$), there are two spans of text that correspond to higher probabilities.
 We can examine the corresponding sentence in (a3) and (b2).
 Both sentences exhibit excellent alignment with the question.
-The spans with high probability are ``Two'' and ``No'' (highlight in orange), which both align well with many.
-Another interesting observation is that the number ``9'' (in ``Falcon 9') is also aligned with ``many'', yet in the prediction both ``Two'' and ``No'' have significantly higher probability.
-One possible explanation is the word ``Two'' has much higher \emph{att2} attention value compare to ``9'', which may contribute to the current outcome.
+The spans with high probability are ``Two'' and ``No'' (highlight in orange), which both align well with the word ``many''.
+%Another interesting observation is that the number ``9'' (in ``Falcon 9') is also aligned with ``many'', yet in the prediction both ``Two'' and ``No'' have significantly higher probability.
+We can explore the robustness of the model by examining how the prediction varies when the question is perturbed.
+%
+As illustrated in ($b1$, and $b2$), the perturbed sentence does not include the ``word'' partial, which lead to a different yet still correct answer ``No'', which also exhibits high probability for the original question.
+%
+The user can manually edit the text directly. As shown in ($b3$), the model still produces the correct answer when changing the question from ``how many'' to ``which''.
+%One possible explanation is the word ``Two'' has much higher \emph{att2} attention value compare to ``9'', which may contribute to the current outcome.

### 2018-05-31 EMNLP-demo-paper/conclusion.tex
minor fix

@@
 %
-We demonstrate the usability and flexibility of tool by configuring the visual components to investigate models for solving different NLP tasks (e.g., NLI, MC).
+We demonstrate the usability and flexibility of tool by configuring the visual components to investigate models for different NLP tasks (e.g., NLI, MC).
 %
-We also conducted a small-scale user evaluation, where we ask five Ph.D.
-level students with NLP background to spend 30 minutes with the tool and then provide feedback.
-Most suggest the environment allow them to refine queries iteratively and identify potential issues with the model, but some student also mentioned the tool might not provide enough guidance for user do not already have an in-depth understanding of the model at hand.
+We also conducted a small-scale user evaluation, where five Ph.D.
+level students with NLP background spent 30 minutes with the tool and then provided feedback.
+Most suggested the environment allow them to refine queries iteratively and identify potential issues with the model, but some student also mentioned the tool might not provide enough guidance for users do not have an in-depth understanding of the model at hand.
 
-Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available configurations.
+Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure compatibility with all the available configurations.
 %

### 2018-05-31 EMNLP-demo-paper/result.tex
update result

@@
  \includegraphics[width=1.0\linewidth]{NLIexample}
-  \vspace{-6mm}
+  \vspace{-7mm}
  \caption{
@@
 \label{sec:MCexample}
-In machine comprehension task, two sequences of texts are given: context/paragraph and question.
+In machine comprehension task, two sequences of texts are given: context and question.
 The goal is to select a span of text from the context that answers the question. 
@@
 Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2} (the \emph{att2} is a vector instead of a matrix, see \cite{Seo2016} for more details.
-In this demo, we applied a min max normalization for \emph{att2} after the softmax computation to better distinguish attention values).
+In this demo, we applied a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values).
 
@@
  \includegraphics[width=1.0\linewidth]{MC_interface}
-  \vspace{-6mm}
+  \vspace{-7mm}
  \caption{
@@
 
-As illustrated in Figure~\ref{fig:MCexample}, we show \emph{att2} as the colored bars with \emph{yellow-green-blue} colormap.
+As illustrated in Figure~\ref{fig:MCexample}, we represent \emph{att2} as colored bars with \emph{yellow-green-blue} colormap.
 Each rectangular bar corresponds to one sentence.
@@
 %The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
-The $p1$, $p2$ colored bars (\emph{white-red} colormap) illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
-The span of text defined by the start and end index with the highest probability is the answer.
+The $p1$, $p2$ colored bars (\emph{white-red} colormap) illustrate the predicted beginning and ending index for the answer (deeper the red the higher the probability).
+%The span of text defined by the beginning and end index with the highest probability is the answer.
 %
 As we can see in Figure~\ref{fig:MCexample} ($a3$), there are two spans of text that correspond to higher probabilities. 
-We can examine the corresponding sentence in (a3) and (b2).
-Both sentences exhibit excellent alignment with the question.
-The spans with high probability are ``Two'' and ``No'' (highlight in orange), which both align well with the word ``many''.
-%Another interesting observation is that the number ``9'' (in ``Falcon 9') is also aligned with ``many'', yet in the prediction both ``Two'' and ``No'' have significantly higher probability.
-We can explore the robustness of the model by examining how the prediction varies when the question is perturbed.
+In (a3), we examine the sentence that contains the answer, which exhibits excellent alignment with the question (e.g., ``Two'' is aligned with ``many''). 
+%The spans of text with high probability are ``Two'' and ``No'' (highlight in orange), both align well with the word ``many''.
+An interesting observation is that the number ``9'' (in ``Falcon 9') is also aligned with ``many'', which may potentially lead to problems.
+
+The user can explore the robustness of the model by examining how the prediction varies when the question is perturbed.
 %
-As illustrated in ($b1$, and $b2$), the perturbed sentence does not include the ``word'' partial, which lead to a different yet still correct answer ``No'', which also exhibits high probability for the original question.
+As illustrated in ($b1$, and $b2$), the perturbation removes the word ``partial'' in the original sentence, which leads the model to produce a different yet correct answer (``No'').
+Refer back to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
 %
-The user can manually edit the text directly. As shown in ($b3$), the model still produces the correct answer when changing the question from ``how many'' to ``which''.
+The user can also manually edit the text. As shown in ($b3$). The model still produces the correct answer when changing the question from ``how many'' to ``which''.
 %One possible explanation is the word ``Two'' has much higher \emph{att2} attention value compare to ``9'', which may contribute to the current outcome.

### 2018-05-31 EMNLP-demo-paper/conclusion.tex

@@
 level students with NLP background spent 30 minutes with the tool and then provided feedback.
-Most suggested the environment allow them to refine queries iteratively and identify potential issues with the model, but some student also mentioned the tool might not provide enough guidance for users do not have an in-depth understanding of the model at hand.
+Most suggested the environment allow them to refine queries iteratively and identify potential issues with the model, but some also mentioned the tool might not provide enough guidance for users do not have an in-depth understanding of the model at hand.
 

### 2018-05-31 EMNLP-demo-paper/result.tex
fixes

@@
 \label{sec:MCexample}
-In machine comprehension task, two sequences of texts are given: context and question.
-The goal is to select a span of text from the context that answers the question. 
+In machine comprehension task, the goal is to select a span of text as the answer
+to a question sentence.
+%two sequences of texts are given: context and question.
+%The goal is to select a span of text from the context that answers the question. 
 %We provide a simple model formulation and refer the reader to the paper for details.
@@
 %The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
-Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2} (the \emph{att2} is a vector instead of a matrix, see \cite{Seo2016} for more details.
-In this demo, we applied a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values).
+Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}).
+In this demo, we apply a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values).
 
@@
 %The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
-The $p1$, $p2$ colored bars (\emph{white-red} colormap) illustrate the predicted beginning and ending index for the answer (deeper the red the higher the probability).
+The $p1$, $p2$ colored bars (\emph{white-red} colormap) illustrate the predicted probabilities of the start and the end index for the answer (the deeper the higher).
 %The span of text defined by the beginning and end index with the highest probability is the answer.
 %
-As we can see in Figure~\ref{fig:MCexample} ($a3$), there are two spans of text that correspond to higher probabilities. 
-In (a3), we examine the sentence that contains the answer, which exhibits excellent alignment with the question (e.g., ``Two'' is aligned with ``many''). 
+%In Figure~\ref{fig:MCexample} ($a3$), there are two spans of text that correspond to higher probabilities. 
+In Figure~\ref{fig:MCexample}(a3), the sentence containing the answer exhibits good alignment with the question (e.g. ``Two'' with ``many'').
+%In (a3), we examine the sentence that contains the answer, which exhibits excellent alignment with the question (e.g., ``Two'' is aligned with ``many''). 
 %The spans of text with high probability are ``Two'' and ``No'' (highlight in orange), both align well with the word ``many''.
-An interesting observation is that the number ``9'' (in ``Falcon 9') is also aligned with ``many'', which may potentially lead to problems.
+Interestingly, the number ``9'' (in ``Falcon 9') is also aligned with ``many'', which may potentially lead to problems.
 

### 2018-05-31 EMNLP-demo-paper/result.tex
fix
use BIDAF instead of bidrectional attention flow

@@
 We demonstrate the proposed visualization system on the decomposable attention network~\cite{parikh2016emnlp}
-for the NLI task and the bi-directional attention flow network~\cite{Seo2016} for the MC task.
+for the NLI task and the BIDAF model~\cite{Seo2016} for the MC task.
 
@@
 As illustrated in ($b1$, and $b2$), the perturbation removes the word ``partial'' in the original sentence, which leads the model to produce a different yet correct answer (``No'').
-Refer back to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
+Referring back to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
 %

### 2018-05-31 EMNLP-demo-paper/system.tex
fixes in system.tex

@@
 Due to the discrete nature of the natural language, automatically applying perturbation to sentence for sensitivity analysis can be particularly challenging (compared to other domain, i.e., image), as small changes in words can leading to drastic differences in the semantics of the sentences.
-To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the wordNet~\cite{Miller1995}.
-However, the limitation is apparent, as synonyms replacement does not guarantee the meaning of the sentence remains the same.
+To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the WordNet~\cite{Miller1995}.
+However, synonyms replacement does not guarantee the meaning of the sentence remains the same.
 And the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
-However, this method requires minimal computation and is easy to implement.
+%However, this method requires minimal computation and is easy to implement.
 
-To improve the perturbation quality, we also adopted a translation based paraphrasing technique that is similar to the one discussed in \cite{mallinson2017paraphrasing}.
+To improve the perturbation quality, we adopted a translation based paraphrasing technique similar to \citet{mallinson2017paraphrasing}.
 Here, we translate the original English sentence into several other languages and then translate back into English.
-Provided the translation produce correct result (in our case, we utilize the Google cloud translation platform), we obtain paraphrasing of the original sentences (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the paraphrased/perturbed sentences).
+Provided the translation produces good result (in our case, we utilize the Google cloud translation platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).
 

### 2018-05-31 EMNLP-demo-paper/result.tex
fixes

@@
 
-As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be entailment, which is incorrect.
+As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
 By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea".
-However, these two ``green'' decorate different nouns, which lead to the wrong prediction.
-The grammar structure is captured by the dependency tree, i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
-However, the model does not has access to the grammar information and mistakenly assume the two \emph{greens} are describing the same thing (thus predict \emph{entailment}).
+However, these two \emph{green}`s decorate different nouns, which potentially lead to the wrong prediction.
+The grammar structure is visually presented by dependency tree.
+%i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
+However, the model does not has access to the grammar information and mistakenly assumes the two \emph{greens} are describing the same thing.
+% (thus predict \emph{entailment}). 
 %

### 2018-05-31 EMNLP-demo-paper/system.tex
fixes

@@
 %
-For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entail}, \emph{contradict}, and \emph{neutral}).
+For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}).
 The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.

### 2018-05-31 EMNLP-demo-paper/system.tex
minor fix

@@
 %
-For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting in the summary visualization.
+For highly asymmetric attention, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting in the summary visualization.
 }
@@
 The user can focus on localized attention information by selecting a pixel bar that presents a single sentence (the colored blocks in the bar correspond to individual works).
-We can also link this attention representation with matrix form, such that whenever a sentence is selected the local attention relationship is shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).
+We also link this attention representation with matrix form, such that whenever a sentence is selected the local attention is shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).
 

### 2018-05-31 EMNLP-demo-paper/result.tex
minor fix

@@
 \label{sec:NLIexample}
-The NLI task predicts the relationship between a premise sentence (\textbf{P}) and a hypothesis sentence (\textbf{H}).
+The NLI task predicts the relationship between a premise sentence (P) and a hypothesis sentence (H).
 The attention matrix captures the alignment of words between these two sentences.
@@
 
-As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
+As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
 By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea".

### 2018-05-31 EMNLP-demo-paper/result.tex
update application
chris feedback

@@
 An illustration of the attention editing process.
-The dependency structure is shown in (a), where the two ``green'' are decorating different nouns.
-By removing the ``wrong'' alignment in (b), the originally prediction \emph{entailment} is corrected to \emph{netural} in (c).
+The dependency structure is shown in (a), where the two ``greens'' are decorating different nouns.
+By removing the ``wrong'' alignment in (b), the original prediction \emph{entailment} is corrected to \emph{netural} in (c).
 }
@@
 
-As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
+As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pair (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
 By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea".
-However, these two \emph{green}`s decorate different nouns, which potentially lead to the wrong prediction.
+However, these two \emph{greens} decorate different nouns, which potentially leads to the wrong prediction.
 The grammar structure is visually presented by dependency tree.
@@
 %
-To correct the mistake, we can edit the attention value and remove the align between these two "green" (see (c)(b)).
+To correct the mistake, we can edit the attention value and remove the align between these two "greens" (see (c)(b)).
 As expected, the prediction label is corrected (\emph{neutral}).
@@
 \label{sec:MCexample}
-In machine comprehension task, the goal is to select a span of text as the answer
+In the machine comprehension task, the goal is to select a span of text as the answer
 to a question sentence.
@@
 %The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
-Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}).
+Here, we refer the context to question attention as \emph{att1}; and the question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}).
 In this demo, we apply a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values).
@@
  \caption{
-In the machine comprehension visualization interface (a), the $p1$, $p2$ colored bar (in $a3$) illustrate the predicted start and end index of the answer in the context (the deeper the red the higher the probability).
+In the machine comprehension visualization interface (a), the $p1$, $p2$ colored bar (in $a3$) illustrates the predicted start and end index of the answer in the context (the deeper the red, the higher the probability).
 The most likely answer is shown in ($a1$).
@@
 We can evaluate the robustness of the prediction by perturbing the question sentence ($b1$, $b3$).
-As illustrated in ($b1$, $b2$) by removing the word ``partial'' the model still find the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
+As illustrated in ($b1$, $b2$) by removing the word ``partial'', the model still finds the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
 }
@@
 Each rectangular bar corresponds to one sentence.
-The user can focus on individual sentences by click on the bar (see Figure~\ref{fig:MCexample}).
+The user can focus on individual sentences by clicking on the rectangular bar (see Figure~\ref{fig:MCexample}).
 %The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
@@
 The user can also manually edit the text. As shown in ($b3$). The model still produces the correct answer when changing the question from ``how many'' to ``which''.
-%One possible explanation is the word ``Two'' has much higher \emph{att2} attention value compare to ``9'', which may contribute to the current outcome.
+%One possible explanation is that the word ``Two'' has a much higher \emph{att2} attention value compared to ``9'', which may contribute to the current outcome.

### 2018-06-01 EMNLP-demo-paper/system.tex
add video link

@@
 The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task.
-In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video).
+In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0&t=59s}{link}).
 %such as a prediction summary statistics the entire development set, as well as a scheme to update the model based

### 2018-06-01 EMNLP-demo-paper/system.tex
update link

--- 2018-05-31 EMNLP-demo-paper/system.tex
@@
 The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task.
-In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video).
+In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0}{link}).
 %such as a prediction summary statistics the entire development set, as well as a scheme to update the model based

### 2018-06-01 EMNLP-demo-paper/system.tex
typo

@@
 
-However, when the text sequence becomes signification longer, i.e., a full paragraph in the machine comprehension task,  even the simplified sentence cannot be meaningfully represented in the graph or matrix visual encoding.
+However, when the text sequence becomes significantly longer, i.e., a full paragraph in the machine comprehension task,  even the simplified sentence cannot be meaningfully represented in the graph or matrix visual encoding.
 To address this visualization challenge, as illustrated in Figure~\ref{fig:attentionVis}(d), we introduce a hierarchical representation.

### 2018-06-01 EMNLP-demo-paper/relatedWorks.tex
minor edits to related work

@@
 %
-In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based text representation is investigated utilizing instance-level attribution techniques originated from the vision community, i.e., \cite{ZeilerFergus2014}.
+In recent work,~\citet{LiChenHovy2015} investigated the composability of the vector-based text representations using instance-level attribution techniques originated from the vision community~\cite[e.g.,][]{ZeilerFergus2014}.
 %
-In a study of the representation of erasure, \citet{li2016understanding} explain the neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
+In a study of the representation of erasure, \citet{li2016understanding} explained neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
 
-Besides interpreting the model via carefully designed experiments, interactive demo/visualization systems, such as AllenNLP demo (\url{http://demo.allennlp.org/}), also attract attention.
-These systems often rely on visual encodings to summarize the critical information of the model and provide a flexible environment in which the user can experiment and explore the various input combinations and carry out error analysis.
+Besides interpreting the model via carefully designed experiments, several interactive demo/visualization systems, such as AllenNLP's demos (\url{http://demo.allennlp.org/})  often rely on visual encodings to summarize the model predictions.
+They  provide a flexible environment in which the user can experiment with the various inputs and perform error analysis.
 %The training dynamic of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and 
 The hidden state properties of the LSTM are visualized and investigated in the LSTMvis visualization system \cite{StrobeltGehrmannPfister2018}.
-\citet{lee2017interactive} visualize the beam search and attention component in the NMT model,  in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
-In the visualization work on the question and answering model~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that is used to answers the question. 
+\citet{lee2017interactive} visualized the beam search and attention component in neural machine translation models, in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
+In the visualization work on question answering~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that is used to answers the question. 
 %The user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "NLPVis-demo-paper"
+%%% End:

### 2018-06-01 EMNLP-demo-paper/system.tex
grammar
fix grammar

@@
 \section{Visualization System}
-As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provides a window to peek into the model decision making process.
+As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP models follow a similar encoder, attention, and classifier structure, in which the attention stage provides a window to peek into the model decision-making process.
 However, the static attention alone likely does not tell the whole story. 
-The proposed system utilizes a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes in others.
+The proposed system utilizes a perturbation-driven exploration strategy that allows the user to manually or automatically perturb part of the pipeline and observe the changes in others.
 %
 The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task.
-In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0}{link}).
+In the following section, we will cover some of the essential components (The usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0}{link})
 %such as a prediction summary statistics the entire development set, as well as a scheme to update the model based
@@
 The user can manually edit the words or apply automatic perturbation/paraphrasing of the inputs.
-In the ``perturbed'' drop-down menu, the blue background highlight words not in the original sentence.
+In the ``perturbed'' drop-down menu, the blue background highlights words not in the original sentence.
  }
@@
 \label{sec:perturb}
-Due to the discrete nature of the natural language, automatically applying perturbation to sentence for sensitivity analysis can be particularly challenging (compared to other domain, i.e., image), as small changes in words can leading to drastic differences in the semantics of the sentences.
+Due to the discrete nature of the natural language, automatically applying perturbation to a sentence for sensitivity analysis can be particularly challenging (compared to other domains, i.e., image), as small changes in words can lead to drastic differences in the semantics of the sentences.
 To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the WordNet~\cite{Miller1995}.
-However, synonyms replacement does not guarantee the meaning of the sentence remains the same.
-And the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
+However, synonym replacement does not guarantee the meaning of the sentence remains the same, and  \the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
 %However, this method requires minimal computation and is easy to implement.
 
-To improve the perturbation quality, we adopted a translation based paraphrasing technique similar to \citet{mallinson2017paraphrasing}.
-Here, we translate the original English sentence into several other languages and then translate back into English.
-Provided the translation produces good result (in our case, we utilize the Google cloud translation platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).
+To improve the perturbation quality, we adopted a translation-based paraphrasing technique similar to \citet{mallinson2017paraphrasing}.
+Here, we translate the original English sentence into several other languages and then translate it back into English.
+Provided the translation produces  a good result (in our case, we utilize the Google cloud translation platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).
 
@@
  \caption{
-Summarize the prediction results of the perturbed input for the natural language inference model.
-the prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label.
+Summary of the prediction results of the perturbed input for the natural language inference model.
+The prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label.
 }
@@
 \subsection{Prediction Visualization}
-Efficient visual encoding for prediction is crucial for communicating the model behavior.
-And to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
+Efficient visual encoding for prediction is crucial for communicating the model behavior, and to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
 %
 For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}).
-The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.
+The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller gray circles.
 A density contour of the prediction is computed to emphasize the highly cluttered areas and detect outliers.
@@
 %
-For highly asymmetric attention, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting in the summary visualization.
+For highly asymmetric attention, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting the summary visualization.
 }
@@
 \subsection{Attention Visualization}
-As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted visual encodings for attention matrix are bipartite graph (a) and heatmap (b). 
+As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted visual encodings for the attention matrix are the bipartite graph (a) and heat-map (b). 
 %
@@
 
-We augment these standard visual encoding with grammar structure to address the challenge of long sentences.
+We augment these standard visual encodings with grammar structure to address the challenge of long sentences.
 The text can be dynamically simplified based on the dependency tree (see Figure~\ref{fig:attentionVis}(a1)).
@@
 Here, a pure graphical encoding (the color bars marked by \emph{att2}) is used to capture the aggregated attention information for the whole paragraph.
-The user can focus on localized attention information by selecting a pixel bar that presents a single sentence (the colored blocks in the bar correspond to individual works).
-We also link this attention representation with matrix form, such that whenever a sentence is selected the local attention is shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).
+The user can focus on localized attention information by selecting a pixel bar that represents a single sentence (the colored blocks in the bar correspond to individual works).
+We also link this attention representation with the matrix form, such that whenever a sentence is selected the local attention is shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).
 
 \subsection{Implementation}
-The initial setup cost and unnecessary learning curve are often the barriers to the broad adaptation of a tool. 
-Therefore, instead of design visualization system as a monolithic standalone application, 
-we implement the proposed system as a python library with modularity and ease of use in mind.
+The initial setup cost and unnecessary learning curve are often the barriers to broad adaptation of a tool. 
+Therefore, instead of designing a visualization system as a monolithic standalone application, 
+we implement the proposed system as a Python library with modularity and ease of use in mind.
 The different pieces of the visualization (i.e., matrix-based attention encoding) can be accessed individually, 
-or combined with other components to fit one's workflow via a simple API.
+or combined with other components to fit one's work-flow via a simple API.
 More importantly, the library-based design allows easy integration with the existing model implemented in python.

### 2018-06-01 EMNLP-demo-paper/result.tex
grammar fix
feedback from chris

@@
 An illustration of the attention editing process.
-The dependency structure is shown in (a), where the two ``greens'' are decorating different nouns.
-By removing the ``wrong'' alignment in (b), the original prediction \emph{entailment} is corrected to \emph{netural} in (c).
+The dependency structure is shown in (a), where the two ``greens'' decorate different nouns.
+By removing the ``wrong'' alignment in (b), the original prediction \emph{entailment} is corrected to \emph{neutral} in (c).
 }
@@
 The attention matrix captures the alignment of words between these two sentences.
-Here we give an example of how a wrong prediction can be correct by editing the attention value.
+Here we give an example of how a wrong prediction can be corrected by editing the attention value.
 
@@
 However, these two \emph{greens} decorate different nouns, which potentially leads to the wrong prediction.
-The grammar structure is visually presented by dependency tree.
+The grammar structure is visually presented by a dependency tree.
 %i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
-However, the model does not has access to the grammar information and mistakenly assumes the two \emph{greens} are describing the same thing.
+However, the model does not have access to the grammar information and mistakenly assumes the two \emph{greens} are describing the same thing.
 % (thus predict \emph{entailment}). 
@@
 The most likely answer is shown in ($a1$).
-The global and local attention are visualized by ($a2$, $a3$).
+The global attention and local attention are visualized by ($a2$, $a3$).
 %
 We can evaluate the robustness of the prediction by perturbing the question sentence ($b1$, $b3$).
-As illustrated in ($b1$, $b2$) by removing the word ``partial'', the model still finds the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
+As illustrated in ($b1$, $b2$), by removing the word ``partial'', the model still finds the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
 }
@@
 
-As illustrated in Figure~\ref{fig:MCexample}, we represent \emph{att2} as colored bars with \emph{yellow-green-blue} colormap.
+As illustrated in Figure~\ref{fig:MCexample}, we represent \emph{att2} as colored bars with a \emph{yellow-green-blue} colormap.
 Each rectangular bar corresponds to one sentence.
@@
 %In Figure~\ref{fig:MCexample} ($a3$), there are two spans of text that correspond to higher probabilities. 
-In Figure~\ref{fig:MCexample}(a3), the sentence containing the answer exhibits good alignment with the question (e.g. ``Two'' with ``many'').
+In Figure~\ref{fig:MCexample}(a3), the sentence containing the answer exhibits good alignment with the question (e.g., ``Two'' with ``many'').
 %In (a3), we examine the sentence that contains the answer, which exhibits excellent alignment with the question (e.g., ``Two'' is aligned with ``many''). 
 %The spans of text with high probability are ``Two'' and ``No'' (highlight in orange), both align well with the word ``many''.
-Interestingly, the number ``9'' (in ``Falcon 9') is also aligned with ``many'', which may potentially lead to problems.
+Interestingly, the number ``9'' (in ``Falcon 9') is also aligned with ``many'', which may lead to problems.
 
@@
 As illustrated in ($b1$, and $b2$), the perturbation removes the word ``partial'' in the original sentence, which leads the model to produce a different yet correct answer (``No'').
-Referring back to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
+Referring to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
 %
-The user can also manually edit the text. As shown in ($b3$). The model still produces the correct answer when changing the question from ``how many'' to ``which''.
+The user can also manually edit the text. As shown in ($b3$), the model still produces the correct answer when changing the question from ``how many'' to ``which''.
 %One possible explanation is that the word ``Two'' has a much higher \emph{att2} attention value compared to ``9'', which may contribute to the current outcome.

### 2018-06-01 EMNLP-demo-paper/intro.tex
minor fix

@@
 To address these challenges in interpreting attention-based models, 
-we introduce a python library that allows users to create web-based interactive visual analytics environments,
+we introduce a Python library that allows users to create web-based interactive visual analytics environments,
 in which they can interrogate the model by perturbing the input text and observing the effects on the attention and prediction, or modifying the attention and studying how it affects predictions (see Figure~\ref{fig:modelPipeline}).

### 2018-06-01 EMNLP-demo-paper/system.tex
minor fix

@@
 To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the WordNet~\cite{Miller1995}.
-However, synonym replacement does not guarantee the meaning of the sentence remains the same, and  \the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
+However, synonym replacement does not guarantee the meaning of the sentence remains the same, and the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
 %However, this method requires minimal computation and is easy to implement.
@@
 %
-For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}).
+For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangular barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}).
 The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller gray circles.

### 2018-06-01 EMNLP-demo-paper/result.tex
minor edits all over

--- 2018-05-31 EMNLP-demo-paper/result.tex
@@
 \label{sec:NLIexample}
-The NLI task predicts the relationship between a premise sentence (P) and a hypothesis sentence (H).
+The NLI task predicts the entailment relationship between a premise sentence (P) and a hypothesis sentence (H).
 The attention matrix captures the alignment of words between these two sentences.
-Here we give an example of how a wrong prediction can be correct by editing the attention value.
+Here we give an example of how a wrong prediction can be corrected by editing attention values.
 
@@
 By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea".
-However, these two \emph{greens} decorate different nouns, which potentially leads to the wrong prediction.
-The grammar structure is visually presented by dependency tree.
+However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction.
+The grammatical structure is visually shown in the form of the dependency tree.
 %i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
-However, the model does not has access to the grammar information and mistakenly assumes the two \emph{greens} are describing the same thing.
+However, the model does not have access to the syntactic information and mistakenly assumes the two \emph{greens} modify the same thing.
 % (thus predict \emph{entailment}). 
@@
 Here, we refer the context to question attention as \emph{att1}; and the question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}).
-In this demo, we apply a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values).
+In this demo, we apply a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values.
 
@@
 %One possible explanation is that the word ``Two'' has a much higher \emph{att2} attention value compared to ``9'', which may contribute to the current outcome.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "NLPVis-demo-paper"
+%%% End:

### 2018-06-01 EMNLP-demo-paper/system.tex
minor edits all over

--- 2018-06-01 EMNLP-demo-paper/system.tex
@@
 \section{Visualization System}
-As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provides a window to peek into the model decision making process.
-However, the static attention alone likely does not tell the whole story. 
-The proposed system utilizes a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes in others.
+As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP models follow a similar encoder--attention--classifier structure.
+The attention stage provides a window to peek into the model decision making process.
+However, the static attention alone does not tell the whole story. 
+Our proposed system uses a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes downstream.
 %
 The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task.
-In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0}{link}).
+In the following section, we will cover some of the essential components; the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0}{link}.
 %such as a prediction summary statistics the entire development set, as well as a scheme to update the model based
@@
 \label{sec:perturb}
-Due to the discrete nature of the natural language, automatically applying perturbation to sentence for sensitivity analysis can be particularly challenging (compared to other domain, i.e., image), as small changes in words can leading to drastic differences in the semantics of the sentences.
-To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the WordNet~\cite{Miller1995}.
-However, synonyms replacement does not guarantee the meaning of the sentence remains the same.
-And the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
+Due to the discrete nature of natural language, automatically perturbing a sentence for sensitivity analysis can be particularly challenging (compared to other domains such as images) --- small changes in words can lead to drastic differences in the semantics of the sentences.
+To reduce the potential semantic deviation, we allow for a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in WordNet~\cite{Miller1995}.
+However, synonym replacement does not guarantee that the meaning of the sentence remains the same.
+Furthermore, WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
 %However, this method requires minimal computation and is easy to implement.
 
-To improve the perturbation quality, we adopted a translation based paraphrasing technique similar to \citet{mallinson2017paraphrasing}.
-Here, we translate the original English sentence into several other languages and then translate back into English.
-Provided the translation produces good result (in our case, we utilize the Google cloud translation platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).
+To improve the perturbation quality, we also allow for a translation-based paraphrasing technique similar to \citet{mallinson2017paraphrasing}.
+Here, we translate the original English sentence into several other languages and then pivot back to English.
+Provided the translation produces good result (in our case, we use the Google cloud translation platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).
 
@@
 %
-For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}).
+For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded via a triangular barycentric coordinate system, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}).
 The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.
@@
 \subsection{Attention Visualization}
-As illustrated in Figure~\ref{fig:attentionVis}(a)(b), the most widely adopted visual encodings for attention matrix are bipartite graph (a) and heatmap (b). 
+As illustrated in Figures~\ref{fig:attentionVis}(a)(b), the most widely adopted visual encodings for attention are  bipartite graphs (a) and heatmaps (b). 
 %
-In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), the edge thickness corresponds to the attention value of word pairs.
+In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), the edge thickness corresponds to the attention value of the word pairs.
 %The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
@@
 \end{lstlisting}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "NLPVis-demo-paper"
+%%% End:

### 2018-06-01 EMNLP-demo-paper/conclusion.tex

@@
 %
-We demonstrate the usability and flexibility of tool by configuring the visual components to investigate models for different NLP tasks (e.g., NLI, MC).
+We demonstrate the usability and flexibility of the tool by configuring the visual components to investigate models for different NLP tasks (e.g., NLI, MC).
 %
-We also conducted a small-scale user evaluation, where five Ph.D.
+We also conducted a small-scale user evaluation, in which five Ph.D.
 level students with NLP background spent 30 minutes with the tool and then provided feedback.
-Most suggested the environment allow them to refine queries iteratively and identify potential issues with the model, but some also mentioned the tool might not provide enough guidance for users do not have an in-depth understanding of the model at hand.
+Most suggested the environment allowed them to refine queries iteratively and identify potential issues with the model, but some also mentioned the tool might not provide enough guidance for users who do not have an in-depth understanding of the model at hand.
 
-Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure compatibility with all the available configurations.
+Even though we designed the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure compatibility with all the available configurations.
 %
-In the future, we plan to improve upon the current attention interface, release the library as an open source package, and expand the visualization components to handle tasks such neural machine translation and more.
+In the future, we plan to improve upon the current attention interface, release the library as an open-source package, and expand the visualization components to handle tasks such neural machine translation and more.

### 2018-06-01 EMNLP-demo-paper/result.tex

--- 2018-06-01 EMNLP-demo-paper/result.tex
@@
 \label{sec:NLIexample}
-The NLI task predicts the relationship between a premise sentence (P) and a hypothesis sentence (H).
+The NLI task predicts the entailment relationship between a premise sentence (P) and a hypothesis sentence (H).
 The attention matrix captures the alignment of words between these two sentences.
-Here we give an example of how a wrong prediction can be corrected by editing the attention value.
+Here we give an example of how a wrong prediction can be corrected by editing attention values.
 
@@
 By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea".
-However, these two \emph{greens} decorate different nouns, which potentially leads to the wrong prediction.
-The grammar structure is visually presented by a dependency tree.
+However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction.
+The grammatical structure is visually shown in the form of the dependency tree.
 %i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
-However, the model does not have access to the grammar information and mistakenly assumes the two \emph{greens} are describing the same thing.
+However, the model does not have access to the syntactic information and mistakenly assumes the two \emph{greens} modify the same thing.
 % (thus predict \emph{entailment}). 

### 2018-06-01 EMNLP-demo-paper/system.tex

@@
 \subsection{Prediction Visualization}
-Efficient visual encoding for prediction is crucial for communicating the model behavior.
-And to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
+Efficient visual encoding for prediction is crucial for communicating the model behavior, and to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
 %
+
 For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded via a triangular barycentric coordinate system, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}).
 The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.
+
 A density contour of the prediction is computed to emphasize the highly cluttered areas and detect outliers.

### 2018-06-01 EMNLP-demo-paper/system.tex
update figure

--- 2018-06-01 EMNLP-demo-paper/system.tex
@@
 The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task.
-In the following section, we will cover some of the essential components (The usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0}{link})
+In the following section, we will cover some of the essential components (The usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=PKiM4i0oIuY}{link})
 %such as a prediction summary statistics the entire development set, as well as a scheme to update the model based

### 2018-06-01 EMNLP-demo-paper/intro.tex

@@
 
-Deep neural networks have been successfully applied to various natural language processing tasks,
+Deep neural networks have been successfully applied to various natural language processing tasks.
 %where end-to-end training become a primary option.
-and as the design of neural networks evolves, there is a clear trend of increasing model complexity in terms of both the architecture and the parameters count. 
+As the design of neural networks evolves, there is a clear trend of increasing model complexity in terms of both the architecture and the parameter count. 
 %
-The expressiveness of these models helps improve the prediction performance, there is a fundamental lack of interpretability leads many researchers to consider neural network models black boxes. 
+While expressive models help improve the prediction performance, the fundamental lack of interpretability leads many researchers to consider neural network models black boxes. 
 %
-Despite the difficulties, interpreting the model internals and reason about predictions are essential for understanding the limitation of the models and improving upon the existing designs.
+The ability to interpret model internals and reason about predictions is essential for understanding the limitation of the models and improving upon them.
 
@@
 
-Recently, the attention networks have become a widely-adopted mechanism \cite{bahdanau2014neural,seo2016bidirectional,Parikh2016, VaswaniShazeerParmar2017}.
-The attention not only improves the model performance but also yields interpretable intermediate representations (i.e., alignment among words).
-As a result, attention is often considered as a natural interface for analyzing the internals of neural networks.
-Conduct analysis directly on the raw attention values can be challenging for human users, and therefore, visual representations that highlight word alignments between sentences have been proposed, such as bipartite graph and heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
+Recently, the attention networks have become  widely-adopted~\cite{bahdanau2014neural,seo2016bidirectional,Parikh2016, VaswaniShazeerParmar2017}.
+It not only improves the model performance but also yields interpretable intermediate representations (i.e., alignment among words).
+As a result, attention can provide a natural interface for analyzing the internals of neural networks.
+Conducting analysis directly on the raw attention values can be challenging for human users, and therefore, visual representations that highlight word alignments between sentences have been proposed, such as bipartite graph and heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
 However, many challenges remain.
@@
 However, the ability to provide an interactive environment, in which the user can instantaneously look at how changes in the input affect the attention, and how small variations in the attention alter the prediction, is crucial for interpreting the model.
-Finally, many previous visualization efforts, despite revealing many exciting results, focus more on illustrating potentially useful visualization technique than on providing a flexible software tool that can be easily integrated into an existing code base.
+Finally, many previous visualization efforts, despite revealing many exciting results, focus more on illustrating potentially useful visualization techniques than on providing a flexible software tool that can be easily integrated into an existing code base.
 As a result, applying these proposed techniques to real-world examples may involve substantial engineering effort that could prevent wide adoption.
@@
 %
-We demonstrate our system on two primary NLP tasks: natural language
+We demonstrate our library applied to two NLP tasks: natural language
 inference (NLI) and machine comprehension (MC). 
@@
 %\end{itemize}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "NLPVis-demo-paper"
+%%% End:

### 2018-06-01 EMNLP-demo-paper/system.tex

--- 2018-06-01 EMNLP-demo-paper/system.tex
@@
 The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task.
-In the following section, we will cover some of the essential components; the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0}{link}.
+In the following section, we will cover some of the essential components; the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=PKiM4i0oIuY}{link}.
 %such as a prediction summary statistics the entire development set, as well as a scheme to update the model based

### 2018-06-01 EMNLP-demo-paper/conclusion.tex
grammar fix

@@
 %
-In the future, we plan to improve upon the current attention interface, release the library as an open-source package, and expand the visualization components to handle tasks such neural machine translation and more.
+In the future, we plan to improve upon the current attention interface, release the library as an open-source package, and expand the visualization components to handle tasks such as neural machine translation and more.

### 2018-06-08 paper/itemizedReviewResponse.tex
add review/response

Summary Review

The Summary Review
Reviewers were split on whether or not to accept the paper. R2 and R4 rated the paper very highly (5 and 4.5), while R1 and R3 gave lower scores of neutral or weak reject (3 and 2.5). As the scores average to 3.75, and because the primary and secondary reviewers are in agreement, we are advocating for an "Accept". However, the authors should pay careful attention to the comments by reviewers, and use the time remaining before the next version is due to revise the paper for clarity, to emphasize the main contributions of the paper, to provide rationale for the design choices, to provide more detailed information about the domain-expert collaborators, and to better justify the results of the task analysis. Some reviewers advocated for reducing the number of usage scenarios and providing a more in-depth examination of a single scenario, or a scenario composed of a series of sub-investigations. On the other hand, other reviewers found the breadth of potential analyses to be a positive component of the paper.

R1:
+ interesting topic
+ usage scenarios are interesting
- description of NLP NN and attention models are not sufficiently detailed in the paper
- details of collaboration with domain experts are missing
- justification of tasks are not sufficiently detailed
- differences between graph and matrix view should be explained in more detail
- density contour in the prediction view needs to be explained in more detail
- claims about extension of visualization system to non-NLI tasks is not supported
- need to clarify difference between proposed perturbation-driven analysis and gradient-based analysis
- qualitative evaluation is weak

R2:
+ important area for visualization research
+ article is well-written
+ application with linked views is well-designed and powerful
+ system supports debugging of inference models
- scalability of system is not discussed

R3: 
- article is dense and difficult to read
- rationale for design choices are not clear
- core contributions are not highlighted, too much emphasis on background material (explanation of NLI), not enough on the visualization system itself
- claims based on user evaluation aren?t supported

Reviewer 1
Paper type
Application / Design Study
Expertise
Knowledgeable
Overall Rating
<b>3 - Possible Accept</b><br/> The paper is not acceptable in its current state, but might be made acceptable with significant revisions within the conference review cycle.<br/>If the specified revisions are addressed fully and effectively I may be able to return a score of '4 - Accept'.
Supplemental Materials
Acceptable
Justification
This paper presents an interactive visualization system for analyzing natural language inference models with attention mechanisms. The perturbation-driven paradigm proposed by the authors are well implemented with various visualization components. However, there is still room to improve the presentation of the task analysis and the system design. The contribution of the visualization tool is limited to NLI models and it?s unclear how it could be extended to support the analysis of other tasks/models.
The Review
This paper presents an interactive visualization system, NLIZE, for analyzing natural language inference models. Based on a perturbation-driven exploration scheme and a regularized optimization scheme, the system allows users to interrogate how the prediction or the model would change if the input, attention or the predicted label changed. The system implemented visualization as a list of flexible visualization components that allow easy integration. The usefulness of the system is demonstrated through five usage scenarios and the system is evaluated through the feedback from both VIS and NLP researchers.

Understanding and analyzing the inner mechanisms of deep neural nets for NLP tasks is an interesting and unexplored topic. A flexible visualization tool might indeed help researchers develop more powerful models. The main contribution of this paper is the novel perturbation-driven scheme that allows domain experts flexibly explore the stability and the internals of an NLI model. The proposed analytic scheme treats a trained model as dynamic and allows modifications of the model on the fly.

The proposed idea is interesting, and the flexible design of the tool may also increase the adoption of the tool. The usage scenarios also look interesting, especially the Scenario 3. Does the result to some extent suggest that the attention mechanism is not a very efficient component in this task? I expect the authors dig it further.

However, the current shape of this paper may require a major revision before it is in an acceptable shape.

My major concern is the presentation of the paper.

1. In Section 2, the neural net in NLP and attention mechanisms are introduced. But the descriptions are unsatisfactory. There is no formal definition or description of the model and the attention mechanism. It?s still unclear how the attention mechanism is applied in the model. I would suggest the authors include a concise and formal introduction in the background part and include some formula.

2. In Section 4, the paper indicates that the system is developed under a long-term collaboration with NLP experts, but there is no description describing the details of the collaboration (the number of experts, the length and the form of the collaboration, the frequency of the meetings). It?s not until Section 7 did I learn that there are 2 NLP experts in collaboration. The task analysis can also be improved by including more detailed justification of the three tasks.

3. The presentation of the system design in Section 5 could be improved. 
- In Section 5.2, Attention View include both a bipartite graph and a matrix view, which visualize the same information. From the description of the paper, the graph view is only good for highlighting the most dominant alignments. I suspect that matrix view can also reveal the most dominant alignments by identifying the most salient color. Please justify the design decision. 
- It?s unclear how the simplification of attention representation is done from Section 5.2, please include more details.
- In Section 5.3, how do you compute the density contour? Why is a contour needed in the analysis?
- It?s better if the authors present the relation between Section 5.3 and 5.4 in a clearer way. It?s confusing to read how one can perturb a prediction in Section 5.3 before he/she read the algorithm in Section 5.4. I suggest put the algorithm along with the perturbation-driven paradigm at the beginning of Section 5

Except for the presentation issue, the contribution of this paper is somewhat limited to only NLI models with attention mechanisms. It?s not sure how the visualization can be easily extended for other NLP tasks. For example, I am not sure how the proposed visualization can easily adapt to machine translation, considering that there are no neutral/contradiction/entailment labels.

In addition, the perturbation-driven scheme is somewhat related to the gradient-based analysis (both are the local analysis of the model on a specific prediction). It is better if the authors discuss the two and differentiate them.

The evaluation is acceptable but a bit weak. There is no description of what questions have the authors asked during the evaluation sessions. It would be better to have formal interviews and ask the participants to perform specific tasks and observe how they performed.

Please also proofread the work and fix typos. For example, the word ?work? in Section 3 should be uncountable; In Section 5.3 ?the three points defines a triangle? -> ?the three points defining a triangle?
Reviewer 2
Paper type
Technique
Expertise
Expert
Overall Rating
<b>5 - Strong Accept</b><br/> The paper is an excellent contribution and should certainly be accepted, possibly with some minor revisions.<br/>It more than meets the quality standard.
Supplemental Materials
Acceptable
Justification
Overall, this is an excellent contribution, it successfully demonstrates the value of visualization, and sheds light on hidden mechanisms performed by complex models.
It also closes the analysis loop by enabling experts to introduce model adjustments and examine their effectiveness in mitigating mis-predictions.
The Review
The authors propose a system to debug the predictions of deep inference models in language domain.
These models focus on predicting whether a hypothesis entails, contradicts, or is neutral to a given premise. 
This is a very essential task in natural language understanding that goes beyond machine translation where the models transform an input language to an output language without being able to evaluate logical entailment between sentences nor to answer questions based on given text.

The system is very well designed and the article is very well written.
The authors employ five linked views to show different facets about the model at varying granularity and at stages in the model pipeline. The visualization design in each of these views is mapped smoothly from the data it shows and the analysis task it serves.
Likewise, the linkage between these views and the corresponding interactions are well suited for debugging purposes. In particular:
- they enable tracing the root cause of certain entailment predictions e.g. by exposing the model attention computed at any selected part of an input sentence.
- they enable examining different perturbations of the input sentence and easily identifying the ones that lead to changes in the prediction, hence revealing the language features behind these predictions and the corresponding attention values computed by the model.
- they enable reducing visual clutter by interactively collapsing irrelevant parts, which improves resolution.
Furthermore, the authors provide auxiliary helps such as grammar dependency tree and a diff heatmap.

In addition, the authors propose a simple method to adjust the model in order to avoid certain prediction errors, and to accordingly examine the effect of such optimizations.

The authors demonstrate five application scenarios on Bowman's NLI large corpus (cited as [24]) for Natural Language Inference.
These scenarios show the power of the proposed system. In particular the system exposes the "decision-making" process of the model, its stability, and the grammar it learns to capture via its attention mechanism, and accordingly enables exploring avenues to correct mispredictions by identifying at which stage they develop.

Finally, the authors discuss the limitations of their system, highlighting inherent difficulty of perturbating textual data without distorting the legibility or the language-wise plausibility of the input (unlike image data were perturbations are easy to impose). They provide sufficient details about their model and a video demonstration of the system in the supplementary.

Few remarks:
- A brief guidance of how to interpret visual patterns that emerge in each view would be very beneficial. In particular, did the authors notice any systematic / repetitive patterns in the triangular prediction view? Do these patterns indicate certain issues in the model / attention / perturbation schemes?
Same thing applies to the attention heatmap, the parameter histograms, and the overview scatterplots in Figure 8 (e.g. does the curve in Figure 8d tell us something?)
- Discuss scalability of the system. Can it visually handle long sentences? Would collapsing the heatmaps help here?
Can it handle a large number of sentences? This is important for the noted future applicability to question answering where the data items can be as large as text documents.
- Explain more about the Bowman's dataset in use [24], its dimensionality, coverage, complexity, language features, etc.
- A brief discussion of the applicability to other languages would be interesting maybe? Any anticipated challenges?
- Add label to the color scale in Figure 3 (the caption mentions attention by just to avoid confusion). Same for Figure 7a (frequency to the vertical axis), Figure 8b, and Figure 9a-c.
- Add narration to the video and maybe include a 1-min self-contained demo of the system before illustrating the use cases in the video.

Language mispredictions (misspelling):
As discussion in [8, 13]
tasks T1-3 (maybe T1-T3?)
correspondance 
studys
Reviewer 3
Paper type
Application / Design Study
Expertise
Knowledgeable
Overall Rating
<b>2.5 - Between Reject and Possible Accept</b><br/>
Supplemental Materials
Acceptable with minor revisions (specify revisions in The Review section)
Justification
This paper presents an application of multiple coordinated views to expert refinement of natural language inferences. The organization and presentation of the paper focuses very heavily on the neural network and natural language aspects of the application. The style of the paper is very dense, and occasionally oddly enthusiastic in tone, making for a very difficult read. The different views in the combined tool are described, but there is little rationale for and analysis of the visual representation choices that went into them.

The application itself seems interesting and appears to have some value, albeit apparently only for a very narrow group of expert users who have a particular mix of technical skills. The several described use cases look useful but as described are largely isolated in their utility; it's unclear how they can be integrated to support the broader analysis efforts of the target users.
The Review
This was a difficult paper to digest. Research on ways to bring together visualization and AI has become popular in the last few years, so the authors are targeting a fast-moving and dense space of possibilities. One of the main challenges in reading this paper was digesting not two but three different pillars of cutting edge work: richly interactive visual analytic tool design, neural networks, and natural language inference modeling. After the teaser image, the paper spends the first four pages on neural networks, NLP, and inference. One has to look hard to detect the lede in the next to last paragraph of the introduction ("Moreover, we propose...") Highlight it!

Even as a visualization-centric researcher who is aware of NNs and has done a little direct work in NLP, I found it hard to connect to the organization and balance of coverage of these topics in the paper. Despite the prominent teaser visualization and the description of individual views in section 5, the paper comes off as very visualization-light. For each view there it's clear what the visual representation is, but the majority of description is dedicated to the underlying mechanics of calculating and thinking about the NL inference. The specific interactions involved are also mostly implied, although I was able to deduce them. They should be made explicit.

More importantly, there is little rationale for the visual representation designs of the various views. The design choices do make sense (at least to an experienced visualization designer) but there are alternatives in each case. It's not clear that the visualization are particularly good or bad for their intended uses as described in section 6. A few questions that arise:

* How does one handle very different sentence lengths in the sentence view?
* What if the sentence structures between premise and hypothesis are not drastically different; will the matrix be as effective, and thus the graph need to be focused on?
* In the matrix view, how hard is it to control rows when they're renormalizing?
* How much reduction in the grammar dependency tree is necessary to combat visual clutter, and how does that relate to the expert's ability to dissect sentences at the desired level of detail?
* How do the matrices combined in figure 5f align for comparison?
* Why does the prediction view use a continuous interaction like drag when the target is to select one of only three discrete options?
* What happens in the prediction view if many predictions are close to each other? Between the predictions and the density contour map, the view could get very dense, particular if much data is involved from the 10k set.
* In the pipeline view, doesn't the formulation to approximate the assigned label introduce another black box that the user need to factor into their analytic thinking?
* Why a treemap in the summary view? It's just a 3x3 set of quantities. A simple 3x3 matrix heatmap would be more familiar, more readable, and assure that all of the prediction/label combinations are large enough to select easily.
* The description of interaction for the E/E category in the summary view says what one can do, but it's not clear how or why.

Part of the problem is that the language is very dense in this paper. Although the grammar is acceptable, it was a slow read and there were some passages that I found all but indecipherable, such as the figure 7 caption, the last paragraph of section 5.5, and the bullet list at the end of the introduction.

There were many small errors that need correcting, too many to bother listing here. There was also some hyperbole ("stunning", "unprecedented", "vision", "paradigm") that distracts me as a serious reader and should be replaced. A thorough copyediting should fix both issues.

The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination. The scenarios essentially describe individual tasks that experts might perform in individual views. Scenario 4 goes a little further, but is brief. The paper would very much benefit from a more complete example story of how an analyst might work with the various views in concert to perform higher-level activities. For an application paper like this, some sense of those activities, and how well the tool design works for them, is needed. The last couple paragraphs of section 7 offers only a glimpse of "interrogation" as the authors say. Their conclusion (participants believe it convenient) isn't sufficiently supported. As it stands, there isn't clear justification of the many visualization design choices. A longer scenario encompassing the larger process would go a long way toward rectifying that.

The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.
Reviewer 4
Paper type
Application / Design Study
Expertise
Knowledgeable
Overall Rating
<b>4.5 - Between Accept and Strong Accept</b><br/>
Supplemental Materials
Acceptable with minor revisions (specify revisions in The Review section)
Justification
see below
The Review
This paper introduces an application that lets a user to visualize aspects of a complex neural network model, and to interactively perturb that model? its inputs, its internal state, and its expected output? and then see how those perturbations affect other elements in the system. The application looks at networks that support an natural language processing task-- investigating the relationships between ideas expressed by two different sentences-- and specifically investigating attention mechanisms that weight particular words as being more or less relevant in determining these relationships.

? The introduction is for the most part well written and clearly sets up the motivation for the NLIZE application

? I was confused by the distinction between image networks and language networks. CNNs are not only used to make binary classifications, and there are certainly challenges in image networks that do not provide ?clear meaning? and seem like they would also benefit from the proposed work. In other words, I understand the focus on NLP tasks, but the reasoning for it doesn?t seem accurate (in the 3rd paragraph of the introduction).

? It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs. If it?s the former (as it seems to be), then I think this needs to be emphasized in the introduction.

? The discussion of why the authors chose to focus on NLI is well articulated and interesting

? The related work is sufficiently comprehensive and clearly contextualizes the main contributions of the NLIZE application

? I appreciated the task analysis in section 4. However, it seems a bit too brief, and the tasks don?t seem to directly follow from the description of the authors experience with the NLP researchers. The scenarios described in Section 6 provide much more detail about these tasks, and Section 5 clarifies them as well, but a bit more detail here would be useful. For example, it?s not clear who the NLP researchers are, how many of them were interviewed, what type of NLP projects they were working on, etc.

? The visual interface described in Section 5 seems very useful for performing the three main tasks. Some of the elements of the application are quite dense upon first encounter, but a lot of thought has gone into how they work together to provide different windows into the NN.

? Work by Ma et al. ("Visualizing dynamic brain networks using an animated dual-representation? from EuroVis 2015) is work related to NLIZE having both graph and matrix views that complement each other and provide the same information from different perspectives, as described in Section 5.2.

? Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4). I wonder if it would make sense to use other types of annotations here, such as those created from event extraction tools or information extraction tools that would highlight other structures (besides grammar/POS) that could be useful in helping understanding the inference model. Work by Forbes et al. supports the use of semantic hypergraphs to provide richer textual annotations alongside text sequences ("Text annotation graphs: Annotating complex natural language phenomena? from LREC 2018).

? The prediction triangle/contour view is very interesting!

? In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile? with ?heap?). This updates the system and changes the inference output. Are the successful results of such an interaction remembered by the system? That is, could NLIZE be used to tweak/update the model so that, say, the ambiguity between pile and heap is automatically and more accurately resolved in future queries?

A:

? Section 6.3 is very interesting, but I don?t understand why perturbing the attention stage has less of an effect that the other perturbations. This seems like a preliminary contribution in and of itself (i.e., that using the NLIZE application leads to global understanding such as this), and worthy of further examination.

A:

In sum, this paper presents an exciting approach to analyzing complex inference models? one which could in theory be extended easily to other NLP tasks and other inference models. The visualization, although somewhat complicated, seems to aid domain experts in understanding nuances of NLI tasks, and giving them a playground in which to formulate and test hypothesis through perturbing various elements within the system and seeing how they change others. The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach. It might make more sense to focus more on only one or two scenarios and cover them in more depth. Overall, despite some of the issues mentioned above, the paper presents innovation in interactive visualization to better understand NNs for language inference tasks, and I think this paper is a strong accept.

A:

### 2018-06-09 paper/background.tex
fix typo

@@
 Subsequently, the next stage aims at finding alignment between words in the input sequences.
-For the NLI task, this means finding the correspondance between words from the premise sentence to the hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
+For the NLI task, this means finding the correspondence between words from the premise sentence to the hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}).
 Finally, in the last stage, the alignment information and the encoded vector representations are aggregated and then used as features for a classification network (last part of the end-to-end neural network).

### 2018-06-09 paper/overview.tex
fix typo

@@
 \section{NLIZE System}
-In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-3}).
+In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-T3}).
 %

### 2018-06-09 paper/relatedWorks.tex
fix typo

@@
 Before one can solve the model interpretability challenge, it worth to understand what constitutes an explanation for a machine learning model.
-As discussion in~\cite{Lipton2016, Doshi-Velez2017}, there is little consensus on what interpretability is in the context of machine learning.
+As discussed in~\cite{Lipton2016, Doshi-Velez2017}, there is little consensus on what interpretability is in the context of machine learning.
 A taxonomy is suggested~\cite{Doshi-Velez2017} to promote a more rigorous study on such a subject.
@@
 \textbf{Visualization of NLP Models.}
-Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studys have been dedicated to neural language processing models.
+Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studies have been dedicated to neural language processing models.
 %

### 2018-06-09 paper/itemizedReviewResponse.tex
fix typos

@@
 Reviewer 1
-Paper type
-Application / Design Study
-Expertise
-Knowledgeable
-Overall Rating
-<b>3 - Possible Accept</b><br/> The paper is not acceptable in its current state, but might be made acceptable with significant revisions within the conference review cycle.<br/>If the specified revisions are addressed fully and effectively I may be able to return a score of '4 - Accept'.
-Supplemental Materials
+
 Acceptable
@@
 The Review
-This paper presents an interactive visualization system, NLIZE, for analyzing natural language inference models.
-Based on a perturbation-driven exploration scheme and a regularized optimization scheme, the system allows users to interrogate how the prediction or the model would change if the input, attention or the predicted label changed.
-The system implemented visualization as a list of flexible visualization components that allow easy integration.
-The usefulness of the system is demonstrated through five usage scenarios and the system is evaluated through the feedback from both VIS and NLP researchers.
 
-Understanding and analyzing the inner mechanisms of deep neural nets for NLP tasks is an interesting and unexplored topic.
-A flexible visualization tool might indeed help researchers develop more powerful models.
-The main contribution of this paper is the novel perturbation-driven scheme that allows domain experts flexibly explore the stability and the internals of an NLI model.
-The proposed analytic scheme treats a trained model as dynamic and allows modifications of the model on the fly.
-
-The proposed idea is interesting, and the flexible design of the tool may also increase the adoption of the tool.
+Q1.
 The usage scenarios also look interesting, especially the Scenario 3.
@@
 
-However, the current shape of this paper may require a major revision before it is in an acceptable shape.
+A:
 
-My major concern is the presentation of the paper.
-
-1.
+Q2.
 In Section 2, the neural net in NLP and attention mechanisms are introduced.
@@
 There is no formal definition or description of the model and the attention mechanism.
-It?s still unclear how the attention mechanism is applied in the model.
+It's still unclear how the attention mechanism is applied in the model.
 I would suggest the authors include a concise and formal introduction in the background part and include some formula.
 
-2.
-In Section 4, the paper indicates that the system is developed under a long-term collaboration with NLP experts, but there is no description describing the details of the collaboration (the number of experts, the length and the form of the collaboration, the frequency of the meetings).
+A:
+
+Q, In Section 4, the paper indicates that the system is developed under a long-term collaboration with NLP experts, but there is no description describing the details of the collaboration (the number of experts, the length and the form of the collaboration, the frequency of the meetings).
 It?s not until Section 7 did I learn that there are 2 NLP experts in collaboration.
@@
 
-3. The presentation of the system design in Section 5 could be improved. 
+Q The presentation of the system design in Section 5 could be improved.
 - In Section 5.2, Attention View include both a bipartite graph and a matrix view, which visualize the same information.
@@
 Please justify the design decision.
-- It?s unclear how the simplification of attention representation is done from Section 5.2, please include more details.
-- In Section 5.3, how do you compute the density contour? Why is a contour needed in the analysis?
-- It?s better if the authors present the relation between Section 5.3 and 5.4 in a clearer way.
+
+Q, It's unclear how the simplification of attention representation is done from Section 5.2, please include more details.
+
+Q, In Section 5.3, how do you compute the density contour? Why is a contour needed in the analysis?
+
+Q, It's better if the authors present the relation between Section 5.3 and 5.4 in a clearer way.
 It?s confusing to read how one can perturb a prediction in Section 5.3 before he/she read the algorithm in Section 5.4.
@@
 
-Except for the presentation issue, the contribution of this paper is somewhat limited to only NLI models with attention mechanisms.
-It?s not sure how the visualization can be easily extended for other NLP tasks.
+Q Except for the presentation issue, the contribution of this paper is somewhat limited to only NLI models with attention mechanisms.
+It's not sure how the visualization can be easily extended for other NLP tasks.
 For example, I am not sure how the proposed visualization can easily adapt to machine translation, considering that there are no neutral/contradiction/entailment labels.
 
-In addition, the perturbation-driven scheme is somewhat related to the gradient-based analysis (both are the local analysis of the model on a specific prediction).
+A: The composability of the system is the key to extend its capability
+
+Q, In addition, the perturbation-driven scheme is somewhat related to the gradient-based analysis (both are the local analysis of the model on a specific prediction).
 It is better if the authors discuss the two and differentiate them.
 
-The evaluation is acceptable but a bit weak.
+A: connection with sensitivity analysis
+
+Q, The evaluation is acceptable but a bit weak.
 There is no description of what questions have the authors asked during the evaluation sessions.
@@
 
+A:
+
 Please also proofread the work and fix typos.
-For example, the word ?work?
-in Section 3 should be uncountable; In Section 5.3 ?the three points defines a triangle?
--> ?the three points defining a triangle?
-Reviewer 2
-Paper type
-Technique
-Expertise
-Expert
-Overall Rating
-<b>5 - Strong Accept</b><br/> The paper is an excellent contribution and should certainly be accepted, possibly with some minor revisions.<br/>It more than meets the quality standard.
-Supplemental Materials
-Acceptable
-Justification
-Overall, this is an excellent contribution, it successfully demonstrates the value of visualization, and sheds light on hidden mechanisms performed by complex models.
-It also closes the analysis loop by enabling experts to introduce model adjustments and examine their effectiveness in mitigating mis-predictions.
+For example, the word 'work' in Section 3 should be uncountable; In Section 5.3, "the three points defines a triangle" -> "the three points defining a triangle"
+
+A:
+
 The Review
+
 The authors propose a system to debug the predictions of deep inference models in language domain.
@@
 The visualization design in each of these views is mapped smoothly from the data it shows and the analysis task it serves.
+
 Likewise, the linkage between these views and the corresponding interactions are well suited for debugging purposes. In particular:

### 2018-06-09 paper/prediction.tex
fix typos

@@
 In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle. 
-Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defines a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction or entailment.
+Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defining a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction or entailment.
 The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.

### 2018-06-09 paper/relatedWorks.tex
fix typos

@@
 Due to the effectiveness of exploring complex relationships, visualization has long been adopted for interpreting neural network models~\cite{TzengMa2005}.
-Recently, the increasing demand for interpretability for machine learning models has motivated the introduction of many visualization works that are dedicated to neural network models.
+Recently, the increasing demand for interpretability for machine learning models has motivated the introduction of many visualization work that are dedicated to neural network models.
 % The classification~\cite{KrausePererNg2016}

### 2018-06-10 paper/itemizedReviewResponse.tex
update itemized info

@@
 
-The Summary Review
 Reviewers were split on whether or not to accept the paper.
@@
 As the scores average to 3.75, and because the primary and secondary reviewers are in agreement, we are advocating for an "Accept".
+
 However, the authors should pay careful attention to the comments by reviewers, and use the time remaining before the next version is due to revise the paper for clarity, to emphasize the main contributions of the paper, to provide rationale for the design choices, to provide more detailed information about the domain-expert collaborators, and to better justify the results of the task analysis.
@@
 
-Reviewer 1
+Response to the summary:
 
-Acceptable
-Justification
-This paper presents an interactive visualization system for analyzing natural language inference models with attention mechanisms.
-The perturbation-driven paradigm proposed by the authors are well implemented with various visualization components.
-However, there is still room to improve the presentation of the task analysis and the system design.
-The contribution of the visualization tool is limited to NLI models and it?s unclear how it could be extended to support the analysis of other tasks/models.
-The Review
+------------------------------- Reviewer 1 -------------------------------
 
@@
 
+A:
+
 Q The presentation of the system design in Section 5 could be improved.
@@
 
+A:
+
 Q, It's unclear how the simplification of attention representation is done from Section 5.2, please include more details.
+
+A:
 
@@
 
+A:
+
 Q, It's better if the authors present the relation between Section 5.3 and 5.4 in a clearer way.
 It?s confusing to read how one can perturb a prediction in Section 5.3 before he/she read the algorithm in Section 5.4.
-I suggest put the algorithm along with the perturbation-driven paradigm at the beginning of Section 5
+I suggest put the algorithm along with the perturbation-driven paradigm at the beginning of Section 5.
+
+A:
 
@@
 
-The Review
+------------------------------- Reviewer 2 -------------------------------
 
-The authors propose a system to debug the predictions of deep inference models in language domain.
-These models focus on predicting whether a hypothesis entails, contradicts, or is neutral to a given premise.
-This is a very essential task in natural language understanding that goes beyond machine translation where the models transform an input language to an output language without being able to evaluate logical entailment between sentences nor to answer questions based on given text.
-
-The system is very well designed and the article is very well written.
-The authors employ five linked views to show different facets about the model at varying granularity and at stages in the model pipeline.
-The visualization design in each of these views is mapped smoothly from the data it shows and the analysis task it serves.
-
-Likewise, the linkage between these views and the corresponding interactions are well suited for debugging purposes. In particular:
-- they enable tracing the root cause of certain entailment predictions e.g. by exposing the model attention computed at any selected part of an input sentence.
-- they enable examining different perturbations of the input sentence and easily identifying the ones that lead to changes in the prediction, hence revealing the language features behind these predictions and the corresponding attention values computed by the model.
-- they enable reducing visual clutter by interactively collapsing irrelevant parts, which improves resolution.
-Furthermore, the authors provide auxiliary helps such as grammar dependency tree and a diff heatmap.
-
-In addition, the authors propose a simple method to adjust the model in order to avoid certain prediction errors, and to accordingly examine the effect of such optimizations.
-
-The authors demonstrate five application scenarios on Bowman's NLI large corpus (cited as [24]) for Natural Language Inference.
-These scenarios show the power of the proposed system.
-In particular the system exposes the "decision-making" process of the model, its stability, and the grammar it learns to capture via its attention mechanism, and accordingly enables exploring avenues to correct mispredictions by identifying at which stage they develop.
-
-Finally, the authors discuss the limitations of their system, highlighting inherent difficulty of perturbating textual data without distorting the legibility or the language-wise plausibility of the input (unlike image data were perturbations are easy to impose).
-They provide sufficient details about their model and a video demonstration of the system in the supplementary.
-
-Few remarks:
-- A brief guidance of how to interpret visual patterns that emerge in each view would be very beneficial.
+Q, A brief guidance of how to interpret visual patterns that emerge in each view would be very beneficial.
 In particular, did the authors notice any systematic / repetitive patterns in the triangular prediction view?
 Do these patterns indicate certain issues in the model / attention / perturbation schemes?
-Same thing applies to the attention heatmap, the parameter histograms, and the overview scatterplots in Figure 8 (e.g. does the curve in Figure 8d tell us something?)
+
+A:
+
+Q, Same thing applies to the attention heatmap, the parameter histograms, and the overview scatterplots in Figure 8 (e.g. does the curve in Figure 8d tell us something?)
 - Discuss scalability of the system. Can it visually handle long sentences? Would collapsing the heatmaps help here?
-Can it handle a large number of sentences? This is important for the noted future applicability to question answering where the data items can be as large as text documents.
-- Explain more about the Bowman's dataset in use [24], its dimensionality, coverage, complexity, language features, etc.
-- A brief discussion of the applicability to other languages would be interesting maybe? Any anticipated challenges?
-- Add label to the color scale in Figure 3 (the caption mentions attention by just to avoid confusion). Same for Figure 7a (frequency to the vertical axis), Figure 8b, and Figure 9a-c.
-- Add narration to the video and maybe include a 1-min self-contained demo of the system before illustrating the use cases in the video.
 
-Language mispredictions (misspelling):
+A:
+
+Q, Can it handle a large number of sentences? This is important for the noted future applicability to question answering where the data items can be as large as text documents.
+
+Q, Explain more about the Bowman's dataset in use [24], its dimensionality, coverage, complexity, language features, etc.
+
+Q, A brief discussion of the applicability to other languages would be interesting maybe? Any anticipated challenges?
+
+A:
+
+Q, Add label to the color scale in Figure 3 (the caption mentions attention by just to avoid confusion). Same for Figure 7a (frequency to the vertical axis), Figure 8b, and Figure 9a-c.
+
+A:
+
+Q, Add narration to the video and maybe include a 1-min self-contained demo of the system before illustrating the use cases in the video.
+
+A:
+
+Q, Language mispredictions (misspelling):
 As discussion in [8, 13]
@@
 studys
-Reviewer 3
-Paper type
-Application / Design Study
-Expertise
-Knowledgeable
-Overall Rating
-<b>2.5 - Between Reject and Possible Accept</b><br/>
-Supplemental Materials
-Acceptable with minor revisions (specify revisions in The Review section)
-Justification
-This paper presents an application of multiple coordinated views to expert refinement of natural language inferences.
-The organization and presentation of the paper focuses very heavily on the neural network and natural language aspects of the application.
-The style of the paper is very dense, and occasionally oddly enthusiastic in tone, making for a very difficult read.
-The different views in the combined tool are described, but there is little rationale for and analysis of the visual representation choices that went into them.
 
-The application itself seems interesting and appears to have some value, albeit apparently only for a very narrow group of expert users who have a particular mix of technical skills.
-The several described use cases look useful but as described are largely isolated in their utility; it's unclear how they can be integrated to support the broader analysis efforts of the target users.
-The Review
-This was a difficult paper to digest.
-Research on ways to bring together visualization and AI has become popular in the last few years, so the authors are targeting a fast-moving and dense space of possibilities.
-One of the main challenges in reading this paper was digesting not two but three different pillars of cutting edge work: richly interactive visual analytic tool design, neural networks, and natural language inference modeling.
-After the teaser image, the paper spends the first four pages on neural networks, NLP, and inference.
+A: these errors have been fixed.
+
+------------------------------- Reviewer 3 -------------------------------
+
+Q, After the teaser image, the paper spends the first four pages on neural networks, NLP, and inference.
 One has to look hard to detect the lede in the next to last paragraph of the introduction ("Moreover, we propose...") Highlight it!
 
-Even as a visualization-centric researcher who is aware of NNs and has done a little direct work in NLP, I found it hard to connect to the organization and balance of coverage of these topics in the paper.
+A:
+
+Q, Even as a visualization-centric researcher who is aware of NNs and has done a little direct work in NLP, I found it hard to connect to the organization and balance of coverage of these topics in the paper.
 Despite the prominent teaser visualization and the description of individual views in section 5, the paper comes off as very visualization-light.
-For each view there it's clear what the visual representation is, but the majority of description is dedicated to the underlying mechanics of calculating and thinking about the NL inference.
+
+A:
+
+Q,For each view there it's clear what the visual representation is, but the majority of description is dedicated to the underlying mechanics of calculating and thinking about the NL inference.
 The specific interactions involved are also mostly implied, although I was able to deduce them.
@@
 
-More importantly, there is little rationale for the visual representation designs of the various views.
+A:
+
+Q, More importantly, there is little rationale for the visual representation designs of the various views.
 The design choices do make sense (at least to an experienced visualization designer) but there are alternatives in each case.
@@
 * How does one handle very different sentence lengths in the sentence view?
+
+A:
+
 * What if the sentence structures between premise and hypothesis are not drastically different; will the matrix be as effective, and thus the graph need to be focused on?
+
+A:
+
 * In the matrix view, how hard is it to control rows when they're renormalizing?
+
+A:
+
 * How much reduction in the grammar dependency tree is necessary to combat visual clutter, and how does that relate to the expert's ability to dissect sentences at the desired level of detail?
+
+A:
+
 * How do the matrices combined in figure 5f align for comparison?
+
+A:
+
 * Why does the prediction view use a continuous interaction like drag when the target is to select one of only three discrete options?
+
+A:
+
 * What happens in the prediction view if many predictions are close to each other?
 Between the predictions and the density contour map, the view could get very dense, particular if much data is involved from the 10k set.
+
+A:
+
 * In the pipeline view, doesn't the formulation to approximate the assigned label introduce another black box that the user need to factor into their analytic thinking?
+
+A:
+
 * Why a treemap in the summary view?
@@
 A simple 3x3 matrix heatmap would be more familiar, more readable, and assure that all of the prediction/label combinations are large enough to select easily.
+
+A:
+
 * The description of interaction for the E/E category in the summary view says what one can do, but it's not clear how or why.
 
-Part of the problem is that the language is very dense in this paper.
+A:
+
+Q, Part of the problem is that the language is very dense in this paper.
 Although the grammar is acceptable, it was a slow read and there were some passages that I found all but indecipherable, such as the figure 7 caption, the last paragraph of section 5.5, and the bullet list at the end of the introduction.
 
-There were many small errors that need correcting, too many to bother listing here.
+A:
+
+Q, There were many small errors that need correcting, too many to bother listing here.
 There was also some hyperbole ("stunning", "unprecedented", "vision", "paradigm") that distracts me as a serious reader and should be replaced.
@@
 
-The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination.
+A: We remove/replace the words mentioned by the reviewer.
+For example, the following is the updated first sentence of the introduction in which "stunning", "unprecedented" are removed.
+"Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications."
+
+Q, The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination.
 The scenarios essentially describe individual tasks that experts might perform in individual views.
@@
 
-The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.
-Reviewer 4
-Paper type
-Application / Design Study
-Expertise
-Knowledgeable
-Overall Rating
-<b>4.5 - Between Accept and Strong Accept</b><br/>
-Supplemental Materials
-Acceptable with minor revisions (specify revisions in The Review section)
-Justification
-see below
-The Review
-This paper introduces an application that lets a user to visualize aspects of a complex neural network model, and to interactively perturb that model?
-its inputs, its internal state, and its expected output?
-and then see how those perturbations affect other elements in the system.
-The application looks at networks that support an natural language processing task-- investigating the relationships between ideas expressed by two different sentences-- and specifically investigating attention mechanisms that weight particular words as being more or less relevant in determining these relationships.
+A:
 
-? The introduction is for the most part well written and clearly sets up the motivation for the NLIZE application
+Q: The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.
 
-?
-I was confused by the distinction between image networks and language networks.
+A:
+
+------------------------------- Reviewer 4 -------------------------------
+
+Q, I was confused by the distinction between image networks and language networks.
 CNNs are not only used to make binary classifications, and there are certainly challenges in image networks that do not provide ?clear meaning?
 and seem like they would also benefit from the proposed work.
-In other words, I understand the focus on NLP tasks, but the reasoning for it doesn?t seem accurate (in the 3rd paragraph of the introduction).
+In other words, I understand the focus on NLP tasks, but the reasoning for it doesn't seem accurate (in the 3rd paragraph of the introduction).
 
-?
-It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs.
+A:
+
+Q, It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs.
 If it?s the former (as it seems to be), then I think this needs to be emphasized in the introduction.
 
-? The discussion of why the authors chose to focus on NLI is well articulated and interesting
+A:
 
-? The related work is sufficiently comprehensive and clearly contextualizes the main contributions of the NLIZE application
-
-?
-I appreciated the task analysis in section 4.
+Q, I appreciated the task analysis in section 4.
 However, it seems a bit too brief, and the tasks don?t seem to directly follow from the description of the authors experience with the NLP researchers.
 The scenarios described in Section 6 provide much more detail about these tasks, and Section 5 clarifies them as well, but a bit more detail here would be useful.
-For example, it?s not clear who the NLP researchers are, how many of them were interviewed, what type of NLP projects they were working on, etc.
+For example, it's not clear who the NLP researchers are, how many of them were interviewed, what type of NLP projects they were working on, etc.
 
-?
-The visual interface described in Section 5 seems very useful for performing the three main tasks.
-Some of the elements of the application are quite dense upon first encounter, but a lot of thought has gone into how they work together to provide different windows into the NN.
+A:
 
-?
-Work by Ma et al.
+Q, Work by Ma et al.
 ("Visualizing dynamic brain networks using an animated dual-representation?
@@
 
-?
-Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4).
+A:
+
+Q, Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4).
 I wonder if it would make sense to use other types of annotations here, such as those created from event extraction tools or information extraction tools that would highlight other structures (besides grammar/POS) that could be useful in helping understanding the inference model.
@@
 
-? The prediction triangle/contour view is very interesting!
+A:
 
-?
-In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile?
+Q, In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile?
 with ?heap?).
@@
 
-?
-Section 6.3 is very interesting, but I don?t understand why perturbing the attention stage has less of an effect that the other perturbations.
+Q, Section 6.3 is very interesting, but I don?t understand why perturbing the attention stage has less of an effect that the other perturbations.
 This seems like a preliminary contribution in and of itself (i.e., that using the NLIZE application leads to global understanding such as this), and worthy of further examination.
@@
 
-In sum, this paper presents an exciting approach to analyzing complex inference models?
-one which could in theory be extended easily to other NLP tasks and other inference models.
-The visualization, although somewhat complicated, seems to aid domain experts in understanding nuances of NLI tasks, and giving them a playground in which to formulate and test hypothesis through perturbing various elements within the system and seeing how they change others.
-The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach.
+Q, The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach.
 It might make more sense to focus more on only one or two scenarios and cover them in more depth.
-Overall, despite some of the issues mentioned above, the paper presents innovation in interactive visualization to better understand NNs for language inference tasks, and I think this paper is a strong accept.
 

### 2018-06-10 paper/intro.tex
update itemized info

@@
 % What is the obstacle for effectively apply machine learning model
-Based on some stunning recent advances, neural networks based machine learning approaches have gained unprecedented popularity, and have been adopted in a wide variety of applications.
+%Based on some stunning recent advances, neural networks based machine learning approaches have gained unprecedented popularity, and have been adopted in a wide variety of applications.
+Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications.
 %
@@
 
-We implement our vision of the perturbation-driven exploration in an interactive visualization system for natural language inference models~\cite{Parikh2016}.
-However, the components of the visualization and the overall paradigm can be readily extended to other NLP tasks, such as question and answer, text summarization, etc.
+We materialize the goal of the perturbation-driven exploration in an interactive visualization system for natural language inference models~\cite{Parikh2016}.
+%We implement our vision of the perturbation-driven exploration in an interactive visualization system for natural language inference models~\cite{Parikh2016}.
+However, the components of the visualization and the overall concept can be readily extended to other NLP tasks, such as question and answer, text summarization, etc.
 %

### 2018-06-11 paper/appendix_modelDescription.tex
fixes in model description

@@
 where $F$ function is the encoder layer (e.g.
-a context-free two-layer ReLU).
+a context-free layer with ReLU activation).
 Let $\boldsymbol{P}$ denote the output premise encoding of size $m \times d$, and $\boldsymbol{H}$ the hypothesis encoding of size $n \times d$ where $d$ is the encoding size.
@@
 \subsection{Attention} \label{sec:att}
-The job of attention layer is to capture pairwise interaction between encodings of premise and hypothesis. First we compute a similarity score matrix $\boldsymbol{S}$ ($m \times n$) by the following
+The job of the attention layer is to capture pairwise interaction between encodings of premise and hypothesis.
+First we get transformed encodings that are specialized for attention and then compute a similarity score matrix $\boldsymbol{S}$ ($m \times n$) by the following
 \begin{align}
-  S_{ij} &= \boldsymbol{p}_i ^T \boldsymbol{h}_j
+  \boldsymbol{P}^\prime, \boldsymbol{H}^\prime &= R(\boldsymbol{P}), R(\boldsymbol{H})\\
+  S_{ij} &= \boldsymbol{p}^{\prime T}_i \boldsymbol{h}^\prime_j
 \end{align}
-
-Then attention weights are obtained by normalizing $\boldsymbol{S}$ bidirectionally.
+where $R$ is the specialized transformation layer (e.g. a two-layer feedforward network with ReLU activation).
+Attention weights are obtained by normalizing $\boldsymbol{S}$ bidirectionally.
 We will use $\leftarrow$ and $\rightarrow$ to differentiate the notation.
@@
 \begin{align}
-  \boldsymbol{u}_i &= G([\overleftarrow{\boldsymbol{a}}_i \cdot \boldsymbol{H} \hspace{1ex} | \hspace{1ex}  \overline{\boldsymbol{p}}_i]) \\
-  \boldsymbol{v}_j &= G([\overrightarrow{\boldsymbol{a}}_j \cdot \boldsymbol{P} \hspace{1ex}  | \hspace{1ex}  \overline{\boldsymbol{h}}_j])
+  \boldsymbol{u}_i &= G([\overleftarrow{\boldsymbol{a}}_i \cdot \boldsymbol{H} \hspace{1ex} | \hspace{1ex}  \boldsymbol{p}_i]) \\
+  \boldsymbol{v}_j &= G([\overrightarrow{\boldsymbol{a}}_j \cdot \boldsymbol{P} \hspace{1ex}  | \hspace{1ex} \boldsymbol{h}_j])
 \end{align}

### 2018-06-14 paper/itemizedReviewResponse.tex
update questions

@@
 On the other hand, other reviewers found the breadth of potential analyses to be a positive component of the paper.
+
+///// for discussion ////
+- How to interpret MIRA show attention has less impact
+Q1,
+
+- Formal definition for attention
+Q2
 
@@
 
-A:
+A: The separation between different stages is based on the specific model implementation, so the result should be analyzed on a per implementation basis.
+In addition, the result in Scenario 3 does not necssarily imply the attention mechanism is not very efficient, since the core attention operation does not include tunable parameters.
+What the result indicates is that the weight of the transformation operation before the attention operation (also implemented in the attention stage of the pipeline) has less impact on the prediction compare to others.
+[how to interpret this from NLP perspective]
 
@@
 
-A:
+A: []
 
-Q, In Section 4, the paper indicates that the system is developed under a long-term collaboration with NLP experts, but there is no description describing the details of the collaboration (the number of experts, the length and the form of the collaboration, the frequency of the meetings).
-It?s not until Section 7 did I learn that there are 2 NLP experts in collaboration.
+Q3, In Section 4, the paper indicates that the system is developed under a long-term collaboration with NLP experts, but there is no description describing the details of the collaboration (the number of experts, the length and the form of the collaboration, the frequency of the meetings).
+It's not until Section 7 did I learn that there are 2 NLP experts in collaboration.
 The task analysis can also be improved by including more detailed justification of the three tasks.
@@
 
-Q The presentation of the system design in Section 5 could be improved.
+Q4, The presentation of the system design in Section 5 could be improved.
 - In Section 5.2, Attention View include both a bipartite graph and a matrix view, which visualize the same information.
@@
 
-A:
+A: The advantage of the bipartite graph is not only the ability to allow the domain experts quickly understand the domain alignment but more importantly the corresponding words.
+However, in the matrix view, it is much harder to instantaously link the alignment with the corresponding words.
+[We update the text to better reflect this point]
 
-Q, It's unclear how the simplification of attention representation is done from Section 5.2, please include more details.
+Q5, It's unclear how the simplification of attention representation is done from Section 5.2, please include more details.
 
@@
 
-Q, In Section 5.3, how do you compute the density contour? Why is a contour needed in the analysis?
+Q6, In Section 5.3, how do you compute the density contour? Why is a contour needed in the analysis?
 
@@
 
-Q, It's better if the authors present the relation between Section 5.3 and 5.4 in a clearer way.
+Q7, It's better if the authors present the relation between Section 5.3 and 5.4 in a clearer way.
 It?s confusing to read how one can perturb a prediction in Section 5.3 before he/she read the algorithm in Section 5.4.
@@
 
-Q Except for the presentation issue, the contribution of this paper is somewhat limited to only NLI models with attention mechanisms.
+Q8, Except for the presentation issue, the contribution of this paper is somewhat limited to only NLI models with attention mechanisms.
 It's not sure how the visualization can be easily extended for other NLP tasks.
@@
 
-Q, In addition, the perturbation-driven scheme is somewhat related to the gradient-based analysis (both are the local analysis of the model on a specific prediction).
+Q9, In addition, the perturbation-driven scheme is somewhat related to the gradient-based analysis (both are the local analysis of the model on a specific prediction).
 It is better if the authors discuss the two and differentiate them.
@@
 
-Q, The evaluation is acceptable but a bit weak.
+Q10, The evaluation is acceptable but a bit weak.
 There is no description of what questions have the authors asked during the evaluation sessions.
@@
 
-Please also proofread the work and fix typos.
+Q11, Please also proofread the work and fix typos.
 For example, the word 'work' in Section 3 should be uncountable; In Section 5.3, "the three points defines a triangle" -> "the three points defining a triangle"
@@
 
-Q, A brief guidance of how to interpret visual patterns that emerge in each view would be very beneficial.
+Q12, A brief guidance of how to interpret visual patterns that emerge in each view would be very beneficial.
 In particular, did the authors notice any systematic / repetitive patterns in the triangular prediction view?
@@
 
-A:
+A: [grouping pattern]
 
-Q, Same thing applies to the attention heatmap, the parameter histograms, and the overview scatterplots in Figure 8 (e.g. does the curve in Figure 8d tell us something?)
-- Discuss scalability of the system. Can it visually handle long sentences? Would collapsing the heatmaps help here?
+Q13, Same thing applies to the attention heatmap, the parameter histograms, and the overview scatterplots in Figure 8 (e.g. does the curve in Figure 8d tell us something?)
 
@@
 
-Q, Can it handle a large number of sentences? This is important for the noted future applicability to question answering where the data items can be as large as text documents.
+Q14, Discuss scalability of the system.
+Can it visually handle long sentences?
+Would collapsing the heatmaps help here?
+Can it handle a large number of sentences?
+This is important for the noted future applicability to question answering where the data items can be as large as text documents.
 
-Q, Explain more about the Bowman's dataset in use [24], its dimensionality, coverage, complexity, language features, etc.
+A: The collasping will have visually handle long sentences, however, different collasping strategy
 
-Q, A brief discussion of the applicability to other languages would be interesting maybe? Any anticipated challenges?
+Q15, Explain more about the Bowman's dataset in use [24], its dimensionality, coverage, complexity, language features, etc.
 
@@
 
-Q, Add label to the color scale in Figure 3 (the caption mentions attention by just to avoid confusion). Same for Figure 7a (frequency to the vertical axis), Figure 8b, and Figure 9a-c.
+Q16, A brief discussion of the applicability to other languages would be interesting maybe? Any anticipated challenges?
 
@@
 
-Q, Add narration to the video and maybe include a 1-min self-contained demo of the system before illustrating the use cases in the video.
+Q17, Add label to the color scale in Figure 3 (the caption mentions attention by just to avoid confusion). Same for Figure 7a (frequency to the vertical axis), Figure 8b, and Figure 9a-c.
 
@@
 
-Q, Language mispredictions (misspelling):
+Q18, Add narration to the video and maybe include a 1-min self-contained demo of the system before illustrating the use cases in the video.
+
+A:
+
+Q19, Language mispredictions (misspelling):
 As discussion in [8, 13]
@@
 
-Q, After the teaser image, the paper spends the first four pages on neural networks, NLP, and inference.
+Q20, After the teaser image, the paper spends the first four pages on neural networks, NLP, and inference.
 One has to look hard to detect the lede in the next to last paragraph of the introduction ("Moreover, we propose...") Highlight it!
@@
 
-Q, Even as a visualization-centric researcher who is aware of NNs and has done a little direct work in NLP, I found it hard to connect to the organization and balance of coverage of these topics in the paper.
+Q21, Even as a visualization-centric researcher who is aware of NNs and has done a little direct work in NLP, I found it hard to connect to the organization and balance of coverage of these topics in the paper.
 Despite the prominent teaser visualization and the description of individual views in section 5, the paper comes off as very visualization-light.
@@
 
-Q,For each view there it's clear what the visual representation is, but the majority of description is dedicated to the underlying mechanics of calculating and thinking about the NL inference.
+Q22,For each view there it's clear what the visual representation is, but the majority of description is dedicated to the underlying mechanics of calculating and thinking about the NL inference.
 The specific interactions involved are also mostly implied, although I was able to deduce them.
@@
 
-Q, More importantly, there is little rationale for the visual representation designs of the various views.
+Q23, More importantly, there is little rationale for the visual representation designs of the various views.
 The design choices do make sense (at least to an experienced visualization designer) but there are alternatives in each case.
@@
 
-Q, Part of the problem is that the language is very dense in this paper.
+Q24, Part of the problem is that the language is very dense in this paper.
 Although the grammar is acceptable, it was a slow read and there were some passages that I found all but indecipherable, such as the figure 7 caption, the last paragraph of section 5.5, and the bullet list at the end of the introduction.
@@
 
-Q, There were many small errors that need correcting, too many to bother listing here.
+Q25, There were many small errors that need correcting, too many to bother listing here.
 There was also some hyperbole ("stunning", "unprecedented", "vision", "paradigm") that distracts me as a serious reader and should be replaced.
@@
 
-Q, The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination.
+Q26, The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination.
 The scenarios essentially describe individual tasks that experts might perform in individual views.
@@
 
-Q: The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.
+Q27, The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.
 
@@
 
-Q, I was confused by the distinction between image networks and language networks.
+Q28, I was confused by the distinction between image networks and language networks.
 CNNs are not only used to make binary classifications, and there are certainly challenges in image networks that do not provide ?clear meaning?
@@
 
-Q, It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs.
+Q29, It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs.
 If it?s the former (as it seems to be), then I think this needs to be emphasized in the introduction.
@@
 
-Q, I appreciated the task analysis in section 4.
+Q30, I appreciated the task analysis in section 4.
 However, it seems a bit too brief, and the tasks don?t seem to directly follow from the description of the authors experience with the NLP researchers.
@@
 
-Q, Work by Ma et al.
+Q31, Work by Ma et al.
 ("Visualizing dynamic brain networks using an animated dual-representation?
@@
 
-Q, Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4).
+Q32, Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4).
 I wonder if it would make sense to use other types of annotations here, such as those created from event extraction tools or information extraction tools that would highlight other structures (besides grammar/POS) that could be useful in helping understanding the inference model.
@@
 
-Q, In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile?
+Q33, In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile?
 with ?heap?).
@@
 
-Q, Section 6.3 is very interesting, but I don?t understand why perturbing the attention stage has less of an effect that the other perturbations.
+Q34, Section 6.3 is very interesting, but I don't understand why perturbing the attention stage has less of an effect that the other perturbations.
 This seems like a preliminary contribution in and of itself (i.e., that using the NLIZE application leads to global understanding such as this), and worthy of further examination.
@@
 
-Q, The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach.
+Q35, The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach.
 It might make more sense to focus more on only one or two scenarios and cover them in more depth.
 
-A:
+A: [additional discussion of]

### 2018-06-14 paper/itemizedReviewResponse.tex
update question list

@@
 Q2
+
+- Why treemap for prediction summary, what about the heatmap matrix
 
@@
 
-A:
+A: The introduction, related works, and background took first three pages.
+The task analysis which is an essential part of a given visualization system is started on page 4.
+The text following "Moreover, we propose..." is not the only visualization contributions, to better convey the core visualization contributions, [we update the intro to highlight the visualization components],
 

### 2018-06-14 paper/itemizedReviewResponse.tex
update question

@@
 
-- Why treemap for prediction summary, what about the heatmap matrix
+- Why treemap for prediction summary, what about the heatmap matrix, confusion matrix, showing errors
 
-R1:
+- is perturbation contribution, learned perturbation, user perturbation (part of interactive system)
+
+R1(3):
 + interesting topic
@@
 
-R2:
+R2 (5):
 + important area for visualization research
@@
 
-R3:
+R3 (2.5):
 - article is dense and difficult to read
@@
 - core contributions are not highlighted, too much emphasis on background material (explanation of NLI), not enough on the visualization system itself
-- claims based on user evaluation aren?t supported
+- claims based on user evaluation aren't supported
 
@@
 
+Refer to review 4, Q34, for NLP expert to explore
+[figure 10, gradient based update, attention operation is not tunable parameter]
 A: The separation between different stages is based on the specific model implementation, so the result should be analyzed on a per implementation basis.
@@
 
-A: []
+A: [not formal definition]
 
@@
 
-A:
+A: [mention NLP experts early on]
 
@@
 
+[highlight ]
 A: The introduction, related works, and background took first three pages.
@@
 
-A:
+A: self-contained information, technical detail drive visualization
 
@@
 
-A:
+A: Clarify in the intro, input modality different, very often CV have human interpretable neuron filter, in NLP such often not,   attention is the exception,
 
@@
 
-A:
+A: agree, point out the interesting direction [graph anotation] linear + graph structure
 
@@
 
-A:
+A: NLP question, further explore NLP
 

### 2018-06-18 paper/application.tex
add discussion

@@
 %In this section, we discuss application scenarios, in which the domain experts utilize the
-To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios (first three roughly correspond to \textbf{T1-3}) gathered by the domain experts who integrated the proposed tool into their analysis workflow.
+To illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model,
+\shusen{we present five interconnected application scenarios a domain expert may employ in their analysis workflow.
+For example, the users can start the exploration by examining the stability of prediction (Scenario 1), from which they may identify the individual instances worth further investigation (Scenario 2, 3, 4).
+Alternatively, the user can also start with handcrafted common/extreme cases (Scenario 5) and further the exploration based on the instantaneous feedbacks provide by the visualization tool.
+}
+%we present five application scenarios
+%(first three roughly correspond to \textbf{T1-3}) gathered by the domain experts who integrated the proposed tool into their analysis workflow.
 
@@
 %
-In other words, the updating of the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder stage of the model.
-Similar observations can be obtained for most examples we have experimented with.
+%In other words, the updating of the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder stage of the model.
+%Similar observations can be obtained for most examples we have experimented with.
+\shusen{
+To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
+In our case, the result indicates that the tunable parameters of the attention stage (the transformation before the alignment operation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
+The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
+However, this result does not necessarily imply the limitation of attention mechanism as the core alignment computation does not have tunable parameters that can be modified by the proposed optimization.
+}
 %The attention layer is less sensitive compared to encoding layer and classification layer.

### 2018-06-18 paper/itemizedReviewResponse.tex
update response to review 2

@@
 
-Response to the summary:
+Summary of major changes:
+1. Revise section 6 to better convey the relationship between the different senarios and provide further clarification on the result observered in 6.3
 
@@
 
-Refer to review 4, Q34, for NLP expert to explore
-[figure 10, gradient based update, attention operation is not tunable parameter]
-A: The separation between different stages is based on the specific model implementation, so the result should be analyzed on a per implementation basis.
-In addition, the result in Scenario 3 does not necssarily imply the attention mechanism is not very efficient, since the core attention operation does not include tunable parameters.
-What the result indicates is that the weight of the transformation operation before the attention operation (also implemented in the attention stage of the pipeline) has less impact on the prediction compare to others.
-[how to interpret this from NLP perspective]
+A: To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
+In this case, the result indicates that the tunable parameters of the attention stage (the transformation before the alignment operation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
+The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
+However, this result does not necessarily imply the limitation of attention mechanism as the core alignment computation does not have tunable parameters that can be modified by the proposed optimization.
+We revised section 6.3 to clarify this point.
 
@@
 
-A: [not formal definition]
+A: The exact computation of attention can vary from model to model, though the overall concept is shared as they are specially designed for understanding the corresponding relationship between sequence of texts.
 
@@
 
-A: [mention NLP experts early on]
+A: We had added additional details of the collobration in the begining of the section 4, include the number of NLP collaborators, frequency, duration of the meeting for this specific tasks.
 
@@
 
-A:
+A: The simplification is achieve by collapsing the dependency tree structure.
+We assume by focusing on the more important grammar structure, we can remove the decorative words and the reduce sentence length to focus on the more crucial part of the sentences.
 
@@
 
-A:
+A: We employed the standard kernel density estimation technique in 2D.
+As stated in Section 5.3, the primary motivation is to highlight overlaped point (where multiple prediction fall on top of each other) and identify outliers.
 
 Q7, It's better if the authors present the relation between Section 5.3 and 5.4 in a clearer way.
-It?s confusing to read how one can perturb a prediction in Section 5.3 before he/she read the algorithm in Section 5.4.
+It's confusing to read how one can perturb a prediction in Section 5.3 before he/she read the algorithm in Section 5.4.
 I suggest put the algorithm along with the perturbation-driven paradigm at the beginning of Section 5.
 
-A:
+A: Thanks for catching the ordering problem and providing a soluation.
+To address the problem, we add references to the optimization discussed in section 5.4 in the beginning of section 5 as well as in section 5.3.
+We didn't move all the optimization discussion in the beginning of the section 5, because we believe that presenting details of the all three perturbations (input, attention, prediciton) without any discussion about the interface can also be confusing.
+And the separation between the operation and UI componenet may also make the description hard to read (requre the reader to refer back to the computation discussion while describing the user interface)
 
@@
 
-A: The composability of the system is the key to extend its capability
+A: The composability of the system is the key to extend its capability.
+The proposed API allow user to include only the panel that is necessary for the given task.
+For new task (i.e., machine translation), we do not need to include the prediction view for NLI task.
+We can reuse the attention view to representating the alignment between the original sentence and the translated sentence and introduce new panel for visualizing other information that may not present in the NLI model.
+However, the main idea is to allow use the combine the panels/functionality to suit their goals.
 
@@
 
-A: connection with sensitivity analysis
+A: Gradient-based sensitivity analysis can often be carried out for domain that is differentiable (i.e., image pixel values), however, for natural language sentences these techniques often can not directly be adopted directly.
+[??
+add the discussion to where?]
 
@@
 
-A:
+A: We didn't design a specific list tasks and answers due to the exploratory nature of system as well as the open ended analysis goal.
+If the user didn't follow the particular exploration path the designer of the question goes, it may find some unexpected result that may not directly corresponds to the "correct" answer, but view the problem from a different perspective.
+However, to properly evaluation the proposed technique is extremely important, so we plan to recurite more domain experts to test and evaluation the system in the new future.
 
@@
 
-A:
+A: Thanks for pointing out the grammar issues, we have fixed the mentioned problem. And the renew version has been through a thorough copy edit pass by an editor.
 

### 2018-06-18 paper/evaluation.tex
update response to review 2

@@
 \section{Evaluation and Feedback}
-The motivation for designing the proposed tool is the error analysis challenges faced by our long-term collaborators working on natural language inference research.
+%The motivation for designing the proposed tool is the error analysis challenges faced by our long-term collaborators working on natural language inference research.
 During the entire design and development process, we worked closely with two NLP experts, and their constant evaluation and feedback have helped shape the tool we see today.
 %
-Since these two NLP experts have been heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.
+As discussed previously, we have worked closely with NLP experts during the development of the tool.
+However, since these two NLP experts have been heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.
 To uncover the limitation and identify areas for improvement, we gathered a wider audience from either visualization (4 researchers, including 3 Ph.D.-level students and one postdoc researcher) or NLP backgrounds (5 Ph.D.-level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.

### 2018-06-18 paper/overview.tex
update response to review 2

@@
 %
-As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (i.e., adjust the prediction by making updates to the model).
+As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (i.e., adjust the prediction by making updates to the model, the optimization is disucssed in Section~\ref{sec:pipeline}).
 %

### 2018-06-18 paper/prediction.tex
update response to review 2

@@
 
-To perturb the prediction (\textbf{T3}), we need a way to communicate the reassignment of the predicted label.
+To perturb the prediction (\textbf{T3}) (optimization for solving the prediction perturbation is discussed in Section~\ref{sec:pipeline}), we need a way to communicate the reassignment of the predicted label.
 As illustrated in Fig.~\ref{fig:predictionView}(b), we integrate such an operation in the prediction view.

### 2018-06-18 paper/relatedWorks.tex
update response to review 2

@@
 %
-Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications.
+Besides the techniques designed for specific types of models, a few work~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications.
 In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understand snapshot of the classifier near a specific input.

### 2018-06-18 paper/task.tex
update response to review 2

--- 2018-03-31 paper/task.tex
@@
 In this section, we examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
-Then, we distill the numerous discussions with domain experts into concrete tasks, which guide the design and implementation of the proposed tool.
 
-During our long-term collaboration with NLP experts, we have conducted extensive discussions to understand the common approach employed by researcher for assessing the behavior of a model.%
+\shusen{
+The primary motivation for designing the proposed tool is the error analysis challenges faced by our long-term collaborators working on natural language inference research.
+During the entire design and development process, we worked closely with two NLP experts via weekly meetings in a period of roughly six month (however, our previous collaborations extends well beyond this period), their constant evaluation and feedback have helped shape the tool we see today.
+}
+%Then, we distill the numerous discussions with domain experts into concrete tasks, which guide the design and implementation of the proposed tool.
+During our long-term collaboration with two NLP experts, we have conducted extensive discussions to understand the common approach employed by researchers for assessing the behavior of a model.% as well as provide feedback on the various prototyping stages of the proposed visualization.%
 The predictive accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model; however, the accuracy number alone does not provide the full story.

### 2018-06-19 paper/itemizedReviewResponse.tex
update response

@@
-Summary Review
+Response to the reviews
 
-Reviewers were split on whether or not to accept the paper.
-R2 and R4 rated the paper very highly (5 and 4.5), while R1 and R3 gave lower scores of neutral or weak reject (3 and 2.5).
-As the scores average to 3.75, and because the primary and secondary reviewers are in agreement, we are advocating for an "Accept".
-
-However, the authors should pay careful attention to the comments by reviewers, and use the time remaining before the next version is due to revise the paper for clarity, to emphasize the main contributions of the paper, to provide rationale for the design choices, to provide more detailed information about the domain-expert collaborators, and to better justify the results of the task analysis.
-Some reviewers advocated for reducing the number of usage scenarios and providing a more in-depth examination of a single scenario, or a scenario composed of a series of sub-investigations.
-On the other hand, other reviewers found the breadth of potential analyses to be a positive component of the paper.
-
-///// for discussion ////
-- How to interpret MIRA show attention has less impact
-Q1,
-
-- Formal definition for attention
-Q2
-
-- Why treemap for prediction summary, what about the heatmap matrix, confusion matrix, showing errors
-
-- is perturbation contribution, learned perturbation, user perturbation (part of interactive system)
-
-R1(3):
-+ interesting topic
-+ usage scenarios are interesting
-- description of NLP NN and attention models are not sufficiently detailed in the paper
-- details of collaboration with domain experts are missing
-- justification of tasks are not sufficiently detailed
-- differences between graph and matrix view should be explained in more detail
-- density contour in the prediction view needs to be explained in more detail
-- claims about extension of visualization system to non-NLI tasks is not supported
-- need to clarify difference between proposed perturbation-driven analysis and gradient-based analysis
-- qualitative evaluation is weak
-
-R2 (5):
-+ important area for visualization research
-+ article is well-written
-+ application with linked views is well-designed and powerful
-+ system supports debugging of inference models
-- scalability of system is not discussed
-
-R3 (2.5):
-- article is dense and difficult to read
-- rationale for design choices are not clear
-- core contributions are not highlighted, too much emphasis on background material (explanation of NLI), not enough on the visualization system itself
-- claims based on user evaluation aren't supported
+We greatly appreciate all reviewers' valuable comments. The summary of major changes are listed below. We have itemized the 35 questions/comments and answer each individually.
 
@@
 
-A: The collasping will have visually handle long sentences, however, different collasping strategy
+A: The key rational for collasping the sentence to reduce the length while still preserving the main structure of the sentence.
+Therefore, the collasping operation will greatly improve the scability of the show a long sentence.
+However, it may not suitable for a whole paragraph (multiple sentence), when the length of collapsed sentence can still be too long to be effectively represented in the matrix or biparite graph view.
+For task such as machine comprehension, in which the context paragraph and be extremely long, we likely will need a hierarchical type of structure.
 
@@
 
-A:
+A: Since we utilize unicode text representation through out the code, the proposed system can be easily adapting to other aphateical language (however, we have not test the capability).
+One potential challenge may originated from NLP training set, as there are not as many large scale training data in language other than english.
 

### 2018-06-19 paper/itemizedReviewResponse.tex
update response to review 4

@@
 
-A: We didn't design a specific list tasks and answers due to the exploratory nature of system as well as the open ended analysis goal.
+A: We didn't design a specific list tasks and the corresponding answers due to the exploratory nature of system as well as the open ended analysis goal.
 If the user didn't follow the particular exploration path the designer of the question goes, it may find some unexpected result that may not directly corresponds to the "correct" answer, but view the problem from a different perspective.
@@
 
-A: [grouping pattern]
+A: As discussed in the experiment of section 6.1, the spread of the pattern directly corresponds to the stability of the prediction.
+A recurring pattern we noticed is illustrated in Fig.
+9(d), where the given sentence pair have low stability due to the fact the original prediction is a boundary prediction (probability is in between two classes).
+In addition, the perturbation procedure will also affect the pattern as longer sentence will likely have more perturbed variations (contains more nouns and verbs).
+We include a brief discusison on the potential variability caused by the perturbation procedure in section 5.4.
 
@@
 
-A:
+A: The curve pattern in the Figure 8d are likely cause by the different number of words that was perturbed (i.e., each line pattern corresponds to sentence pair that include the same number of nouns and verbs that to be perturbed).
+This illustrate the additional variation the perturbation bring into the system.
+We include a brief discusison on the potential variability caused by the perturbation procedure in section 5.4.
 
@@
 
-A:
+A: The SNLI dataset (https://nlp.stanford.edu/projects/snli/) includes "570k human-written English sentence pairs manually labeled for balanced classification with the labels entailment, contradiction, and neutral".
+Therefore, it does not have direct connection to the word embedding dimension or language features.
+It is a benchmark dataset for natural language processing task, which can be attacked by different type of models.
+In our case, we investigated a neural network based approach.
 
@@
 
-A:
+A: We've added caption "attention" to the color scale as well as the "frequency" captions to the histograms.
 
@@
 
-A:
+A: We add an introduction section to illustrate the NLP problem and interface. We also include voice over to better convey the contains.
 

### 2018-06-19 paper/prediction.tex
update response to review 4

@@
 % The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
-A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+A density contour of the prediction is computed via kernal density estimation to emphasize the highly cluttered areas and distinguish the outliers.
 As illustrated in (b), the predicted label does not match the ground truth. Therefore, we apply a label reassignment operation, which triggers a model update.
+\shusen{
+The prediction spread pattern of the perturbed pairs directly convey the stability of the model for the given instance.
+However, we should also take the length of the sentence into consideration as more nouns and verbs will lead to more perturbed inputs.
+}
 % when press and drag the circle (prediction), the user is presented with the three option corresponds to the labels. The dotted line and arrow indicate the newly assigned label.

### 2018-06-19 paper/itemizedReviewResponse.tex
update intro

@@
 
-[highlight ]
-A: The introduction, related works, and background took first three pages.
-The task analysis which is an essential part of a given visualization system is started on page 4.
-The text following "Moreover, we propose..." is not the only visualization contributions, to better convey the core visualization contributions, [we update the intro to highlight the visualization components],
+A: We have revise the last paragraph of the introduction to highlight the visualization contributions.
+The text following "Moreover, we propose..." is not the only place describe visualization contributions, the integrated model pipeline that allow user perturbation in all stages is another contribution, the same holds for the visual encoding for the prediction for the NLI problem.
 
@@
 
-A: self-contained information, technical detail drive visualization
+A: We appreciated the reviewer concern as organizing a visualization paper for a domain specific application is a very challenge task.
+The rational for our current orgnaiziation is that the NLP background provides the minimally necessary information for the average reader to understand the application problem.
+It is an essential part of the paper which make it self-contained.
+In addition, a lot of the technical details is directly connected to how the visualization encoding is designed (such as the attention view and prediction view).
+Without a highlevel understanding of the model, it would be impossible for the reader to understand the purpose of most views and the application senarios.
+Finally, we also try to compress the background information, we spend less than one page on the background, even through other sections mentioned NLP related topics but they mostly still focus on presenting the visualization system.
 
@@
 
-A:
+A: The biggest benefit of the graph is the ability for the domain expert to directly see the connection between words.
+In the matrix, one need to first identify the high value entry and then finding the corresponding row and column to identify the words.
+If there are multiple correspondence, the user need to check one by one.
 
@@
 
-A:
+A: We agree that a 3x3 heatmap (confusion matrix) is also an efficient alternative to represent the summary prediction result.
+The motivation is use treemap is that it provides a more direct encoding for conveying the count (area instead of variation of colors).
+And the separate between orange and green tile intuitively convey the correct and incorrect predictions.
+However, we do think a confusion matrix like encoding could also be beneficial.
+In the future, we plan to add the confusion matrix as an alternative, so the user can use either one of them based on their preference.
 
@@
 
-A:
+A: These sections has been revised to improve the readability.
 
@@
 
-A:
+A: These different senarios should naturally arise during the exploration session, the senarios 1 is often the first step to identify the sentence pair of interests (the user can also manually type the one they interested in senarios 6).
 
@@
 
-A:
+A: We have revised the video and include voice over and an simple introduction in the begninning.
 

### 2018-06-19 paper/intro.tex
update intro

@@
 Instead of viewing the models as invariant objects, we approach the interpretability challenge by studying them in a dynamic environment.
-By employing a perturbation-driven paradigm, we probe the internal states of the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provides a new perspective to address the model interpretation problem.
+By employing a perturbation-driven scheme, we probe the internal states of the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provides a new perspective to address the model interpretation problem.
 
@@
   % \item Distill the visualization tasks for making sense of the role of attention in natural language inference (section~\ref{sec:task});
-    \item A perturbation-driven exploration paradigm derived from close examination of how domain experts conduct exploratory analysis on end-to-end NLP neural network models;
+    \item A perturbation-driven exploration scheme derived from close examination of how domain experts conduct exploratory analysis on end-to-end NLP neural network models;
 
-    \item The NLIZE system that enriches such a paradigm by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback; 
+    \item The NLIZE system that implements the perturbation exploration scheme by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback;
     %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;

### 2018-06-20 paper/itemizedReviewResponse.tex
update response letter

@@
 Q28, I was confused by the distinction between image networks and language networks.
-CNNs are not only used to make binary classifications, and there are certainly challenges in image networks that do not provide ?clear meaning?
-and seem like they would also benefit from the proposed work.
+CNNs are not only used to make binary classifications, and there are certainly challenges in image networks that do not provide "clear meaning" and seem like they would also benefit from the proposed work.
 In other words, I understand the focus on NLP tasks, but the reasoning for it doesn't seem accurate (in the 3rd paragraph of the introduction).
 
-A: Clarify in the intro, input modality different, very often CV have human interpretable neuron filter, in NLP such often not,   attention is the exception,
+A: In the introduction we want to highlgith the input modality different.
+Continuous for image, and discrete for natural language.
+The different has introduced additional challenge especially regarding optimization as well as interpretation.
+In addition, in CNN we often can reveal human interpretable neuron filter, but these method has been generalized for NLP.
+The attention is the exception, which represent often the only interpretable part of the model.
 
 Q29, It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs.
-If it?s the former (as it seems to be), then I think this needs to be emphasized in the introduction.
+If it's the former (as it seems to be), then I think this needs to be emphasized in the introduction.
 
-A:
+A: The perturbation of nous and verbs on itself is not novel from NLP perspective, and truly solving the challenge of producing grammarly correct and meaningful perturbation/paraphrasing is still an open research area.
+In our case, we believe the novality come from the integration of the model with the three stage perturbation scheme in an explorable visual analytic system.
 
 Q30, I appreciated the task analysis in section 4.
-However, it seems a bit too brief, and the tasks don?t seem to directly follow from the description of the authors experience with the NLP researchers.
+However, it seems a bit too brief, and the tasks don't seem to directly follow from the description of the authors experience with the NLP researchers.
 The scenarios described in Section 6 provide much more detail about these tasks, and Section 5 clarifies them as well, but a bit more detail here would be useful.
@@
 
-A:
+A: In the current system, we did not record the user interaction/correction result.
+The mira optimization update may correct the model for the given example (to some extend overfit to the example), however, we don't think there is guarantee that the fix can be easily generalized to other examples.
+In addition, the ambiguity between pile and heap may also originated from the word embedding (the input numerical representation for words).
+What the proposed system do is to communicate to the NLP experts that the ambiguity between pile and heap is likely the cause of the wrong prediciton.
+The experts can chose to dive further and examine the problem with their NLP background.
 
@@
 
-A: [additional discussion of]
+A: We added a overview in the begining of the section 6 to illustrate how different tasks related to one another and provide addtional discussion on section 6.3.

### 2018-06-20 paper/intro.tex
update response letter

@@
 
-Compared to image classification tasks, natural language processing (NLP) systems have innate restrictions (e.g., the discrete nature of words) that make the road to interpretation even more challenging.
+Compared to image classification tasks, natural language processing (NLP) systems often involve additional challenges such as the discrete nature of words.
 For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) captures, cannot be readily generalized to natural language.
-An image (pixel values) represents a continuous solution space, in which human can quickly recognize the existence (or the absence) of patterns or shapes.
-For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.
+\shusen{
+An image (pixel values) corresponds to a continuous solution space. which is more accessable for optimization and human visual recognation (i.e., the existence or the absence of patterns).
+For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.}
 %

### 2018-06-20 paper/itemizedReviewResponse.tex
finish response to review 4

@@
 
-A:
+A: We moved the description of the collabration into the beginning of section 4, in which we describe the number of NLP experts, frequency, and the duration of the meeting for this specific projects.
+We also add pointer to application senarios that corresponds to the tasks to instantiate the more abstract concepts.
 
 Q31, Work by Ma et al.
-("Visualizing dynamic brain networks using an animated dual-representation?
-from EuroVis 2015) is work related to NLIZE having both graph and matrix views that complement each other and provide the same information from different perspectives, as described in Section 5.2.
+("Visualizing dynamic brain networks using an animated dual-representation" from EuroVis 2015) is work related to NLIZE having both graph and matrix views that complement each other and provide the same information from different perspectives, as described in Section 5.2.
 
-A:
+A: We've citated this work in Section 5.2 when discussing the due visual representations.
 
@@
 Work by Forbes et al.
-supports the use of semantic hypergraphs to provide richer textual annotations alongside text sequences ("Text annotation graphs: Annotating complex natural language phenomena?
-from LREC 2018).
+supports the use of semantic hypergraphs to provide richer textual annotations alongside text sequences ("Text annotation graphs: Annotating complex natural language phenomena" from LREC 2018).
 
-A: agree, point out the interesting direction [graph anotation] linear + graph structure
+A: After discussing with domain experts, they believe this would be a very interesting direction for future works.
+Coming up with efficient visual encoding for these type of information they go beyond grammar tree is a challenge on its own.
+For example the extract structure can be graph, which likely require a complete redesign of the annotation visualization.
 
@@
 
-A: NLP question, further explore NLP
+A: As discussion in the answer for Q1, the core attention operation is not tunable, only the intial transformation in the beginning of the attention stage includes tunable parameters.
+This can partially explain the result.
+However, the domain experts mentioned they are interested in exploring more from NLP perspective to understand this result fully.
 

### 2018-06-20 paper/attention.tex
finish response to review 4

@@
 The matrix attention view (Fig.~\ref{fig:attentionVis}(b)), despite being more verbose and less efficient in highlighting the dominant alignment, does not have similar shortcomings.
-Together, the graph and matrix views complement each other and provide the same information from different perspectives.
+Together, the graph and matrix views complement each other and provide the same information from different perspectives (a similar due space visualization is presented in \cite{MaKenyonForbes2015} for studying brain network).
 As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.

### 2018-06-20 paper/task.tex
update intro
finish response to review 4

@@
 Moreover, by introducing new visual encodings and summarizations, we can drastically expand the ways domain experts interact with the model, enable exploration options that previously were not possible either due to tedious manual operation or the lack of communication channels.
-
-%Through many rounds of discussions with NLP experts,
+%
 %In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
 %
-To support the exploratory workflow for analyzing NLI models, we need to address the following tasks.
+\shusen{
+To support the exploratory workflow for analyzing NLI models,
+we aim to address the following tasks based on our extensive discussions with NLP experts.
+}
 
 \begin{itemize}
-
     \item \textbf{T1}: Understand the stability of a prediction, i.e., how perturbations of the input affect the behavior of the model?
@@
     \item \textbf{T3}: When the predicted label is wrong, how can we update the model to correct the prediction? What are the effects of updating different parts of the model?
+\end{itemize}
+
+In Section~\ref{sec:caseStudy}, we will discussion in detail how we can use the proposed tool to address these tasks. The application Senarios 1,2,3 corresponds to \textbf{T1-T3}, respectively.
 
@@
 
-\end{itemize}
 %Through many rounds of discussions with NLP experts,

### 2018-06-21 paper/itemizedReviewResponse.tex
finish review 3 response

@@
 
-A:
+A: [We've revised descriptions to make interaction more explicit. TODO]
 
@@
 
-A:
+A: One can expand the text box to include multiple line to show the longer sentence. There is no special encoding here, since we are just showing the raw text.
 
@@
 
-A: The biggest benefit of the graph is the ability for the domain expert to directly see the connection between words.
+A: If the sentence structures are drastically different, the matrix view may have benefit as the structure difference likely result in crossed lines in the biparite graph view, which can lead to poorer perception.
+The biggest benefit of the graph is the ability for the domain expert to directly see the connection between words.
 In the matrix, one need to first identify the high value entry and then finding the corresponding row and column to identify the words.
-If there are multiple correspondence, the user need to check one by one.
+If there are multiple correspondences, the user need to check them one by one in the matrix view.
 
@@
 
-A:
+A: For the given model there are two attention matrices, one have row normalization while the other have column normalization.
+We follow the same rule to apply renormalization after sentence collapsing.
 
@@
 
-A:
+A: The amount of necessary reduction is influenced by the structure of the sentences as well as the capability of the parser.
+There is a trade-off between visual clutter and text readability.
+The more collapse is equal to less visual clutter, but likely reduce the readability of the text.
+The From our experiment, we notice the NLP experts have far better ability to understand the collapsed sentence compared to others.
+The desired level should be a good trade-off based on the experts preference.
 
@@
 
-A:
+A: We make sure to only compute the comparison when the two matrices are of same size and utilizing the same normalization pattern.
 
@@
 
-A:
+A: There are two rational to design the re-assignment as drag.
+Firstly, the semantic of changing prediction corresponds well to a drag operation.
+We intially plan to implement the re-assignment as a continuous drag operation.
+However, we believe it is more meaningful for human to assign discrete label (instead of a probability).
+Secondly, we want to distingish this action with click which is already reserved for selection operation.
 
@@
 
-A:
+A: The number of points in the prediction view is limited by the number of perturbations per sentence pair.
+In another work, we will only look at one sentence pair at a time for the detailed analysis.
+The motivation for including the density contour is to help convey the overlapping information.
 
@@
 
-A:
+A: The MIRA optimization process indeed introduces unpredibility and opaqueness in the solution.
+To mitigate the limitation, we provide summary of the paramter changes in the pipeline view to help reveal the effect of the optimization on the parameter.
+Morever, we can also utilizing the attention visualization to interpret the effect the optimiztion.
+Finally, compared to a end-to-end neural network (which is often referred to as a blackbox) this optimization has a more restricted setting as we are only fitting the model to the given example instead of jointly optimizing for the entire dataset.
 
@@
 
-A: We agree that a 3x3 heatmap (confusion matrix) is also an efficient alternative to represent the summary prediction result.
+A: We agree that a 3x3 heatmap (essentially a confusion matrix) is also an efficient alternative to represent the summary prediction result.
 The motivation is use treemap is that it provides a more direct encoding for conveying the count (area instead of variation of colors).
@@
 
-A: We have revised the video and include voice over and an simple introduction in the begninning.
+A: We have revised the video and included voice over and a simple introduction in the begninning.
 

### 2018-06-21 paper/itemizedReviewResponse.tex
spelling pass

--- 2018-06-20 paper/itemizedReviewResponse.tex
@@
 Summary of major changes:
-1. Revise section 6 to better convey the relationship between the different senarios and provide further clarification on the result observered in 6.3
+1. Revise section 6 to better convey the relationship between the different scenarios and provide further clarification on the result observed in 6.3
 
@@
 
-A: The exact computation of attention can vary from model to model, though the overall concept is shared as they are specially designed for understanding the corresponding relationship between sequence of texts.
+A: The exact computation of attention can vary from model to model, though the overall concept is shared as they are specially designed for understanding the corresponding relationship between the sequence of texts.
 
@@
 
-A: We had added additional details of the collobration in the begining of the section 4, include the number of NLP collaborators, frequency, duration of the meeting for this specific tasks.
+A: We had added additional details of the collaboration at the beginning of section 4, including the number of NLP collaborators, frequency, duration of the meeting for this specific tasks.
 
 Q4, The presentation of the system design in Section 5 could be improved.
-- In Section 5.2, Attention View include both a bipartite graph and a matrix view, which visualize the same information.
+- In Section 5.2, Attention View includes both a bipartite graph and a matrix view, which visualize the same information.
 From the description of the paper, the graph view is only good for highlighting the most dominant alignments.
@@
 
-A: The advantage of the bipartite graph is not only the ability to allow the domain experts quickly understand the domain alignment but more importantly the corresponding words.
-However, in the matrix view, it is much harder to instantaously link the alignment with the corresponding words.
+A: The advantage of the bipartite graph is not only the ability to allow the domain experts to quickly understand the domain alignment but more importantly the corresponding words.
+However, in the matrix view, it is much harder to instantaneously link the alignment with the corresponding words.
 [We update the text to better reflect this point]
@@
 
-A: The simplification is achieve by collapsing the dependency tree structure.
+A: The simplification is achieved by collapsing the dependency tree structure.
 We assume by focusing on the more important grammar structure, we can remove the decorative words and the reduce sentence length to focus on the more crucial part of the sentences.
@@
 A: We employed the standard kernel density estimation technique in 2D.
-As stated in Section 5.3, the primary motivation is to highlight overlaped point (where multiple prediction fall on top of each other) and identify outliers.
+As stated in Section 5.3, the primary motivation is to highlight overlapped point (where multiple predictions fall on top of/near each other) and identify outliers.
 
@@
 
-A: Thanks for catching the ordering problem and providing a soluation.
-To address the problem, we add references to the optimization discussed in section 5.4 in the beginning of section 5 as well as in section 5.3.
-We didn't move all the optimization discussion in the beginning of the section 5, because we believe that presenting details of the all three perturbations (input, attention, prediciton) without any discussion about the interface can also be confusing.
-And the separation between the operation and UI componenet may also make the description hard to read (requre the reader to refer back to the computation discussion while describing the user interface)
+A: Thanks for catching the ordering problem and providing a solution.
+To address the issue, we add references to the optimization discussed in section 5.4 at the beginning of section 5 as well as in section 5.3.
+We didn't move all the optimization discussion at the beginning of section 5, because we believe that presenting details of the all three perturbations (input, attention, prediction) without any discussion about the interface can also be confusing.
+And the separation between the operation and UI componenet may also make the description hard to read (require the reader to refer back to the computation discussion while describing the user interface)
 
@@
 A: The composability of the system is the key to extend its capability.
-The proposed API allow user to include only the panel that is necessary for the given task.
+The proposed API allows the user to include only the panel that is necessary for the given task.
 For new task (i.e., machine translation), we do not need to include the prediction view for NLI task.
@@
 
-A: We didn't design a specific list tasks and the corresponding answers due to the exploratory nature of system as well as the open ended analysis goal.
-If the user didn't follow the particular exploration path the designer of the question goes, it may find some unexpected result that may not directly corresponds to the "correct" answer, but view the problem from a different perspective.
-However, to properly evaluation the proposed technique is extremely important, so we plan to recurite more domain experts to test and evaluation the system in the new future.
+A: We didn't design a specific list of tasks and the corresponding answers due to the exploratory nature of the system as well as the open-ended analysis goal.
+If the user didn't follow the particular exploration path the designer of the question goes, it might find some unexpected result that may not directly correspond to the "correct" answer, but view the problem from a different perspective.
+However, to properly evaluate the proposed technique is extremely important, so we plan to recruit more domain experts to test and evaluate the system in the new future.
 
@@
 9(d), where the given sentence pair have low stability due to the fact the original prediction is a boundary prediction (probability is in between two classes).
-In addition, the perturbation procedure will also affect the pattern as longer sentence will likely have more perturbed variations (contains more nouns and verbs).
-We include a brief discusison on the potential variability caused by the perturbation procedure in section 5.4.
+In addition, the perturbation procedure will also affect the pattern as the longer sentence will likely have more perturbed variations (contains more nouns and verbs).
+We include a brief discussion on the potential variability caused by the perturbation procedure in section 5.4.
 
@@
 
-A: The curve pattern in the Figure 8d are likely cause by the different number of words that was perturbed (i.e., each line pattern corresponds to sentence pair that include the same number of nouns and verbs that to be perturbed).
-This illustrate the additional variation the perturbation bring into the system.
-We include a brief discusison on the potential variability caused by the perturbation procedure in section 5.4.
+A: The curve patterns in the Figure 8d are likely caused by the different number of words that was perturbed (i.e., each line pattern corresponds to sentence pairs that include the same numbers of nouns plus verbs that will be perturbed).
+This demonstrates the added variation the perturbation bring into the system.
+We include a brief discussion on the potential variability caused by the perturbation procedure in section 5.4.
 
@@
 
-A: The key rational for collasping the sentence to reduce the length while still preserving the main structure of the sentence.
-Therefore, the collasping operation will greatly improve the scability of the show a long sentence.
-However, it may not suitable for a whole paragraph (multiple sentence), when the length of collapsed sentence can still be too long to be effectively represented in the matrix or biparite graph view.
-For task such as machine comprehension, in which the context paragraph and be extremely long, we likely will need a hierarchical type of structure.
+A: The key rationale for collapsing the sentence to reduce the length while still preserving the primary structure of the sentence.
+Therefore, the collapsing operation will significantly improve the scalability of the show a long sentence.
+However, it may not suitable for a whole paragraph (multiple sentences), when the length of collapsed sentence can still be too long to be effectively represented in the matrix or bipartite graph view.
+For the task such as machine comprehension, in which the context paragraph and be extremely long, we likely will need a hierarchical type of structure.
 
@@
 A: The SNLI dataset (https://nlp.stanford.edu/projects/snli/) includes "570k human-written English sentence pairs manually labeled for balanced classification with the labels entailment, contradiction, and neutral".
-Therefore, it does not have direct connection to the word embedding dimension or language features.
-It is a benchmark dataset for natural language processing task, which can be attacked by different type of models.
+Therefore, it does not have a direct connection to the word embedding dimension or language features.
+It is a benchmark dataset for natural language processing task, which can be attacked by different types of models.
 In our case, we investigated a neural network based approach.
@@
 
-A: Since we utilize unicode text representation through out the code, the proposed system can be easily adapting to other aphateical language (however, we have not test the capability).
-One potential challenge may originated from NLP training set, as there are not as many large scale training data in language other than english.
+A: Since we utilize Unicode text encoding throughout the code, the proposed system can be easily adapting to other alphabetical languages (however, we have not tested the capability).
+One potential challenge may be originated from NLP training set, as there are not as many large-scale training data in languages other than English.
 
@@
 
-A: We have revise the last paragraph of the introduction to highlight the visualization contributions.
-The text following "Moreover, we propose..." is not the only place describe visualization contributions, the integrated model pipeline that allow user perturbation in all stages is another contribution, the same holds for the visual encoding for the prediction for the NLI problem.
+A: We have revised the last paragraph of the introduction to highlight the visualization contributions.
+The text following "Moreover, we propose..." is not the only place describe visualization contributions, the integrated model pipeline that allows user perturbation in all stages is another contribution, the same holds for the visual encoding for the prediction for the NLI problem.
 
@@
 A: We appreciated the reviewer concern as organizing a visualization paper for a domain specific application is a very challenge task.
-The rational for our current orgnaiziation is that the NLP background provides the minimally necessary information for the average reader to understand the application problem.
+The rationale for our current organization is that the NLP background provides the minimally necessary information for the average reader to understand the application problem.
 It is an essential part of the paper which make it self-contained.
 In addition, a lot of the technical details is directly connected to how the visualization encoding is designed (such as the attention view and prediction view).
-Without a highlevel understanding of the model, it would be impossible for the reader to understand the purpose of most views and the application senarios.
-Finally, we also try to compress the background information, we spend less than one page on the background, even through other sections mentioned NLP related topics but they mostly still focus on presenting the visualization system.
+Without a high-level understanding of the model, it would be impossible for the reader to understand the purpose of most views and the application scenarios.
+Finally, we also try to compress the background information, we spend less than one page on the background, even though other sections mentioned NLP related topics but they mostly still focus on presenting the visualization system.
 
@@
 
-A:
+A: One can expand the text box to include multiple lines to show the longer sentence. There is no particular encoding here since we are just showing the raw text.
 
@@
 
-A: The biggest benefit of the graph is the ability for the domain expert to directly see the connection between words.
-In the matrix, one need to first identify the high value entry and then finding the corresponding row and column to identify the words.
-If there are multiple correspondence, the user need to check one by one.
+A: If the sentence structures are drastically different, the matrix view may be the better option as the structure difference likely result in crossed lines in the bipartite graph view, which can lead to poorer perception.
+The most significant benefit of the graph is the ability for the domain expert to see the connection between words directly.
+In the matrix, one needs to first identify the high-value entry and then finding the corresponding row and column to recognize the words.
+If there are multiple correspondences, the user needs to check them one by one in the matrix view.
 
@@
 
-A:
+A: For the given model there are two attention matrices, one have row normalization while the other has column normalization.
+We follow the same rule to apply renormalization after sentence collapsing.
 
@@
 
-A:
+A: The amount of necessary reduction is influenced by the structure of the sentences as well as the capability of the parser.
+There is a trade-off between visual clutter and text readability.
+The more collapse is equal to less visual clutter, but likely reduce the readability of the text.
+The From our experiment, we notice the NLP experts have a far better capability to understand the collapsed sentence compared to others.
+The desired level should be a good trade-off based on the expert's preference.
 
@@
 
-A:
+A: There are two rational to design the re-assignment as drag.
+Firstly, the semantic of changing prediction corresponds well to a drag operation.
+We initially plan to implement the re-assignment as a continuous drag operation.
+However, we believe it is more meaningful for a human to assign discrete labels (instead of a probability).
+Secondly, we want to distinguish this action from the mouse click which is reserved for selection operation.
 
@@
 
-A:
+A: The MIRA optimization process indeed introduces unpredictability and opaqueness in the solution.
+To mitigate the limitation, we provide a summary of the parameter changes in the pipeline view to help reveal the effect of the optimization on the parameter.
+Moreover, we can also utilize the attention visualization to interpret the impact the optimization.
+Finally, compared to an end-to-end neural network (which is often referred to as a black box) this optimization has a more restricted setting as we are only fitting the model to the given instance.
 
@@
 
-A: We agree that a 3x3 heatmap (confusion matrix) is also an efficient alternative to represent the summary prediction result.
-The motivation is use treemap is that it provides a more direct encoding for conveying the count (area instead of variation of colors).
-And the separate between orange and green tile intuitively convey the correct and incorrect predictions.
+A: We agree that a 3x3 heatmap (essentially a confusion matrix) is also an efficient alternative to represent the summary prediction result.
+The motivation is use treemap is that it provides a more direct encoding for conveying the count (area instead of a variation of colors).
+And the separate between orange and green tile intuitively express the correct and incorrect predictions.
 However, we do think a confusion matrix like encoding could also be beneficial.
-In the future, we plan to add the confusion matrix as an alternative, so the user can use either one of them based on their preference.
+In the future, we plan to add the confusion matrix as an alternative so that the user can use either one of them based on their preference.
 
@@
 
-A: These sections has been revised to improve the readability.
+A: These sections have been revised to improve the readability.
 
@@
 A: We remove/replace the words mentioned by the reviewer.
-For example, the following is the updated first sentence of the introduction in which "stunning", "unprecedented" are removed.
-"Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications."
+For example, we updated the first sentence to "Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications."
 
@@
 
-A: These different senarios should naturally arise during the exploration session, the senarios 1 is often the first step to identify the sentence pair of interests (the user can also manually type the one they interested in senarios 6).
+A: These different scenarios should naturally arise during the exploration session, the scenarios 1 is often the first step to identify the sentence pair of interests (the user can also manually type the one they interested in scenarios 6).
 
@@
 
-A: We have revised the video and include voice over and an simple introduction in the begninning.
+A: We have revised the video and included voice over and a simple introduction at the beginning of the video.
 
@@
 
-A: In the introduction we want to highlgith the input modality different.
-Continuous for image, and discrete for natural language.
+A: In the introduction, we want to highlight the input modality different.
+Continuous for the image, and discrete for natural language.
 The different has introduced additional challenge especially regarding optimization as well as interpretation.
 In addition, in CNN we often can reveal human interpretable neuron filter, but these method has been generalized for NLP.
-The attention is the exception, which represent often the only interpretable part of the model.
+The attention is the exception, which represents often the only interpretable part of the model.
 
@@
 
-A: The perturbation of nous and verbs on itself is not novel from NLP perspective, and truly solving the challenge of producing grammarly correct and meaningful perturbation/paraphrasing is still an open research area.
-In our case, we believe the novality come from the integration of the model with the three stage perturbation scheme in an explorable visual analytic system.
+A: The perturbation of nouns and verbs on itself is not novel from NLP perspective, and truly solving the challenge of producing grammatically correct and meaningful perturbation/paraphrasing is still an open research area.
+In our case, we believe the novelty comes from the integration of the model with the three-stage perturbation scheme in an explorable visual analytic system.
 
@@
 
-A: We moved the description of the collabration into the beginning of section 4, in which we describe the number of NLP experts, frequency, and the duration of the meeting for this specific projects.
-We also add pointer to application senarios that corresponds to the tasks to instantiate the more abstract concepts.
+A: We moved the description of the collaboration into the beginning of section 4, in which we describe the number of NLP experts, frequency, and the duration of the meeting for this specific projects.
+We also add a pointer to application scenarios that corresponds to the tasks to instantiate the more abstract concepts.
 
@@
 
-A: We've citated this work in Section 5.2 when discussing the due visual representations.
+A: We've cited this work in Section 5.2 when discussing the due visual representations.
 
@@
 Coming up with efficient visual encoding for these type of information they go beyond grammar tree is a challenge on its own.
-For example the extract structure can be graph, which likely require a complete redesign of the annotation visualization.
+For example, the extract structure can be a graph, which likely requires a complete redesign of the annotation visualization.
 
@@
 A: In the current system, we did not record the user interaction/correction result.
-The mira optimization update may correct the model for the given example (to some extend overfit to the example), however, we don't think there is guarantee that the fix can be easily generalized to other examples.
-In addition, the ambiguity between pile and heap may also originated from the word embedding (the input numerical representation for words).
-What the proposed system do is to communicate to the NLP experts that the ambiguity between pile and heap is likely the cause of the wrong prediciton.
-The experts can chose to dive further and examine the problem with their NLP background.
+The MIRA optimization update may correct the model for the given example (to some extend overfit to the example), however, we don't think there is a guarantee that the fix can be readily generalized to other cases.
+Also, the ambiguity between pile and heap may also originate from the word embedding (the numerical input representation for words).
+What the proposed system does is to communicate to the NLP experts that the ambiguity between pile and heap is likely the cause of the wrong prediction.
+The experts can choose to dive further and examine the problem with their NLP background.
 
@@
 
-A: As discussion in the answer for Q1, the core attention operation is not tunable, only the intial transformation in the beginning of the attention stage includes tunable parameters.
+A: As discussed in the answer for Q1, the core attention operation is not tunable, only the initial transformation at the beginning of the attention stage includes tunable parameters.
 This can partially explain the result.
@@
 
-A: We added a overview in the begining of the section 6 to illustrate how different tasks related to one another and provide addtional discussion on section 6.3.
+A: We added an overview at the beginning of section 6 to illustrate how different tasks related to one another and provide additional discussion on section 6.3.

### 2018-06-21 paper/itemizedReviewResponse.tex
add summary list

@@
 Summary of major changes:
-1. Revise section 6 to better convey the relationship between the different scenarios and provide further clarification on the result observed in 6.3
-
+- Revise section 6 to better convey the relationship between the different scenarios and provide further clarification on the result observed in 6.3.
+- Revise the introduction to remove hyperbole words, clarify the NLP vs. CNN data modality comparison, and simplify the contribution list.
+- Clarify the domain experts involvement in the beginning of section 4.
+- Revise section 5 to better explain the user interactions and add discussion on how to interpret the visual encodings.
 ------------------------------- Reviewer 1 -------------------------------

### 2018-06-21 paper/itemizedReviewResponse.tex
nlp response pass

@@
 A: To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
-In this case, the result indicates that the tunable parameters of the attention stage (the transformation before the alignment operation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
+In this case, the result indicates that the tunable parameters of the attention stage (the transformation before the core alignment computation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
 The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
@@
 
-A: The exact computation of attention can vary from model to model, though the overall concept is shared as they are specially designed for understanding the corresponding relationship between the sequence of texts.
+A: The exact computation of attention can vary from model to model despite the overall concept is shared.
+As a result, when we discuss the general concept of attention we can not fix on a single mathematical formulation (the detailed formulation for the model we investigated is discussed in Appendix A ).
 
@@
 
-A: We had added additional details of the collaboration at the beginning of section 4, including the number of NLP collaborators, frequency, duration of the meeting for this specific tasks.
+A: We had added additional details of the collaboration at the beginning of section 4, including the number of NLP collaborators, frequency, duration of the meeting for the proposed work.
 
@@
 
-A: The advantage of the bipartite graph is not only the ability to allow the domain experts to quickly understand the domain alignment but more importantly the corresponding words.
-However, in the matrix view, it is much harder to instantaneously link the alignment with the corresponding words.
-[We update the text to better reflect this point]
+A: The advantage of the bipartite graph is the ability to allow the domain experts to quickly uncover not only the most dominant alignments but also the corresponding words.
+However, in the matrix view, it take more efforts to link the strong alignment with the corresponding words (especially if there are several strong alignments).
+[We have updated the text to better reflect this point]
 
@@
 
-A: The simplification is achieved by collapsing the dependency tree structure.
+A: The simplification is achieved by replacing the children of the dependency tree structure with the parents.
 We assume by focusing on the more important grammar structure, we can remove the decorative words and the reduce sentence length to focus on the more crucial part of the sentences.
@@
 To address the issue, we add references to the optimization discussed in section 5.4 at the beginning of section 5 as well as in section 5.3.
-We didn't move all the optimization discussion at the beginning of section 5, because we believe that presenting details of the all three perturbations (input, attention, prediction) without any discussion about the interface can also be confusing.
-And the separation between the operation and UI componenet may also make the description hard to read (require the reader to refer back to the computation discussion while describing the user interface)
+We didn't move all the optimization discussion at the beginning of section 5, because we believe that presenting details of the all three perturbations (input, attention, prediction) without any discussion about the interface can also be very confusing.
+And the separation between the operation and UI component may also make the description hard to read (require the reader to refer back to the computation discussion while describing the user interface).
+We believe the revised version provide a decent compromise.
 
@@
 A: The composability of the system is the key to extend its capability.
-The proposed API allows the user to include only the panel that is necessary for the given task.
-For new task (i.e., machine translation), we do not need to include the prediction view for NLI task.
-We can reuse the attention view to representating the alignment between the original sentence and the translated sentence and introduce new panel for visualizing other information that may not present in the NLI model.
-However, the main idea is to allow use the combine the panels/functionality to suit their goals.
+The proposed API allows the user to include only the view that is necessary for the given task.
+For new task (i.e., machine translation), we do not need to include the prediction view for the NLI task.
+We can reuse the attention views to representing the alignment between the original sentence and the translated sentence and introduce new views for visualizing other information that may not present in the NLI model.
+The main idea is to allow user to combine the view/functionality to suit their analysis goals.
 
@@
 A: Gradient-based sensitivity analysis can often be carried out for domain that is differentiable (i.e., image pixel values), however, for natural language sentences these techniques often can not directly be adopted directly.
-[??
-add the discussion to where?]
+In the proposed work, we can think the perturbation as way to approximate gradient-based analysis for discrete domain.
+[add the discussion to where?
+TODO]
 
@@
 A: We didn't design a specific list of tasks and the corresponding answers due to the exploratory nature of the system as well as the open-ended analysis goal.
-If the user didn't follow the particular exploration path the designer of the question goes, it might find some unexpected result that may not directly correspond to the "correct" answer, but view the problem from a different perspective.
+If the user didn't follow the particular exploration path the designer of the question goes, he/she might find some unexpected result that may not directly correspond to the "correct" answer, but view the problem from a different perspective.
 However, to properly evaluate the proposed technique is extremely important, so we plan to recruit more domain experts to test and evaluate the system in the new future.
@@
 
-A: Since we utilize Unicode text encoding throughout the code, the proposed system can be easily adapting to other alphabetical languages (however, we have not tested the capability).
-One potential challenge may be originated from NLP training set, as there are not as many large-scale training data in languages other than English.
+A: Since we have utilized Unicode text encoding throughout the code, the proposed system can be easily adapting to other alphabetical languages (however, we have not tested the capability).
+One potential challenge may be originated from NLP training dataset, as there are not many large-scale training data in languages other than English.
 
@@
 
-Q23, More importantly, there is little rationale for the visual representation designs of the various views.
-The design choices do make sense (at least to an experienced visualization designer) but there are alternatives in each case.
-It's not clear that the visualization are particularly good or bad for their intended uses as described in section 6.
-A few questions that arise:
-
-* How does one handle very different sentence lengths in the sentence view?
+Q23, How does one handle very different sentence lengths in the sentence view?
 
@@
 
-* What if the sentence structures between premise and hypothesis are not drastically different; will the matrix be as effective, and thus the graph need to be focused on?
+Q24, What if the sentence structures between premise and hypothesis are not drastically different; will the matrix be as effective, and thus the graph need to be focused on?
 
@@
 
-* In the matrix view, how hard is it to control rows when they're renormalizing?
+Q25, In the matrix view, how hard is it to control rows when they're renormalizing?
 
@@
 
-* How much reduction in the grammar dependency tree is necessary to combat visual clutter, and how does that relate to the expert's ability to dissect sentences at the desired level of detail?
+Q26, How much reduction in the grammar dependency tree is necessary to combat visual clutter, and how does that relate to the expert's ability to dissect sentences at the desired level of detail?
 
@@
 
-* How do the matrices combined in figure 5f align for comparison?
+Q27, How do the matrices combined in figure 5f align for comparison?
 
@@
 
-* Why does the prediction view use a continuous interaction like drag when the target is to select one of only three discrete options?
+Q28, Why does the prediction view use a continuous interaction like drag when the target is to select one of only three discrete options?
 
@@
 
-* What happens in the prediction view if many predictions are close to each other?
+Q29, What happens in the prediction view if many predictions are close to each other?
 Between the predictions and the density contour map, the view could get very dense, particular if much data is involved from the 10k set.
@@
 
-* In the pipeline view, doesn't the formulation to approximate the assigned label introduce another black box that the user need to factor into their analytic thinking?
+Q30, n the pipeline view, doesn't the formulation to approximate the assigned label introduce another black box that the user need to factor into their analytic thinking?
 
 A: The MIRA optimization process indeed introduces unpredictability and opaqueness in the solution.
-To mitigate the limitation, we provide a summary of the parameter changes in the pipeline view to help reveal the effect of the optimization on the parameter.
-Moreover, we can also utilize the attention visualization to interpret the impact the optimization.
-Finally, compared to an end-to-end neural network (which is often referred to as a black box) this optimization has a more restricted setting as we are only fitting the model to the given instance.
+To mitigate the limitation, we provide a summary of the parameter changes in the pipeline view to help reveal the effect of the optimization on the parameters.
+Moreover, we can also utilize the attention visualization to interpret the impact of the optimization.
+Finally, compared to an end-to-end neural network (which is often referred to as a black box) this optimization has a more restricted setting that is easier to interpret as we are only fitting the model to the given instance.
 
-* Why a treemap in the summary view?
+Q31, Why a treemap in the summary view?
 It's just a 3x3 set of quantities.
@@
 
-* The description of interaction for the E/E category in the summary view says what one can do, but it's not clear how or why.
+Q32, The description of interaction for the E/E category in the summary view says what one can do, but it's not clear how or why.
 
-A:
+A: [The description is revised TODO]
 
-Q24, Part of the problem is that the language is very dense in this paper.
+Q33, Part of the problem is that the language is very dense in this paper.
 Although the grammar is acceptable, it was a slow read and there were some passages that I found all but indecipherable, such as the figure 7 caption, the last paragraph of section 5.5, and the bullet list at the end of the introduction.
@@
 
-Q25, There were many small errors that need correcting, too many to bother listing here.
+Q34, There were many small errors that need correcting, too many to bother listing here.
 There was also some hyperbole ("stunning", "unprecedented", "vision", "paradigm") that distracts me as a serious reader and should be replaced.
@@
 
-Q26, The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination.
+Q35, The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination.
 The scenarios essentially describe individual tasks that experts might perform in individual views.
@@
 
-Q27, The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.
+Q36, The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.
 
@@
 
-Q28, I was confused by the distinction between image networks and language networks.
+Q37, I was confused by the distinction between image networks and language networks.
 CNNs are not only used to make binary classifications, and there are certainly challenges in image networks that do not provide "clear meaning" and seem like they would also benefit from the proposed work.
@@
 
-Q29, It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs.
+Q38, It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs.
 If it's the former (as it seems to be), then I think this needs to be emphasized in the introduction.
@@
 
-Q30, I appreciated the task analysis in section 4.
+Q39, I appreciated the task analysis in section 4.
 However, it seems a bit too brief, and the tasks don't seem to directly follow from the description of the authors experience with the NLP researchers.
@@
 
-Q31, Work by Ma et al.
+Q40, Work by Ma et al.
 ("Visualizing dynamic brain networks using an animated dual-representation" from EuroVis 2015) is work related to NLIZE having both graph and matrix views that complement each other and provide the same information from different perspectives, as described in Section 5.2.
@@
 
-Q32, Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4).
+Q41, Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4).
 I wonder if it would make sense to use other types of annotations here, such as those created from event extraction tools or information extraction tools that would highlight other structures (besides grammar/POS) that could be useful in helping understanding the inference model.
@@
 
-Q33, In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile?
+Q42, In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile?
 with ?heap?).
@@
 Also, the ambiguity between pile and heap may also originate from the word embedding (the numerical input representation for words).
-What the proposed system does is to communicate to the NLP experts that the ambiguity between pile and heap is likely the cause of the wrong prediction.
-The experts can choose to dive further and examine the problem with their NLP background.
+The proposed system suggests to NLP experts that the ambiguity between pile and heap is likely the cause of the incorrect prediction.
+The experts can choose to dive further and examine the problem.
 
-Q34, Section 6.3 is very interesting, but I don't understand why perturbing the attention stage has less of an effect that the other perturbations.
+Q43, Section 6.3 is very interesting, but I don't understand why perturbing the attention stage has less of an effect that the other perturbations.
 This seems like a preliminary contribution in and of itself (i.e., that using the NLIZE application leads to global understanding such as this), and worthy of further examination.
@@
 
-Q35, The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach.
+Q44, The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach.
 It might make more sense to focus more on only one or two scenarios and cover them in more depth.

### 2018-06-21 paper/itemizedReviewResponse.tex
Update itemizedReviewResponse.tex
added comment to Q1

@@
 We revised section 6.3 to clarify this point.
+
+\emph{tli} The attention layer indeed has tunable parameters (there is a two-layer ReLU specialized for attention layer, checkout the revised appendix).
+The explanation can be this: Attention provides a way to compose word semantics.
+Individual word semantics are yielded by encoder and input embedding, while the composed semantics participate in classification layer.
+We can see from this analysis that, only adjusting the word alignment only affects composed semantics but has no effect on word semantics while the later plays a significant role in good model (as this was also justified by recent works in word embeddings, e.g.
+Elmo).
+Without proper semantics (in both encoder and classifier), only adjusting alignment is not sufficient to yield good model.
 

### 2018-06-21 paper/itemizedReviewResponse.tex
Update itemizedReviewResponse.tex
Some comments

@@
 
+\emph{tli} I think we might add it when we introduce perturbation, as something like the challenge of using gradient-based method in NLP inspired us to use perturbation.
+
 Q10, The evaluation is acceptable but a bit weak.
@@
 In our case, we investigated a neural network based approach.
+
+\emph{tli}: In our case, we investigated a typical neural network based approach.
 
@@
 Finally, compared to an end-to-end neural network (which is often referred to as a black box) this optimization has a more restricted setting that is easier to interpret as we are only fitting the model to the given instance.
+
+\emph{tli} Our MIRA optimization is a simplified version that only added a L2 regularization on the weight change during backpropagation.
+And yes, it is much more intuitive than a deep neural black box.
 

### 2018-06-21 paper/itemizedReviewResponse.tex
integrated the comment and update the paper

--- 2018-06-21 paper/itemizedReviewResponse.tex
@@
 - Revise section 5 to better explain the user interactions and add discussion on how to interpret the visual encodings.
+- Reworked the video, included a new introduction section and added the voice over.
+
 ------------------------------- Reviewer 1 -------------------------------
@@
 
-A: To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
-In this case, the result indicates that the tunable parameters of the attention stage (the transformation before the core alignment computation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
-The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
-However, this result does not necessarily imply the limitation of attention mechanism as the core alignment computation does not have tunable parameters that can be modified by the proposed optimization.
-We revised section 6.3 to clarify this point.
-
-\emph{tli} The attention layer indeed has tunable parameters (there is a two-layer ReLU specialized for attention layer, checkout the revised appendix).
-The explanation can be this: Attention provides a way to compose word semantics.
+A: The domain experts provide the following way to interpret the result.
+Attention provides a way to compose word semantics.
 Individual word semantics are yielded by encoder and input embedding, while the composed semantics participate in classification layer.
@@
 Without proper semantics (in both encoder and classifier), only adjusting alignment is not sufficient to yield good model.
+We revised section 6.3 to clarify this point.
 
@@
 
-A: Gradient-based sensitivity analysis can often be carried out for domain that is differentiable (i.e., image pixel values), however, for natural language sentences these techniques often can not directly be adopted directly.
-In the proposed work, we can think the perturbation as way to approximate gradient-based analysis for discrete domain.
-[add the discussion to where?
-TODO]
+A: Gradient-based sensitivity analysis can often be carried out for domain that is differentiable (i.e., image pixel values).
+In the proposed work, the challenge of using gradient-based method in NLP actually inspired us to utilize perturbation.
+This is related to discussion in the introduction where the difference between NLP and CV is highlighted.
 
@@
 It is a benchmark dataset for natural language processing task, which can be attacked by different types of models.
-In our case, we investigated a neural network based approach.
+In our case, we investigated a typical neural network based approach.
 
@@
 Moreover, we can also utilize the attention visualization to interpret the impact of the optimization.
-Finally, compared to an end-to-end neural network (which is often referred to as a black box) this optimization has a more restricted setting that is easier to interpret as we are only fitting the model to the given instance.
+Finally, our MIRA optimization is a simplified version that only added a L2 regularization on the weight change during backpropagation.
+Compared to an end-to-end neural network (which is often referred to as a black box) this optimization has a more restricted setting that is easier to interpret as we are only fitting the model to the given instance.
 
@@
 
-A: As discussed in the answer for Q1, the core attention operation is not tunable, only the initial transformation at the beginning of the attention stage includes tunable parameters.
-This can partially explain the result.
-However, the domain experts mentioned they are interested in exploring more from NLP perspective to understand this result fully.
+A: As discussed in the answer for Q1, the domain experts mentioned they are interested in exploring more from NLP perspective to understand this result fully.
+They also provide some preliminary explanation.
+We included them in the revise 6.3 section.
 

### 2018-06-21 paper/application.tex
integrated the comment and update the paper

@@
 \shusen{
-To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
-In our case, the result indicates that the tunable parameters of the attention stage (the transformation before the alignment operation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
 The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
-However, this result does not necessarily imply the limitation of attention mechanism as the core alignment computation does not have tunable parameters that can be modified by the proposed optimization.
+The domain experts suggest a preliminary understanding as the following.
+Attention provides a way to compose word semantics.
+Individual word semantics are yielded by the encoder and input embedding, while the composed semantics participate in classification layer.
+We can see from this analysis that, only adjusting the word alignment only affects composed semantics but has no effect on word semantics while the later plays a significant role in good model (as this was also justified by recent works in word embeddings, e.g.
+Elmo).
+Without proper semantics (in both encoder and classifier), only adjusting alignment is not sufficient to yield good model.
+%To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
+%In our case, the result indicates that the tunable parameters of the attention stage (the transformation before the alignment operation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
+%However, this result does not necessarily imply the limitation of attention mechanism as the core alignment computation does not have tunable parameters that can be modified by the proposed optimization.
 }

### 2018-06-22 paper/application.tex
update response

@@
 To illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model,
-\shusen{we present five interconnected application scenarios a domain expert may employ in their analysis workflow.
-For example, the users can start the exploration by examining the stability of prediction (Scenario 1), from which they may identify the individual instances worth further investigation (Scenario 2, 3, 4).
-Alternatively, the user can also start with handcrafted common/extreme cases (Scenario 5) and further the exploration based on the instantaneous feedbacks provide by the visualization tool.
-}
+we present five interconnected application scenarios a domain expert may employ in their analysis workflow.
+The user can start the exploration by examining the stability of prediction (Scenario 1), from which they may identify the individual instances worth further investigation (Scenario 2, 3, 4).
+Alternatively, the user can begin with handcrafted common/extreme cases (Scenario 5) and continue from there.
 %we present five application scenarios
@@
 %Similar observations can be obtained for most examples we have experimented with.
-\shusen{
-The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
-The domain experts suggest a preliminary understanding as the following.
-Attention provides a way to compose word semantics.
-Individual word semantics are yielded by the encoder and input embedding, while the composed semantics participate in classification layer.
-We can see from this analysis that, only adjusting the word alignment only affects composed semantics but has no effect on word semantics while the later plays a significant role in good model (as this was also justified by recent works in word embeddings, e.g.
-Elmo).
+%\shusen{
+%The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
+The domain experts find this observation very interesting and suggest a preliminary interpretation.
+They believe the attention provides a way to compose word semantics.
+Individual word semantics are yielded from the encoder and input embedding, while the composed semantics participate in classification layer.
+From this analysis, we can extrapolate that adjusting the word alignment affects only the composed semantics but has no effect on word semantics, which often plays a significant role in a good model (as supported by recent works in word embeddings, e.g., ELMo~\cite{salant2017contextualized}).
 Without proper semantics (in both encoder and classifier), only adjusting alignment is not sufficient to yield good model.
@@
 %However, this result does not necessarily imply the limitation of attention mechanism as the core alignment computation does not have tunable parameters that can be modified by the proposed optimization.
-}
+%}
 %The attention layer is less sensitive compared to encoding layer and classification layer.

### 2018-06-22 paper/intro.tex
integrated the comment and update the paper
update response

@@
 \shusen{
-An image (pixel values) corresponds to a continuous solution space. which is more accessable for optimization and human visual recognation (i.e., the existence or the absence of patterns).
+An image (pixel values) corresponds to a continuous solution space. which is more accessible for optimization and human visual recognition (i.e., the existence or the absence of patterns).
 For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.}
@@
 
-    \item The NLIZE system that implements the perturbation exploration scheme by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback;
+    \item The NLIZE system that enables the perturbation-driven exploration by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback;
     %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
@@
 
-    \item An optimization scheme for correcting a failed prediction based on a natural extension of the margin-infused relaxed algorithm (MIRA) to neural networks; and
+    \item An optimization method for correcting a failed prediction based on a natural extension of the margin-infused relaxed algorithm (MIRA) to neural networks; and
     % to minimally update the model to fix a failed prediction, which help reason about the  better understand the re the question about how t
@@
     \item A visual encoding of the attention by imposing sentence linguistic structure to allow grammar-guided sentence simplification.
+
 \end{itemize}

### 2018-06-22 paper/attention.tex
remove related works

--- 2018-03-31 paper/attention.tex
@@
 Also, if the sentence structures between premise and hypothesis are drastically different, we are likely to see the prominent edges cross each other, which can also lead to confusing and misleading visual patterns.
-
+%
 The matrix attention view (Fig.~\ref{fig:attentionVis}(b)), despite being more verbose and less efficient in highlighting the dominant alignment, does not have similar shortcomings.
-Together, the graph and matrix views complement each other and provide the same information from different perspectives.
-As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.
+However, extra effort may be required for identifying the words corresponds to high-value entries in the matrix.
+Together, the graph and matrix views complement each other and provide the same information from different perspectives (a related matrix/graph visualization scheme is presented in \cite{MaKenyonForbes2015} for studying brain network).
+%As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.
 To help the user recognize the correspondence during the exploration, we enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), the attention of the two ``couple'' is highlighted).
@@
 %
-Since the dependency tree encodes the word importance information in a hierarchical matter, it is very suitable for sentence simplification tasks.
+Since the dependency tree encodes the word importance information in a hierarchical manner, it is very suitable for sentence simplification tasks.
 Therefore, we utilize the grammar dependency tree to simplify the attention representations to combat the visual clutter when examining long sentences (see Fig.~\ref{fig:attentionVis}(d)).

### 2018-06-22 paper/intro.tex
remove related works

@@
 For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) captures, cannot be readily generalized to natural language.
-\shusen{
+%\shusen{
 An image (pixel values) corresponds to a continuous solution space. which is more accessible for optimization and human visual recognition (i.e., the existence or the absence of patterns).
-For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.}
+For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.%}
 %

### 2018-06-22 paper/relatedWorks.tex
remove related works

@@
 \textbf{Model Interpretability.}
-Before one can solve the model interpretability challenge, it worth to understand what constitutes an explanation for a machine learning model.
-As discussed in~\cite{Lipton2016, Doshi-Velez2017}, there is little consensus on what interpretability is in the context of machine learning.
+%Before one can solve the model interpretability challenge, it worth to understand what constitutes an explanation for a machine learning model.
+%As discussed in~\cite{Lipton2016, Doshi-Velez2017}, there is little consensus on what interpretability is in the context of machine learning.
 A taxonomy is suggested~\cite{Doshi-Velez2017} to promote a more rigorous study on such a subject.

### 2018-06-22 paper/task.tex
remove related works

--- 2018-03-31 paper/task.tex
@@
 \label{sec:task}
-Identifying the analysis goals and the corresponding visualization tasks is the first significant step in designing a useful tool.
-In this section, we examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
-Then, we distill the numerous discussions with domain experts into concrete tasks, which guide the design and implementation of the proposed tool.
-
-During our long-term collaboration with NLP experts, we have conducted extensive discussions to understand the common approach employed by researchers for assessing the behavior of a model.%
+%Identifying the analysis goals and the corresponding visualization tasks is the first significant step in designing a useful tool. 
+%In this section, we examine how domain experts normally approach the task of analyzing a model (i.e., assess its strength and weakness) and identify where and how an interactive visualization system can aid in such a process.
+%\shusen{
+The primary driving force for designing the proposed tool is the error analysis challenges faced by our long-term collaborators working on natural language inference research.
+During the entire design and development process, we worked closely with two NLP experts via weekly meetings in a period of roughly seven month, their constant evaluation and feedback have helped shape the tool we see today.
+%}
+%Then, we distill the numerous discussions with domain experts into concrete tasks, which guide the design and implementation of the proposed tool.
+%During our long-term collaboration with two NLP experts, 
+During this period, we have conducted extensive discussions to understand the common approaches employed by researchers for assessing the behavior of a model.
+% as well as provide feedback on the various prototyping stages of the proposed visualization.%
 The predictive accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model; however, the accuracy number alone does not provide the full story.
@@
 As a result, the domain experts rely on an exploration-centric approach to conduct error analysis and obtain intuition.
-
+%
 There is little one can learn when everything is behaving as expected, and therefore,
@@
 Moreover, by introducing new visual encodings and summarizations, we can drastically expand the ways domain experts interact with the model, enable exploration options that previously were not possible either due to tedious manual operation or the lack of communication channels.
-
-%Through many rounds of discussions with NLP experts,
+%
 %In such a highly exploratory process, the expert likely will have many ``what if'' type of questions (e.g., what if I make change to this word in the input, what if I force the words to align correctly in the attention), get responsive answers to these queries is essential to maintain the flow of reasoning.
-%
-To support the exploratory workflow for analyzing NLI models, we need to address the following tasks.
+%\shusen{
+To support the exploratory workflow for analyzing NLI models,
+we aim to address the following tasks based on our extensive discussions with NLP experts.
+%}
 
 \begin{itemize}
-
     \item \textbf{T1}: Understand the stability of a prediction, i.e., how perturbations of the input affect the behavior of the model?
@@
     \item \textbf{T3}: When the predicted label is wrong, how can we update the model to correct the prediction? What are the effects of updating different parts of the model?
+\end{itemize}
+
+In Section~\ref{sec:caseStudy}, we will discussion in detail how we can utilize the proposed tool to address these tasks (the application scenarios 1,2,3 corresponds to \textbf{T1-T3}, respectively).
 

### 2018-06-22 paper/attention.tex
update paper

@@
 Since the dependency tree encodes the word importance information in a hierarchical manner, it is very suitable for sentence simplification tasks.
-Therefore, we utilize the grammar dependency tree to simplify the attention representations to combat the visual clutter when examining long sentences (see Fig.~\ref{fig:attentionVis}(d)).
+Here, we utilize the grammar dependency tree to trim the decorative structure to shorten the sentence to combat the visual clutter when examining long sentences (see Fig.~\ref{fig:attentionVis}(d)).
 A simplification example is shown in  Fig.~\ref{fig:attentionVis}(d)(e)(f).

### 2018-06-22 paper/intro.tex
update paper

@@
 There have been many speculations on how attention works in various models.
-Using the proposed tool, the domain experts can study how changes in sentence input, attention, or prediction affect each other, which helps them develop deeper intuitive and alternative hypotheses.
+The proposed tool introduces a perturbation-driven visual analytics enviroment, where the domain experts can study how changes in sentence input, attention, or prediction affect each other, which helps them develop deeper intuitive and alternative hypotheses.
 %we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention.
@@
 %Such type of exploration is not only essential to interpret the language inference problem, but can also be generalized to other NLP model utilized the attention mechanisms.
-Moreover, we propose to enhance the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar-guided simplification of the visual representation.
+In addition, we propose to enhance the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar-guided simplification of the visual representation.
 %

### 2018-06-22 paper/pipeline.tex
update paper

@@
  \caption{
-The pipeline view provides the visual representation of the three-stage (encoder, attention, classifier) model. 
+The pipeline view provides the visual representation of the three-stage (encoder, attention, classifier) of the NLI model. 
 %
-In the proposed tool, we allow model parameters to be updated to correct a prediction error. 
-The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the blue rectangle marked with the word ``parameter'' to enable or disable its update (the legend is shown in (d)).
-In (c), we select whether we want to use the current pipeline setting as displayed or try all the pipeline configuration combinations as the parameter update operation can be enabled or disabled for each stage.
+In the proposed tool, we allow model parameters to be updated to correct a prediction error via a constrained optimization.
+The hyperparameters for this optimization are shown in (a). 
+In (b), we utilizes a graphical representation for each stage of the pipeline.
+% where the user can click on the blue rectangle marked with the word ``parameter'' to enable or disable its update (the legend is shown in (d)). 
+In (c), the user can select whether to use the current pipeline configuration as displayed or try all the pipeline configuration combinations for the optimization.
+%whether we want to use the current pipeline configuration as displayed or try all the pipeline configuration combinations as the parameter update operation can be enabled or disabled for each stage.
 }

### 2018-06-22 paper/predSummary.tex
update paper

@@
-\begin{figure}[htbp]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{summaryView}
- \vspace{-6mm}
- \caption{
-%Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
-We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) shows the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
-%
-The user can select the treemap node to focus on the specific type of scenarios (e.g., E/E) and reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
-The selection can be further narrowed down by selecting the bin in the histogram.
-In (c) and (d), each point corresponds to one sentence pair.
- }
- \vspace{-2mm}
-\label{fig:summaryView}
-\end{figure}
-
 \subsection{Summary View}
@@
 The selection task will become easier if we can generate a good visual summary of the $10k$ examples.% that could also help experts obtain a deeper understanding of the whole $10k$ examples.
+
+\begin{figure}[htbp]
+\centering
+\vspace{-2mm}
+ \includegraphics[width=1.0\linewidth]{summaryView}
+ \vspace{-6mm}
+ \caption{
+%Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
+We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) shows the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
+%
+The user can click on the treemap node to focus on the specific type of scenarios (e.g., E/E) to automatically reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
+The selection can be further narrowed down by selecting the bin in the histogram.
+In (c) and (d), each point corresponds to one sentence pair.
+ }
+ \vspace{-2mm}
+\label{fig:summaryView}
+\end{figure}
 

### 2018-06-22 paper/prediction.tex
update response letter
finish response to review 4
remove related works
update paper

--- 2018-06-18 paper/prediction.tex
@@
 A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+%\shusen{
+The pattern of the perturbed pairs' prediction directly convey the stability of the model for the given instance. 
+We should also take the length of the sentence into consideration as more nouns and verbs will likely lead to more perturbed inputs.
+%}
 
@@
 % The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
-A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+A density contour of the prediction is computed via kernel density estimation to emphasize the highly cluttered areas and distinguish the outliers.
 As illustrated in (b), the predicted label does not match the ground truth. Therefore, we apply a label reassignment operation, which triggers a model update.

### 2018-06-22 paper/application.tex
update paper

@@
 %The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
-The domain experts find this observation very interesting and suggest a preliminary interpretation.
+%The domain experts find this observation very interesting and suggest a preliminary interpretation.
 They believe the attention provides a way to compose word semantics.
@@
 Without proper semantics (in both encoder and classifier), only adjusting alignment is not sufficient to yield good model.
+%
+The domain experts find this observation very interesting and suggest a preliminary interpretation.
+They believe the attention provides a way to compose word semantics.
+Individual word semantics are yielded from the encoder and input embedding, while the composed semantics participate in classification layer.
+From this analysis, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in classifier).
+The encoder and classifier layer can swiftly adjust weights for word/composed semantics to correct prediction.
+But the attention layer, which only works on how individual words are aligned, affects the prediction less significantly.
+Recent works also support this observation in word embeddings, e.g., ELMo~\cite{salant2017contextualized}, where better word embeddings can substantially benefit a model.
+However, it by no means implies attention is not useful, as it serves as a way to compose word semantics.
 %To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.

### 2018-06-22 paper/itemizedReviewResponse.txt
add response letter

--- 2018-06-21 paper/itemizedReviewResponse.tex
@@
 
-We greatly appreciate all reviewers' valuable comments. The summary of major changes are listed below. We have itemized the 35 questions/comments and answer each individually.
+We greatly appreciate all reviewers' valuable comments. The summary of major changes are listed below. We have itemized the 44 questions/comments and answer each individually.
 
 Summary of major changes:
-- Revise section 6 to better convey the relationship between the different scenarios and provide further clarification on the result observed in 6.3.
-- Revise the introduction to remove hyperbole words, clarify the NLP vs. CNN data modality comparison, and simplify the contribution list.
-- Clarify the domain experts involvement in the beginning of section 4.
-- Revise section 5 to better explain the user interactions and add discussion on how to interpret the visual encodings.
-- Reworked the video, included a new introduction section and added the voice over.
+- Revised section 6 to better convey the relationship between the different scenarios and provide further clarification on the result observed in 6.3.
+- Revised the introduction to remove hyperbole words, clarify the NLP vs. CNN data modality comparison, and simplify the contribution list.
+- Clarified the domain experts' involvement at the beginning of section 4, and link the task with the application scenarios.
+- Revised section 5 to better explain the user interactions and add discussion on how to interpret the visual encodings.
+- Reworked the video, included a new introduction section and added a voiceover.
 
@@
 
-A: The domain experts provide the following way to interpret the result.
-Attention provides a way to compose word semantics.
-Individual word semantics are yielded by encoder and input embedding, while the composed semantics participate in classification layer.
-We can see from this analysis that, only adjusting the word alignment only affects composed semantics but has no effect on word semantics while the later plays a significant role in good model (as this was also justified by recent works in word embeddings, e.g.
-Elmo).
-Without proper semantics (in both encoder and classifier), only adjusting alignment is not sufficient to yield good model.
-We revised section 6.3 to clarify this point.
+A: The domain experts find this observation very interesting and suggest a preliminary interpretation.
+They believe the attention provides a way to compose word semantics.
+Individual word semantics are yielded from the encoder and input embedding, while the composed semantics participate in classification layer.
+From this analysis, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in classifier).
+The encoder and classifier layer can swiftly adjust weights for word/composed semantics to correct prediction.
+But the attention layer, which only works on how individual words are aligned, affects the prediction less significantly.
+Recent works also support this observation in word embeddings, e.g., ELMo~\cite{salant2017contextualized}, where better word embeddings can substantially benefit a model.
+However, it by no means implies attention is not useful, as it serves as a way to compose word semantics although it does not directly output that.
+We revised section 6.3 to include this comment on the interpretation of the visualization result.
 
@@
 
-A: The exact computation of attention can vary from model to model despite the overall concept is shared.
-As a result, when we discuss the general concept of attention we can not fix on a single mathematical formulation (the detailed formulation for the model we investigated is discussed in Appendix A ).
+A: The exact computation of attention can vary from model to model despite the shared overall concept, i.e., the alignment between words.
+As a result, when we discuss the general concept of attention we can not fix on a single mathematical formulation.
+The exact formulation for the model we investigated is discussed in Appendix A.
 
@@
 
-A: We had added additional details of the collaboration at the beginning of section 4, including the number of NLP collaborators, frequency, duration of the meeting for the proposed work.
+A: We had added additional details of the collaboration at the beginning of section 4, including the number of NLP collaborators, frequency, duration of the meeting period for the proposed work.
 
@@
 A: The advantage of the bipartite graph is the ability to allow the domain experts to quickly uncover not only the most dominant alignments but also the corresponding words.
-However, in the matrix view, it take more efforts to link the strong alignment with the corresponding words (especially if there are several strong alignments).
-[We have updated the text to better reflect this point]
+However, in the matrix view, it takes the user more efforts to link the strong alignment with the corresponding words (especially if there are several strong alignments).
+We have updated the text to better reflect this point.
 
@@
 We assume by focusing on the more important grammar structure, we can remove the decorative words and the reduce sentence length to focus on the more crucial part of the sentences.
+We have revise the section 5.2 to clarify the simplification process.
 
@@
 As stated in Section 5.3, the primary motivation is to highlight overlapped point (where multiple predictions fall on top of/near each other) and identify outliers.
+We have included the description for density computation in Section 5.3.
 
@@
 A: Thanks for catching the ordering problem and providing a solution.
-To address the issue, we add references to the optimization discussed in section 5.4 at the beginning of section 5 as well as in section 5.3.
-We didn't move all the optimization discussion at the beginning of section 5, because we believe that presenting details of the all three perturbations (input, attention, prediction) without any discussion about the interface can also be very confusing.
-And the separation between the operation and UI component may also make the description hard to read (require the reader to refer back to the computation discussion while describing the user interface).
-We believe the revised version provide a decent compromise.
+To address the issue, we added references to the optimization discussed in section 5.4 at the beginning of section 5 as well as in section 5.3.
+We didn't move all the optimization discussion at the beginning of section 5, since we believe presenting details of the all three perturbations (input, attention, prediction) without any discussion about the interface can also be very confusing.
+And the separation between the operation and UI component may also make the description hard to read (require the reader to refer back to the computation discussion when describing the user interface).
+We believe the revised version provide a decent tradeoff.
 
@@
 We can reuse the attention views to representing the alignment between the original sentence and the translated sentence and introduce new views for visualizing other information that may not present in the NLI model.
-The main idea is to allow user to combine the view/functionality to suit their analysis goals.
+The main idea is to allow user to combine the view/functionality and add new view if necessary to suit their analysis goals.
 
@@
 In the proposed work, the challenge of using gradient-based method in NLP actually inspired us to utilize perturbation.
-This is related to discussion in the introduction where the difference between NLP and CV is highlighted.
+This point is partly discussion in the introduction where the difference between NLP and CV is highlighted (image has a differentiable domain).
 
@@
 
-A: We didn't design a specific list of tasks and the corresponding answers due to the exploratory nature of the system as well as the open-ended analysis goal.
-If the user didn't follow the particular exploration path the designer of the question goes, he/she might find some unexpected result that may not directly correspond to the "correct" answer, but view the problem from a different perspective.
-However, to properly evaluate the proposed technique is extremely important, so we plan to recruit more domain experts to test and evaluate the system in the new future.
+A: We didn't design a specific list of tasks and the corresponding answers mostly due to the the open-ended analysis goal.
+If the user didn't follow the particular exploration path the designer of the question goes, he/she might find some unexpected result that may not directly correspond to the "correct" answer, but instead viewing the problem from a different perspective.
+However, we do believe extensive evaluation the system is extremely important.
+We plan to recruit more domain experts to test and evaluate the system in the future.
 
@@
 
-A: Thanks for pointing out the grammar issues, we have fixed the mentioned problem. And the renew version has been through a thorough copy edit pass by an editor.
+A: Thanks for pointing out the grammar issues, we have fixed the mentioned problem. And the renewed version has been through a copy edit pass by an editor.
 
@@
 A recurring pattern we noticed is illustrated in Fig.
-9(d), where the given sentence pair have low stability due to the fact the original prediction is a boundary prediction (probability is in between two classes).
+9(d), where the given sentence pair has low stability due to the fact the original prediction is a boundary prediction (probability is in between two classes).
 In addition, the perturbation procedure will also affect the pattern as the longer sentence will likely have more perturbed variations (contains more nouns and verbs).
@@
 This demonstrates the added variation the perturbation bring into the system.
-We include a brief discussion on the potential variability caused by the perturbation procedure in section 5.4.
+We include a brief discussion on the additional variability caused by the perturbation procedure and sentence length in section 5.4.
 
@@
 
-A: We add an introduction section to illustrate the NLP problem and interface. We also include voice over to better convey the contains.
+A: We have added an introduction section to illustrate the NLP problem and interface. We also included voice over to make understanding the content easier.
 
@@
 
-A: We appreciated the reviewer concern as organizing a visualization paper for a domain specific application is a very challenge task.
+A: We appreciated the reviewer's comment as organizing a visualization paper for a domain specific application is a very challenge task.
 The rationale for our current organization is that the NLP background provides the minimally necessary information for the average reader to understand the application problem.
@@
 In addition, a lot of the technical details is directly connected to how the visualization encoding is designed (such as the attention view and prediction view).
-Without a high-level understanding of the model, it would be impossible for the reader to understand the purpose of most views and the application scenarios.
+Without a sufficient understanding of the model and related NLP background, it would be impossible for the reader to understand the purpose of most views and the application scenarios.
 Finally, we also try to compress the background information, we spend less than one page on the background, even though other sections mentioned NLP related topics but they mostly still focus on presenting the visualization system.
@@
 
-A: [We've revised descriptions to make interaction more explicit. TODO]
+A: We've revised descriptions to make interaction more explicit (i.e., for the prediction, attention, summary view).
 
@@
 
-A: There are two rational to design the re-assignment as drag.
+A: There are two rationales to design the re-assignment as drag.
 Firstly, the semantic of changing prediction corresponds well to a drag operation.
@@
 A: The number of points in the prediction view is limited by the number of perturbations per sentence pair.
-In another work, we will only look at one sentence pair at a time for the detailed analysis.
+In another word, we will only look at one sentence pair at a time for the detailed analysis.
 The motivation for including the density contour is to help convey the overlapping information.
 
-Q30, n the pipeline view, doesn't the formulation to approximate the assigned label introduce another black box that the user need to factor into their analytic thinking?
+Q30, In the pipeline view, doesn't the formulation to approximate the assigned label introduce another black box that the user need to factor into their analytic thinking?
 
@@
 A: We agree that a 3x3 heatmap (essentially a confusion matrix) is also an efficient alternative to represent the summary prediction result.
-The motivation is use treemap is that it provides a more direct encoding for conveying the count (area instead of a variation of colors).
-And the separate between orange and green tile intuitively express the correct and incorrect predictions.
+The motivation to use treemap is that it provides a more direct encoding for conveying the count (area instead of a variation of colors).
+And the separate between orange and green tile also intuitively expresses the correct and incorrect predictions.
 However, we do think a confusion matrix like encoding could also be beneficial.
@@
 
-A: [The description is revised TODO]
+A: The description is revised, we specified the exact operation the user need to take.
 
@@
 
-A: These sections have been revised to improve the readability.
+A: We've revised the text in the mentioned sections to improve the readability.
 
@@
 
-A: We remove/replace the words mentioned by the reviewer.
+A: We removed/replaced the words mentioned by the reviewer.
 For example, we updated the first sentence to "Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications."
@@
 
-A: These different scenarios should naturally arise during the exploration session, the scenarios 1 is often the first step to identify the sentence pair of interests (the user can also manually type the one they interested in scenarios 6).
+A: These different scenarios are interconnected and often arise naturally during the exploration sessions.
+The scenarios 1 is often used as the first step to identify the sentence pair of interests (the user can also manually type the one they interested in scenarios 5).
+Then the user can close examine the individual pair as shown in scenarios 2, 3, 4 (depend on what question they want to ask).
+We included a brief discussion on how these scenarios related to each other and expanded the scenarios 3 to include domain experts'  interpretation of the result.
+We didn't following a specific exploration path of a single user, because they may focus on only one or two scenarios and repeatedly applied the same analysis on different data, which may not be the best way to showcase the variety of the functionality this tool can provide.
 
@@
 
-A: We have revised the video and included voice over and a simple introduction at the beginning of the video.
+A: We have revised the video and included voice over and a simple introduction at the beginning.
 
@@
 
-A: In the introduction, we want to highlight the input modality different.
+A: In the introduction, we want to highlight the input modality difference.
 Continuous for the image, and discrete for natural language.
-The different has introduced additional challenge especially regarding optimization as well as interpretation.
-In addition, in CNN we often can reveal human interpretable neuron filter, but these method has been generalized for NLP.
-The attention is the exception, which represents often the only interpretable part of the model.
+The difference has introduced additional challenge especially regarding optimization as well as interpretation.
+In addition, in CNN we often can reveal human interpretable neuron filter (but these methods can not be easily generalized for NLP), whereas the attention is often the only interpretable part of the NLP model.
+We have updated the description in the introduction to better convey this message.
 
@@
 In our case, we believe the novelty comes from the integration of the model with the three-stage perturbation scheme in an explorable visual analytic system.
+We have revised the introduction to highlight the core contribution.
 
@@
 
-A: We moved the description of the collaboration into the beginning of section 4, in which we describe the number of NLP experts, frequency, and the duration of the meeting for this specific projects.
-We also add a pointer to application scenarios that corresponds to the tasks to instantiate the more abstract concepts.
+A: We moved the description of the collaboration into the beginning of section 4, in which we described the number of NLP experts, frequency, and the duration of the meeting for this specific projects.
+We also added a reference to application scenarios that corresponds to the tasks to help instantiate the more abstract concepts.
 
@@
 
-A: After discussing with domain experts, they believe this would be a very interesting direction for future works.
-Coming up with efficient visual encoding for these type of information they go beyond grammar tree is a challenge on its own.
-For example, the extract structure can be a graph, which likely requires a complete redesign of the annotation visualization.
+A: After discussing with domain experts, we believe the reviewer's comment would be a very interesting direction for future works.
+Coming up with efficient visual encoding for these types of information that go beyond grammar tree is a challenge on its own.
+For example, the extract structure can be a graph (instead of a tree), which likely requires a complete redesign of the existing visualization.
 
@@
 The proposed system suggests to NLP experts that the ambiguity between pile and heap is likely the cause of the incorrect prediction.
-The experts can choose to dive further and examine the problem.
+The experts can choose to dive further and close examine the root cause.
 
@@
 
-A: As discussed in the answer for Q1, the domain experts mentioned they are interested in exploring more from NLP perspective to understand this result fully.
+A: As discussed in the answer for Q1, the domain experts mentioned that they are interested in exploring more from NLP perspective to understand this result fully.
 They also provide some preliminary explanation.
-We included them in the revise 6.3 section.
+We included them in the revised 6.3 section.
 
@@
 
-A: We added an overview at the beginning of section 6 to illustrate how different tasks related to one another and provide additional discussion on section 6.3.
+A: We added an overview at the beginning of section 6 to illustrate how different tasks related to one another and provided additional discussion on section 6.3 to dive deeper into the interpretation of the result.

### 2018-06-22 paper/attention.tex
finalize change in section 5

@@
 To support the ability to perturb the attention values (\textbf{T2}), we include the attention editing functionality.
-The attention matrix view is the most suitable place to conduct the edit operation since it provides a direct mapping of attention value.
+The attention matrix view is the most suitable place to conduct the editing operation since it provides a direct mapping of attention value.
 As we can see in Fig.~\ref{fig:attentionVis}(c), when a user clicks the cell of the matrix, a sider will pop up for customizing the attention value (as the user edits the value, each row is automatically renormalized).
 %
-As illustrated in Fig.~\ref{fig:attentionVis}($a_{2}$)(f), we allow the user to compare currently and previously displayed attentions by computing and visualizing their difference.
+As illustrated in Fig.~\ref{fig:attentionVis}($a_{2}$)(f), we also allow the user to compare currently and previously displayed attentions by computing and visualizing their cell-wise difference (the user can toggle between different display modes using the C (current), P (previous), D (difference) buttons bellow the colormap).
 

### 2018-06-22 paper/overview.tex
finalize change in section 5

@@
 \section{NLIZE System}
-In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-T3}).
-%
+In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system. 
+%, which address the visualization tasks (\textbf{T1-T3}).
 As discussed in the previous section, the experts often analyze and obtain intuition about the model by studying how altering one part of the model affects other stages of the pipeline.

### 2018-06-22 paper/predSummary.tex
finalize change in section 5

@@
 The size of the block encodes the number of examples belonging to each category.
-%
+
 By clicking on the treemap node, we can narrow down the selection by focusing on a specific scenario.
-
 As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are shown.
@@
 For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and the all the perturbed pairs.
-Considering we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonymous), the stability is 0.8 if 80 out of the 100 maintain the original prediction label.
+Assuming we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonymous), the stability is 0.8 if 80 out of the 100 maintain the original label.
 %The \emph{stability} measures how likely a sentence pair will change its prediction after applying minor perturbations.% which helps the expert infer the model stability on the given example.
@@
 %
-In the scatterplot (Fig.~\ref{fig:summaryView}(c)(d)), besides showing the stability values, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{stability} number (i.e., if the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} value is likely very noisy).
+In the scatterplot (Fig.~\ref{fig:summaryView}(c)(d)), each point corresponds to a sentence pair (the user can focus the rest of the visualization on one particular instance by selection).
+To help users better assess the \emph{stability} number, we also include the number of perturbed pairs (labeled as \emph{perturbCount}).
+If the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} value is likely very noisy and unreliable.
 %For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.

### 2018-06-22 paper/task.tex
finalize change in section 5

@@
 As a result, the domain experts rely on an exploration-centric approach to conduct error analysis and obtain intuition.
-%
-There is little one can learn when everything is behaving as expected, and therefore,
-observing how models make mistakes under various scenarios is at the center of such a process.
-The experts often start with simple failure examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction.
-This exercise helps isolate where in the input likely contribute to the failures.
+%There is little one can learn when everything is behaving as expected, and therefore, observing how models make mistakes under various scenarios is at the center of such a process.
+The experts often start with simple examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction (and potential failures).
+This exercise helps the domain experts reason about the relationship between input elements and the predicted results.
 For many NLP models, the attention information (see Section~\ref{sec:attention}) is essential to infer the mechanism of the model.
@@
 %\shusen{
+%As discussed previously, the perturbation-driven scheme is at the core 
 To support the exploratory workflow for analyzing NLI models,
-we aim to address the following tasks based on our extensive discussions with NLP experts.
-%}
+we design the proposed tool to address the following tasks based on the discussions with NLP experts.
 
+\vspace {-2mm}
 \begin{itemize}
@@
 \end{itemize}
+\vspace {-2mm}
 
-In Section~\ref{sec:caseStudy}, we will discussion in detail how we can utilize the proposed tool to address these tasks (the application scenarios 1,2,3 corresponds to \textbf{T1-T3}, respectively).
+In Section~\ref{sec:caseStudy}, we will illustrate how to utilize the proposed tool for these tasks (the application scenarios 1,2,3 corresponds to \textbf{T1-T3}, respectively).
 

### 2018-06-23 paper/itemizedReviewResponse.txt
update response letter

@@
 Summary of major changes:
-- Revised section 6 to better convey the relationship between the different scenarios and provide further clarification on the result observed in 6.3.
+- Revised section 6 to better convey the relationship among the different scenarios and provide further clarification on the result observed in 6.3.
 - Revised the introduction to remove hyperbole words, clarify the NLP vs. CNN data modality comparison, and simplify the contribution list.
@@
 
-A: The domain experts find this observation very interesting and suggest a preliminary interpretation.
+A: The domain experts indeed find this observation very interesting and suggest a preliminary interpretation.
 They believe the attention provides a way to compose word semantics.
 Individual word semantics are yielded from the encoder and input embedding, while the composed semantics participate in classification layer.
-From this analysis, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in classifier).
+From the result from Scenario 3, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in classifier).
 The encoder and classifier layer can swiftly adjust weights for word/composed semantics to correct prediction.
@@
 A: We had added additional details of the collaboration at the beginning of section 4, including the number of NLP collaborators, frequency, duration of the meeting period for the proposed work.
+And we also revised the motivation for these tasks and pointed out their connection with the scenarios discussion in section 6.
 
@@
 A: The simplification is achieved by replacing the children of the dependency tree structure with the parents.
-We assume by focusing on the more important grammar structure, we can remove the decorative words and the reduce sentence length to focus on the more crucial part of the sentences.
-We have revise the section 5.2 to clarify the simplification process.
+We assume by focusing on the more important grammar structure, we can remove the decorative words and reduce sentence length to focus on the more crucial part of the sentences.
+We have revised the section 5.2 to clarify the simplification process.
 
@@
 A: We employed the standard kernel density estimation technique in 2D.
-As stated in Section 5.3, the primary motivation is to highlight overlapped point (where multiple predictions fall on top of/near each other) and identify outliers.
+As stated in Section 5.3, the primary motivation is to highlight overlapped points (where multiple predictions fall on top of/near each other) and identify outliers.
 We have included the description for density computation in Section 5.3.
@@
 
-A: Thanks for catching the ordering problem and providing a solution.
+A: We thank the reviewer for catching the ordering problem and providing a solution.
 To address the issue, we added references to the optimization discussed in section 5.4 at the beginning of section 5 as well as in section 5.3.
 We didn't move all the optimization discussion at the beginning of section 5, since we believe presenting details of the all three perturbations (input, attention, prediction) without any discussion about the interface can also be very confusing.
-And the separation between the operation and UI component may also make the description hard to read (require the reader to refer back to the computation discussion when describing the user interface).
+And the separation between the operation and UI component may also make the description harder to read (require the reader to refer back to the computation discussion when reading about the user interface).
 We believe the revised version provide a decent tradeoff.
@@
 The proposed API allows the user to include only the view that is necessary for the given task.
-For new task (i.e., machine translation), we do not need to include the prediction view for the NLI task.
+For a new task (i.e., machine translation), we do not need to include the prediction view for the NLI task.
 We can reuse the attention views to representing the alignment between the original sentence and the translated sentence and introduce new views for visualizing other information that may not present in the NLI model.
@@
 In the proposed work, the challenge of using gradient-based method in NLP actually inspired us to utilize perturbation.
-This point is partly discussion in the introduction where the difference between NLP and CV is highlighted (image has a differentiable domain).
+This point is partly discussed in the introduction where the difference between NLP and CV is highlighted (image has a continuous domain whereas words are discrete).
 
@@
 A: We didn't design a specific list of tasks and the corresponding answers mostly due to the the open-ended analysis goal.
-If the user didn't follow the particular exploration path the designer of the question goes, he/she might find some unexpected result that may not directly correspond to the "correct" answer, but instead viewing the problem from a different perspective.
-However, we do believe extensive evaluation the system is extremely important.
+If the user didn't follow the particular exploration path the designer of the question goes, he/she might find some result that not directly related to the "correct" answer.
+However, that does not mean the analysis is wrong, they just approach the data from a different perspective.
+However, we do believe extensive evaluation is extremely important for improving the usability of the tool.
 We plan to recruit more domain experts to test and evaluate the system in the future.
@@
 
-A: Thanks for pointing out the grammar issues, we have fixed the mentioned problem. And the renewed version has been through a copy edit pass by an editor.
+A: Thanks for pointing out the grammar issues, we have fixed the mentioned problems. And the renewed version has been through a copy edit pass by an editor.
 
@@
 A recurring pattern we noticed is illustrated in Fig.
-9(d), where the given sentence pair has low stability due to the fact the original prediction is a boundary prediction (probability is in between two classes).
-In addition, the perturbation procedure will also affect the pattern as the longer sentence will likely have more perturbed variations (contains more nouns and verbs).
-We include a brief discussion on the potential variability caused by the perturbation procedure in section 5.4.
+9(d), where the given sentence pair has low stability because the original prediction is a boundary prediction (probability is in between two classes).
+In addition, the perturbation procedure will also affect the pattern as longer sentences will likely have more varied perturbations (contains more nouns and verbs).
+We include a brief discussion on the variability caused by the perturbation procedure in section 5.4.
 
@@
 
-A: The curve patterns in the Figure 8d are likely caused by the different number of words that was perturbed (i.e., each line pattern corresponds to sentence pairs that include the same numbers of nouns plus verbs that will be perturbed).
-This demonstrates the added variation the perturbation bring into the system.
-We include a brief discussion on the additional variability caused by the perturbation procedure and sentence length in section 5.4.
+A: The curve patterns in the Figure 8d are likely caused by the different number of words that was perturbed (i.e., each line pattern corresponds to sentence pairs that include the same numbers of nouns plus verbs that was perturbed).
+This demonstrated the added variation the perturbation procedure bring into the system.
+We include a brief discussion on the additional variability caused by the perturbation procedure and sentence length in section 5.3.
 
@@
 
-A: The key rationale for collapsing the sentence to reduce the length while still preserving the primary structure of the sentence.
-Therefore, the collapsing operation will significantly improve the scalability of the show a long sentence.
+A: The key motivation for collapsing the sentence is to reduce the length while still preserving the primary structure of the sentence.
+Therefore, the collapsing operation often will significantly improve the scalability when showing a long sentence.
 However, it may not suitable for a whole paragraph (multiple sentences), when the length of collapsed sentence can still be too long to be effectively represented in the matrix or bipartite graph view.
-For the task such as machine comprehension, in which the context paragraph and be extremely long, we likely will need a hierarchical type of structure.
+For the task such as machine comprehension, in which the context paragraph and be extremely long, we likely will need a hierarchical visual encoding.
 
@@
 Therefore, it does not have a direct connection to the word embedding dimension or language features.
-It is a benchmark dataset for natural language processing task, which can be attacked by different types of models.
+It is a benchmark dataset for natural language processing task, which can be solved by different types of models.
 In our case, we investigated a typical neural network based approach.
@@
 
-A: Since we have utilized Unicode text encoding throughout the code, the proposed system can be easily adapting to other alphabetical languages (however, we have not tested the capability).
+A: Since we have utilized Unicode text encoding throughout the code base, the proposed system can be easily adapting to other alphabetical languages (however, we have not tested the capability).
 One potential challenge may be originated from NLP training dataset, as there are not many large-scale training data in languages other than English.
@@
 A: We have revised the last paragraph of the introduction to highlight the visualization contributions.
-The text following "Moreover, we propose..." is not the only place describe visualization contributions, the integrated model pipeline that allows user perturbation in all stages is another contribution, the same holds for the visual encoding for the prediction for the NLI problem.
+The text following "Moreover, we propose..." is not the only place that describs visualization contributions, the integrated model pipeline that allows user perturbation in all stages is another major contribution, the same holds for the visual encoding for the prediction of the NLI problem.
 
@@
 It is an essential part of the paper which make it self-contained.
-In addition, a lot of the technical details is directly connected to how the visualization encoding is designed (such as the attention view and prediction view).
+In addition, a lot of the technical details is directly connected to how the visualization encoding is designed/used (such as the attention view and prediction view).
 Without a sufficient understanding of the model and related NLP background, it would be impossible for the reader to understand the purpose of most views and the application scenarios.
@@
 
-A: One can expand the text box to include multiple lines to show the longer sentence. There is no particular encoding here since we are just showing the raw text.
+A: One can expand the text box to include multiple lines to show longer sentences. There is no special encoding here since we are just showing the raw text.
 
@@
 
-A: If the sentence structures are drastically different, the matrix view may be the better option as the structure difference likely result in crossed lines in the bipartite graph view, which can lead to poorer perception.
+A: If the sentence structures are not drastically different, the matrix view will still be effective which often highlight alignment as entries in the matrix diagnal.
 The most significant benefit of the graph is the ability for the domain expert to see the connection between words directly.
-In the matrix, one needs to first identify the high-value entry and then finding the corresponding row and column to recognize the words.
+In the matrix, one needs to first identify the high-value entry and then find the row and column then identify the corresponding words.
 If there are multiple correspondences, the user needs to check them one by one in the matrix view.
@@
 
-A: For the given model there are two attention matrices, one have row normalization while the other has column normalization.
-We follow the same rule to apply renormalization after sentence collapsing.
+A: For the given model, there are two attention matrices, one have row normalization while the other has column normalization of the raw attention.
+We follow the same rule when applying renormalization after sentence collapsing on the raw attention.
 
@@
 There is a trade-off between visual clutter and text readability.
-The more collapse is equal to less visual clutter, but likely reduce the readability of the text.
-The From our experiment, we notice the NLP experts have a far better capability to understand the collapsed sentence compared to others.
-The desired level should be a good trade-off based on the expert's preference.
+More collapsing is equal to less visual clutter, but it likely also reduce the readability of the text.
+From our experiment, we noticed the NLP experts have a far better capability to understand the collapsed sentence compared to others.
+The desired level should provide a good trade-off based on the expert's preference.
 
@@
 
-A: We make sure to only compute the comparison when the two matrices are of same size and utilizing the same normalization pattern.
+A: We make sure to only compute the comparison when the two matrices are of same size and utilizes the same normalization pattern.
 
@@
 A: The MIRA optimization process indeed introduces unpredictability and opaqueness in the solution.
-To mitigate the limitation, we provide a summary of the parameter changes in the pipeline view to help reveal the effect of the optimization on the parameters.
+To mitigate the limitation, we provide a summary of the parameter changes (histogram) in the pipeline view to help reveal the effect of the optimization on the parameters.
 Moreover, we can also utilize the attention visualization to interpret the impact of the optimization.
 Finally, our MIRA optimization is a simplified version that only added a L2 regularization on the weight change during backpropagation.
-Compared to an end-to-end neural network (which is often referred to as a black box) this optimization has a more restricted setting that is easier to interpret as we are only fitting the model to the given instance.
+Compared to an end-to-end neural network (which is often referred to as a black box) this optimization has a more restricted setting that is easier to interpret and we are only fitting the model to the given instance.
 
@@
 However, we do think a confusion matrix like encoding could also be beneficial.
-In the future, we plan to add the confusion matrix as an alternative so that the user can use either one of them based on their preference.
+In the future, we plan to add the confusion matrix as an alternative so that the users can use either one of them based on their preference.
 
@@
 A: We removed/replaced the words mentioned by the reviewer.
-For example, we updated the first sentence to "Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications."
+For example, we updated the first sentence to "Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications.".
+The revised paper also went through a copy editing pass by an editor.
 
@@
 We included a brief discussion on how these scenarios related to each other and expanded the scenarios 3 to include domain experts'  interpretation of the result.
-We didn't following a specific exploration path of a single user, because they may focus on only one or two scenarios and repeatedly applied the same analysis on different data, which may not be the best way to showcase the variety of the functionality this tool can provide.
+We didn't following a specific exploration path of a single user, because they (from our case study) often focus on only one or two scenarios and repeatedly applied the same analysis on different data, which may not be the best way to showcase the variety of the functionalities this tool provides.
 
@@
 In addition, in CNN we often can reveal human interpretable neuron filter (but these methods can not be easily generalized for NLP), whereas the attention is often the only interpretable part of the NLP model.
-We have updated the description in the introduction to better convey this message.
+We have revised the description in the introduction to better convey this message.
 
@@
 
-A: The perturbation of nouns and verbs on itself is not novel from NLP perspective, and truly solving the challenge of producing grammatically correct and meaningful perturbation/paraphrasing is still an open research area.
+A: The perturbation of nouns and verbs on itself is not novel from NLP perspective.
+And truly solving the challenge of producing grammatically correct and meaningful perturbation/paraphrasing is still an open research area.
 In our case, we believe the novelty comes from the integration of the model with the three-stage perturbation scheme in an explorable visual analytic system.
@@
 
-A: We moved the description of the collaboration into the beginning of section 4, in which we described the number of NLP experts, frequency, and the duration of the meeting for this specific projects.
+A: We moved the description of the collaboration into the beginning of section 4, in which we described the number of NLP experts, frequency, and the duration of the meetings for this specific projects.
 We also added a reference to application scenarios that corresponds to the tasks to help instantiate the more abstract concepts.
@@
 
-A: In the current system, we did not record the user interaction/correction result.
-The MIRA optimization update may correct the model for the given example (to some extend overfit to the example), however, we don't think there is a guarantee that the fix can be readily generalized to other cases.
-Also, the ambiguity between pile and heap may also originate from the word embedding (the numerical input representation for words).
+A: In the current system, we do not record the user interaction/correction result.
+The MIRA optimization update may correct the model for the given example (to some extend overfit to the example).
+However, we don't think there is a guarantee that the fix can be readily generalized to other cases.
+Also, the ambiguity between pile and heap may also originate from the word embedding (the numerical representation for words).
 The proposed system suggests to NLP experts that the ambiguity between pile and heap is likely the cause of the incorrect prediction.
-The experts can choose to dive further and close examine the root cause.
+The experts can choose to dive further and examine the root cause.
 
@@
 A: As discussed in the answer for Q1, the domain experts mentioned that they are interested in exploring more from NLP perspective to understand this result fully.
-They also provide some preliminary explanation.
-We included them in the revised 6.3 section.
+They also provide some preliminary explanation, which we included in section 6.3.
 
@@
 
-A: We added an overview at the beginning of section 6 to illustrate how different tasks related to one another and provided additional discussion on section 6.3 to dive deeper into the interpretation of the result.
+A: We added an overview at the beginning of section 6 to illustrate how different tasks related to one another and provided additional discussion in section 6.3 to dive deeper into the interpretation of the result.

### 2018-06-23 paper/pipeline.tex
update response letter

@@
 In the proposed tool, we obtain the target parameters by the following optimization:
+
 \begin{equation}
+\vspace{-1mm}
 \underset{\mathbf{W}'}{\mathrm{argmin}}( C \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W_o}||^2)
+%\vspace{-0.5mm}
 \end{equation}
+
 where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural network model, $\mathbf{W_o}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the updated parameters, and $C$ is the weighting term, which determines whether we intended to emphasize more on obtaining better fitting or deviating less from the original model.

### 2018-06-23 paper/predSummary.tex
update response letter

@@
 %Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
-We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) shows the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
+We summarized all prediction results of $10k$ sentence pairs in (a).
+The green block indicates correct predictions, the orange block indicates wrong predictions.
+%The tag on the node (e.g., E/E, E/N) encodes different types of the ground truth and the predicted label combinations (i.e., E/N is Entailment/Neural).
 %
-The user can click on the treemap node to focus on the specific type of scenarios (e.g., E/E) to automatically reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
+The user can click on a treemap node to focus on the specific type of scenarios (e.g., E/E, indicating both the ground truth and the predicted label are Entailment) to automatically reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
+%
 The selection can be further narrowed down by selecting the bin in the histogram.

### 2018-06-23 paper/itemizedReviewResponse.txt
spelling fix

@@
 
-We greatly appreciate all reviewers' valuable comments. The summary of major changes are listed below. We have itemized the 44 questions/comments and answer each individually.
+We greatly appreciate all reviewers' valuable comments. The summary of major changes is listed below. We have itemized the 44 questions/comments and answer each individually.
 
@@
 - Revised the introduction to remove hyperbole words, clarify the NLP vs. CNN data modality comparison, and simplify the contribution list.
-- Clarified the domain experts' involvement at the beginning of section 4, and link the task with the application scenarios.
+- Clarified the domain experts' involvement at the beginning of section 4 and link the task with the application scenarios.
 - Revised section 5 to better explain the user interactions and add discussion on how to interpret the visual encodings.
@@
 A: The exact computation of attention can vary from model to model despite the shared overall concept, i.e., the alignment between words.
-As a result, when we discuss the general concept of attention we can not fix on a single mathematical formulation.
+As a result, when we discuss the general concept of attention we cannot fix on a single mathematical formulation.
 The exact formulation for the model we investigated is discussed in Appendix A.
@@
 A: The curve patterns in the Figure 8d are likely caused by the different number of words that was perturbed (i.e., each line pattern corresponds to sentence pairs that include the same numbers of nouns plus verbs that was perturbed).
-This demonstrated the added variation the perturbation procedure bring into the system.
+This demonstrated the added variation the perturbation procedure brings into the system.
 We include a brief discussion on the additional variability caused by the perturbation procedure and sentence length in section 5.3.
@@
 A: We have revised the last paragraph of the introduction to highlight the visualization contributions.
-The text following "Moreover, we propose..." is not the only place that describs visualization contributions, the integrated model pipeline that allows user perturbation in all stages is another major contribution, the same holds for the visual encoding for the prediction of the NLI problem.
+The text following "Moreover, we propose..." is not the only place that describes visualization contributions, the integrated model pipeline that allows user perturbation in all stages is another major contribution, the same holds for the visual encoding for the prediction of the NLI problem.
 
@@
 
-A: If the sentence structures are not drastically different, the matrix view will still be effective which often highlight alignment as entries in the matrix diagnal.
+A: If the sentence structures are not drastically different, the matrix view will still be effective which often highlight alignment as entries in the matrix diagonal.
 The most significant benefit of the graph is the ability for the domain expert to see the connection between words directly.
@@
 For example, we updated the first sentence to "Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications.".
-The revised paper also went through a copy editing pass by an editor.
+The revised paper also went through a copy-editing pass by an editor.
 
@@
 Then the user can close examine the individual pair as shown in scenarios 2, 3, 4 (depend on what question they want to ask).
-We included a brief discussion on how these scenarios related to each other and expanded the scenarios 3 to include domain experts'  interpretation of the result.
-We didn't following a specific exploration path of a single user, because they (from our case study) often focus on only one or two scenarios and repeatedly applied the same analysis on different data, which may not be the best way to showcase the variety of the functionalities this tool provides.
+We included a brief discussion on how these scenarios related to each other and expanded the scenarios 3 to include domain experts’ interpretation of the result.
+We didn't follow a specific exploration path of a single user, because they (from our case study) often focus on only one or two scenarios and repeatedly applied the same analysis on different data, which may not be the best way to showcase the variety of the functionalities this tool provides.
 
@@
 The difference has introduced additional challenge especially regarding optimization as well as interpretation.
-In addition, in CNN we often can reveal human interpretable neuron filter (but these methods can not be easily generalized for NLP), whereas the attention is often the only interpretable part of the NLP model.
+In addition, in CNN we often can reveal human interpretable neuron filter (but these methods cannot be easily generalized for NLP), whereas the attention is often the only interpretable part of the NLP model.
 We have revised the description in the introduction to better convey this message.
@@
 
-A: We moved the description of the collaboration into the beginning of section 4, in which we described the number of NLP experts, frequency, and the duration of the meetings for this specific projects.
+A: We moved the description of the collaboration into the beginning of section 4, in which we described the number of NLP experts, frequency, and the duration of the meetings for this specific project.
 We also added a reference to application scenarios that corresponds to the tasks to help instantiate the more abstract concepts.
@@
 
-Q42, In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile?
-with ?heap?).
+Q42, In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching "pile" with "heap").
 This updates the system and changes the inference output.

### 2018-06-23 paper/itemizedReviewResponse.txt
update figure

@@
 But the attention layer, which only works on how individual words are aligned, affects the prediction less significantly.
-Recent works also support this observation in word embeddings, e.g., ELMo~\cite{salant2017contextualized}, where better word embeddings can substantially benefit a model.
+Recent works also support this observation in word embeddings, e.g., ELMo by Salant et al., where better word embeddings can substantially benefit a model.
 However, it by no means implies attention is not useful, as it serves as a way to compose word semantics although it does not directly output that.
@@
 
-A: We've added caption "attention" to the color scale as well as the "frequency" captions to the histograms.
+A: We've added "attention" label to the color scale and the "frequency" label to the histograms.
 

### 2018-06-26 paper/intro.tex
grammar fix

@@
 %Based on some stunning recent advances, neural networks based machine learning approaches have gained unprecedented popularity, and have been adopted in a wide variety of applications.
-Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications.
+As demonstrated by many recent successes, neural network-based machine learning approaches have garnered increasing popularity and have been adopted in a wide variety of applications.
 %
@@
 %
-Interpreting the internal mechanism and analyzing how predictions are made is critical to both the design and deployment of a model.
+Interpreting the internal mechanism and analyzing how predictions are made are critical for both the design and deployment of a model.
 More importantly, the ability to pinpoint where and how an error is made and propose hypotheses for the cause of the failure is key to identifying the limitations of and improving upon existing models.
@@
 % Beside explore the internal states of the model, understand how different parts of the model work together and how one may affect one another is as or if not more important.
-Despite a number of recent advances, the majority of existing techniques study the model as an invariant object, where the model's behaviors are recorded and analyzed in an offline fashion.
+Despite a number of recent advances, most of existing techniques study the model as an invariant object, where the model's behaviors are recorded and analyzed in an offline fashion.
 %
@@
 And how would it affect the internal state we care about?
-These types of queries form a natural way to gain understanding and develop hypotheses of the model mechanisms by \emph{interrogating} how the components of a model interact with each other in a dynamic setting.
+These types of queries form a natural way to gain an understanding and develop hypotheses of the model mechanisms by \emph{interrogating} how the components of a model interact with each other in a dynamic setting.
 Hypothetically, we can code specialized experiments for each of these scenarios.
@@
 
-Here, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and direct online query/optimization of the neural network model.
+Here, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and the direct online query/optimization of the neural network model.
 Instead of viewing the models as invariant objects, we approach the interpretability challenge by studying them in a dynamic environment.
@@
 %
-In the simplest form, the inference task asks whether the
-relationship between \textbf{sentence A} and \textbf{sentence B}: (1) is \emph{entailment} (one can infer \textbf{B} from \textbf{A}), (2) \emph{contradiction} (\textbf{B} disagrees with \textbf{A}) or (3) is \emph{neutral} (\textbf{A} and \textbf{B} talk about different/unrelated things).
+In its simplest form, the inference task asks whether the
+relationship between \textbf{sentence A} and \textbf{sentence B}: is (1) \emph{entailment} (one can infer \textbf{B} from \textbf{A}), (2) \emph{contradiction} (\textbf{B} disagrees with \textbf{A}) or (3) \emph{neutral} (\textbf{A} and \textbf{B} talk about different/unrelated things).
 % we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), if they contradict with each other (\emph{contradiction}), or whether two sentences talk about different/unrelated things (\emph{neutral}).
-Natural language inference addresses the fundamental challenge of identifying semantic relationships between sentences, and is a core NLP task (see Section~\ref{sec:languageInference} for details).
+Natural language inference addresses the fundamental challenge of identifying semantic relationships between sentences and is a core NLP task (see Section~\ref{sec:languageInference} for details).
 
@@
 (Section~\ref{sec:attention}). Intuitively, attention asks which parts of the
-input are deemed more important for making a prediction.
-The attention is often represented via weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
+input are deemed more important for making a prediction. Attention is often represented via weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
 %
 %\shusen{seems repeated some of the previous points}
-There have been many speculations on how attention works in various models.
-The proposed tool introduces a perturbation-driven visual analytics enviroment, where the domain experts can study how changes in sentence input, attention, or prediction affect each other, which helps them develop deeper intuitive and alternative hypotheses.
+There have been many theories about how attention works in various models.
+The proposed tool introduces a perturbation-driven visual analytics environment, where the domain experts can study how changes in sentence input, attention, or prediction affect each other, which helps the experts develop deeper intuitive and alternative hypotheses.
 %we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention.

### 2018-06-26 paper/paper_entailVis.tex
space saving
update task
adjust figures
grammar fix

@@
 
-%make paper compact
-\setlength{\parskip}{0.04cm}
-\setlength{\parindent}{0.7em}
-
 %% If you are submitting a paper to a conference for review with a double
@@
 However, this rapid progress also brings enormous challenges.
-The opaque nature of neural network model leads to hard-to-debug-systems and difficult to interpret mechanisms.
-Here, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, and prediction while observing changes in other parts of the pipeline.
-We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states, and interpret and form hypothesize about fundamental model mechanisms such as attention.
+The opaque nature of a neural network model leads to hard-to-debug-systems and difficult-to-interpret mechanisms.
+Here, we introduce a visualization system that, through a tight yet flexible integration between visualization elements and the underlying model, allows a user to interrogate the model by perturbing the input, internal state, and prediction while observing changes in other parts of the pipeline.
+We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states, and interpret and form hypotheses about fundamental model mechanisms such as attention.
 } % end of abstract
@@
  \centering
- \vspace{-4mm}
+ \vspace{-6mm}
   \caption{
-The interface of the NLIZE system.
-During exploration, we can filter through a large number of sentence pairs summarized in (a) and the current selected pair is displayed in (b).
+The interface of the proposed system.
+During exploration, we can filter through a large number of sentence pairs summarized in (a).
+the current selected pair is displayed in (b).
 The model internal information (attention) is displayed in (d) and (e).
@@
 %% if specified like this the section will be committed in review mode
-% \acknowledgments{
-% The authors wish to thank A, B, and C. This work was supported in part by
-% a grant from XYZ (\# 12345-67890).}
+\acknowledgments{
+The authors wish to thank A, B, and C. This work was supported in part by
+a grant from XYZ (\# 12345-67890).
+}
 

### 2018-06-26 paper/background.tex
grammar fix

@@
 \section{Background}
-The target audiences of the proposed tool are domain experts who analyze and develop NLP models.
+The target audience of the proposed tool is domain experts who analyze and develop NLP models.
 Therefore, certain background knowledge in NLP is required to fully understand and appreciate the technique discussed in this paper.
-In this section, we first explain the definition of natural language inference (NLI) task and how it fits into the grand challenges in NLP.
+In this section, we first explain the definition of a natural language inference (NLI) task and how it fits into the grand challenges in NLP.
 Then, we examine the common architectural characteristics shared by many state-of-the-art neural network models.
@@
 
-At first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
+At first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish the entailment and contradiction relationship is fundamental to understanding natural language at large.
 %
-Considering the ambiguousness of natural language and polysemy of words, the inference task can become quite challenging (especially from the learning algorithm's point of view).
+Considering the ambiguousness of natural language and the polysemy of words, the inference task can become quite challenging (especially from the learning algorithm's point of view).
 Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO.
@@
 %
-Since all these three stages of the model are trained jointly in an end-to-end fashion, it is important to explore the interaction between intermediate representations and predictions to make sense of how predictions are made inside such a model.
+Since all three stages of the model are trained jointly in an end-to-end fashion, it is important to explore the interaction between intermediate representations and predictions to make sense of how predictions are made inside such a model.
 
@@
 %As the only interpretable part of the internal state of the network, understanding how attention information 
-Recently, attention has contributed to the strong performance of many NLP models~\cite{parikh2016emnlp,rush2015neural,yang2016hierarchical,seo2016bidirectional,schwartz2017high}.
+Recently, the attention mechanism has contributed to the strong performance of many NLP models~\cite{parikh2016emnlp,rush2015neural,yang2016hierarchical,seo2016bidirectional,schwartz2017high}.
 
@@
   \vspace{-2mm}
- \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks.
+ \caption{Attention can be naturally explained as a form of alignment that exposes an interpretable layer in end-to-end neural networks.
 On the left, the matrix shows the attention between the premise and hypothesis pair.
@@
 
-For natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft alignment between words in the premise and the words in the hypothesis.
+For natural language inference task, as illustrated in Fig.~\ref{fig:attention}, the attention information can be represented as a matrix describing the soft alignment between words in the premise and words in the hypothesis.
 As we can see in this example, the higher values indicate significant alignments between words.
@@
 Interestingly, the difference between the subject words does not affect their alignment.
-The classification stage can then utilize this information to determine the subject of the sentence is different, and therefore, despite the other part of the sentences are identical, the relationship between the premise and the hypothesis is neutral.
+The classification stage can then utilize this information to determine if the subject of the sentence is different, and therefore, despite the other part of the sentences being identical, the relationship between the premise and the hypothesis is neutral.
 

### 2018-06-26 paper/relatedWorks.tex
grammar fix

@@
 %
-These methods either identify the pattern that maximally activates a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures?), or reveals what areas in the input that contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
+These methods either identify the pattern that maximally activates a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer capture?), or reveals what areas in the input contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
 %
-Besides the techniques designed for specific types of models, a few work~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications.
+Besides the techniques designed for specific types of models, a few study~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications.
 In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understand snapshot of the classifier near a specific input.
 %
-Despite being invaluable for generating a human understandable explanation, however, the lack of the ability to access and explore the internal states of the system limits their application.
+Despite being invaluable for generating a human understandable explanation, however, the lack of ability to access and explore the internal states of the system limits their application.
 %which is vitally important for making sense of the inner works of a model,
@@
 Due to the effectiveness of exploring complex relationships, visualization has long been adopted for interpreting neural network models~\cite{TzengMa2005}.
-Recently, the increasing demand for interpretability for machine learning models has motivated the introduction of many visualization work that are dedicated to neural network models.
+Recently, the increasing demand for interpretability for machine learning models has motivated the introduction of many visualization studies that are dedicated to neural network models.
 % The classification~\cite{KrausePererNg2016}
@@
 %
-In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzed classification errors in convolutional neural networks (CNN) and answered the question of whether class hierarchy is learned in the network.
+In~\cite{BilalJourablooYe2018}, Bilal et al. analyzed classification errors in convolutional neural networks (CNN) and answered the question of whether class hierarchy is learned in the network.
 %
-The DeepEyes~\cite{Pezzotti2018} focused on analyzing the training process of CNN, which provided domain experts design guideline of the deep neutral network architecture.
+DeepEyes~\cite{Pezzotti2018} focused on analyzing the training process of CNN, which provided domain experts design guidelines for deep neutral network architecture.
 %
-The ActiVis~\cite{KahngAndrewsKalro2018} introduced an interactive system tailored for tuning industry-scale neural networks in Facebook.
+ActiVis~\cite{KahngAndrewsKalro2018} introduced an interactive system tailored for tuning industry-scale neural networks in Facebook.
 The TensorFlow Graph Visualizer~\cite{Wongsuphasawat2018} work designed a hierarchical visual representation to encode complex computation graphs of deep neural networks for the TensorFlow framework~\cite{Abadi2016}.
@@
 \textbf{Visualization of NLP Models.}
-Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studies have been dedicated to neural language processing models.
+Compared to many studies for making sense of convolutional neural networks, relatively fewer studies have been dedicated to neural language processing models.
 %
@@
 The RNNbow~\cite{CashmanPattersonMosca2017} system helps domain experts understand how the model is trained by visualizing the backpropagation gradient information.
-The LSTMvis~\cite{StrobeltGehrmannPfister2018} work employs a line plot style visual encoding to represent the time varying hidden states of the recurrent neural network.
-The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrates how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space (e.g., word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}).
+The LSTMvis~\cite{StrobeltGehrmannPfister2018} work employs a line-plot style visual encoding to represent the time-varying hidden states of the recurrent neural network.
+The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrates how semantic relationships can be recovered by linear projections in the high-dimensional word embedding space (e.g., word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}).
 %As discussed in the introduction, the experts guided exploration calls for the ability to interact with internal of the model in a dynamic setting.
@@
 All the previously discussed NLP model visualization works either focus on the training process or examine the trained model as a fixed object.
-In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that is not possible before.
+In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that has not been possible before.
 %In addition, instead of exploring a language model or low-level, the proposed method focus on a specific NLP task, which provide insight on

### 2018-06-26 paper/discussion.tex
grammar fix

@@
 \section{Discussion}
-The current setup for the proposed tool is suitable only for natural language inference task.
+The current setup for the proposed tool is suitable only for the natural language inference task.
 However, due to the modular design and the many shared attributions among the end-to-end NLP models, we can readily extend the system to handle other tasks.
@@
 
-To conclude, this work introduces a perturbation-driven visual interrogation system that provides experts with a streamlined exploration environment for testing hypothesis and obtaining intuition about the model.
+To conclude, this work introduces a perturbation-driven visual interrogation system that provides experts with a streamlined exploration environment for testing hypotheses and obtaining intuition about the model.
 The proposed system frees the researchers from interruptions and tedious operations, thereby allowing them to focus on more productive activities.

### 2018-06-26 paper/evaluation.tex
grammar fix

@@
 However, since these two NLP experts have been heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.
-To uncover the limitation and identify areas for improvement, we gathered a wider audience from either visualization (4 researchers, including 3 Ph.D.-level students and one postdoc researcher) or NLP backgrounds (5 Ph.D.-level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.
+To uncover the limitation and identify areas for improvement, we gathered a wider audience from either visualization (four researchers, including three Ph.D.-level students and one postdoc researcher) or NLP backgrounds (five Ph.D.-level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.
 
@@
 We then demonstrated the features of the tool in detail.
-After that, we answered questions and seek feedback.
+After that, we answered questions and sought feedback.
 %
@@
 
-We conduct an individual revaluation session with each participant from the NLP group, in which the participant is given 30 minutes to experiment with the tool after an overall feature demonstration. 
+We conducted an individual revaluation session with each participant from the NLP group, in which the participant was given 30 minutes to experiment with the tool after an overall feature demonstration.
 %
-Since both the matrix and graph-based visual encodings are the most common attention representations used in the NLP literature, most participants can utilize them immediately and find the linked highlighting feature of the two views quite useful.
+Since both the matrix and graph-based visual encodings were the most common attention representations used in the NLP literature, most participants can utilize them immediately and find the linked highlighting feature of the two views quite useful.
 % 
-Once the participants familiarize with the tool, they often try to type two similar sentences and examine the attention and prediction.
+Once the participants become familiar with the tool, they often try to type two similar sentences and examine the attention and prediction.
 After that, they will modify some words, or negate the hypothesis sentence, and then check the attention and prediction again.
@@
 %
-Another participant comments that the ability to enable or disable model parameter update in the pipeline view is beneficial.
+Another participant comments that the ability to enable or disable the model parameter update in the pipeline view is beneficial.
 
@@
 Also, for the participants who do not focus on NLI research, understanding all the views at first can be a bit challenging.
-However, this issue can be addressed by the modular design, as the user can simply enable, only the sentence, attention, and prediction views.
+However, this issue can be addressed by the modular design, as the user can simply enable only the sentence, attention, and prediction views.
 %

### 2018-06-26 paper/task.tex
grammar fix

@@
 The primary driving force for designing the proposed tool is the error analysis challenges faced by our long-term collaborators working on natural language inference research.
-During the entire design and development process, we worked closely with two NLP experts via weekly meetings in a period of roughly seven month, their constant evaluation and feedback have helped shape the tool we see today.
+During the entire design and development process, we worked closely with two NLP experts via weekly meetings over a period of roughly seven monthes.
+Their constant evaluation and feedback have helped shape the tool we see today.
 %}
@@
 % as well as provide feedback on the various prototyping stages of the proposed visualization.%
-The predictive accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model; however, the accuracy number alone does not provide the full story.
+Predictive accuracy has its place as an objective evaluation metric to measure the overall effectiveness of the model; however, the accuracy number alone does not provide the full story.
 For example, the model may produce correct predictions for the ``wrong'' reasons (e.g., pick up an unintended pattern in the training data that cannot be generalized in real-word scenarios).
@@
 %There is little one can learn when everything is behaving as expected, and therefore, observing how models make mistakes under various scenarios is at the center of such a process.
-The experts often start with simple examples, and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction (and potential failures).
+The experts often start with simple examples and then make minor perturbations (replace a word or phrase) to the input and observe the change in the prediction (and potential failures).
 This exercise helps the domain experts reason about the relationship between input elements and the predicted results.
@@
 Experts often print out the attention values or generate plots to visualize sentence alignment or compare attention values.
-As the experts explore more variation of similar examples, combined with their domain knowledge, they may develop hypotheses about the cause of failures, or ask additional questions that lead to further experimentation.
+As the experts explore more variation of similar examples, combined with their domain knowledge, they may develop hypotheses about the cause of failures or ask additional questions that lead to further experimentation.
 
 In such an exploration workflow, NLP researchers often need to utilize multiple scripts and manually run all the experiments.
-The batch process based approach, is not only time consuming, but also hinders the flow of reasoning which rely on obtaining instantaneous feedbacks, and making many on-the-fly adjustments.
+The batch process approach is not only time consuming, but it also hinders the flow of reasoning that relies on obtaining instantaneous feedback and making many on-the-fly adjustments.
 %
-Therefore, the expert driven exploration process can greatly benefit from the introduction of an interactive visual exploration environment, where the researchers can easily express their hypotheses and obtain quick visual feedback of the results.
+Therefore, the expert-driven exploration process can greatly benefit from the introduction of an interactive visual exploration environment, where the researchers can easily express their hypotheses and obtain quick visual feedback of the results.
 %
-Moreover, by introducing new visual encodings and summarizations, we can drastically expand the ways domain experts interact with the model, enable exploration options that previously were not possible either due to tedious manual operation or the lack of communication channels.
+Moreover, by introducing new visual encodings and summarizations, we can drastically expand the ways domain experts interact with the model, enabling exploration options that previously were not possible either due to either tedious manual operation or the lack of communication channels.
 %
@@
 To support the exploratory workflow for analyzing NLI models,
-we design the proposed tool to address the following tasks based on the discussions with NLP experts.
+we design the proposed tool to address the following tasks based on the discussions with NLP experts;
 
@@
 \begin{itemize}
-\item \textbf{T1}: Understand the stability of a prediction, i.e., how perturbations of the input affect the behavior of the model?
+\item \textbf{T1}: Understand the stability of a prediction, i.e., how do perturbations of the input affect the behavior of the model?
 
@@
 
-In Section~\ref{sec:caseStudy}, we will illustrate how to utilize the proposed tool for these tasks (the application scenarios 1,2,3 corresponds to \textbf{T1-T3}, respectively).
+In Section~\ref{sec:caseStudy}, we will illustrate how to utilize the proposed tool for these tasks (the application scenarios 1, 2, 3 correspond to \textbf{T1-T3}, respectively).
 

### 2018-06-26 paper/sentence.tex
grammar fix

@@
 %%% sentence perturbation %%%%
-The previously explored original sentences are stored in the dropdown list (on the right side of the buttons) that allow the user to revisit examined examples.
+The previously explored original sentences are stored in the dropdown list (on the right side of the buttons) that allows the user to revisit examined examples.
 Also, the user can type any sentences or modify existing text in the sentence display areas to accommodate user-defined inputs.

### 2018-06-26 paper/attention.tex
grammar fix

--- 2018-06-22 paper/attention.tex
@@
 
-As illustrated in Fig.~\ref{fig:attentionVis}, we employ two visual encodings for visualizing attention.
+As illustrated in Fig.~\ref{fig:attentionVis}, we employ graph and matrix two visual encodings for visualizing attention.
 In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
-The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
+The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blue corresponds to higher values).
 %
@@
 The matrix attention view (Fig.~\ref{fig:attentionVis}(b)), despite being more verbose and less efficient in highlighting the dominant alignment, does not have similar shortcomings.
-However, extra effort may be required for identifying the words corresponds to high-value entries in the matrix.
-Together, the graph and matrix views complement each other and provide the same information from different perspectives (a related matrix/graph visualization scheme is presented in \cite{MaKenyonForbes2015} for studying brain network).
+However, extra effort may be required for identifying the words that correspond to high-value entries in the matrix.
+Together, the graph and matrix views complement each other and provide the same information from different perspectives (a related matrix/graph visualization scheme is presented in \cite{MaKenyonForbes2015} for studying the brain network).
 %As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.
@@
 To support the ability to perturb the attention values (\textbf{T2}), we include the attention editing functionality.
-The attention matrix view is the most suitable place to conduct the edit operation since it provides a direct mapping of attention value.
+The attention matrix view is the most suitable place to conduct the editing operation since it provides a direct mapping of the attention value.
 As we can see in Fig.~\ref{fig:attentionVis}(c), when a user clicks the cell of the matrix, a sider will pop up for customizing the attention value (as the user edits the value, each row is automatically renormalized).
 %
-As illustrated in Fig.~\ref{fig:attentionVis}($a_{2}$)(f), we allow the user to compare currently and previously displayed attentions by computing and visualizing their difference.
+As illustrated in Fig.~\ref{fig:attentionVis}($a_{2}$)(f), we also allow the user to compare currently and previously displayed attentions by computing and visualizing their cell-wise differences (the user can toggle between different display modes using the C (current), P (previous), D (difference) buttons bellow the colormap).
 

### 2018-06-26 paper/prediction.tex
finalize change in section 5
grammar fix

--- 2018-06-18 paper/prediction.tex
@@
 In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle.
-Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defining a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction or entailment.
+Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defining a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction, or entailment.
 The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.
-In the triangle, the distinctly colored background (grey, light grey, and light green) indicates the regions that correspond to different labels.
+In the triangle, the distinctly colored background (gray, light gray, and light green) indicates the regions that correspond to different labels.
 The prediction result for the original sentence pair is represented by the larger yellow circle, whereas the smaller gray circles illustrate the perturbed sentence pairs.
 A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+%\shusen{
+The pattern of the perturbed pairs' prediction directly conveys the stability of the model for the given instance. 
+Here, we should also take the length of the sentence into consideration as more nouns and verbs will likely lead to more varied perturbations.
+%}
 

### 2018-06-26 paper/pipeline.tex
grammar fix

@@
 \label{sec:pipeline}
-The Pipeline view provides a direct visual representation of the three stages (encoder, attention, classifier) of the model.
+The pipeline view provides a direct visual representation of the three stages (encoder, attention, classifier) of the model.
 In the proposed tool, we allow model parameters to be updated (via an optimization) to correct a prediction error (\textbf{T3}).
@@
 % \shusen{what is the benefit of using mira?}
-Instead, we adopt the idea in \emph{margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the L2-norm of the parameter change.
+Instead, we adopt the idea in the \emph{margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the L2-norm of the parameter change.
 In the proposed tool, we obtain the target parameters by the following optimization:
@@
 %
-With this formulation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
+With this formulation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small changes with respect to the original model.
 
@@
  \caption{
-The pipeline view provides the visual representation of the three-stage (encoder, attention, classifier) of the NLI model. 
+The pipeline view provides the visual representation of the three stages (encoder, attention, classifier) of the NLI model. 
 %
@@
 The hyperparameters for this optimization are shown in (a). 
-In (b), we utilizes a graphical representation for each stage of the pipeline.
+In (b), we utilize a graphical representation for each stage of the pipeline.
 % where the user can click on the blue rectangle marked with the word ``parameter'' to enable or disable its update (the legend is shown in (d)). 
@@
 The optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a).
-Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the blue rectangle marked with the word``parameter'' (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d)).
-In Fig.~\ref{fig:pipelineView}(c), we select whether we want to use the current pipeline update setting as displayed or try all the pipeline configuration combinations (i.e., each stage can either be enabled or disabled; therefore, there are $8$ combinations in total, or $7$ if we discard the case where all stages are not enabled).
+Each stage is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the blue rectangle marked with the word ``parameter'' (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d)).
+In Fig.~\ref{fig:pipelineView}(c), we select whether we want to use the current pipeline update setting as displayed or try all the pipeline configuration combinations (i.e., each stage can be either enabled or disabled; therefore, there are $8$ combinations in total, or $7$ if we discard the case where all stages are not enabled).
 

### 2018-06-26 paper/predSummary.tex
grammar fix

@@
 The histogram shows the distribution of the prediction stability in the selected category.
-For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and the all the perturbed pairs.
-Assuming we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonymous), the stability is 0.8 if 80 out of the 100 maintain the original label.
+For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and all the perturbed pairs.
+Assuming we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonyms), the stability is 0.8 if 80 of the 100 maintain the original label.
 %The \emph{stability} measures how likely a sentence pair will change its prediction after applying minor perturbations.% which helps the expert infer the model stability on the given example.

### 2018-06-26 paper/implementation.tex
grammar fix

@@
 %
-To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models (see the code example in \textbf{Appendix B}).
+To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction and accessing attention, to link the visualization to their NLP models (see the code example in \textbf{Appendix B}).
 
@@
 In the proposed work, the NLI model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
-The visual interface is implemented in Javascript using \emph{D3.js} library , and a Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.
+The visual interface is implemented in Javascript using \emph{D3.js} library, and a Python server acts as the glue between the Javascript visualization and the \emph{pytorch} model.

### 2018-06-26 paper/application.tex
grammar fix

@@
 To illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model,
-we present five interconnected application scenarios a domain expert may employ in their analysis workflow.
-The user can start the exploration by examining the stability of prediction (Scenario 1), from which they may identify the individual instances worth further investigation (Scenario 2, 3, 4).
-Alternatively, the user can begin with handcrafted common/extreme cases (Scenario 5) and continue from there.
+we present five interconnected application scenarios domain experts may employ in their analysis workflow.
+Users can start the exploration by examining the stability of prediction (Scenario 1), from which they may identify the individual instances worth further investigation (Scenario 2, 3, 4).
+Alternatively, users can begin with handcrafted common/extreme cases (Scenario 5) and continue from there.
 %we present five application scenarios
@@
 Prediction stability assessment.
-In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type of predictions over the entire development set (10k examples).
+In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type of prediction over the entire development set (10k examples).
 The user can drill down to individual examples by using the interface described in Fig.~\ref{fig:summaryView}.
@@
 \subsection{Scenario 1: Assess the Model Prediction Stability}
-The robustness of the prediction is often hard to evaluate. However, the prediction stability provides valuable information for the researchers to better understand the model.
+The robustness of the prediction is often hard to evaluate. However, the prediction stability provides valuable information for researchers to better understand the model.
 %
@@
 Compared to other types of input (e.g., image), the perturbation of the natural language can be particularly tricky, as small alterations of words can drastically change the meaning of the sentence.
-As discussed in Section~\ref{sec:sentence}, we try to maintain the sentence semantic by replacing only words with their synonymous and only one word for each pair.
-As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert not only can examine a visual summary of the stability but also quickly dive into individual examples for a case-by-case analysis.
+As discussed in Section~\ref{sec:sentence}, we try to maintain the sentence semantic by replacing only words with their synonyms and only one word for each pair.
+As illustrated in Fig.~\ref{fig:predictStability}, by utilizing the proposed tool, the domain expert can not only examine a visual summary of the stability but also quickly dive into individual examples for a case-by-case analysis.
 
@@
 The predicted label alone provides limited information.
-Often, domain experts want to know how the model arrives at a conclusion, and if the prediction is incorrect, where in the model the error occurs?
+Often, domain experts want to know how the model arrives at a conclusion, and if the prediction is incorrect, where in the model the error occurs.
 Examining the decision-making process is not only instrumental in evaluating the model performance but also essential for hypothesizing improvement strategies for future models.
@@
 
-In the previous section, we have noticed that a minor perturbation of the sentence may result in change of the final prediction (Fig.~\ref{fig:predictStability}(e)).
+In the previous section, we have noticed that a minor perturbation of the sentence may result a change in the final prediction (Fig.~\ref{fig:predictStability}(e)).
 Here, we want to make sense of what leads to the failed prediction.
@@
 The perturbed hypothesis \textbf{H2} replaces the word \textbf{pile} with \textbf{heap} in \textbf{H1}.
-This example should be rather straightforward for the model since there are only minor differences between the \textbf{P} and \textbf{H1}/\textbf{H2}.
+This example should be rather straightforward for the model since there are only minor differences between \textbf{P} and \textbf{H1}/\textbf{H2}.
 
@@
 For example, in the sentence pair (\textbf{P}: ``A couple is taking a break from bicycling'', \textbf{H}: ``sisters sit next to their bikes''), the words \textbf{take} and \textbf{next} should not align with each other,
-yet it still produces the correct label (\emph{neutral}).% (Fig.~\ref{fig:wrongAlignRightPred}(b)).
+yet the model still predict the correct label (\emph{neutral}).% (Fig.~\ref{fig:wrongAlignRightPred}(b)).
 
@@
 %\subsection{Scenario 3: What Does It Take to Correct a Failed Prediction?}
-Up to here, we have employed perturbation for input to understand prediction robustness, and utilized the perturbation of attention (and input) to infer the model decision-making process.
+Up to here, we have employed perturbation for input to understand prediction robustness and utilized the perturbation of attention (and input) to infer the model decision-making process.
 Both these perturbation operations rely on forward propagation in the pipeline and assume the model parameter remains unchanged.
@@
 However, the model produces an incorrect label \emph{entailment}.
-The domain expert reassigns the prediction to \emph{neutral}, which triggers the prediction update optimization for $7$ different pipeline configurations.
+The domain expert reassigns the prediction to \emph{neutral}, which triggers the prediction update optimization for seven different pipeline configurations.
 Four configurations are shown in Fig.~\ref{fig:pipelineUpdate}(a)(b)(c)(d).
@@
 They believe the attention provides a way to compose word semantics.
-Individual word semantics are yielded from the encoder and input embedding, while the composed semantics participate in classification layer.
-From this analysis, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in classifier).
+Individual word semantics are yielded from the encoder and input embedding, whereas the composed semantics participate in the classification layer.
+From this analysis, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in the classifier).
 The encoder and classifier layer can swiftly adjust weights for word/composed semantics to correct prediction.
-But the attention layer, which only works on how individual words are aligned, affects the prediction less significantly.
+However, the attention layer, which only works on how individual words are aligned, affects the prediction less significantly.
 Recent works also support this observation in word embeddings, e.g., ELMo~\cite{salant2017contextualized}, where better word embeddings can substantially benefit a model.
-However, it by no means implies attention is not useful, as it serves as a way to compose word semantics.
+However, word embeddings by no means implies attention is not useful, because it serves as a way to compose word semantics.
 %To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
@@
 Therefore, domain experts wish to understand whether attention alone is sufficient to capture sentence structure;
-and, more importantly, what kind of benefit the additional information from grammar parsing can help address the NLI challenge.
+and, more importantly, what kind of additional information from grammar parsing can help address the NLI challenge.
 
 In the proposed system, we overlay the sentence dependency tree with the attention, which enables researchers to conduct comparisons between attention and grammar structure.
-As illustrated in Fig.~\ref{fig:depTreeExample}(a), the prediction of the sentence pair (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is wrong.
+As illustrated in Fig.~\ref{fig:depTreeExample}(a), the prediction of the sentence pair (\textbf{P}: ``A woman in a green jacket is drinking tea.'' \textbf{H}: ``A woman is drinking green tea.'') is wrong.
 We can infer the cause by examining the attention, in which the word \textbf{green} in ``\textbf{green} jacket" is aligned to the \textbf{green} in ``\textbf{green} tea".
@@
 %
-And interestingly, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the alignment of the two \textbf{greens} to be zero, the prediction label is corrected (\emph{neutral}).
+Interestingly, as illustrated in Fig.~\ref{fig:depTreeExample}(b), by editing the attention and forcing the alignment of the two \textbf{greens} to be zero, the prediction label is corrected (\emph{neutral}).
 
@@
 %
-In some way, we can think of such a process as a natural blend of all previously discussed scenarios.
+We can think of such a process as a natural blend of all previously discussed scenarios.
 However, instead of having a specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-the-ordinary behaviors in the model.

### 2018-06-26 paper/itemizedReviewResponse.txt
minor fix

@@
 A: The exact computation of attention can vary from model to model despite the shared overall concept, i.e., the alignment between words.
-As a result, when we discuss the general concept of attention we cannot fix on a single mathematical formulation.
+As a result, when we discuss the general concept of attention, we cannot fix on a single mathematical formulation.
 The exact formulation for the model we investigated is discussed in Appendix A.
@@
 A: We had added additional details of the collaboration at the beginning of section 4, including the number of NLP collaborators, frequency, duration of the meeting period for the proposed work.
-And we also revised the motivation for these tasks and pointed out their connection with the scenarios discussion in section 6.
+And we also revised the motivation for these tasks and pointed out their connection with the scenarios discussed in section 6.
 
@@
 And the separation between the operation and UI component may also make the description harder to read (require the reader to refer back to the computation discussion when reading about the user interface).
-We believe the revised version provide a decent tradeoff.
+We believe the revised version provides a decent tradeoff.
 
@@
 For a new task (i.e., machine translation), we do not need to include the prediction view for the NLI task.
-We can reuse the attention views to representing the alignment between the original sentence and the translated sentence and introduce new views for visualizing other information that may not present in the NLI model.
-The main idea is to allow user to combine the view/functionality and add new view if necessary to suit their analysis goals.
+We can reuse the attention views for representing the alignment between the original sentence and the translated sentence and introduce new views for visualizing other information that may not present in the NLI model.
+The main idea is to allow the user to combine the view/functionality and add new view if necessary to suit their analysis goals.
 
@@
 
-A: Gradient-based sensitivity analysis can often be carried out for domain that is differentiable (i.e., image pixel values).
-In the proposed work, the challenge of using gradient-based method in NLP actually inspired us to utilize perturbation.
+A: Gradient-based sensitivity analysis can often be carried out for a domain that is differentiable (i.e., image pixel values).
+In the proposed work, the challenge of using the gradient-based method in NLP inspired us to utilize perturbation.
 This point is partly discussed in the introduction where the difference between NLP and CV is highlighted (image has a continuous domain whereas words are discrete).
@@
 
-A: We didn't design a specific list of tasks and the corresponding answers mostly due to the the open-ended analysis goal.
+A: We didn't design a specific list of tasks and the corresponding answers mostly due to the open-ended analysis goal.
 If the user didn't follow the particular exploration path the designer of the question goes, he/she might find some result that not directly related to the "correct" answer.
@@
 A: We moved the description of the collaboration into the beginning of section 4, in which we described the number of NLP experts, frequency, and the duration of the meetings for this specific project.
-We also added a reference to application scenarios that corresponds to the tasks to help instantiate the more abstract concepts.
+We also added a reference to application scenarios that correspond to the tasks to help instantiate the more abstract concepts.
 
@@
 
-A: After discussing with domain experts, we believe the reviewer's comment would be a very interesting direction for future works.
+A: After discussing with domain experts, we believe the reviewer's comment would be an exciting direction for future works.
 Coming up with efficient visual encoding for these types of information that go beyond grammar tree is a challenge on its own.
@@
 Also, the ambiguity between pile and heap may also originate from the word embedding (the numerical representation for words).
-The proposed system suggests to NLP experts that the ambiguity between pile and heap is likely the cause of the incorrect prediction.
-The experts can choose to dive further and examine the root cause.
+The proposed system suggests to NLP experts that the uncertainty between pile and heap is likely the cause of the incorrect prediction.
+The experts can choose to dive further and examine the exact cause.
 

### 2018-06-26 paper/intro.tex
minor fix

@@
 %Based on some stunning recent advances, neural networks based machine learning approaches have gained unprecedented popularity, and have been adopted in a wide variety of applications.
-As demonstrated by many recent successes, neural network-based machine learning approaches have garnered increasing popularity and have been adopted in a wide variety of applications.
+As demonstrated by many recent successes, neural-network-based machine learning approaches have garnered increasing popularity and have been adopted in a wide variety of applications.
 %

### 2018-06-27 paper/itemizedReviewResponse.txt
update revised version

@@
 
-We greatly appreciate all reviewers' valuable comments. The summary of major changes is listed below. We have itemized the 44 questions/comments and answer each individually.
+We greatly appreciate all reviewers' valuable comments. The summary of major changes is listed below. We have itemized the 44 questions/comments and answered each individually.
 
@@
 - Revised the introduction to remove hyperbole words, clarify the NLP vs. CNN data modality comparison, and simplify the contribution list.
-- Clarified the domain experts' involvement at the beginning of section 4 and link the task with the application scenarios.
+- Clarified the domain experts' involvement at the beginning of section 4 and link the tasks with the application scenarios.
 - Revised section 5 to better explain the user interactions and add discussion on how to interpret the visual encodings.
@@
 
-A: The domain experts indeed find this observation very interesting and suggest a preliminary interpretation.
+A: The domain experts indeed find this observation very interesting and suggest a preliminary interpretation (which we included in the revised version).
 They believe the attention provides a way to compose word semantics.
 Individual word semantics are yielded from the encoder and input embedding, while the composed semantics participate in classification layer.
-From the result from Scenario 3, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in classifier).
+From the result of Scenario 3, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in classifier).
 The encoder and classifier layer can swiftly adjust weights for word/composed semantics to correct prediction.

### 2018-06-27 paper/application.tex
update revised version

@@
 However, the attention layer, which only works on how individual words are aligned, affects the prediction less significantly.
-Recent works also support this observation in word embeddings, e.g., ELMo~\cite{salant2017contextualized}, where better word embeddings can substantially benefit a model.
-However, word embeddings by no means implies attention is not useful, because it serves as a way to compose word semantics.
+Recent word embeddings works (e.g., ELMo~\cite{salant2017contextualized}) also support such an observation that better word embeddings can substantially benefit a model.
+However, the result by no means implies attention is not useful, because it serves as a way to compose word semantics.
 %To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.

### 2018-06-27 paper/attention.tex
update revised version

@@
 
-As illustrated in Fig.~\ref{fig:attentionVis}, we employ graph and matrix two visual encodings for visualizing attention.
+As illustrated in Fig.~\ref{fig:attentionVis}, we employ both graph and matrix visual encodings for visualizing attention.
 In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value.
@@
 However, extra effort may be required for identifying the words that correspond to high-value entries in the matrix.
-Together, the graph and matrix views complement each other and provide the same information from different perspectives (a related matrix/graph visualization scheme is presented in \cite{MaKenyonForbes2015} for studying the brain network).
+Together, the graph and matrix views complement each other and provide the same information from different perspectives (a related matrix/graph visualization scheme is explored in \cite{MaKenyonForbes2015} for studying the brain network).
 %As illustrated by the pink arrowed lines, we can see how the same attention value is visualized in both the graph and the matrix view.

### 2018-06-27 paper/prediction.tex
update revised version

@@
 The prediction result for the original sentence pair is represented by the larger yellow circle, whereas the smaller gray circles illustrate the perturbed sentence pairs.
-A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+%A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
+A density contour of the prediction is computed via kernel density estimation to emphasize the highly cluttered areas and distinguish the outliers.
 %\shusen{
-The pattern of the perturbed pairs' prediction directly conveys the stability of the model for the given instance. 
-Here, we should also take the length of the sentence into consideration as more nouns and verbs will likely lead to more varied perturbations.
+The pattern of the perturbed pairs' prediction directly conveys the stability of the model for the given sentence pair. 
+Here, we should also take the length of the sentence into consideration as greater numbers of nouns and verbs will likely lead to more varied perturbations.
 %}
@@
 
-To perturb the prediction (\textbf{T3}) (optimization for solving the prediction perturbation is discussed in Section~\ref{sec:pipeline}), we need a way to communicate the reassignment of the predicted label.
+To perturb the prediction (\textbf{T3}) (the optimization for solving the prediction perturbation is discussed in Section~\ref{sec:pipeline}), we need a way to communicate the reassignment of the predicted label.
 As illustrated in Fig.~\ref{fig:predictionView}(b), we integrate such an operation in the prediction view.

### 2018-06-27 paper/predSummary.tex
finial edit

@@
 The histogram shows the distribution of the prediction stability in the selected category.
-For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and all the perturbed pairs.
+For each example, the stability is defined by the ratio of the number of perturbed pairs that maintain the same predicted label and all the perturbed pairs.
 Assuming we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonyms), the stability is 0.8 if 80 of the 100 maintain the original label.

### 2018-07-23 paper/paper_entailVis.tex
add author list

@@
-% \documentclass[journal]{vgtc}                % final (journal style)
-\documentclass[review,journal]{vgtc}         % review (journal style)
+\documentclass[journal]{vgtc}                % final (journal style)
+%\documentclass[review,journal]{vgtc}         % review (journal style)
 % \documentclass[review,journal]{vgtc}         % review (journal style)
@@
 %% indicate IEEE Member or Student Member in form indicated below
-% \author{Roy G. Biv, Ed Grimley, \textit{Member, IEEE}, and Martha Stewart}
-% \authorfooter{
+ \author{Shusen Liu, Zhimin Li, Tao Li, Vivek Srikumar, Valerio Pascucci, Peer-Timo Bremer}
+ \authorfooter{
+ \vspace{-2mm}
 % %% insert punctuation at end of each item
-% \item
-%  Roy G. Biv is with Starbucks Research. E-mail: roy.g.biv@aol.com.
-% \item
-%  Ed Grimley is with Grimley Widgets, Inc.. E-mail: ed.grimley@aol.com.
-% \item
-%  Martha Stewart is with Martha Stewart Enterprises at Microsoft
-%  Research. E-mail: martha.stewart@marthastewart.com.
-% }
+ \item
+  Shusen Liu, Peer-Timo Bremer is with Lawrence Livermore National Laboratory. E-mail: \{liu42, bremer5\}@llnl.gov.
+ \item
+  Zhimin Li, Valerio Pascucci is with SCI Institute, University of Utah. E-mail: \{zhiminl, pascucci\}@sci.utah.edu.
+  Tao Li, Vivek Srikumar is with School of Computing, University of Utah, E-mail:\{tli,svivek\}@cs.utah.edu
+}
 
@@
 \teaser{
-\vspace{-4mm}
+%\vspace{-4mm}
  % \includegraphics[width=0.78\linewidth]{teaser}
@@
 \acknowledgments{
-The authors wish to thank A, B, and C. This work was supported in part by
-a grant from XYZ (\# 12345-67890).
+This work was performed under the auspices of the U.S.
+Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344.
+This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, and PIPER: ER26142 DE-SC0010498.
+This material is based upon work supported by the Department of Energy, National Nuclear Security Administration, under Award Number(s) DE-NA0002375.
 }

### 2018-07-23 paper/paper_entailVis.tex
fit into the limit

@@
 %% indicate IEEE Member or Student Member in form indicated below
- \author{Shusen Liu, Zhimin Li, Tao Li, Vivek Srikumar, Valerio Pascucci, Peer-Timo Bremer}
+ \author{Shusen Liu, Zhimin Li, Tao Li, Vivek Srikumar, Valerio Pascucci and Peer-Timo Bremer}
  \authorfooter{
@@
  \item
-  Zhimin Li, Valerio Pascucci is with SCI Institute, University of Utah. E-mail: \{zhiminl, pascucci\}@sci.utah.edu.
+  Zhimin Li, Valerio Pascucci is with SCI Institute, University of Utah. E-mail: \{zhimin, pascucci\}@sci.utah.edu.
   Tao Li, Vivek Srikumar is with School of Computing, University of Utah, E-mail:\{tli,svivek\}@cs.utah.edu
@@
 Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344.
-This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, and PIPER: ER26142 DE-SC0010498.
+This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, PIPER: ER26142 DE-SC0010498, and NVIDIA Corporation.
 This material is based upon work supported by the Department of Energy, National Nuclear Security Administration, under Award Number(s) DE-NA0002375.

### 2018-08-01 EMNLP-demo-paper/NLPVis-demo-paper.tex
update figure
minor edits all over
update application

@@
 
-\title{Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension}
+\title{Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension}
 
@@
 Despite their advantages, the lack of interpretability hinders the deployment and refinement of the models.
-%These models often relying on the attention mechanism, which not only helps improve predicting performance but also provide interpretable representations for users to peak into the opaque models that are usually considered as black boxes.
-%
 In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationships among the input, the model internals (i.e., attention), and the output predictions which in turn shed light on the model decision-making processing.
-
 \end{abstract}
@@
 
+\section*{Acknowledgments}
+This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344.
+
 \bibliographystyle{acl_natbib_nourl}
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2018-08-01 paper/application.tex
fit into the limit
update application

@@
 \vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{att2pred}
- \vspace{-6mm}
+ \includegraphics[width=0.9\linewidth]{att2pred}
+ \vspace{-4mm}
  \caption{
@@
 \label{fig:att2pred}
+\vspace{-3mm}
 \end{figure}
@@
 \centering
+\vspace{-3mm}
+ \includegraphics[width=0.95\linewidth]{pipelineUpdate}
   \vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{pipelineUpdate}
-  \vspace{-6mm}
  \caption{
@@
 The domain experts find this observation very interesting and suggest a preliminary interpretation.
-They believe the attention provides a way to compose word semantics.
-Individual word semantics are yielded from the encoder and input embedding, whereas the composed semantics participate in the classification layer.
-From this analysis, we can extrapolate that the ultimate decision relies on the semantics (i.e., encodings and composed encodings in the classifier).
-The encoder and classifier layer can swiftly adjust weights for word/composed semantics to correct prediction.
-However, the attention layer, which only works on how individual words are aligned, affects the prediction less significantly.
+The reason, as they believe, is that the attention layer functions differently from the encoder and the classifier in terms of word semantics.
+The attention layer in this model is more specialized in composing word semantics rather than creating new semantics.
+When it comes to fixing a wrong prediction, attention layer affects the prediction less significantly while the encoder and the classifier can swiftly adapt to the correct label.
+Thus from this analysis, we can extrapolate that the ultimate prediction relies on the semantics (i.e., encodings and composed encodings in the classifier).
 Recent word embeddings works (e.g., ELMo~\cite{salant2017contextualized}) also support such an observation that better word embeddings can substantially benefit a model.
@@
 \vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{depTreeExample}
-  \vspace{-6mm}
+ \includegraphics[width=0.98\linewidth]{DepTreeExample}
+  \vspace{-3mm}
  \caption{

### 2018-08-15 EMNLP-demo-paper/NLPVis-demo-paper.tex
add acknowledgement

@@
 \section*{Acknowledgments}
-This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344.
+This work was performed under the auspices of the U.S.
+Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344.
+This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, PIPER: ER26142 DE-SC0010498, and NVIDIA Corporation.
+This material is based upon work supported by the Department of Energy, National Nuclear Security Administration, under Award Number(s) DE-NA0002375.
 

### 2018-08-17 EMNLP-demo-paper/NLPVis-demo-paper.tex
grammar check for nlp paper

@@
 Despite their advantages, the lack of interpretability hinders the deployment and refinement of the models.
-In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationships among the input, the model internals (i.e., attention), and the output predictions which in turn shed light on the model decision-making processing.
+In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationships among the input, the model internals (i.e., attention), and the output predictions, which in turn shed light on the model decision-making process.
 \end{abstract}

### 2018-08-17 EMNLP-demo-paper/conclusion.tex
grammar check for nlp paper

@@
 \section{Discussion}
-In this work, we introduce a visualization library for creating customized environments that allow the user to interrogate the relationship between different parts of the model pipeline via interactive queries.
+In this work, we introduce a visualization library for creating customized environments that allows the user to interrogate the relationships among different parts of the model pipeline via interactive queries.
 %
@@
 %
-We also conducted a small-scale user evaluation, in which five Ph.D.
-level students with NLP background spent 30 minutes with the tool and then provided feedback.
+We also conducted a small-scale user evaluation, in which five Ph.D.-level students with an NLP background spent 30 minutes with the tool and then provided feedback.
 Most suggested the environment allowed them to refine queries iteratively and identify potential issues with the model, but some also mentioned the tool might not provide enough guidance for users who do not have an in-depth understanding of the model at hand.
 
-Even though we designed the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure compatibility with all the available configurations.
+Even though we designed the individual components with versatility in mind, due to a large number of variants of attention networks, we found it difficult to ensure compatibility with all the available configurations.
 %

### 2018-08-17 EMNLP-demo-paper/intro.tex
grammar check for nlp paper

@@
 %where end-to-end training become a primary option.
-As the design of neural networks evolves, there is a clear trend of increasing model complexity in terms of both the architecture and the parameter count. 
+As the design of neural networks evolves, there is a trend of increasing model complexity become clear in terms of both the architecture and the parameter count. 
 %
-While expressive models help improve the prediction performance, the fundamental lack of interpretability leads many researchers to consider neural network models black boxes. 
+Although expressive models help improve the prediction performance, the fundamental lack of interpretability leads many researchers to consider neural network models black boxes. 
 %
@@
 
-Recently, the attention networks have become  widely-adopted~\cite{bahdanau2014neural,seo2016bidirectional,Parikh2016, VaswaniShazeerParmar2017}.
-It not only improves the model performance but also yields interpretable intermediate representations (i.e., alignment among words).
+Recently, the attention networks have recently become  widely-adopted~\cite{bahdanau2014neural,seo2016bidirectional,Parikh2016, VaswaniShazeerParmar2017}.
+Attention not only improves the model performance but also yields interpretable intermediate representations (i.e., alignment among words).
 As a result, attention can provide a natural interface for analyzing the internals of neural networks.
-Conducting analysis directly on the raw attention values can be challenging for human users, and therefore, visual representations that highlight word alignments between sentences have been proposed, such as bipartite graph and heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
+Conducting analysis directly on the raw attention values can be challenging for human users, and therefore, visual representations that highlight word alignments between sentences have been proposed, such as the bipartite graph and the heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.
 However, many challenges remain.
@@
 Also, many previous works present the attention in a static setting.
-However, the ability to provide an interactive environment, in which the user can instantaneously look at how changes in the input affect the attention, and how small variations in the attention alter the prediction, is crucial for interpreting the model.
+However, the ability to provide an interactive environment in which the user can instantaneously look at how changes in the input affect the attention, and how small variations in the attention alter the prediction, is crucial for interpreting the model.
 Finally, many previous visualization efforts, despite revealing many exciting results, focus more on illustrating potentially useful visualization techniques than on providing a flexible software tool that can be easily integrated into an existing code base.
-As a result, applying these proposed techniques to real-world examples may involve substantial engineering effort that could prevent wide adoption.
+As a result, applying these proposed techniques to real-world examples may involve substantial engineering effort, which could prevent wide adoption.
 

### 2018-08-17 EMNLP-demo-paper/relatedWorks.tex
grammar check for nlp paper

@@
 %
-In recent work,~\citet{LiChenHovy2015} investigated the composability of the vector-based text representations using instance-level attribution techniques originated from the vision community~\cite[e.g.,][]{ZeilerFergus2014}.
+In recent work,~\citet{LiChenHovy2015} investigated the composability of the vector-based text representations using instance-level attribution techniques that originated from the vision community~\cite[e.g.,][]{ZeilerFergus2014}.
 %
-In a study of the representation of erasure, \citet{li2016understanding} explained neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
+In a study of the representation of erasure, \citet{li2016understanding} explained neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units or input words) on the prediction performance.
 
-Besides interpreting the model via carefully designed experiments, several interactive demo/visualization systems, such as AllenNLP's demos (\url{http://demo.allennlp.org/})  often rely on visual encodings to summarize the model predictions.
-They  provide a flexible environment in which the user can experiment with the various inputs and perform error analysis.
+Besides interpreting the model via carefully designed experiments, several interactive demo/visualization systems, such as AllenNLP's demos (\url{http://demo.allennlp.org/}), often rely on visual encodings to summarize the model predictions.
+These systems provide a flexible environment in which the user can experiment with the various inputs and perform error analysis.
 %The training dynamic of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and 
@@
 \citet{lee2017interactive} visualized the beam search and attention component in neural machine translation models, in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
-In the visualization work on question answering~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that is used to answers the question. 
+In the visualization work on question answering~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that is used to answer the question. 
 %The user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.

### 2018-08-17 EMNLP-demo-paper/result.tex
figure spacing
grammar check for nlp paper

@@
 \centering
-\vspace{-2mm}
  \includegraphics[width=1.0\linewidth]{NLIexample}
-  \vspace{-7mm}
+  \vspace{-6mm}
  \caption{
@@
 }
-\vspace{-2mm}
 \label{fig:NLIexample}
@@
 
+\begin{figure*}[t]
+\centering
+ \includegraphics[width=1.0\linewidth]{MC_interface}
+  \vspace{-6mm}
+ \caption{
+In the machine comprehension visualization interface (a), the $p1$, $p2$ colored bar (in $a3$) illustrates the predicted start and end index of the answer in the context (the deeper the red, the higher the probability).
+The most likely answer is shown in ($a1$).
+The global attention and local attention are visualized by ($a2$, $a3$).
+%
+We can evaluate the robustness of the prediction by perturbing the question sentence ($b1$, $b3$).
+As illustrated in ($b1$, $b2$), by removing the word ``partial'', the model still finds the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
+}
+\vspace{-2mm}
+\label{fig:MCexample}
+\end{figure*}
+
 \subsection{Machine Comprehension}
@@
 %$s$ and $e$.
-The attention information is encoded as a bi-directional alignment (i.e., from context to question and vice versa). 
+The attention information is encoded as a bidirectional alignment (i.e., from context to question and vice versa). 
 %The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
-Here, we refer the context to question attention as \emph{att1}; and the question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}).
+Here, we refer the context to question attention as \emph{att1} and the question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}).
 In this demo, we apply a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values.
-
-\begin{figure*}[t]
-\centering
-\vspace{-2mm}
- \includegraphics[width=1.0\linewidth]{MC_interface}
-  \vspace{-7mm}
- \caption{
-In the machine comprehension visualization interface (a), the $p1$, $p2$ colored bar (in $a3$) illustrates the predicted start and end index of the answer in the context (the deeper the red, the higher the probability).
-The most likely answer is shown in ($a1$).
-The global attention and local attention are visualized by ($a2$, $a3$).
-%
-We can evaluate the robustness of the prediction by perturbing the question sentence ($b1$, $b3$).
-As illustrated in ($b1$, $b2$), by removing the word ``partial'', the model still finds the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question).
-}
-\label{fig:MCexample}
-\end{figure*}
 
@@
 %The spans of text with high probability are ``Two'' and ``No'' (highlight in orange), both align well with the word ``many''.
-Interestingly, the number ``9'' (in ``Falcon 9') is also aligned with ``many'', which may lead to problems.
+Interestingly, the number "9" (in "Falcon 9") is also aligned with "many", which may lead to problems.
 
@@
 %
-As illustrated in ($b1$, and $b2$), the perturbation removes the word ``partial'' in the original sentence, which leads the model to produce a different yet correct answer (``No'').
-Referring to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
+As illustrated in ($b1$, and $b2$), the perturbation removes the word "partial" in the original sentence, which leads the model to produce a different yet correct answer ("No").
+Referring to ($a1$), we can see the word "No" exhibits the second highest probability for the original question.
 %
-The user can also manually edit the text. As shown in ($b3$), the model still produces the correct answer when changing the question from ``how many'' to ``which''.
+The user can also manually edit the text. As shown in ($b3$), the model still produces the correct answer when changing the question from "how many" to "which".
 %One possible explanation is that the word ``Two'' has a much higher \emph{att2} attention value compared to ``9'', which may contribute to the current outcome.

### 2018-08-17 EMNLP-demo-paper/system.tex
figure spacing
grammar check for nlp paper

@@
 As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP models follow a similar encoder--attention--classifier structure.
-The attention stage provides a window to peek into the model decision making process.
+The attention stage provides a window to peek into the model decision-making process.
 However, the static attention alone does not tell the whole story. 
-Our proposed system uses a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes downstream.
+Our proposed system uses a perturbation-driven exploration strategy that allows the user to manually or automatically perturb part of the pipeline and observe the changes downstream.
 %
@@
 
-To improve the perturbation quality, we also allow for a translation-based paraphrasing technique similar to \citet{mallinson2017paraphrasing}.
+To improve the perturbation quality, we also allow for a translation-based paraphrasing technique similar to that proposed by \citet{mallinson2017paraphrasing}.
 Here, we translate the original English sentence into several other languages and then pivot back to English.
-Provided the translation produces good result (in our case, we use the Google cloud translation platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).
+Provided the translation produces a good result (in our case, we use the Google Cloud Translation Platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).
 
@@
 \centering
-\vspace{-2mm}
+%\vspace{-2mm}
  \includegraphics[width=0.8\linewidth]{prediction}
@@
 For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded via a triangular barycentric coordinate system, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}).
-The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.
+The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller gray circles.
 
@@
 %
-For highly asymmetric attention, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting the summary visualization.
+For highly asymmetric attention, we utilize a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting the summary visualization.
 }
@@
 we implement the proposed system as a Python library with modularity and ease of use in mind.
-The different pieces of the visualization (i.e., matrix-based attention encoding) can be accessed individually, 
-or combined with other components to fit one's work-flow via a simple API.
-More importantly, the library-based design allows easy integration with the existing model implemented in python.
+The different pieces of the visualization (i.e., matrix-based attention encoding) can be accessed individually or combined with other components to fit one's workflow via a simple API.
+More importantly, the library-based design allows easy integration with the existing model implemented in Python.
 %To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models.

### 2018-08-17 EMNLP-demo-paper/result.tex
fix quote mark problem

@@
 %
-To correct the mistake, we can edit the attention value and remove the align between these two "greens" (see (c)(b)).
+To correct the mistake, we can edit the attention value and remove the align between these two ``greens" (see (c)(b)).
 As expected, the prediction label is corrected (\emph{neutral}).
@@
 %The spans of text with high probability are ``Two'' and ``No'' (highlight in orange), both align well with the word ``many''.
-Interestingly, the number "9" (in "Falcon 9") is also aligned with "many", which may lead to problems.
+Interestingly, the number ``9" (in ``Falcon 9") is also aligned with ``many", which may lead to problems.
 
@@
 %
-As illustrated in ($b1$, and $b2$), the perturbation removes the word "partial" in the original sentence, which leads the model to produce a different yet correct answer ("No").
-Referring to ($a1$), we can see the word "No" exhibits the second highest probability for the original question.
+As illustrated in ($b1$, and $b2$), the perturbation removes the word ``partial" in the original sentence, which leads the model to produce a different yet correct answer (``No").
+Referring to ($a1$), we can see the word ``No" exhibits the second highest probability for the original question.
 %
-The user can also manually edit the text. As shown in ($b3$), the model still produces the correct answer when changing the question from "how many" to "which".
+The user can also manually edit the text. As shown in ($b3$), the model still produces the correct answer when changing the question from ``how many" to ``which".
 %One possible explanation is that the word ``Two'' has a much higher \emph{att2} attention value compared to ``9'', which may contribute to the current outcome.

### 2018-08-17 EMNLP-demo-paper/result.tex
minor fix in result

@@
 As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pair (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
-By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea".
-However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction.
+By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea." However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction.
 The grammatical structure is visually shown in the form of the dependency tree.

### 2018-08-17 EMNLP-demo-paper/result.tex
change fig.-> figure

@@
 
-As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pair (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
+As illustrated in Figure~\ref{fig:NLIexample}(a), the input sentence pair (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
 By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea." However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction.

### 2018-08-17 EMNLP-demo-paper/system.tex
change fig.-> figure

@@
 %
-In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), the edge thickness corresponds to the attention value of the word pairs.
+In the graph attention view (Figure~\ref{fig:attentionVis}(a)), the edge thickness corresponds to the attention value of the word pairs.
 %The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
 The graph view is suitable for highlighting the most dominant alignments. However, the edges may become cluttered if multiple attention values are high. 
-The matrix attention view (Fig.~\ref{fig:attentionVis}(b)) resolves these issues, despite being more verbose and less efficient in highlighting the most dominant alignments. 
-We also enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), where one alignment relationship is highlighted).
+The matrix attention view (Figure~\ref{fig:attentionVis}(b)) resolves these issues, despite being more verbose and less efficient in highlighting the most dominant alignments. 
+We also enable the linkage between highlighted actions in both views (see Figure~\ref{fig:attentionVis}(a)(b), where one alignment relationship is highlighted).
 

### 2018-08-20 EMNLP-demo-paper/NLPVis-demo-paper.tex
update camera ready

@@
 \section*{Acknowledgments}
-This work was performed under the auspices of the U.S.
-Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344.
-This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, PIPER: ER26142 DE-SC0010498, and NVIDIA Corporation.
+This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344. 
+This work is also supported in part by NSF: CGV: Award: 1314896, NSF: IIP: Award: 1602127, NSF: ACI: award: 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, PIPER: ER26142 DE-SC0010498, and NVIDIA Corporation.
 This material is based upon work supported by the Department of Energy, National Nuclear Security Administration, under Award Number(s) DE-NA0002375.

### 2018-08-20 EMNLP-demo-paper/intro.tex
update camera ready

@@
 %where end-to-end training become a primary option.
-As the design of neural networks evolves, there is a trend of increasing model complexity become clear in terms of both the architecture and the parameter count. 
+As the design of neural networks evolves, there is a clear trend of increasing model complexity in terms of both the architecture and the parameter count. 
 %
@@
 The ability to interpret model internals and reason about predictions is essential for understanding the limitation of the models and improving upon them.
-
-%Without understanding the background meaning that features carry, visualization relies
-%on proper quantification analysis (cite). Such analysis is not easy to come up with,
-%and is tied to specific task (cite).
 
@@
 inference (NLI) and machine comprehension (MC).
-%For the NLI task, we visualize
-%decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
-%For the MC task, we present your visualization methods on bidirectional attention flow model,
-%which also represents a line of state-of-the-art models \cite{Seo2016}.
 

### 2018-08-20 EMNLP-demo-paper/result.tex
update camera ready

@@
 We demonstrate the proposed visualization system on the decomposable attention network~\cite{parikh2016emnlp}
-for the NLI task and the BIDAF model~\cite{Seo2016} for the MC task.
+for the NLI task and the BIDAF model~\cite{seo2016bidirectional} for the MC task.
 
@@
 %The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
-Here, we refer the context to question attention as \emph{att1} and the question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}).
+Here, we refer the context to question attention as \emph{att1} and the question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{seo2016bidirectional}).
 In this demo, we apply a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values.

### 2018-09-06 gateVis-paper/intro.tex
add template

The, recently several visualization work has focused on visualizing the recurrent neural network such as the long-short term memory (LSTM) network

### 2018-09-07 gateVis-paper/intro.tex
update comments

@@
+Outline
+\begin{itemize}
+    \item the important of LSTM/RNN
+    \item the criptic natural of the hidden state, where a single state represents the whole sequence
+    \item the need to understand how does the model remember and forget? especially in analysis long sequence in the real world scenarios
+    \item Understand how the gate affect the prediction
+\end{itemize}
+
+Many recent advances of neural language processing is driven by the continoues evolving and improving of the recurrent neural networks.
+These model processes information in a sequenctial fashion, which can easily handle the flexible and variable length
+
 The, recently several visualization work has focused on visualizing the recurrent neural network such as the long-short term memory (LSTM) network

### 2018-10-02 visPackage/static/components/sentenceComponent.js
fix prediction indexing

@@ -52,8 +52,8 @@ class sentenceComponent extends baseComponent {
                 this.onReceiveSentenceList();
                 break;
             case "currentPair":
-                // console.log(msg, this.data["currentPair"]["sentences"]);
                 let pair = msg["data"]["data"]["sentences"];
+                // console.log("sentenceComponent:", pair);
                 if (this.oldPair) {
                     if (this.oldPair[0].split(" ").length !== pair[0].split(
                             " ").length ||
@@ -62,13 +62,12 @@ class sentenceComponent extends baseComponent {
                     ) {
                         this.clearDropdown(this.div + "srcInput");
                         this.clearDropdown(this.div + "targInput");
-                        console.log("refresh the allSourceSens");
+                        // console.log("refresh the allSourceSens");
                     }
                 }
 
                 this.onReceiveCurrentPair();
                 this.oldPair = JSON.parse(JSON.stringify(pair));
-
                 break;
         }
     }
@@ -103,22 +102,6 @@ class sentenceComponent extends baseComponent {
     onReceiveCurrentPair() {
         var currentPair = this.data['currentPair']["sentences"];
 
-        this.clearPreviousPair();
-        // console.log(this.data["currentPair"]["sentences"]);
-
-        // if (currentPair[0].startsWith("<s>")) {
-        //     this.source = currentPair[0].substring(4);
-        //     this.target = currentPair[1].substring(4);
-        //     if (this.data["allTargetSens"])
-        //         this.orig_source = this.data["allTargetSens"][0].substring(
-        //             4);
-        //
-        // } else {
-        //     this.source = currentPair[0];
-        //     this.target = currentPair[1];
-        //     if (this.data["allTargetSens"])
-        //         this.orig_source = this.data["allTargetSens"][0];
-        // }
         this.source = currentPair[0].substring(4);
         this.target = currentPair[1].substring(4);
 
@@ -142,6 +125,7 @@ class sentenceComponent extends baseComponent {
                 className: 'blue'
             });
         }
+        // console.log(currentPair);
     }
 
     onChangeOriginalPair() {
@@ -190,6 +174,7 @@ class sentenceComponent extends baseComponent {
     }
 
     updatePerturbedSentences(sentences) {
+        //sentences[0] is the unperturbed sentence
         if (this.data["currentPair"]["sentences"][0] === "<s> " + sentences[
                 0]) {
             this.setData("allSourceSens", sentences.map(d => "<s> " + d));

### 2018-10-02 visPackage/static/plot/treeMapPlot.js

@@ -26,7 +26,7 @@ class treeMapPlot {
             values: nestData
         }
 
-        console.log(data);
+        // console.log(data);
         return data;
     }
 
